### 2023-02-15 Code/initial_implementation.Rmd
Initial Implementation

```{r}
set.seed(1234)
mystat <- function(x) {
    c(c(x),  # Bootstrap will return actual pseudo-sample, mean, and standard deviation
      mean(x),
      sd(x))
}
```

```{r}
n <- 100
phi <- 0.5
blksize <- 6
B = 100

mysim <- function(n, phi, blksize, B) {
  if (phi == 0) {
    x <- rnorm(n)
  } else {
    x <- arima.sim(list(ar = phi), n = n) * sqrt(1 - phi^2)
  }
  bts <- boot::tsboot(x, mystat, l = blksize, sim = "fixed", R = B)
  list_cdf <- matrix(, nrow = 0, ncol = n)
  list_theta <- matrix(, nrow = 0, ncol = 2)
  sum_theta <- 0
  for (i in 1:B) {
    list_cdf <- rbind(list_cdf, c(ecdf(bts$t[i, (1:n)])(sort(bts$t0[1:n]))))
    list_theta <- rbind(list_theta, c(bts$t[i, -(1:n)]))
  }
  exp_cdf <- colMeans(list_cdf)
  exp_theta <- colMeans(list_theta)
  ks_values <- c()
  for (i in 1:B) {
    ks_values <- c(ks_values, max(abs(sqrt(n) * (list_cdf[i,] - exp_cdf - pnorm(sort(bts$t0[1:n]), list_theta[i, 1], list_theta[i, 2]) + pnorm(sort(bts$t0[1:n]), exp_theta[1], exp_theta[2])))))
  }
  c(ks_values)
}

```

```{r}
print(mysim(n, phi, blksize, B))
```

### 2023-02-16 Code/initial_implementation.Rmd
Format Changes

@@
 ```{r}
-n <- 100
-phi <- 0.5
-blksize <- 6
-B = 100
-
 mysim <- function(n, phi, blksize, B) {
@@
   bts <- boot::tsboot(x, mystat, l = blksize, sim = "fixed", R = B)
-  list_cdf <- matrix(, nrow = 0, ncol = n)
-  list_theta <- matrix(, nrow = 0, ncol = 2)
+  list_cdf <- matrix(, nrow = 0, ncol = n) # initialize list of ecdf applied to original sample values
+  list_theta <- matrix(, nrow = 0, ncol = 2) # initialize list of theta
+  # bts$t[i, (1:n)] : values of bootstrap sample
+  # bts$t[i, -(1:n)] : theta (mu, and sigma)
+  # sort(bts$t0[1:n]) : original sample values sorted
   sum_theta <- 0
@@
 ```{r}
+n <- 100
+phi <- 0.5
+blksize <- 6
+B = 100
 print(mysim(n, phi, blksize, B))

### 2023-02-22 Code/initial_implementation.Rmd
Code Update

--- 2023-02-15 Code/initial_implementation.Rmd
@@
 set.seed(1234)
-mystat <- function(x) {
+mystat <- function(x, dist) {
     c(c(x),  # Bootstrap will return actual pseudo-sample, mean, and standard deviation
-      mean(x),
-      sd(x))
+      MASS::fitdistr(x, dist)$estimate)
 }
@@
 ```{r}
-n <- 100
-phi <- 0.5
-blksize <- 6
-B = 100
+mysim <- function(n, phi, blksize, B, dist, f) {
 
-mysim <- function(n, phi, blksize, B) {
   if (phi == 0) {
@@
   }
-  bts <- boot::tsboot(x, mystat, l = blksize, sim = "fixed", R = B)
+  emp <- ecdf(x)(sort(x)) # observed empirical distribution
+  fit_theta <- MASS::fitdistr(x, dist)$estimate # observed fitted values
+  fit <- do.call(f, c(list(sort(x)), as.list(fit_theta))) # observed fitted distribution
+  obsv_ks <- sqrt(n) * max(abs(emp - fit)) # observed ks statistic
+  bts <- boot::tsboot(x, mystat, l = blksize, sim = "fixed", R = B, dist = dist)
   list_cdf <- matrix(, nrow = 0, ncol = n) 
+  # initialize list of each pseudo-sample's ecdf applied to original sample values
   list_theta <- matrix(, nrow = 0, ncol = 2) 
+  # initialize list of each pseudo-sample's fitted theta
+  # bts$t[i, (1:n)] : values of bootstrap sample
+  # bts$t[i, -(1:n)] : theta (mu, and sigma)
   sum_theta <- 0
   for (i in 1:B) {
-    list_cdf <- rbind(list_cdf, c(ecdf(bts$t[i, (1:n)])(sort(bts$t0[1:n]))))
+    list_cdf <- rbind(list_cdf, c(ecdf(bts$t[i, (1:n)])(sort(x))))
     list_theta <- rbind(list_theta, c(bts$t[i, -(1:n)]))
   }
-  exp_cdf <- colMeans(list_cdf)
+  exp_emp_cdf <- colMeans(list_cdf)
   exp_theta <- colMeans(list_theta)
+  exp_fit_cdf <- do.call(f, c(list(sort(x)), as.list(exp_theta)))
+  bias_term <- exp_emp_cdf - exp_fit_cdf
   ks_values <- c()
   for (i in 1:B) {
-    ks_values <- c(ks_values, max(abs(sqrt(n) * (list_cdf[i,] - exp_cdf - pnorm(sort(bts$t0[1:n]), list_theta[i, 1], list_theta[i, 2]) + pnorm(sort(bts$t0[1:n]), exp_theta[1], exp_theta[2])))))
+    emp_cdf <- list_cdf[i,]
+    fit_cdf <- do.call(f, c(list(sort(x)), as.list(list_theta[i, ])))
+    ks_values <- c(ks_values, sqrt(n) * max(abs((emp_cdf - fit_cdf - bias_term))))
   }
-  c(ks_values)
+  c(length(which(ks_values > obsv_ks)) / n)
 }
@@
 ```{r}
-print(mysim(n, phi, blksize, B))
+n <- 100
+phi <- -0.4
+blksize <- 6
+B = 100
+dist = 'normal'
+f = pnorm
+print(mysim(n, phi, blksize, B, dist, f))
 ```
+```{r}
+phi <- -0.4
+(d_n_0.4 <- replicate(100, mysim(n, phi, blksize, B, dist, f)))
+hist(d_n_0.4)
+```
+```{r}
+phi <- -0.2
+(d_n_0.2 <- replicate(100, mysim(n, phi, blksize, B, dist, f)))
+hist(d_n_0.2)
+```
+```{r}
+phi <- 0
+(d_n_0 <- replicate(100, mysim(n, phi, blksize, B, dist, f)))
+hist(d_n_0)
+```
+```{r}
+phi <- 0.2
+(d_0.2 <- replicate(100, mysim(n, phi, blksize, B, dist, f)))
+hist(d_0.2)
+```
+```{r}
+phi <- 0.4
+(d_0.4 <- replicate(100, mysim(n, phi, blksize, B, dist, f)))
+hist(d_0.4)
+```

### 2023-09-16 Code/initial_implementation.Rmd
Created New Directories

--- 2023-02-15 Code/initial_implementation.Rmd
@@
   }
-  bts <- boot::tsboot(x, mystat, l = blksize, sim = "fixed", R = B)
+  emp <- ecdf(x)(sort(x)) # observed empirical distribution
+  fit_theta <- MASS::fitdistr(x, dist)$estimate # observed fitted values
+  fit <- do.call(f, c(list(sort(x)), as.list(fit_theta))) # observed fitted distribution
+  obsv_ks <- sqrt(n) * max(abs(emp - fit)) # observed ks statistic
+  bts <- boot::tsboot(x, mystat, l = blksize, sim = "fixed", R = B, dist = dist)
   list_cdf <- matrix(, nrow = 0, ncol = n) 
+  # initialize list of each pseudo-sample's ecdf applied to original sample values
   list_theta <- matrix(, nrow = 0, ncol = 2) 
+  # initialize list of each pseudo-sample's fitted theta
+  # bts$t[i, (1:n)] : values of bootstrap sample
+  # bts$t[i, -(1:n)] : theta (mu, and sigma)
   sum_theta <- 0
   for (i in 1:B) {
-    list_cdf <- rbind(list_cdf, c(ecdf(bts$t[i, (1:n)])(sort(bts$t0[1:n]))))
+    list_cdf <- rbind(list_cdf, c(ecdf(bts$t[i, (1:n)])(sort(x))))
     list_theta <- rbind(list_theta, c(bts$t[i, -(1:n)]))
   }
-  exp_cdf <- colMeans(list_cdf)
+  exp_emp_cdf <- colMeans(list_cdf)
   exp_theta <- colMeans(list_theta)
+  exp_fit_cdf <- do.call(f, c(list(sort(x)), as.list(exp_theta)))
+  bias_term <- exp_emp_cdf - exp_fit_cdf
   ks_values <- c()
   for (i in 1:B) {
-    ks_values <- c(ks_values, max(abs(sqrt(n) * (list_cdf[i,] - exp_cdf - pnorm(sort(bts$t0[1:n]), list_theta[i, 1], list_theta[i, 2]) + pnorm(sort(bts$t0[1:n]), exp_theta[1], exp_theta[2])))))
+    emp_cdf <- list_cdf[i,]
+    fit_cdf <- do.call(f, c(list(sort(x)), as.list(list_theta[i, ])))
+    ks_values <- c(ks_values, sqrt(n) * max(abs((emp_cdf - fit_cdf - bias_term))))
   }
-  c(ks_values)
+  c(mean(ks_values > obsv_ks))
 }
@@
 ```{r}
-print(mysim(n, phi, blksize, B))
+n <- 200
+phi <- -0.4
+blksize <- 6
+B = 1000
+dist = 'normal'
+f = pnorm
+print(mysim(n, phi, blksize, B, dist, f))
 ```
+```{r}
+phi <- -0.4
+d_n_0.4 <- replicate(1000, mysim(n, phi, blksize, B, dist, f))
+hist(d_n_0.4)
+```
+```{r}
+phi <- -0.2
+d_n_0.2 <- replicate(1000, mysim(n, phi, blksize, B, dist, f))
+hist(d_n_0.2)
+```
+```{r}
+phi <- 0
+(d_n_0 <- replicate(1000, mysim(n, phi, blksize, B, dist, f)))
+hist(d_n_0)
+```
+```{r}
+phi <- 0.2
+(d_0.2 <- replicate(1000, mysim(n, phi, blksize, B, dist, f)))
+hist(d_0.2)
+```
+```{r}
+phi <- 0.4
+(d_0.4 <- replicate(1000, mysim(n, phi, blksize, B, dist, f)))
+hist(d_0.4)
+```

### 2023-09-16 manuscript/manuscript.tex
Created New Directories

\documentclass[12pt, letterpaper]{article}
%\documentclass[12pt, letterpaper, titlepage]{article}

\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{colorlinks = true, linkcolor = blue, citecolor=blue, urlcolor = blue}
\usepackage{natbib}
\usepackage{enumitem}
\usepackage{setspace}

\usepackage[]{lineno}
\linenumbers*[1]
% %% patches to make lineno work better with amsmath
\newcommand*\patchAmsMathEnvironmentForLineno[1]{%
 \expandafter\let\csname old#1\expandafter\endcsname\csname #1\endcsname
 \expandafter\let\csname oldend#1\expandafter\endcsname\csname end#1\endcsname
 \renewenvironment{#1}%
 {\linenomath\csname old#1\endcsname}%
 {\csname oldend#1\endcsname\endlinenomath}}%
\newcommand*\patchBothAmsMathEnvironmentsForLineno[1]{%
 \patchAmsMathEnvironmentForLineno{#1}%
 \patchAmsMathEnvironmentForLineno{#1*}}%

\AtBeginDocument{%
 \patchBothAmsMathEnvironmentsForLineno{equation}%
 \patchBothAmsMathEnvironmentsForLineno{align}%
 \patchBothAmsMathEnvironmentsForLineno{flalign}%
 \patchBothAmsMathEnvironmentsForLineno{alignat}%
 \patchBothAmsMathEnvironmentsForLineno{gather}%
 \patchBothAmsMathEnvironmentsForLineno{multline}%
}

% control floats
\renewcommand\floatpagefraction{.9}
\renewcommand\topfraction{.9}
\renewcommand\bottomfraction{.9}
\renewcommand\textfraction{.1}
\setcounter{totalnumber}{50}
\setcounter{topnumber}{50}
\setcounter{bottomnumber}{50}

\newcommand{\jy}[1]{\textcolor{blue}{JY: #1}}
\newcommand{\eds}[1]{\textcolor{red}{EDS: (#1)}}

% NOTE: To produce blinded version, replace "0" with "1" below.
\newcommand{\blind}{0}

\begin{document}
%\maketitle

\if0\blind
{
  \title{\bf Nonparametric Bootstrap KS Test with Stationary Time Series}
  \author{Mathew Chandy, %\\
%   \href{mailto:mathew.chandy@uconn.edu}
% {\nolinkurl{mathew.chandy@uconn.edu}}\\
  Jun Yan, %\\
  Xianyang Zhang\\
}
\date{}
  \maketitle
} \fi

\if1\blind
{
  \bigskip
  \bigskip
  \bigskip
  \begin{center}
    {\LARGE\bf Nonparametric Bootstrap KS Test with Stationary Time Series}
\end{center}
  \bigskip
} \fi

\doublespace

\begin{abstract}

\bigskip
\noindent{\sc Keywords}:
\end{abstract}

%\doublespace

\section{Introduction}
\label{sec:intro}

\section{Concluding Remarks}
\label{sec:conclusion}

\bibliographystyle{chicago}
\bibliography{citations}

\end{document}
%%% LocalWords: nonparametric semiparametric autocorrelation ARMA
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% ispell-personal-dictionary: ".aspell.en.pws"
%%% fill-column: 80
%%% eval: (auto-fill-mode 1)
%%% End:

### 2023-09-16 code/simulation.Rmd
Renamed Code

```{r}
set.seed(1234)
mystat <- function(x, dist) {
    c(c(x),  # Bootstrap will return actual pseudo-sample, mean, and standard deviation
      MASS::fitdistr(x, dist)$estimate)
}
```

```{r}
mysim <- function(n, blksize, B, dist, f, phi = 0, theta = 0) {
  if (mean(phi == 0)) {
      x <- arima.sim(list(ma = theta), n = n) / sqrt(1 + sum(theta^2))
  } else {
      x <- arima.sim(list(ar = phi, ma = theta), n = n) * sqrt(1 - sum(phi^2) / 1 + sum(theta^2))
  }
  emp <- ecdf(x)(sort(x)) # observed empirical distribution
  fit_theta <- MASS::fitdistr(x, dist)$estimate # observed fitted values
  fit <- do.call(f, c(list(sort(x)), as.list(fit_theta))) # observed fitted distribution
  obsv_ks <- sqrt(n) * max(abs(emp - fit)) # observed ks statistic
  bts <- boot::tsboot(x, mystat, l = blksize, sim = "fixed", R = B, dist = dist)
  list_cdf <- matrix(, nrow = 0, ncol = n) 
  # initialize list of each pseudo-sample's ecdf applied to original sample values
  list_theta <- matrix(, nrow = 0, ncol = 2) 
  # initialize list of each pseudo-sample's fitted theta
  # bts$t[i, (1:n)] : values of bootstrap sample
  # bts$t[i, -(1:n)] : theta (mu, and sigma)
  sum_theta <- 0
  for (i in 1:B) {
    list_cdf <- rbind(list_cdf, c(ecdf(bts$t[i, (1:n)])(sort(x))))
    list_theta <- rbind(list_theta, c(bts$t[i, -(1:n)]))
  }
  exp_emp_cdf <- colMeans(list_cdf)
  exp_theta <- colMeans(list_theta)
  exp_fit_cdf <- do.call(f, c(list(sort(x)), as.list(exp_theta)))
  bias_term <- exp_emp_cdf - exp_fit_cdf
  ks_values <- c()
  for (i in 1:B) {
    emp_cdf <- list_cdf[i,]
    fit_cdf <- do.call(f, c(list(sort(x)), as.list(list_theta[i, ])))
    ks_values <- c(ks_values, sqrt(n) * max(abs((emp_cdf - fit_cdf - bias_term))))
  }
  c(mean(ks_values > obsv_ks))
}

```

```{r ar = -0.3}
nrep = 1000
n = 100
blksize = 5
B = 1000
dist = 'normal'
f = pnorm
phi <- -0.3
theta <- 0
sim_ar1_n.3 <- replicate(nrep, mysim(n, blksize, B, dist, f, phi, theta))
write.csv(sim_ar1_n.3, "../Data/sim_ar1_n.3.csv", row.names = FALSE)
hist(sim_ar1_n.3)
```

```{r ar = -0.2}
nrep = 1000
n = 100
blksize = 5
B = 1000
dist = 'normal'
f = pnorm
phi <- -0.2
theta <- 0
sim_ar1_n.2 <- replicate(nrep, mysim(n, blksize, B, dist, f, phi, theta))
write.csv(sim_ar1_n.2, "../Data/sim_ar1_n.2.csv", row.names = FALSE)
hist(sim_ar1_n.2)
```

```{r ar = -0.1}
nrep = 1000
n = 100
blksize = 5
B = 1000
dist = 'normal'
f = pnorm
phi <- -0.1
theta <- 0
sim_ar1_n.1 <- replicate(nrep, mysim(n, blksize, B, dist, f, phi, theta))
write.csv(sim_ar1_n.1, "../Data/sim_ar1_n.1.csv", row.names = FALSE)
hist(sim_ar1_n.1)
```

```{r ar = 0}
nrep = 1000
n = 100
blksize = 5
B = 1000
dist = 'normal'
f = pnorm
phi <- 0
theta <- 0
sim_ar1_0 <- replicate(nrep, mysim(n, blksize, B, dist, f, phi, theta))
write.csv(sim_ar1_0, "../Data/sim_ar1_0.csv", row.names = FALSE)
hist(sim_ar1_0)
```

```{r ar = .1}
nrep = 1000
n = 100
blksize = 5
B = 1000
dist = 'normal'
f = pnorm
phi <- .1
theta <- 0
sim_ar1_.1 <- replicate(nrep, mysim(n, blksize, B, dist, f, phi, theta))
write.csv(sim_ar1_.1, "../Data/sim_ar1_.1.csv", row.names = FALSE)
hist(sim_ar1_.1)
```

```{r ar = .2}
nrep = 1000
n = 100
blksize = 5
B = 1000
dist = 'normal'
f = pnorm
phi <- .2
theta <- 0
sim_ar1_.2 <- replicate(nrep, mysim(n, blksize, B, dist, f, phi, theta))
write.csv(sim_ar1_.2, "../Data/sim_ar1_.2.csv", row.names = FALSE)
hist(sim_ar1_.2)
```

```{r ar = .3}
nrep = 1000
n = 100
blksize = 5
B = 1000
dist = 'normal'
f = pnorm
phi <- .3
theta <- 0
sim_ar1_.3 <- replicate(nrep, mysim(n, blksize, B, dist, f, phi, theta))
write.csv(sim_ar1_.3, "../Data/sim_ar1_.3.csv", row.names = FALSE)
hist(sim_ar1_.3)
```

```{r ar = .5}
nrep = 1000
n = 100
blksize = 5
B = 1000
dist = 'normal'
f = pnorm
phi <- .5
theta <- 0
sim_ar1_.5 <- replicate(nrep, mysim(n, blksize, B, dist, f, phi, theta))
write.csv(sim_ar1_.5, "../Data/sim_ar1_.5.csv", row.names = FALSE)
hist(sim_ar1_.5)
```

```{r ma = .5}
nrep = 1000
n = 100
blksize = 5
B = 1000
dist = 'normal'
f = pnorm
phi <- 0
theta <- .5
sim_ma1_.5 <- replicate(nrep, mysim(n, blksize, B, dist, f, phi, theta))
write.csv(sim_ma1_.5, "../Data/sim_ma1_.5.csv", row.names = FALSE)
hist(sim_ma1_.5)
```

```{r ar = .5, ma = .3}
nrep = 1000
n = 100
blksize = 5
B = 1000
dist = 'normal'
f = pnorm
phi <- .5
theta <- .3
sim_arma <- replicate(nrep, mysim(n, blksize, B, dist, f, phi, theta))
write.csv(sim_arma, "../Data/sim_arma.csv", row.names = FALSE)
hist(sim_arma)
```

```{r ar = (.5, .3)}
nrep = 1000
n = 100
blksize = 5
B = 1000
dist = 'normal'
f = pnorm
phi <- c(.5, .3)
theta <- 0
sim_ar2 <- replicate(nrep, mysim(n, blksize, B, dist, f, phi, theta))
write.csv(sim_ar2, "../Data/sim_ar2.csv", row.names = FALSE)
hist(sim_ar2)
```

### 2023-10-02 manuscript/manuscript.tex
Added Note to Manuscript

@@
 
+Consider the goodness of fit statistic:
+\begin{equation*}
+KS_n := \sup_x|Y_n(x; \hat\theta)|, 
+Y_n(x; \hat\theta) = \sqrt{n}(F_n(x) - F(x; \hat\theta_n)),
+\end{equation*}
+where $F_n$ denotes the empirical distribution function based on $X_1,...,X_n$.
+We note that
+\begin{equation*}
+Y_n(x; \hat\theta) = \sqrt{n}(F_n(x) - F(x)) - 
+\sqrt{n}(F(x; \hat\theta_n) - F(x)),
+\end{equation*}
+where $F(x)$ is the true cdf (under the null $F(x) = F(x, \theta_0)$ for some
+true parameter $\theta_0$).
+
+Let us first consider the case where $X_i$'s are i.i.d. Denote by $F^*_n$ the
+empirical distribution of the bootstrap sample $X^*_1,...,X^*_n$ and let
+$\hat\theta^*_n$ be the parameter estimate based on the bootstrap samples. 
+Using the bootstrap (asymptotic) theory, we can approximate the distribution of
+\[
+\sqrt{n}(F_n(x) - F(x))
+\]
+by that of
+\[
+\sqrt{n}(F^*_n(x) - F_n(x))
+\]
+and the distribution of
+\[
+\sqrt{n}(F(x; \hat\theta_n) - F(x))
+\]
+by that of
+\[
+\sqrt{n}(F(x; \hat\theta^*_n) - F(x; \hat\theta_n)).
+\]
+Therefore, if we define
+\begin{equation*}
+Y^*_n(x) = \sqrt{n}(F^*_n(x) - F_n(x)) - 
+\sqrt{n}(F(x; \hat\theta^*_n) - F(x; \hat\theta_n)) 
+= \sqrt{n}(F^*_n(x) - F(x; \hat\theta^*_n)) - 
+\sqrt{n}(F_n(x) - F(x; \hat\theta_n)),
+\end{equation*}
+then $KS^*_n := \sup_x|Y^*_n(x)|$ is the bootstrap statistic that is expected
+to approximate the distribution of $KS_n$. We note that the term
+$\sqrt{n}(F_n(x) - F(x; \hat\theta_n))$ is exactly the bias term considered in 
+Babu and Rao (2004).
+
+We now consider the case where $X_i$'s are realizations from a time series and
+$X^*_1,...,X^*_n$ are generated by block bootstrap. In this case, we can 
+approximate the distribution of
+\[
+\sqrt{n}(F_n(x) - F(x))
+\]
+by that of
+\[
+\sqrt{n}(F^*_n(x) - E^*[F^*_n(x)])
+\]
+and the distribution of
+\[
+\sqrt{n}(F(x; \theta_n) - F(x))
+\]
+by that of
+\[
+\sqrt{n}(F(x; \hat\theta^*_n) - F(x; E^*[\hat\theta^*_n])).
+\]
+Here $E^*$ denotes the expectation with respect to the bootstrap distribution
+(i.e., the randomness due to the resampling using block botostrap) conditional
+on the observations $X_1,...,X_n$. We can compute $E^*[F^*_n(x)]$ and 
+$E^*[\hat\theta^*_n]$ numerically (they can also be computed analytically, 
+depending on the types of block bootstrap we use). For example, let 
+$X^*_{1,b},...,X^*_{n,b}$ be the $b$th block bootstrap sample for 
+$1 \leq b \leq B$. One can compute $F^*_{n,b}$ and $\hat\theta^*_{n,b}$ based on
+$X^*_{1,b},...,X^*_{n,b}$. Then
+\begin{equation*}
+E^*[F^*_n(x)] \approx \frac{1}{B}\sum_{b = 1}^BF^*_{n, b}(x),
+E^*[\hat\theta^*_n] \approx \frac{1}{B}\sum_{b = 1}^B\hat\theta^*_{n,b}.
+\end{equation*}
+In this case, we can define
+\begin{equation*}
+Y^*_n(x) = \sqrt{n}(F^*_n(x) - E^*[F^*_n(x)]) - 
+\sqrt{n}(F(x; \hat\theta^*_n) - F(x; E^*[\hat\theta^*_n)]) 
+= \sqrt{n}(F^*_n(x) - F(x; \hat\theta^*_n)) - 
+\sqrt{n}(E^*[F^*_n(x)] - F(x; E^*[\hat\theta^*_n])),
+\end{equation*}
+and $KS^*_n = \sup_x|Y^*_n(x)|$.
+
 \section{Concluding Remarks}

### 2023-10-03 manuscript/manuscript.tex
New Simulations

@@
 
+The Kolgomorov-Smirnov (KS) test is a popular goodness-of-fit statistic that can
+be used to assess how well a sample fits a given distribution.
+
 Consider the goodness of fit statistic:
@@
 
+The rest of the paper is outlined as follows: in the first 
+section, we assess whether the KS
+test works under the null hypothesis, in the second section, we evaluate the 
+test's 
+power when the null hypothesis is false, and in the third section, we end with 
+concluding remarks.
+
+\section{Null Hypothesis}
+\label{sec:null}
+
+\section{Alternative Hypothesis}
+\label{sec:alternative}
+
 \section{Concluding Remarks}

### 2023-10-03 code/functions.R

@@ -44,3 +44,24 @@ mysim <- function(n, blksize, B, dist, f, phi = 0, theta = 0) {
   }
   c(mean(ks_values > obsv_ks)) # Which are greater than the observed ks statistic
 }
+
+plot_p_vals <- function(n, blksize, B, dist, f, phi, theta, nrep = 1000) {
+  df <- data.frame(matrix(NA,    # Create empty data frame
+                          nrow = nrep,
+                          ncol = 1))
+  p <- replicate(nrep, mysim(n, blksize, B, dist, f, phi, theta))
+  df$p <- p
+  ## Section 2: Fitted parameters
+  gg.f <- ggplot(data = df, mapping = aes(sample = p)) +
+    scale_x_continuous(breaks=c(0, 1)) +
+    scale_y_continuous(breaks=c(0, 1)) + 
+    stat_pp_band(distribution = "unif") +
+    stat_pp_line() +
+    stat_pp_point(distribution = "unif", cex = .1) +
+    labs(x = "Probability Points", y = "Cumulative Probability") +
+    coord_fixed() # theme(aspect.ratio=1)
+  ggsave(filename = paste("sim_", n, '_norm_', 
+                          phi, '_', 
+                          theta, ".pdf", sep = ''), plot = gg.f, 
+         path = "../manuscript", height = 4, width = 4)
+}

### 2023-10-10 manuscript/manuscript.tex
Figures

--- 2023-10-02 manuscript/manuscript.tex
@@
 
+The Kolmogorov-Smirnov (KS) statistic is widely used to test if a sample is
+from a given distribution.
+
 \bigskip
@@
 \label{sec:intro}
+
+The Kolmogorov-Smirnov (KS) test is a useful goodness-of-fit statistic. It 
+can be used to see if a population follows a hypothesized distribution and has 
+and can be applied to a variety of fields. It has
+been used to analyze the random distribution of cosmic microwave background 
+radiation \citep{naess2012application}. A common misuse of the KS test is when
+the hypothesized distribution has unspecified parameters. 
+\citet{babu2004goodness} approaches this scenario using basic 
+non-parametric bootstrap. There is also the scenario where both the hypothesized 
+distribution has unspecified parameters and additionally the data are 
+serially dependent. \citet{zeimbekakis2022misuses} demonstrates a remedy for
+this scenario using semi-parametric bootstrap. This study aims to address this
+scenario with non-parametric block bootstrap.
+
+The rest of the paper is outlined as follows: in the first 
+section, we assess whether the KS
+test holds its size; that is, does the test fail to reject the null hypothesis
+when it is true. In the second section, we evaluate the 
+test's power; that is, does the test reject the null hypothesis when it is 
+false.
+Finally, we end with 
+concluding remarks in the third section.
+
+\section{Methods}
+\label{sec:methods}
+
+Consider a stationary time series $\{X_t: t = 1, \ldots, n\}$ with length~$n$. 
+Our goal is to see if the data generating model of the series matches a 
+hypothesized distribution. If the observations in the series were independent, a 
+standard
+nonparametric bootstrap KS test would draw a large number~$B$ bootstrap copies 
+of the observed data, and compute the empirical distribution and a
+fitted distribution from the fitted parameters
+$\hat\theta_n^{(b)}$ for each copy $b = 1, \ldots, B$. ____ When serial 
+dependence is present, the bootstrap procedure 
+needs to preserve the serial dependence. Block bootstrap was motivated for this 
+situation.
 
@@
 
+\section{Null Hypothesis}
+\label{sec:null}
+
+\section{Alternative Hypothesis}
+\label{sec:alternative}
+
 \section{Concluding Remarks}

### 2023-10-10 code/functions.R

@@ -1,20 +1,22 @@
+library(tidyverse)
+library(qqplotr)
 mystat <- function(x, dist) {
   # Bootstrap will return actual pseudo-sample, mean, and standard deviation
   c(c(x),  
     MASS::fitdistr(x, dist)$estimate)
 }
 
-mysim <- function(n, blksize, B, dist, f0, f = qnorm, phi = 0, theta = 0) {
-  # phi cannot be set to 0, but theta can
+mysim <- function(n, blksize, B, dist, f0, f, theta, phi, rho) {
+  # phi cannot be set to 0, but rho can
   if (mean(phi == 0)) {
-    y <- arima.sim(list(ma = theta), n = n) / sqrt(1 + sum(theta^2))
+    y <- arima.sim(list(ma = rho), n = n) / sqrt(1 + sum(rho^2))
   } else {
-    y <- arima.sim(list(ar = phi, ma = theta), n = n) * sqrt(1 - sum(phi^2) / 1 + sum(theta^2))
+    y <- arima.sim(list(ar = phi, ma = rho), n = n) * sqrt(1 - sum(phi^2) / 1 + sum(rho^2))
   }
-  y <- f(pnorm(y))
+  y <- do.call(f, c(list(pnorm(y)), as.list(theta)))
   emp <- ecdf(y)(sort(y)) # observed empirical distribution
   fit_theta <- MASS::fitdistr(y, dist)$estimate # observed fitted values
-  fit <- do.call(f0, c(list(sort(y)), as.list(theta))) # observed fitted distribution
+  fit <- do.call(f0, c(list(sort(y)), as.list(fit_theta))) # observed fitted distribution
   obsv_ks <- sqrt(n) * max(abs(emp - fit)) # observed ks statistic
   
   # Block Bootstrap
@@ -45,11 +47,11 @@ mysim <- function(n, blksize, B, dist, f0, f = qnorm, phi = 0, theta = 0) {
   c(mean(ks_values > obsv_ks)) # Which are greater than the observed ks statistic
 }
 
-plot_p_vals <- function(n, blksize, B, dist, f0, f = qnorm, phi, theta, nrep = 1000) {
+plot_p_vals <- function(n, blksize, B, dist, f0, f, theta, phi, rho, nrep = 1000) {
   df <- data.frame(matrix(NA,    # Create empty data frame
                           nrow = nrep,
                           ncol = 1))
-  p <- replicate(nrep, mysim(n, blksize, B, dist, f0, f, phi, theta))
[…]

### 2023-10-10 code/simulation.R

@@ -1,43 +1,36 @@
 source('functions.R')
-library(tidyverse)
-library(qqplotr)
-
 
 set.seed(0123)
-plot_p_vals(400, 20, 1000, 'normal', pnorm, phi = -0.4, theta = 0)
-
-
-set.seed(1234)
-plot_p_vals(400, 20, 1000, 'normal', pnorm, phi = -0.2, theta = 0)
-
-
-set.seed(2345)
-plot_p_vals(400, 20, 1000, 'normal', pnorm, phi = 0, theta = 0)
-
-
-set.seed(3456)
-plot_p_vals(400, 20, 1000, 'normal', pnorm, phi = 0.2, theta = 0)
-
-
-set.seed(4567)
-plot_p_vals(400, 20, 1000, 'normal', pnorm, phi = 0.4, theta = 0)
-
-
-set.seed(0123)
-plot_p_vals(400, 20, 1000, 'exponential', pexp, qexp, phi = -0.4, theta = 0)
-
+plot_p_vals(200, 1, 1000, 'normal', pnorm, qnorm, c(8,8), 0, 0)
 
 set.seed(1234)
-plot_p_vals(400, 20, 1000, 'exponential', pexp, qexp, phi = -0.2, theta = 0)
-
+plot_p_vals(200, ceiling(200^(1/3)), 1000, 'normal', pnorm, qnorm, 
+            c(8,8), -0.4, 0)
 
 set.seed(2345)
-plot_p_vals(400, 20, 1000, 'exponential', pexp, qexp, phi = 0, theta = 0)
-
+plot_p_vals(200, ceiling(200^(1/3)), 1000, 'normal', pnorm, qnorm, 
+            c(8,8), -0.2, 0)
 
 set.seed(3456)
-plot_p_vals(400, 20, 1000, 'exponential', pexp, qexp, phi = 0.2, theta = 0)
-
+plot_p_vals(200, ceiling(200^(1/3)), 1000, 'normal', pnorm, qnorm, 
+            c(8,8), 0.2, 0)
 
 set.seed(4567)
-plot_p_vals(400, 20, 1000, 'exponential', pexp, qexp, phi = 0.4, theta = 0)
+plot_p_vals(200, ceiling(200^(1/3)), 1000, 'normal', pnorm, qnorm, 
+            c(8,8), 0.4, 0)
+
+set.seed(1234)
[…]

### 2023-10-11 manuscript/manuscript.tex
removed underscores in text that prevented compiling
comments

@@
 
+\jy{double blank liines to better separate paragraphs}
+
 \section{Introduction}
@@
 Consider a stationary time series $\{X_t: t = 1, \ldots, n\}$ with length~$n$.
+\jy{state the null hypothesis explicitly; we are testing the marginal
+  distribution. Point out the challenges.}
 Our goal is to see if the data generating model of the series matches a 
-hypothesized distribution. If the observations in the series were independent, a 
+hypothesized distribution.
+
+\jy{define $\hat\theta_n$}
+If the observations in the series were independent, a 
 standard
@@
 fitted distribution from the fitted parameters
-$\hat\theta_n^{(b)}$ for each copy $b = 1, \ldots, B$. ____ When serial 
+$\hat\theta_n^{(b)}$ for each copy $b = 1, \ldots, B$. When serial 
 dependence is present, the bootstrap procedure 
@@
 
+\jy{No double letter notations}
 Consider the goodness of fit statistic:
 \begin{equation*}
-KS_n := \sup_x|Y_n(x; \hat\theta)|, 
+  T_n := \sup_x|Y_n(x; \hat\theta)|, 
 Y_n(x; \hat\theta) = \sqrt{n}(F_n(x) - F(x; \hat\theta_n)),
@@
 Using the bootstrap (asymptotic) theory, we can approximate the distribution of
+\jy{no need for so many in-display equations}
 \[
@@
 approximate the distribution of
+\jy{No need for in-display}
 \[
@@
 \]
+\jy{change the languages to add variety}
 and the distribution of
@@
 \]
+\jy{no closing a sentence before all the notations are introduced}
 Here $E^*$ denotes the expectation with respect to the bootstrap distribution
@@
 $X^*_{1,b},...,X^*_{n,b}$. Then
-\begin{equation*}
-E^*[F^*_n(x)] \approx \frac{1}{B}\sum_{b = 1}^BF^*_{n, b}(x),
-E^*[\hat\theta^*_n] \approx \frac{1}{B}\sum_{b = 1}^B\hat\theta^*_{n,b}.
-\end{equation*}
+\begin{align*}
+E^*[F^*_n(x)] &\approx \frac{1}{B}\sum_{b = 1}^BF^*_{n, b}(x),\\
+E^*[\hat\theta^*_n] &\approx \frac{1}{B}\sum_{b = 1}^B\hat\theta^*_{n,b}.
+\end{align*}
 In this case, we can define
+\jy{too long}
 \begin{equation*}
@@
 
-\section{Null Hypothesis}
-\label{sec:null}
+\section{Simulation Studies}
+\label{sec:simu}
 
-\section{Alternative Hypothesis}
-\label{sec:alternative}
+\jy{First size and then power}
+
+\section{Real Data Analysis}
+
+\jy{Find some real time series to test for their marginal distributions. Open
+  data, for example, temperatures or stock returns or ...}
 

### 2023-10-18 manuscript/manuscript.tex
New Figures n = 400

@@
 \newcommand{\eds}[1]{\textcolor{red}{EDS: (#1)}}
+\newcommand{\mc}[1]{\textcolor{green}{MC: (#1)}}
 
@@
 {
-  \title{\bf Nonparametric Bootstrap KS Test with Stationary Time Series}
+  \title{\bf Nonparametric Bootstrap Kolmogorov-Smirnov Test with Stationary 
+  Time Series}
   \author{Mathew Chandy, %\\
@@
   \begin{center}
-    {\LARGE\bf Nonparametric Bootstrap KS Test with Stationary Time Series}
+    {\LARGE\bf Nonparametric Bootstrap Kolmogorv-Smirnov Test with Stationary 
+    Time Series}
 \end{center}
@@
 %\doublespace
-
-\jy{double blank liines to better separate paragraphs}
 
@@
   distribution. Point out the challenges.}
-Our goal is to see if the data generating model of the series matches a 
-hypothesized distribution.
+Let $H_0: X_t ~ F$, where if $F$ is a hypothesized distribution with unknown 
+parameters. Let $H_A$ be that $X_t$ does not follow $F$. This is challenging because we are
+dealing with a situation with both unknown parameters and temporal dependence.
+If $X_t ~ F$, the true marginal distribution of $X_t$ has some parameters 
+$\theta$.
 
 \jy{define $\hat\theta_n$}
-If the observations in the series were independent, a 
-standard
-nonparametric bootstrap KS test would draw a large number~$B$ bootstrap copies 
-of the observed data, and compute the empirical distribution and a
-fitted distribution from the fitted parameters
-$\hat\theta_n^{(b)}$ for each copy $b = 1, \ldots, B$. When serial 
-dependence is present, the bootstrap procedure 
-needs to preserve the serial dependence. Block bootstrap was motivated for this 
-situation.
+\mc{addressed}
 
 \jy{No double letter notations}
+\mc{addressed}
 Consider the goodness of fit statistic:
@@
 \end{equation*}
-where $F_n$ denotes the empirical distribution function based on $X_1,...,X_n$.
+where $F_n$ denotes the empirical distribution function based on $X_1,...,X_n$,
+and $\hat\theta_n$ denotes the fitted parameters for the hypothesized 
+distribution fitted onto $X_t$.
 We note that
@@
 
-Let us first consider the case where $X_i$'s are i.i.d. Denote by $F^*_n$ the
-empirical distribution of the bootstrap sample $X^*_1,...,X^*_n$ and let
-$\hat\theta^*_n$ be the parameter estimate based on the bootstrap samples. 
+Let us first consider the case where $X_i$'s are i.i.d. Denote by $F^{(b)}_n$ the
+empirical distribution of the $b$th bootstrap sample and let
+$\hat\theta^{(b)}_n$ be the parameter estimate based on the bootstrap samples. 
 Using the bootstrap (asymptotic) theory, we can approximate the distribution of
 \jy{no need for so many in-display equations}
-\[
-\sqrt{n}(F_n(x) - F(x))
-\]
+$\sqrt{n}(F_n(x) - F(x))$
+by that of $\sqrt{n}(F^{(b)}_n(x) - F_n(x))$
+and the distribution of
+$\sqrt{n}(F(x; \hat\theta_n) - F(x))$
 by that of
-\[
-\sqrt{n}(F^*_n(x) - F_n(x))
-\]
-and the distribution of
-\[
-\sqrt{n}(F(x; \hat\theta_n) - F(x))
-\]
-by that of
-\[
-\sqrt{n}(F(x; \hat\theta^*_n) - F(x; \hat\theta_n)).
-\]
+$\sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; \hat\theta_n))$.
 Therefore, if we define
 \begin{equation*}
-Y^*_n(x) = \sqrt{n}(F^*_n(x) - F_n(x)) - 
-\sqrt{n}(F(x; \hat\theta^*_n) - F(x; \hat\theta_n)) 
-= \sqrt{n}(F^*_n(x) - F(x; \hat\theta^*_n)) - 
+Y^{(b)}_n(x) = \sqrt{n}(F^{(b)}_n(x) - F_n(x)) - 
+\sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; \hat\theta_n)) 
+= \sqrt{n}(F^{(b)}_n(x) - F(x; \hat\theta^{(b)}_n)) - 
 \sqrt{n}(F_n(x) - F(x; \hat\theta_n)),
 \end{equation*}
-then $KS^*_n := \sup_x|Y^*_n(x)|$ is the bootstrap statistic that is expected
-to approximate the distribution of $KS_n$. We note that the term
+then $T^{(b)}_n := \sup_x|Y^{(b)}_n(x)|$ is the bootstrap statistic that is expected
+to approximate the distribution of $T_n$. We note that the term
 $\sqrt{n}(F_n(x) - F(x; \hat\theta_n))$ is exactly the bias term considered in 
@@
 We now consider the case where $X_i$'s are realizations from a time series and
-$X^*_1,...,X^*_n$ are generated by block bootstrap. In this case, we can 
+$X^{(b)}_1,...,X^{(b)}_n$ are generated by block bootstrap for 
+$b \in \{1, \ldots, B\}$. Let $E^{b}$ refer to the expectation with respect to
+the bootstrap distribution
+In this case, we can 
 approximate the distribution of
-\jy{No need for in-display}
-\[
-\sqrt{n}(F_n(x) - F(x))
-\]
+$\sqrt{n}(F_n(x) - F(x))$
 by that of
-\[
-\sqrt{n}(F^*_n(x) - E^*[F^*_n(x)])
-\]
+$\sqrt{n}(F^{(b)}_n(x) - E^{(b)}[F^{(b)}_n(x)])$,
+where 
 \jy{change the languages to add variety}
-and the distribution of
-\[
-\sqrt{n}(F(x; \theta_n) - F(x))
-\]
-by that of
-\[
-\sqrt{n}(F(x; \hat\theta^*_n) - F(x; E^*[\hat\theta^*_n])).
-\]
+and the distribution of $\sqrt{n}(F(x; \theta_n) - F(x))$
+by that of $\sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; E^*[\hat\theta^{(b)}_n]))$.
 \jy{no closing a sentence before all the notations are introduced}
-Here $E^*$ denotes the expectation with respect to the bootstrap distribution
-(i.e., the randomness due to the resampling using block botostrap) conditional
-on the observations $X_1,...,X_n$. We can compute $E^*[F^*_n(x)]$ and 
-$E^*[\hat\theta^*_n]$ numerically (they can also be computed analytically, 
-depending on the types of block bootstrap we use). For example, let 
-$X^*_{1,b},...,X^*_{n,b}$ be the $b$th block bootstrap sample for 
-$1 \leq b \leq B$. One can compute $F^*_{n,b}$ and $\hat\theta^*_{n,b}$ based on
-$X^*_{1,b},...,X^*_{n,b}$. Then
-\begin{align*}
-E^*[F^*_n(x)] &\approx \frac{1}{B}\sum_{b = 1}^BF^*_{n, b}(x),\\
-E^*[\hat\theta^*_n] &\approx \frac{1}{B}\sum_{b = 1}^B\hat\theta^*_{n,b}.
-\end{align*}
+We can compute $E^{(b)}[F^{(b)}_n(x)]$ and 
+$E^{(b)}[\hat\theta^{(b)}_n]$ numerically (they can also be computed analytically, 
+depending on the types of block bootstrap we use). One can compute 
+$F^{(b)}_n$ 
+and $\hat\theta^{(b)}_n$ based on
+the $b$th bootstrap sample. Then
+$E^{(b)}[F^{(b)}_n(x)] \approx \frac{1}{B}\sum_{b = 1}^BF^{(b)}_n(x)$, and
+$E^{(b)}[\hat\theta^{(b)}_n] \approx \frac{1}{B}\sum_{b = 1}^B\hat\theta^{(b)}_n$.
 In this case, we can define
 \jy{too long}
-\begin{equation*}
-Y^*_n(x) = \sqrt{n}(F^*_n(x) - E^*[F^*_n(x)]) - 
-\sqrt{n}(F(x; \hat\theta^*_n) - F(x; E^*[\hat\theta^*_n)]) 
-= \sqrt{n}(F^*_n(x) - F(x; \hat\theta^*_n)) - 
-\sqrt{n}(E^*[F^*_n(x)] - F(x; E^*[\hat\theta^*_n])),
-\end{equation*}
-and $KS^*_n = \sup_x|Y^*_n(x)|$.
+
+$Y^*_n(x) = \sqrt{n}(F^{(b)}_n(x) - E^{(b)}[F^{(b)}_n(x)]) - 
+\sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; E^{(b)}[\hat\theta^{(b)}_n)]) \\
+= \sqrt{n}(F^{(b)}_n(x) - F(x; \hat\theta^{(b)}_n)) - 
+\sqrt{n}(E^{(b)}[F^{(b)}_n(x)] - F(x; E^{(b)}[\hat\theta^{(b)}_n]))$,
+
+and $T^{(b)}_n = \sup_x|Y^{(b)}_n(x)|$.
+
+The p-value of the block bootstrap KS test can be computed 
+as $p = \#\{T^{(b)}_n < T_n\} / B$ for 
+$b \in \{1, \ldots, B\}$.
 
@@
 \jy{First size and then power}
+
+\paragraph{Size}
+We first must evaluate whether this method works when $H_0$ is true. To
+test this, we can
+generate a simulated sample $X_t$ from a certain distribution $F(\theta)$,
+and use the block bootstrap KS test to test if $X_t$ is generated from 
+distribution $F$ with some unknown $\theta$. If the test holds its size, the 
+p-value
+of the test should be uniformally distributed between 0 and 1. We must try the
+method with different marginal distributions to ensure that it is robust.
+The results of the method depend on the sample size, so we must find the minimum
+sample size required for the block bootstrap KS test to work.
+We can implement the procedure described in methods with the true distribution
+$F ~ N$, hypothesize distribution $F_0 ~ N$, and true $\mu = 8$ and 
+$\sigma = 8$.
+We replicate this procedure 1000 times to get the distribution of the p-values 
+for the test when applied to samples from the same data generating process.
+Then, we repeat the same procedure with $F ~ \Gamma$.
+
+\paragraph{Power}
+We must also evaluate if this method works when $H_0$ is false. We can use
+the block bootstrap KS test to test if $X_t$ is generated from some other 
+distribution $G$ with some unknown $\theta$. In this scenario, if the test is 
+indeed powerful,
+we would ideally want $\Beta$, or the probability of rejection to be 1, but we
+expect it to be generally high. Again, we must try the method with different
+marginal distributions to ensure that it is robust.
 

### 2023-10-18 code/functions.R

@@ -65,5 +65,5 @@ plot_p_vals <- function(n, blksize, B, dist, f0, f, theta, phi, rho, nrep = 1000
   ggsave(filename = paste("sim_", n, "_", dist, "_",
                           phi, '_', 
                           rho, ".pdf", sep = ''), plot = gg.f, 
-         path = "../figures/manuscript", height = 4, width = 4)
+         path = "../manuscript/figures", height = 4, width = 4)
 }

### 2023-10-18 code/simulation.R

@@ -1,8 +1,10 @@
 source('functions.R')
 
+# Independent Data Basic Bootstrap
 set.seed(0123)
 plot_p_vals(200, 1, 1000, 'normal', pnorm, qnorm, c(8,8), 0, 0)
 
+# Dependent Data Basic Bootstrap n = 200 Normal(8,8)
 set.seed(1234)
 plot_p_vals(200, ceiling(200^(1/3)), 1000, 'normal', pnorm, qnorm, 
             c(8,8), -0.4, 0)
@@ -13,12 +15,17 @@ plot_p_vals(200, ceiling(200^(1/3)), 1000, 'normal', pnorm, qnorm,
 
 set.seed(3456)
 plot_p_vals(200, ceiling(200^(1/3)), 1000, 'normal', pnorm, qnorm, 
-            c(8,8), 0.2, 0)
+            c(8,8), 0, 0)
 
 set.seed(4567)
 plot_p_vals(200, ceiling(200^(1/3)), 1000, 'normal', pnorm, qnorm, 
+            c(8,8), 0.2, 0)
+
+set.seed(5678)
+plot_p_vals(200, ceiling(200^(1/3)), 1000, 'normal', pnorm, qnorm, 
             c(8,8), 0.4, 0)
 
+# Dependent Data Basic Bootstrap n = 200 Gamma(8,1)
 set.seed(1234)
 plot_p_vals(200, ceiling(200^(1/3)), 1000, 'gamma', pgamma, qgamma, 
             c(8,1), -0.4, 0)
@@ -29,8 +36,54 @@ plot_p_vals(200, ceiling(200^(1/3)), 1000, 'gamma', pgamma, qgamma,
 
 set.seed(3456)
 plot_p_vals(200, ceiling(200^(1/3)), 1000, 'gamma', pgamma, qgamma, 
-            c(8,1), 0.2, 0)
+            c(8,1), 0, 0)
 
 set.seed(4567)
 plot_p_vals(200, ceiling(200^(1/3)), 1000, 'gamma', pgamma, qgamma, 
+            c(8,1), 0.2, 0)
+
+set.seed(5678)
+plot_p_vals(200, ceiling(200^(1/3)), 1000, 'gamma', pgamma, qgamma, 
+            c(8,1), 0.4, 0)
+
+# Dependent Data Basic Bootstrap n = 400 Normal(8,8)
+set.seed(1234)
[…]

### 2023-10-18 manuscript/manuscript.tex
10/18 Notes

@@
 $X^{(b)}_1,...,X^{(b)}_n$ are generated by block bootstrap for 
-$b \in \{1, \ldots, B\}$. Let $E^{b}$ refer to the expectation with respect to
+$b \in \{1, \ldots, B\}$. Let $E^{(b)}$ refer to the expectation with respect to
 the bootstrap distribution

### 2023-10-25 manuscript/manuscript.tex
Zoomed In Plots

@@
 
+\subsection{Precipitation in Mansfield Connecticut}
+Precipitation annual maximum in inches series data was retrieved from the 
+National Oceanic and Atmospheric Administration.
+\mc{https://hdsc.nws.noaa.gov/pfds/pfds_map_cont.html?bkmrk=ct}
+
+\subsection{Microsoft Stock Returns}
+
+\mc{https://www.nasdaq.com/market-activity/stocks/msft/historical}
+
 \section{Concluding Remarks}

### 2023-10-25 code/functions.R

@@ -53,6 +53,9 @@ plot_p_vals <- function(n, blksize, B, dist, f0, f, theta, phi, rho, nrep = 1000
                           ncol = 1))
   p <- replicate(nrep, mysim(n, blksize, B, dist, f0, f, theta, phi, rho))
   df$p <- p
+  saveRDS(df, paste("../data/sim_", n, "_", dist, "_",
+                    phi, '_', 
+                    rho, ".RDS", sep = ''))
   ## Section 2: Fitted parameters
   gg.f <- ggplot(data = df, mapping = aes(sample = p)) +
     scale_x_continuous(breaks=c(0, 1)) +
@@ -63,6 +66,21 @@ plot_p_vals <- function(n, blksize, B, dist, f0, f, theta, phi, rho, nrep = 1000
     labs(x = "Probability Points", y = "Cumulative Probability") +
     coord_fixed() # theme(aspect.ratio=1)
   ggsave(filename = paste("sim_", n, "_", dist, "_",
+                          phi, '_', 
+                          rho, ".pdf", sep = ''), plot = gg.f, 
+         path = "../manuscript/figures", height = 4, width = 4)
+}
+
+zoomed_in <- function(df, n, dist, phi, rho) {
+  gg.f <- ggplot(data = df, mapping = aes(sample = p)) +
+    scale_x_continuous(breaks=c(0, 0.1)) +
+    scale_y_continuous(breaks=c(0, 0.1)) + 
+    stat_pp_band(distribution = "unif") +
+    stat_pp_line() +
+    stat_pp_point(distribution = "unif", cex = .1) +
+    labs(x = "Probability Points", y = "Cumulative Probability") +
+    coord_cartesian(ylim = c(0, 0.1), xlim = c(0, 0.1))
+  ggsave(filename = paste("zoom_", n, "_", dist, "_",
                           phi, '_', 
                           rho, ".pdf", sep = ''), plot = gg.f, 
          path = "../manuscript/figures", height = 4, width = 4)

### 2023-10-25 code/simulation.R

@@ -87,3 +87,45 @@ plot_p_vals(400, ceiling(400^(1/3)), 1000, 'gamma', pgamma, qgamma,
 set.seed(5678)
 plot_p_vals(400, ceiling(400^(1/3)), 1000, 'gamma', pgamma, qgamma, 
             c(8,1), 0.4, 0)
+
+# Dependent Data Basic Bootstrap n = 400 Normal(8,8)
+set.seed(1234)
+plot_p_vals(800, ceiling(800^(1/3)), 1000, 'normal', pnorm, qnorm, 
+            c(8,8), -0.4, 0)
+
+set.seed(2345)
+plot_p_vals(800, ceiling(800^(1/3)), 1000, 'normal', pnorm, qnorm, 
+            c(8,8), -0.2, 0)
+
+set.seed(3456)
+plot_p_vals(800, ceiling(800^(1/3)), 1000, 'normal', pnorm, qnorm, 
+            c(8,8), 0, 0)
+
+set.seed(4567)
+plot_p_vals(800, ceiling(800^(1/3)), 1000, 'normal', pnorm, qnorm, 
+            c(8,8), 0.2, 0)
+
+set.seed(5678)
+plot_p_vals(800, ceiling(800^(1/3)), 1000, 'normal', pnorm, qnorm, 
+            c(8,8), 0.4, 0)
+
+# Dependent Data Basic Bootstrap n = 400 Gamma(8,1)
+set.seed(1234)
+plot_p_vals(800, ceiling(800^(1/3)), 1000, 'gamma', pgamma, qgamma, 
+            c(8,1), -0.4, 0)
+
+set.seed(2345)
+plot_p_vals(800, ceiling(800^(1/3)), 1000, 'gamma', pgamma, qgamma, 
+            c(8,1), -0.2, 0)
+
+set.seed(3456)
+plot_p_vals(800, ceiling(800^(1/3)), 1000, 'gamma', pgamma, qgamma, 
+            c(8,1), 0, 0)
+
+set.seed(4567)
+plot_p_vals(800, ceiling(800^(1/3)), 1000, 'gamma', pgamma, qgamma, 
+            c(8,1), 0.2, 0)
+
+set.seed(5678)
+plot_p_vals(800, ceiling(800^(1/3)), 1000, 'gamma', pgamma, qgamma, 
+            c(8,1), 0.4, 0)

### 2023-11-07 manuscript/manuscript.tex
10/25 Notes
Figures

@@
 
+We constructed Q-Q plots of the distribution of the p-values to see if they are
+normally distributed. A zoomed in plot for probabilities between 0 and 0.1, as
+that is the most common range for significance levels $\alpha$.
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=\textwidth]{figures/sim_800_normal_-0.4_0}
+  \caption{Q-Q p}
+  \label{fig:mu}
+\end{figure}
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=\textwidth]{figures/zoom_800_normal_-0.4_0}
+  \caption{}
+  \label{fig:mu}
+\end{figure}
+
 \paragraph{Power}
@@
 
+We expect the distribution of Microsoft stock returns to have a slightly
+heavier tail than the normal distribution. We can test that it is normally
+distributed (which we expect to reject). Then we can try testing if it follows
+the $t$ distribution with different degrees of freedoms.
+
 \section{Concluding Remarks}

### 2023-11-07 code/data_processing.R

@@ -1,3 +1,22 @@
-precipitation <- read.csv("../data/precipitation.txt", header = TRUE, sep = ' ')
+setwd("../data")
 
-microsoft <- read.csv('../data/microsoft.csv')
+#precipitation <- read.csv("precipitation.txt", header = TRUE, sep = ' ')
+
+microsoft <- read.csv('microsoft.csv')
+
+file_names <- list.files(pattern = "^sim")
+for (phi in c(-.4, -.2, 0, .2, .4)) {
+  for (n in c(100, 200, 400, 800, 1600, 3200)) {
+    for (dist in c("normal", "gamma")) {
+      list <- file_names[which(grepl(paste("_", n, "_", dist, "_", phi, "_0_", sep = ''), 
+                                     file_names))]
+      tosave <- c()
+      for (file in list) {
+        tosave <- c(tosave, readRDS(file)$p)
+      }
+      saveRDS(tosave, file = paste("sim_", n, "_", dist, "_",
+                                   phi, '_', 
+                                   '0', ".RDS", sep = ''))
+    }
+  }
+}

### 2023-11-07 code/jobs.R

@@ -1,18 +1,0 @@
-source("functions.R")
-i <- Sys.getenv("SLURM_ARRAY_TASK_ID")
-for (phi in c(-.4, -.2, 0, .2, .4)) {
-  for (n in c(100, 200, 400, 800, 1600, 3200)) {
-    nrep = 100
-    n = n
-    blksize = 10
-    B = 100
-    dist = 'normal'
-    f = pnorm
-    phi <- -0.4
-    theta <- 0
-    sim_ar1_n.4 <- replicate(nrep, mysim(n, blksize, B, dist, f, phi, theta))
-    hist(sim_ar1_n.4)
-  }
-}
-saveRDS(norm_results, paste('../Data/norm_results', '_', i, '.rds', sep = ''))
-saveRDS(exp_results, paste('../Data/exp_results', '_', i, '.rds', sep = ''))

### 2023-11-08 manuscript/manuscript.tex
Wrote a little Under Size and Power

@@
 We constructed Q-Q plots of the distribution of the p-values to see if they are
-normally distributed. A zoomed in plot for probabilities between 0 and 0.1, as
-that is the most common range for significance levels $\alpha$.
+uniformly distributed. If the distribution of the p-values is uniform, this 
+indicates that the time series follows the null distribution. 
+A zoomed in plot for probabilities between 0 and 0.1 is
+also provided, as
+that is the most common range for significance levels $\alpha$. We can also
+compute the rate of rejection $\#P < \alpha$ for different values of
+$\alpha$, as well as a confidence interval
+for this proportion.
 
@@
 indeed powerful,
-we would ideally want $\Beta$, or the probability of rejection to be 1, but we
+we would ideally want $\beta$, or the probability of rejection to be 1, but we
 expect it to be generally high. Again, we must try the method with different
 marginal distributions to ensure that it is robust.
+We would then expect the distribution of p-values to be non-normal, and the rate
+of $\#P < \alpha$ to be high, meaning a higher density of low p-values.
+
+If we can show that the test correctly fails to reject $H_0$ under the null
+distribution, and correctly rejects $H_0$ for an alternate distribution, we can
+state tht the method works.
 
@@
 National Oceanic and Atmospheric Administration.
-\mc{https://hdsc.nws.noaa.gov/pfds/pfds_map_cont.html?bkmrk=ct}
+%\mc{https://hdsc.nws.noaa.gov/pfds/pfds_map_cont.html?bkmrk=ct}
 
@@
 
-\mc{https://www.nasdaq.com/market-activity/stocks/msft/historical}
+%\mc{https://www.nasdaq.com/market-activity/stocks/msft/historical}
 

### 2023-11-30 manuscript/manuscript.tex
11/29 Notes

@@
 The Kolmogorov-Smirnov (KS) statistic is widely used to test if a sample is
-from a given distribution.
+from a given distribution. This study demonstrates how block bootstrap can be 
+used to approximate the KS statistic in situations where parameters are 
+not specified and the data are serially dependent. We demonstrate the 
+theoretical justication for this method, then through simulation we verify that
+it holds it size under the null distribution and is powerful when the null 
+hypothesis is false. Finally, we demonstrate applications of the method to
+precipitation data from JFK airport and Microsoft stock returns.
 
@@
 We can implement the procedure described in methods with the true distribution
-$F ~ N$, hypothesize distribution $F_0 ~ N$, and true $\mu = 8$ and 
-$\sigma = 8$.
+$F ~ N$, hypothesize distribution $F_0 ~ N$, and true mean $\mu = 8$ and 
+standard deviation $\sigma = \sqrt{8}$.
 We replicate this procedure 1000 times to get the distribution of the p-values 
 for the test when applied to samples from the same data generating process.
-Then, we repeat the same procedure with $F ~ \Gamma$.
+Then, we repeat the same procedure with $F ~ \Gamma$, and true shape $k = 8$ and
+scale $\theta = 1$.
 
@@
 also provided, as
-that is the most common range for significance levels $\alpha$. We can also
-compute the rate of rejection $\#P < \alpha$ for different values of
-$\alpha$, as well as a confidence interval
-for this proportion.
+that is the most common range for significance levels $\alpha$. 
+%We can also
+%compute the rate of rejection $\#P < \alpha$ for different values of
+%$\alpha$, as well as a confidence interval
+%for this proportion.
 
@@
   \centering
-  \includegraphics[width=\textwidth]{figures/sim_800_normal_-0.4_0}
-  \caption{Q-Q p}
+  \includegraphics[scale=1]{figures/normal}
+  \caption{A Q-Q plot of the p-values testing that a distribution
+  generated from a $N(8,8)$ data generating process is normal.}
   \label{fig:mu}
@@
   \centering
-  \includegraphics[width=\textwidth]{figures/zoom_800_normal_-0.4_0}
-  \caption{}
+  \includegraphics[scale=1]{figures/zoom_normal}
+  \caption{A version of the above plot zoomed in to probabilities between 0 and
+  0.1}
+  \label{fig:mu}
+\end{figure}
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[scale=1]{figures/gamma}
+  \caption{A Q-Q plot of the p-values testing that a distribution
+  generated from a $\gamma(8,1)$ data generating process is gamma distributed.}
+  \label{fig:mu}
+\end{figure}
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[scale=1]{figures/zoom_gamma}
+  \caption{A version of the above plot zoomed in to probabilities between 0 and
+  0.1}
   \label{fig:mu}
@@
 marginal distributions to ensure that it is robust.
-We would then expect the distribution of p-values to be non-normal, and the rate
+We would then expect the distribution of p-values to be non-uniform, and the rate
 of $\#P < \alpha$ to be high, meaning a higher density of low p-values.
@@
 distribution, and correctly rejects $H_0$ for an alternate distribution, we can
-state tht the method works.
+state that the method works.
+
+We can find the rate of rejection for  different values for the significance 
+level $\alpha$. Additionally, we can construct a 95\% confidence interval for 
+this rate. Below are rejection rates for $\phi = 0.2$ and $n = 800$, when
+applied to the normal and gamma distributions using $\alpha =$ 0.01, 0.05, and 
+0.10.
+
+\input{tables/rr}
+
+As shown in the above table, the rejection rates for these settings are very 
+high (almost 1), indicating that the test is very powerful for these settings.
 
@@
 \subsection{Precipitation in Mansfield Connecticut}
-Precipitation annual maximum in inches series data was retrieved from the 
+Monthly maximums of daily precipiation in inches time series data was retrieved 
+from the John F. Kennedy (JFK) International Airport station from the 
 National Oceanic and Atmospheric Administration.
@@
 
+We have shown that given a large enough sample of a time series, the block 
+bootstrap KS test can appropriately fail to reject the null hypothesis when the
+series follows the null distribution. It requires a larger sample size than 
+basic bootstrap.
+
 \bibliographystyle{chicago}

### 2023-11-30 code/alt_jobs.R

@@ -1,0 +1,35 @@
+source("functions.R")
+i <- Sys.getenv("SLURM_ARRAY_TASK_ID")
+B <- 1000
+nrep <- 100
+for (phi in c(-.4, -.2, 0, .2, .4)) {
+  for (n in c(100, 200, 400, 800, 1600, 3200)) {
+    for (true_dist in c("normal", "gamma")) {
+      set.seed(as.integer(i))
+      if (true_dist == "normal") {
+        h0_dist <- "gamma"
+        f0 <- pgamma
+        f <- qnorm
+        theta <- c(8, sqrt(8))
+      }
+      if (true_dist == "gamma") {
+        h0_dist <- "normal"
+        f0 <- pnorm
+        f <- qgamma
+        theta <- c(8,1)
+      }
+      df <- data.frame(matrix(NA,    
+                              nrow = nrep,
+                              ncol = 1))
+      blksize <- ceiling(n^(1/3))
+      p <- replicate(nrep, mysim(n, blksize, B, h0_dist, true_dist, f0, f, 
+                                 theta, phi, 0))
+      df$p <- p
+      saveRDS(df, paste("../data/alt_", n, "_", true_dist, "_",
+                        phi, "_", 
+                        "0", "_",  i, ".RDS", sep = ""))
+    }
+  }
+}
+
+

### 2023-11-30 code/microsoft.R

@@ -1,0 +1,7 @@
+source("functions.R")
+library(tseries)
+microsoft <- get.hist.quote(instrument = "msft", start = "1998-01-01")
+#log difference
+set.seed(123)
+mc_norm_pval <- myapp(as.vector(microsoft[, "Close"]), 1000, "normal", pnorm)
+saveRDS(mc_norm_pval, "../data/mc_norm_pval.RDS")

### 2023-11-30 code/plots.R

@@ -1,10 +1,14 @@
 setwd("../code")
 source("functions.R")
 
-for (phi in c(-.4, -.2, 0, .2, .4)) {
-  for (n in c(100, 200, 400, 800, 1600, 3200)) {
-    for (dist in c("normal", "gamma")) {
-      plot_p_vals(paste("sim_", n, "_", dist, "_", phi, "_0", sep = ""))
-    }
-  }
-}
+df <- readRDS("../data/pvals.RDS") %>% 
+  filter(phi == -0.2 | phi == 0 | phi == 0.2, n == 400) %>% 
+  mutate(pval = as.numeric(pval))
+
+normal <- df %>% filter(dist == 'normal')
+plot_p_vals(normal, 'normal.pdf')
+
+gamma <- df %>% filter(dist == 'gamma')
+plot_p_vals(gamma, 'gamma.pdf')
+
+

### 2023-11-30 code/precipitation.R

@@ -1,0 +1,28 @@
+source('functions.R')
+library(tidyverse)
+library(janitor)
+library(evd)
+precipitation <- read.csv("../data/precipitation.csv") %>% 
+  clean_names() %>% 
+  filter(station_name == "JFK INTERNATIONAL AIRPORT NY US", hpcp != 999.99) %>% 
+  mutate(date = strptime(date, format = "%Y%m%d %H:%M"))
+
+annual_max_hpcp <- precipitation %>% 
+  group_by(year = as.numeric(format(date, "%Y"))) %>% 
+  summarize(annual_max_hpcp = max(hpcp)) %>% 
+  ungroup()
+
+monthly_max_dpcp <- precipitation %>%
+  group_by(year = as.numeric(format(date, "%Y")),
+           month = as.numeric(format(date, "%m")),
+           day = as.numeric(format(date, "%d"))) %>% 
+  summarize(dpcp = sum(hpcp)) %>% 
+  ungroup(day) %>% 
+  summarize(monthly_max_dpcp = max(dpcp)) %>% 
+  ungroup()
+
+set.seed(123)
+nyc_pvals <- myapp(annual_max_hpcp$annual_max_hpcp, 10000, 'gev', pgev)
+
+saveRDS(nyc_pvals, "../data/nyc_pvals.RDS")
+

### 2023-12-05 manuscript/manuscript.tex
meta cleaning in preamble
comments and minor edits

@@
 % NOTE: To produce blinded version, replace "0" with "1" below.
-\newcommand{\blind}{0}
+\newcommand{\blind}{0]}
 
@@
 
+\title{\bf Nonparametric Bootstrap Kolmogorov-Smirnov Test for
+  Goodness-of-Fit of Marginal Distributions of Stationary Time Series}
 \if0\blind
 {
-  \title{\bf Nonparametric Bootstrap Kolmogorov-Smirnov Test with Stationary 
-  Time Series}
   \author{Mathew Chandy, %\\
@@
 %   {\nolinkurl{mathew.chandy@uconn.edu}}\\
+  Elizabeth Schifano\\
   Jun Yan, %\\
@@
 }
-\date{}
-  \maketitle
 } \fi
 
-\if1\blind
-{
-  \bigskip
-  \bigskip
-  \bigskip
-  \begin{center}
-    {\LARGE\bf Nonparametric Bootstrap Kolmogorv-Smirnov Test with Stationary 
-    Time Series}
-\end{center}
-  \bigskip
-} \fi
-
-\doublespace
+\maketitle
 
@@
 
-%\doublespace
+\doublespace
 
@@
 \label{sec:intro}
+
+\jy{Flow:
+  Review misuses of one-sample KS test; focus on serial dependence;
+  criticize Zeimbakakis; highlight contributions (connection to Babu and Rao).}
+
+\jy{Borrow the introduction of Zeimbakakis and, of course, rephase them.}
 
@@
 
+\jy{Clarify the GoF test is for the marginal distribution of a statoinary
+  series.}
 Consider a stationary time series $\{X_t: t = 1, \ldots, n\}$ with length~$n$.
@@
 
-\jy{define $\hat\theta_n$}
-\mc{addressed}
-
 \jy{No double letter notations}
@@
 Consider the goodness of fit statistic:
+\jy{define $Y_n$ before introducing $T_n$}
 \begin{equation*}
@@
 
+\jy{respond to my comments}
+
 Let us first consider the case where $X_i$'s are i.i.d. Denote by $F^{(b)}_n$ the
@@
 Using the bootstrap (asymptotic) theory, we can approximate the distribution of
-\jy{no need for so many in-display equations}
+\jy{Need rephrasing. The two terms are approximated altogether jointly not
+  separately.}
 $\sqrt{n}(F_n(x) - F(x))$
@@
 $\sqrt{n}(F_n(x) - F(x; \hat\theta_n))$ is exactly the bias term considered in 
-Babu and Rao (2004).
+Babu and Rao (2004).\jy{cite}
 
@@
 $b \in \{1, \ldots, B\}$. Let $E^{(b)}$ refer to the expectation with respect to
-the bootstrap distribution
-In this case, we can 
+the bootstrap distribution. In this case, we can 
 approximate the distribution of
@@
 $\sqrt{n}(F^{(b)}_n(x) - E^{(b)}[F^{(b)}_n(x)])$,
-where 
 \jy{change the languages to add variety}
@@
 by that of $\sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; E^*[\hat\theta^{(b)}_n]))$.
-\jy{no closing a sentence before all the notations are introduced}
+
 We can compute $E^{(b)}[F^{(b)}_n(x)]$ and 
@@
 In this case, we can define
-\jy{too long}
-
-$Y^*_n(x) = \sqrt{n}(F^{(b)}_n(x) - E^{(b)}[F^{(b)}_n(x)]) - 
+\begin{align*}
+  Y^*_n(x) &= \sqrt{n}(F^{(b)}_n(x) - E^{(b)}[F^{(b)}_n(x)]) - 
              \sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; E^{(b)}[\hat\theta^{(b)}_n)]) \\
-= \sqrt{n}(F^{(b)}_n(x) - F(x; \hat\theta^{(b)}_n)) - 
-\sqrt{n}(E^{(b)}[F^{(b)}_n(x)] - F(x; E^{(b)}[\hat\theta^{(b)}_n]))$,
-
+           &= \sqrt{n}(F^{(b)}_n(x) - F(x; \hat\theta^{(b)}_n)) -
+             \sqrt{n}(E^{(b)}[F^{(b)}_n(x)] - F(x; E^{(b)}[\hat\theta^{(b)}_n])),
+\end{align*}
 and $T^{(b)}_n = \sup_x|Y^{(b)}_n(x)|$.
 
+\jy{Summary the procedure in an algorithm.}
+
 The p-value of the block bootstrap KS test can be computed
+\jy{not right}
 as $p = \#\{T^{(b)}_n < T_n\} / B$ for 
@@
 \label{sec:simu}
-
-\jy{First size and then power}
 

### 2023-12-06 manuscript/manuscript.tex
Changed Figures and Added Tables

--- 2023-11-30 manuscript/manuscript.tex
@@
   generated from a $N(8,8)$ data generating process is normal.}
-  \label{fig:mu}
+  \label{fig:normal}
 \end{figure}
@@
   \includegraphics[scale=1]{figures/zoom_normal}
-  \caption{A version of the above plot zoomed in to probabilities between 0 and
+  \caption{A Q-Q plot of the p-values displayed in \ref{fig:normal} zoomed in to 
+  probabilities between 0 and
   0.1}
-  \label{fig:mu}
+  \label{fig:zoom_normal}
 \end{figure}
@@
   generated from a $\gamma(8,1)$ data generating process is gamma distributed.}
-  \label{fig:mu}
+  \label{fig:gamma}
 \end{figure}
@@
   \includegraphics[scale=1]{figures/zoom_gamma}
-  \caption{A version of the above plot zoomed in to probabilities between 0 and
+  \caption{A Q-Q plot of the p-values displayed in \ref{fig:gamma} zoomed in to 
+  probabilities between 0 and
   0.1}
-  \label{fig:mu}
+  \label{fig:zoom_gamma}
 \end{figure}
@@
 
-\input{tables/rr}
+\input{tables/rr_100}
+
+From \ref{table:rr_100}, we can see that when $n = 100$, the rejection rate may 
+be quite low, especially for lower values of $\alpha$. From \ref{table:rr_200}, 
+the rejection rates are a little higher for $n = 200$, but they may still be 
+drop below 50\% is the $\alpha = 0.1$. Once $n$ reaches 400, we can observe 
+from \ref{table:rr_400} that the rejection rate
+is consistently above 50\%. For larger sample sizes, the rejection rate is 
+consistently above 90\%. We can also
+observe that the rejection rate is higher for the $\gamma(8, 1)$ sample than for 
+the $N(8, 8)$ As the strength of the temporal dependence increases, the 
+rejection rate decreases, and the rejection
+rate appears to be slightly higher for negative temporal dependence versus 
+positive temporal dependence values of the same strength.
+
+\input{tables/rr_200}
+
+\input{tables/rr_400}
+
+\input{tables/rr_800}
+
+\input{tables/rr_1600}
+
+\input{tables/rr_3200}
 
@@
 \subsection{Precipitation in Mansfield Connecticut}
-Monthly maximums of daily precipiation in inches time series data was retrieved 
-from the John F. Kennedy (JFK) International Airport station from the 
-National Oceanic and Atmospheric Administration.
+Annual maximums of hourly precipitation in inches time series data were 
+retrieved 
+from the Chicago Midway International Airport, New York LaGuardia International 
+Airport,
+and Los Angeles International Airport stations from the 
+National Oceanic and Atmospheric Administration. These stations were selected 
+from places of importance in the three largest American cities. LaGuardia and
+Midway were chosen over John F. Kennedy and O'Hare as more data was available
+from these stations. The data is from
+May 1st of 1948 to January 1st of 2014. To confirm that our method works, we 
+used it to test that
+the precipitation time series from each of these locations followed the 
+Generalized Extreme Value (GEV) distribution.
+
+\input{tables/precipitation_pvals}
 %\mc{https://hdsc.nws.noaa.gov/pfds/pfds_map_cont.html?bkmrk=ct}
+
+Using a significance level as high as .10 still results in a failed rejection
+of the null hypothesis that all three time series follow the GEV distribution.
 
@@
 heavier tail than the normal distribution. We can test that it is normally
-distributed (which we expect to reject). Then we can try testing if it follows
-the $t$ distribution with different degrees of freedoms.
+distributed (which we expect to reject).  While we 
+could choose to estimate a fited value of the degrees of freedom parameter as
+part of our method, it is very difficult to do so. Therefore, we can try testing 
+if it follows
+the $t$ distribution with increasingly smaller degrees of freedoms.
+
+\input{tables/mc_pvals}
+
+F
 
@@
 
-We have shown that given a large enough sample of a time series, the block 
+Using simulation, we have shown that given a large enough sample of a time 
+series, the block 
 bootstrap KS test can appropriately fail to reject the null hypothesis when the
-series follows the null distribution. It requires a larger sample size than 
-basic bootstrap.
+series follows the null distribution. In addition, when the marginal
+distribution is not
+the one hypothesized, the test is powerful. It requires a larger sample size 
+than basic bootstrap to avoid either type I or type II errors. Unsurprisingly,
+the method performs better as the temporal dependence gets weaker. We have also 
+demonstrated possible applications of this method to precipitation and 
+stock return data. This method can be used for any study where the goal is
+to see if a time series follows a hypothesized distribution and the parameters
+are unknown or unspecified.
 

### 2023-12-06 code/jobs.sh

@@ -1,7 +1,7 @@
 #!/bin/bash
 #SBATCH --partition=general
 #SBATCH --output=../out/ja_%A_%a.out
-#SBATCH --array=1-10%10
+#SBATCH --array=1-100%100
 #SBATCH --ntasks=1 ## OBS 1
 #SBATCH --cpus-per-task=1 ## OBS 2
 #SBATCH --mem-per-cpu=500M ## OBS 3
@@ -13,4 +13,5 @@ module load r/4.2.2
 ## avoiding implicit paralellism
 export OMP_NUM_THREADS=1
 
+Rscript null_jobs.R
 Rscript alt_jobs.R

### 2023-12-06 code/microsoft.R

@@ -1,7 +1,158 @@
 source("functions.R")
 library(tseries)
-microsoft <- get.hist.quote(instrument = "msft", start = "1998-01-01")
+microsoft <- 
+  diff(log(get.hist.quote(instrument = "msft", start = "1998-01-01")))
 #log difference
 set.seed(123)
 mc_norm_pval <- myapp(as.vector(microsoft[, "Close"]), 1000, "normal", pnorm)
-saveRDS(mc_norm_pval, "../data/mc_norm_pval.RDS")
+
+set.seed(123)
+mc_t30_pval <- myapp(as.vector(microsoft[, "Close"]), 1000, "t", plst, 
+                      df = 30)
+
+set.seed(123)
+mc_t20_pval <- myapp(as.vector(microsoft[, "Close"]), 1000, "t", plst, 
+                     df = 20)
+
+set.seed(123)
+mc_t10_pval <- myapp(as.vector(microsoft[, "Close"]), 1000, "t", plst, 
+                     df = 10)
+
+set.seed(123)
+mc_t5_pval <- myapp(as.vector(microsoft[, "Close"]), 1000, "t", plst, 
+                     df = 5)
+
+set.seed(123)
+mc_t2_pval <- myapp(as.vector(microsoft[, "Close"]), 1000, "t", plst, 
+                    df = 2)
+
+set.seed(123)
+mc_t2.5_pval <- myapp(as.vector(microsoft[, "Close"]), 1000, "t", plst, 
+                    df = 2.5)
+
+set.seed(123)
+mc_t2.2_pval <- myapp(as.vector(microsoft[, "Close"]), 1000, "t", plst, 
+                      df = 2.2)
+
+set.seed(123)
+mc_t2.15_pval <- myapp(as.vector(microsoft[, "Close"]), 1000, "t", plst, 
+                      df = 2.15)
+
+# We fail to reject that the degrees of freedom is 2.15 at alpha = 0.1 using
+# the entire data (about 25 years)
+
+microsoft_5y <- 
+  diff(log(get.hist.quote(instrument = "msft", start = "2019-01-01")))
+
+set.seed(123)
+mc_norm_pval_5y <- myapp(as.vector(microsoft_5y[, "Close"]), 1000, "normal", 
+                         pnorm)
+
+set.seed(123)
+mc_t30_pval_5y <- myapp(as.vector(microsoft_5y[, "Close"]), 1000, "t", plst, 
+                     df = 30)
+
+set.seed(123)
[…]

### 2023-12-06 code/plots.R

@@ -2,7 +2,7 @@ setwd("../code")
 source("functions.R")
 
 df <- readRDS("../data/pvals.RDS") %>% 
-  filter(phi == -0.2 | phi == 0 | phi == 0.2, n == 400) %>% 
+#  filter(phi == -0.2 | phi == 0 | phi == 0.2, n == 400) %>% 
   mutate(pval = as.numeric(pval))
 
 normal <- df %>% filter(dist == 'normal')

### 2023-12-06 code/precipitation.R

@@ -4,25 +4,40 @@ library(janitor)
 library(evd)
 precipitation <- read.csv("../data/precipitation.csv") %>% 
   clean_names() %>% 
-  filter(station_name == "JFK INTERNATIONAL AIRPORT NY US", hpcp != 999.99) %>% 
   mutate(date = strptime(date, format = "%Y%m%d %H:%M"))
 
-annual_max_hpcp <- precipitation %>% 
+mdw <- precipitation %>% 
+  filter(station == "COOP:111577", hpcp != 999.99) %>%
   group_by(year = as.numeric(format(date, "%Y"))) %>% 
   summarize(annual_max_hpcp = max(hpcp)) %>% 
   ungroup()
 
-monthly_max_dpcp <- precipitation %>%
-  group_by(year = as.numeric(format(date, "%Y")),
-           month = as.numeric(format(date, "%m")),
-           day = as.numeric(format(date, "%d"))) %>% 
-  summarize(dpcp = sum(hpcp)) %>% 
-  ungroup(day) %>% 
-  summarize(monthly_max_dpcp = max(dpcp)) %>% 
+set.seed(123)
+mdw_pvals <- myapp(mdw$annual_max_hpcp, 10000, 'gev', evd::pgev, df = NULL)
+
+
+lga <- precipitation %>% 
+  filter(station == "COOP:305811", hpcp != 999.99) %>%
+  group_by(year = as.numeric(format(date, "%Y"))) %>% 
+  summarize(annual_max_hpcp = max(hpcp)) %>% 
   ungroup()
 
 set.seed(123)
-nyc_pvals <- myapp(annual_max_hpcp$annual_max_hpcp, 10000, 'gev', pgev)
+lga_pvals <- myapp(lga$annual_max_hpcp, 10000, 'gev', evd::pgev)
 
-saveRDS(nyc_pvals, "../data/nyc_pvals.RDS")
+
+lax <- precipitation %>% 
+  filter(station == "COOP:045114", hpcp != 999.99) %>%
+  group_by(year = as.numeric(format(date, "%Y"))) %>% 
+  summarize(annual_max_hpcp = max(hpcp)) %>% 
+  ungroup()
+
+set.seed(123)
+lax_pvals <- myapp(lax$annual_max_hpcp, 10000, 'gev', evd::pgev)
+
+write(print(xtable(data.frame(MDW = mdw_pvals, LGA = lga_pvals, LAX =
+                                lax_pvals),
+                   caption = "P-values for testing that annual maximum of hourly 
[…]

### 2023-12-06 code/tables.R

@@ -1,6 +1,75 @@
 library(xtable)
 df <- readRDS("../data/rejection_rates.RDS")
-df <- df %>% filter(phi == 0.2, n == 800) %>% select(-R) %>% 
+df_100 <- df %>% 
+  filter(n == 100) %>% 
+  select(-R) %>% 
   rename(distribution = dist, `lower bound` = rr_lb, `rejection rate` = rr, 
          `upper bound` = rr_ub)
-write(print(xtable(df)), file = "../manuscript/tables/rr.tex")      
+write(print(xtable(df_100, 
+                   caption = "Rejection rates for test when n = 100 for 
+                   different values of AR(1) coefficient and for different 
+                   significance levels. Lower and upper bounds are also 
+                   included.",
+                   label = "rr_100")), 
+      file = "../manuscript/tables/rr_100.tex")  
+
+df_200 <- df %>% 
+  filter(n == 200) %>% 
+  select(-R) %>% 
+  rename(distribution = dist, `lower bound` = rr_lb, `rejection rate` = rr, 
+         `upper bound` = rr_ub)
+write(print(xtable(df_200,
+                   caption = "Rejection rates for test when n = 200 for 
+                   different values of AR(1) coefficient and for different 
+                   significance levels. Lower and upper bounds are also 
+                   included.",
+                   label = "rr_200")), file = "../manuscript/tables/rr_200.tex")
+
+df_400 <- df %>% 
+  filter(n == 400) %>% 
+  select(-R) %>% 
+  rename(distribution = dist, `lower bound` = rr_lb, `rejection rate` = rr, 
+         `upper bound` = rr_ub)
+write(print(xtable(df_400,
+                   caption = "Rejection rates for test when n = 400 for 
+                   different values of AR(1) coefficient and for different 
+                   significance levels. Lower and upper bounds are also 
+                   included.",
+                   label = "rr_400")), file = "../manuscript/tables/rr_400.tex")
+
+df_800 <- df %>% 
+  filter(n == 800) %>% 
+  select(-R) %>% 
+  rename(distribution = dist, `lower bound` = rr_lb, `rejection rate` = rr, 
+         `upper bound` = rr_ub)
+write(print(xtable(df_800,
+                   caption = "Rejection rates for test when n = 800 for 
+                   different values of AR(1) coefficient and for different 
+                   significance levels. Lower and upper bounds are also 
+                   included.",
[…]

### 2023-12-13 manuscript/manuscript.tex
Added Algorithm for Method

--- 2023-12-05 manuscript/manuscript.tex
@@
 % NOTE: To produce blinded version, replace "0" with "1" below.
-\newcommand{\blind}{0]}
+\newcommand{\blind}{1]}
 
@@
   Xianyang Zhang\\
-}
 } \fi
@@
 The Kolmogorov-Smirnov (KS) statistic is widely used to test if a sample is
-from a given distribution. This study demonstrates how block bootstrap can be 
+from a given distribution. This study demonstrates how non-parametric 
+block bootstrap can be 
 used to approximate the KS statistic in situations where parameters are 
@@
 hypothesis is false. Finally, we demonstrate applications of the method to
-precipitation data from JFK airport and Microsoft stock returns.
+precipitation data from three airports and Microsoft stock returns.
 
@@
 \noindent{\sc Keywords}:
+bias-correction; 
+dependent data; 
+time series. 
 \end{abstract}
@@
 
-\jy{Flow:
-  Review misuses of one-sample KS test; focus on serial dependence;
-  criticize Zeimbakakis; highlight contributions (connection to Babu and Rao).}
+The Kolmogorov-Smirnov (KS) test is a useful goodness-of-fit statistic. 
+Let $X_1, ..., X_n$ be a random sample of size~$n$ from some continuous
+distribution. The null hypothesis $H_0$ is that $X_i$'s follow the
+hypothesized distribution~$F$.
+Let $F_n(t) = \sum_{i=1}^n I(X_i \le t) / n$ be the empirical cumulative
+distribution function of the sample, where $I(\cdot)$ is the indicator
+function. The KS test statistic takes the form
+\begin{equation}
+  \label{eq:ks_standard}
+  D_n = \sqrt{n} \sup_x | F_{n}(x) - F(x) |.
+\end{equation}
 
-\jy{Borrow the introduction of Zeimbakakis and, of course, rephase them.}
-
-The Kolmogorov-Smirnov (KS) test is a useful goodness-of-fit statistic. It 
+The statistic 
 can be used to see if a population follows a hypothesized distribution and has 
@@
 been used to analyze the random distribution of cosmic microwave background 
-radiation \citep{naess2012application}. A common misuse of the KS test is when
+radiation \citep{naess2012application}. \citet{zeimbekakis2022misuses} reviews
+some of the common misuses of the one-sample KS test. One of the most common 
+misuses of the KS test is when
 the hypothesized distribution has unspecified parameters. 
 \citet{babu2004goodness} approaches this scenario using basic 
-non-parametric bootstrap. There is also the scenario where both the hypothesized 
-distribution has unspecified parameters and additionally the data are 
-serially dependent. \citet{zeimbekakis2022misuses} demonstrates a remedy for
-this scenario using semi-parametric bootstrap. This study aims to address this
-scenario with non-parametric block bootstrap.
+non-parametric bootstrap. There is also the scenario where the data are serially
+dependent, which \citet{zeimbekakis2022misuses} partially remedies with 
+semi-parametric
+bootstrap. The last scenario \citet{zeimbekakis2022misuses} discusses is that
+where both the hypothesized 
+distribution has unspecified parameters and the data are 
+serially dependent. \citet{zeimbekakis2022misuses}'s remedy for
+this scenario also uses semi-parametric bootstrap.
 
-The rest of the paper is outlined as follows: in the first 
-section, we assess whether the KS
+A complete remedy for KS tests with serially dependent data is
+a challenging task. The null distribution depends on the structure of the serial
+dependence, which can be arbitrary in practice. A parametric bootstrap procedure
+would demand a specification for a model for the dependence, whereas the primary 
+interest
+is to test the marginal distribution of the stationary series. A bias 
+correction
+for block bootstrap similar to what \citet{babu2004goodness} did for basic
+bootstrap had not yet been shown.  This study aims to resolve this gap by 
+demonstrating a bias 
+correction
+for non-parametric block bootstrap to use when the hypothesized distribution
+has unspecified parameters and the data are serially dependent.
+
+The rest of the paper is outlined as follows: Section~\ref{sec:methods} reviews
+block bootstrap procedure and demonstrates the basis for bias correction for
+the non-parametric block bootstrap KS test. In Section~\ref{sec:simu}, we first 
+assess whether the KS
 test holds its size; that is, does the test fail to reject the null hypothesis
-when it is true. In the second section, we evaluate the 
+when it is true. In the second part of Section~\ref{sec:simu}, we 
+evaluate the 
 test's power; that is, does the test reject the null hypothesis when it is 
-false.
+false. We show practical applications of this method in Section~\ref{sec:real}.
+First, we apply the method to test if annual maximums of hourly precipitation
+in three U.S. airports follows the GEV distribution in 
+Subsection~\ref{sec:precipitation}.
+Then, we test if Microsoft stock return data follows the Normal or the Student's
+$t$ distribution in Subsection~\ref{sec:microsoft}.
 Finally, we end with 
-concluding remarks in the third section.
+concluding remarks in Section~\ref{sec:conclusion}.
 
@@
 
-\jy{Clarify the GoF test is for the marginal distribution of a statoinary
-  series.}
 Consider a stationary time series $\{X_t: t = 1, \ldots, n\}$ with length~$n$.
-\jy{state the null hypothesis explicitly; we are testing the marginal
-  distribution. Point out the challenges.}
-Let $H_0: X_t ~ F$, where if $F$ is a hypothesized distribution with unknown 
-parameters. Let $H_A$ be that $X_t$ does not follow $F$. This is challenging because we are
-dealing with a situation with both unknown parameters and temporal dependence.
-If $X_t ~ F$, the true marginal distribution of $X_t$ has some parameters 
-$\theta$.
+Let $H_0: X_t \sim F$, where $F$ is a hypothesized marginal distribution with 
+unknown 
+parameters. Let $H_A$ be that the marginal distribution of $X_t$ does not follow 
+$F$. This is challenging 
+because we are
+dealing with a situation with both unknown parameters and serial dependence.
+If $X_t \sim F$, the true marginal distribution of $X_t$ has some parameters 
+$\theta$. The KS goodness-of-fit statistic is to test for the marginal 
+distribution of a stationary series.
 
-\jy{No double letter notations}
-\mc{addressed}
-Consider the goodness of fit statistic:
-\jy{define $Y_n$ before introducing $T_n$}
+Let
 \begin{equation*}
-  T_n := \sup_x|Y_n(x; \hat\theta)|, 
-Y_n(x; \hat\theta) = \sqrt{n}(F_n(x) - F(x; \hat\theta_n)),
+Y_n(x; \hat\theta) = \sqrt{n}(F_n(x) - F(x; \hat\theta_n)).
+\end{equation*}
+Then, the
+goodness of fit statistic is 
+\begin{equation*}
+T_n := \sup_x|Y_n(x; \hat\theta)|.
 \end{equation*}
@@
 
-\jy{respond to my comments}
-
-Let us first consider the case where $X_i$'s are i.i.d. Denote by $F^{(b)}_n$ the
+Let us first consider the case where $X_i$'s are i.i.d. Denote by $F^{(b)}_n$ 
+the
 empirical distribution of the $b$th bootstrap sample and let
-$\hat\theta^{(b)}_n$ be the parameter estimate based on the bootstrap samples. 
+$\hat\theta^{(b)}_n$ be the parameter estimate based on the $b$th bootstrap 
+sample. 
 Using the bootstrap (asymptotic) theory, we can approximate the distribution of
-\jy{Need rephrasing. The two terms are approximated altogether jointly not
-  separately.}
-$\sqrt{n}(F_n(x) - F(x))$
+$\sqrt{n}(F_n(x) - F(x))$ and $\sqrt{n}(F(x; \hat\theta_n) - F(x))$
 by that of $\sqrt{n}(F^{(b)}_n(x) - F_n(x))$
-and the distribution of
-$\sqrt{n}(F(x; \hat\theta_n) - F(x))$
-by that of
-$\sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; \hat\theta_n))$.
+and
+$\sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; \hat\theta_n))$, respectively.
 Therefore, if we define
@@
 \end{equation*}
-then $T^{(b)}_n := \sup_x|Y^{(b)}_n(x)|$ is the bootstrap statistic that is expected
+then $T^{(b)}_n := \sup_x|Y^{(b)}_n(x)|$ is the bootstrap statistic that is 
+expected
 to approximate the distribution of $T_n$. We note that the term
 $\sqrt{n}(F_n(x) - F(x; \hat\theta_n))$ is exactly the bias term considered in 
-Babu and Rao (2004).\jy{cite}
+\citet{babu2004goodness}.
 
@@
 $X^{(b)}_1,...,X^{(b)}_n$ are generated by block bootstrap for 
-$b \in \{1, \ldots, B\}$. Let $E^{(b)}$ refer to the expectation with respect to
+$b \in \{1, \ldots, B\}$.
+
+Block-bootstrap can be done with overlapping or moving blocks.
+Define 
+moving blocks (assuming $l > 1$) as:
+\begin{equation*}
+Z_j =
+    \begin{cases}
+        \{X_j, \ldots, X_{j + l - 1}\}, & \text{if } j = 1, \dots, n - l + 1,\\
+        \{X_j, \ldots, X_n, X_1, \ldots, X_{j-n+l-1}\}, & \text{if } j = n - l
+        + 2 ,\dots, n.
+    \end{cases}
+\end{equation*}
+
+A common 
+function for block size that is considered optimal is 
+$l = \lceil n^{1/3} \rceil$, \citep{buhlmann1999block} 
+which was adopted in this study.
+
+Let $E^{(b)}$ refer to the expectation with respect to
 the bootstrap distribution. In this case, we can 
-approximate the distribution of
-$\sqrt{n}(F_n(x) - F(x))$
-by that of
-$\sqrt{n}(F^{(b)}_n(x) - E^{(b)}[F^{(b)}_n(x)])$,
-\jy{change the languages to add variety}
-and the distribution of $\sqrt{n}(F(x; \theta_n) - F(x))$
-by that of $\sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; E^*[\hat\theta^{(b)}_n]))$.
+use the distribution of $\sqrt{n}(F^{(b)}_n(x) - E^{(b)}[F^{(b)}_n(x)])$ 
+as an approximation of the distribution of
+$\sqrt{n}(F_n(x) - F(x))$,
+and the distribution of 
+$\sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; E^*[\hat\theta^{(b)}_n]))$ to 
+approximate $\sqrt{n}(F(x; \theta_n) - F(x))$'s distribution.
 
@@
 \begin{align*}
-  Y^*_n(x) &= \sqrt{n}(F^{(b)}_n(x) - E^{(b)}[F^{(b)}_n(x)]) - 
+  Y^{(b)}_n(x) &= \sqrt{n}(F^{(b)}_n(x) - E^{(b)}[F^{(b)}_n(x)]) - 
              \sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; E^{(b)}[\hat\theta^{(b)}_n)]) \\
@@
 
-\jy{Summary the procedure in an algorithm.}
+In summary, the procedure of the nonparametric block bootstrap test is 
+summarized as follows.
+\begin{enumerate}
+\item
+  Draw a random sample $X^{(b)}_1,...,X^{(b)}_n$ from the empirical distribution 
+  $F_n$
+  with replacement.
+\item
+  Fit $F_\theta$ to $X^{(b)}_1,...,X^{(b)}_n$ and obtain estimate 
+	$\hat\theta^{(b)}_n$ of $\theta$.
+\item
+  Obtain the empirical distribution function $F^{(b)}_n$ of
+  $X^{(b)}_1,...,X^{(b)}_n$. 
+\item
+  Calculate bootstrap KS statistic
+  \[
+    T^{(b)}_n = \sup_x | \sqrt{n}\left(F^{(b)}_n(x) 
+    - F(x; \hat\theta^{(b)}_n)\right) - B_n(x) |.
+  \]
+  where 
+  $B_{n}(x) = \sqrt{n}(E^{(b)}[F^{(b)}_n(x)] - 
+  F(x; E^{(b)}[\hat\theta^{(b)}_n]))$ is the known
+  bias term.
+\item
+  Repeat the previous steps a large number $B$ times and use the empirical
+  distribution of $T^{(b)}_n$ to approximate the null distribution of the observed
+  statistic. 
+\end{enumerate}
 
 The p-value of the block bootstrap KS test can be computed
-\jy{not right}
-as $p = \#\{T^{(b)}_n < T_n\} / B$ for 
+as $p = \#\{T^{(b)}_n > T_n\} / B$ for 
 $b \in \{1, \ldots, B\}$.
@@
 
+If we can show that the test correctly fails to reject $H_0$ under the null
+distribution, and correctly rejects $H_0$ for an alternate distribution, we can
+state that the method works.
+
 \paragraph{Size}
@@
 test this, we can
-generate a simulated sample $X_t$ from a certain distribution $F(\theta)$,
-and use the block bootstrap KS test to test if $X_t$ is generated from 
-distribution $F$ with some unknown $\theta$. If the test holds its size, the 
+generate a simulated sample $X_t$ with a certain marginal distribution 
+$F_\theta$,
+and use our method to test if $X_t$ indeed has the marginal distribution $F$ 
+with some unknown $\theta$. If the test holds its size, the 
 p-value
@@
 method with different marginal distributions to ensure that it is robust.
-The results of the method depend on the sample size, so we must find the minimum
-sample size required for the block bootstrap KS test to work.
-We can implement the procedure described in methods with the true distribution
-$F ~ N$, hypothesize distribution $F_0 ~ N$, and true mean $\mu = 8$ and 
-standard deviation $\sigma = \sqrt{8}$.
-We replicate this procedure 1000 times to get the distribution of the p-values 
+In order for the method to work, a large sample size may be necessary.
+
+We generated time series with marginal distributions $N(8, 8)$ and 
+$\Gamma(8, 1)$, lag-1 autocorrelation $\phi \in \{-.4, -.2, 0, .2, .4\}$, and
+sample size $n \in \{100, 200, 400, 600, 800, 1600, 3200\}$. For the purposes of 
+evaluating if the test holds it size, when $X_t \sim N(8, 8)$, we tested that the 
+marginal distribution family is normal, and when $X_t \sim \Gamma(8, 1)$, we tested
+that the marginal distribution family is gamma.
+For each setting for $F$, $\phi$, and $n$, we replicate the method 1000 times 
+to get the distribution of the p-values 
 for the test when applied to samples from the same data generating process.
-Then, we repeat the same procedure with $F ~ \Gamma$, and true shape $k = 8$ and
-scale $\theta = 1$.
 
@@
 uniformly distributed. If the distribution of the p-values is uniform, this 
-indicates that the time series follows the null distribution. 
+indicates that under the null hypothesis, our method will only reject the $H_0$
+at a rate of $\alpha$.
 A zoomed in plot for probabilities between 0 and 0.1 is
@@
   \includegraphics[scale=1]{figures/zoom_normal}
-  \caption{A version of the above plot zoomed in to probabilities between 0 and
+  \caption{A Q-Q plot of the p-values displayed in Figure~\ref{fig:normal} zoomed in to 
+  probabilities between 0 and
   0.1}
-  \label{fig:mu}
+  \label{fig:zoom_normal}
 \end{figure}
@@
   \includegraphics[scale=1]{figures/zoom_gamma}
-  \caption{A version of the above plot zoomed in to probabilities between 0 and
+  \caption{A Q-Q plot of the p-values displayed in Figure~\ref{fig:gamma} zoomed in to 
+  probabilities between 0 and
   0.1}
-  \label{fig:mu}
+  \label{fig:zoom_gamma}
 \end{figure}
+
+Although the p-values do not appear to be completely aligned with the line
+in the Q-Q plots for smaller sample sizes like $n = 100$ or $200$, they match
+the lines very closely for $n = 1600$ and $3200$. More importantly, almost
+all of the p-values appear to be within the confidence bands when looking at the
+plots zoomed in to probabilities between 0 and 0.1, and as stated before, 
+researchers are unlikely to choose significance levels above 0.1.
+
+Under $H_0$, the p-values for the non-parametric block bootstrap KS test are
+uniformly distributed. This is an indication that our method 
+holds its size and that we can expect the probability
+of a type 1 error to be the significance level $\alpha$.
 
@@
 We must also evaluate if this method works when $H_0$ is false. We can use
-the block bootstrap KS test to test if $X_t$ is generated from some other 
+the block bootstrap KS test to test if some $X_t \sim F$ is generated from 
+some other 
 distribution $G$ with some unknown $\theta$. In this scenario, if the test is 
 indeed powerful,
-we would ideally want $\beta$, or the probability of rejection to be 1, but we
-expect it to be generally high. Again, we must try the method with different
+we would ideally want $\beta$ 
+(or the probability of failed rejection under $H_A$) 
+to be 0, but we
+expect it to be generally low. Again, we must try the method with different
 marginal distributions to ensure that it is robust.
-We would then expect the distribution of p-values to be non-uniform, and the rate
+We would then expect the distribution of p-values to be non-uniform, and the 
+rate
 of $\#P < \alpha$ to be high, meaning a higher density of low p-values.
 
-If we can show that the test correctly fails to reject $H_0$ under the null
-distribution, and correctly rejects $H_0$ for an alternate distribution, we can
-state that the method works.
+Like we did to see if the test holds its size, we generated time series with marginal distributions $N(8, 8)$ and 
+$\Gamma(8, 1)$, lag-1 autocorrelation $\phi \in \{-.4, -.2, 0, .2, .4\}$, and
+sample size $n \in \{100, 200, 400, 600, 800, 1600, 3200\}$. However, 
+to evaluate the test's power, when $X_t \sim N(8, 8)$, we tested that the 
+marginal distribution family is gamma, and when $X_t \sim \Gamma(8, 1)$, we tested
+that the marginal distribution family is normal.
+For each setting for $F$, $\phi$, and $n$, we replicate the method $R$ times 
+to obtain a p-value $p_r$ for each $r \in \{1, \ldots, R\}$.
 
-We can find the rate of rejection for  different values for the significance 
-level $\alpha$. Additionally, we can construct a 95\% confidence interval for 
-this rate. Below are rejection rates for $\phi = 0.2$ and $n = 800$, when
-applied to the normal and gamma distributions using $\alpha =$ 0.01, 0.05, and 
-0.10.
+Given some significance level $\alpha$, we can compute a rejection rate 
+$q = \#\{p_r < \alpha\} / R$ for $r \in \{1, \ldots, R\}$.
+Additionally, we can construct a 95\% confidence interval for 
+this rate. Below are tables containing rejection rates showcasing the 
+differences when simulation settings are changed.
 
-\input{tables/rr}
+\input{tables/rr_100}
 
-As shown in the above table, the rejection rates for these settings are very 
-high (almost 1), indicating that the test is very powerful for these settings.
+\input{tables/rr_200}
+
+\input{tables/rr_400}
+
+\input{tables/rr_800}
+
+\input{tables/rr_1600}
+
+\input{tables/rr_3200}
+
+From Figure~\ref{table:rr_100}, we can see that when $n = 100$, the rejection rate may 
+be quite low, especially for lower values of $\alpha$. From Figure~\ref{table:rr_200}, 
+the rejection rates are a little higher for $n = 200$, but they may still be 
+drop below 50\% is the $\alpha = 0.1$. Once $n$ reaches 400, we can observe 
+from Figure~\ref{table:rr_400} that the rejection rate
+is consistently above 50\%. For larger sample sizes, the rejection rate is 
+consistently above 90\%. We can also
+observe that the rejection rate is slightly higher for the $\gamma(8, 1)$ sample 
+than for 
+the $N(8, 8)$. As the strength of the temporal dependence increases, the 
+rejection rate decreases, and the rejection
+rate appears to be slightly higher for negative temporal dependence versus 
+positive temporal dependence values of the same strength.
+
+As shown in Figures~\ref{table:rr_800}, \ref{table:rr_1600}, and 
+\ref{table:rr_3200}, the rejection rates for these settings are very 
+high (almost 1), indicating that under $H_A$, the test is very powerful 
+(low probability of failed rejection $\beta$) when a large enough
+sample size is used.
 
 \section{Real Data Analysis}
-
-\jy{Find some real time series to test for their marginal distributions. Open
-  data, for example, temperatures or stock returns or ...}
+\label{sec:real}
 
 \subsection{Precipitation in Mansfield Connecticut}
-Monthly maximums of daily precipiation in inches time series data was retrieved 
-from the John F. Kennedy (JFK) International Airport station from the 
-National Oceanic and Atmospheric Administration.
+\label{sec:precipitation}
+Annual maximums of hourly precipitation in inches time series data were 
+retrieved 
+from the Chicago Midway International Airport (MDW), New York LaGuardia 
+International 
+Airport (LGA),
+and Los Angeles International Airport (LAX) stations from the 
+National Oceanic and Atmospheric Administration. These stations were selected 
+from places of importance in the three largest American cities. LGA and
+MDW were chosen over John F. Kennedy and O'Hare as more data was available
+from these stations. The data for MDW is from
+1948 to 2014, the data for LGA is from 1948 to 2013, and the
+data for LAX is also from 1948 to 2013. We can apply our method to
+the precipitation time series from each of these locations to test if they
+follow the
+Generalized Extreme Value (GEV) distribution. Precipitation maximum series 
+typically do follow the GEV distribution, so we expect to fail to reject the
+null hypothesis.
+
+\input{tables/precipitation_pvals}
 %\mc{https://hdsc.nws.noaa.gov/pfds/pfds_map_cont.html?bkmrk=ct}
 
+Using a significance level as high as .10 still results in a failed rejection
+of the null hypothesis for each of the three tests that the respective 
+time series follow the GEV distribution.
+
 \subsection{Microsoft Stock Returns}
+\label{sec:microsoft}
 
@@
 
-We expect the distribution of Microsoft stock returns to have a slightly
-heavier tail than the normal distribution. We can test that it is normally
-distributed (which we expect to reject). Then we can try testing if it follows
-the $t$ distribution with different degrees of freedoms.
+We expect the marginal distribution of Microsoft stock returns to have a 
+slightly
+heavier tail than the normal distribution. Using the \textsl{tseries} package, 
+\citet{tseries}
+we gathered closing stock prices from January 1st, 1998 to December 31st, 2022.
+Then we approximated stock returns by taking the difference in the logarithm 
+of the closing prices.
+We can test that the stock returns are normally
+distributed (which we expect to reject).  After that, we can test that the
+marginal distribution of the time series follows the Student's $t$ distribution.
+While we 
+could choose to estimate a fitted value of the degrees of freedom parameter $v$
+as
+part of our method, it is very difficult to do so. Therefore, we can try testing 
+if it follows
+the $t$ distribution with increasingly smaller specified degrees of freedoms. We
+can also observe how the method performs using increasingly smaller durations of
+time. First, we try the entire data set which has a duration of 25 years. Then,
+we use the last 5 years of data: January 1st, 2018 to December 31st, 2022.
+Finally, we try the method only using the last year of data: January 1st, 2022
+to December 31st, 2022.
+
+\input{tables/mc_pvals}
+
+We observe that when the duration of time is large, our method rejects the null
+hypothesis unless the degrees of freedom specified is very precise. When
+we use 25 years of data, the method
+only fails to reject the null hypothesis at $\alpha = .05$ when 
+the hypothesized $v = 2.2$, when 
+the precision
+is to the tenths place. For $\alpha = .10$, we only rail to reject the null 
+hypothesis when the hypothesized $v = 2.15$, when the precision is to the 
+hundredths place.
+When using only 5 years of data, the method reaches a p-value of 
+$0.05$ when the hypothesized $v = 2.5$, but the p-value is
+lower for $v = 2.2$ and $v = 2.15$.
+When we only use 1 year of data, the method fails to reject the null hypothesis
+even when the hypothesized distribution family is normal ($v \to \infty$). The
+p-value is maximized at 0.65 when we hypothesize that $v = 5$, but the p-value 
+is lower for smaller values of $v$ when using only 1 year of data.
 
@@
 
-We have shown that given a large enough sample of a time series, the block 
+Using simulation, we have shown that given a large enough sample of a time 
+series, the block 
 bootstrap KS test can appropriately fail to reject the null hypothesis when the
-series follows the null distribution. It requires a larger sample size than 
-basic bootstrap.
+series follows the null distribution. In addition, when the marginal
+distribution is not
+the one hypothesized, the test is powerful. It requires a larger sample size 
+than basic bootstrap to avoid either type I or type II errors. Unsurprisingly,
+the method performs better as the temporal dependence gets weaker. Through
+simulation studies with Normal and Gamma-distributed data, we have shown that
+that the method is robust. We have also 
+demonstrated possible applications of this method to precipitation and 
+stock return data. This method can be used for any study where the goal is
+to see if a time series follows a hypothesized distribution and the parameters
+are unknown or unspecified. Future studies could apply the method showcased
+in this paper to fields like earthquake prediction and astronomy.
 

### 2023-12-13 code/microsoft.R

@@ -1,7 +1,10 @@
 source("functions.R")
 library(tseries)
+library(extraDistr)
+library(xtable)
 microsoft <- 
-  diff(log(get.hist.quote(instrument = "msft", start = "1998-01-01")))
+  diff(log(get.hist.quote(instrument = "msft", start = "1998-01-01", 
+                          end = "2022-12-31")))
 #log difference
 set.seed(123)
 mc_norm_pval <- myapp(as.vector(microsoft[, "Close"]), 1000, "normal", pnorm)
@@ -42,7 +45,8 @@ mc_t2.15_pval <- myapp(as.vector(microsoft[, "Close"]), 1000, "t", plst,
 # the entire data (about 25 years)
 
 microsoft_5y <- 
-  diff(log(get.hist.quote(instrument = "msft", start = "2019-01-01")))
+  diff(log(get.hist.quote(instrument = "msft", start = "2018-01-01",
+                          end = "2022-12-31")))
 
 set.seed(123)
 mc_norm_pval_5y <- myapp(as.vector(microsoft_5y[, "Close"]), 1000, "normal", 
@@ -83,7 +87,8 @@ mc_t2.15_pval_5y <- myapp(as.vector(microsoft_5y[, "Close"]), 1000, "t", plst,
 # the entire data (about 25 years)
 
 microsoft_1y <- 
-  diff(log(get.hist.quote(instrument = "msft", start = "2023-01-01")))
+  diff(log(get.hist.quote(instrument = "msft", start = "2022-01-01",
+                          end = "2022-12-31")))
 
 set.seed(123)
 mc_norm_pval_1y <- myapp(as.vector(microsoft_1y[, "Close"]), 1000, "normal", 
@@ -127,30 +132,30 @@ mc_t2.15_pval_1y <- myapp(as.vector(microsoft_1y[, "Close"]), 1000, "t", plst,
 
 write(print(xtable(
   rbind(data.frame(Duration = "25 Years", Normal = mc_norm_pval, 
-                   `t~30` = mc_t30_pval, `t~20` = mc_t20_pval, 
-                   `t~10` = mc_t10_pval, 
-                   `t~5` = mc_t5_pval, `t~2` = mc_t2_pval, 
-                   `t~2.5` = mc_t2.5_pval, 
-                   `t~2.2` = mc_t2.2_pval, 
-                   `t~2.15` = mc_t2.15_pval),
+                   `t(30)` = mc_t30_pval, `t(20)` = mc_t20_pval, 
[…]

### 2023-12-13 code/precipitation.R

@@ -2,6 +2,7 @@ source('functions.R')
 library(tidyverse)
 library(janitor)
 library(evd)
+library(xtable)
 precipitation <- read.csv("../data/precipitation.csv") %>% 
   clean_names() %>% 
   mutate(date = strptime(date, format = "%Y%m%d %H:%M"))
@@ -37,7 +38,7 @@ lax_pvals <- myapp(lax$annual_max_hpcp, 10000, 'gev', evd::pgev)
 
 write(print(xtable(data.frame(MDW = mdw_pvals, LGA = lga_pvals, LAX =
                                 lax_pvals),
-                   caption = "P-values for testing that annual maximum of hourly 
+                   caption = "P-values for testing that annual maximums of hourly 
             precipitation from the three airports follows the GEV distribution.")), 
         file = "../manuscript/tables/precipitation_pvals.tex")
 

### 2023-12-13 code/tables.R

@@ -10,7 +10,7 @@ write(print(xtable(df_100,
                    different values of AR(1) coefficient and for different 
                    significance levels. Lower and upper bounds are also 
                    included.",
-                   label = "rr_100")), 
+                   label = "table:rr_100")), 
       file = "../manuscript/tables/rr_100.tex")  
 
 df_200 <- df %>% 
@@ -23,7 +23,7 @@ write(print(xtable(df_200,
                    different values of AR(1) coefficient and for different 
                    significance levels. Lower and upper bounds are also 
                    included.",
-                   label = "rr_200")), file = "../manuscript/tables/rr_200.tex")
+                   label = "table:rr_200")), file = "../manuscript/tables/rr_200.tex")
 
 df_400 <- df %>% 
   filter(n == 400) %>% 
@@ -35,7 +35,7 @@ write(print(xtable(df_400,
                    different values of AR(1) coefficient and for different 
                    significance levels. Lower and upper bounds are also 
                    included.",
-                   label = "rr_400")), file = "../manuscript/tables/rr_400.tex")
+                   label = "table:rr_400")), file = "../manuscript/tables/rr_400.tex")
 
 df_800 <- df %>% 
   filter(n == 800) %>% 
@@ -47,7 +47,7 @@ write(print(xtable(df_800,
                    different values of AR(1) coefficient and for different 
                    significance levels. Lower and upper bounds are also 
                    included.",
-                   label = "rr_800")), file = "../manuscript/tables/rr_800.tex")
+                   label = "table:rr_800")), file = "../manuscript/tables/rr_800.tex")
 
 df_1600 <- df %>% 
   filter(n == 1600) %>% 
@@ -59,7 +59,7 @@ write(print(xtable(df_1600,
                    different values of AR(1) coefficient and for different 
                    significance levels. Lower and upper bounds are also 
                    included.",
-                   label = "rr_1600")), file = "../manuscript/tables/rr_1600.tex")
+                   label = "table:rr_1600")), file = "../manuscript/tables/rr_1600.tex")
 
 df_3200 <- df %>% 
   filter(n == 3200) %>% 
@@ -71,5 +71,5 @@ write(print(xtable(df_3200,
                    different values of AR(1) coefficient and for different 
                    significance levels. Lower and upper bounds are also 
                    included.",
-                   label = "rr_3200")), file = "../manuscript/tables/rr_3200.tex")
+                   label = "table:rr_3200")), file = "../manuscript/tables/rr_3200.tex")
 

### 2023-12-14 manuscript/manuscript.tex
Fixed Style Issues

@@
   \label{eq:ks_standard}
-  D_n = \sqrt{n} \sup_x | F_{n}(x) - F(x) |.
+  T_n = \sqrt{n} \sup_x | F_{n}(x) - F(x) |.
 \end{equation}
@@
 function for block size that is considered optimal is 
-$l = \lceil n^{1/3} \rceil$, \citep{buhlmann1999block} 
+$l = \lceil n^{1/3} \rceil$ \citep{buhlmann1999block},  
 which was adopted in this study.
@@
 
-We constructed Q-Q plots of the distribution of the p-values to see if they are
+Using the \textsl{qqplotr} and \textsl{ggplot2} packages 
+\citep{qqplotr, ggplot2},
+we constructed Q-Q plots of the distribution of the p-values to see if they are
 uniformly distributed. If the distribution of the p-values is uniform, this 
@@
 
-Although the p-values do not appear to be completely aligned with the line
+From Figures~\ref{fig:normal} and \ref{fig:gamma}, we can observe that 
+although the p-values do not appear to be 
+completely aligned with the line
 in the Q-Q plots for smaller sample sizes like $n = 100$ or $200$, they match
@@
 all of the p-values appear to be within the confidence bands when looking at the
-plots zoomed in to probabilities between 0 and 0.1, and as stated before, 
+plots zoomed in to probabilities between 0 and 0.1 in 
+Figures~\ref{fig:zoom_normal} and \ref{fig:zoom_gamma}, and as stated 
+before, 
 researchers are unlikely to choose significance levels above 0.1.
@@
 
-Like we did to see if the test holds its size, we generated time series with marginal distributions $N(8, 8)$ and 
+Like we did to see if the test holds its size, we generated time series with 
+marginal distributions $N(8, 8)$ and 
 $\Gamma(8, 1)$, lag-1 autocorrelation $\phi \in \{-.4, -.2, 0, .2, .4\}$, and
@@
 to evaluate the test's power, when $X_t \sim N(8, 8)$, we tested that the 
-marginal distribution family is gamma, and when $X_t \sim \Gamma(8, 1)$, we tested
+marginal distribution family is gamma. Because the support of $N(8, 8)$ is
+$(-\infty, \infty)$, but the support of $\Gamma(8, 1)$ is $(0, \infty)$, we used
+the \textsl{truncdist} package \citep{truncdist} to truncate the series at 
+values less than or equal to 0.
+When $X_t \sim \Gamma(8, 1)$, we tested
 that the marginal distribution family is normal.
@@
 
-From Figure~\ref{table:rr_100}, we can see that when $n = 100$, the rejection rate may 
-be quite low, especially for lower values of $\alpha$. From Figure~\ref{table:rr_200}, 
+From Table~\ref{table:rr_100}, we can see that when $n = 100$, the rejection 
+rate may 
+be quite low, especially for lower values of $\alpha$. From 
+Table~\ref{table:rr_200}, 
 the rejection rates are a little higher for $n = 200$, but they may still be 
 drop below 50\% is the $\alpha = 0.1$. Once $n$ reaches 400, we can observe 
-from Figure~\ref{table:rr_400} that the rejection rate
+from Table~\ref{table:rr_400} that the rejection rate
 is consistently above 50\%. For larger sample sizes, the rejection rate is 
@@
 
-As shown in Figures~\ref{table:rr_800}, \ref{table:rr_1600}, and 
+As shown in Tables~\ref{table:rr_800}, \ref{table:rr_1600}, and 
 \ref{table:rr_3200}, the rejection rates for these settings are very 
@@
 follow the
-Generalized Extreme Value (GEV) distribution. Precipitation maximum series 
+Generalized Extreme Value (GEV) distribution using the \textsl{evd} 
+package \citep{evd}. Precipitation maximum series 
 typically do follow the GEV distribution, so we expect to fail to reject the
@@
 
-Using a significance level as high as .10 still results in a failed rejection
+As displayed in Table~\ref{table:precipitation}, using a significance level as 
+high as .10 still results in a failed rejection
 of the null hypothesis for each of the three tests that the respective 
@@
 slightly
-heavier tail than the normal distribution. Using the \textsl{tseries} package, 
-\citet{tseries}
+heavier tail than the normal distribution. Using the \textsl{tseries} package 
+\citep{tseries}, 
 we gathered closing stock prices from January 1st, 1998 to December 31st, 2022.
@@
 of the closing prices.
-We can test that the stock returns are normally
-distributed (which we expect to reject).  After that, we can test that the
+We tested that the stock returns are normally
+distributed (which we expect to reject).  After that, we tested that the
 marginal distribution of the time series follows the Student's $t$ distribution.
@@
 as
-part of our method, it is very difficult to do so. Therefore, we can try testing 
+part of our method, it is very difficult to do so. Therefore, we attempted to
+test 
 if it follows
-the $t$ distribution with increasingly smaller specified degrees of freedoms. We
-can also observe how the method performs using increasingly smaller durations of
-time. First, we try the entire data set which has a duration of 25 years. Then,
-we use the last 5 years of data: January 1st, 2018 to December 31st, 2022.
-Finally, we try the method only using the last year of data: January 1st, 2022
+the location-scale $t$ distribution with increasingly smaller specified degrees 
+of freedoms. This was achieved with the \textsl{extraDistr} 
+package \citep{extraDistr}. We
+also observed how the method performs using increasingly smaller durations of
+time. First, we tred the entire data set which has a duration of 25 years. Then,
+we used the last 5 years of data: January 1st, 2018 to December 31st, 2022.
+Finally, we tried the method only using the last year of data: January 1st, 2022
 to December 31st, 2022.
@@
 
+The p-values of our test when applied to Microsoft stock return data using
+different settings are showcased in Table~\ref{table:microsoft}.
 We observe that when the duration of time is large, our method rejects the null

### 2023-12-14 code/functions.R

@@ -127,7 +127,7 @@ plot_p_vals <- function(df, filename) {
     stat_pp_point(distribution = "unif", cex = .1) +
     facet_grid(vars(as.numeric(phi)), vars(as.numeric(n))) +
     labs(x = "Probability Points", y = "Cumulative Probability") +
-    coord_cartesian(ylim = c(0, 0.1), xlim = c(0, 0.1))
+    coord_fixed(ylim = c(0, 0.1), xlim = c(0, 0.1))
   ggsave(filename = paste('zoom_', filename, sep = ''), plot = gg.f, 
          path = "../manuscript/figures", height = 4, width = 4)
 }

### 2023-12-14 code/microsoft.R

@@ -132,32 +132,33 @@ mc_t2.15_pval_1y <- myapp(as.vector(microsoft_1y[, "Close"]), 1000, "t", plst,
 
 write(print(xtable(
   rbind(data.frame(Duration = "25 Years", Normal = mc_norm_pval, 
-                   `t(30)` = mc_t30_pval, `t(20)` = mc_t20_pval, 
-                   `t(10)` = mc_t10_pval, 
-                   `t(5)` = mc_t5_pval, `t(2)` = mc_t2_pval, 
-                   `t(2.5)` = mc_t2.5_pval, 
-                   `t(2.2)` = mc_t2.2_pval, 
-                   `t(2.15)` = mc_t2.15_pval),
+                   `t, v = 30` = mc_t30_pval, `t, v = 20` = mc_t20_pval, 
+                   `t, v = 10` = mc_t10_pval, 
+                   `t, v = 5` = mc_t5_pval, `t, v = 2` = mc_t2_pval, 
+                   `t, v = 2.5` = mc_t2.5_pval, 
+                   `t, v = 2.2` = mc_t2.2_pval, 
+                   `t, v = 2.15` = mc_t2.15_pval),
         data.frame(Duration = "5 Years", Normal = mc_norm_pval_5y, 
-                   `t(30)` = mc_t30_pval_5y, 
-                   `t(20)` = mc_t20_pval_5y, 
-                   `t(10)` = mc_t10_pval_5y, 
-                   `t(5)` = mc_t5_pval_5y, 
-                   `t(2)` = mc_t2_pval_5y, 
-                   `t(2.5)` = mc_t2.5_pval_5y, 
-                   `t(2.2)` = mc_t2.2_pval_5y, 
-                   `t(2.15)` = mc_t2.15_pval_5y),
+                   `t, v = 30` = mc_t30_pval_5y, 
+                   `t, v = 20` = mc_t20_pval_5y, 
+                   `t, v = 10` = mc_t10_pval_5y, 
+                   `t, v = 5` = mc_t5_pval_5y, 
+                   `t, v = 2` = mc_t2_pval_5y, 
+                   `t, v = 2.5` = mc_t2.5_pval_5y, 
+                   `t, v = 2.2` = mc_t2.2_pval_5y, 
+                   `t, v = 2.15` = mc_t2.15_pval_5y),
         data.frame(Duration = "1 Year", Normal = mc_norm_pval_1y, 
[…]

### 2023-12-14 code/precipitation.R

@@ -39,6 +39,8 @@ lax_pvals <- myapp(lax$annual_max_hpcp, 10000, 'gev', evd::pgev)
 write(print(xtable(data.frame(MDW = mdw_pvals, LGA = lga_pvals, LAX =
                                 lax_pvals),
                    caption = "P-values for testing that annual maximums of hourly 
-            precipitation from the three airports follows the GEV distribution.")), 
+            precipitation from the three airports follows the GEV distribution.",
+            label = "table:precipitation"), 
+            caption.placement = "top"), 
         file = "../manuscript/tables/precipitation_pvals.tex")
 

### 2024-01-15 manuscript/manuscript.tex
comments/edits

@@
-\documentclass[12pt, letterpaper]{article}
+\documentclass[12pt, titlepage, letterpaper]{article}
 %\documentclass[12pt, letterpaper, titlepage]{article}
@@
 
-\title{\bf Nonparametric Bootstrap Kolmogorov-Smirnov Test for
-  Goodness-of-Fit of Marginal Distributions of Stationary Time Series}
+\title{\bf Nonparametric Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test for
+  Marginal Distributions of Stationary Time Series}
 \if0\blind
@@
 \label{sec:intro}
+
+\jy{Start from the need for KS test for stationary series; review existing works
+  and identify the gap; summarize the contribution.}
 
@@
 Consider a stationary time series $\{X_t: t = 1, \ldots, n\}$ with length~$n$.
-Let $H_0: X_t \sim F$, where $F$ is a hypothesized marginal distribution with 
-unknown 
-parameters. Let $H_A$ be that the marginal distribution of $X_t$ does not follow 
-$F$. This is challenging 
-because we are
-dealing with a situation with both unknown parameters and serial dependence.
-If $X_t \sim F$, the true marginal distribution of $X_t$ has some parameters 
-$\theta$. The KS goodness-of-fit statistic is to test for the marginal 
-distribution of a stationary series.
+We are interested in testing whether or not $X_t$ follows a distribution in a
+parametric family of distribution~$F$ indexed by a parameter
+vector~$\theta$. That is, the null hypothesis is
+\[
+  H_0: X_t \sim F(\cdot \mid \theta), \quad t = 1, \ldots, n,
+\]
+for some unspecified parameter $\theta$.
+The alternative hypothesis $H_A$ is that the marginal distribution of $X_t$ does
+not follow~$F$ for any parameter value~$\theta$. This is a challenging situation
+both the parameters and the serial dependence structure are unknown.
+
+\jy{Need a better opening sentence. Notation $\hat\theta_n$ and $F_n$ have
+  not been defined.}
 
@@
 Let us first consider the case where $X_i$'s are i.i.d. Denote by $F^{(b)}_n$ 
-the
-empirical distribution of the $b$th bootstrap sample and let
+the empirical distribution of the $b$th bootstrap sample and let
 $\hat\theta^{(b)}_n$ be the parameter estimate based on the $b$th bootstrap 
@@
 Using the bootstrap (asymptotic) theory, we can approximate the distribution of
+\jy{need references to back up}
 $\sqrt{n}(F_n(x) - F(x))$ and $\sqrt{n}(F(x; \hat\theta_n) - F(x))$
@@
 Therefore, if we define
-\begin{equation*}
-Y^{(b)}_n(x) = \sqrt{n}(F^{(b)}_n(x) - F_n(x)) - 
-\sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; \hat\theta_n)) 
-= \sqrt{n}(F^{(b)}_n(x) - F(x; \hat\theta^{(b)}_n)) - 
+\begin{align*}
+Y^{(b)}_n(x) &= \sqrt{n}(F^{(b)}_n(x) - F_n(x)) - 
+               \sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; \hat\theta_n)) \\
+             &= \sqrt{n}(F^{(b)}_n(x) - F(x; \hat\theta^{(b)}_n)) - 
                \sqrt{n}(F_n(x) - F(x; \hat\theta_n)),
-\end{equation*}
+\end{align*}
 then $T^{(b)}_n := \sup_x|Y^{(b)}_n(x)|$ is the bootstrap statistic that is 
@@
 $b \in \{1, \ldots, B\}$.  
-
 Block-bootstrap can be done with overlapping or moving blocks.
@@
 \end{equation*}
-
 A common 
@@
 
+\jy{Not good opening sentence}
 Let $E^{(b)}$ refer to the expectation with respect to
@@
 use the distribution of $\sqrt{n}(F^{(b)}_n(x) - E^{(b)}[F^{(b)}_n(x)])$
+\jy{The second term: does it depend on $b$? }
 as an approximation of the distribution of
@@
 We can compute $E^{(b)}[F^{(b)}_n(x)]$ and
+\jy{Are these two terms $b$-specific?}
 $E^{(b)}[\hat\theta^{(b)}_n]$ numerically (they can also be computed analytically, 
@@
 
-\paragraph{Size}
+\subsection{Size}
 We first must evaluate whether this method works when $H_0$ is true. To
@@
 
+\jy{Give details on how the data were generated. Are these enough infomation for
+  people reproduce the results? I'd suggest that we use Kendall's tau to measure
+  the serial dependence. }
+
+\jy{How many replicates were used to estimate the size and power?}
+
 We generated time series with marginal distributions $N(8, 8)$ and
+\jy{why choose these two distributions?}
 $\Gamma(8, 1)$, lag-1 autocorrelation $\phi \in \{-.4, -.2, 0, .2, .4\}$, and
@@
 
+\jy{Reduce width of  the panel title section. Reduce the font size of the
+  labels. Generate the figures with the right size in mind. Use whole textwidth.}
+
 \begin{figure}[tbp]
   \centering
-  \includegraphics[scale=1]{figures/normal}
+  \includegraphics[width = \textwidth]{figures/normal}
   \caption{A Q-Q plot of the p-values testing that a distribution
@@
   \centering
-  \includegraphics[scale=1]{figures/zoom_normal}
+  \includegraphics[width = \textwidth]{figures/zoom_normal}
   \caption{A Q-Q plot of the p-values displayed in Figure~\ref{fig:normal} zoomed in to 
@@
 
-\paragraph{Power}
+\subsection{Power}
 We must also evaluate if this method works when $H_0$ is false. We can use
@@
 differences when simulation settings are changed.
+
+\jy{Clean up the tables. Use percentage for power. Keep three effective
+  digits. Why are there so many decimal places? }
+
+\jy{Only three sample sizes will be enough. Sample size 800 or higher give
+  power~1. Only report nominal size 0.05 would be ok. May consider presenting
+  the intervals in a figure.}
 
@@
 
+\jy{No need for such small a table. Could plot the histogram and fitted density.}
+
 \input{tables/precipitation_pvals}
@@
 distributed (which we expect to reject).  After that, we tested that the
-marginal distribution of the time series follows the Student's $t$ distribution.
+marginal distribution of the time series follows the Student's $t$ distribution
+with a fixed degrees of freedom.
 While we 
@@
 \input{tables/mc_pvals}
+
+\jy{Normal was not rejected for 1 year. How about 2 year, 3 year, 4 year?}
 
@@
 
+\jy{Quality control the bib source}
+
 \bibliographystyle{chicago}

### 2024-01-21 manuscript/manuscript.tex
Tried Different Durations

@@
 
+First, let us consider how the KS statistic is typically computed for a sample
+with no dependence structure.
+Let $\hat\theta_n$ denote the fitted parameters for the hypothesized 
+distribution fitted onto $X_t$, and let 
+$F_n$ denote the empirical distribution function based on $X_1,...,X_n$
 \jy{Need a better opening sentence. Notation $\hat\theta_n$ and $F_n$ have
   not been defined.}
+\mc{addressed}
 
@@
 \end{equation*}
-where $F_n$ denotes the empirical distribution function based on $X_1,...,X_n$,
-and $\hat\theta_n$ denotes the fitted parameters for the hypothesized 
-distribution fitted onto $X_t$.
+
 We note that
@@
 
-\jy{Not good opening sentence}
+We then use the bootstrap distribution to construct an approximation of
+the KS statistic.
+\jy{Not good opening sentence}\mc{addressed}
 Let $E^{(b)}$ refer to the expectation with respect to
@@
 \jy{How many replicates were used to estimate the size and power?}
+\mc{addressed}
 
@@
 marginal distribution family is normal, and when $X_t \sim \Gamma(8, 1)$, we tested
-that the marginal distribution family is gamma.
+that the marginal distribution family is gamma. For the block bootstrap step,
+we used $B = 1000$ and $l = \lceil n^{1/3} \rceil$.
 For each setting for $F$, $\phi$, and $n$, we replicate the method 1000 times 
@@
 When $X_t \sim \Gamma(8, 1)$, we tested
-that the marginal distribution family is normal.
-For each setting for $F$, $\phi$, and $n$, we replicate the method $R$ times 
-to obtain a p-value $p_r$ for each $r \in \{1, \ldots, R\}$.
+that the marginal distribution family is normal. For the block bootstrap step,
+we used $B = 1000$ and $l = \lceil n^{1/3} \rceil$.
+For each setting for $F$, $\phi$, and $n$, we replicate the method $1000$ times 
+to obtain a p-value $p_r$ for each $r \in \{1, \ldots, 1000\}$.
 
 Given some significance level $\alpha$, we can compute a rejection rate 
-$q = \#\{p_r < \alpha\} / R$ for $r \in \{1, \ldots, R\}$.
+$q = \#\{p_r < \alpha\} / 1000$ for $r \in \{1, \ldots, 1000\}$.
 Additionally, we can construct a 95\% confidence interval for 

### 2024-01-21 code/hpc_functions.R

@@ -1,16 +1,10 @@
 library(tidyverse)
-#library(evd)
 library(truncdist)
 #library(qqplotr)
-mystat <- function(x, dist, df = NULL) {
+mystat <- function(x, dist) {
   # Bootstrap will return actual pseudo-sample, mean, and standard deviation
-  if (dist == 'gev') {
-    c(c(x), 
-      evd::fgev(x, std.err = FALSE)$estimate)
-  } else {
-    c(c(x),  
-      MASS::fitdistr(x, dist, df = df)$estimate)
-  }
+  c(c(x),  
+    MASS::fitdistr(x, dist)$estimate)
 }
 
 mysim <- function(n, blksize, B, h0_dist, true_dist, f0, f, theta, phi, rho) {
@@ -39,7 +33,7 @@ mysim <- function(n, blksize, B, h0_dist, true_dist, f0, f, theta, phi, rho) {
   # of the cdfs can be computed
   list_emp <- matrix(, nrow = 0, ncol = n) 
   list_theta <- matrix(, nrow = 0, ncol = length(fit_theta)) 
-
+  
   sum_theta <- 0
   
   for (i in 1:B) {
@@ -61,72 +55,42 @@ mysim <- function(n, blksize, B, h0_dist, true_dist, f0, f, theta, phi, rho) {
   c(mean(ks_values > obsv_ks)) # Which are greater than the observed ks statistic
 }
 
-myapp <- function(y, B, h0_dist, f0, df = NULL) {
-  n <- length(y)
-  blksize <- ceiling(n^(1/3))
-  emp <- ecdf(y)(sort(y)) # observed empirical distribution
-  if (h0_dist == 'gev') {
-    fit_theta <- evd::fgev(y, std.err = FALSE)$estimate # gev not recognised by fitdistr
-  } else {
-    fit_theta <- MASS::fitdistr(y, h0_dist, df = df)$estimate # observed fitted values
-  }
-  
-  fit <- do.call(f0, c(list(sort(y)), as.list(c(df, fit_theta)))) # observed fitted distribution
-  obsv_ks <- sqrt(n) * max(abs(emp - fit)) # observed ks statistic
-  
-  # Block Bootstrap
-  bts <- boot::tsboot(y, mystat, l = blksize, sim = "fixed", R = B, 
-                      dist = h0_dist, df = df)
-  
-  # Data must be restructured in the following ways, so the expected value
-  # of the cdfs can be computed
-  list_emp <- matrix(, nrow = 0, ncol = n) 
[…]

### 2024-01-21 code/jobs.sh

@@ -1,7 +1,7 @@
 #!/bin/bash
 #SBATCH --partition=general
 #SBATCH --output=../out/ja_%A_%a.out
-#SBATCH --array=1-100%100
+#SBATCH --array=1-200%200
 #SBATCH --ntasks=1 ## OBS 1
 #SBATCH --cpus-per-task=1 ## OBS 2
 #SBATCH --mem-per-cpu=500M ## OBS 3

### 2024-01-21 code/null_jobs.R

@@ -1,7 +1,7 @@
-source("functions.R")
+source("hpc_functions.R")
 i <- Sys.getenv("SLURM_ARRAY_TASK_ID")
 B <- 1000
-nrep <- 10
+nrep <- 5
 for (phi in c(-.4, -.2, 0, .2, .4)) {
   for (n in c(100, 200, 400, 800, 1600, 3200)) {
     for (true_dist in c("normal", "gamma")) {

### 2024-01-22 manuscript/manuscript.tex
responded to some comments

@@
   digits. Why are there so many decimal places? }
+\mc{reduced number of digits}
 
@@
   the intervals in a figure.}
-
-\input{tables/rr_100}
+\mc{only included three sample sizes and for alpha $=$ 0.05}
 
@@
 
-\input{tables/rr_1600}
-
-\input{tables/rr_3200}
-
-From Table~\ref{table:rr_100}, we can see that when $n = 100$, the rejection 
-rate may 
-be quite low, especially for lower values of $\alpha$. From 
+From 
 Table~\ref{table:rr_200}, 
@@
 
-As shown in Tables~\ref{table:rr_800}, \ref{table:rr_1600}, and 
-\ref{table:rr_3200}, the rejection rates for these settings are very 
+As shown in Tables~\ref{table:rr_800}, the rejection rates for this settings 
+are very 
 high (almost 1), indicating that under $H_A$, the test is very powerful 
@@
 \jy{Normal was not rejected for 1 year. How about 2 year, 3 year, 4 year?}
+\mc{tried these sample sizes, normal is rejected for all three might want to
+try 1.5 years}
 

### 2024-01-22 manuscript/manuscript.tex
removed unnecessary b

@@
 \jy{Not good opening sentence}\mc{addressed}
-Let $E^{(b)}$ refer to the expectation with respect to
-the bootstrap distribution. In this case, we can 
-use the distribution of $\sqrt{n}(F^{(b)}_n(x) - E^{(b)}[F^{(b)}_n(x)])$
-\jy{The second term: does it depend on $b$? }
+In this case, we can 
+use the distribution of $\sqrt{n}(F^{(b)}_n(x) - E[F^{(b)}_n(x)])$
+\jy{The second term: does it depend on $b$? }\mc{addressed}
 as an approximation of the distribution of
@@
 and the distribution of 
-$\sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; E^*[\hat\theta^{(b)}_n]))$ to
+$\sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; E[\hat\theta^{(b)}_n]))$ to
 approximate $\sqrt{n}(F(x; \theta_n) - F(x))$'s distribution.
 
-We can compute $E^{(b)}[F^{(b)}_n(x)]$ and
-\jy{Are these two terms $b$-specific?}
-$E^{(b)}[\hat\theta^{(b)}_n]$ numerically (they can also be computed analytically, 
+We can compute $E[F^{(b)}_n(x)]$ and
+\jy{Are these two terms $b$-specific?}\mc{addressed}
+$E[\hat\theta^{(b)}_n]$ numerically (they can also be computed analytically, 
 depending on the types of block bootstrap we use). One can compute 
@@
 the $b$th bootstrap sample. Then
-$E^{(b)}[F^{(b)}_n(x)] \approx \frac{1}{B}\sum_{b = 1}^BF^{(b)}_n(x)$, and
-$E^{(b)}[\hat\theta^{(b)}_n] \approx \frac{1}{B}\sum_{b = 1}^B\hat\theta^{(b)}_n$.
+$E[F^{(b)}_n(x)] \approx \frac{1}{B}\sum_{b = 1}^BF^{(b)}_n(x)$, and
+$E[\hat\theta^{(b)}_n] \approx \frac{1}{B}\sum_{b = 1}^B\hat\theta^{(b)}_n$.
 In this case, we can define
 \begin{align*}
-  Y^{(b)}_n(x) &= \sqrt{n}(F^{(b)}_n(x) - E^{(b)}[F^{(b)}_n(x)]) - 
-             \sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; E^{(b)}[\hat\theta^{(b)}_n)]) \\
+  Y^{(b)}_n(x) &= \sqrt{n}(F^{(b)}_n(x) - E[F^{(b)}_n(x)]) - 
+             \sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; E[\hat\theta^{(b)}_n)]) \\
            &= \sqrt{n}(F^{(b)}_n(x) - F(x; \hat\theta^{(b)}_n)) -
-             \sqrt{n}(E^{(b)}[F^{(b)}_n(x)] - F(x; E^{(b)}[\hat\theta^{(b)}_n])),
+             \sqrt{n}(E[F^{(b)}_n(x)] - F(x; E[\hat\theta^{(b)}_n])),
 \end{align*}
@@
   where 
-  $B_{n}(x) = \sqrt{n}(E^{(b)}[F^{(b)}_n(x)] - 
-  F(x; E^{(b)}[\hat\theta^{(b)}_n]))$ is the known
+  $B_{n}(x) = \sqrt{n}(E[F^{(b)}_n(x)] - 
+  F(x; E[\hat\theta^{(b)}_n]))$ is the known
   bias term.

### 2024-01-23 manuscript/manuscript.tex
comments

@@
 $F_n$ denote the empirical distribution function based on $X_1,...,X_n$
-\jy{Need a better opening sentence. Notation $\hat\theta_n$ and $F_n$ have
-  not been defined.}
-\mc{addressed}
-
 Let
@@
     \begin{cases}
-        \{X_j, \ldots, X_{j + l - 1}\}, & \text{if } j = 1, \dots, n - l + 1,\\
-        \{X_j, \ldots, X_n, X_1, \ldots, X_{j-n+l-1}\}, & \text{if } j = n - l
+        \{X_j, \ldots, X_{j + l - 1}\}, & j = 1, \dots, n - l + 1,\\
+        \{X_j, \ldots, X_n, X_1, \ldots, X_{j-n+l-1}\}, & j = n - l
         + 2 ,\dots, n.
@@
 
-We then use the bootstrap distribution to construct an approximation of
-the KS statistic.
-\jy{Not good opening sentence}\mc{addressed}
-In this case, we can 
+We then use bootstrap to approximate the distribuition of
+the KS statistic under $H_0$. In this case, we can 
 use the distribution of $\sqrt{n}(F^{(b)}_n(x) - E[F^{(b)}_n(x)])$
-\jy{The second term: does it depend on $b$? }\mc{addressed}
 as an approximation of the distribution of
@@
 We can compute $E[F^{(b)}_n(x)]$ and
-\jy{Are these two terms $b$-specific?}\mc{addressed}
 $E[\hat\theta^{(b)}_n]$ numerically (they can also be computed analytically, 
@@
 \end{align*}
-and $T^{(b)}_n = \sup_x|Y^{(b)}_n(x)|$.
+and $T^{(b)}_n = \sup_x|Y^{(b)}_n(x)|$. Each $T_n^{(b)}$,
+$b =1, \ldots, B$, is considered a draw from a distribution that approximates
+the distribution of $T_n$. Therefore, the p-value of the observed statistic
+$T_n$ can be assessed by positioning it agains the empirical distribution of
+$T_n^{(b)}$, $b = 1, \ldots, B$.
 
@@
 summarized as follows.
+\jy{Whrere is the 'block' part?}
 \begin{enumerate}
 \item
-  Draw a random sample $X^{(b)}_1,...,X^{(b)}_n$ from the empirical distribution 
-  $F_n$
-  with replacement.
+  Draw a random sample $X^{(b)}_1,...,X^{(b)}_n$ from the empirical
+  distribution~$F_n$.
 \item
@@
   the serial dependence. }
-
-\jy{How many replicates were used to estimate the size and power?}
-\mc{addressed}
 
@@
 
+\jy{The large number decimals in the old table: some numerical issues?}
+
 \jy{Only three sample sizes will be enough. Sample size 800 or higher give
@@
 \mc{only included three sample sizes and for alpha $=$ 0.05}
+
+\jy{Consider presenting this in a graph. Try explaining the pattern.
+  Keep the notations consistent: $n$ and n are different.}
 
@@
 
+\jy{I'm surprised that t does not fit well even for two years data.}
+
+\jy{Report the autocorrelation estimate of residual and residual squared in the
+  text.}
+
 The p-values of our test when applied to Microsoft stock return data using

### 2024-01-23 manuscript/manuscript.tex
some changes

--- 2024-01-22 manuscript/manuscript.tex
@@
 We generated time series with marginal distributions $N(8, 8)$ and
-\jy{why choose these two distributions?}
+\jy{why choose these two distributions?}\mc{addressed}
 $\Gamma(8, 1)$, lag-1 autocorrelation $\phi \in \{-.4, -.2, 0, .2, .4\}$, and
-sample size $n \in \{100, 200, 400, 600, 800, 1600, 3200\}$. For the purposes of 
+sample size $n \in \{100, 200, 400, 800, 1600, 3200\}$. These distributions
+were chosen to compare results on normal and non-normal
+error structures, and the parameters were chosen so that the distributions
+have the same mean 8 and variance 8. To generate 
+For the purposes of 
 evaluating if the test holds it size, when $X_t \sim N(8, 8)$, we tested that the 
@@
 $\Gamma(8, 1)$, lag-1 autocorrelation $\phi \in \{-.4, -.2, 0, .2, .4\}$, and
-sample size $n \in \{100, 200, 400, 600, 800, 1600, 3200\}$. However, 
+sample size $n \in \{200, 400, 800\}$. However, 
 to evaluate the test's power, when $X_t \sim N(8, 8)$, we tested that the 

### 2024-01-23 code/hpc_functions.R

@@ -1,6 +1,6 @@
+.libPaths("~/rlibs")
 library(tidyverse)
 library(truncdist)
-#library(qqplotr)
 mystat <- function(x, dist) {
   # Bootstrap will return actual pseudo-sample, mean, and standard deviation
   c(c(x),  
@@ -53,44 +53,4 @@ mysim <- function(n, blksize, B, h0_dist, true_dist, f0, f, theta, phi, rho) {
     ks_values <- c(ks_values, sqrt(n) * max(abs((boot_emp - boot_fit - bias_term)))) # bootstrap ks statistics
   }
   c(mean(ks_values > obsv_ks)) # Which are greater than the observed ks statistic
-}
-
-plot_p_vals <- function(filename) {
-  pvals <- readRDS(paste("../data/", filename, ".RDS", sep = ''))
-  nrep <- length(pvals)
-  df <- data.frame(matrix(NA,    # Create empty data frame
-                          nrow = nrep,
-                          ncol = 1))
-  df$p <- pvals
-  gg.f <- ggplot(data = df, mapping = aes(sample = p)) +
-    scale_x_continuous(breaks=c(0, 1)) +
-    scale_y_continuous(breaks=c(0, 1)) + 
-    stat_pp_band(distribution = "unif") +
-    stat_pp_line() +
-    stat_pp_point(distribution = "unif", cex = .1) +
-    labs(x = "Probability Points", y = "Cumulative Probability") +
-    coord_fixed() # theme(aspect.ratio=1)
-  ggsave(filename = paste(filename, ".pdf", sep = ''), plot = gg.f, 
-         path = "../manuscript/figures", height = 4, width = 4)
-  gg.f <- ggplot(data = df, mapping = aes(sample = p)) +
-    scale_x_continuous(breaks=c(0, 0.1)) +
-    scale_y_continuous(breaks=c(0, 0.1)) + 
-    stat_pp_band(distribution = "unif") +
-    stat_pp_line() +
-    stat_pp_point(distribution = "unif", cex = .1) +
-    labs(x = "Probability Points", y = "Cumulative Probability") +
-    coord_cartesian(ylim = c(0, 0.1), xlim = c(0, 0.1))
-  ggsave(filename = paste("zoom_", filename, ".pdf", sep = ''), plot = gg.f, 
-         path = "../manuscript/figures", height = 4, width = 4)
-  gg.f <- ggplot(data = df, mapping = aes(sample = p)) +
[…]

### 2024-01-28 manuscript/manuscript.tex
New Plots

@@
 
-\input{tables/rr_200}
-
-\input{tables/rr_400}
-
-\input{tables/rr_800}
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[scale=1]{figures/rr}
+  \caption{A plot of the rejection rates as a function of $\tau$ for
+ $n \in \{100, 200, 400, 800\}$ and marginal distribution 
+ $\in \{N(8,8), \gamma(8,1)\}$.}
+  \label{fig:rr}
+\end{figure}
 
 From 
-Table~\ref{table:rr_200}, 
+Table~\ref{fig:rr}, 
 the rejection rates are a little higher for $n = 200$, but they may still be 
 drop below 50\% is the $\alpha = 0.1$. Once $n$ reaches 400, we can observe 
-from Table~\ref{table:rr_400} that the rejection rate
+that the rejection rate
 is consistently above 50\%. For larger sample sizes, the rejection rate is 
@@
 
-As shown in Tables~\ref{table:rr_800}, the rejection rates for this settings 
+The rejection rates for $n = 800$
 are very 

### 2024-01-28 code/alt_jobs.R

@@ -1,9 +1,17 @@
 source("hpc_functions.R")
+# library(copula)
 i <- Sys.getenv("SLURM_ARRAY_TASK_ID")
 B <- 1000
 nrep <- 5
-for (phi in c(-.4, -.2, 0, .2, .4)) {
-  for (n in c(100, 200, 400, 800, 1600, 3200)) {
+phis <- c()
+# for (i in c(-.75, -.5, -.25, 0, .25, .5, .75)) {
+#   phis <- c(phis, iTau(normalCopula(), i))
+# }
+phis <- 
+  c(-0.9238795, -0.7071068, -0.3826834, 0, 0.3826834, 0.7071068, 0.9238795)
+i <- Sys.getenv("SLURM_ARRAY_TASK_ID")
+for (phi in phis) {
+  for (n in c(100, 200, 400, 800)) {
     for (true_dist in c("normal", "gamma")) {
       set.seed(as.integer(i))
       if (true_dist == "normal") {

### 2024-01-28 code/data_processing.R

@@ -1,10 +1,12 @@
 library(tidyverse)
 library(janitor)
-setwd("../data")
+setwd("../data/simulation")
 
 file_names <- list.files(pattern = "^sim")
-for (phi in c(-.4, -.2, 0, .2, .4)) {
-  for (n in c(100, 200, 400, 800, 1600, 3200)) {
+phis <- 
+  c(-0.9238795, -0.7071068, -0.3826834, 0, 0.3826834, 0.7071068, 0.9238795)
+for (phi in phis) {
+  for (n in c(100, 200, 400, 800)) {
     for (dist in c("normal", "gamma")) {
       list <- file_names[which(grepl(paste("_", n, "_", dist, "_", phi, "_0_", sep = ''), 
                                      file_names))]
@@ -12,7 +14,7 @@ for (phi in c(-.4, -.2, 0, .2, .4)) {
       for (file in list) {
         tosave <- c(tosave, readRDS(file)$p)
       }
-      saveRDS(tosave, file = paste("sim_", n, "_", dist, "_",
+      saveRDS(tosave, file = paste("../sim_", n, "_", dist, "_",
                                    phi, '_', 
                                    '0', ".RDS", sep = ''))
     }
@@ -20,8 +22,8 @@ for (phi in c(-.4, -.2, 0, .2, .4)) {
 }
 
 file_names <- list.files(pattern = "^alt")
-for (phi in c(-.4, -.2, 0, .2, .4)) {
-  for (n in c(100, 200, 400, 800, 1600, 3200)) {
+for (phi in phis) {
+  for (n in c(100, 200, 400, 800)) {
     for (dist in c("normal", "gamma")) {
       list <- file_names[which(grepl(paste("_", n, "_", dist, "_", phi, "_0_", sep = ''), 
                                      file_names))]
@@ -29,7 +31,7 @@ for (phi in c(-.4, -.2, 0, .2, .4)) {
       for (file in list) {
         tosave <- c(tosave, readRDS(file)$p)
       }
-      saveRDS(tosave, file = paste("alt_", n, "_", dist, "_",
+      saveRDS(tosave, file = paste("../alt_", n, "_", dist, "_",
                                    phi, '_', 
                                    '0', ".RDS", sep = ''))
     }
[…]

### 2024-01-28 code/functions.R

@@ -2,6 +2,7 @@ library(tidyverse)
 library(evd)
 library(truncdist)
 library(qqplotr)
+library(copula)
 mystat <- function(x, dist, df = NULL) {
   # Bootstrap will return actual pseudo-sample, mean, and standard deviation
   if (dist == 'gev') {
@@ -105,13 +106,22 @@ myapp <- function(y, B, h0_dist, f0, df = NULL) {
 }
 
 plot_p_vals <- function(df, filename) {
+  
+  df$tau <- case_when(df$phi == -0.9238795 ~ -0.75,
+                      df$phi == -0.7071068 ~ -0.5,
+                      df$phi == -0.3826834 ~ -0.25,
+                      df$phi == 0 ~ 0,
+                      df$phi == 0.9238795 ~ 0.75,
+                      df$phi == 0.7071068 ~ 0.5,
+                      df$phi == 0.3826834 ~ 0.25)
+  
   gg.f <- ggplot(data = df, mapping = aes(sample = pval)) +
     scale_x_continuous(breaks=c(0, 1)) +
     scale_y_continuous(breaks=c(0, 1)) + 
     stat_pp_band(distribution = "unif") +
     stat_pp_line() +
     stat_pp_point(distribution = "unif", cex = .1) +
-    facet_grid(vars(as.numeric(phi)), vars(as.numeric(n))) +
+    facet_grid(vars(as.numeric(n)), vars(as.numeric(tau))) +
     labs(x = "Probability Points", y = "Cumulative Probability") +
     coord_fixed() +
     theme(strip.text.x = element_text(size = 8))
@@ -124,11 +134,28 @@ plot_p_vals <- function(df, filename) {
     stat_pp_band(distribution = "unif") +
     stat_pp_line() +
     stat_pp_point(distribution = "unif", cex = .1) +
-    facet_grid(vars(as.numeric(phi)), vars(as.numeric(n))) +
+    facet_grid(vars(as.numeric(n)), vars(as.numeric(tau))) +
     labs(x = "Probability Points", y = "Cumulative Probability") +
     coord_fixed(ylim = c(0, 0.1), xlim = c(0, 0.1)) +
     theme(strip.text.x = element_text(size = 8))
   ggsave(filename = paste('zoom_', filename, sep = ''), plot = gg.f, 
          path = "../manuscript/figures", height = 6, width = 6)
+}
+
+plot_rr <- function(df, filename) {
[…]

### 2024-01-28 code/hpc_functions.R

@@ -1,4 +1,4 @@
-.libPaths("~/rlibs")
+.libPaths("/gpfs/homefs1/mac18033/rlibs")
 library(tidyverse)
 library(truncdist)
 mystat <- function(x, dist) {
@@ -27,7 +27,7 @@ mysim <- function(n, blksize, B, h0_dist, true_dist, f0, f, theta, phi, rho) {
   
   # Block Bootstrap
   bts <- boot::tsboot(y, mystat, l = blksize, sim = "fixed", R = B, 
-                      dist = h0_dist, df = df)
+                      dist = h0_dist)
   
   # Data must be restructured in the following ways, so the expected value
   # of the cdfs can be computed

### 2024-01-28 code/plots.R

@@ -12,3 +12,5 @@ gamma <- df %>% filter(dist == 'gamma')
 plot_p_vals(gamma, 'gamma.pdf')
 
 
+df <- readRDS("../data/rejection_rates.RDS") %>% filter(alpha == 0.05)
+plot_rr(df, 'rr.pdf')

### 2024-01-28 code/precipitation.R

@@ -13,6 +13,15 @@ mdw <- precipitation %>%
   summarize(annual_max_hpcp = max(hpcp)) %>% 
   ungroup()
 
+acf(mdw$annual_max_hpcp)
+pacf(mdw$annual_max_hpcp)
+arima0(mdw$annual_max_hpcp, order = c(1, 0, 1))
+# Coefficients:
+#   ar1     ma1  intercept
+# -0.7886  0.6723     1.3957
+# s.e.   0.0966  0.5436     0.0635
+#
+# sigma^2 estimated as 0.3086:  log likelihood = -55.71,  aic = 119.41
 set.seed(123)
 mdw_pvals <- myapp(mdw$annual_max_hpcp, 10000, 'gev', evd::pgev, df = NULL)
 
@@ -23,6 +32,15 @@ lga <- precipitation %>%
   summarize(annual_max_hpcp = max(hpcp)) %>% 
   ungroup()
 
+acf(lga$annual_max_hpcp)
+pacf(lga$annual_max_hpcp)
+arima0(lga$annual_max_hpcp, order = c(1, 0, 1))
+# Coefficients:
+#   ar1     ma1  intercept
+# -0.4624  0.3793     1.1507
+# s.e.   0.1123  0.6820     0.0473
+#
+# sigma^2 estimated as 0.1656:  log likelihood = -34.32,  aic = 76.64
 set.seed(123)
 lga_pvals <- myapp(lga$annual_max_hpcp, 10000, 'gev', evd::pgev)
 
@@ -33,6 +51,15 @@ lax <- precipitation %>%
   summarize(annual_max_hpcp = max(hpcp)) %>% 
   ungroup()
 
+acf(lax$annual_max_hpcp)
+pacf(lax$annual_max_hpcp)
+arima0(lax$annual_max_hpcp, order = c(1, 0, 1))
+# Coefficients:
+#   ar1     ma1  intercept
+# -0.8726  0.8123     0.5946
+# s.e.   0.0824  0.8140     0.0311
+#
+# sigma^2 estimated as 0.06766:  log likelihood = -4.78,  aic = 17.56
 set.seed(123)
 lax_pvals <- myapp(lax$annual_max_hpcp, 10000, 'gev', evd::pgev)
 

### 2024-01-28 code/tables.R

@@ -56,29 +56,3 @@ write(print(xtable(df_800,
                    label = "table:rr_800"), caption.placement = "top"), 
       file = "../manuscript/tables/rr_800.tex")
 
-df_1600 <- df %>% 
-  filter(n == 1600) %>% 
-  select(-R) %>% 
-  rename(distribution = dist, `lower bound` = rr_lb, `rejection rate` = rr, 
-         `upper bound` = rr_ub)
-write(print(xtable(df_1600,
-                   caption = "Rejection rates for test when n = 1600 for 
-                   different values of AR(1) coefficient and for different 
-                   significance levels. Lower and upper bounds are also 
-                   included.",
-                   label = "table:rr_1600"), caption.placement = "top"), 
-      file = "../manuscript/tables/rr_1600.tex")
-
-df_3200 <- df %>% 
-  filter(n == 3200) %>% 
-  select(-R) %>% 
-  rename(distribution = dist, `lower bound` = rr_lb, `rejection rate` = rr, 
-         `upper bound` = rr_ub)
-write(print(xtable(df_3200,
-                   caption = "Rejection rates for test when n = 3200 for 
-                   different values of AR(1) coefficient and for different 
-                   significance levels. Lower and upper bounds are also 
-                   included.",
-                   label = "table:rr_3200"), caption.placement = "top"), 
-      file = "../manuscript/tables/rr_3200.tex")
-

### 2024-01-29 manuscript/manuscript.tex
fixed summary
did some bib cleaning

@@
 \item
-  Draw a random sample $X^{(b)}_1,...,X^{(b)}_n$ from the empirical
-  distribution~$F_n$.
+  Generate $X^{(b)}_1,...,X^{(b)}_n$ by applying moving block bootstrap 
+  on the original sample as
+  defined previously.
 \item
@@
  $n \in \{100, 200, 400, 800\}$ and marginal distribution 
- $\in \{N(8,8), \gamma(8,1)\}$.}
+ $\in \{N(8,8), \Gamma(8,1)\}$.}
   \label{fig:rr}
@@
 consistently above 90\%. We can also
-observe that the rejection rate is slightly higher for the $\gamma(8, 1)$ sample 
+observe that the rejection rate is slightly higher for the $\Gamma(8, 1)$ sample 
 than for 

### 2024-01-29 code/functions.R

@@ -115,13 +115,22 @@ plot_p_vals <- function(df, filename) {
                       df$phi == 0.7071068 ~ 0.5,
                       df$phi == 0.3826834 ~ 0.25)
   
+  df$dist <- factor(case_when(df$dist == "normal" ~ "N(8,8)",
+                              df$dist == "gamma" ~ "Gamma(8,1)"))
+  
+  df$n <- factor(case_when(df$n == 100 ~ "n = 100",
+                           df$n == 200 ~ "n = 200",
+                           df$n == 400 ~ "n = 400",
+                           df$n == 800 ~ "n = 800"))
+  
   gg.f <- ggplot(data = df, mapping = aes(sample = pval)) +
     scale_x_continuous(breaks=c(0, 1)) +
     scale_y_continuous(breaks=c(0, 1)) + 
     stat_pp_band(distribution = "unif") +
     stat_pp_line() +
     stat_pp_point(distribution = "unif", cex = .1) +
-    facet_grid(vars(as.numeric(n)), vars(as.numeric(tau))) +
+    facet_grid(vars(n), vars(as.numeric(tau)),
+               labeller = label_parsed) +
     labs(x = "Probability Points", y = "Cumulative Probability") +
     coord_fixed() +
     theme(strip.text.x = element_text(size = 8))
@@ -134,7 +143,8 @@ plot_p_vals <- function(df, filename) {
     stat_pp_band(distribution = "unif") +
     stat_pp_line() +
     stat_pp_point(distribution = "unif", cex = .1) +
-    facet_grid(vars(as.numeric(n)), vars(as.numeric(tau))) +
+    facet_grid(vars(n), vars(as.numeric(tau)), 
+               labeller = label_parsed) +
     labs(x = "Probability Points", y = "Cumulative Probability") +
     coord_fixed(ylim = c(0, 0.1), xlim = c(0, 0.1)) +
     theme(strip.text.x = element_text(size = 8))
@@ -143,6 +153,15 @@ plot_p_vals <- function(df, filename) {
 }
 
 plot_rr <- function(df, filename) {
+  
+  df$dist <- factor(case_when(df$dist == "normal" ~ "N(8,8)",
+                       df$dist == "gamma" ~ "Gamma(8,1)"))
+  
+  df$n <- factor(case_when(df$n == 100 ~ "n = 100",
+                           df$n == 200 ~ "n = 200",
+                           df$n == 400 ~ "n = 400",
[…]

### 2024-01-30 manuscript/manuscript.tex
replaced phi with tau still need to specify how kendall's tau is computed

@@
 \jy{why choose these two distributions?}\mc{addressed}
-$\Gamma(8, 1)$, lag-1 autocorrelation $\phi \in \{-.4, -.2, 0, .2, .4\}$, and
-sample size $n \in \{100, 200, 400, 800, 1600, 3200\}$. These distributions
+$\Gamma(8, 1)$, Kendall's $\tau \in \{-.75, -.5, -.25, 0, .25, .5, 
+.75\}$, and
+sample size $n \in \{100, 200, 400, 800}$. These distributions
 were chosen to compare results on normal and non-normal
@@
 we used $B = 1000$ and $l = \lceil n^{1/3} \rceil$.
-For each setting for $F$, $\phi$, and $n$, we replicate the method 1000 times 
+For each setting for $F$, $\tau$, and $n$, we replicate the method 1000 times 
 to get the distribution of the p-values 
@@
 marginal distributions $N(8, 8)$ and 
-$\Gamma(8, 1)$, lag-1 autocorrelation $\phi \in \{-.4, -.2, 0, .2, .4\}$, and
-sample size $n \in \{200, 400, 800\}$. However, 
+$\Gamma(8, 1)$, Kendall's $\tau \in \{-.75, -.5, -.25, 0, .25, .5, 
+.75\}$, and
+sample size $n \in \{100, 200, 400, 800\}$. However, 
 to evaluate the test's power, when $X_t \sim N(8, 8)$, we tested that the 
@@
 we used $B = 1000$ and $l = \lceil n^{1/3} \rceil$.
-For each setting for $F$, $\phi$, and $n$, we replicate the method $1000$ times 
+For each setting for $F$, $\tau$, and $n$, we replicate the method $1000$ times 
 to obtain a p-value $p_r$ for each $r \in \{1, \ldots, 1000\}$.

### 2024-01-30 code/microsoft.R

@@ -10,6 +10,10 @@ microsoft_5y <-
   diff(log(get.hist.quote(instrument = "msft", start = "2018-01-01",
                           end = "2022-12-31")))
 
+acf(as.vector(microsoft_5y[, "Close"]))
+pacf(as.vector(microsoft_5y[, "Close"]))
+arima0(as.vector(microsoft_5y[, "Close"]), order = c(1, 0, 1))
+
 set.seed(123)
 mc_norm_pval_5y <- myapp(as.vector(microsoft_5y[, "Close"]), 1000, "normal", 
                          pnorm)
@@ -52,6 +56,10 @@ microsoft_4y <-
   diff(log(get.hist.quote(instrument = "msft", start = "2019-01-01",
                           end = "2022-12-31")))
 
+acf(as.vector(microsoft_4y[, "Close"]))
+pacf(as.vector(microsoft_4y[, "Close"]))
+arima0(as.vector(microsoft_4y[, "Close"]), order = c(1, 0, 1))
+
 set.seed(123)
 mc_norm_pval_4y <- myapp(as.vector(microsoft_4y[, "Close"]), 1000, "normal", 
                          pnorm)
@@ -92,6 +100,10 @@ mc_t2.15_pval_4y <- myapp(as.vector(microsoft_4y[, "Close"]), 1000, "t", plst,
 microsoft_3y <- 
   diff(log(get.hist.quote(instrument = "msft", start = "2020-01-01",
                           end = "2022-12-31")))
+
+acf(as.vector(microsoft_3y[, "Close"]))
+pacf(as.vector(microsoft_3y[, "Close"]))
+arima0(as.vector(microsoft_3y[, "Close"]), order = c(1, 0, 1))
 
 set.seed(123)
 mc_norm_pval_3y <- myapp(as.vector(microsoft_3y[, "Close"]), 1000, "normal", 
@@ -175,6 +187,10 @@ mc_t2.15_pval_2y <- myapp(as.vector(microsoft_2y[, "Close"]), 1000, "t", plst,
 microsoft_1y <- 
   diff(log(get.hist.quote(instrument = "msft", start = "2022-01-01",
                           end = "2022-12-31")))
+
+acf(as.vector(microsoft_1y[, "Close"]))
+pacf(as.vector(microsoft_1y[, "Close"]))
+arima0(as.vector(microsoft_1y[, "Close"]), order = c(1, 0, 1))
 
 set.seed(123)
[…]

### 2024-02-03 manuscript/manuscript.tex
1/30 Notes

@@
 .75\}$, and
-sample size $n \in \{100, 200, 400, 800}$. These distributions
+sample size $n \in \{100, 200, 400, 800\}$. These distributions
 were chosen to compare results on normal and non-normal

### 2024-02-03 code/microsoft.R

@@ -12,7 +12,8 @@ microsoft_5y <-
 
 acf(as.vector(microsoft_5y[, "Close"]))
 pacf(as.vector(microsoft_5y[, "Close"]))
-arima0(as.vector(microsoft_5y[, "Close"]), order = c(1, 0, 1))
+fit <- arima0(as.vector(microsoft_5y[, "Close"]), order = c(1, 0, 1))
+mc_resid <- residuals(fit)
 
 set.seed(123)
 mc_norm_pval_5y <- myapp(as.vector(microsoft_5y[, "Close"]), 1000, "normal", 

### 2024-02-05 manuscript/manuscript.tex
wrote a little about phi and distributions

@@
 \jy{Whrere is the 'block' part?}
+\mc{addressed}
 \begin{enumerate}
@@
 .75\}$, and
-sample size $n \in \{100, 200, 400, 800\}$. These distributions
+sample size $n \in \{100, 200, 400, 800\}$. Kendall's $\tau$ was chosen as
+it ...
+The autocorrelation $\phi$ of the series was set to \{-0.9238795, -0.7071068, 
+-0.3826834, 0, 0.3826834, 0.7071068, 0.9238795\}.
+\mc{my explanation needs work}
+
+These distributions
 were chosen to compare results on normal and non-normal
-error structures, and the parameters were chosen so that the distributions
-have the same mean 8 and variance 8. To generate 
+error structures. The specific parameters were chosen because the distributions 
+are very similar and their
+first two moments are the same.  To generate...
 For the purposes of 

### 2024-02-05 manuscript/manuscript.tex
precipitation tables

@@
 
-\input{tables/precipitation_pvals}
+%\input{tables/precipitation_pvals}
 %\mc{https://hdsc.nws.noaa.gov/pfds/pfds_map_cont.html?bkmrk=ct}
 
-As displayed in Table~\ref{table:precipitation}, using a significance level as 
+The p-value is 0.71 for MDW, 0.13 for LGA, and 0.36 for LAX. Using a 
+significance level as 
 high as .10 still results in a failed rejection

### 2024-02-05 code/microsoft.R

@@ -10,10 +10,9 @@ microsoft_5y <-
   diff(log(get.hist.quote(instrument = "msft", start = "2018-01-01",
                           end = "2022-12-31")))
 
-acf(as.vector(microsoft_5y[, "Close"]))
-pacf(as.vector(microsoft_5y[, "Close"]))
-fit <- arima0(as.vector(microsoft_5y[, "Close"]), order = c(1, 0, 1))
-mc_resid <- residuals(fit)
+mc5_fit <- auto.arima(as.vector(microsoft_5y[, "Close"]))
+mc5_resid <- residuals(fit)
+plot(mc5_resid)
 
 set.seed(123)
 mc_norm_pval_5y <- myapp(as.vector(microsoft_5y[, "Close"]), 1000, "normal", 
@@ -32,34 +31,33 @@ mc_t10_pval_5y <- myapp(as.vector(microsoft_5y[, "Close"]), 1000, "t", plst,
                      df = 10)
 
 set.seed(123)
+mc_t7_pval_5y <- myapp(as.vector(microsoft_5y[, "Close"]), 1000, "t", plst, 
+                       df = 7)
+
+set.seed(123)
 mc_t5_pval_5y <- myapp(as.vector(microsoft_5y[, "Close"]), 1000, "t", plst, 
                     df = 5)
+
+set.seed(123)
+mc_t4_pval_5y <- myapp(as.vector(microsoft_5y[, "Close"]), 1000, "t", plst, 
+                       df = 4)
+
+set.seed(123)
+mc_t3_pval_5y <- myapp(as.vector(microsoft_5y[, "Close"]), 1000, "t", plst, 
+                       df = 3)
 
 set.seed(123)
 mc_t2_pval_5y <- myapp(as.vector(microsoft_5y[, "Close"]), 1000, "t", plst, 
                     df = 2)
 
-set.seed(123)
-mc_t2.5_pval_5y <- myapp(as.vector(microsoft_5y[, "Close"]), 1000, "t", plst, 
-                      df = 2.5)
-
-set.seed(123)
-mc_t2.2_pval_5y <- myapp(as.vector(microsoft_5y[, "Close"]), 1000, "t", plst, 
-                      df = 2.2)
-
-set.seed(123)
-mc_t2.15_pval_5y <- myapp(as.vector(microsoft_5y[, "Close"]), 1000, "t", plst, 
-                       df = 2.15)
[…]

### 2024-02-05 code/precipitation.R

@@ -13,15 +13,7 @@ mdw <- precipitation %>%
   summarize(annual_max_hpcp = max(hpcp)) %>% 
   ungroup()
 
-acf(mdw$annual_max_hpcp)
-pacf(mdw$annual_max_hpcp)
-arima0(mdw$annual_max_hpcp, order = c(1, 0, 1))
-# Coefficients:
-#   ar1     ma1  intercept
-# -0.7886  0.6723     1.3957
-# s.e.   0.0966  0.5436     0.0635
-#
-# sigma^2 estimated as 0.3086:  log likelihood = -55.71,  aic = 119.41
+auto.arima(mdw$annual_max_hpcp)
 set.seed(123)
 mdw_pvals <- myapp(mdw$annual_max_hpcp, 10000, 'gev', evd::pgev, df = NULL)
 
@@ -32,15 +24,7 @@ lga <- precipitation %>%
   summarize(annual_max_hpcp = max(hpcp)) %>% 
   ungroup()
 
-acf(lga$annual_max_hpcp)
-pacf(lga$annual_max_hpcp)
-arima0(lga$annual_max_hpcp, order = c(1, 0, 1))
-# Coefficients:
-#   ar1     ma1  intercept
-# -0.4624  0.3793     1.1507
-# s.e.   0.1123  0.6820     0.0473
-#
-# sigma^2 estimated as 0.1656:  log likelihood = -34.32,  aic = 76.64
+auto.arima(lga$annual_max_hpcp)
 set.seed(123)
 lga_pvals <- myapp(lga$annual_max_hpcp, 10000, 'gev', evd::pgev)
 
@@ -51,15 +35,7 @@ lax <- precipitation %>%
   summarize(annual_max_hpcp = max(hpcp)) %>% 
   ungroup()
 
-acf(lax$annual_max_hpcp)
-pacf(lax$annual_max_hpcp)
-arima0(lax$annual_max_hpcp, order = c(1, 0, 1))
-# Coefficients:
-#   ar1     ma1  intercept
-# -0.8726  0.8123     0.5946
-# s.e.   0.0824  0.8140     0.0311
-#
-# sigma^2 estimated as 0.06766:  log likelihood = -4.78,  aic = 17.56
+auto.arima(lga$annual_max_hpcp)
 set.seed(123)
 lax_pvals <- myapp(lax$annual_max_hpcp, 10000, 'gev', evd::pgev)
 

### 2024-02-11 code/alt_functions.R
new microsoft data

@@ -1,0 +1,104 @@
+library(tidyverse)
+library(evd)
+library(truncdist)
+library(qqplotr)
+library(copula)
+mystat <- function(x, dist, df = NULL) {
+  # Bootstrap will return actual pseudo-sample, mean, and standard deviation
+  if (dist == 'gev') {
+    c(c(x), 
+      evd::fgev(x, std.err = FALSE)$estimate)
+  } else {
+    c(c(x),  
+      MASS::fitdistr(x, dist, df = df)$estimate)
+  }
+}
+
+my_babu <- function(y, B, h0_dist, f0, df = NULL) {
+  n <- length(y)
+  blksize <- 1
+  emp <- ecdf(y)(sort(y)) # observed empirical distribution
+  if (h0_dist == 'gev') {
+    fit_theta <- evd::fgev(y, std.err = FALSE)$estimate # gev not recognised by fitdistr
+  } else {
+    fit_theta <- MASS::fitdistr(y, h0_dist, df = df)$estimate # observed fitted values
+  }
+  
+  fit <- do.call(f0, c(list(sort(y)), as.list(c(df, fit_theta)))) # observed fitted distribution
+  obsv_ks <- sqrt(n) * max(abs(emp - fit)) # observed ks statistic
+  
+  # Basic Bootstrap
+  bts <- boot::tsboot(y, mystat, l = blksize, sim = "fixed", R = B, 
+                      dist = h0_dist, df = df)
+  
+  # Data must be restructured in the following ways, so the expected value
+  # of the cdfs can be computed
+  list_emp <- matrix(, nrow = 0, ncol = n) 
+  list_theta <- matrix(, nrow = 0, ncol = length(fit_theta)) 
+  
+  sum_theta <- 0
+  
+  for (i in 1:B) {
+    list_emp <- rbind(list_emp, c(ecdf(bts$t[i, (1:n)])(sort(y))))
+    list_theta <- rbind(list_theta, c(bts$t[i, -(1:n)]))
+  }
+  
+  bias_term <- emp - fit # bias term
+  
+  ks_values <- c()
+  for (i in 1:B) {
+    boot_emp <- list_emp[i,] # bootstrap empirical distribution
+    boot_theta <- list_theta[i, ] # bootstrap fitted values
+    boot_fit <- do.call(f0, c(list(sort(y)), as.list(c(df, boot_theta)))) # distribution with bootstrap fitted values
[…]

### 2024-02-11 code/functions.R

@@ -133,8 +133,7 @@ plot_p_vals <- function(df, filename) {
                labeller = label_parsed) +
     labs(x = "Probability Points", y = "Cumulative Probability") +
     coord_fixed() +
-    theme(strip.text.x = element_text(size = 8),
-          axis.text.x = element_text(angle = -45))
+    theme(strip.text.x = element_text(size = 8))
   ggsave(filename = filename, plot = gg.f, path = "../manuscript/figures", 
          height = 6, width = 6)
   
@@ -147,9 +146,8 @@ plot_p_vals <- function(df, filename) {
     facet_grid(vars(n), vars(as.numeric(tau)), 
                labeller = label_parsed) +
     labs(x = "Probability Points", y = "Cumulative Probability") +
-    coord_fixed(ylim = c(0, 0.1), xlim = c(0, 0.1)) +
-    theme(strip.text.x = element_text(size = 8),
-          axis.text.x = element_text(angle = -45))
+    coord_fixed(ylim = c(-0.01, 0.11), xlim = c(-0.01, 0.11)) +
+    theme(strip.text.x = element_text(size = 8))
   ggsave(filename = paste('zoom_', filename, sep = ''), plot = gg.f, 
          path = "../manuscript/figures", height = 6, width = 6)
 }
@@ -178,9 +176,10 @@ plot_rr <- function(df, filename) {
     geom_line() +
     geom_point() +
     facet_grid(cols = vars(dist), labeller = label_parsed) +
-    theme(axis.text.x = element_text(angle = -45),
+    theme(
           legend.position = "bottom") +
-    labs(x = latex2exp::TeX("$\\tau$"), y = latex2exp::TeX("Rejection Rate"))
+    labs(x = latex2exp::TeX("$\\tau$"), y = latex2exp::TeX("Rejection Rate")) +
+    coord_fixed(ylim = c(0, 1), xlim = c(-1, 1))
   ggsave(filename = filename, plot = gg.f, path = "../manuscript/figures", 
          height = 4, width = 6)
     

### 2024-02-11 code/microsoft.R

@@ -1,99 +1,61 @@
 source("functions.R")
+source("alt_functions.R")
+library(forecast)
 library(tseries)
 library(extraDistr)
 library(xtable)
-microsoft <- 
-  diff(log(get.hist.quote(instrument = "msft", start = "1998-01-01", 
-                          end = "2022-12-31")))
-
 microsoft_5y <- 
   diff(log(get.hist.quote(instrument = "msft", start = "2018-01-01",
                           end = "2022-12-31")))
 
 mc5_fit <- auto.arima(as.vector(microsoft_5y[, "Close"]))
-mc5_resid <- residuals(fit)
-plot(mc5_resid)
+mc5_resid <- residuals(mc5_fit)
 
 set.seed(123)
-mc_norm_pval_5y <- myapp(as.vector(microsoft_5y[, "Close"]), 1000, "normal", 
-                         pnorm)
+mc_pval_5y <- c(myapp(mc5_resid, 1000, "normal", 
+                         pnorm),
+                     my_babu(mc5_resid, 1000, "normal", 
+                         pnorm))
 
-set.seed(123)
-mc_t30_pval_5y <- myapp(as.vector(microsoft_5y[, "Close"]), 1000, "t", plst, 
-                     df = 30)
+for (v in c(30, 20, 10, 5, 4, 3, 2, 1)) {
+  mc_pval_5y <- rbind(mc_pval_5y,
+                        c(myapp(as.vector(microsoft_5y[, "Close"]), 1000, "t", plst, 
+                                df = v),
+                          my_babu(mc5_resid, 1000, "normal", 
+                                  pnorm)))
+}
 
-set.seed(123)
-mc_t20_pval_5y <- myapp(as.vector(microsoft_5y[, "Close"]), 1000, "t", plst, 
-                     df = 20)
-
-set.seed(123)
-mc_t10_pval_5y <- myapp(as.vector(microsoft_5y[, "Close"]), 1000, "t", plst, 
-                     df = 10)
-
-set.seed(123)
-mc_t7_pval_5y <- myapp(as.vector(microsoft_5y[, "Close"]), 1000, "t", plst, 
-                       df = 7)
-
-set.seed(123)
-mc_t5_pval_5y <- myapp(as.vector(microsoft_5y[, "Close"]), 1000, "t", plst, 
-                    df = 5)
-
[…]

### 2024-02-12 manuscript/manuscript.tex
new microsoft data
addressed few problems in manuscript

@@
 In summary, the procedure of the nonparametric block bootstrap test is 
-summarized as follows.
+summarized as follows. Repeat the following steps for $b \in \{1, ..., B\}$.
 \jy{Whrere is the 'block' part?}
@@
   bias term.
-\item
-  Repeat the previous steps a large number $B$ times and use the empirical
-  distribution of $T^{(b)}_n$ to approximate the null distribution of the observed
-  statistic. 
 \end{enumerate}
@@
 it ...
-The autocorrelation $\phi$ of the series was set to \{-0.9238795, -0.7071068, 
--0.3826834, 0, 0.3826834, 0.7071068, 0.9238795\}.
+The autocorrelation $\phi$ of the series was set to \{-0.924, -0.707, 
+-0.383, 0, 0.383, 0.707, 0.924\}. These
+are the autocorrelations of the normal series, but after the transformation
+to the marginal gamma distribution
 \mc{my explanation needs work}

### 2024-02-13 manuscript/manuscript.tex
parametric bootstrap need to test

@@
 Let $X_1, ..., X_n$ be a random sample of size~$n$ from some continuous
-distribution. The null hypothesis $H_0$ is that $X_i$'s follow the
+distribution and the null hypothesis $H_0$ be that $X_i$'s follow the
 hypothesized distribution~$F$.
-Let $F_n(t) = \sum_{i=1}^n I(X_i \le t) / n$ be the empirical cumulative
+If we let $F_n(t) = \sum_{i=1}^n I(X_i \le t) / n$ be the empirical cumulative
 distribution function of the sample, where $I(\cdot)$ is the indicator
-function. The KS test statistic takes the form
+function, the KS test statistic takes the form
 \begin{equation}
@@
 
-The statistic 
+The KS statistic 
 can be used to see if a population follows a hypothesized distribution and has 
@@
 
-A complete remedy for KS tests with serially dependent data is
+A non-parametric remedy for KS tests with serially dependent data is
 a challenging task. The null distribution depends on the structure of the serial

### 2024-02-13 code/alt_functions.R

@@ -3,6 +3,7 @@ library(evd)
 library(truncdist)
 library(qqplotr)
 library(copula)
+library(tseries)
 mystat <- function(x, dist, df = NULL) {
   # Bootstrap will return actual pseudo-sample, mean, and standard deviation
   if (dist == 'gev') {
@@ -55,7 +56,7 @@ my_babu <- function(y, B, h0_dist, f0, df = NULL) {
   c(mean(ks_values > obsv_ks)) # Which are greater than the observed ks statistic
 }
 
-my_param_app <- function(y, B, h0_dist, f0, rgen = NULL, df = NULL) {
+my_param <- function(y, B, h0_dist, f0, rgen, df = NULL) {
   n <- length(y)
   blksize <- 1
   emp <- ecdf(y)(sort(y)) # observed empirical distribution
@@ -68,15 +69,15 @@ my_param_app <- function(y, B, h0_dist, f0, rgen = NULL, df = NULL) {
   fit <- do.call(f0, c(list(sort(y)), as.list(c(df, fit_theta)))) # observed fitted distribution
   obsv_ks <- sqrt(n) * max(abs(emp - fit)) # observed ks statistic
   
-  # Parametric Bootstrap
-  bts <- NA
-  if (h0_dist == 'gev') {
-    bts <- replicate(B, c(evd::rgev(length(y)), 
-                          evd::fgev(y, std.err = FALSE)$estimate)) # gev not recognised by fitdistr
-  } else {
-    bts <- replicate(B, c(rgen(length(y)),
-                     MASS::fitdistr(y, dist, df = df)$estimate)) # observed fitted values
+  bts <- t(replicate(B, c(
+    do.call(rgen, c(n, as.list(c(df, fit_theta)))))))
+  
+  theta <- c()
+  for(row in 1:nrow(bts)) {
+    theta <- rbind(theta, MASS::fitdistr(bts[row,], h0_dist, df = df)$estimate)
   }
+ 
+  bts <- cbind(bts, theta)
   
   # Data must be restructured in the following ways, so the expected value
   # of the cdfs can be computed
@@ -86,8 +87,8 @@ my_param_app <- function(y, B, h0_dist, f0, rgen = NULL, df = NULL) {
   sum_theta <- 0
   
   for (i in 1:B) {
-    list_emp <- rbind(list_emp, c(ecdf(bts$t[i, (1:n)])(sort(y))))
-    list_theta <- rbind(list_theta, c(bts$t[i, -(1:n)]))
[…]

### 2024-02-13 code/microsoft.R

@@ -4,140 +4,16 @@ library(forecast)
 library(tseries)
 library(extraDistr)
 library(xtable)
-microsoft_5y <- 
-  diff(log(get.hist.quote(instrument = "msft", start = "2018-01-01",
-                          end = "2022-12-31")))
 
-mc5_fit <- auto.arima(as.vector(microsoft_5y[, "Close"]))
-mc5_resid <- residuals(mc5_fit)
+mc_pval_5y <- microsoft_app("2018-01-01", "2022-12-31", 5)
 
-set.seed(123)
-mc_pval_5y <- c(myapp(mc5_resid, 1000, "normal", 
-                         pnorm),
-                     my_babu(mc5_resid, 1000, "normal", 
-                         pnorm))
+mc_pval_4y <- microsoft_app("2019-01-01", "2022-12-31", 4)
 
-for (v in c(30, 20, 10, 5, 4, 3, 2, 1)) {
-  mc_pval_5y <- rbind(mc_pval_5y,
-                        c(myapp(as.vector(microsoft_5y[, "Close"]), 1000, "t", plst, 
-                                df = v),
-                          my_babu(mc5_resid, 1000, "normal", 
-                                  pnorm)))
-}
+mc_pval_3y <- microsoft_app("2020-01-01", "2022-12-31", 3)
 
-mc_pval_5y <- cbind(rep(5, dim(mc_pval_5y)[1]), 
-                     c("norm", 30, 20, 10, 5, 4, 3, 2, 1), mc_pval_5y)
-colnames(mc_pval_5y) <- c("duration", "df", "block", "basic")
-rownames(mc_pval_5y) <- NULL
+mc_pval_2y <- microsoft_app("2021-01-01", "2022-12-31", 2)
 
-
-microsoft_4y <- 
-  diff(log(get.hist.quote(instrument = "msft", start = "2019-01-01",
-                          end = "2021-12-31")))
-
-mc4_fit <- auto.arima(as.vector(microsoft_4y[, "Close"]))
-mc4_resid <- residuals(mc4_fit)
-
-set.seed(123)
-mc_pval_4y <- c(myapp(mc4_resid, 1000, "normal", 
-                      pnorm),
-                my_babu(mc4_resid, 1000, "normal", 
-                        pnorm))
-
-for (v in c(30, 20, 10, 5, 4, 3, 2, 1)) {
-  mc_pval_4y <- rbind(mc_pval_4y,
[…]

### 2024-02-13 manuscript/manuscript.tex
new tables in manuscript

@@
 
-\input{tables/mc_pvals}
+\input{tables/mc_pval_1y}
+
+\input{tables/mc_pval_2y}
+
+\input{tables/mc_pval_3y}
+
+\input{tables/mc_pval_4y}
+
+\input{tables/mc_pval_5y}
 
@@
 The p-values of our test when applied to Microsoft stock return data using
-different settings are showcased in Table~\ref{table:microsoft}.
+different settings are showcased in 
+Tables~\ref{table:microsoft1}--\ref{table:microsoft2}.
 We observe that when the duration of time is large, our method rejects the null

### 2024-02-13 code/alt_functions.R

@@ -103,8 +103,8 @@ my_param <- function(y, B, h0_dist, f0, rgen, df = NULL) {
 
 microsoft_app <- function(start, end, years) {
   microsoft <- 
-    diff(log(get.hist.quote(instrument = "msft", start = "2018-01-01",
-                            end = "2022-12-31")))
+    diff(log(get.hist.quote(instrument = "msft", start = start,
+                            end = end)))
   
   mc_fit <- auto.arima(as.vector(microsoft[, "Close"]))
   mc_resid <- residuals(mc_fit)
@@ -135,7 +135,7 @@ microsoft_app <- function(start, end, years) {
                           param))
   }
   
-  mc_pval <- cbind(rep(years, dim(mc_pval_5y)[1]), 
+  mc_pval <- cbind(rep(years, dim(mc_pval)[1]), 
                       c("norm", 30, 20, 10, 5, 4, 3, 2, 1), mc_pval)
   colnames(mc_pval) <- c("duration", "df", "block", "basic", "param")
   rownames(mc_pval) <- NULL

### 2024-02-13 code/microsoft.R

@@ -15,14 +15,49 @@ mc_pval_2y <- microsoft_app("2021-01-01", "2022-12-31", 2)
 
 mc_pval_1y <- microsoft_app("2022-01-01", "2022-12-31", 1)
 
-microsoft_df <- rbind(mc_pval_1y, mc_pval_2y, mc_pval_3y, mc_pval_4y, 
+microsoft_df <- t(rbind(mc_pval_1y, mc_pval_2y, mc_pval_3y, mc_pval_4y, 
                       mc_pval_5y
-)
+))
 
 saveRDS(microsoft_df, "../data/microsoft_df")
-write(print(xtable(microsoft_df,
-  caption = "P-values for Microsoft stock return data using different durations
+
+
+write(print(xtable(mc_pval_1y,
+  caption = "P-values for 1 year of Microsoft stock return data using different 
+  methods
   and different degrees of freedom for Student's t distribution.",
-  label = "table:microsoft"
+  label = "table:microsoft1"
   ), caption.placement = "top"), 
-      file = "../manuscript/tables/mc_pvals.tex")
+      file = "../manuscript/tables/mc_pval_1y.tex")
+
+write(print(xtable(mc_pval_2y,
+                   caption = "P-values for 2 years of Microsoft stock return 
+                   data using different durations
+  and different degrees of freedom for Student's t distribution.",
+  label = "table:microsoft2"
+), caption.placement = "top"), 
+file = "../manuscript/tables/mc_pval_2y.tex")
+
+write(print(xtable(mc_pval_3y,
+                   caption = "P-values for 3 years of Microsoft stock return 
+                   data using different durations
+  and different degrees of freedom for Student's t distribution.",
+  label = "table:microsoft3"
+), caption.placement = "top"), 
+file = "../manuscript/tables/mc_pval_3y.tex")
+
+write(print(xtable(mc_pval_4y,
+                   caption = "P-values for 4 years of Microsoft stock return 
+                   data using different durations
+  and different degrees of freedom for Student's t distribution.",
+  label = "table:microsoft4"
+), caption.placement = "top"), 
+file = "../manuscript/tables/mc_pval_4y.tex")
+
+write(print(xtable(mc_pval_5y,
+                   caption = "P-values for 5 years of Microsoft stock return 
+                   data using different durations
+  and different degrees of freedom for Student's t distribution.",
+  label = "table:microsoft5"
+), caption.placement = "top"), 
+file = "../manuscript/tables/mc_pval_5y.tex")

### 2024-02-16 manuscript/manuscript.tex
sp500

@@
 The KS statistic 
-can be used to see if a population follows a hypothesized distribution and has 
-and can be applied to a variety of fields. It has
+can be used to see if a population follows a hypothesized distribution and can 
+be applied to a variety of fields. It has
 been used to analyze the random distribution of cosmic microwave background 
@@
 From Figures~\ref{fig:normal} and \ref{fig:gamma}, we can observe that 
-although the p-values do not appear to be 
+although the extent to which the p-values appear to be 
 completely aligned with the line
-in the Q-Q plots for smaller sample sizes like $n = 100$ or $200$, they match
-the lines very closely for $n = 1600$ and $3200$. More importantly, almost
-all of the p-values appear to be within the confidence bands when looking at the
-plots zoomed in to probabilities between 0 and 0.1 in 
-Figures~\ref{fig:zoom_normal} and \ref{fig:zoom_gamma}, and as stated 
-before, 
-researchers are unlikely to choose significance levels above 0.1.
+in the Q-Q plots is dependent on the sample size and the level of serial 
+dependence.
+A small sample size like $n = 100$ or $200$ seems adequate when Kendall's
+$\tau$ is lower than 0.25. For Kendall's $\tau \geq 0.5$, a sample larger than
+$n = 200$ seems necessary for the p-values to be normally distributed. For
+Kendall's $\tau \geq 0.75$, a sample larger than $n = 800$ appears to be 
+necessary, as the p-values are not aligned with the line in the Q-Q plots, even
+in Figures~\ref{fig:zoom_normal} and \ref{fig:zoom_gamma}. This
+is not necessarily a cause for concern, as (for normal margins)
+a Kendall's $\tau$ corresponds to
+a $\phi$ of 0.924, which is very high. Additionally, performance generally seems
+better for negative $\tau$ values versus positive $\tau$ values of the same
+strength.
 

### 2024-02-16 code/microsoft.R

@@ -5,15 +5,15 @@ library(tseries)
 library(extraDistr)
 library(xtable)
 
-mc_pval_5y <- microsoft_app("2018-01-01", "2022-12-31", 5)
+mc_pval_5y <- app_scheme("2018-01-01", "2022-12-31", 5, "msft")
 
-mc_pval_4y <- microsoft_app("2019-01-01", "2022-12-31", 4)
+mc_pval_4y <- app_scheme("2019-01-01", "2022-12-31", 4, "msft")
 
-mc_pval_3y <- microsoft_app("2020-01-01", "2022-12-31", 3)
+mc_pval_3y <- app_scheme("2020-01-01", "2022-12-31", 3, "msft")
 
-mc_pval_2y <- microsoft_app("2021-01-01", "2022-12-31", 2)
+mc_pval_2y <- app_scheme("2021-01-01", "2022-12-31", 2, "msft")
 
-mc_pval_1y <- microsoft_app("2022-01-01", "2022-12-31", 1)
+mc_pval_1y <- app_scheme("2022-01-01", "2022-12-31", 1, "msft")
 
 microsoft_df <- t(rbind(mc_pval_1y, mc_pval_2y, mc_pval_3y, mc_pval_4y, 
                       mc_pval_5y

### 2024-02-16 code/sp500.R

@@ -1,0 +1,24 @@
+source("functions.R")
+source("alt_functions.R")
+library(forecast)
+library(tseries)
+library(extraDistr)
+library(xtable)
+
+sp500_pval_5y <- app_scheme("2018-01-01", "2022-12-31", 5, "^gspc")
+
+sp500_pval_4y <- app_scheme("2019-01-01", "2022-12-31", 4, "^gspc")
+
+sp500_pval_3y <- app_scheme("2020-01-01", "2022-12-31", 3, "^gspc")
+
+sp500_pval_2y <- app_scheme("2021-01-01", "2022-12-31", 2, "^gspc")
+
+sp500_pval_1y <- app_scheme("2022-01-01", "2022-12-31", 1, "^gspc")
+
+sp500_df <- t(rbind(sp500_pval_1y, sp500_pval_2y, sp500_pval_3y, sp500_pval_4y, 
+                        sp500_pval_5y
+))
+
+saveRDS(sp500_df, "../data/sp500_df")
+
+

### 2024-02-17 manuscript/manuscript.tex
sp100

@@
 better for negative $\tau$ values versus positive $\tau$ values of the same
-strength.
+strength. Results are very similar for normal and gamma margins.
 
@@
 From 
-Table~\ref{fig:rr}, 
-the rejection rates are a little higher for $n = 200$, but they may still be 
-drop below 50\% is the $\alpha = 0.1$. Once $n$ reaches 400, we can observe 
-that the rejection rate
-is consistently above 50\%. For larger sample sizes, the rejection rate is 
-consistently above 90\%. We can also
-observe that the rejection rate is slightly higher for the $\Gamma(8, 1)$ sample 
-than for 
-the $N(8, 8)$. As the strength of the temporal dependence increases, the 
-rejection rate decreases, and the rejection
-rate appears to be slightly higher for negative temporal dependence versus 
-positive temporal dependence values of the same strength.
+Figure~\ref{fig:rr}, 
+the rejection rates appear to get lower as $\tau$ increases in a
+positive direction. Using a sample size $n \geq 800$ appears to be sufficient
+when $\tau$ is not too high, but for $\tau \geq 0.75$, all sample sizes 
+observed appeared to have less than desirable rejection rates. Results
+do not appear to be to different when comparing gamma and normal 
+margins, indicating that the method is robust to the marginal distribution.
 

### 2024-02-19 manuscript/manuscript.tex
small manuscript changes

@@
 1948 to 2014, the data for LGA is from 1948 to 2013, and the
-data for LAX is also from 1948 to 2013. We can apply our method to
+data for LAX is also from 1948 to 2013. We can apply our method (as well
+as the non-parametric bootstrap KS Test \citep{babu2004goodness} and
+the parametric bootstrap KS Test) to
 the precipitation time series from each of these locations to test if they
@@
 
-The p-value is 0.71 for MDW, 0.13 for LGA, and 0.36 for LAX. Using a 
-significance level as 
-high as .10 still results in a failed rejection
-of the null hypothesis for each of the three tests that the respective 
-time series follow the GEV distribution.
+The p-value is 0.71 for MDW, 0.13 for LGA, and 0.36 for LAX when using our 
+method.
+When using Babu's non-parametric method which does not account for serial
+dependence, the p-value is 0.74 for MDW, 0.19 for LGA, and 0.40 for LAX. 
+When using the parametric bootstrap KS test, the p-value is 0.64 for MDW,
+0.12 for LGA, and 0.35 for LAX. In this instance, the conclusions are the same 
+(the three series follow the GEV distribution), but because of the difference
+in p-values, it is possible for different conclusions to be found in another
+study.
 
@@
 also observed how the method performs using increasingly smaller durations of
-time. First, we tred the entire data set which has a duration of 25 years. Then,
-we used the last 5 years of data: January 1st, 2018 to December 31st, 2022.
-Finally, we tried the method only using the last year of data: January 1st, 2022
-to December 31st, 2022.
+time. ,
+we used the last 5 years of data: January 1st, 2018 to December 31st, 2022,
+4 years of data: January 1st, 2019 to December 31st, 2022,
+3 years of data: January 1st, 2020 to December 31st, 2022,
+2 years of data: January 1st, 2021 to December 31st, 2022,
+and 1 year of data: January 1st, 2022
+to December 31st, 2022. In addition, we compared it to results from 
+the Babu non-parametric and 
+the parametric bootstrap KS Test.
 
@@
 different settings are showcased in 
-Tables~\ref{table:microsoft1}--\ref{table:microsoft2}.
-We observe that when the duration of time is large, our method rejects the null
-hypothesis unless the degrees of freedom specified is very precise. When
-we use 25 years of data, the method
-only fails to reject the null hypothesis at $\alpha = .05$ when 
-the hypothesized $v = 2.2$, when 
-the precision
-is to the tenths place. For $\alpha = .10$, we only rail to reject the null 
-hypothesis when the hypothesized $v = 2.15$, when the precision is to the 
-hundredths place.
-When using only 5 years of data, the method reaches a p-value of 
-$0.05$ when the hypothesized $v = 2.5$, but the p-value is
-lower for $v = 2.2$ and $v = 2.15$.
-When we only use 1 year of data, the method fails to reject the null hypothesis
-even when the hypothesized distribution family is normal ($v \to \infty$). The
-p-value is maximized at 0.65 when we hypothesize that $v = 5$, but the p-value 
-is lower for smaller values of $v$ when using only 1 year of data.
+Tables~\ref{table:microsoft1}--\ref{table:microsoft2}. Although the p-values
+are indeed different between the three methods, the conclusions at a .05 
+significance 
+level are mostly the same. This motivated an additional application on SP500
+and SP100 data.
 

### 2024-02-19 code/precipitation.R

@@ -1,4 +1,5 @@
 source('functions.R')
+source('alt_functions.R')
 library(tidyverse)
 library(janitor)
 library(evd)
@@ -13,9 +14,13 @@ mdw <- precipitation %>%
   summarize(annual_max_hpcp = max(hpcp)) %>% 
   ungroup()
 
-acf(mdw$annual_max_hpcp)
-set.seed(123)
-mdw_pvals <- myapp(mdw$annual_max_hpcp, 10000, 'gev', evd::pgev, df = NULL)
+mdw_fit <- auto.arima(mdw$annual_max_hpcp)
+mdw_resid <- residuals(mdw_fit)
+
+mdw_pvals <- myapp(mdw_resid, 10000, 'gev', evd::pgev, df = NULL)
+mdw_pvals <- c(mdw_pvals, my_babu(mdw_resid, 10000, 'gev', evd::pgev, df = NULL))
+mdw_pvals <- c(mdw_pvals, my_param(mdw_resid, 10000, 'gev', evd::pgev, evd::rgev, 
+                                   df = NULL))
 
 
 lga <- precipitation %>% 
@@ -24,10 +29,13 @@ lga <- precipitation %>%
   summarize(annual_max_hpcp = max(hpcp)) %>% 
   ungroup()
 
-acf(lga$annual_max_hpcp)
-set.seed(123)
-lga_pvals <- myapp(lga$annual_max_hpcp, 10000, 'gev', evd::pgev)
+lga_fit <- auto.arima(lga$annual_max_hpcp)
+lga_resid <- residuals(lga_fit)
 
+lga_pvals <- myapp(lga_resid, 10000, 'gev', evd::pgev, df = NULL)
+lga_pvals <- c(lga_pvals, my_babu(lga_resid, 10000, 'gev', evd::pgev, df = NULL))
+lga_pvals <- c(lga_pvals, my_param(lga_resid, 10000, 'gev', evd::pgev, evd::rgev, 
+                                   df = NULL))
 
 lax <- precipitation %>% 
   filter(station == "COOP:045114", hpcp != 999.99) %>%
@@ -35,12 +43,22 @@ lax <- precipitation %>%
   summarize(annual_max_hpcp = max(hpcp)) %>% 
   ungroup()
 
-acf(lga$annual_max_hpcp)
-set.seed(123)
-lax_pvals <- myapp(lax$annual_max_hpcp, 10000, 'gev', evd::pgev)
[…]

### 2024-02-19 manuscript/manuscript.tex
small manuscript changes

@@
 .75\}$, and
-sample size $n \in \{100, 200, 400, 800\}$. Kendall's $\tau$ was chosen as
-it ...
+sample size $n \in \{100, 200, 400, 800\}$. Kendall's $\tau$ was chosen as a
+measure of serial dependence as it does not vary between two different 
+distributions.
 The autocorrelation $\phi$ of the series was set to \{-0.924, -0.707, 
@@
 are the autocorrelations of the normal series, but after the transformation
-to the marginal gamma distribution
+to the marginal gamma distribution, the autocorrelations are $\{-0.607, 
+diverges,
+-0.287, 0, 0.339, 0.668, 0.911\}$.
 \mc{my explanation needs work}
@@
 are very similar and their
-first two moments are the same.  To generate...
+first two moments are the same. The series were generated by marginally 
+transforming the
+marginal normal AR(1) series $X_t$ by
+\begin{equation*}
+W_t = F^{-1}[\Phi(X_t)],
+\end{equation*}
+where $F^{-1}(p)$ is the quantile function for the $\Gamma(8, 1)$.
 For the purposes of 

### 2024-02-19 code/copula.R

@@ -1,0 +1,32 @@
+## Need packages copula and pracma
+
+library(copula)
+library(pracma)
+
+mymvd <- copula::mvdc(normalCopula(0.4), margins = "exp", paramMargins = list(rate=1), marginsIdentical = TRUE)
+
+## numerical integration to get 
+EXY <- pracma::dblquad(function(x, y) x * y * copula::dMvdc(cbind(x, y), mymvd),
+                       0, 20, 0, 20)
+## approximate true rho
+rho <- (EXY - 1) / 1
+
+## empirical check
+z <- rMvdc(100000, mymvd)
+cor(z[,1], z[,2])
+
+
+
+rho2phi <- function(rho) {
+  mymvd <- copula::mvdc(copula::normalCopula(rho), margins = "gamma",
+                        paramMargins = list(rate=1, scale=1), marginsIdentical = TRUE)
+  EXY <- pracma::dblquad(function(x, y) x * y * copula::dMvdc(cbind(x, y), mymvd),
+                         0, 20, 0, 20)
+  phi <- (EXY - 1) / 1
+  phi
+}
+
+uniroot(function(x) rho2phi(x) - 0.707, interval = c(0, 0.9))
+
+uniroot(function(x) rho2phi(x) + 0.707, interval = c(-.56, 0))
+

### 2024-02-26 manuscript/manuscript.tex
temperature

@@
 
-\subsection{Precipitation in Mansfield Connecticut}
+\subsection{Precipitation at Airports}
 \label{sec:precipitation}
@@
 and Los Angeles International Airport (LAX) stations from the 
-National Oceanic and Atmospheric Administration. These stations were selected 
+National Oceanic and Atmospheric Administration (NOAA). These stations were selected 
 from places of importance in the three largest American cities. LGA and
@@
 When using the parametric bootstrap KS test, the p-value is 0.64 for MDW,
-0.12 for LGA, and 0.35 for LAX. In this instance, the conclusions are the same 
+0.12 for LGA, and 0.35 for LAX. In this instance, the conclusions are the
+same 
 (the three series follow the GEV distribution), but because of the difference
@@
 study.
+
+\subsection{Temperature in Central Park}
+\label{sec:temperature}
+
+Annual temperature maximums recorded in Central Park, New York, NY from
+1895 to 2023 were sourced from the NOAA. Again, we are interested in seeing
+if our method, which
+accounts for serial dependence and does not require parameter specification,
+performs differently than the non-parametric bootstrap KS Test 
+\citep{babu2004goodness} and the parametric bootstrap KS Test, neither of
+which account for serial dependence. We found that when using our method,
+the p-value for the test that the series follows the GEV distribution is 0.1420.
+When using Babu's method, the p-value is 0.0666, and when using the parametric
+method, the p-value is 0.0682. At the common significance level of .05,
+the conclusions would be the same regardless of the method used. However, it
+is clear that for this series, our method more decisively fails to reject the 
+null hypothesis at a significance level of .10.
 

### 2024-02-26 code/precipitation.R

@@ -10,45 +10,52 @@ precipitation <- read.csv("../data/precipitation.csv") %>%
 
 mdw <- precipitation %>% 
   filter(station == "COOP:111577", hpcp != 999.99) %>%
-  group_by(year = as.numeric(format(date, "%Y"))) %>% 
-  summarize(annual_max_hpcp = max(hpcp)) %>% 
-  ungroup()
+  group_by(day = as.numeric(format(date, "%Y%m%d"))) %>% 
+  summarize(dpcp = sum(hpcp)) %>% 
+  ungroup() %>% 
+  mutate(year = substr(day, start = 1, stop = 4)) %>% 
+  group_by(year) %>% 
+  summarize(annual_max_dpcp = max(dpcp))
+  
 
-mdw_fit <- auto.arima(mdw$annual_max_hpcp)
-mdw_resid <- residuals(mdw_fit)
+mdw_fit <- auto.arima(mdw$annual_max_dpcp)
 
-mdw_pvals <- myapp(mdw$annual_max_hpcp, 10000, 'gev', evd::pgev, df = NULL)
-mdw_pvals <- c(mdw_pvals, my_babu(mdw_resid, 10000, 'gev', evd::pgev, df = NULL))
-mdw_pvals <- c(mdw_pvals, my_param(mdw_resid, 10000, 'gev', evd::pgev, evd::rgev, 
+mdw_pvals <- myapp(mdw$annual_max_dpcp, 10000, 'gev', evd::pgev, df = NULL)
+mdw_pvals <- c(mdw_pvals, my_babu(mdw$annual_max_dpcp, 10000, 'gev', evd::pgev, df = NULL))
+mdw_pvals <- c(mdw_pvals, my_param(mdw$annual_max_dpcp, 10000, 'gev', evd::pgev, evd::rgev, 
                                    df = NULL))
 
 
 lga <- precipitation %>% 
   filter(station == "COOP:305811", hpcp != 999.99) %>%
-  group_by(year = as.numeric(format(date, "%Y"))) %>% 
-  summarize(annual_max_hpcp = max(hpcp)) %>% 
-  ungroup()
+  group_by(day = as.numeric(format(date, "%Y%m%d"))) %>% 
+  summarize(dpcp = sum(hpcp)) %>% 
+  ungroup() %>% 
+  mutate(year = substr(day, start = 1, stop = 4)) %>% 
+  group_by(year) %>% 
[…]

### 2024-02-26 code/temperature.R

@@ -1,0 +1,56 @@
+source('functions.R')
+source('alt_functions.R')
+library(tidyverse)
+library(janitor)
+library(evd)
+library(xtable)
+ny_temp <- read.csv("../data/ny_temp.csv") %>% 
+  clean_names()
+colnames(ny_temp) <- ny_temp[4,]
+ny_temp <- ny_temp[-(1:4),] %>% 
+  mutate(Value = as.numeric(Value)) %>% 
+  select(Value) 
+
+ny_temp <- as.vector(ny_temp)[[1]]
+
+
+ny_temp_fit <- auto.arima(ny_temp)
+
+ny_temp_pvals <- myapp(ny_temp, 10000, 'gev', evd::pgev, df = NULL)
+ny_temp_pvals <- c(ny_temp_pvals, my_babu(ny_temp, 10000, 'gev', evd::pgev, df = NULL))
+ny_temp_pvals <- c(ny_temp_pvals, my_param(ny_temp, 10000, 'gev', evd::pgev, evd::rgev, 
+                                   df = NULL))
+
+la_temp <- read.csv("../data/la_temp.csv") %>% 
+  clean_names()
+colnames(la_temp) <- la_temp[4,]
+la_temp <- la_temp[-(1:4),] %>% 
+  mutate(Value = as.numeric(Value)) %>% 
+  select(Value) 
+
+la_temp <- as.vector(la_temp)[[1]]
+
+
+la_temp_fit <- auto.arima(la_temp)
+
+la_temp_pvals <- myapp(la_temp, 10000, 'gev', evd::pgev, df = NULL)
+la_temp_pvals <- c(la_temp_pvals, my_babu(la_temp, 10000, 'gev', evd::pgev, df = NULL))
+la_temp_pvals <- c(la_temp_pvals, my_param(la_temp, 10000, 'gev', evd::pgev, evd::rgev, 
+                                           df = NULL))
+
+chi_temp <- read.csv("../data/chi_temp.csv") %>% 
+  clean_names()
+colnames(chi_temp) <- chi_temp[4,]
+chi_temp <- chi_temp[-(1:4),] %>% 
+  mutate(Value = as.numeric(Value)) %>% 
+  select(Value) 
+
+chi_temp <- as.vector(chi_temp)[[1]]
+
+
+chi_temp_fit <- auto.arima(chi_temp)
+
+chi_temp_pvals <- myapp(chi_temp, 10000, 'gev', evd::pgev, df = NULL)
[…]

### 2024-02-29 manuscript/manuscript.tex
removed addressed comments

@@
 
-Let us first consider the case where $X_i$'s are i.i.d. Denote by $F^{(b)}_n$ 
-the empirical distribution of the $b$th bootstrap sample and let
+Let us first consider the case where $X_i$'s are independent. Denote by
+$F^{(b)}_n$ the empirical distribution of the $b$th bootstrap sample and let
 $\hat\theta^{(b)}_n$ be the parameter estimate based on the $b$th bootstrap 
@@
 Using the bootstrap (asymptotic) theory, we can approximate the distribution of
-\jy{need references to back up}
 $\sqrt{n}(F_n(x) - F(x))$ and $\sqrt{n}(F(x; \hat\theta_n) - F(x))$
-by that of $\sqrt{n}(F^{(b)}_n(x) - F_n(x))$
-and
+by that of $\sqrt{n}(F^{(b)}_n(x) - F_n(x))$ and
 $\sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; \hat\theta_n))$, respectively.
@@
 then $T^{(b)}_n := \sup_x|Y^{(b)}_n(x)|$ is the bootstrap statistic that is 
-expected
-to approximate the distribution of $T_n$. We note that the term
+expected to approximate the distribution of $T_n$. We note that the term
 $\sqrt{n}(F_n(x) - F(x; \hat\theta_n))$ is exactly the bias term considered in 
@@
 summarized as follows. Repeat the following steps for $b \in \{1, ..., B\}$.
-\jy{Whrere is the 'block' part?}
-\mc{addressed}
 \begin{enumerate}
@@
 
-\jy{Give details on how the data were generated. Are these enough infomation for
-  people reproduce the results? I'd suggest that we use Kendall's tau to measure
-  the serial dependence. }
-
 We generated time series with marginal distributions $N(8, 8)$ and
-\jy{why choose these two distributions?}\mc{addressed}
-$\Gamma(8, 1)$, Kendall's $\tau \in \{-.75, -.5, -.25, 0, .25, .5, 
-.75\}$, and
+$\Gamma(8, 1)$, Kendall's
+\jy{Need to state how serial dependence were introduced, like you did in the
+  first paper: transforming a normal series.}
+$\tau \in \{-.75, -.5, -.25, 0, .25, .5, 75\}$, and
 sample size $n \in \{100, 200, 400, 800\}$. Kendall's $\tau$ was chosen as a
@@
 distributions.
-The autocorrelation $\phi$ of the series was set to \{-0.924, -0.707, 
--0.383, 0, 0.383, 0.707, 0.924\}. These
+The autocorrelation $\phi$ of the series was set to
+$\{-0.924, -0.707, -0.383, 0, 0.383, 0.707, 0.924\}$. These
 are the autocorrelations of the normal series, but after the transformation
 to the marginal gamma distribution, the autocorrelations are $\{-0.607, 
-diverges,
--0.287, 0, 0.339, 0.668, 0.911\}$.
+diverges, -0.287, 0, 0.339, 0.668, 0.911\}$.
 \mc{my explanation needs work}
@@
 %for this proportion.
-
-\jy{Reduce width of  the panel title section. Reduce the font size of the
-  labels. Generate the figures with the right size in mind. Use whole textwidth.}
 
@@
 
-\jy{Clean up the tables. Use percentage for power. Keep three effective
-  digits. Why are there so many decimal places? }
-\mc{reduced number of digits}
-
-\jy{The large number decimals in the old table: some numerical issues?}
-
-\jy{Only three sample sizes will be enough. Sample size 800 or higher give
-  power~1. Only report nominal size 0.05 would be ok. May consider presenting
-  the intervals in a figure.}
-\mc{only included three sample sizes and for alpha $=$ 0.05}
-
 \jy{Consider presenting this in a graph. Try explaining the pattern.
@@
 
-\jy{No need for such small a table. Could plot the histogram and fitted density.}
+\jy{Is the parametric method by Zeimberkakis?}
 
@@
 null hypothesis at a significance level of .10.
+
+\jy{Sorry I forgot to send you the data I promised. Remind in the future
+  please. }
 
@@
 
-\jy{Normal was not rejected for 1 year. How about 2 year, 3 year, 4 year?}
-\mc{tried these sample sizes, normal is rejected for all three might want to
-  try 1.5 years}
-
-\jy{I'm surprised that t does not fit well even for two years data.}
-
 \jy{Report the autocorrelation estimate of residual and residual squared in the

### 2024-03-03 manuscript/manuscript.tex
smoothed intro

@@
 \end{equation}
+As sample size $n\to \infty$, the distribution of $T_n$ converges to that of the
+absolute value of standard Brownian bridge, which is known as the Kolmogorov
+distribution \citep{stephens1974edf}. The distribution function can be
+accurately evaluated in modern statistical software
+\citep{marsaglia2003evaluating}. The KS test can be applied to a variety of
+fields. \jy{cite a few  references in various field to show its wide
+  applications.}
+ It has
+been used to analyze the random distribution of cosmic microwave background 
+radiation \citep{naess2012application}.
 
-The KS statistic 
-can be used to see if a population follows a hypothesized distribution and can 
-be applied to a variety of fields. It has
-been used to analyze the random distribution of cosmic microwave background 
-radiation \citep{naess2012application}. \citet{zeimbekakis2022misuses} reviews
-some of the common misuses of the one-sample KS test. One of the most common 
-misuses of the KS test is when
-the hypothesized distribution has unspecified parameters. 
-\citet{babu2004goodness} approaches this scenario using basic 
-non-parametric bootstrap. There is also the scenario where the data are serially
-dependent, which \citet{zeimbekakis2022misuses} partially remedies with 
-semi-parametric
-bootstrap. The last scenario \citet{zeimbekakis2022misuses} discusses is that
-where both the hypothesized 
-distribution has unspecified parameters and the data are 
-serially dependent. \citet{zeimbekakis2022misuses}'s remedy for
-this scenario also uses semi-parametric bootstrap.
+Despite its widespread use, the Kolmogorov-Smirnov (KS) test can be 
+misapplied when its foundational assumptions are overlooked. The KS test 
+assumes the data are independently and identically distributed (i.i.d.) and 
+that the hypothesized distribution is continuous and fully specified without 
+the need for parameter estimation. \citet{zeimbekakis2022misuses} examines 
+common misapplications of the one-sample KS test, notably the inappropriate
+use when the hypothesized distribution contains unspecified parameters.
+Another commonly encountered situation is when the data are serially
+dependent. \citet{babu2004goodness} addresses this issue through the
+application of basic non-parametric bootstrap methods. Alternatively, 
+\citet{zeimbekakis2022misuses} proposed a semi-parametric bootstrap
+where the serial dependence structure is modeled via a working serial copula.
+A particularly complex scenario arises when the distribution has unspecified
+parameters, and the data are serially dependent. For this,
+\citet{zeimbekakis2022misuses} also recommends a semi-parametric bootstrap
+approach, where the parameters of the hypothesized distribution and the serial
+dependence both need to be estimated and their uncertainty accounted for.
 
-A non-parametric remedy for KS tests with serially dependent data is
-a challenging task. The null distribution depends on the structure of the serial
-dependence, which can be arbitrary in practice. A parametric bootstrap procedure
-would demand a specification for a model for the dependence, whereas the primary 
-interest
-is to test the marginal distribution of the stationary series. A bias 
-correction
-for block bootstrap similar to what \citet{babu2004goodness} did for basic
-bootstrap had not yet been shown.  This study aims to resolve this gap by 
-demonstrating a bias 
-correction
-for non-parametric block bootstrap to use when the hypothesized distribution
-has unspecified parameters and the data are serially dependent.
+Developing a fully non-parametric solution for the Kolmogorov-Smirnov (KS) 
+tests in the presence of serially dependent data presents a significant 
+challenge. The null distribution's characteristics are intricately linked to 
+the structure of the serial dependence, which can vary widely in practical 
+situations. Employing a parametric bootstrap would necessitate defining a 
+specific model for this dependence, despite the primary focus being on 
+evaluating the marginal distribution of a stationary series. To date, a bias 
+correction method for block bootstrap, akin to the approach \citet{babu2004goodness} 
+applied to the basic bootstrap, has not been established. This study seeks 
+to bridge this gap by introducing a bias correction technique for the 
+non-parametric block bootstrap, tailored for use in scenarios where the 
+hypothesized distribution includes unspecified parameters and the data 
+exhibit serial dependence. Our approach reduces to that of
+\citet{babu2004goodness} when the data are independent.
 
-The rest of the paper is outlined as follows: Section~\ref{sec:methods} reviews
-block bootstrap procedure and demonstrates the basis for bias correction for
-the non-parametric block bootstrap KS test. In Section~\ref{sec:simu}, we first 
-assess whether the KS
-test holds its size; that is, does the test fail to reject the null hypothesis
-when it is true. In the second part of Section~\ref{sec:simu}, we 
-evaluate the 
-test's power; that is, does the test reject the null hypothesis when it is 
-false. We show practical applications of this method in Section~\ref{sec:real}.
-First, we apply the method to test if annual maximums of hourly precipitation
-in three U.S. airports follows the GEV distribution in 
-Subsection~\ref{sec:precipitation}.
-Then, we test if Microsoft stock return data follows the Normal or the Student's
-$t$ distribution in Subsection~\ref{sec:microsoft}.
-Finally, we end with 
-concluding remarks in Section~\ref{sec:conclusion}.
+The remainder of this paper is structured as follows: 
+Section~\ref{sec:methods} provides an overview of the block bootstrap 
+procedure and introduces the bias correction methodology for the 
+non-parametric block bootstrap KS test. Section~\ref{sec:simu} is divided 
+into two parts; initially, we evaluate the KS test's ability to maintain 
+its size, i.e., its consistency in not rejecting the null hypothesis when 
+it is indeed true. Subsequently, we examine the test's power, assessing 
+whether it can reject the null hypothesis when it is false. Practical 
+applications of our method are presented in Section~\ref{sec:real}, where 
+we first apply the approach to assess whether annual maximums of hourly 
+precipitation at three U.S. airports conform to the Generalized Extreme 
+Value (GEV) distribution in Subsection~\ref{sec:precipitation}. Following 
+this, we analyze if Microsoft stock return data adhere to either the Normal 
+or the Student's $t$ distribution in Subsection~\ref{sec:microsoft}. The 
+paper concludes with Section~\ref{sec:conclusion}, offering final thoughts 
+and remarks.
 
@@
 
+\jy{The number of references seems low. Need to cite more related works.}
+
 \jy{Quality control the bib source}
 
-\bibliographystyle{chicago}
+\bibliographystyle{asa}
 \bibliography{citations}

### 2024-03-04 manuscript/manuscript.tex
eas

--- 2024-02-26 manuscript/manuscript.tex
@@
 
+Annual temperature minimums were also recorded from Central Park, and the
+same method comparison was applied to this series. We found that our method
+yields a p-value of 0.0015, Babu's method yields a p-value of 0.2747, and
+the parametric method yields a p-value of 0.0002.
+
+\subsection{Temperature in Eastern Asia}
+\label{sec:temperature}
+
+Annual maximums of daily maximum (TXx) and minimum (TNx) temperatures, and annual 
+minimums of daily maximum (TXn) and minimum (TNn) temperatures were collected
+for 60 years from 44 locations in Eastern Asia.
+
 \subsection{Microsoft Stock Returns}
@@
 that the method is robust. We have also 
-demonstrated possible applications of this method to precipitation and 
-stock return data. This method can be used for any study where the goal is
+demonstrated possible applications of this method to climate and financial data.
+Although in many cases, the conclusions may not differ between our method
+and other bootstrap KS tests, the p-values are different enough where in a case
+where the temporal dependence in the data is more extreme, conclusions could
+be drastically different if a different method is used.
+This method can be used for any study where the goal is
 to see if a time series follows a hypothesized distribution and the parameters

### 2024-03-04 code/eas.R

@@ -1,0 +1,58 @@
+source('functions.R')
+source('alt_functions.R')
+library(tidyverse)
+library(janitor)
+library(evd)
+library(xtable)
+library(forecast)
+load(file = "../data/EAS.txx.RData")
+
+txx_df <- data.frame(matrix(NA, nrow = 2, ncol = 3))
+
+for (col in 1:ncol(EAS.txx)) {
+  series <- EAS.txx[, col]
+  pvals <- myapp(series, 10000, 'gev', evd::pgev, df = NULL)
+  pvals <- c(pvals, my_babu(series, 10000, 'gev', evd::pgev, df = NULL))
+  pvals <- c(pvals, my_param(series, 10000, 'gev', evd::pgev, evd::rgev, 
+                                             df = NULL))
+  txx_df <- rbind(txx_df, pvals)
+}
+
+load(file = "../data/EAS.txn.RData")
+
+txn_df <- data.frame(matrix(NA, nrow = 2, ncol = 3))
+
+for (col in 1:ncol(EAS.txn)) {
+  series <- -EAS.txn[, col]
+  pvals <- myapp(series, 10000, 'gev', evd::pgev, df = NULL)
+  pvals <- c(pvals, my_babu(series, 10000, 'gev', evd::pgev, df = NULL))
+  pvals <- c(pvals, my_param(series, 10000, 'gev', evd::pgev, evd::rgev, 
+                             df = NULL))
+  txn_df <- rbind(txn_df, pvals)
+}
+
+load(file = "../data/EAS.tnx.RData")
+
+tnx_df <- data.frame(matrix(NA, nrow = 2, ncol = 3))
+
+for (col in 1:ncol(EAS.tnx)) {
+  series <- EAS.tnx[, col]
+  pvals <- myapp(series, 10000, 'gev', evd::pgev, df = NULL)
+  pvals <- c(pvals, my_babu(series, 10000, 'gev', evd::pgev, df = NULL))
+  pvals <- c(pvals, my_param(series, 10000, 'gev', evd::pgev, evd::rgev, 
+                             df = NULL))
+  tnx_df <- rbind(tnx_df, pvals)
+}
+
+load(file = "../data/EAS.tnn.RData")
+
+tnn_df <- data.frame(matrix(NA, nrow = 2, ncol = 3))
+
+for (col in 1:ncol(EAS.tnn)) {
+  series <- -EAS.tnn[, col]
[…]

### 2024-03-04 manuscript/manuscript.tex
fixed merge conflict

--- 2024-03-03 manuscript/manuscript.tex
@@
 
+Annual temperature minimums were also recorded from Central Park, and the
+same method comparison was applied to this series. We found that our method
+yields a p-value of 0.0015, Babu's method yields a p-value of 0.2747, and
+the parametric method yields a p-value of 0.0002.
+
+\subsection{Temperature in Eastern Asia}
+\label{sec:asia}
+
+Annual maximums of daily maximum (TXx) and minimum (TNx) temperatures, and annual 
+minimums of daily maximum (TXn) and minimum (TNn) temperatures were collected
+for 60 years from 44 locations in Eastern Asia.
 \jy{Sorry I forgot to send you the data I promised. Remind in the future

### 2024-03-12 manuscript/manuscript.tex
sp100 and sp500 tables

@@
 been used to analyze the random distribution of cosmic microwave background 
-radiation \citep{naess2012application}.
+radiation \citep{naess2012application}. \citep{aslam2020introducing} 
+applied the method to test if the count rate per second of
+radioactive data followed the Poisson distribution. 
+Researchers have proposed the
+method as a technique for gear condition monitoring \citep{andrade2001gear}. It
+can also be used to compare images of breast
+cancer tumors \citep{demidenko2004kolmogorov}.
 
@@
 use when the hypothesized distribution contains unspecified parameters.
+For this situation, \citet{zeimbekakis2022misuses} proposed a parametric
+bootstrap, where bootstrap samples of the test statistics are constructed from samples generated from the fitted hypothesized distribution.
 Another commonly encountered situation is when the data are serially
@@
 distributions.
-The autocorrelation $\phi$ of the series was set to
-$\{-0.924, -0.707, -0.383, 0, 0.383, 0.707, 0.924\}$. These
-are the autocorrelations of the normal series, but after the transformation
+We generated time series $W_t$ from a 1st 
+order autoregressive (AR(1)) process:
+\begin{equation*}
+W_t = \phi X_{t-1} + \epsilon_t,
+\end{equation*}
+where $\phi$ is an autoregressive coefficient, and $\epsilon_t$ is a series of
+independent errors from a normal distribution with mean zero and variance
+$\sigma_{\epsilon}^2$. The strength of the serial dependence is controlled by
+$\phi$, which was set to five levels: 
+$\{-0.924, -0.707, -0.383, 0, 0.383, 0.707, 0.924\}$, as these
+correspond to the desired values for $\tau$. First, we generated a
+marginal $N(8, 8)$ by marginally transforming the $W_t$ by
+\begin{equation*}
+X_t = F^{-1}[\Phi(X_t)],
+\end{equation*}
+where $F^{-1}(p)$ is the quantile function for the $N(8, 8)$ 
+distribution.
+Then we generated a marginal gamma series by the same procedure, but
+replacing $F^{-1}(p)$ with the quantile function for the unit exponential 
+distribution.
+After the transformation
 to the marginal gamma distribution, the autocorrelations are $\{-0.607, 
@@
 are very similar and their
-first two moments are the same. The series were generated by marginally 
-transforming the
-marginal normal AR(1) series $X_t$ by
-\begin{equation*}
-W_t = F^{-1}[\Phi(X_t)],
-\end{equation*}
-where $F^{-1}(p)$ is the quantile function for the $\Gamma(8, 1)$.
+first two moments are the same. 
 For the purposes of 
@@
   Keep the notations consistent: $n$ and n are different.}
+\mc{addressed}
 
@@
 as the non-parametric bootstrap KS Test \citep{babu2004goodness} and
-the parametric bootstrap KS Test) to
+the parametric bootstrap KS Test \citep{zeimbekakis2022misuses}) to
 the precipitation time series from each of these locations to test if they
@@
 \jy{Is the parametric method by Zeimberkakis?}
+\mc{yes}
 
@@
 
+\subsection{SP500}
+\label{sec:sp500}
+
+Using the \textsl{tseries} package 
+\citep{tseries}, 
+we gathered closing stock prices for the SP500 index. We
+observed how the method performs using increasingly smaller durations of
+time.
+We used the last 5 years of data: January 1st, 2019 to December 31st, 2023,
+4 years of data: January 1st, 2020 to December 31st, 2023,
+3 years of data: January 1st, 2021 to December 31st, 2023,
+2 years of data: January 1st, 2022 to December 31st, 2023,
+and 1 year of data: January 1st, 2023
+to December 31st, 2023.
+We approximated stock returns by taking the difference in the logarithm 
+of the closing prices.
+We tested that the stock returns are normally
+distributed and Student's $t$ distributed 
+with degrees of freedom $v \in \{30, 20, 10, 5, 4, 3, 2, 1\}$.
+The p-values for these tests are highlighted in 
+Tables~\ref{table:SP5001}--\ref{table:SP5005}.
+
+\input{tables/sp500_pval_1y}
+
+\input{tables/sp500_pval_2y}
+
+\input{tables/sp500_pval_3y}
+
+\input{tables/sp500_pval_4y}
+
+\input{tables/sp500_pval_5y}
+
+While we expect there to be differences in the p-values for the different 
+methods, in this example, there are many instances where the conclusions
+at the .05 significance level for our method are different than those
+for both
+\citep{babu2004goodness}'s and \citet{zeimbekakis2022misuses}'s method.
+For instance, for a duration of 4 years, our method fails to reject that
+the series follows the $v = 5$ Student's $t$ distribution with p-value .064,
+wheraeas \citep{babu2004goodness}'s method finds a p-value of .016, and 
+\citet{zeimbekakis2022misuses}'s method finds a p-value of .01.
+
+\subsection{SP100}
+\label{sec:sp100}
+
+Once again using the \textsl{tseries} package 
+\citep{tseries}, 
+we gathered closing stock prices for the SP100 index. We varied the
+durations as we did with the SP500 index.
+We approximated stock returns by taking the difference in the logarithm 
+of the closing prices.
+We tested that the stock returns are normally
+distributed and Student's $t$ distributed 
+with degrees of freedom $v \in \{30, 20, 10, 5, 4, 3, 2, 1\}$.
+The p-values for these tests are highlighted in 
+Tables~\ref{table:SP1001}--\ref{table:SP1005}.
+For a duration of 4 years, our method fails to reject that
+the series follows the $v = 5$ Student's $t$ distribution with p-value .092,
+wheraeas \citep{babu2004goodness}'s method finds a p-value of .031, and 
+\citet{zeimbekakis2022misuses}'s method finds a p-value of .027.
+
+\input{tables/sp100_pval_1y}
+
+\input{tables/sp100_pval_2y}
+
+\input{tables/sp100_pval_3y}
+
+\input{tables/sp100_pval_4y}
+
+\input{tables/sp100_pval_5y}
+
 \section{Concluding Remarks}

### 2024-03-12 code/ComputeReturnLevels.R

@@ -1,0 +1,936 @@
+########################################################################################
+##### Name: ComputeReturnLevels.R                                                  #####
+#####                                                                              #####
+##### Description:                                                                 #####
+##### This codes is to accompany the Trend and Return Level of Extreme Snow Events #####                   
+##### in New York City (TAS-17-202)                                                #####
+#####                                                                              #####
+##### Purpose:                                                                     #####
+##### This code calculates MLE GEV and GP parameters, MLE return levels, and BCa   #####
+##### bootstrap confidence intervals for return levels for the model 3.            #####
+#####                                                                              #####
+##### Last Updated: July 12, 2018                                                  #####
+########################################################################################
+
+
+########################################################################################
+##### Setting up variables                                                         #####
+########################################################################################
+
+## Starting time
+ptm <- proc.time()
+
+## Loading required libraries
+library(ismev)
+library(quantreg)
+library(foreach)
+library(doParallel)
+
+## setup parallel backend to use many processors
+cores <- detectCores()
+cl <- makeCluster(cores[1]-1)
+registerDoParallel(cl)
+
+## Settings
+# T for GEV model and F for GP model
[…]

### 2024-03-12 code/snowfall.R

@@ -1,0 +1,31 @@
+source('functions.R')
+source('alt_functions.R')
+library(tidyverse)
+library(janitor)
+library(evd)
+library(xtable)
+load(file = "../data/SnowfallData.RData")
+
+series <- annmax.1
+pvals <- myapp(series, 10000, 'gev', evd::pgev, df = NULL)
+pvals <- c(pvals, my_babu(series, 10000, 'gev', evd::pgev, df = NULL))
+pvals <- c(pvals, my_param(series, 10000, 'gev', evd::pgev, evd::rgev, 
+                             df = NULL))
+
+series <- annmax.2
+pvals <- myapp(series, 10000, 'gev', evd::pgev, df = NULL)
+pvals <- c(pvals, my_babu(series, 10000, 'gev', evd::pgev, df = NULL))
+pvals <- c(pvals, my_param(series, 10000, 'gev', evd::pgev, evd::rgev, 
+                           df = NULL))
+
+series <- annmax.3
+pvals <- myapp(series, 10000, 'gev', evd::pgev, df = NULL)
+pvals <- c(pvals, my_babu(series, 10000, 'gev', evd::pgev, df = NULL))
+pvals <- c(pvals, my_param(series, 10000, 'gev', evd::pgev, evd::rgev, 
+                           df = NULL))
+
+series <- annmax.4
+pvals <- myapp(series, 10000, 'gev', evd::pgev, df = NULL)
+pvals <- c(pvals, my_babu(series, 10000, 'gev', evd::pgev, df = NULL))
+pvals <- c(pvals, my_param(series, 10000, 'gev', evd::pgev, evd::rgev, 
+                           df = NULL))

### 2024-03-12 code/sp100.R

@@ -5,19 +5,59 @@ library(tseries)
 library(extraDistr)
 library(xtable)
 
-sp100_pval_5y <- app_scheme("2018-01-01", "2022-12-31", 5, "^sp100")
+sp100_pval_5y <- app_scheme("2019-01-01", "2023-12-31", 5, "^sp100")
 
-sp100_pval_4y <- app_scheme("2019-01-01", "2022-12-31", 4, "^sp100")
+sp100_pval_4y <- app_scheme("2020-01-01", "2023-12-31", 4, "^sp100")
 
-sp100_pval_3y <- app_scheme("2020-01-01", "2022-12-31", 3, "^sp100")
+sp100_pval_3y <- app_scheme("2021-01-01", "2023-12-31", 3, "^sp100")
 
-sp100_pval_2y <- app_scheme("2021-01-01", "2022-12-31", 2, "^sp100")
+sp100_pval_2y <- app_scheme("2022-01-01", "2023-12-31", 2, "^sp100")
 
-sp100_pval_1y <- app_scheme("2022-01-01", "2022-12-31", 1, "^sp100")
+sp100_pval_1y <- app_scheme("2023-01-01", "2023-12-31", 1, "^sp100")
 
 sp100_df <- t(rbind(sp100_pval_1y, sp100_pval_2y, sp100_pval_3y, sp100_pval_4y, 
                     sp100_pval_5y
 ))
 
 saveRDS(sp100_df, "../data/sp100_df")
+
+write(print(xtable(sp100_pval_1y,
+                   caption = "P-values for 1 year of SP100 stock return data using different 
+  methods
+  and different degrees of freedom for Student's t distribution.",
+  label = "table:SP1001"
+), caption.placement = "top"), 
+file = "../manuscript/tables/sp100_pval_1y.tex")
+
+write(print(xtable(sp100_pval_2y,
+                   caption = "P-values for 2 years of SP100 stock return 
+                   data using different durations
+  and different degrees of freedom for Student's t distribution.",
+  label = "table:SP1002"
+), caption.placement = "top"), 
+file = "../manuscript/tables/sp100_pval_2y.tex")
+
+write(print(xtable(sp100_pval_3y,
+                   caption = "P-values for 3 years of SP100 stock return 
+                   data using different durations
+  and different degrees of freedom for Student's t distribution.",
+  label = "table:SP1003"
+), caption.placement = "top"), 
+file = "../manuscript/tables/sp100_pval_3y.tex")
+
+write(print(xtable(sp100_pval_4y,
[…]

### 2024-03-12 code/sp500.R

@@ -5,15 +5,15 @@ library(tseries)
 library(extraDistr)
 library(xtable)
 
-sp500_pval_5y <- app_scheme("2018-01-01", "2022-12-31", 5, "^gspc")
+sp500_pval_5y <- app_scheme("2019-01-01", "2023-12-31", 5, "^gspc")
 
-sp500_pval_4y <- app_scheme("2019-01-01", "2022-12-31", 4, "^gspc")
+sp500_pval_4y <- app_scheme("2020-01-01", "2023-12-31", 4, "^gspc")
 
-sp500_pval_3y <- app_scheme("2020-01-01", "2022-12-31", 3, "^gspc")
+sp500_pval_3y <- app_scheme("2021-01-01", "2023-12-31", 3, "^gspc")
 
-sp500_pval_2y <- app_scheme("2021-01-01", "2022-12-31", 2, "^gspc")
+sp500_pval_2y <- app_scheme("2022-01-01", "2023-12-31", 2, "^gspc")
 
-sp500_pval_1y <- app_scheme("2022-01-01", "2022-12-31", 1, "^gspc")
+sp500_pval_1y <- app_scheme("2023-01-01", "2023-12-31", 1, "^gspc")
 
 sp500_df <- t(rbind(sp500_pval_1y, sp500_pval_2y, sp500_pval_3y, sp500_pval_4y, 
                         sp500_pval_5y
@@ -21,4 +21,43 @@ sp500_df <- t(rbind(sp500_pval_1y, sp500_pval_2y, sp500_pval_3y, sp500_pval_4y,
 
 saveRDS(sp500_df, "../data/sp500_df")
 
+write(print(xtable(sp500_pval_1y,
+                   caption = "P-values for 1 year of SP500 stock return data using different 
+  methods
+  and different degrees of freedom for Student's t distribution.",
+  label = "table:SP5001"
+), caption.placement = "top"), 
+file = "../manuscript/tables/sp500_pval_1y.tex")
+
+write(print(xtable(sp500_pval_2y,
+                   caption = "P-values for 2 years of SP500 stock return 
+                   data using different durations
+  and different degrees of freedom for Student's t distribution.",
+  label = "table:SP5002"
+), caption.placement = "top"), 
+file = "../manuscript/tables/sp500_pval_2y.tex")
+
+write(print(xtable(sp500_pval_3y,
+                   caption = "P-values for 3 years of SP500 stock return 
+                   data using different durations
[…]

### 2024-03-14 manuscript/manuscript.tex
little smoothing in introductions and methods

@@
 hypothesis is false. Finally, we demonstrate applications of the method to
-precipitation data from three airports and Microsoft stock returns.
+the S&P 100 and S&P 500 indices stock returns.
 
@@
 
-Despite its widespread use, the Kolmogorov-Smirnov (KS) test can be 
+Despite its widespread use, the KS test can be 
 misapplied when its foundational assumptions are overlooked. The KS test 
@@
 bootstrap, where bootstrap samples of the test statistics are constructed from samples generated from the fitted hypothesized distribution.
+Alternatively, \citet{babu2004goodness} addresses this issue through the
+application of basic non-parametric bootstrap methods.
 Another commonly encountered situation is when the data are serially
-dependent. \citet{babu2004goodness} addresses this issue through the
-application of basic non-parametric bootstrap methods. Alternatively, 
+dependent.
 \citet{zeimbekakis2022misuses} proposed a semi-parametric bootstrap
@@
 
-Developing a fully non-parametric solution for the Kolmogorov-Smirnov (KS) 
+Developing a fully non-parametric solution for the KS 
 tests in the presence of serially dependent data presents a significant 
@@
 the structure of the serial dependence, which can vary widely in practical 
-situations. Employing a parametric bootstrap would necessitate defining a 
+situations. Employing a non-parametric bootstrap would necessitate defining a 
 specific model for this dependence, despite the primary focus being on 
@@
 applications of our method are presented in Section~\ref{sec:real}, where 
-we first apply the approach to assess whether annual maximums of hourly 
-precipitation at three U.S. airports conform to the Generalized Extreme 
-Value (GEV) distribution in Subsection~\ref{sec:precipitation}. Following 
-this, we analyze if Microsoft stock return data adhere to either the Normal 
-or the Student's $t$ distribution in Subsection~\ref{sec:microsoft}. The 
+we apply the approach to analyze if S&P 100 and S&P 500 index stock return data adhere to either the Normal 
+or the Student's $t$ distribution in Subsection~\ref{sec:sp100} and
+\ref{sec:sp500}. The 
 paper concludes with Section~\ref{sec:conclusion}, offering final thoughts 
@@
 not follow~$F$ for any parameter value~$\theta$. This is a challenging situation
-both the parameters and the serial dependence structure are unknown.
+because both the parameters and the serial dependence structure are unknown.
 
@@
 which was adopted in this study.
+Now we draw $k$ blocks from the $(n - l + 1)$ blocks 
+of $Z_j$'s with replacement and then align them in the order they were picked to
+form a block bootstrap sample. If $n$ is not a multiple of~$l$, the last block 
+selected will be reduced in size so that the final size of the block bootstrap 
+sample is $n$.
 
-We then use bootstrap to approximate the distribuition of
+We then use bootstrap to approximate the distribution of
 the KS statistic under $H_0$. In this case, we can 

### 2024-03-14 code/alt_functions.R

@@ -119,24 +119,24 @@ app_scheme <- function(start, end, years, stock) {
   resid <- series
   
   set.seed(123)
-  pval <- myapp(resid, 1000, "normal", 
+  pval <- myapp(resid, 10000, "normal", 
                       pnorm)
   set.seed(123)
-  pval <- c(pval, my_babu(resid, 1000, "normal", 
+  pval <- c(pval, my_babu(resid, 10000, "normal", 
                                       pnorm))
   set.seed(123)
-  pval <- c(pval, my_param(resid, 1000, "normal", 
+  pval <- c(pval, my_param(resid, 10000, "normal", 
                                 pnorm, rnorm))
   
   for (v in c(30, 20, 10, 5, 4, 3, 2, 1)) {
     set.seed(123)
-    np <- myapp(resid, 1000, "t", plst, 
+    np <- myapp(resid, 10000, "t", plst, 
                 df = v)
     set.seed(123)
-    babu <- my_babu(resid, 1000, "t", plst, 
+    babu <- my_babu(resid, 10000, "t", plst, 
                     df = v)
     set.seed(123)
-    param <- my_param(resid, 1000, "t", plst, rlst,
+    param <- my_param(resid, 10000, "t", plst, rlst,
                     df = v)
     pval <- rbind(pval,
                         c(np,

### 2024-03-15 manuscript/manuscript.tex
little bit to conclusion

@@
 
-If we can show that the test correctly fails to reject $H_0$ under the null
-distribution, and correctly rejects $H_0$ for an alternate distribution, we can
-state that the method works.
+In this simulation study, we aim to show that the test correctly fails to 
+reject $H_0$ under the null
+distribution, and correctly rejects $H_0$ for an alternate distribution. If
+both of these things are true, we can state that the method works
+reasonably well.
 
@@
 We generated time series with marginal distributions $N(8, 8)$ and
-$\Gamma(8, 1)$, Kendall's
+$\Gamma(8, 1)$ with Kendall's
 \jy{Need to state how serial dependence were introduced, like you did in the
@@
 measure of serial dependence as it does not vary between two different 
-distributions.
-We generated time series $W_t$ from a 1st 
+marginal distributions.
+To generate the samples to which our
+method would be applied, we simulated a time series $W_t$ from a 1st 
 order autoregressive (AR(1)) process:
@@
 correspond to the desired values for $\tau$. First, we generated a
-marginal $N(8, 8)$ by marginally transforming the $W_t$ by
+marginal $N(8, 8)$ by marginally transforming $W_t$ by
 \begin{equation*}
-X_t = F^{-1}[\Phi(X_t)],
+X_t = F^{-1}[\Phi(W_t)],
 \end{equation*}
@@
 Then we generated a marginal gamma series by the same procedure, but
-replacing $F^{-1}(p)$ with the quantile function for the unit exponential 
+replacing $F^{-1}(p)$ with the quantile function for the $\Gamma(8, 1)$
 distribution.
@@
 evaluating if the test holds it size, when $X_t \sim N(8, 8)$, we tested that the 
-marginal distribution family is normal, and when $X_t \sim \Gamma(8, 1)$, we tested
-that the marginal distribution family is gamma. For the block bootstrap step,
+marginal distribution is from the
+Normal family, or 
+$X_t \sim N(\cdot \mid \mu, \sigma^2), \quad t = 1, \ldots, n$
+for some unspecified $\mu$ and $\sigma$. When $X_t \sim \Gamma(8, 1)$, we tested
+that the marginal distribution family is from the Gamma family,
+or
+$X_t \sim \Gamma(\cdot \mid \alpha, \beta), \quad t = 1, \ldots, n$.
+for some unspecified $\alpha$ and $\beta$.
+For the block
+bootstrap step,
 we used $B = 1000$ and $l = \lceil n^{1/3} \rceil$.
@@
 sample size $n \in \{100, 200, 400, 800\}$. However, 
-to evaluate the test's power, when $X_t \sim N(8, 8)$, we tested that the 
-marginal distribution family is gamma. Because the support of $N(8, 8)$ is
+to evaluate the test's power, when $X_t \sim N(8, 8)$, we tested
+that the marginal distribution family is from the Gamma family,
+or
+$X_t \sim \Gamma(\cdot \mid \alpha, \beta), \quad t = 1, \ldots, n$.
+for some unspecified $\alpha$ and $\beta$. Because the support of $N(8, 8)$ is
 $(-\infty, \infty)$, but the support of $\Gamma(8, 1)$ is $(0, \infty)$, we used
@@
 values less than or equal to 0.
-When $X_t \sim \Gamma(8, 1)$, we tested
-that the marginal distribution family is normal. For the block bootstrap step,
+When $X_t \sim \Gamma(8, 1)$, we tested that the 
+marginal distribution is from the
+Normal family, or 
+$X_t \sim N(\cdot \mid \mu, \sigma^2), \quad t = 1, \ldots, n$
+for some unspecified $\mu$ and $\sigma$. For the block bootstrap step,
 we used $B = 1000$ and $l = \lceil n^{1/3} \rceil$.
@@
 \label{sec:real}
-
-\subsection{Precipitation at Airports}
-\label{sec:precipitation}
-Annual maximums of hourly precipitation in inches time series data were 
-retrieved 
-from the Chicago Midway International Airport (MDW), New York LaGuardia 
-International 
-Airport (LGA),
-and Los Angeles International Airport (LAX) stations from the 
-National Oceanic and Atmospheric Administration (NOAA). These stations were selected 
-from places of importance in the three largest American cities. LGA and
-MDW were chosen over John F. Kennedy and O'Hare as more data was available
-from these stations. The data for MDW is from
-1948 to 2014, the data for LGA is from 1948 to 2013, and the
-data for LAX is also from 1948 to 2013. We can apply our method (as well
-as the non-parametric bootstrap KS Test \citep{babu2004goodness} and
-the parametric bootstrap KS Test \citep{zeimbekakis2022misuses}) to
-the precipitation time series from each of these locations to test if they
-follow the
-Generalized Extreme Value (GEV) distribution using the \textsl{evd} 
-package \citep{evd}. Precipitation maximum series 
-typically do follow the GEV distribution, so we expect to fail to reject the
-null hypothesis.
-
-\jy{Is the parametric method by Zeimberkakis?}
-\mc{yes}
-
-%\input{tables/precipitation_pvals}
-%\mc{https://hdsc.nws.noaa.gov/pfds/pfds_map_cont.html?bkmrk=ct}
-
-The p-value is 0.71 for MDW, 0.13 for LGA, and 0.36 for LAX when using our 
-method.
-When using Babu's non-parametric method which does not account for serial
-dependence, the p-value is 0.74 for MDW, 0.19 for LGA, and 0.40 for LAX. 
-When using the parametric bootstrap KS test, the p-value is 0.64 for MDW,
-0.12 for LGA, and 0.35 for LAX. In this instance, the conclusions are the
-same 
-(the three series follow the GEV distribution), but because of the difference
-in p-values, it is possible for different conclusions to be found in another
-study.
-
-\subsection{Temperature in Central Park}
-\label{sec:temperature}
-
-Annual temperature maximums recorded in Central Park, New York, NY from
-1895 to 2023 were sourced from the NOAA. Again, we are interested in seeing
-if our method, which
-accounts for serial dependence and does not require parameter specification,
-performs differently than the non-parametric bootstrap KS Test 
-\citep{babu2004goodness} and the parametric bootstrap KS Test, neither of
-which account for serial dependence. We found that when using our method,
-the p-value for the test that the series follows the GEV distribution is 0.1420.
-When using Babu's method, the p-value is 0.0666, and when using the parametric
-method, the p-value is 0.0682. At the common significance level of .05,
-the conclusions would be the same regardless of the method used. However, it
-is clear that for this series, our method more decisively fails to reject the 
-null hypothesis at a significance level of .10.
-
-Annual temperature minimums were also recorded from Central Park, and the
-same method comparison was applied to this series. We found that our method
-yields a p-value of 0.0015, Babu's method yields a p-value of 0.2747, and
-the parametric method yields a p-value of 0.0002.
-
-\subsection{Temperature in Eastern Asia}
-\label{sec:asia}
-
-Annual maximums of daily maximum (TXx) and minimum (TNx) temperatures, and annual 
-minimums of daily maximum (TXn) and minimum (TNn) temperatures were collected
-for 60 years from 44 locations in Eastern Asia.
-\jy{Sorry I forgot to send you the data I promised. Remind in the future
-  please. }
-
-\subsection{Microsoft Stock Returns}
-\label{sec:microsoft}
-
-%\mc{https://www.nasdaq.com/market-activity/stocks/msft/historical}
-
-We expect the marginal distribution of Microsoft stock returns to have a 
-slightly
-heavier tail than the normal distribution. Using the \textsl{tseries} package 
-\citep{tseries}, 
-we gathered closing stock prices from January 1st, 1998 to December 31st, 2022.
-Then we approximated stock returns by taking the difference in the logarithm 
-of the closing prices.
-We tested that the stock returns are normally
-distributed (which we expect to reject).  After that, we tested that the
-marginal distribution of the time series follows the Student's $t$ distribution
-with a fixed degrees of freedom.
-While we 
-could choose to estimate a fitted value of the degrees of freedom parameter $v$
-as
-part of our method, it is very difficult to do so. Therefore, we attempted to
-test 
-if it follows
-the location-scale $t$ distribution with increasingly smaller specified degrees 
-of freedoms. This was achieved with the \textsl{extraDistr} 
-package \citep{extraDistr}. We
-also observed how the method performs using increasingly smaller durations of
-time. ,
-we used the last 5 years of data: January 1st, 2018 to December 31st, 2022,
-4 years of data: January 1st, 2019 to December 31st, 2022,
-3 years of data: January 1st, 2020 to December 31st, 2022,
-2 years of data: January 1st, 2021 to December 31st, 2022,
-and 1 year of data: January 1st, 2022
-to December 31st, 2022. In addition, we compared it to results from 
-the Babu non-parametric and 
-the parametric bootstrap KS Test.
-
-\input{tables/mc_pval_1y}
-
-\input{tables/mc_pval_2y}
-
-\input{tables/mc_pval_3y}
-
-\input{tables/mc_pval_4y}
-
-\input{tables/mc_pval_5y}
-
-\jy{Report the autocorrelation estimate of residual and residual squared in the
-  text.}
-
-The p-values of our test when applied to Microsoft stock return data using
-different settings are showcased in 
-Tables~\ref{table:microsoft1}--\ref{table:microsoft2}. Although the p-values
-are indeed different between the three methods, the conclusions at a .05 
-significance 
-level are mostly the same. This motivated an additional application on SP500
-and SP100 data.
 
@@
 
+The Kolmogorov-Smirnov test provides a way for researchers in a broad array
+of applications to compare the distributions of populations. The
+method proposed in this paper offers a variant of the test that can
+be utilized for serially dependent data without specifying parameters.
 Using simulation, we have shown that given a large enough sample of a time 
@@
 that the method is robust. We have also 
-demonstrated possible applications of this method to climate and financial data.
-Although in many cases, the conclusions may not differ between our method
-and other bootstrap KS tests, the p-values are different enough where in a case
-where the temporal dependence in the data is more extreme, conclusions could
-be drastically different if a different method is used.
+demonstrated possible applications of this method to financial data.
+Through comparison with \citep{babu2004goodness}'s non-parametric
+bootstrap KS test and \citet{zeimbekakis2022misuses}'s parametric bootstrap
+KS test, we have shown that our method can reach different conclusions which
+would perhaps be missed if serial dependence was neglected and another
+method was chosen.
 This method can be used for any study where the goal is
-to see if a time series follows a hypothesized distribution and the parameters
-are unknown or unspecified. Future studies could apply the method showcased
+to see if a serially dependenttime series follows a hypothesized distribution and the parameters
+are unknown or unspecified. Future studies could investigate
+the method's performance on different marginal distributions and
+different dependence structures. One could also apply the method showcased
 in this paper to fields like earthquake prediction and astronomy.

### 2024-03-15 manuscript/manuscript.tex
paper compiles now

@@
 hypothesis is false. Finally, we demonstrate applications of the method to
-the S&P 100 and S&P 500 indices stock returns.
+the S\&P 100 and S\&P 500 indices stock returns.
 
@@
 applications of our method are presented in Section~\ref{sec:real}, where 
-we apply the approach to analyze if S&P 100 and S&P 500 index stock return data adhere to either the Normal 
+we apply the approach to analyze if S\&P 100 and S\&P 500 index stock return data adhere to either the Normal 
 or the Student's $t$ distribution in Subsection~\ref{sec:sp100} and
@@
 \citep{tseries}, 
-we gathered closing stock prices for the SP500 index. We
+we gathered closing stock prices for the S\&P 500 index. We
 observed how the method performs using increasingly smaller durations of
@@
 \citep{tseries}, 
-we gathered closing stock prices for the SP100 index. We varied the
-durations as we did with the SP500 index.
+we gathered closing stock prices for the S\&P 100 index. We varied the
+durations as we did with the S\&P 500 index.
 We approximated stock returns by taking the difference in the logarithm 

### 2024-03-16 manuscript/manuscript.tex
10000 replicates

@@
 with degrees of freedom $v \in \{30, 20, 10, 5, 4, 3, 2, 1\}$.
+We used $B = 10,000$ bootstrap 
+replicates in this analysis.
 The p-values for these tests are highlighted in 
@@
 For instance, for a duration of 4 years, our method fails to reject that
-the series follows the $v = 5$ Student's $t$ distribution with p-value .064,
-wheraeas \citep{babu2004goodness}'s method finds a p-value of .016, and 
-\citet{zeimbekakis2022misuses}'s method finds a p-value of .01.
+the series follows the $v = 5$ Student's $t$ distribution with p-value .061,
+wheraeas \citep{babu2004goodness}'s method finds a p-value of .0222, and 
+\citet{zeimbekakis2022misuses}'s method finds a p-value of .0141. Although this
+will not always be the case, we have found at least one example of a difference
+in conclusions for different methods.
 
@@
 with degrees of freedom $v \in \{30, 20, 10, 5, 4, 3, 2, 1\}$. 
+We used $B = 10,000$ bootstrap 
+replicates in this analysis as well.
 The p-values for these tests are highlighted in 
-Tables~\ref{table:SP1001}--\ref{table:SP1005}.
+Tables~\ref{table:SP1001}--\ref{table:SP1005}. One can observe more examples
+of our method reaching different conclusions at the .05 level than others.
 For a duration of 4 years, our method fails to reject that
-the series follows the $v = 5$ Student's $t$ distribution with p-value .092,
-wheraeas \citep{babu2004goodness}'s method finds a p-value of .031, and 
-\citet{zeimbekakis2022misuses}'s method finds a p-value of .027.
+the series follows the $v = 5$ Student's $t$ distribution with p-value .0873,
+wheraeas \citep{babu2004goodness}'s method finds a p-value of .0368, and 
+\citet{zeimbekakis2022misuses}'s method finds a p-value of .03. we have here
+another instance where using a different method would lead to a different
+conclusion about the marginal distribution of the population of interest.
 

### 2024-03-19 manuscript/manuscript.tex
comments on intro

@@
 
-\jy{Start from the need for KS test for stationary series; review existing works
-  and identify the gap; summarize the contribution.}
-
 The Kolmogorov-Smirnov (KS) test is a useful goodness-of-fit statistic. 
@@
 \citep{marsaglia2003evaluating}. The KS test can be applied to a variety of
-fields. \jy{cite a few  references in various field to show its wide
-  applications.}
- It has
-been used to analyze the random distribution of cosmic microwave background 
-radiation \citep{naess2012application}. \citep{aslam2020introducing} 
-applied the method to test if the count rate per second of
-radioactive data followed the Poisson distribution. 
-Researchers have proposed the
-method as a technique for gear condition monitoring \citep{andrade2001gear}. It
-can also be used to compare images of breast
-cancer tumors \citep{demidenko2004kolmogorov}.
+fields. Examples are cosmic microwave background 
+radiation \citep{naess2012application},
+count rate of redioactive data??? \citep{aslam2020introducing},
+gear condition monitoring \citep{andrade2001gear}, and
+images of breast cancer tumors \citep{demidenko2004kolmogorov}.
 
@@
 For this situation, \citet{zeimbekakis2022misuses} proposed a parametric
-bootstrap, where bootstrap samples of the test statistics are constructed from samples generated from the fitted hypothesized distribution.
+bootstrap, where bootstrap samples of the test statistics are constructed from
+samples generated from the fitted hypothesized distribution.
 Alternatively, \citet{babu2004goodness} addresses this issue through the
@@
 dependence both need to be estimated and their uncertainty accounted for.
+\jy{This reference is an example of abuse in time series settings:
+Tuncer, O., Ates, E., Zhang, Y., Turk, A., Brandt, J., Leung, V.
+J., Egele, M., and Coskun, A.
+K.
+(2019), “Online Diagnosis of Performance Variation in HPC Systems Using Machine Learning,” IEEE Transactions on Parallel and Distributed Systems, 30, 883–896.
+}
 

### 2024-03-24 manuscript/manuscript.tex
more references

@@
 radiation \citep{naess2012application},
-count rate of redioactive data??? \citep{aslam2020introducing},
-gear condition monitoring \citep{andrade2001gear}, and
-images of breast cancer tumors \citep{demidenko2004kolmogorov}.
+count rate of radioactive data \citep{aslam2020introducing},
+gear condition monitoring \citep{andrade2001gear},
+images of breast cancer tumors \citep{demidenko2004kolmogorov},
+and financial markets \citep{lux2001turbulence}.
 
@@
 Another commonly encountered situation is when the data are serially
-dependent.
+dependent. The KS test is frequently misused without accounting for the
+assumption of independence. In an investigation of performance variation in
+high-performance computing systems, \citet{tuncer2019ieee} did not describe
+how or if they accounted for serial dependence when applying the two-sample
+KS test.
 \citet{zeimbekakis2022misuses} proposed a semi-parametric bootstrap
@@
 dependence both need to be estimated and their uncertainty accounted for.
+
 \jy{This reference is an example of abuse in time series settings:
@@
 }
+\mc{addressed}
 
@@
 
-First, let us consider how the KS statistic is typically computed for a sample
-with no dependence structure.
+\subsection{Review of Kolmogorov-Smirnov Test}
+
+First, let us review how the KS statistic is typically computed for a sample
+with no serial dependence and specified parameters.
 Let $\hat\theta_n$ denote the fitted parameters for the hypothesized 
 distribution fitted onto $X_t$, and let 
-$F_n$ denote the empirical distribution function based on $X_1,...,X_n$
+$F_n$ denote the empirical distribution function based on $X_1,...,X_n$.
 Let
@@
 
-Let us first consider the case where $X_i$'s are independent. Denote by
+\subsection{Non-Parametric Basic Bootstrap}
+
+Let us then consider the case where $X_i$'s are independent, but parameters
+are unspecified. Denote by
 $F^{(b)}_n$ the empirical distribution of the $b$th bootstrap sample and let
@@
 \citet{babu2004goodness}.
+
+\subsection{Non-Parametric Block Bootstrap}
 
@@
 
-In this simulation study, we aim to show that the test correctly fails to 
-reject $H_0$ under the null
-distribution, and correctly rejects $H_0$ for an alternate distribution. If
+In this simulation study, we aim to show that under the null
+distribution, our test rejects the $H_0$ at the significance level, 
+and that under the alternate distribution, our test rejects the $H_0$ at a high
+rate. If
 both of these things are true, we can state that the method works
@@
 After the transformation
-to the marginal gamma distribution, the autocorrelations are $\{-0.607, 
-diverges, -0.287, 0, 0.339, 0.668, 0.911\}$.
+to the marginal gamma distribution, the autocorrelations are $\{-0.8837545, 
+-0.686256, -0.3887456, -0.03336129, 0.3265704, 0.6389938, 0.8610347\}$.
 \mc{my explanation needs work}
@@
 This method can be used for any study where the goal is
-to see if a serially dependenttime series follows a hypothesized distribution and the parameters
+to see if a serially dependent time series follows a hypothesized distribution
+and the parameters
 are unknown or unspecified. Future studies could investigate
 the method's performance on different marginal distributions and
-different dependence structures. One could also apply the method showcased
+different dependence structures. Additionally, one could propose a 
+similar method
+for comparing two serially dependent methods. One could also apply the method
+showcased
 in this paper to fields like earthquake prediction and astronomy.

### 2024-03-24 code/functions.R

@@ -131,7 +131,8 @@ plot_p_vals <- function(df, filename) {
     stat_pp_point(distribution = "unif", cex = .1) +
     facet_grid(vars(n), vars(as.numeric(tau)),
                labeller = label_parsed) +
-    labs(x = "Probability Points", y = "Cumulative Probability") +
+    labs(x = "Theoretical Cumulative Distribution", 
+         y = "Empirical Cumulative Distribution") +
     coord_fixed() +
     theme(strip.text.x = element_text(size = 8))
   ggsave(filename = filename, plot = gg.f, path = "../manuscript/figures", 
@@ -145,7 +146,8 @@ plot_p_vals <- function(df, filename) {
     stat_pp_point(distribution = "unif", cex = .1) +
     facet_grid(vars(n), vars(as.numeric(tau)), 
                labeller = label_parsed) +
-    labs(x = "Probability Points", y = "Cumulative Probability") +
+    labs(x = "Theoretical Cumulative Distribution", 
+         y = "Empirical Cumulative Distribution") +
     coord_fixed(ylim = c(-0.01, 0.11), xlim = c(-0.01, 0.11)) +
     theme(strip.text.x = element_text(size = 8))
   ggsave(filename = paste('zoom_', filename, sep = ''), plot = gg.f, 

### 2024-03-31 manuscript/manuscript.tex
three digits

@@
 After the transformation
-to the marginal gamma distribution, the autocorrelations are $\{-0.8837545, 
--0.686256, -0.3887456, -0.03336129, 0.3265704, 0.6389938, 0.8610347\}$.
+to the marginal gamma distribution, the autocorrelations are $\{-0.884, 
+-0.686, -0.389, -0.033, 0.327, 0.639, 0.861\}$.
 \mc{my explanation needs work}

### 2024-04-01 manuscript/manuscript.tex
steps for basic bootstrap

@@
 \citet{babu2004goodness}.
+
+In summary, the procedure of the nonparametric basic bootstrap test is 
+summarized as follows. Repeat the following steps for $b \in \{1, ..., B\}$.
+\begin{enumerate}
+\item
+  Generate $X^{(b)}_1,...,X^{(b)}_n$ by applying basic bootstrap 
+  on the original sample as
+  defined previously.
+\item
+  Fit $F_\theta$ to $X^{(b)}_1,...,X^{(b)}_n$ and obtain estimate 
+	$\hat\theta^{(b)}_n$ of $\theta$.
+\item
+  Obtain the empirical distribution function $F^{(b)}_n$ of
+  $X^{(b)}_1,...,X^{(b)}_n$. 
+\item
+  Calculate bootstrap KS statistic
+  \[
+    T^{(b)}_n = \sup_x | \sqrt{n}\left(F^{(b)}_n(x) 
+    - F(x; \hat\theta^{(b)}_n)\right) - B_n(x) |.
+  \]
+  where 
+  $B_{n}(x) = \sqrt{n}(F_n(x) - F(x; \hat\theta_n))$ is the known
+  bias term.
+\end{enumerate}
+
+The p-value of the basic bootstrap KS test can be computed
+as $p = \#\{T^{(b)}_n > T_n\} / B$ for 
+$b \in \{1, \ldots, B\}$.
 

### 2024-04-02 manuscript/manuscript.tex
opening paragraph

@@
   Elizabeth Schifano\\
-  Jun Yan, %\\
+  Jun Yan\\
   Xianyang Zhang\\
@@
 
-The Kolmogorov-Smirnov (KS) test is a useful goodness-of-fit statistic. 
-Let $X_1, ..., X_n$ be a random sample of size~$n$ from some continuous
-distribution and the null hypothesis $H_0$ be that $X_i$'s follow the
+The standard one-sample Kolmogorov-Smirnov (KS) test is widely
+recoganized as effective good-of-fit test for continuous distributions.
+Consider $X_1, ..., X_n$, a random sample of size~$n$ from some continuous
+distribution and the null hypothesis $H_0$ that $X_i$'s follow a specific
 hypothesized distribution~$F$.
@@
 absolute value of standard Brownian bridge, which is known as the Kolmogorov
-distribution \citep{stephens1974edf}. The distribution function can be
-accurately evaluated in modern statistical software
-\citep{marsaglia2003evaluating}. The KS test can be applied to a variety of
-fields. Examples are cosmic microwave background 
-radiation \citep{naess2012application},
-count rate of radioactive data \citep{aslam2020introducing},
-gear condition monitoring \citep{andrade2001gear},
-images of breast cancer tumors \citep{demidenko2004kolmogorov},
-and financial markets \citep{lux2001turbulence}.
+distribution \citep{stephens1974edf}. This distribution function is
+precisely computable using contemporary statistical software
+\citep{marsaglia2003evaluating}. The versatility of the KS test allows its
+application across various domains, such as analyzing cosmic microwave
+background radiation \citep{naess2012application}, monitoring the count rate of
+radioactive data \citep{aslam2020introducing}, gear condition monitoring
+\citep{andrade2001gear}, studying images of breast cancer tumors
+\citep{demidenko2004kolmogorov}, and examining financial markets
+\citep{lux2001turbulence}.
 
@@
 dependence both need to be estimated and their uncertainty accounted for.
-
-\jy{This reference is an example of abuse in time series settings:
-Tuncer, O., Ates, E., Zhang, Y., Turk, A., Brandt, J., Leung, V.
-J., Egele, M., and Coskun, A.
-K.
-(2019), “Online Diagnosis of Performance Variation in HPC Systems Using Machine Learning,” IEEE Transactions on Parallel and Distributed Systems, 30, 883–896.
-}
-\mc{addressed}
 

### 2024-04-02 code/alt_functions.R
few manuscript changes

@@ -144,9 +144,8 @@ app_scheme <- function(start, end, years, stock) {
                           param))
   }
   
-  pval <- cbind(rep(years, dim(pval)[1]), 
-                      c("norm", 30, 20, 10, 5, 4, 3, 2, 1), pval)
-  colnames(pval) <- c("duration", "df", "block", "basic", "param")
+  pval <- cbind(c("normal", 30, 20, 10, 5, 4, 3, 2, 1), pval)
+  colnames(pval) <- c("$v$", "Our Method", "Babu", "Zeimbekakis")
   rownames(pval) <- NULL
   return(pval)
 }

### 2024-04-02 manuscript/manuscript.tex
few manuscript changes
manuscript tidying up

@@
 
-The Kolmogorov-Smirnov (KS) statistic is widely used to test if a sample is
-from a given distribution. This study demonstrates how non-parametric 
-block bootstrap can be 
-used to approximate the KS statistic in situations where parameters are 
-not specified and the data are serially dependent. We demonstrate the 
-theoretical justication for this method, then through simulation we verify that
-it holds it size under the null distribution and is powerful when the null 
-hypothesis is false. Finally, we demonstrate applications of the method to
-the S\&P 100 and S\&P 500 indices stock returns.
+The Kolmogorov-Smirnov (KS) test is widely used to test if a sample is
+from a given distribution. While a non-parametric bootstrap bias correction
+exists for independent and identically distributed (i.i.d.) samples with unknown
+parameters, a comparable correction suitable 
+for serially dependent data is lacking.
+This study proposes a bias correction
+using non-parametric 
+block bootstrap, designed to approximate the KS statistic in scenarios where
+parameters are unspecified and data exhibit serial dependence. We provide
+theoretical justification for this approach, then we evaluate its size
+and power through simulation. Finally, we demonstrate applications of 
+the method to
+stock returns of the S\&P 100 and S\&P 500 indices.
 
@@
 The standard one-sample Kolmogorov-Smirnov (KS) test is widely
-recoganized as effective good-of-fit test for continuous distributions.
+recognized as an effective good-of-fit test for continuous distributions.
 Consider $X_1, ..., X_n$, a random sample of size~$n$ from some continuous
@@
 samples generated from the fitted hypothesized distribution.
-Alternatively, \citet{babu2004goodness} addresses this issue through the
+Alternatively, \citet{babu2004goodness} address this issue through the
 application of basic non-parametric bootstrap methods.
-Another commonly encountered situation is when the data are serially
-dependent. The KS test is frequently misused without accounting for the
-assumption of independence. In an investigation of performance variation in
+
+Another prevalent misapplication of the KS test arises when data exhibit serial dependence, often overlooked in analyses. In an investigation of performance variation in
 high-performance computing systems, \citet{tuncer2019ieee} did not describe
@@
 where the serial dependence structure is modeled via a working serial copula.
+
 A particularly complex scenario arises when the distribution has unspecified
@@
 we apply the approach to analyze if S\&P 100 and S\&P 500 index stock return data adhere to either the Normal 
-or the Student's $t$ distribution in Subsection~\ref{sec:sp100} and
-\ref{sec:sp500}. The 
+or the Student's $t$ distribution. The 
 paper concludes with Section~\ref{sec:conclusion}, offering final thoughts 
@@
 First, let us review how the KS statistic is typically computed for a sample
-with no serial dependence and specified parameters.
+with no serial dependence with fitted parameters.
 Let $\hat\theta_n$ denote the fitted parameters for the hypothesized 
@@
 
-In this simulation study, we aim to show that under the null
-distribution, our test rejects the $H_0$ at the significance level, 
-and that under the alternate distribution, our test rejects the $H_0$ at a high
-rate. If
-both of these things are true, we can state that the method works
-reasonably well.
+In this simulation study, our objective is twofold: firstly, to demonstrate that
+under the null distribution, our test rejects the null hypothesis ($H_0$) 
+approximately at the specified significance level. Secondly, we aim to
+illustrate that under the alternate distribution, our test reliably rejects
+$H_0$ at a high frequency. The fulfillment of both these criteria would indicate
+the method's efficacy.
 
@@
   first paper: transforming a normal series.}
+\mc{addressed}
 $\tau \in \{-.75, -.5, -.25, 0, .25, .5, 75\}$, and
@@
 -0.686, -0.389, -0.033, 0.327, 0.639, 0.861\}$.
-\mc{my explanation needs work}
 
@@
 
-\subsection{SP500}
-\label{sec:sp500}
-
 Using the \textsl{tseries} package 
@@
 we gathered closing stock prices for the S\&P 500 index. We
-observed how the method performs using increasingly smaller durations of
-time.
-We used the last 5 years of data: January 1st, 2019 to December 31st, 2023,
-4 years of data: January 1st, 2020 to December 31st, 2023,
-3 years of data: January 1st, 2021 to December 31st, 2023,
-2 years of data: January 1st, 2022 to December 31st, 2023,
-and 1 year of data: January 1st, 2023
-to December 31st, 2023.
+observed how the method performs using the last 
+4 years of data: January 1st, 2020 to December 31st, 2023.
 We approximated stock returns by taking the difference in the logarithm 
 of the closing prices.
-We tested that the stock returns are normally
+Using our method, we tested that the stock returns are normally
 distributed and Student's $t$ distributed 
 with degrees of freedom $v \in \{30, 20, 10, 5, 4, 3, 2, 1\}$.
+We tested the same hypotheses using \citet{babu2004goodness}'s 
+non-parametric basic bootstrap bias correction and 
+\citet{zeimbekakis2022misuses}'s parametric bootstrap method.
 We used $B = 10,000$ bootstrap 
@@
 The p-values for these tests are highlighted in 
-Tables~\ref{table:SP5001}--\ref{table:SP5005}.
+Table~\ref{table:SP5004}.
 
-\input{tables/sp500_pval_1y}
-
-\input{tables/sp500_pval_2y}
-
-\input{tables/sp500_pval_3y}
+Once again, utilizing the \textsl{tseries} package \citep{tseries}, we collected
+closing stock prices for the S\&P 100 index. Employing the same methodology as
+our study on the S\&P 500 index, we conducted our analysis. The resulting 
+p-values for these tests are presented in Table~\ref{table:SP1004}.
 
@@
 
-\input{tables/sp500_pval_5y}
-
-While we expect there to be differences in the p-values for the different 
-methods, in this example, there are many instances where the conclusions
-at the .05 significance level for our method are different than those
-for both
-\citep{babu2004goodness}'s and \citet{zeimbekakis2022misuses}'s method.
-For instance, for a duration of 4 years, our method fails to reject that
-the series follows the $v = 5$ Student's $t$ distribution with p-value .061,
-wheraeas \citep{babu2004goodness}'s method finds a p-value of .0222, and 
-\citet{zeimbekakis2022misuses}'s method finds a p-value of .0141. Although this
-will not always be the case, we have found at least one example of a difference
-in conclusions for different methods.
-
-\subsection{SP100}
-\label{sec:sp100}
-
-Once again using the \textsl{tseries} package 
-\citep{tseries}, 
-we gathered closing stock prices for the S\&P 100 index. We varied the
-durations as we did with the S\&P 500 index.
-We approximated stock returns by taking the difference in the logarithm 
-of the closing prices.
-We tested that the stock returns are normally
-distributed and Student's $t$ distributed 
-with degrees of freedom $v \in \{30, 20, 10, 5, 4, 3, 2, 1\}$. 
-We used $B = 10,000$ bootstrap 
-replicates in this analysis as well.
-The p-values for these tests are highlighted in 
-Tables~\ref{table:SP1001}--\ref{table:SP1005}. One can observe more examples
-of our method reaching different conclusions at the .05 level than others.
-For a duration of 4 years, our method fails to reject that
-the series follows the $v = 5$ Student's $t$ distribution with p-value .0873,
-wheraeas \citep{babu2004goodness}'s method finds a p-value of .0368, and 
-\citet{zeimbekakis2022misuses}'s method finds a p-value of .03. we have here
-another instance where using a different method would lead to a different
-conclusion about the marginal distribution of the population of interest.
-
-\input{tables/sp100_pval_1y}
-
-\input{tables/sp100_pval_2y}
-
-\input{tables/sp100_pval_3y}
-
 \input{tables/sp100_pval_4y}
 
-\input{tables/sp100_pval_5y}
+While differences in p-values among different methods are expected, our analysis
+reveals numerous instances where conclusions at the 0.05 significance level
+using our method differ from those obtained using the methods proposed by
+\citet{babu2004goodness} and \citet{zeimbekakis2022misuses}.
+
+For example, when assessing the S\&P 500 series, our method fails to reject the
+hypothesis that the series follows a Student's $t$ distribution with degrees of
+freedom $v = 5$ with a p-value of 0.061. In contrast, Babu and Sen's method
+yields a p-value of 0.0222, and Zeimbekakis et al.'s method yields a p-value of
+0.0141. Although such differences are not guaranteed, this
+instance highlights a disagreement in conclusions among methods for the S\&P 500
+index.
+
+For the S\&P 100 index, our method demonstrates more instances where it reaches
+different conclusions at the 0.05 significance level compared to other methods.
+Our method fails to reject the hypothesis that the series conforms to a
+Student's $t$ distribution with degrees of freedom $v = 5$, yielding a p-value
+of 0.0873. In contrast, \citet{babu2004goodness}'s method yields a p-value of 
+0.0368, and \citet{zeimbekakis2022misuses}'s method yields a p-value of 0.03. 
+We have here
+another instance where employing different methods leads to divergent
+conclusions regarding the marginal distribution of the population under scrutin.
 
@@
 
-The Kolmogorov-Smirnov test provides a way for researchers in a broad array
-of applications to compare the distributions of populations. The
-method proposed in this paper offers a variant of the test that can
-be utilized for serially dependent data without specifying parameters.
+The Kolmogorov-Smirnov test stands as a crucial tool for researchers across
+diverse fields, enabling comparisons of population distributions. This paper
+introduces a variant of the test tailored for serially dependent data without
+necessitating parameter specification.
 Using simulation, we have shown that given a large enough sample of a time 
@@
 distribution is not
-the one hypothesized, the test is powerful. It requires a larger sample size 
-than basic bootstrap to avoid either type I or type II errors. Unsurprisingly,
+the one hypothesized, the test is powerful. Notably, it demands a larger sample
+size compared to basic bootstrap methods to avoid both type I and type II 
+errors. Unsurprisingly,
 the method performs better as the temporal dependence gets weaker. Through
 simulation studies with Normal and Gamma-distributed data, we have shown that
-that the method is robust. We have also 
+that the method is robust.
+
+We have also 
 demonstrated possible applications of this method to financial data.
 Through comparison with \citep{babu2004goodness}'s non-parametric
-bootstrap KS test and \citet{zeimbekakis2022misuses}'s parametric bootstrap
-KS test, we have shown that our method can reach different conclusions which
-would perhaps be missed if serial dependence was neglected and another
-method was chosen.
-This method can be used for any study where the goal is
-to see if a serially dependent time series follows a hypothesized distribution
-and the parameters
+bootstrap bias correction and \citet{zeimbekakis2022misuses}'s parametric
+bootstrap method, we have underscored the importance of accounting for serial
+dependence in choosing an appropriate methodology.
+This method holds relevance for studies aiming to assess if a serially dependent
+time series adheres to a hypothesized distribution in scenarios where parameters
 are unknown or unspecified. Future studies could investigate
@@
 
-\jy{The number of references seems low. Need to cite more related works.}
-
 \jy{Quality control the bib source}
+\mc{addressed}
 

### 2024-04-02 code/sp100.R

@@ -5,59 +5,45 @@ library(tseries)
 library(extraDistr)
 library(xtable)
 
-sp100_pval_5y <- app_scheme("2019-01-01", "2023-12-31", 5, "^sp100")
+#sp100_pval_5y <- app_scheme("2019-01-01", "2023-12-31", 5, "^sp100")
 
 sp100_pval_4y <- app_scheme("2020-01-01", "2023-12-31", 4, "^sp100")
 
-sp100_pval_3y <- app_scheme("2021-01-01", "2023-12-31", 3, "^sp100")
+#sp100_pval_3y <- app_scheme("2021-01-01", "2023-12-31", 3, "^sp100")
 
-sp100_pval_2y <- app_scheme("2022-01-01", "2023-12-31", 2, "^sp100")
+#sp100_pval_2y <- app_scheme("2022-01-01", "2023-12-31", 2, "^sp100")
 
-sp100_pval_1y <- app_scheme("2023-01-01", "2023-12-31", 1, "^sp100")
+#sp100_pval_1y <- app_scheme("2023-01-01", "2023-12-31", 1, "^sp100")
 
-sp100_df <- t(rbind(sp100_pval_1y, sp100_pval_2y, sp100_pval_3y, sp100_pval_4y, 
-                    sp100_pval_5y
-))
+#sp100_df <- t(rbind(sp100_pval_1y, sp100_pval_2y, sp100_pval_3y, sp100_pval_4y, 
+#                    sp100_pval_5y
+#))
 
-saveRDS(sp100_df, "../data/sp100_df")
+saveRDS(sp100_pval_4y, "../data/sp100_pval_4y")
 
-write(print(xtable(sp100_pval_1y,
-                   caption = "P-values for 1 year of SP100 stock return data using different 
-  methods
-  and different degrees of freedom for Student's t distribution.",
-  label = "table:SP1001"
-), caption.placement = "top"), 
-file = "../manuscript/tables/sp100_pval_1y.tex")
+my_format <- function(x) {
+  format(round(x, 4), nsmall = 4)
+}
 
-write(print(xtable(sp100_pval_2y,
-                   caption = "P-values for 2 years of SP100 stock return 
-                   data using different durations
-  and different degrees of freedom for Student's t distribution.",
-  label = "table:SP1002"
-), caption.placement = "top"), 
-file = "../manuscript/tables/sp100_pval_2y.tex")
[…]

### 2024-04-02 code/sp500.R

@@ -5,59 +5,45 @@ library(tseries)
 library(extraDistr)
 library(xtable)
 
-sp500_pval_5y <- app_scheme("2019-01-01", "2023-12-31", 5, "^gspc")
+#sp500_pval_5y <- app_scheme("2019-01-01", "2023-12-31", 5, "^gspc")
 
 sp500_pval_4y <- app_scheme("2020-01-01", "2023-12-31", 4, "^gspc")
 
-sp500_pval_3y <- app_scheme("2021-01-01", "2023-12-31", 3, "^gspc")
+#sp500_pval_3y <- app_scheme("2021-01-01", "2023-12-31", 3, "^gspc")
 
-sp500_pval_2y <- app_scheme("2022-01-01", "2023-12-31", 2, "^gspc")
+#sp500_pval_2y <- app_scheme("2022-01-01", "2023-12-31", 2, "^gspc")
 
-sp500_pval_1y <- app_scheme("2023-01-01", "2023-12-31", 1, "^gspc")
+#sp500_pval_1y <- app_scheme("2023-01-01", "2023-12-31", 1, "^gspc")
 
-sp500_df <- t(rbind(sp500_pval_1y, sp500_pval_2y, sp500_pval_3y, sp500_pval_4y, 
-                        sp500_pval_5y
-))
+#sp500_df <- t(rbind(sp500_pval_1y, sp500_pval_2y, sp500_pval_3y, sp500_pval_4y, 
+#                        sp500_pval_5y
+#))
 
-saveRDS(sp500_df, "../data/sp500_df")
+saveRDS(sp500_pval_4y, "../data/sp500_pval_4y")
 
-write(print(xtable(sp500_pval_1y,
-                   caption = "P-values for 1 year of SP500 stock return data using different 
-  methods
-  and different degrees of freedom for Student's t distribution.",
-  label = "table:SP5001"
-), caption.placement = "top"), 
-file = "../manuscript/tables/sp500_pval_1y.tex")
+my_format <- function(x) {
+  format(round(x, 4), nsmall = 4)
+}
 
-write(print(xtable(sp500_pval_2y,
-                   caption = "P-values for 2 years of SP500 stock return 
-                   data using different durations
-  and different degrees of freedom for Student's t distribution.",
-  label = "table:SP5002"
-), caption.placement = "top"), 
-file = "../manuscript/tables/sp500_pval_2y.tex")
[…]

### 2024-04-07 manuscript/manuscript.tex

@@
 
-\title{\bf Nonparametric Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test for
-  Marginal Distributions of Stationary Time Series}
+\title{Nonparametric Block Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test}
 \if0\blind
@@
 
-The Kolmogorov-Smirnov (KS) test is widely used to test if a sample is
-from a given distribution. While a non-parametric bootstrap bias correction
-exists for independent and identically distributed (i.i.d.) samples with unknown
-parameters, a comparable correction suitable 
-for serially dependent data is lacking.
-This study proposes a bias correction
-using non-parametric 
-block bootstrap, designed to approximate the KS statistic in scenarios where
-parameters are unspecified and data exhibit serial dependence. We provide
-theoretical justification for this approach, then we evaluate its size
-and power through simulation. Finally, we demonstrate applications of 
-the method to
-stock returns of the S\&P 100 and S\&P 500 indices.
+The Kolmogorov-Smirnov (KS) test is a widely used statistical test that
+assesses the conformity of a sample to a specified distribution. Its efficacy,
+however, diminishes with serially dependent data and when parameters
+within the hypothesized distribution are unknown. For independent data,
+parametric and nonparametric bootstrap procedure are available to adjust for
+estimated parameters. For serially dependent stationary data, parametric
+bootstrap has been developed with a working serial dependence structure. A
+counterpart for the nonparametric bootstrap approach, which needs a bias
+correction, has not been studied. Addressing this gap, our study introduces a
+bias correction method employing a non-parametric block bootstrap, which
+adeptly the distribution of the KS statistic for by unspecified serial
+dependence and unspecified parameters. We assess its effectiveness
+through simulations, scrutinizing both its size and power. The practicality of
+our method is further illustrated with an examination of stock returns from the
+S\&P 100 and S\&P 500 indices, showcasing its utility in real-world
+applications.
 
@@
 bias-correction; 
-dependent data; 
+serial dependence;
 time series. 
@@
 assumes the data are independently and identically distributed (i.i.d.) and 
+\jy{no defining acronyms that are not used later}
 that the hypothesized distribution is continuous and fully specified without 
 the need for parameter estimation. \citet{zeimbekakis2022misuses} examines
-common misapplications of the one-sample KS test, notably the inappropriate
-use when the hypothesized distribution contains unspecified parameters.
-For this situation, \citet{zeimbekakis2022misuses} proposed a parametric
+common misapplications of the one-sample KS test. One notable inappropriate
+use is when the hypothesized distribution contains unspecified parameters.
+In this case, the tests are generally constructed by substituting the unknown
+parameters by their estimates, and the asymptotic null distribution of
+the test statistic may depend in a complex way on the unknown parameters.
+The problem of unspecified parameters can be handled by a parametric
 bootstrap, where bootstrap samples of the test statistics are constructed from
 samples generated from the fitted hypothesized distribution.
-Alternatively, \citet{babu2004goodness} address this issue through the
-application of basic non-parametric bootstrap methods.
+Alternatively, \citet{babu2004goodness} address this issue through a
+non-parametric bootstrap method that corrects the bias in the asymptotic null
+distribution.
 
-Another prevalent misapplication of the KS test arises when data exhibit serial dependence, often overlooked in analyses. In an investigation of performance variation in
-high-performance computing systems, \citet{tuncer2019ieee} did not describe
-how or if they accounted for serial dependence when applying the two-sample
-KS test.
+Another prevalent misapplication of the KS test arises when data exhibit serial
+dependence, which is often overlooked in analyses. For example, in an
+investigation of performance variation in high-performance computing systems,
+\citet{tuncer2019ieee} did not describe how or if they accounted for serial
+dependence when applying the two-sample KS test.
 \citet{zeimbekakis2022misuses} proposed a semi-parametric bootstrap
 where the serial dependence structure is modeled via a working serial copula.
-
 A particularly complex scenario arises when the distribution has unspecified
@@
 evaluating the marginal distribution of a stationary series. To date, a bias 
-correction method for block bootstrap, akin to the approach \citet{babu2004goodness} 
-applied to the basic bootstrap, has not been established. This study seeks 
+correction method for block bootstrap, akin to the non-parametric bootstrap
+approach of \citet{babu2004goodness} for independent data,
+has not been established. This study seeks 
 to bridge this gap by introducing a bias correction technique for the 
@@
 applications of our method are presented in Section~\ref{sec:real}, where 
-we apply the approach to analyze if S\&P 100 and S\&P 500 index stock return data adhere to either the Normal 
-or the Student's $t$ distribution. The 
+we apply the approach to analyze if S\&P 100 and S\&P 500 index stock return
+data adhere to either the Normal or the Student's $t$ distribution. The 
 paper concludes with Section~\ref{sec:conclusion}, offering final thoughts 
@@
 
-\subsection{Review of Kolmogorov-Smirnov Test}
+\subsection{Kolmogorov--Smirnov Test}
 
@@
 
+\jy{State clearly the test statistic definition. Point out that the null
+  distribution depends on the unknown parameters and unknown serial
+  dependence. Point out the challenges are to approximate the null distribution.}
+
 We note that
@@
 \end{equation*}
+\jy{clean up the notations. Has $F$ been defined yet? do you need cdf?}
 where $F(x)$ is the true cdf (under the null $F(x) = F(x, \theta_0)$ for some
@@
 
-\subsection{Non-Parametric Basic Bootstrap}
+\subsection{Non-Parametric Bootstrap for Independent Data}
 
@@
 
-The p-value of the basic bootstrap KS test can be computed
-as $p = \#\{T^{(b)}_n > T_n\} / B$ for 
-$b \in \{1, \ldots, B\}$.
+The p-value of the basic bootstrap KS test can be approximated
+as $p = \sum_{b=1}^BB I\{T^{(b)}_n > T_n\} / B$.
 
-\subsection{Non-Parametric Block Bootstrap}
+\subsection{Non-Parametric Block Bootstrap for Stationary Series}
 
@@
 Block-bootstrap can be done with overlapping or moving blocks.
-Define 
-moving blocks (assuming $l > 1$) as:
+Define moving blocks (assuming $l > 1$) as:
 \begin{equation*}
@@
 
-We then use bootstrap to approximate the distribution of
-the KS statistic under $H_0$. In this case, we can 
+Continuing using the notation in the independent case,
+we use $F^{(b)}_n$ and $\hat\theta^{(b)}_n$ for the empirical distribution and
+the estimated parameters based on the $b$th bootstrap sample,
+$b = 1, \ldots, B$.
+We then use block bootstrap to approximate the asymptotic distribution of
+the KS statistic under $H_0$. In particular, we
 use the distribution of $\sqrt{n}(F^{(b)}_n(x) - E[F^{(b)}_n(x)])$
 as an approximation of the distribution of
-$\sqrt{n}(F_n(x) - F(x))$,
-and the distribution of 
-$\sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; E[\hat\theta^{(b)}_n]))$ to
-approximate $\sqrt{n}(F(x; \theta_n) - F(x))$'s distribution.
+$\sqrt{n}(F_n(x) - F(x))$, and the distribution of 
+$\sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; E[\hat\theta^{(b)}_n]))$ as
+an approximation of the distribution of $\sqrt{n}(F(x; \theta_n) - F(x))$.
+The expected values $E[F^{(b)}_n(x)]$ and
+$E[\hat\theta^{(b)}_n]$ can be approximated by, respectively,
+$E_n[F^{(b)}_n(x)] = \frac{1}{B}\sum_{b = 1}^BF^{(b)}_n(x)$ and
+$E_n[\hat\theta^{(b)}_n]  =  \frac{1}{B}\sum_{b = 1}^B\hat\theta^{(b)}_n$.
 
-We can compute $E[F^{(b)}_n(x)]$ and
-$E[\hat\theta^{(b)}_n]$ numerically (they can also be computed analytically, 
-depending on the types of block bootstrap we use). One can compute 
-$F^{(b)}_n$ 
-and $\hat\theta^{(b)}_n$ based on
-the $b$th bootstrap sample. Then
-$E[F^{(b)}_n(x)] \approx \frac{1}{B}\sum_{b = 1}^BF^{(b)}_n(x)$, and
-$E[\hat\theta^{(b)}_n] \approx \frac{1}{B}\sum_{b = 1}^B\hat\theta^{(b)}_n$.
-In this case, we can define
+Then, we can define
 \begin{align*}
@@
 
-The p-value of the block bootstrap KS test can be computed
-as $p = \#\{T^{(b)}_n > T_n\} / B$ for 
-$b \in \{1, \ldots, B\}$.
+The p-value of the block bootstrap KS test can be approximated
+as $p = \sum_{b=1}^N I\{T^{(b)}_n > T_n\} / B$.
 
@@
 p-value
-of the test should be uniformally distributed between 0 and 1. We must try the
+of the test should be uniformly distributed between 0 and 1. We must try the
 method with different marginal distributions to ensure that it is robust.
@@
 $\Gamma(8, 1)$ with Kendall's
-\jy{Need to state how serial dependence were introduced, like you did in the
-  first paper: transforming a normal series.}
-\mc{addressed}
 $\tau \in \{-.75, -.5, -.25, 0, .25, .5, 75\}$, and
@@
 \end{equation*}
+\jy{define $\Phi$}
+\jy{The language issues are more than I expected. Please do a careful proofread,
+  now that you are more experienced.}
 where $F^{-1}(p)$ is the quantile function for the $N(8, 8)$ 
@@
 
-\jy{Consider presenting this in a graph. Try explaining the pattern.
-  Keep the notations consistent: $n$ and n are different.}
-\mc{addressed}
-
 \begin{figure}[tbp]
@@
 margins, indicating that the method is robust to the marginal distribution.
-
-The rejection rates for $n = 800$
-are very 
+The rejection rates for $n = 800$ are very 
 high (almost 1), indicating that under $H_A$, the test is very powerful 
@@
 
-\jy{Quality control the bib source}
-\mc{addressed}
-
 \bibliographystyle{asa}

### 2024-04-07 manuscript/manuscript.tex
commented on simulation, application and conclusion

@@
 that is the most common range for significance levels $\alpha$.
-%We can also
-%compute the rate of rejection $\#P < \alpha$ for different values of
-%$\alpha$, as well as a confidence interval
-%for this proportion.
+
+\jy{Remove the white space in the pdf figures. Could put the zoomed version in
+  the same figure.}
 
@@
   \caption{A Q-Q plot of the p-values displayed in Figure~\ref{fig:normal} zoomed in to 
-  probabilities between 0 and
-  0.1}
+  probabilities between 0 and  0.1.}
   \label{fig:zoom_normal}
@@
   \caption{A Q-Q plot of the p-values displayed in Figure~\ref{fig:gamma} zoomed in to 
-  probabilities between 0 and
-  0.1}
+  probabilities between 0 and 0.1.}
   \label{fig:zoom_gamma}
@@
 strength. Results are very similar for normal and gamma margins.
+\jy{Summarize findings in bullet points before forming text.}
 
 Under $H_0$, the p-values for the non-parametric block bootstrap KS test are
+\jy{Not true from the plots.}
 uniformly distributed. This is an indication that our method 
@@
 \subsection{Power}
-We must also evaluate if this method works when $H_0$ is false. We can use
-the block bootstrap KS test to test if some $X_t \sim F$ is generated from 
-some other 
-distribution $G$ with some unknown $\theta$. In this scenario, if the test is 
-indeed powerful,
-we would ideally want $\beta$ 
-(or the probability of failed rejection under $H_A$) 
+The power of the proposed test is investigated with data generated from
+distributions that are not in the hypothesized distribution family. If the test
+is indeed powerful, we would ideally want $\beta$ \jy{beta has been
+  used. Discuss in terms of power: the probability of rejecting $H_0$ when $H_0$
+  is false.}
 to be 0, but we
@@
 We would then expect the distribution of p-values to be non-uniform, and the 
-rate
+rate \jy{Does not sound right. What is $\alpha$?}
 of $\#P < \alpha$ to be high, meaning a higher density of low p-values.
 
+\jy{Description too wordy, Be concise. Basically generate data from one
+  distribution but test for the other distribution.}
 Like we did to see if the test holds its size, we generated time series with 
 marginal distributions $N(8, 8)$ and 
-$\Gamma(8, 1)$, Kendall's $\tau \in \{-.75, -.5, -.25, 0, .25, .5, 
-.75\}$, and
+$\Gamma(8, 1)$, Kendall's $\tau \in \{-.75, -.5, -.25, 0, .25, .5, .75\}$, and
 sample size $n \in \{100, 200, 400, 800\}$. However, 
@@
 
+\jy{alpha has been used as gamma parameters. This is not necessary, Just say we
+  checked the power when the significance level is .05.}
 Given some significance level $\alpha$, we can compute a rejection rate 
@@
 
-From 
-Figure~\ref{fig:rr}, 
-the rejection rates appear to get lower as $\tau$ increases in a
-positive direction. Using a sample size $n \geq 800$ appears to be sufficient
+Figure~\ref{fig:rr} displays the empirical power curve of the test at
+significance level 0.05 as the lag-1 Kendall's~$\tau$ increases from
+$-0.9$ to $0.9$. Using a sample size $n \geq 800$ appears to be sufficient
+\jy{What are the findings? summarize bullet points before forming texts.}
 when $\tau$ is not too high, but for $\tau \geq 0.75$, all sample sizes 
@@
 
-\section{Real Data Analysis}
+\section{Real Data Examples}
 \label{sec:real}
 
-Using the \textsl{tseries} package 
-\citep{tseries}, 
-we gathered closing stock prices for the S\&P 500 index. We
-observed how the method performs using the last 
-4 years of data: January 1st, 2020 to December 31st, 2023.
-We approximated stock returns by taking the difference in the logarithm 
-of the closing prices.
-Using our method, we tested that the stock returns are normally
+Using the \textsl{tseries} package  \citep{tseries}, 
+we gathered daily closing prices for the S\&P 500 index from January 1st, 2020
+to December 31st, 2023. Daily returns were obtained by taking the difference in
+the logarithm of the closing prices.
+Using our method, we tested that the daily returns are normally
 distributed and Student's $t$ distributed 
@@
 
-Once again, utilizing the \textsl{tseries} package \citep{tseries}, we collected
-closing stock prices for the S\&P 100 index. Employing the same methodology as
-our study on the S\&P 500 index, we conducted our analysis. The resulting 
-p-values for these tests are presented in Table~\ref{table:SP1004}.
+\jy{Put them into one table; add results for paremetric bootstrap with
+  Zeimbakakis' approach with serial dependence accounted for; label the methods
+  as serial dependence accounted for and not accounted for, two methods
+  (parametric and nonparametric) under each.}
+
+\jy{Discuss the difference between the semiparametric bootstrap and the proposed
+  nonparametric bootstrap. The semiparametric method depends on a working copula
+  model for the serial dependence. If that is severely misspecified, I'd expect
+  poor performance. The proposed method does not need to specify that dependence
+  structure.}
 
@@
 
+\jy{Stock returns are known to be serially dependent and heavy-tailed. Search
+  google scholar ``stylized facts of daily returns series'' and cite them.}
+
 While differences in p-values among different methods are expected, our analysis
@@
 \citet{babu2004goodness} and \citet{zeimbekakis2022misuses}.
+\jy{I don't like one-sentence paragraphs.}
 
@@
 
-For the S\&P 100 index, our method demonstrates more instances where it reaches
+The same analyses were repeated on the daily returns of the S\&P 100 index.
+Our method demonstrates more instances where it reaches
 different conclusions at the 0.05 significance level compared to other methods.
-Our method fails to reject the hypothesis that the series conforms to a
+Our method does not reject the hypothesis that the series conforms to a
 Student's $t$ distribution with degrees of freedom $v = 5$, yielding a p-value
@@
 0.0368, and \citet{zeimbekakis2022misuses}'s method yields a p-value of 0.03.
-We have here
-another instance where employing different methods leads to divergent
 conclusions regarding the marginal distribution of the population under scrutin.
@@
 demonstrated possible applications of this method to financial data.
+\jy{don't astrophie citet; let alone citep}
 Through comparison with \citep{babu2004goodness}'s non-parametric
@@
 are unknown or unspecified. Future studies could investigate
+\jy{Too vague.}
 the method's performance on different marginal distributions and
@@
 in this paper to fields like earthquake prediction and astronomy.
+
+\jy{summarize remarks in bullet points first. Let's talk on Tuesday.}
 

### 2024-04-16 manuscript/manuscript.tex
responded to some comments

@@
 misapplied when its foundational assumptions are overlooked. The KS test 
-assumes the data are independently and identically distributed (i.i.d.) and 
-\jy{no defining acronyms that are not used later}
+assumes the data are independently and identically distributed and 
 that the hypothesized distribution is continuous and fully specified without 
@@
 \end{equation*}
-\jy{define $\Phi$}
+\jy{define $\Phi$}\mc{addressed}
 \jy{The language issues are more than I expected. Please do a careful proofread,
@@
 where $F^{-1}(p)$ is the quantile function for the $N(8, 8)$ 
+distribution and $\Phi$ is the distribution function of the standard normal
 distribution.
@@
 \jy{Remove the white space in the pdf figures. Could put the zoomed version in
-  the same figure.}
+  the same figure.}\mc{addressed}
 
@@
   \centering
-  \includegraphics[width = \textwidth]{figures/zoom_normal}
-  \caption{A Q-Q plot of the p-values displayed in Figure~\ref{fig:normal} zoomed in to 
-  probabilities between 0 and  0.1.}
-  \label{fig:zoom_normal}
-\end{figure}
-
-\begin{figure}[tbp]
-  \centering
   \includegraphics[scale=1]{figures/gamma}
@@
 
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[scale=1]{figures/zoom_gamma}
-  \caption{A Q-Q plot of the p-values displayed in Figure~\ref{fig:gamma} zoomed in to 
-  probabilities between 0 and 0.1.}
-  \label{fig:zoom_gamma}
-\end{figure}
+\input{tables/rr_100}
+
+\input{tables/rr_200}
+
+\input{tables/rr_400}
+
+\input{tables/rr_800}
 
@@
 Kendall's $\tau \geq 0.75$, a sample larger than $n = 800$ appears to be 
-necessary, as the p-values are not aligned with the line in the Q-Q plots, even
-in Figures~\ref{fig:zoom_normal} and \ref{fig:zoom_gamma}. This
+necessary, as the p-values are not aligned with the line in the Q-Q plots. This
 is not necessarily a cause for concern, as (for normal margins)
@@
 Under $H_0$, the p-values for the non-parametric block bootstrap KS test are
-\jy{Not true from the plots.}
-uniformly distributed. This is an indication that our method 
-holds its size and that we can expect the probability
+\jy{Not true from the plots.}\mc{addressed}
+uniformly distributed as long as the serial dependence is not too high. 
+This is an indication that our method 
+holds its size for moderate serial dependence levels.
+For such cases, we can expect the probability
 of a type 1 error to be the significance level $\alpha$.
@@
 distributions that are not in the hypothesized distribution family. If the test
-is indeed powerful, we would ideally want $\beta$ \jy{beta has been
+is indeed powerful, we would ideally want the probability of
+rejecting $H_0$ when $H_0$ is false\jy{beta has been
   used. Discuss in terms of power: the probability of rejecting $H_0$ when $H_0$
   is false.}
-to be 0, but we
-expect it to be generally low. Again, we must try the method with different
+to be 1, but we
+expect it to be generally high. Again, we must try the method with different
 marginal distributions to ensure that it is robust.
@@
 \citet{babu2004goodness} and \citet{zeimbekakis2022misuses}.
-\jy{I don't like one-sentence paragraphs.}
-
 For example, when assessing the S\&P 500 series, our method fails to reject the
@@
 demonstrated possible applications of this method to financial data.
-\jy{don't astrophie citet; let alone citep}
-Through comparison with \citep{babu2004goodness}'s non-parametric
-bootstrap bias correction and \citet{zeimbekakis2022misuses}'s parametric
-bootstrap method, we have underscored the importance of accounting for serial
+\jy{don't astrophie citet; let alone citep}\mc{addressed}
+Through comparison with the non-parametric
+bootstrap bias correction developed by \citet{babu2004goodness}
+and the parametric
+bootstrap method developed by \citet{zeimbekakis2022misuses}, we have 
+underscored the importance of accounting for serial
 dependence in choosing an appropriate methodology.

### 2024-04-16 code/data_processing.R

@@ -44,6 +44,29 @@ for (phi in phis) {
     for (dist in c("normal", "gamma")) {
       for(alpha in c(.01, .05, .10)) {
         pvals <- readRDS(
+          paste("../", "sim_", n, "_", dist, "_", phi, "_0", ".RDS", 
+                sep = ''))
+        R <- length(pvals)
+        if (R <= 0) next
+        x <- sum(pvals < alpha)
+        prop_test <- prop.test(x, R, correct=FALSE)
+        rr_lb <- prop_test$conf.int[1]
+        rr_ub <- prop_test$conf.int[2]
+        rr <- mean(c(rr_lb, rr_ub))
+        df <- rbind(df, c(phi, n, dist, alpha, rr_lb, rr, rr_ub, R))
+      }
+    }
+  }
+}
+colnames(df) <- c("phi", "n", "dist", "alpha", "rr_lb", "rr", "rr_ub", "R")
+saveRDS(df, file = "../rejection_rates1.RDS")
+
+df <- data.frame(matrix(ncol = 8, nrow = 0))
+for (phi in phis) {
+  for (n in c(100, 200, 400, 800)) {
+    for (dist in c("normal", "gamma")) {
+      for(alpha in c(.01, .05, .10)) {
+        pvals <- readRDS(
           paste("../", "alt_", n, "_", dist, "_", phi, "_0", ".RDS", 
                 sep = ''))
         R <- length(pvals)
@@ -59,7 +82,7 @@ for (phi in phis) {
   }
 }
 colnames(df) <- c("phi", "n", "dist", "alpha", "rr_lb", "rr", "rr_ub", "R")
-saveRDS(df, file = "../rejection_rates.RDS")
+saveRDS(df, file = "../rejection_rates2.RDS")
 
 df <- data.frame(matrix(ncol = 4, nrow = 0))
 for (phi in phis) {

### 2024-04-16 code/functions.R

@@ -143,7 +143,7 @@ plot_p_vals <- function(df, filename) {
     coord_fixed() +
     theme(strip.text.x = element_text(size = 8))
   ggsave(filename = filename, plot = gg.f, path = "../manuscript/figures", 
-         height = 6, width = 6)
+         height = 4, width = 6)
   
   gg.f <- ggplot(data = df, mapping = aes(sample = pval)) +
     scale_x_continuous(breaks=c(0, 0.1)) +
@@ -158,7 +158,7 @@ plot_p_vals <- function(df, filename) {
     coord_fixed(ylim = c(-0.01, 0.11), xlim = c(-0.01, 0.11)) +
     theme(strip.text.x = element_text(size = 8))
   ggsave(filename = paste('zoom_', filename, sep = ''), plot = gg.f, 
-         path = "../manuscript/figures", height = 6, width = 6)
+         path = "../manuscript/figures", height = 4, width = 6)
 }
 
 plot_rr <- function(df, filename) {
@@ -187,7 +187,7 @@ plot_rr <- function(df, filename) {
     labs(x = latex2exp::TeX("$\\tau$"), y = latex2exp::TeX("Rejection Rate")) +
     coord_fixed(ylim = c(0, 1), xlim = c(-1, 1))
   ggsave(filename = filename, plot = gg.f, path = "../manuscript/figures", 
-         height = 4, width = 6)
+         height = 3, width = 6)
     
     
 }

### 2024-04-16 code/tables.R

@@ -1,58 +1,70 @@
 library(xtable)
-df <- readRDS("../data/rejection_rates.RDS") %>% 
+df <- readRDS("../data/rejection_rates1.RDS") %>% 
   mutate(rr_lb = round(as.numeric(rr_lb), 3),
          rr = round(as.numeric(rr), 3),
-         rr_ub = round(as.numeric(rr_ub), 3)) %>% 
-  filter(alpha == 0.05)
+         rr_ub = round(as.numeric(rr_ub), 3))
+
 df_100 <- df %>% 
   filter(n == 100) %>% 
   select(-R) %>% 
-  rename(distribution = dist, `lower bound` = rr_lb, `rejection rate` = rr, 
+  rename(`$\\phi$` = phi, `$n$` = n, distribution = dist, 
+         `$\\alpha$` = alpha, `lower bound` = rr_lb, `rejection rate` = rr, 
          `upper bound` = rr_ub)
 write(print(xtable(df_100, 
-                   caption = "Rejection rates for test when n = 100 for 
+                   caption = "Rejection rates for test under true null hypothesis
+                   when n = 100 for 
                    different values of AR(1) coefficient and for different 
                    significance levels. Lower and upper bounds are also 
                    included.",
-                   label = "table:rr_100"), caption.placement = "top"), 
+                   label = "table:rr_100"), caption.placement = "top",
+            sanitize.text.function=function(x){x}), 
       file = "../manuscript/tables/rr_100.tex")  
 
 df_200 <- df %>% 
   filter(n == 200) %>% 
   select(-R) %>% 
-  rename(distribution = dist, `lower bound` = rr_lb, `rejection rate` = rr, 
+  rename(`$\\phi$` = phi, `$n$` = n, distribution = dist, 
+         `$\\alpha$` = alpha, `lower bound` = rr_lb, `rejection rate` = rr, 
          `upper bound` = rr_ub)
-write(print(xtable(df_200,
-                   caption = "Rejection rates for test when n = 200 for 
+write(print(xtable(df_200, 
+                   caption = "Rejection rates for test under true null hypothesis
+                   when n = 200 for 
                    different values of AR(1) coefficient and for different 
                    significance levels. Lower and upper bounds are also 
                    included.",
-                   label = "table:rr_200"), caption.placement = "top"), 
-      file = "../manuscript/tables/rr_200.tex")
+                   label = "table:rr_200"), caption.placement = "top",
+            sanitize.text.function=function(x){x}), 
[…]

### 2024-04-16 manuscript/manuscript.tex
abstract smooth

@@
 bias correction method employing a non-parametric block bootstrap, which
-adeptly the distribution of the KS statistic for by unspecified serial
-dependence and unspecified parameters. We assess its effectiveness
+approximates the distribution of the KS statistic accounting for unspecified
+serial dependence and unspecified parameters. We assess its effectiveness
 through simulations, scrutinizing both its size and power. The practicality of

### 2024-04-18 manuscript/manuscript.tex
small changes to notation

--- 2024-04-16 manuscript/manuscript.tex
@@
 Let $\hat\theta_n$ denote the fitted parameters for the hypothesized 
-distribution fitted onto $X_t$, and let 
+distribution $F(x; \hat\theta_n)$ fitted onto $X_t$, and let 
 $F_n$ denote the empirical distribution function based on $X_1,...,X_n$.
@@
 \end{equation*}
+
 Then, the
@@
 Y_n(x; \hat\theta) = \sqrt{n}(F_n(x) - F(x)) - 
-\sqrt{n}(F(x; \hat\theta_n) - F(x)),
+\sqrt{n}(F(x; \hat\theta_n) - F(x)).
 \end{equation*}
 \jy{clean up the notations. Has $F$ been defined yet? do you need cdf?}
-where $F(x)$ is the true cdf (under the null $F(x) = F(x, \theta_0)$ for some
-true parameter $\theta_0$).
+\mc{addressed}
 

### 2024-04-18 code/blk2_jobs.R

@@ -1,0 +1,62 @@
+source("hpc_functions.R")
+# library(copula)
+B <- 1000
+nrep <- 5
+phis <- c()
+# for (i in c(-.75, -.5, -.25, 0, .25, .5, .75)) {
+#   phis <- c(phis, iTau(normalCopula(), i))
+# }
+phis <- 
+  c(-0.9238795, 0.9238795)
+i <- Sys.getenv("SLURM_ARRAY_TASK_ID")
+for (phi in phis) {
+  for (n in c(100, 200, 400, 800)) {
+    for (true_dist in c("normal", "gamma")) {
+      blksize <- ceiling(2*n^(1/3))
+      set.seed(as.integer(i))
+      if (true_dist == "normal") {
+        h0_dist <- "normal"
+        f0 <- pnorm
+        f <- qnorm
+        theta <- c(8, sqrt(8))
+      }
+      if (true_dist == "gamma") {
+        h0_dist <- "gamma"
+        f0 <- pgamma
+        f <- qgamma
+        theta <- c(8,1)
+      }
+      df <- data.frame(matrix(NA,    
+                              nrow = nrep,
+                              ncol = 1))
+      p <- replicate(nrep, mysim(n, blksize, B, h0_dist, true_dist, f0, f, 
+                                 theta, phi, 0))
+      df$p <- p
+      saveRDS(df, paste("../data/sim2_", n, "_", true_dist, "_",
+                        phi, "_", 
+                        "0", "_",  i, ".RDS", sep = ""))
+      set.seed(as.integer(i))
+      if (true_dist == "normal") {
+        h0_dist <- "gamma"
+        f0 <- pgamma
+        f <- qnorm
+        theta <- c(8, sqrt(8))
+      }
+      if (true_dist == "gamma") {
+        h0_dist <- "normal"
+        f0 <- pnorm
+        f <- qgamma
+        theta <- c(8,1)
+      }
+      df <- data.frame(matrix(NA,    
+                              nrow = nrep,
+                              ncol = 1))
+      p <- replicate(nrep, mysim(n, blksize, B, h0_dist, true_dist, f0, f, 
+                                 theta, phi, 0))
+      df$p <- p
+      saveRDS(df, paste("../data/alt2_", n, "_", true_dist, "_",
+                        phi, "_", 
+                        "0", "_",  i, ".RDS", sep = ""))
+    }
+  }
+}

### 2024-04-18 code/data_processing.R

@@ -49,10 +49,10 @@ for (phi in phis) {
         R <- length(pvals)
         if (R <= 0) next
         x <- sum(pvals < alpha)
-        prop_test <- prop.test(x, R, correct=FALSE)
+        prop_test <- prop.test(x, R, correct=TRUE)
         rr_lb <- prop_test$conf.int[1]
         rr_ub <- prop_test$conf.int[2]
-        rr <- mean(c(rr_lb, rr_ub))
+        rr <- x / R
         df <- rbind(df, c(phi, n, dist, alpha, rr_lb, rr, rr_ub, R))
       }
     }

### 2024-04-18 code/jobs.sh

@@ -13,5 +13,4 @@ module load r/4.2.2
 ## avoiding implicit paralellism
 export OMP_NUM_THREADS=1
 
-Rscript null_jobs.R
-Rscript alt_jobs.R
+Rscript blk2_jobs.R

### 2024-04-23 manuscript/manuscript.tex
edits on ks definition

@@
 
-First, let us review how the KS statistic is typically computed for a sample
-with no serial dependence with fitted parameters.
-Let $\hat\theta_n$ denote the fitted parameters for the hypothesized 
-distribution $F(x; \hat\theta_n)$ fitted onto $X_t$, and let 
-$F_n$ denote the empirical distribution function based on $X_1,...,X_n$.
-Let
+First, let us review how the KS statistic is computed for an independent
+sample with fitted parameters. Let $\hat\theta_n$ denote the parametrically
+fitted parameters, which can be obtained from any consistent estimator with
+asymptotic normality properties,  Let $F_n$ be the empirical distribution
+function based on $X_1,...,X_n$.
+Define 
 \begin{equation*}
@@
 \end{equation*}
-
-Then, the
-goodness of fit statistic is 
+Then, the one-sample KS goodness of fit statistic is 
 \begin{equation*}
@@
 
-\jy{State clearly the test statistic definition. Point out that the null
-  distribution depends on the unknown parameters and unknown serial
-  dependence. Point out the challenges are to approximate the null distribution.}
-
-We note that
+Because of the estimation uncertainty in $\hat\theta_n$, the asymptotic
+distribution of $Y_n$ is no longer distribution-free. This is in contrast to the
+case where $\theta$ is known.  Note that
 \begin{equation*}
@@
 \end{equation*}
-\jy{clean up the notations. Has $F$ been defined yet? do you need cdf?}
-\mc{addressed}
+When $\hat\theta_n$ is replaced with $\theta$, as in the standard KS testing
+situation, the second term vanishes, and $T_n$ converges in distribution to that
+of $\sup_t | B(F(t)) |$, where $B(\cdot)$ is the standard Brownian bridge
+\citep{kolmogorov1933sulla}. With $\hat\theta_n$ in place of $\theta$, the
+second term leads to a bias in the Brownian bridge, which was addressed by
+\citet{babu2004goodness}.
+
+When $\{X_t: t = 1, \ldots, n\}$ are further serially dependent, the statistics
+$T_n$ still provides a reasonable metric for deviation from the null
+hypothesis. Nonetheless, the asymptotic distribution of $T_n$ cannot be fixed
+even with the bias correction of \citet{babu2004goodness}, because the
+correction requires independent sample.
 
@@
 
-Let us then consider the case where $X_i$'s are independent, but parameters
+Continue with the case where $X_i$'s are independent but the parameters
 are unspecified. Denote by
@@
 
-In summary, the procedure of the nonparametric basic bootstrap test is 
+In summary, the procedure of the nonparametric bootstrap KS test for independent
+sample is 
 summarized as follows. Repeat the following steps for $b \in \{1, ..., B\}$.
@@
 The p-value of the basic bootstrap KS test can be approximated
-as $p = \sum_{b=1}^BB I\{T^{(b)}_n > T_n\} / B$.
+as $p = \sum_{b=1}^B I\{T^{(b)}_n > T_n\} / B$.
 
@@
 \end{equation*}
-\jy{define $\Phi$}\mc{addressed}
 \jy{The language issues are more than I expected. Please do a careful proofread,
@@
 After the transformation
-to the marginal gamma distribution, the autocorrelations are $\{-0.884, 
--0.686, -0.389, -0.033, 0.327, 0.639, 0.861\}$.
+to the marginal gamma distribution, the autocorrelations are
+\[
+  \{-0.884, -0.686, -0.389, -0.033, 0.327, 0.639, 0.861\}.
+\]
 
@@
 
-Using the \textsl{qqplotr} and \textsl{ggplot2} packages 
-\citep{qqplotr, ggplot2},
+Using R packages \textsl{qqplotr} and \textsl{ggplot2} \citep{qqplotr, ggplot2},
 we constructed Q-Q plots of the distribution of the p-values to see if they are
@@
 indicates that under the null hypothesis, our method will only reject the $H_0$
-at a rate of $\alpha$.
+at a rate of $\alpha$. \jy{Describe the table not zoomed-in figure.}
 A zoomed in plot for probabilities between 0 and 0.1 is
@@
 that is the most common range for significance levels $\alpha$.
-
-\jy{Remove the white space in the pdf figures. Could put the zoomed version in
-  the same figure.}\mc{addressed}
 
@@
 Under $H_0$, the p-values for the non-parametric block bootstrap KS test are
-\jy{Not true from the plots.}\mc{addressed}
+\jy{The flow doesn't read right from the last paragraph}
 uniformly distributed as long as the serial dependence is not too high. 
@@
 demonstrated possible applications of this method to financial data.
-\jy{don't astrophie citet; let alone citep}\mc{addressed}
 Through comparison with the non-parametric

### 2024-04-23 manuscript/manuscript.tex
many edits

--- 2024-04-18 manuscript/manuscript.tex
@@
 distribution and the null hypothesis $H_0$ that $X_i$'s follow a specific
-hypothesized distribution~$F$.
+hypothesized distribution~$F(x; \theta_0)$, where $\theta_0$ are the 
+specified parameters
+of the hypothesized distribution family.
 If we let $F_n(t) = \sum_{i=1}^n I(X_i \le t) / n$ be the empirical cumulative
@@
   \label{eq:ks_standard}
-  T_n = \sqrt{n} \sup_x | F_{n}(x) - F(x) |.
+  T_n = \sqrt{n} \sup_x | F_{n}(x) - F(x; \theta_0)|.
 \end{equation}
@@
 dependence when applying the two-sample KS test.
+The distribution of the test statistic under
+the null hypothesis depends on the unknown parameters and unknown 
+serial dependence. Therefore, the null distribution under dependence cannot be
+used,
+and the challenge is to approximate said distribution.
 \citet{zeimbekakis2022misuses} proposed a semi-parametric bootstrap
@@
 approach, where the parameters of the hypothesized distribution and the serial
-dependence both need to be estimated and their uncertainty accounted for.
+dependence both need to be estimated and their uncertainty accounted for,
+but this could affect results if the estimated serial
+dependence is too far from the truth. For this reason, a non-parametric method
+is motivated.
 
@@
   dependence. Point out the challenges are to approximate the null distribution.}
+\mc{addressed in third paragraph of introduction}
 
@@
 Y_n(x; \hat\theta) = \sqrt{n}(F_n(x) - F(x)) - 
-\sqrt{n}(F(x; \hat\theta_n) - F(x)).
+\sqrt{n}(F(x; \hat\theta_n) - F(x)),
 \end{equation*}
@@
 \mc{addressed}
+where $F(x)$ is the true cumulative distribution function 
+(under the $H_0: F(x) = F(x; \theta_0)$ for some true
+parameter $\theta_0$.)
 
@@
 to the marginal gamma distribution, the autocorrelations are $\{-0.884, 
--0.686, -0.389, -0.033, 0.327, 0.639, 0.861\}$.
+-0.686, -0.389, -0.033, 0.327, 
+\break 0.639, 0.861\}$.
 
@@
 For each setting for $F$, $\tau$, and $n$, we replicate the method 1000 times 
-to get the distribution of the p-values 
+to get the distribution of the p-values $p_r$
 for the test when applied to samples from the same data generating process.
@@
 we constructed Q-Q plots of the distribution of the p-values to see if they are
-uniformly distributed. If the distribution of the p-values is uniform, this 
+uniformly distributed. If the distribution of the p-values is uniform, the
+points will be aligned with the diagonal line. This 
 indicates that under the null hypothesis, our method will only reject the $H_0$
-at a rate of $\alpha$.
-A zoomed in plot for probabilities between 0 and 0.1 is
-also provided, as
-that is the most common range for significance levels $\alpha$.
+at the rate of the significance level.
 
@@
 
-\input{tables/rr_100}
+\input{tables/rr_norm}
 
-\input{tables/rr_200}
-
-\input{tables/rr_400}
-
-\input{tables/rr_800}
+\input{tables/rr_gamma}
 
 From Figures~\ref{fig:normal} and \ref{fig:gamma}, we can observe that 
-although the extent to which the p-values appear to be 
-completely aligned with the line
-in the Q-Q plots is dependent on the sample size and the level of serial 
+the extent to which the p-values are uniformly distributed
+is dependent on the sample size and the level of serial 
 dependence.
@@
 Kendall's $\tau \geq 0.75$, a sample larger than $n = 800$ appears to be 
-necessary, as the p-values are not aligned with the line in the Q-Q plots. This
+necessary, as the p-values are not aligned with the line in any of the Q-Q 
+plots. This
 is not necessarily a cause for concern, as (for normal margins)
 a Kendall's $\tau$ corresponds to
-a $\phi$ of 0.924, which is very high. Additionally, performance generally seems
-better for negative $\tau$ values versus positive $\tau$ values of the same
-strength. Results are very similar for normal and gamma margins.
+a $\phi$ of 0.924, which is very high.
+Additionally, positive serial dependence appears to misalign the distribution
+of the p-values moreso than negative serial dependences of the same strength.
+Results are very similar for normal and gamma margins.
 \jy{Summarize findings in bullet points before forming text.}
@@
 For such cases, we can expect the probability
-of a type 1 error to be the significance level $\alpha$.
+of a type 1 error to be approximately equivalent to the significance level.
+
+From Tables~\ref{table:rr_norm} and \ref{table:rr_gamma}, we can observe 
+that the rejection rate is close to the significance level
+as long as 
+Kendall's $\tau$ is less than or equal to 0.5 and a sample size greater
+than 100 is used.
 
@@
   used. Discuss in terms of power: the probability of rejecting $H_0$ when $H_0$
-  is false.}
+  is false.}\mc{addressed}
 to be 1, but we
@@
 marginal distributions to ensure that it is robust.
-We would then expect the distribution of p-values to be non-uniform, and the 
-rate \jy{Does not sound right. What is $\alpha$?}
-of $\#P < \alpha$ to be high, meaning a higher density of low p-values.
+We would then expect the distribution of p-values to be non-uniform -
+specifically a higher density of low p-values - and the 
+rate \jy{Does not sound right. What is $\alpha$?}\mc{addressed}
+of $\#(p_r < 0.05)$ - where 0.05 is the significance level - to be high,
 
 \jy{Description too wordy, Be concise. Basically generate data from one
-  distribution but test for the other distribution.}
-Like we did to see if the test holds its size, we generated time series with 
-marginal distributions $N(8, 8)$ and 
-$\Gamma(8, 1)$, Kendall's $\tau \in \{-.75, -.5, -.25, 0, .25, .5, .75\}$, and
-sample size $n \in \{100, 200, 400, 800\}$. However, 
-to evaluate the test's power, when $X_t \sim N(8, 8)$, we tested
-that the marginal distribution family is from the Gamma family,
-or
-$X_t \sim \Gamma(\cdot \mid \alpha, \beta), \quad t = 1, \ldots, n$.
-for some unspecified $\alpha$ and $\beta$. Because the support of $N(8, 8)$ is
+  distribution but test for the other distribution.}\mc{addressed}
+We generated the same scheme of time series as we did when testing size, but
+tested that the time series was from the other distribution.
+Because the support of $N(8, 8)$ is
 $(-\infty, \infty)$, but the support of $\Gamma(8, 1)$ is $(0, \infty)$, we used
 the \textsl{truncdist} package \citep{truncdist} to truncate the series at 
-values less than or equal to 0.
-When $X_t \sim \Gamma(8, 1)$, we tested that the 
-marginal distribution is from the
-Normal family, or 
-$X_t \sim N(\cdot \mid \mu, \sigma^2), \quad t = 1, \ldots, n$
-for some unspecified $\mu$ and $\sigma$. For the block bootstrap step,
-we used $B = 1000$ and $l = \lceil n^{1/3} \rceil$.
-For each setting for $F$, $\tau$, and $n$, we replicate the method $1000$ times 
+values less than or equal to 0 when testing that $N(8, 8)$ sample was
+from $\Gamma(8, 1)$. For each setting for $F$, $\tau$, and $n$, we replicate the 
+method $1000$ times 
 to obtain a p-value $p_r$ for each $r \in \{1, \ldots, 1000\}$.
@@
 \jy{alpha has been used as gamma parameters. This is not necessary, Just say we
-  checked the power when the significance level is .05.}
-Given some significance level $\alpha$, we can compute a rejection rate 
-$q = \#\{p_r < \alpha\} / 1000$ for $r \in \{1, \ldots, 1000\}$.
+  checked the power when the significance level is .05.}\mc{addressed}
+We can compute a rejection rate 
+$q = \#\{p_r < 0.05\} / 1000$ for $r \in \{1, \ldots, 1000\}$.
 Additionally, we can construct a 95\% confidence interval for 
@@
   structure.}
+\mc{addressed earlier}
 
@@
   google scholar ``stylized facts of daily returns series'' and cite them.}
+\mc{addressed}
 
@@
 0.0368, and \citet{zeimbekakis2022misuses}'s method yields a p-value of 0.03.
-conclusions regarding the marginal distribution of the population under scrutin.
+conclusions regarding the marginal distribution of the population under 
+scrutiny.
 
@@
 are unknown or unspecified. Future studies could investigate
-\jy{Too vague.}
-the method's performance on different marginal distributions and
-different dependence structures. Additionally, one could propose a 
+\jy{Too vague.}\mc{addressed}
+the method's performance on different marginal distributions such
+as the generalized extreme value distribution and
+different dependence structures such as MA, ARMA, and ARIMA processes. Additionally, one could propose a 
 similar method

### 2024-04-23 code/alt_functions.R

@@ -114,9 +114,25 @@ ks.sb <- function(x, B = 1000, q0, f0, df = NULL) {
   rk <- rank(x)
   for (i in 1:B) {
     u <- runif(n)
-    x.b <- q0(sort(u)[rk], df)
+    x.b <- q0(sort(u)[rk], df, mean(x), sd(x))
     ## The ks stat remained the same as the one before sorting
-    stat.b[i] <- ks.test(x.b, f0, df = df)$statistic
+    stat.b[i] <- ks.test(x.b, f0, df = df, mean(x.b), sd(x.b))$statistic
+  }
+  p.value <-  (sum(stat.b >= stat) + 0.5) / (B + 1)
+  list(p.value = p.value,
+       statistic = stat, stat.b = stat.b)
+}
+
+normal.ks.sb <- function(x, B = 1000, q0, f0, df = NULL) {
+  stat <- ks.test(x, f0)$statistic
+  stat.b <- rep(0, B)
+  n <- length(x)
+  rk <- rank(x)
+  for (i in 1:B) {
+    u <- runif(n)
+    x.b <- q0(sort(u)[rk], mean(x), sd(x))
+    ## The ks stat remained the same as the one before sorting
+    stat.b[i] <- ks.test(x.b, f0, mean(x.b), sd(x.b))$statistic
   }
   p.value <-  (sum(stat.b >= stat) + 0.5) / (B + 1)
   list(p.value = p.value,
@@ -124,7 +140,11 @@ ks.sb <- function(x, B = 1000, q0, f0, df = NULL) {
 }
 
 my_sb <- function(x, B = 1000, q0, f0, df = NULL) {
-  ks.sb(x, B = 1000, q0, f0, df = NULL)$p.value
+  if(is.null(df)) {
+    normal.ks.sb(x, B = 1000, q0, f0)$p.value
+  } else {
+    ks.sb(x, B = 1000, q0, f0, df = df)$p.value
+  }
 }
 
 app_scheme <- function(start, end, years, stock) {

### 2024-04-23 code/data_processing2.R

@@ -2,9 +2,9 @@ library(tidyverse)
 library(janitor)
 setwd("../data/simulation")
 
-file_names <- list.files(pattern = "^sim")
+file_names <- list.files(pattern = "^sim2")
 phis <- 
-  c(-0.9238795, -0.7071068, -0.3826834, 0, 0.3826834, 0.7071068, 0.9238795)
+  c(-0.9238795, 0.9238795)
 for (phi in phis) {
   for (n in c(100, 200, 400, 800)) {
     for (dist in c("normal", "gamma")) {
@@ -14,14 +14,14 @@ for (phi in phis) {
       for (file in list) {
         tosave <- c(tosave, readRDS(file)$p)
       }
-      saveRDS(tosave, file = paste("../sim_", n, "_", dist, "_",
+      saveRDS(tosave, file = paste("../sim2_", n, "_", dist, "_",
                                    phi, '_', 
                                    '0', ".RDS", sep = ''))
     }
   }
 }
 
-file_names <- list.files(pattern = "^alt")
+file_names <- list.files(pattern = "^alt2")
 for (phi in phis) {
   for (n in c(100, 200, 400, 800)) {
     for (dist in c("normal", "gamma")) {
@@ -31,7 +31,7 @@ for (phi in phis) {
       for (file in list) {
         tosave <- c(tosave, readRDS(file)$p)
       }
-      saveRDS(tosave, file = paste("../alt_", n, "_", dist, "_",
+      saveRDS(tosave, file = paste("../alt2_", n, "_", dist, "_",
                                    phi, '_', 
                                    '0', ".RDS", sep = ''))
     }
@@ -44,7 +44,7 @@ for (phi in phis) {
     for (dist in c("normal", "gamma")) {
       for(alpha in c(.01, .05, .10)) {
         pvals <- readRDS(
-          paste("../", "sim_", n, "_", dist, "_", phi, "_0", ".RDS", 
+          paste("../", "sim2_", n, "_", dist, "_", phi, "_0", ".RDS", 
                 sep = ''))
         R <- length(pvals)
         if (R <= 0) next
@@ -59,7 +59,7 @@ for (phi in phis) {
   }
 }
 colnames(df) <- c("phi", "n", "dist", "alpha", "rr_lb", "rr", "rr_ub", "R")
[…]

### 2024-04-23 code/plots.R

@@ -11,6 +11,18 @@ plot_p_vals(normal, 'normal.pdf')
 gamma <- df %>% filter(dist == 'gamma')
 plot_p_vals(gamma, 'gamma.pdf')
 
-
-df <- readRDS("../data/rejection_rates.RDS") %>% filter(alpha == 0.05)
+df <- readRDS("../data/alt_rejection_rates.RDS") %>% filter(alpha == 0.05)
 plot_rr(df, 'rr.pdf')
+
+df <- readRDS("../data/pvals2.RDS") %>% 
+  #  filter(phi == -0.2 | phi == 0 | phi == 0.2, n == 400) %>% 
+  mutate(pval = as.numeric(pval))
+
+normal <- df %>% filter(dist == 'normal')
+plot_p_vals(normal, 'normal2.pdf')
+
+gamma <- df %>% filter(dist == 'gamma')
+plot_p_vals(gamma, 'gamma2.pdf')
+
+df <- readRDS("../data/alt_rejection_rates2.RDS") %>% filter(alpha == 0.05)
+plot_rr(df, 'rr2.pdf')

### 2024-04-23 code/sp100.R

@@ -31,8 +31,10 @@ sp100_pval_4y[,3] <- sapply(as.numeric(sp100_pval_4y[,3]), my_format)
 
 sp100_pval_4y[,4] <- sapply(as.numeric(sp100_pval_4y[,4]), my_format)
 
+sp100_pval_4y[,5] <- sapply(as.numeric(sp100_pval_4y[,5]), my_format)
+
 colnames(sp100_pval_4y) <- c("$v$", "Our Method", "Babu's Method",
-                             "Zeimbekakis' Method")
+                             "Zeimbekakis' Method", "Semiparametric Method")
  
 sp100_pval_4y[1, 1] <- "$\\infty$"
 

### 2024-04-23 code/sp500.R

@@ -31,8 +31,10 @@ sp500_pval_4y[,3] <- sapply(as.numeric(sp500_pval_4y[,3]), my_format)
 
 sp500_pval_4y[,4] <- sapply(as.numeric(sp500_pval_4y[,4]), my_format)
 
+sp500_pval_4y[,5] <- sapply(as.numeric(sp500_pval_4y[,5]), my_format)
+
 colnames(sp500_pval_4y) <- c("$v$", "Our Method", "Babu's Method",
-                             "Zeimbekakis' Method")
+                             "Zeimbekakis' Method", "Semiparametric Method")
 
 sp500_pval_4y[1, 1] <- "$\\infty$"
 

### 2024-04-23 code/tables.R

@@ -1,70 +1,50 @@
 library(xtable)
-df <- readRDS("../data/rejection_rates1.RDS") %>% 
+df <- readRDS("../data/sim_rejection_rates.RDS") %>% 
   mutate(rr_lb = round(as.numeric(rr_lb), 3),
          rr = round(as.numeric(rr), 3),
          rr_ub = round(as.numeric(rr_ub), 3))
 
-df_100 <- df %>% 
-  filter(n == 100) %>% 
-  select(-R) %>% 
-  rename(`$\\phi$` = phi, `$n$` = n, distribution = dist, 
-         `$\\alpha$` = alpha, `lower bound` = rr_lb, `rejection rate` = rr, 
-         `upper bound` = rr_ub)
-write(print(xtable(df_100, 
-                   caption = "Rejection rates for test under true null hypothesis
-                   when n = 100 for 
-                   different values of AR(1) coefficient and for different 
-                   significance levels. Lower and upper bounds are also 
-                   included.",
-                   label = "table:rr_100"), caption.placement = "top",
-            sanitize.text.function=function(x){x}), 
-      file = "../manuscript/tables/rr_100.tex")  
+df$tau <- factor(case_when(df$phi == "-0.9238795" ~ "$\\tau = -0.75$",
+                           df$phi == "-0.7071068" ~ "$\\tau = -0.5$",
+                           df$phi == "-0.3826834" ~ "$\\tau = -0.25$",
+                           df$phi == "0" ~ "$\\tau = 0$",
+                           df$phi == "0.9238795" ~ "$\\tau = 0.75$",
+                           df$phi == "0.7071068" ~ "$\\tau = 0.5$",
+                           df$phi == "0.3826834" ~ "$\\tau = 0.25$"),
+                 levels = c("$\\tau = -0.75$",
+                            "$\\tau = -0.5$",
+                            "$\\tau = -0.25$",
+                            "$\\tau = 0$",
+                            "$\\tau = 0.25$",
+                            "$\\tau = 0.5$",
+                            "$\\tau = 0.75$"))
 
-df_200 <- df %>% 
-  filter(n == 200) %>% 
-  select(-R) %>% 
-  rename(`$\\phi$` = phi, `$n$` = n, distribution = dist, 
-         `$\\alpha$` = alpha, `lower bound` = rr_lb, `rejection rate` = rr, 
-         `upper bound` = rr_ub)
-write(print(xtable(df_200, 
-                   caption = "Rejection rates for test under true null hypothesis
-                   when n = 200 for 
[…]

### 2024-04-23 manuscript/manuscript.tex

@@
 
-\jy{State clearly the test statistic definition. Point out that the null
-  distribution depends on the unknown parameters and unknown serial
-  dependence. Point out the challenges are to approximate the null distribution.}
-\mc{addressed in third paragraph of introduction}
-
-We note that
+Because of the estimation uncertainty in $\hat\theta_n$, the asymptotic
+distribution of $Y_n$ is no longer distribution-free. This is in contrast to the
+case where $\theta$ is known.  Note that
 \begin{equation*}
 Y_n(x; \hat\theta) = \sqrt{n}(F_n(x) - F(x)) - 
-\sqrt{n}(F(x; \hat\theta_n) - F(x)),
+\sqrt{n}(F(x; \hat\theta_n) - F(x)).
 \end{equation*}
-\jy{clean up the notations. Has $F$ been defined yet? do you need cdf?}
-\mc{addressed}
-where $F(x)$ is the true cumulative distribution function 
-(under the $H_0: F(x) = F(x; \theta_0)$ for some true
-parameter $\theta_0$.)
+When $\hat\theta_n$ is replaced with $\theta$, as in the standard KS testing
+situation, the second term vanishes, and $T_n$ converges in distribution to that
+of $\sup_t | B(F(t)) |$, where $B(\cdot)$ is the standard Brownian bridge
+\citep{kolmogorov1933sulla}. With $\hat\theta_n$ in place of $\theta$, the
+second term leads to a bias in the Brownian bridge, which was addressed by
+\citet{babu2004goodness}.
+
+When $\{X_t: t = 1, \ldots, n\}$ are further serially dependent, the statistics
+$T_n$ still provides a reasonable metric for deviation from the null
+hypothesis. Nonetheless, the asymptotic distribution of $T_n$ cannot be fixed
+even with the bias correction of \citet{babu2004goodness}, because the
+correction requires independent sample.
+
+>>>>>>> 8ae0002af5827811aa9091e769fc16303007bc1c
 
@@
 After the transformation
-to the marginal gamma distribution, the autocorrelations are $\{-0.884, 
--0.686, -0.389, -0.033, 0.327, 
-\break 0.639, 0.861\}$.
+to the marginal gamma distribution, the autocorrelations are
+\[
+  \{-0.884, -0.686, -0.389, -0.033, 0.327, 0.639, 0.861\}.
+\]
 
@@
 at the rate of the significance level.
-
-\jy{Remove the white space in the pdf figures. Could put the zoomed version in
-  the same figure.}\mc{addressed}
+\jy{Describe the table not zoomed-in figure.}
+A zoomed in plot for probabilities between 0 and 0.1 is
+also provided, as
+that is the most common range for significance levels $\alpha$.
 

### 2024-05-07 manuscript/manuscript.tex
fixed semiparametric

@@
 
-\newcommand{\jy}[1]{\textcolor{blue}{JY: #1}}
+\newcommand{\jy}[1]{\textcolor{blue}{JY: (#1)}}
 \newcommand{\eds}[1]{\textcolor{red}{EDS: (#1)}}
@@
 \title{Nonparametric Block Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test}
-\if0\blind
-{
-  \author{Mathew Chandy, %\\
+  \author{Mathew Chandy %\\
 %   \href{mailto:mathew.chandy@uconn.edu}
 %   {\nolinkurl{mathew.chandy@uconn.edu}}\\
-  Elizabeth Schifano\\
-  Jun Yan\\
-  Xianyang Zhang\\
-} \fi
+%  Elizabeth Schifano\\
+%  Jun Yan\\
+%  Xianyang Zhang\\
+}
 
@@
 correction requires independent sample.
-
->>>>>>> 8ae0002af5827811aa9091e769fc16303007bc1c
 
@@
 at the rate of the significance level.
-\jy{Describe the table not zoomed-in figure.}
-A zoomed in plot for probabilities between 0 and 0.1 is
-also provided, as
-that is the most common range for significance levels $\alpha$.
+\jy{Describe the table not zoomed-in figure.}\mc{addressed}
+A table of the rejection rates for each scheme
+also provided/
 
@@
 Additionally, positive serial dependence appears to misalign the distribution
-of the p-values moreso than negative serial dependences of the same strength.
+of the p-values more so than negative serial dependences of the same strength.
 Results are very similar for normal and gamma margins.
@@
 
-Under $H_0$, the p-values for the non-parametric block bootstrap KS test are
-\jy{The flow doesn't read right from the last paragraph}
-uniformly distributed as long as the serial dependence is not too high. 
-This is an indication that our method 
-holds its size for moderate serial dependence levels.
-For such cases, we can expect the probability
-of a type 1 error to be approximately equivalent to the significance level.
-
 From Tables~\ref{table:rr_norm} and \ref{table:rr_gamma}, we can observe 
-that the rejection rate is close to the significance level
-as long as 
-Kendall's $\tau$ is less than or equal to 0.5 and a sample size greater
-than 100 is used.
+that the agreement between empirical size (rejection rate)
+and nominal size (the
+significance level) improves as sample size increases, but for $\tau = -0.75$
+and $\tau = 0.75$, a sample size larger than 800 seems to be necessary for that 
+agreemet to be reached. Using the criteria of approximate agreement between 
+empirical size and nominal size, we can say that our approach is working 
+for $-0.25 < \tau < 0.25$ for $n > 100$. However a larger sample size seems 
+necessary, greater than 400 perhaps, for $\tau$ as strong as $0.5$. In other
+words, for weaker dependence, our method works without need for a particular
+large sample size, whereas for moderate dependence, a larger sample size may 
+be required. Because $\tau$ is typically less than 0.5, it is still safe to
+recommend our method with a smaller sample size.
 
@@
 significance level 0.05 as the lag-1 Kendall's~$\tau$ increases from
-$-0.9$ to $0.9$. Using a sample size $n \geq 800$ appears to be sufficient
-\jy{What are the findings? summarize bullet points before forming texts.}
-when $\tau$ is not too high, but for $\tau \geq 0.75$, all sample sizes 
-observed appeared to have less than desirable rejection rates. Results
+$-0.5$ to $0.5$. We omitted -0.75 and 0.75 from this study because we already 
+found that our method doesn't work under the null hypothesis for such high
+dependence levels. It appears that rejection rate seems to decline as $\tau$ 
+increases. Using $n \geq 400$ seems to be good enough
+if $\tau < 0.5$, but using a $n \geq 800$ will result in 
+rejection rates close to 1 for $0.5 < \tau < 0.5$.
+Results for $n \geq 400$
 do not appear to be to different when comparing gamma and normal 
@@
 The same analyses were repeated on the daily returns of the S\&P 100 index.
-Our method demonstrates more instances where it reaches
+As shown in Table~\ref{table:SP1004}, 
+our method demonstrates more instances where it reaches
 different conclusions at the 0.05 significance level compared to other methods.

### 2024-05-07 code/alt_functions.R

@@ -4,6 +4,7 @@ library(truncdist)
 library(qqplotr)
 library(copula)
 library(tseries)
+source("ksfitted.R")
 mystat <- function(x, dist, df = NULL) {
   # Bootstrap will return actual pseudo-sample, mean, and standard deviation
   if (dist == 'gev') {

### 2024-05-07 code/functions.R

@@ -185,7 +185,7 @@ plot_rr <- function(df, filename) {
     theme(
           legend.position = "bottom") +
     labs(x = latex2exp::TeX("$\\tau$"), y = latex2exp::TeX("Rejection Rate")) +
-    coord_fixed(ylim = c(0, 1), xlim = c(-1, 1))
+    coord_fixed(ylim = c(0, 1), xlim = c(-0.6, 0.6))
   ggsave(filename = filename, plot = gg.f, path = "../manuscript/figures", 
          height = 3, width = 6)
     

### 2024-05-07 code/ksfitted.R

@@ -1,0 +1,124 @@
+source("tacvfARMA.R")
+##' Distribution Functions with Given Parameters
+##'
+##' Generate a (d, p, q, or r) function of a distribution
+##'
+##' This function creates a function for a distribution with given parameters
+##' and a desired usage (d, p, q, or r).
+##'
+##' @param dist A string specificing the distribution, assuming function names
+##' prefixed with (d, p, q, or r) are available.
+##' @param param A named vector specifying the parameters of the distribution
+##' @param fn A character of `d`, `p`, `q`, or `r` for density, distribution,
+##' quantile, and random number generation.
+##' @return A function with a single argument while other parameters specified
+##' through the input `param`.
+##' 
+getfndist <- function(dist, param, fn) {
+  nm <- names(param); l <- length(param)
+  fun <- get(paste0(fn, dist))
+  f <- formals(fun)
+  args <- names(f)
+  m <- match(nm, args)
+  formals(fun) <- c(f[c(1, m)], f[-c(1, m)])
+  myfun <- function(z) {}
+  body(myfun) <- parse(
+    text = paste("fun(z,", paste0("param[", 1L:l, "]", collapse = ", "), ")"))
+  myfun
+}
+
+
+##' Kolmogorov-Smirnov Tests with Fitted Parameters and Serial Dependence
+##'
+##' Performs a one-sample K-S test with fitted parameters and serial dependence
+##'
+##' This function allows fitted parameters through maximim likelihood when
+##' performing K-S test for commonly used distributions via parametric
+##' bootstrap. Serial dependence in allowed and preserved in bootstrap by a
+##' auto-selected working ARMA model for the residuals on the normal scale.
+##' 
+##' @param x a numeric vector of data values.
+##' @param dist a string of the name of the hypothesized distribution
+##' @param B number of bootstrap replicates
+##' @param fit if TRUE, test performed at the fitted parameter
+##' @param serial if TRUE, account for serial dependence via an auto-selected
+##' working ARMA model
+##' @param param a named vector for the hypothesized distribution. If fit ==
+##' TRUE, it will be used as the starting value for fitting
[…]

### 2024-05-07 code/plots.R

@@ -11,7 +11,8 @@ plot_p_vals(normal, 'normal.pdf')
 gamma <- df %>% filter(dist == 'gamma')
 plot_p_vals(gamma, 'gamma.pdf')
 
-df <- readRDS("../data/alt_rejection_rates.RDS") %>% filter(alpha == 0.05)
+df <- readRDS("../data/alt_rejection_rates.RDS") %>% filter(alpha == 0.05) %>% 
+  filter(phi != "-0.9238795", phi != "0.9238795")
 plot_rr(df, 'rr.pdf')
 
 df <- readRDS("../data/pvals2.RDS") %>% 

### 2024-05-07 code/sp100.R

@@ -1,5 +1,6 @@
 source("functions.R")
 source("alt_functions.R")
+source("ksfitted.R")
 library(forecast)
 library(tseries)
 library(extraDistr)
@@ -18,6 +19,7 @@ sp100_pval_4y <- app_scheme("2020-01-01", "2023-12-31", 4, "^sp100")
 #sp100_df <- t(rbind(sp100_pval_1y, sp100_pval_2y, sp100_pval_3y, sp100_pval_4y, 
 #                    sp100_pval_5y
 #))
+options(scipen = 999)
 
 saveRDS(sp100_pval_4y, "../data/sp100_pval_4y")
 
@@ -38,6 +40,31 @@ colnames(sp100_pval_4y) <- c("$v$", "Our Method", "Babu's Method",
  
 sp100_pval_4y[1, 1] <- "$\\infty$"
 
+
+
+series <- 
+  diff(log(get.hist.quote(instrument = "^sp100", start = "2020-01-01",
+                          end = "2023-12-31")))
+
+series <- as.vector(series[, "Close"])
+#  fit <- auto.arima(as.vector(series[, "Close"]))
+#  resid <- residuals(fit)
+
+resid <- series
+
+set.seed(123)
+semi <- ks.test.fitted(resid, "norm", B = 10000, serial = TRUE, 
+                       param = c(mean = 0, sd = 1))$p.value
+
+for (v in c(30, 20, 10, 5, 4, 3, 2, 1)) {
+  set.seed(123)
+  semi <- c(semi, 
+            ks.test.fitted.lst(resid, "lst", B = 10000, serial = TRUE, 
+                       param = c(mu = 0, sigma = 1), df = v)$p.value)
+}
+
+sp100_pval_4y[,5] <- semi
+
 write(print(xtable(sp100_pval_4y,
                    caption = "P-values for 4 years of S\\&P 100 stock return 
                    data using different durations
@@ -47,5 +74,7 @@ write(print(xtable(sp100_pval_4y,
 ), caption.placement = "top", sanitize.text.function=function(x){x},
 include.rownames = FALSE), 
 file = "../manuscript/tables/sp100_pval_4y.tex")
+
+
 
 

### 2024-05-07 code/tacvfARMA.R

@@ -1,0 +1,71 @@
+##' True Auto-Covariance Function of an ARMA Process
+##'
+##' Produces the true auto-covariance of an ARMA process up to certain lag
+##'
+##' This function is a minorly modified version of the tacvfARMA function from
+##' package ltsa, with a bug fixed. An email was sent to the package maintainer
+##' Dr. A. I. McLeod. This function wouldn't be needed if the bug is fixed in the package.
+##'
+##' @note:
+##' The MA (theta) part is of opposite sign of the stats::arima.sim function
+##' 
+tacvfARMA.my <- function (phi = numeric(0), theta = numeric(0), maxLag = 1, sigma2 = 1) 
+{
+  stopifnot(maxLag >= 0, sigma2 > 0)
+  p <- length(phi)
+  if (p > 0) {
+    pi = numeric(p)
+    phik <- phi
+    for (k in 1:p) {
+      L <- p + 1 - k
+      a <- phik[L]
+      pi[L + 1 - k] <- a
+      phikp1 <- phik[-L]
+      if (is.na(a) || abs(a) == 1) 
+        stop("error: roots outside unit circle -- nonstationary/noncausal model")
+      phik <- (phikp1 + a * rev(phikp1))/(1 - a^2)
+    }
+    if (!all(abs(pi) < 1)) 
+      stop("error: roots outside unit circle -- nonstationary/noncausal model")
+  }
+  q <- length(theta)
+  if (max(p, q) == 0) 
+    return(c(sigma2, numeric(maxLag))) ## was maxLagp1; by JY
+  maxLagp1 <- maxLag + 1
+  r <- max(p, q) + 1
+  b <- numeric(r)
+  C <- numeric(q + 1)
+  C[1] <- 1
+  theta2 <- c(-1, theta)
+  phi2 <- numeric(3 * r)
+  phi2[r] <- -1
+  if (p > 0) 
+    phi2[r + 1:p] <- phi
+  if (q > 0) 
+    for (k in 1:q) {
+      C[k + 1] <- -theta[k]
+      if (p > 0) 
+        for (i in 1:min(p, k)) C[k + 1] <- C[k + 1] + 
+            phi[i] * C[k + 1 - i]
+    }
+  for (k in 0:q) for (i in k:q) b[k + 1] <- b[k + 1] - theta2[i + 
+                                                                1] * C[i - k + 1]
+  if (p == 0) 
+    g <- c(b, numeric(maxLagp1))[1:maxLagp1]
[…]

### 2024-05-07 manuscript/manuscript.tex
addressed some things

@@
 marginal distributions to ensure that it is robust.
-We would then expect the distribution of p-values to be non-uniform -
-specifically a higher density of low p-values - and the 
-rate \jy{Does not sound right. What is $\alpha$?}\mc{addressed}
-of $\#(p_r < 0.05)$ - where 0.05 is the significance level - to be high,
 
@@
 We can compute a rejection rate 
-$q = \#\{p_r < 0.05\} / 1000$ for $r \in \{1, \ldots, 1000\}$.
+at a nominal significance level of 0.05.
 Additionally, we can construct a 95\% confidence interval for 
@@
 to December 31st, 2023. Daily returns were obtained by taking the difference in
-the logarithm of the closing prices.
+the logarithm of the closing prices. The Kendall's $\tau$ for the series
+was about -0.0298, indicating a very slight serial dependence.
 Using our method, we tested that the daily returns are normally
@@
 
-\input{tables/sp100_pval_4y}
-
 \jy{Stock returns are known to be serially dependent and heavy-tailed. Search
@@
 index.
-
-The same analyses were repeated on the daily returns of the S\&P 100 index.
-As shown in Table~\ref{table:SP1004}, 
-our method demonstrates more instances where it reaches
-different conclusions at the 0.05 significance level compared to other methods.
-Our method does not reject the hypothesis that the series conforms to a
-Student's $t$ distribution with degrees of freedom $v = 5$, yielding a p-value
-of 0.0873. In contrast, \citet{babu2004goodness}'s method yields a p-value of 
-0.0368, and \citet{zeimbekakis2022misuses}'s method yields a p-value of 0.03.
-conclusions regarding the marginal distribution of the population under 
-scrutiny.
 

### 2024-05-07 code/sp100.R

@@ -65,6 +65,21 @@ for (v in c(30, 20, 10, 5, 4, 3, 2, 1)) {
 
 sp100_pval_4y[,5] <- semi
 
+non <- sp100_pval_4y[,3]
+
+param <- sp100_pval_4y[,4]
+
+sp100_pval_4y[,3] <- sp100_pval_4y[,5]
+
+sp100_pval_4y[,4] <- non
+
+sp100_pval_4y[,5] <- param
+
+colnames(sp100_pval_4y) <- c("$v$", "Our Method", "Semiparametric Method",
+                             "Nonparametric Method", "Parametric Method")
+
+saveRDS(sp100_pval_4y, "../data/sp100_pval_4y")
+
 write(print(xtable(sp100_pval_4y,
                    caption = "P-values for 4 years of S\\&P 100 stock return 
                    data using different durations

### 2024-05-08 manuscript/manuscript.tex
quick run through

@@
 correction, has not been studied. Addressing this gap, our study introduces a
-bias correction method employing a non-parametric block bootstrap, which
+bias correction method employing a nonparametric block bootstrap, which
 approximates the distribution of the KS statistic accounting for unspecified
@@
 our method is further illustrated with an examination of stock returns from the 
-S\&P 100 and S\&P 500 indices, showcasing its utility in real-world
+S\&P 500 index, showcasing its utility in real-world
 applications.
@@
 Alternatively, \citet{babu2004goodness} address this issue through a
-non-parametric bootstrap method that corrects the bias in the asymptotic null
+nonparametric bootstrap method that corrects the bias in the asymptotic null
 distribution.
@@
 and the challenge is to approximate said distribution.
-\citet{zeimbekakis2022misuses} proposed a semi-parametric bootstrap
+\citet{zeimbekakis2022misuses} proposed a semiparametric bootstrap
 where the serial dependence structure is modeled via a working serial copula.
+
 A particularly complex scenario arises when the distribution has unspecified
 parameters, and the data are serially dependent. For this,
-\citet{zeimbekakis2022misuses} also recommends a semi-parametric bootstrap
+\citet{zeimbekakis2022misuses} also recommends a semiparametric bootstrap
 approach, where the parameters of the hypothesized distribution and the serial
@@
 but this could affect results if the estimated serial
-dependence is too far from the truth. For this reason, a non-parametric method
+dependence is too far from the truth. For this reason, a nonparametric method
 is motivated.
 
-Developing a fully non-parametric solution for the KS 
+Developing a fully nonparametric solution for the KS 
 tests in the presence of serially dependent data presents a significant 
@@
 the structure of the serial dependence, which can vary widely in practical 
-situations. Employing a non-parametric bootstrap would necessitate defining a 
+situations. Employing a nonparametric bootstrap would necessitate defining a 
 specific model for this dependence, despite the primary focus being on 
 evaluating the marginal distribution of a stationary series. To date, a bias 
-correction method for block bootstrap, akin to the non-parametric bootstrap
+correction method for block bootstrap, akin to the nonparametric bootstrap
 approach of \citet{babu2004goodness} for independent data,
@@
 to bridge this gap by introducing a bias correction technique for the 
-non-parametric block bootstrap, tailored for use in scenarios where the 
-hypothesized distribution includes unspecified parameters and the data 
+nonparametric block bootstrap, tailored for use in scenarios where the 
+hypothesized distribution has unspecified parameters and the data 
 exhibit serial dependence. Our approach reduces to that of
@@
 procedure and introduces the bias correction methodology for the 
-non-parametric block bootstrap KS test. Section~\ref{sec:simu} is divided 
+nonparametric block bootstrap KS test. Section~\ref{sec:simu} is divided 
 into two parts; initially, we evaluate the KS test's ability to maintain 
@@
 applications of our method are presented in Section~\ref{sec:real}, where 
-we apply the approach to analyze if S\&P 100 and S\&P 500 index stock return
-data adhere to either the Normal or the Student's $t$ distribution. The 
+we apply the approach to analyze if S\&P 500 index stock return
+data adheres to either the Normal or the Student's $t$ distribution. The 
 paper concludes with Section~\ref{sec:conclusion}, offering final thoughts 
@@
 
-\subsection{Non-Parametric Bootstrap for Independent Data}
+\subsection{Nonparametric Bootstrap for Independent Data}
 
@@
 
-\subsection{Non-Parametric Block Bootstrap for Stationary Series}
+\subsection{Nonparametric Block Bootstrap for Stationary Series}
 
@@
 A table of the rejection rates for each scheme
-also provided/
+also provided.
 
@@
 for $-0.25 < \tau < 0.25$ for $n > 100$. However a larger sample size seems 
-necessary, greater than 400 perhaps, for $\tau$ as strong as $0.5$. In other
-words, for weaker dependence, our method works without need for a particular
+necessary, greater than 400 perhaps, for $\tau$ as strong as $0.5$. To 
+summarize, for weaker dependence, our method works without need for a 
+particularly
 large sample size, whereas for moderate dependence, a larger sample size may 
-be required. Because $\tau$ is typically less than 0.5, it is still safe to
+be required. Because $\tau$ is typically less than 0.5, it is still reasonable
+to
 recommend our method with a smaller sample size.
@@
 with degrees of freedom $v \in \{30, 20, 10, 5, 4, 3, 2, 1\}$.
-We tested the same hypotheses using \citet{babu2004goodness}'s 
-non-parametric basic bootstrap bias correction and 
-\citet{zeimbekakis2022misuses}'s parametric bootstrap method.
+We tested the same hypotheses using 1) the
+semiparametric bootstrap method shown by \citet{zeimbekakis2022misuses} which 
+accounts for both serial dependence and unspecified parameters, 2)
+nonparametric basic bootstrap bias correction developed by 
+\citet{babu2004goodness}, and 3) the parametric bootstrap method shown
+by \citet{zeimbekakis2022misuses}.
 We used $B = 10,000$ bootstrap 
@@
 hypothesis that the series follows a Student's $t$ distribution with degrees of
-freedom $v = 5$ with a p-value of 0.061. In contrast, Babu and Sen's method
-yields a p-value of 0.0222, and Zeimbekakis et al.'s method yields a p-value of
+freedom $v = 5$ with a p-value of 0.061. In contrast, 
+the semiparametric method yields a p-value of 0.0192,
+the basic nonparametric method
+yields a p-value of 0.0222, and the parametric method yields a p-value of
 0.0141. Although such differences are not guaranteed, this
@@
 Using simulation, we have shown that given a large enough sample of a time 
-series, the block 
+series and if the serial dependence is not too extreme, the block 
 bootstrap KS test can appropriately fail to reject the null hypothesis when the
@@
 demonstrated possible applications of this method to financial data.
-Through comparison with the non-parametric
+Through comparison with the nonparametric
 bootstrap bias correction developed by \citet{babu2004goodness}
-and the parametric
-bootstrap method developed by \citet{zeimbekakis2022misuses}, we have 
+and the parametric and semiparametric
+bootstrap methods developed by \citet{zeimbekakis2022misuses}, we have 
 underscored the importance of accounting for serial

### 2024-05-08 code/sp500.R

@@ -75,8 +75,8 @@ sp500_pval_4y[,4] <- non
 
 sp500_pval_4y[,5] <- param
 
-colnames(sp500_pval_4y) <- c("$v$", "Our Method", "Semiparametric Method",
-                             "Nonparametric Method", "Parametric Method")
+colnames(sp500_pval_4y) <- c("$v$", "Nonparametric Block", "Semiparametric",
+                             "Nonparametric Basic", "Parametric")
 
 saveRDS(sp500_pval_4y, "../data/sp500_pval_4y")
 

### 2024-05-08 manuscript/manuscript.tex
edits/comments on simulation

@@
 \documentclass[12pt, titlepage, letterpaper]{article}
-%\documentclass[12pt, letterpaper, titlepage]{article}
 
@@
 \usepackage{setspace}
+\allowdisplaybreaks
 
@@
 \title{Nonparametric Block Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test}
-  \author{Mathew Chandy %\\
+  \author{Mathew Chandy \\
   % \href{mailto:mathew.chandy@uconn.edu}
   % {\nolinkurl{mathew.chandy@uconn.edu}}\\
-%  Elizabeth Schifano\\
-%  Jun Yan\\
-%  Xianyang Zhang\\
+ Elizabeth Schifano\\
+ Jun Yan\\
+ Xianyang Zhang
 }
@@
 dependence when applying the two-sample KS test.
-The distribution of the test statistic under
-the null hypothesis depends on the unknown parameters and unknown 
-serial dependence. Therefore, the null distribution under dependence cannot be
-used,
-and the challenge is to approximate said distribution.
-\citet{zeimbekakis2022misuses} proposed a semiparametric bootstrap
-where the serial dependence structure is modeled via a working serial copula.
-
 A particularly complex scenario arises when the distribution has unspecified
-parameters, and the data are serially dependent. For this,
-\citet{zeimbekakis2022misuses} also recommends a semiparametric bootstrap
+parameters, and the data are serially dependent.
+The distribution of the test statistic under the null hypothesis depends on both
+the unknown parameters and unknown serial dependence. 
+\citet{zeimbekakis2022misuses} recommend a semiparametric bootstrap
 approach, where the parameters of the hypothesized distribution and the serial
-dependence both need to be estimated and their uncertainty accounted for,
-but this could affect results if the estimated serial
-dependence is too far from the truth. For this reason, a nonparametric method
-is motivated.
+dependence both need to be estimated and their uncertainty accounted for.
+Nonetheless, if the working dependence model is too far from the truth, the
+results of the tests would not be reliable. For this reason, a nonparametric
+method that does not specify the serial dependence is desired.
 
@@
 \begin{equation*}
-Y_n(x; \hat\theta) = \sqrt{n}(F_n(x) - F(x; \hat\theta_n)).
+Y_n(x; \hat\theta_n) = \sqrt{n}(F_n(x) - F(x; \hat\theta_n)).
 \end{equation*}
@@
 \begin{equation*}
-T_n := \sup_x|Y_n(x; \hat\theta)|.
+T_n := \sup_x|Y_n(x; \hat\theta_n)|.
 \end{equation*}
@@
 under the null distribution, our test rejects the null hypothesis ($H_0$) 
-approximately at the specified significance level. Secondly, we aim to
-illustrate that under the alternate distribution, our test reliably rejects
-$H_0$ at a high frequency. The fulfillment of both these criteria would indicate
+approximately at the specified size or significance level. Secondly, we aim to
+illustrate that under the alternate distribution, our test rejects
+$H_0$ with substantial power. The fulfillment of both criteria would indicate
 the method's efficacy.
@@
 \subsection{Size}
-We first must evaluate whether this method works when $H_0$ is true. To
-test this, we can
-generate a simulated sample $X_t$ with a certain marginal distribution 
-$F_\theta$,
-and use our method to test if $X_t$ indeed has the marginal distribution $F$ 
-with some unknown $\theta$. If the test holds its size, the 
-p-value
-of the test should be uniformly distributed between 0 and 1. We must try the
+To assess the actual size of the test, our strategy is to
+generate a large number of stationary time series $X_t$ with a certain marginal
+distribution $F(\cdot; \theta)$, and for each time series, use our method to
+test if $X_t$ follows a hypothesized marginal distribution $F(\cdot; \theta)$
+with some unknown $\theta$. If the test holds its size, the p-value
+of the test should be uniformly distributed between 0 and 1. We will validate
 method with different marginal distributions to ensure that it is robust.
-In order for the method to work, a large sample size may be necessary.
+In order for the method to work, a large number of replicates is necessary.
 
 We generated time series with marginal distributions $N(8, 8)$ and
-$\Gamma(8, 1)$ with Kendall's
+$\Gamma(8, 1)$ with seven levels of Kendall's
 $\tau \in \{-.75, -.5, -.25, 0, .25, .5, 75\}$, and
 sample size $n \in \{100, 200, 400, 800\}$. Kendall's $\tau$ was chosen as a
-measure of serial dependence as it does not vary between two different 
-marginal distributions.
-To generate the samples to which our
+measure of serial dependence as it is invariant to monotone marginal
+transformations. To generate the samples to which our
 method would be applied, we simulated a time series $W_t$ from a 1st 
-order autoregressive (AR(1)) process:
+order autoregressive or AR(1) process:
 \begin{equation*}
@@
 independent errors from a normal distribution with mean zero and variance
+\jy{What was the value of $\sigma_\epsilon$?}
 $\sigma_{\epsilon}^2$. The strength of the serial dependence is controlled by
@@
 \end{equation*}
-\jy{The language issues are more than I expected. Please do a careful proofread,
-  now that you are more experienced.}
 where $F^{-1}(p)$ is the quantile function for the $N(8, 8)$ 
@@
 After the transformation
-to the marginal gamma distribution, the autocorrelations are
+to the marginal gamma distribution, the lag-1 autocorrelations are
 \[
@@
 
-Using R packages \textsl{qqplotr} and \textsl{ggplot2} \citep{qqplotr, ggplot2},
-we constructed Q-Q plots of the distribution of the p-values to see if they are
-uniformly distributed. If the distribution of the p-values is uniform, the
-points will be aligned with the diagonal line. This 
-indicates that under the null hypothesis, our method will only reject the $H_0$
-at the rate of the significance level.
-\jy{Describe the table not zoomed-in figure.}\mc{addressed}
-A table of the rejection rates for each scheme
-also provided.
-
 \begin{figure}[tbp]
@@
   \includegraphics[width = \textwidth]{figures/normal}
-  \caption{A Q-Q plot of the p-values testing that a distribution
-  generated from a $N(8,8)$ data generating process is normal.}
+  \includegraphics[width = \textwidth]{figures/gamma}
+  \caption{Q-Q plots of the p-values testing that a time series
+    have marginal normal distribution with true data generating distribution
+    being $N(8,8)$ (upper) and marginal gamma distribution with true data
+    generating distribution $\Gamma(8,1)$ (lower)}
   \label{fig:normal}
@@
 
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[scale=1]{figures/gamma}
-  \caption{A Q-Q plot of the p-values testing that a distribution
-  generated from a $\gamma(8,1)$ data generating process is gamma distributed.}
-  \label{fig:gamma}
-\end{figure}
-
-\input{tables/rr_norm}
-
-\input{tables/rr_gamma}
-
-From Figures~\ref{fig:normal} and \ref{fig:gamma}, we can observe that 
-the extent to which the p-values are uniformly distributed
-is dependent on the sample size and the level of serial 
+Figure~\ref{fig:qq} shows the Quantile-Quantile (Q-Q)
+plots of the p-values testing the marginal distribution of the stationary time
+series generated from the null hypothesis, created with R packages
+\textsl{qqplotr} and \textsl{ggplot2} \citep{qqplotr, ggplot2}. If the
+distribution of the p-values is uniform, the points will be aligned with the
+diagonal line. The plots suggest that the extent to which the p-values are
+uniformly distributed is dependent on the sample size and the level of serial 
 dependence.
@@
 Results are very similar for normal and gamma margins.
-\jy{Summarize findings in bullet points before forming text.}
 
-From Tables~\ref{table:rr_norm} and \ref{table:rr_gamma}, we can observe 
-that the agreement between empirical size (rejection rate)
-and nominal size (the
-significance level) improves as sample size increases, but for $\tau = -0.75$
-and $\tau = 0.75$, a sample size larger than 800 seems to be necessary for that 
-agreemet to be reached. Using the criteria of approximate agreement between 
-empirical size and nominal size, we can say that our approach is working 
-for $-0.25 < \tau < 0.25$ for $n > 100$. However a larger sample size seems 
+\input{tables/rr_norm}
+
+\input{tables/rr_gamma}
+
+\jy{merge the two tables; use bottomrule and toprule instead of hline;
+  put them in this file instead of inputing.}
+
+For a closer scrutiny on whether the test holds its size at commonly used
+significance levels 0.01, 0.05, and 0.10, Table~\ref{table:size}
+summarizes the empirical sizes of the tests based on 1000 replicates.
+The agreement between the empirical sizes and the nominal size
+improves as sample size increases, as expected. For $\tau = -0.75$
+and $\tau = 0.75$, a sample size as large as 800 is still not sufficient for the
+agreemet to be reached. For weaker dependence levels, our approach is working
+for $-0.25 < \tau < 0.25$ for $n = 100$. However, a larger sample size seems 
 necessary, greater than 400 perhaps, for $\tau$ as strong as $0.5$. To 
 summarize, for weaker dependence, our method works without need for a 
-particularly
-large sample size, whereas for moderate dependence, a larger sample size may 
-be required. Because $\tau$ is typically less than 0.5, it is still reasonable
-to
-recommend our method with a smaller sample size.
+particularly large sample size, whereas for moderate dependence, a larger sample
+size is required. For practical situations with a $\tau$ of magnitude 0.5 or
+lower, it is still reasonable to recommend our method with $n \ge 400$.
 
@@
 The power of the proposed test is investigated with data generated from
-distributions that are not in the hypothesized distribution family. If the test
-is indeed powerful, we would ideally want the probability of
-rejecting $H_0$ when $H_0$ is false\jy{beta has been
-  used. Discuss in terms of power: the probability of rejecting $H_0$ when $H_0$
-  is false.}\mc{addressed}
-to be 1, but we
-expect it to be generally high. Again, we must try the method with different
-marginal distributions to ensure that it is robust.
-
-\jy{Description too wordy, Be concise. Basically generate data from one
-  distribution but test for the other distribution.}\mc{addressed}
-We generated the same scheme of time series as we did when testing size, but
-tested that the time series was from the other distribution.
+distributions that are not in the hypothesized distribution family. 
+We generated the same scheme of time series as we did in the size investigation,
+but tested that the time series was from the other distribution.
 Because the support of $N(8, 8)$ is
@@
 to obtain a p-value $p_r$ for each $r \in \{1, \ldots, 1000\}$.
-
-\jy{alpha has been used as gamma parameters. This is not necessary, Just say we
-  checked the power when the significance level is .05.}\mc{addressed}
-We can compute a rejection rate 
-at a nominal significance level of 0.05.
-Additionally, we can construct a 95\% confidence interval for 
-this rate. Below are tables containing rejection rates showcasing the 
-differences when simulation settings are changed.
+The empirical rejection rates were obtained at a nominal significance level 0.05.
+Additionally, we constructed 95\% confidence intervals the actual rejection
+rejection rate.
 
@@
   \includegraphics[scale=1]{figures/rr}
-  \caption{A plot of the rejection rates as a function of $\tau$ for
+  \caption{Power curve as a function of $\tau$ for
     $n \in \{100, 200, 400, 800\}$ and marginal distribution 
- $\in \{N(8,8), \Gamma(8,1)\}$.}
+    $\in \{N(8,8), \Gamma(8,1)\}$.\jy{clarify the data generating distribution and the
+      hypothesized distribution}
+  }
   \label{fig:rr}
@@
 dependence levels. It appears that rejection rate seems to decline as $\tau$
+\jy{comment on the asymmetry of the power in response to tau.}
 increases. Using $n \geq 400$ seems to be good enough
@@
 high (almost 1), indicating that under $H_A$, the test is very powerful 
-(low probability of failed rejection $\beta$) when a large enough
-sample size is used.
+when a large enough sample size is used.
 
@@
 
-\jy{Put them into one table; add results for paremetric bootstrap with
-  Zeimbakakis' approach with serial dependence accounted for; label the methods
-  as serial dependence accounted for and not accounted for, two methods
-  (parametric and nonparametric) under each.}
-
-\jy{Discuss the difference between the semiparametric bootstrap and the proposed
-  nonparametric bootstrap. The semiparametric method depends on a working copula
-  model for the serial dependence. If that is severely misspecified, I'd expect
-  poor performance. The proposed method does not need to specify that dependence
-  structure.}
-\mc{addressed earlier}
-
 \input{tables/sp500_pval_4y}
-
-\jy{Stock returns are known to be serially dependent and heavy-tailed. Search
-  google scholar ``stylized facts of daily returns series'' and cite them.}
-\mc{addressed}
 
@@
 are unknown or unspecified. Future studies could investigate
-\jy{Too vague.}\mc{addressed}
 the method's performance on different marginal distributions such
 as the generalized extreme value distribution and
-different dependence structures such as MA, ARMA, and ARIMA processes. Additionally, one could propose a 
-similar method
+different dependence structures such as MA, ARMA, and ARIMA
+processes. Additionally, one could propose a similar method
 for comparing two serially dependent methods. One could also apply the method
-showcased
-in this paper to fields like earthquake prediction and astronomy.
+showcased in this paper to fields like earthquake prediction and astronomy.
 
-\jy{summarize remarks in bullet points first. Let's talk on Tuesday.}
+\jy{QC bib entries: page numbers missing for some journal articles.}
 

### 2024-05-08 manuscript/manuscript.tex
application and conclusion section

@@
 
-The Kolmogorov-Smirnov (KS) test is a widely used statistical test that
+The Kolmogorov--Smirnov (KS) test is a widely used statistical test that
 assesses the conformity of a sample to a specified distribution. Its efficacy,
@@
 
-The standard one-sample Kolmogorov-Smirnov (KS) test is widely
+The standard one-sample Kolmogorov--Smirnov (KS) test is widely
 recognized as an effective good-of-fit test for continuous distributions.
@@
   \centering
-  \includegraphics[width = \textwidth]{figures/normal}
-  \includegraphics[width = \textwidth]{figures/gamma}
+  \includegraphics[width = .9\textwidth]{figures/normal}
+  \includegraphics[width = .9\textwidth]{figures/gamma}
   \caption{Q-Q plots of the p-values testing that a time series
@@
     generating distribution $\Gamma(8,1)$ (lower)}
-  \label{fig:normal}
+  \label{fig:qq}
 \end{figure}
@@
 to December 31st, 2023. Daily returns were obtained by taking the difference in
-the logarithm of the closing prices. The Kendall's $\tau$ for the series
-was about -0.0298, indicating a very slight serial dependence.
+the logarithm of the closing prices. 
+It is known as stylized facts that daily return series often exhibts nonlinear
+dependence and unconditional heavy tails \citep[e.g.,][]{ryden1998stylized,
+  cont2001empirical}. The Kendall's $\tau$ for the series is
+was about $-0.0298$, indicating a fairly weak serial linear correlation, but
+certainly not meaning absence of serial dependence.
 Using our method, we tested that the daily returns are normally
 distributed and Student's $t$ distributed 
-with degrees of freedom $v \in \{30, 20, 10, 5, 4, 3, 2, 1\}$.
-We tested the same hypotheses using 1) the
-semiparametric bootstrap method shown by \citet{zeimbekakis2022misuses} which 
-accounts for both serial dependence and unspecified parameters, 2)
-nonparametric basic bootstrap bias correction developed by 
-\citet{babu2004goodness}, and 3) the parametric bootstrap method shown
-by \citet{zeimbekakis2022misuses}.
-We used $B = 10,000$ bootstrap 
-replicates in this analysis.
-The p-values for these tests are highlighted in 
+with degrees of freedom $\nu \in \{30, 20, 10, 5, 4, 3, 2, 1\}$
+with the proposed nonparametric block bootstrap (NPBB) method.
+For comparison, we tested the same hypotheses using 1) the
+semiparametric bootstrap (SPB) method of \citet{zeimbekakis2022misuses},
+which accounts for both serial dependence and unspecified parameters;
+2) nonparametric bootstrap (NPB) bias correction method of
+\citet{babu2004goodness}; and and 3) the parametric bootstrap (PB) method shown
+by \citet{zeimbekakis2022misuses}. The latter of the two methods discard the
+serial dependence. In all methods, we used $B = 10,000$ bootstrap replicates.
+The p-values for these tests are summarized in 
 Table~\ref{table:SP5004}.
 
-\input{tables/sp500_pval_4y}
+\begin{table}[ht]
+\centering
+\caption{P-values for 4 years of S\&P 500 stock return 
+  data using different durations
+  and different degrees of freedom for Student's $t$ distribution.
+  NPBB: nonparametric block bootstrap;
+  SPB: semiparametric bootstrap;
+  NPB: nonparametric bootstrap;
+  PB: parametric bootstrap.} 
+\label{table:SP5004}
+\begin{tabular}{ccccc}
+  \toprule
+$\nu$ & NPBB & SPB & NPB & PB\\ 
+  \midrule
+$\infty$ & 0.0001 & 0.0000 & 0.0000 & 0.0000 \\ 
+  30 & 0.0019 & 0.0000 & 0.0000 & 0.0000 \\ 
+  20 & 0.0027 & 0.0000 & 0.0000 & 0.0000 \\ 
+  10 & 0.0125 & 0.0002 & 0.0003 & 0.0003 \\ 
+  5 & 0.0610 & 0.0192 & 0.0222 & 0.0141 \\ 
+  4 & 0.1037 & 0.0733 & 0.0574 & 0.0499 \\ 
+  3 & 0.3133 & 0.3000 & 0.2759 & 0.2686 \\ 
+  2 & 0.0418 & 0.0461 & 0.0377 & 0.0443 \\ 
+  1 & 0.0000 & 0.0000 & 0.0000 & 0.0000 \\ 
+  \bottomrule
+\end{tabular}
+\end{table}
 
 While differences in p-values among different methods are expected, our analysis
-reveals numerous instances where conclusions at the 0.05 significance level
+reveals some instances where conclusions at the 0.05 significance level
 using our method differ from those obtained using the methods proposed by
 \citet{babu2004goodness} and \citet{zeimbekakis2022misuses}.
-For example, when assessing the S\&P 500 series, our method fails to reject the
+For example, our NPBB method fails to reject the
 hypothesis that the series follows a Student's $t$ distribution with degrees of
 freedom $v = 5$ with a p-value of 0.061. In contrast, 
-the semiparametric method yields a p-value of 0.0192,
-the basic nonparametric method
-yields a p-value of 0.0222, and the parametric method yields a p-value of
+the SPB method yields a p-value of 0.0192,
+the NPB method yields a p-value of 0.0222, and the PB yields a p-value of
 0.0141. Although such differences are not guaranteed, this
 instance highlights a disagreement in conclusions among methods for the S\&P 500
-index.
+index. Because NPB and PB both discard serial dependence, it is expected that
+their conclusions could be different from our method. It is worth noting that
+the SPB result is also not reliable here because the working dependence model is
+in the class of ARMA dependence as specified in \citet{zeimbekakis2022misuses},
+which does not cover nonlinear dependence usually captured by autoregressive
+conditional heteroskedasticity \citep{engle1995arch}. The proposed method has
+no need to specify the serial dependence and, hence, produces results under
+weakest assumptions.
 
-\section{Concluding Remarks}
+\section{Conclusion}
 \label{sec:conclusion}
 
-The Kolmogorov-Smirnov test stands as a crucial tool for researchers across
-diverse fields, enabling comparisons of population distributions. This paper
-introduces a variant of the test tailored for serially dependent data without
-necessitating parameter specification.
-Using simulation, we have shown that given a large enough sample of a time 
-series and if the serial dependence is not too extreme, the block 
-bootstrap KS test can appropriately fail to reject the null hypothesis when the
-series follows the null distribution. In addition, when the marginal
-distribution is not
-the one hypothesized, the test is powerful. Notably, it demands a larger sample
-size compared to basic bootstrap methods to avoid both type I and type II 
-errors. Unsurprisingly,
-the method performs better as the temporal dependence gets weaker. Through
-simulation studies with Normal and Gamma-distributed data, we have shown that
-that the method is robust.
+The KS test remains a crucial tool for researchers across diverse fields,
+enabling critical assessments of population distributions. We introduced a
+nonparametric block bootstrap variant of the KS test tailored for data with
+serial dependencies, which eliminates the need for explicit modeling serial
+dependence in addition to parameter specification within the hypothesized
+distribution. Our simulations have demonstrated that, given
+sufficiently large samples of time series data and moderate serial dependencies,
+the test maintains its size under the null hypothesis and have considerable
+power in detecting deviations from the hypothesized marginal distribution. The
+method's performance improves as the strength of temporal dependence decreases
+or the sample size increases. For moderate serial dependence levels in practice,
+the test can be recommended for sample size~$n = 400$ or higher.
+Overall, the test provides an analog of the bias-corrected nonparametric
+bootstrap KS test of \citet{babu2004goodness} in the context of stationaly time
+series with unspecified serial dependence. Compared to the semiparametric method
+of \citet{zeimbekakis2022misuses}, which requires a working dependence model, it
+is reliable regardless of whether the working dependence model approximates the
+true dependence model.
 
-We have also 
-demonstrated possible applications of this method to financial data.
-Through comparison with the nonparametric
-bootstrap bias correction developed by \citet{babu2004goodness}
-and the parametric and semiparametric
-bootstrap methods developed by \citet{zeimbekakis2022misuses}, we have 
-underscored the importance of accounting for serial
-dependence in choosing an appropriate methodology.
-This method holds relevance for studies aiming to assess if a serially dependent
-time series adheres to a hypothesized distribution in scenarios where parameters
-are unknown or unspecified. Future studies could investigate
-the method's performance on different marginal distributions such
-as the generalized extreme value distribution and
-different dependence structures such as MA, ARMA, and ARIMA
-processes. Additionally, one could propose a similar method
-for comparing two serially dependent methods. One could also apply the method
-showcased in this paper to fields like earthquake prediction and astronomy.
+Several promising directions for further research emerge from the findings of
+this study. Firstly, analogous methodologies for other goodness-of-fit tests
+based on empirical distributions, such as the Anderson--Darling and Cramér--von
+Mises tests---which have been shown to outperform the KS test in certain scenarios
+\citep{stephens2017tests}---could be explored. The application of block
+bootstrapping bias correction to these tests could be particularly beneficial in
+environmental studies, such as extreme value modeling, where observations are
+often serially dependent. Secondly, an extension of the proposed nonparametric
+block bootstrap one-sample KS test to a two-sample setting would be
+intriguing. This adaptation would test whether two samples originate from the
+same distribution without requiring specification of serial dependencies in
+either sample, maintaining the advantageous feature of the original method.
 

### 2024-05-09 manuscript/manuscript.tex
addressed comments

@@
 \usepackage{setspace}
+\usepackage{multirow}
 \allowdisplaybreaks
@@
 \begin{equation*}
-W_t = \phi X_{t-1} + \epsilon_t,
+W_t = \phi W_{t-1} + \epsilon_t,
 \end{equation*}
@@
 independent errors from a normal distribution with mean zero and variance
-\jy{What was the value of $\sigma_\epsilon$?}
+\jy{What was the value of $\sigma_\epsilon$?}\mc{addressed}
 $\sigma_{\epsilon}^2$. The strength of the serial dependence is controlled by
@@
 $\{-0.924, -0.707, -0.383, 0, 0.383, 0.707, 0.924\}$, as these
-correspond to the desired values for $\tau$. First, we generated a
+correspond to the desired values for $\tau$. The 
+series $W_t$ has mean zero and variance 
+$\sigma_x^2 = \sigma_{\epsilon}^2 / (1 - \phi^2)$, so for each value of
+$\phi$, 
+we 
+set $\sigma_{\epsilon}^2 = (1 - \phi^2)$ such that $\sigma_x^2 = 1$.
+First, we generated a
 marginal $N(8, 8)$ by marginally transforming $W_t$ by
@@
 
-\input{tables/rr_norm}
+\jy{merge the two tables; use bottomrule and toprule instead of hline;
+  put them in this file instead of inputing.}\mc{addressed, let me know if I 
+  should combine them in a different way}
 
-\input{tables/rr_gamma}
+\begin{table}[ht]
+\centering
+\caption{Rejection rates for test that sample follows its true
+                    distribution family for
+                   different values of AR(1) coefficient and for different 
+                   significance levels.} 
+\label{table:size}
+\begin{tabular}{lllrrrrrrr}
+  \toprule
+$F(\cdot; \theta)$ & $n$ & $\alpha$ & $\tau = -0.75$ & $\tau = -0.5$ & $\tau = -0.25$ 
+& $\tau = 0$ & $\tau = 0.25$ & $\tau = 0.5$ & $\tau = 0.75$ \\ 
+  \midrule
+\multirow{12}{3em}{$N(8,8)$} & \multirow{3}{2em}{100} & 0.01 & 0.052 & 0.013
+& 0.007 & 0.011 & 0.009 & 0.013 & 0.058 \\ 
+& & 0.05 & 0.138 & 0.061 & 0.038 & 0.059 & 0.054 & 0.083 & 0.178 \\ 
+& & 0.10 & 0.238 & 0.125 & 0.089 & 0.124 & 0.102 & 0.152 & 0.272 \\ 
+& \multirow{3}{2em}{200} & 0.01 & 0.043 & 0.009 & 0.006 & 0.017 & 0.011 & 0.018 & 0.062 \\ 
+& & 0.05 & 0.130 & 0.058 & 0.041 & 0.051 & 0.053 & 0.061 & 0.175 \\ 
+& & 0.10 & 0.202 & 0.120 & 0.101 & 0.107 & 0.110 & 0.125 & 0.266 \\ 
+& \multirow{3}{2em}{400} & 0.01 & 0.037 & 0.011 & 0.009 & 0.014 & 0.013 & 0.009 & 0.043 \\ 
+& & 0.05 & 0.109 & 0.047 & 0.052 & 0.061 & 0.044 & 0.064 & 0.133 \\ 
+& & 0.10 & 0.174 & 0.099 & 0.098 & 0.108 & 0.099 & 0.123 & 0.212 \\ 
+& \multirow{3}{2em}{800} & 0.01 & 0.023 & 0.011 & 0.008 & 0.011 & 0.011 & 0.011 & 0.038 \\ 
+& & 0.05 & 0.088 & 0.043 & 0.040 & 0.055 & 0.042 & 0.053 & 0.125 \\ 
+& & 0.10 & 0.166 & 0.097 & 0.095 & 0.102 & 0.107 & 0.109 & 0.196 \\ 
+\multirow{12}{3em}{$N(8,8)$} & \multirow{3}{2em}{100} & 0.01 & 0.056 & 0.014 & 0.006 & 0.011 & 0.009 & 0.015 & 0.063 \\ 
+  & & 0.05 & 0.144 & 0.063 & 0.037 & 0.059 & 0.053 & 0.083 & 0.180 \\ 
+  & & 0.10 & 0.239 & 0.125 & 0.092 & 0.126 & 0.103 & 0.150 & 0.273 \\ 
+  & \multirow{3}{2em}{200} & 0.01 & 0.045 & 0.012 & 0.005 & 0.017 & 0.012 & 0.020 & 0.066 \\ 
+  & & 0.05 & 0.127 & 0.058 & 0.045 & 0.052 & 0.054 & 0.056 & 0.173 \\ 
+  & & 0.10 & 0.204 & 0.123 & 0.103 & 0.106 & 0.108 & 0.129 & 0.263 \\ 
+  & \multirow{3}{2em}{400} & 0.01 & 0.038 & 0.012 & 0.010 & 0.014 & 0.010 & 0.010 & 0.045 \\ 
+  & & 0.05 & 0.106 & 0.049 & 0.051 & 0.062 & 0.042 & 0.063 & 0.128 \\ 
+  & & 0.10 & 0.175 & 0.097 & 0.098 & 0.107 & 0.100 & 0.122 & 0.211 \\ 
+  & \multirow{3}{2em}{800} & 0.01 & 0.024 & 0.011 & 0.007 & 0.011 & 0.011 & 0.010 & 0.039 \\ 
+  & & 0.05 & 0.089 & 0.043 & 0.041 & 0.055 & 0.044 & 0.051 & 0.121 \\ 
+  & & 0.10 & 0.169 & 0.096 & 0.094 & 0.100 & 0.109 & 0.110 & 0.194 \\ 
+   \bottomrule
 
-\jy{merge the two tables; use bottomrule and toprule instead of hline;
-  put them in this file instead of inputing.}
+\end{tabular}
+\end{table}
 
@@
   \caption{Power curve as a function of $\tau$ for
-    $n \in \{100, 200, 400, 800\}$ and marginal distribution 
-    $\in \{N(8,8), \Gamma(8,1)\}$.\jy{clarify the data generating distribution and the
-      hypothesized distribution}
+    $n \in \{100, 200, 400, 800\}$ and true marginal distribution 
+    $\in \{N(8,8), \Gamma(8,1)\}$. When the data was generated from $N(8,8)$,
+    we tested for the gamma family. When the data was generated from 
+    $\Gamma(8,1)$, we tested for the normal family. \jy{clarify the data generating distribution and the
+      hypothesized distribution}\mc{addressed}
   }
@@
 dependence levels. It appears that rejection rate seems to decline as $\tau$
-\jy{comment on the asymmetry of the power in response to tau.}
-increases. Using $n \geq 400$ seems to be good enough
+\jy{comment on the asymmetry of the power in response to tau.}\mc{addressed}
+increases. Rejection rates are negatively affected by positive serial 
+dependence, but they do not seem to be affected by negative serial dependences
+of the same strength.
+Using $n \geq 400$ seems to be good enough
 if $\tau < 0.5$, but using a $n \geq 800$ will result in 
@@
 \jy{QC bib entries: page numbers missing for some journal articles.}
+\mc{couldn't find it for naess2012application}
 

### 2024-05-09 manuscript/manuscript.tex
stat format

@@
-\documentclass[12pt, titlepage, letterpaper]{article}
+\documentclass[APA,Times1COL]{WileyNJDv5} %STIX1COL,STIX2COL,STIXSMALL
 
-\usepackage{amsmath}
-\usepackage{booktabs}
-\usepackage{amsthm}
-\usepackage{graphicx}
-\usepackage[margin=1in]{geometry}
-\usepackage{hyperref}
-\hypersetup{colorlinks = true, linkcolor = blue, citecolor=blue, urlcolor = blue}
 \usepackage{natbib}
-\usepackage{enumitem}
-\usepackage{setspace}
-\usepackage{multirow}
-\allowdisplaybreaks
 
-\usepackage[]{lineno}
-\linenumbers*[1]
-% %% patches to make lineno work better with amsmath
-\newcommand*\patchAmsMathEnvironmentForLineno[1]{%
- \expandafter\let\csname old#1\expandafter\endcsname\csname #1\endcsname
- \expandafter\let\csname oldend#1\expandafter\endcsname\csname end#1\endcsname
- \renewenvironment{#1}%
- {\linenomath\csname old#1\endcsname}%
- {\csname oldend#1\endcsname\endlinenomath}}%
-\newcommand*\patchBothAmsMathEnvironmentsForLineno[1]{%
- \patchAmsMathEnvironmentForLineno{#1}%
- \patchAmsMathEnvironmentForLineno{#1*}}%
+\articletype{Article Type}%
 
-\AtBeginDocument{%
- \patchBothAmsMathEnvironmentsForLineno{equation}%
- \patchBothAmsMathEnvironmentsForLineno{align}%
- \patchBothAmsMathEnvironmentsForLineno{flalign}%
- \patchBothAmsMathEnvironmentsForLineno{alignat}%
- \patchBothAmsMathEnvironmentsForLineno{gather}%
- \patchBothAmsMathEnvironmentsForLineno{multline}%
-}
+\received{Date Month Year}
+\revised{Date Month Year}
+\accepted{Date Month Year}
+\journal{Journal}
+\volume{00}
+\copyyear{2023}
+\startpage{1}
 
-% control floats
-\renewcommand\floatpagefraction{.9}
-\renewcommand\topfraction{.9}
-\renewcommand\bottomfraction{.9}
-\renewcommand\textfraction{.1}
-\setcounter{totalnumber}{50}
-\setcounter{topnumber}{50}
-\setcounter{bottomnumber}{50}
+\raggedbottom
 
@@
 \begin{document}
-%\maketitle
 
 \title{Nonparametric Block Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test}
-  \author{Mathew Chandy \\
-  % \href{mailto:mathew.chandy@uconn.edu}
-  % {\nolinkurl{mathew.chandy@uconn.edu}}\\
- Elizabeth Schifano\\
- Jun Yan\\
- Xianyang Zhang
-}
 
-\maketitle
+\author[1]{Mathew Chandy}
 
-\begin{abstract}
+\author[1]{Elizabeth Schifano}
 
-The Kolmogorov--Smirnov (KS) test is a widely used statistical test that
+\author[1]{Jun Yan}
+
+\author[2]{Xianyang Zhang}
+
+\authormark{CHANDY \textsc{et al.}}
+\titlemark{NONPARAMETRIC BLOCK BOOTSTRAP KOLMOGOROV-SMIRNOV GOODNESS-OF-FIT TEST}
+
+\address[1]{\orgdiv{Statistics}, \orgname{University of Connecticut},
+\orgaddress{\state{Connecticut}, \country{United States}}}
+
+\address[2]{\orgdiv{Statistics}, \orgname{Texas A\&M University}, \orgaddress{\state{Texas}, \country{United States}}}
+
+\corres{\email{mathewchandy03@gmail.com}
+\email{elizabeth.schifano@uconn.edu}
+\email{jun.yan@uconn.edu} 
+\email{zhangxiany@stat.tamu.edu} }
+
+\presentaddress{21 Maxfelix Dr, Storrs, CT 06268}
+
+%\fundingInfo{Text}
+%\JELinfo{ejlje}
+
+\abstract[Abstract]{The Kolmogorov--Smirnov (KS) test is a widely used statistical test that
 assesses the conformity of a sample to a specified distribution. Its efficacy,
@@
 S\&P 500 index, showcasing its utility in real-world
-applications.
+applications.}
 
-\bigskip
-\noindent{\sc Keywords}:
-bias-correction; 
-serial dependence;
-time series. 
-\end{abstract}
+\keywords{bias-correction, p-value, time series, finance}
 
-\doublespace
+\jnlcitation{\cname{%
+\author{Chandy M.},
+\author{Schifano E},
+\author{Yan J}, and
+\author{Zhang X}}.
+\ctitle{Nonparametric block bootstrap Kolmogorov-Smirnov goodness-of-fit test.} \cjournal{\it Stat.} \cvol{2024;}.}
 
-\section{Introduction}
-\label{sec:intro}
+\maketitle
+
+\renewcommand\thefootnote{}
+\footnotetext{\textbf{Abbreviations:} }
+
+\renewcommand\thefootnote{\fnsymbol{footnote}}
+\setcounter{footnote}{1}
+
+\section{Introduction}\label{sec:intro}
 
@@
 
-\section{Methods}
-\label{sec:methods}
+\section{Methods}\label{sec:methods}
 
@@
 
-\subsection{Kolmogorov--Smirnov Test}
+\subsection{Kolmogorov--Smirnov test}
 
@@
 
-\subsection{Nonparametric Bootstrap for Independent Data}
+\subsection{Nonparametric bootstrap for independent data}
 
@@
 
-\subsection{Nonparametric Block Bootstrap for Stationary Series}
+\subsection{Nonparametric block bootstrap for stationary series}
 
@@
 
-\section{Simulation Studies}
-\label{sec:simu}
+\section{Simulation Studies}\label{sec:simu}
 
@@
 of the test should be uniformly distributed between 0 and 1. We will validate
-method with different marginal distributions to ensure that it is robust.
+our method with different marginal distributions to ensure that it is robust.
 In order for the method to work, a large number of replicates is necessary.
@@
 
-\section{Conclusion}
-\label{sec:conclusion}
+\section{Conclusions}\label{sec:conclusion}
 
@@
 
-\jy{QC bib entries: page numbers missing for some journal articles.}
-\mc{couldn't find it for naess2012application}
+%\backmatter
+\bmsection*{Author contributions}
 
-\bibliographystyle{asa}
+This is an author contribution text. This is an author contribution text. This is an author contribution text. This is an author contribution text. This is an author contribution text.
+
+\bmsection*{Acknowledgments}
+This is acknowledgment text.
+Provide text here.
+This is acknowledgment text.
+Provide text here.
+This is acknowledgment text.
+Provide text here.
+This is acknowledgment text.
+Provide text here.
+This is acknowledgment text.
+Provide text here.
+This is acknowledgment text.
+Provide text here.
+This is acknowledgment text.
+Provide text here.
+This is acknowledgment text.
+Provide text here.
+This is acknowledgment text.
+Provide text here.
+
+\bmsection*{Data availability statement}
+
+\bmsection*{Funding statement}
+
+None reported.
+
+\bmsection*{Conflict of interest disclosure}
+
+The authors declare no potential conflict of interests.
+
+\bmsection*{Ethics approval statement}
+
 \bibliography{citations}
 
+\bmsection*{Supporting information}
+
+Additional supporting information may be found in the
+online version of the article at the publisher’s website.
+
+\nocite{*}% Show all bib entries - both cited and uncited; comment this line to view only cited bib entries;
+
 \end{document}
-%%% LocalWords: nonparametric semiparametric autocorrelation ARMA
-%%% Local Variables:
-%%% mode: latex
-%%% TeX-master: t
-%%% ispell-personal-dictionary: ".aspell.en.pws"
-%%% fill-column: 80
-%%% eval: (auto-fill-mode 1)
-%%% End:

### 2024-05-09 manuscript/manuscript.tex
removed addressed comments

@@
 independent errors from a normal distribution with mean zero and variance
-\jy{What was the value of $\sigma_\epsilon$?}\mc{addressed}
 $\sigma_{\epsilon}^2$. The strength of the serial dependence is controlled by
@@
 $\sigma_x^2 = \sigma_{\epsilon}^2 / (1 - \phi^2)$, so for each value of
-$\phi$, 
-we 
+$\phi$,  we 
 set $\sigma_{\epsilon}^2 = (1 - \phi^2)$ such that $\sigma_x^2 = 1$.
@@
 
-\jy{merge the two tables; use bottomrule and toprule instead of hline;
-  put them in this file instead of inputing.}\mc{addressed, let me know if I 
-  should combine them in a different way}
-
-\begin{table}[ht]
+\begin{table}[tbp]
 \centering
@@
   \midrule
-\multirow{12}{3em}{$N(8,8)$} & \multirow{3}{2em}{100} & 0.01 & 0.052 & 0.013
-& 0.007 & 0.011 & 0.009 & 0.013 & 0.058 \\ 
+{$N(8,8)$} & {100} & 0.01 & 0.052 & 0.013& 0.007 & 0.011 & 0.009 & 0.013 & 0.058 \\ 
 & & 0.05 & 0.138 & 0.061 & 0.038 & 0.059 & 0.054 & 0.083 & 0.178 \\ 
 & & 0.10 & 0.238 & 0.125 & 0.089 & 0.124 & 0.102 & 0.152 & 0.272 \\ 
-& \multirow{3}{2em}{200} & 0.01 & 0.043 & 0.009 & 0.006 & 0.017 & 0.011 & 0.018 & 0.062 \\ 
+& {200} & 0.01 & 0.043 & 0.009 & 0.006 & 0.017 & 0.011 & 0.018 & 0.062 \\ 
 & & 0.05 & 0.130 & 0.058 & 0.041 & 0.051 & 0.053 & 0.061 & 0.175 \\ 
 & & 0.10 & 0.202 & 0.120 & 0.101 & 0.107 & 0.110 & 0.125 & 0.266 \\ 
-& \multirow{3}{2em}{400} & 0.01 & 0.037 & 0.011 & 0.009 & 0.014 & 0.013 & 0.009 & 0.043 \\ 
+& {400} & 0.01 & 0.037 & 0.011 & 0.009 & 0.014 & 0.013 & 0.009 & 0.043 \\ 
 & & 0.05 & 0.109 & 0.047 & 0.052 & 0.061 & 0.044 & 0.064 & 0.133 \\ 
 & & 0.10 & 0.174 & 0.099 & 0.098 & 0.108 & 0.099 & 0.123 & 0.212 \\ 
-& \multirow{3}{2em}{800} & 0.01 & 0.023 & 0.011 & 0.008 & 0.011 & 0.011 & 0.011 & 0.038 \\ 
+& {800} & 0.01 & 0.023 & 0.011 & 0.008 & 0.011 & 0.011 & 0.011 & 0.038 \\ 
 & & 0.05 & 0.088 & 0.043 & 0.040 & 0.055 & 0.042 & 0.053 & 0.125 \\ 
-& & 0.10 & 0.166 & 0.097 & 0.095 & 0.102 & 0.107 & 0.109 & 0.196 \\ 
-\multirow{12}{3em}{$N(8,8)$} & \multirow{3}{2em}{100} & 0.01 & 0.056 & 0.014 & 0.006 & 0.011 & 0.009 & 0.015 & 0.063 \\ 
+& & 0.10 & 0.166 & 0.097 & 0.095 & 0.102 & 0.107 & 0.109 & 0.196 \\ [1ex]
+{$\Gamma(8,1)$} & {100} & 0.01 & 0.056 & 0.014 & 0.006 & 0.011 & 0.009 & 0.015 & 0.063 \\
   & & 0.05 & 0.144 & 0.063 & 0.037 & 0.059 & 0.053 & 0.083 & 0.180 \\ 
   & & 0.10 & 0.239 & 0.125 & 0.092 & 0.126 & 0.103 & 0.150 & 0.273 \\ 
-  & \multirow{3}{2em}{200} & 0.01 & 0.045 & 0.012 & 0.005 & 0.017 & 0.012 & 0.020 & 0.066 \\ 
+  & {200} & 0.01 & 0.045 & 0.012 & 0.005 & 0.017 & 0.012 & 0.020 & 0.066 \\ 
   & & 0.05 & 0.127 & 0.058 & 0.045 & 0.052 & 0.054 & 0.056 & 0.173 \\ 
   & & 0.10 & 0.204 & 0.123 & 0.103 & 0.106 & 0.108 & 0.129 & 0.263 \\ 
-  & \multirow{3}{2em}{400} & 0.01 & 0.038 & 0.012 & 0.010 & 0.014 & 0.010 & 0.010 & 0.045 \\ 
+  & {400} & 0.01 & 0.038 & 0.012 & 0.010 & 0.014 & 0.010 & 0.010 & 0.045 \\ 
   & & 0.05 & 0.106 & 0.049 & 0.051 & 0.062 & 0.042 & 0.063 & 0.128 \\ 
   & & 0.10 & 0.175 & 0.097 & 0.098 & 0.107 & 0.100 & 0.122 & 0.211 \\ 
-  & \multirow{3}{2em}{800} & 0.01 & 0.024 & 0.011 & 0.007 & 0.011 & 0.011 & 0.010 & 0.039 \\ 
+  & {800} & 0.01 & 0.024 & 0.011 & 0.007 & 0.011 & 0.011 & 0.010 & 0.039 \\ 
   & & 0.05 & 0.089 & 0.043 & 0.041 & 0.055 & 0.044 & 0.051 & 0.121 \\ 
@@
    \bottomrule
-
 \end{tabular}
@@
     we tested for the gamma family. When the data was generated from 
-    $\Gamma(8,1)$, we tested for the normal family. \jy{clarify the data generating distribution and the
-      hypothesized distribution}\mc{addressed}
+    $\Gamma(8,1)$, we tested for the normal family. 
   }
@@
 dependence levels. It appears that rejection rate seems to decline as $\tau$
-\jy{comment on the asymmetry of the power in response to tau.}\mc{addressed}
 increases. Rejection rates are negatively affected by positive serial 

### 2024-05-09 manuscript/manuscript.tex
minor

@@
 
-\section{Real Data Examples}
+\section{A Real Data Example}
 \label{sec:real}
@@
 dependence and unconditional heavy tails \citep[e.g.,][]{ryden1998stylized,
-  cont2001empirical}. The Kendall's $\tau$ for the series is
-was about $-0.0298$, indicating a fairly weak serial linear correlation, but
+  cont2001empirical}. The lag-1 Kendall's $\tau$ of the series is
+about $-0.0298$, indicating a fairly weak serial linear correlation, but
 certainly not meaning absence of serial dependence.

### 2024-05-10 manuscript/manuscript.tex
added dois
data availability statement
touch up

@@
 %\backmatter
-\bmsection*{Author contributions}
-
-This is an author contribution text. This is an author contribution text. This is an author contribution text. This is an author contribution text. This is an author contribution text.
-
-\bmsection*{Acknowledgments}
-This is acknowledgment text.
-Provide text here.
-This is acknowledgment text.
-Provide text here.
-This is acknowledgment text.
-Provide text here.
-This is acknowledgment text.
-Provide text here.
-This is acknowledgment text.
-Provide text here.
-This is acknowledgment text.
-Provide text here.
-This is acknowledgment text.
-Provide text here.
-This is acknowledgment text.
-Provide text here.
-This is acknowledgment text.
-Provide text here.
 
 \bmsection*{Data availability statement}
+The data and code used in the real data analysis and simulation
+studies are publicly available in a GitHub repo:
+\jy{Give the link}
 
@@
 
-\bmsection*{Ethics approval statement}
+% \bmsection*{Ethics approval statement}
 
@@
 
-\bmsection*{Supporting information}
-
-Additional supporting information may be found in the
-online version of the article at the publisher’s website.
-
-\nocite{*}% Show all bib entries - both cited and uncited; comment this line to view only cited bib entries;
+% \nocite{*}% Show all bib entries - both cited and uncited; comment this line to view only cited bib entries;
 

### 2024-05-13 manuscript/manuscript.tex
added link
changed readme
first thoughts

@@
 
-\presentaddress{21 Maxfelix Dr, Storrs, CT 06268}
+\presentaddress{215 Glenbrook Road, Unit 4120
+Storrs, Connecticut 06269-4120}
 
@@
 within the hypothesized distribution are unknown. For independent data,
-parametric and nonparametric bootstrap procedure are available to adjust for
+parametric and nonparametric bootstrap procedures are available to adjust for
 estimated parameters. For serially dependent stationary data, parametric
@@
 fitted parameters, which can be obtained from any consistent estimator with
-asymptotic normality properties,  Let $F_n$ be the empirical distribution
+asymptotic normality properties.  Let $F_n$ be the empirical distribution
 function based on $X_1,...,X_n$.
@@
 
-When $\{X_t: t = 1, \ldots, n\}$ are further serially dependent, the statistics
+\eds{Please check consistency with how you refer to $F$.  In 
+Equation~\eqref{eq:ks_standard}, it is $F(x; \theta_0)$ where the data and 
+parameter arguments are separated by a semicolon.  At the beginning of 
+Section~\ref{sec:methods}, it is $F(\cdot \mid \theta)$, with the vertical bar
+separating the data argument from the parameter argument (and no 0 subscript
+either).   Then in this first 
+subsection it is $F(x; \hat\theta_n)$ with a semicolon separating the two 
+arguments.  Then immediately above its use is mixed with $F(x)$ without a 
+parameter argument (implying it is the true parameter $\theta$). This continues
+throughout the document. I suggest either using consistent notation throughout, 
+or explicitly defining any shortened/simplified notation at its first use.}
+
+When $\{X_t: t = 1, \ldots, n\}$ are further serially dependent, the statistic
 $T_n$ still provides a reasonable metric for deviation from the null
@@
 even with the bias correction of \citet{babu2004goodness}, because the
-correction requires independent sample.
+correction requires an independent sample.
 
@@
 	$\hat\theta^{(b)}_n$ of $\theta$.  
+	\eds{$F_\theta$ has not yet been defined.}
 \item
@@
 $T_n^{(b)}$, $b = 1, \ldots, B$.
+
+\eds{Do we not define $Y^{(b)}_n(x)$ in terms of the $E_n(\cdot)$'s instead of 
+the $E(\cdot)$ above and below?}
 
@@
 for some unspecified $\alpha$ and $\beta$.
+\eds{Vertical bar vs semicolon to separate data and parameter arguments.}
 For the block
@@
 for the test when applied to samples from the same data generating process.
+\eds{I assume $r$ is for replicate?  Please define and include how many 
+total replicates you are using.}
 
@@
     being $N(8,8)$ (upper) and marginal gamma distribution with true data
-    generating distribution $\Gamma(8,1)$ (lower)}
+    generating distribution $\Gamma(8,1)$ (lower).}
   \label{fig:qq}
@@
 $\tau$ is lower than 0.25. For Kendall's $\tau \geq 0.5$, a sample larger than
-$n = 200$ seems necessary for the p-values to be normally distributed. For
+$n = 200$ seems necessary for the p-values to be normally 
+\eds{uniformly?} distributed. For
 Kendall's $\tau \geq 0.75$, a sample larger than $n = 800$ appears to be 
@@
                    different values of AR(1) coefficient and for different 
-                   significance levels.} 
+                   significance levels.
+		\eds{Not sure if it will help presentation or interpretation, but you could
+	consider presenting the values inside the table as estimated size/true size}}
 \label{table:size}
@@
 summarizes the empirical sizes of the tests based on 1000 replicates.
+\eds{Number of replicates needs to be stated earlier.  Also, is 1000 enough
+to truly evaluate whether size is good at the 0.01 level?}
 The agreement between the empirical sizes and the nominal size
@@
 and $\tau = 0.75$, a sample size as large as 800 is still not sufficient for the
-agreemet to be reached. For weaker dependence levels, our approach is working
+agreement to be reached. For weaker dependence levels, our approach is working
 for $-0.25 < \tau < 0.25$ for $n = 100$. However, a larger sample size seems 
@@
 the \textsl{truncdist} package \citep{truncdist} to truncate the series at 
-values less than or equal to 0 when testing that $N(8, 8)$ sample was
+values less than or equal to 0 when testing that the $N(8, 8)$ sample was
 from $\Gamma(8, 1)$. For each setting for $F$, $\tau$, and $n$, we replicate the 
@@
 found that our method doesn't work under the null hypothesis for such high
-dependence levels. It appears that rejection rate seems to decline as $\tau$
+dependence levels under the sample sizes considered. It appears that the 
+rejection rate seems to decline as $\tau$
 increases. Rejection rates are negatively affected by positive serial 
-dependence, but they do not seem to be affected by negative serial dependences
+dependence, but they do not seem to be affected by negative serial dependencies
 of the same strength.
@@
 the logarithm of the closing prices. 
-It is known as stylized facts that daily return series often exhibts nonlinear
+It is known as stylized facts that daily return series often exhibit nonlinear
 dependence and unconditional heavy tails \citep[e.g.,][]{ryden1998stylized,
@@
 with the proposed nonparametric block bootstrap (NPBB) method.
+\eds{Introduce this acronym earlier (as early as in the intro), and use it 
+throughout the ms.}
 For comparison, we tested the same hypotheses using 1) the
@@
   and different degrees of freedom for Student's $t$ distribution.
+	\eds{how are ``different durations'' reflected in this table?}
   NPBB: nonparametric block bootstrap;
@@
 
+\eds{I think it would be better to show in simulation first (perhaps 
+in supplemental materials if we are concerned with paper length) that the other
+methods are not valid or unreliable under this setting, and then 
+further discredit those results here in the real data analysis.
+(I would expect a reviewer to ask for this comparison anyway.)}
+
 \section{Conclusions}\label{sec:conclusion}
@@
 
+\eds{can Mathew's AJUR paper be cited somewhere in this document?}
+
 %\backmatter

### 2024-05-13 manuscript/manuscript.tex
responded to some comments

@@
 
-\abstract[Abstract]{The Kolmogorov--Smirnov (KS) test is a widely used statistical test that
+\abstract[Abstract]{The Kolmogorov--Smirnov (KS) test is a widely used 
+statistical test that
 assesses the conformity of a sample to a specified distribution. Its efficacy,
@@
 Alternatively, \citet{babu2004goodness} address this issue through a
-nonparametric bootstrap method that corrects the bias in the asymptotic null
+nonparametric bootstrap (NPB) method that corrects the bias in the asymptotic null
 distribution.
@@
 the unknown parameters and unknown serial dependence. 
-\citet{zeimbekakis2022misuses} recommend a semiparametric bootstrap
+\citet{zeimbekakis2022misuses} recommend a semiparametric bootstrap (SPB)
 approach, where the parameters of the hypothesized distribution and the serial
@@
 the structure of the serial dependence, which can vary widely in practical 
-situations. Employing a nonparametric bootstrap would necessitate defining a 
+situations. Employing a nonparametric method would necessitate defining a 
 specific model for this dependence, despite the primary focus being on 
 evaluating the marginal distribution of a stationary series. To date, a bias 
-correction method for block bootstrap, akin to the nonparametric bootstrap
+correction method for block bootstrap, akin to the NPB
 approach of \citet{babu2004goodness} for independent data,
@@
 to bridge this gap by introducing a bias correction technique for the 
-nonparametric block bootstrap, tailored for use in scenarios where the 
+nonparametric block bootstrap (NPBB), tailored for use in scenarios where the 
 hypothesized distribution has unspecified parameters and the data 
@@
 procedure and introduces the bias correction methodology for the 
-nonparametric block bootstrap KS test. Section~\ref{sec:simu} is divided 
+NPBB KS test. Section~\ref{sec:simu} is divided 
 into two parts; initially, we evaluate the KS test's ability to maintain 
@@
 or explicitly defining any shortened/simplified notation at its first use.}
+\mc{I believe the vertical bar is to indicate that the parameters are 
+unspecified}
 
@@
 
-\subsection{Nonparametric bootstrap for independent data}
+\subsection{Nonparametric bootstrap (NPB) for independent data}
 
@@
 
-In summary, the procedure of the nonparametric bootstrap KS test for independent
+In summary, the procedure of the NPB KS test for independent
 sample is 
@@
 \item
-  Fit $F_\theta$ to $X^{(b)}_1,...,X^{(b)}_n$ and obtain estimate 
-	$\hat\theta^{(b)}_n$ of $\theta$.  
-	\eds{$F_\theta$ has not yet been defined.}
+  Obtain parametrically
+  fitted parameters 
+	$\hat\theta^{(b)}_n$ of $\theta$ from $X^{(b)}_1,...,X^{(b)}_n$.  
+	\eds{$F_\theta$ has not yet been defined.}\mc{addressed}
 \item
@@
 
-\subsection{Nonparametric block bootstrap for stationary series}
+\subsection{Nonparametric block bootstrap (NPBB) for stationary series}
 
@@
 $E[\hat\theta^{(b)}_n]$ can be approximated by, respectively,
-$E_n[F^{(b)}_n(x)] = \frac{1}{B}\sum_{b = 1}^BF^{(b)}_n(x)$ and
-$E_n[\hat\theta^{(b)}_n]  =  \frac{1}{B}\sum_{b = 1}^B\hat\theta^{(b)}_n$.
+$E[F^{(b)}_n(x)] = \frac{1}{B}\sum_{b = 1}^BF^{(b)}_n(x)$ and
+$E[\hat\theta^{(b)}_n]  =  \frac{1}{B}\sum_{b = 1}^B\hat\theta^{(b)}_n$.
 
@@
 \eds{Do we not define $Y^{(b)}_n(x)$ in terms of the $E_n(\cdot)$'s instead of 
-the $E(\cdot)$ above and below?}
+the $E(\cdot)$ above and below?}\mc{$E_n$ was a typo}
 
-In summary, the procedure of the nonparametric block bootstrap test is 
+In summary, the procedure of the NPBB test is 
 summarized as follows. Repeat the following steps for $b \in \{1, ..., B\}$.
@@
 \eds{Vertical bar vs semicolon to separate data and parameter arguments.}
+\mc{I believe the vertical bar is indicate that the parameter arguments are 
+unspecified}
 For the block
@@
 For each setting for $F$, $\tau$, and $n$, we replicate the method 1000 times 
-to get the distribution of the p-values $p_r$
+to get the distribution of the p-values $p_r$ for
+$r \in \{1, \dots, 1000\}$
 for the test when applied to samples from the same data generating process.
 \eds{I assume $r$ is for replicate?  Please define and include how many 
-total replicates you are using.}
+total replicates you are using.} \mc{addressed}
 
@@
 $\tau$ is lower than 0.25. For Kendall's $\tau \geq 0.5$, a sample larger than
-$n = 200$ seems necessary for the p-values to be normally 
-\eds{uniformly?} distributed. For
+$n = 200$ seems necessary for the p-values to be uniformly
+\eds{uniformly?}\mc{addressed} distributed. For
 Kendall's $\tau \geq 0.75$, a sample larger than $n = 800$ appears to be 
@@
 \centering
-\caption{Rejection rates for test that sample follows its true
+\caption{Rejection rates or true size for test that sample follows its true
                     distribution family for
                    different values of AR(1) coefficient and for different 
-                   significance levels.
+                   significance levels or estimated sizes.
 		\eds{Not sure if it will help presentation or interpretation, but you could
-	consider presenting the values inside the table as estimated size/true size}}
+	consider presenting the values inside the table as estimated size/true size}
+	\mc{addressed}}
 \label{table:size}
@@
 with degrees of freedom $\nu \in \{30, 20, 10, 5, 4, 3, 2, 1\}$
-with the proposed nonparametric block bootstrap (NPBB) method.
+with the proposed NPBB method.
 \eds{Introduce this acronym earlier (as early as in the intro), and use it 
-throughout the ms.}
+throughout the ms.}\mc{addressed}
 For comparison, we tested the same hypotheses using 1) the
-semiparametric bootstrap (SPB) method of \citet{zeimbekakis2022misuses},
+SPB method of \citet{zeimbekakis2022misuses},
 which accounts for both serial dependence and unspecified parameters;
-2) nonparametric bootstrap (NPB) bias correction method of
+2) NPB bias correction method of
 \citet{babu2004goodness}; and and 3) the parametric bootstrap (PB) method shown
@@
 \caption{P-values for 4 years of S\&P 500 stock return 
-  data using different durations
-  and different degrees of freedom for Student's $t$ distribution.
-	\eds{how are ``different durations'' reflected in this table?}
+  data using different degrees of freedom for Student's $t$ distribution.
+	\eds{how are ``different durations'' reflected in this table?}\mc{addressed}
   NPBB: nonparametric block bootstrap;
@@
 enabling critical assessments of population distributions. We introduced a
-nonparametric block bootstrap variant of the KS test tailored for data with
+NPBB variant of the KS test tailored for data with
 serial dependencies, which eliminates the need for explicit modeling serial
@@
 the test can be recommended for sample size~$n = 400$ or higher.
-Overall, the test provides an analog of the bias-corrected nonparametric
-bootstrap KS test of \citet{babu2004goodness} in the context of stationaly time
-series with unspecified serial dependence. Compared to the semiparametric method
+Overall, the test provides an analog of the bias-corrected NPB KS test of 
+\citet{babu2004goodness} in the context of stationaly time
+series with unspecified serial dependence. Compared to the SPB method
 of \citet{zeimbekakis2022misuses}, which requires a working dependence model, it
@@
 environmental studies, such as extreme value modeling, where observations are
-often serially dependent. Secondly, an extension of the proposed nonparametric
-block bootstrap one-sample KS test to a two-sample setting would be
+often serially dependent. Secondly, an extension of the proposed NPBB
+one-sample KS test to a two-sample setting would be
 intriguing. This adaptation would test whether two samples originate from the
@@
 studies are publicly available in a GitHub repo:
-\jy{Give the link}
+\url{https://github.com/mathewchandy03/Bootstrap_KS_Test}
+\jy{Give the link}\mc{addressed}
 

### 2024-05-14 manuscript/manuscript.tex
cited my paper

@@
 \citet{babu2004goodness} when the data are independent. 
+As noted by 
+\citet{chandy2024sample}, a sample greater than 1600 may be necessary for 
+block bootstrap confidence intervals to have the right coverage 
+rates of parameters. 
+Therefore, although this study uses block bootstrap in a different setting,
+we expect that a large sample size may be required when the data is serially
+dependent.
 
@@
 \[
-  H_0: X_t \sim F(\cdot \mid \theta), \quad t = 1, \ldots, n,
+  H_0: X_t \sim F(\cdot ; \theta), \quad t = 1, \ldots, n,
 \]
@@
 or explicitly defining any shortened/simplified notation at its first use.}
-\mc{I believe the vertical bar is to indicate that the parameters are 
-unspecified}
+\mc{switched everything to semicolons}
 
@@
 measure of serial dependence as it is invariant to monotone marginal
-transformations. To generate the samples to which our
+transformations. 
+To generate the samples to which our
 method would be applied, we simulated a time series $W_t$ from a 1st 
@@
 Normal family, or 
-$X_t \sim N(\cdot \mid \mu, \sigma^2), \quad t = 1, \ldots, n$
+$X_t \sim N(\cdot ; \mu, \sigma^2), \quad t = 1, \ldots, n$
 for some unspecified $\mu$ and $\sigma$. When $X_t \sim \Gamma(8, 1)$, we tested
@@
 or
-$X_t \sim \Gamma(\cdot \mid \alpha, \beta), \quad t = 1, \ldots, n$.
+$X_t \sim \Gamma(\cdot ; \alpha, \beta), \quad t = 1, \ldots, n$.
 for some unspecified $\alpha$ and $\beta$.
 \eds{Vertical bar vs semicolon to separate data and parameter arguments.}
-\mc{I believe the vertical bar is indicate that the parameter arguments are 
-unspecified}
+\mc{changed everything to semicolon}
 For the block
@@
 \eds{can Mathew's AJUR paper be cited somewhere in this document?}
+\mc{addressed}
 

### 2024-05-18 code/blk1_jobs.R
10000 replicates for null, still need to update for alt

@@ -1,41 +1,51 @@
 source("hpc_functions.R")
-source("functions.R")
 # library(copula)
 B <- 1000
-nrep <- 50
+nrep <- 4
 phis <- c()
 # for (i in c(-.75, -.5, -.25, 0, .25, .5, .75)) {
 #   phis <- c(phis, iTau(normalCopula(), i))
 # }
 phis <- 
   c(-0.9238795, -0.7071068, -0.3826834, 0, 0.3826834, 0.7071068, 0.9238795)
-i <- Sys.getenv("SLURM_ARRAY_TASK_ID")
+#i <- Sys.getenv("SLURM_ARRAY_TASK_ID")
+i <- 6
 for (phi in phis) {
   for (n in c(100, 200, 400, 800)) {
     set.seed(as.integer(i))
-    y <- arima.sim(list(ar = phi), n = n) * 
-      sqrt(1 - sum(phi^2))
     for (true_dist in c("normal", "gamma")) {
-      for (truth in c("null", "alt")) {
-        if (true_dist == "normal" & truth == "null" |
-            true_dist == "gamma" & truth == "alt") {
+      for (truth in c("alt")) {
+        if (true_dist == "normal" & truth == "null") {
           h0_dist <- "normal"
           f0 <- pnorm
           f <- qnorm
           theta <- c(8, sqrt(8))
           rgen <- rnorm
         }
-        if (true_dist == "gamma" & truth == "null" |
-            true_dist == "normal" & truth == "alt") {
+        if (true_dist == "gamma" & truth == "alt") {
+          h0_dist <- "normal"
+          f0 <- pnorm
+          f <- qgamma
+          theta <- c(8,1)
+          rgen <- rnorm
+        }
+        if (true_dist == "gamma" & truth == "null") {
           h0_dist <- "gamma"
           f0 <- pgamma
           f <- qgamma
           theta <- c(8,1)
           rgen <- rgamma
+        } 
+        if (true_dist == "normal" & truth == "alt") {
+          h0_dist <- "gamma"
+          f0 <- pgamma
+          f <- qnorm
+          theta <- c(8, sqrt(8))
+          rgen <- rgamma
         }
         blksize <- ceiling(n^(1/3))
         p <- replicate(nrep, mysim(n, blksize, B, h0_dist, true_dist, f0, f, 
-                                   theta, phi, 0, rgen))
+                                   theta, phi, rgen))
[…]

### 2024-05-18 code/jobs.sh

@@ -1,16 +1,18 @@
 #!/bin/bash
 #SBATCH --partition=general
 #SBATCH --output=../out/ja_%A_%a.out
-#SBATCH --array=1-200%200
+#SBATCH --array=1-2500%2500
 #SBATCH --ntasks=1 ## OBS 1
 #SBATCH --cpus-per-task=1 ## OBS 2
 #SBATCH --mem-per-cpu=500M ## OBS 3
 #SBATCH --mail-type=FAIL                       # Event(s) that triggers email notification (BEGIN,END,FAIL,ALL)
 #SBATCH --mail-user=mathew.chandy@uconn.edu    
 
+module unload r/4.2.2
+module unload gcc
 module load r/4.2.2
 
 ## avoiding implicit paralellism
 export OMP_NUM_THREADS=1
 
-Rscript blk2_jobs.R
+Rscript blk1_jobs.R

### 2024-05-18 code/tables.R

@@ -1,7 +1,7 @@
 library(xtable)
-df <- readRDS("../data/sim_rejection_rates.RDS") %>% 
+df <- readRDS("../data/null_rejection_rates.RDS") %>% 
   mutate(rr_lb = round(as.numeric(rr_lb), 3),
-         rr = round(as.numeric(rr), 3),
+         rr = round(as.numeric(rr), 4),
          rr_ub = round(as.numeric(rr_ub), 3),
          alpha = format(round(as.numeric(alpha), 2), nsmall = 2))
 
@@ -31,7 +31,7 @@ write(print(xtable(df_norm,
                    normally distributed for
                    different values of AR(1) coefficient and for different 
                    significance levels.",
-                   label = "table:rr_norm", digits = 3), caption.placement = "top",
+                   label = "table:rr_norm", digits = 4), caption.placement = "top",
             sanitize.text.function=function(x){x}, include.rownames = FALSE), 
       file = "../manuscript/tables/rr_norm.tex")  
 
@@ -46,6 +46,6 @@ write(print(xtable(df_gamma,
                    gamma-distributed for
                    different values of AR(1) coefficient and for different 
                    significance levels.",
-                   label = "table:rr_gamma", digits = 3), caption.placement = "top",
+                   label = "table:rr_gamma", digits = 4), caption.placement = "top",
             sanitize.text.function=function(x){x}, include.rownames = FALSE), 
       file = "../manuscript/tables/rr_gamma.tex") 

### 2024-05-18 code/tables.R
changed table

@@ -1,9 +1,11 @@
 library(xtable)
+library(tidyverse)
 df <- readRDS("../data/null_rejection_rates.RDS") %>% 
   mutate(rr_lb = round(as.numeric(rr_lb), 3),
          rr = round(as.numeric(rr), 4),
          rr_ub = round(as.numeric(rr_ub), 3),
-         alpha = format(round(as.numeric(alpha), 2), nsmall = 2))
+         alpha = format(round(as.numeric(alpha), 2), nsmall = 2),
+         `Empirical Size` = rr / as.numeric(alpha))
 
 df$tau <- factor(case_when(df$phi == "-0.9238795" ~ "$\\tau = -0.75$",
                            df$phi == "-0.7071068" ~ "$\\tau = -0.5$",
@@ -22,13 +24,13 @@ df$tau <- factor(case_when(df$phi == "-0.9238795" ~ "$\\tau = -0.75$",
 
 library(reshape2)
 df_norm <- df %>% filter(dist == "normal") %>% 
-  dplyr::select(n, alpha, rr, tau) %>% 
-  dcast(n + alpha ~ tau, value.var = "rr") %>% 
+  dplyr::select(n, alpha, rr, tau, `Empirical Size`) %>% 
+  dcast(n + alpha ~ tau, value.var = "Empirical Size") %>% 
   rename(`$n$` = n, `$\\alpha$` = alpha)
 
 write(print(xtable(df_norm, 
-                   caption = "Rejection rates for test that $N(8, 8)$ is indeed
-                   normally distributed for
+                   caption = "Empirical sizes for the test that sample follows its true
+                    distribution family for
                    different values of AR(1) coefficient and for different 
                    significance levels.",
                    label = "table:rr_norm", digits = 4), caption.placement = "top",
@@ -36,14 +38,13 @@ write(print(xtable(df_norm,
       file = "../manuscript/tables/rr_norm.tex")  
 
 df_gamma <- df %>% filter(dist == "gamma") %>% 
-  dplyr::select(n, alpha, rr, tau) %>% 
-  dcast(n + alpha ~ tau, value.var = "rr") %>% 
+  dplyr::select(n, alpha, rr, tau, `Empirical Size`) %>% 
+  dcast(n + alpha ~ tau, value.var = "Empirical Size") %>% 
   rename(`$n$` = n, `$\\alpha$` = alpha)
 
 write(print(xtable(df_gamma, 
[…]

### 2024-06-13 manuscript/main.tex
propositions in manuscript

\documentclass[11pt]{article}

\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{authblk}
\usepackage{algorithm}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{algpseudocode}
\usepackage{bbm}
\usepackage{bm}
\usepackage{caption}
\usepackage{color}
\usepackage{enumerate}
\usepackage{enumitem}
\usepackage{float}
\usepackage{mathtools}
\usepackage{makecell}
\usepackage{multirow}
\usepackage{hyperref}
\usepackage{natbib}
\usepackage{comment}
\usepackage{longtable}
\usepackage{rotating}
\usepackage{xcolor}
\usepackage{fullpage}

\newcommand{\mc}[1]{\textcolor{blue}{MC: (#1)}}

\begin{document}

\section{Asymptotic limit of the KS-statistic}
We first derive the limiting distribution of the KS statistic under the null. Suppose $\hat{\theta}_n$ admits the expansion:
\begin{align}\label{eq-expan}
\hat{\theta}_n-\theta_0 = \frac{1}{n}\sum^{n}_{i=1}h(X_i;\theta_0) + \frac{1}{\sqrt{n}}R_n,    
\end{align}
where $h(\cdot;\theta_0)$ is the influence function with $\mathbb{E}[h(X_i;\theta_0)]=0$ and $R_n$ is the remainder term satisfying that
$R_n\overset{p}{\rightarrow} 0.$ Write $G_n(x):=\sqrt{n}(F_n(x)-F(x))$ and let $f(x;\theta)=\partial F(x;\theta)/\partial \theta$. We assume $\theta \in \mathbb{R}$ for ease of presentation.

Given any $x_1,\dots,x_m$ in the domain of $F$, by the CLT for weakly dependent time series, we have the joint convergence of 
$V_n:=(G_n(x_1),\dots,G_n(x_m),\sqrt{n}(\hat{\theta}_n-\theta_0))$
to some Gaussian limit, with the covariance matrix being $\Sigma_{m+1}=\lim_{n\rightarrow+\infty}\text{Cov}(V_n)$.
%\begin{align*}
%\Sigma_{m+1}=\begin{pmatrix}
%df & df & \cdots & df\\   
%df & df & \cdots & df\\ 
%\cdots & \cdots & \ddots & \cdots  \\ 
%df & df & \cdots & df
%\end{pmatrix}    
%\end{align*} 
Moreover, we can show the tightness of the process $G_n(x)$. 
For sufficiently small $\delta$, and leveraging the properties of weakly 
dependent sequences, we can show that
\[ \sup_{|x - y| < \delta} |G_n(x) - G_n(y)| = \sup_{|x - y| < \delta} 
\sqrt{n}|(F_n(x) - F(x)) - (F_n(y) - F(y))| \]
is small with high probability.
Specifically, since $F(x)$ is continuous, for small 
$\delta$, $|F(x) - F(y)|$ is small. For the empirical 
distribution function $F_n(x)$, the increments $|F_n(x) - F_n(y)|$ are 
also controlled. 
This implies that the process $G_n(x)$ does not exhibit large oscillations over 
small intervals, thus satisfying the criterion for tightness.
Therefore, we have
\begin{align*}
\begin{pmatrix}
G_n(x)  \\ 
\sqrt{n}(F(x;\hat{\theta}_n)-F(x;\theta_0))
\end{pmatrix}\Rightarrow
\begin{pmatrix}
G_{\infty}(x) \\
f(x;\theta_0)U
\end{pmatrix}
\end{align*}
jointly, where $G_{\infty}(x)$ is a Gaussian process with the covariance function defined as
\begin{align*}
\text{Cov}(G_{\infty}(x),G_{\infty}(x'))=& \lim_{n\rightarrow+\infty}\frac{1}{n}\sum^{n}_{i,j=1}\text{Cov}(\mathbf{1}\{X_i\leq x\},\mathbf{1}\{X_j\leq x'\})
\\=& \sum^{+\infty}_{h=-\infty}\text{Cov}(\mathbf{1}\{X_{h}\leq x\},\mathbf{1}\{X_0\leq x'\}),
\end{align*}
and $U\sim N(0,s^2)$ with 
\begin{align*}
s^2=\lim_{n\rightarrow+\infty}\frac{1}{n}\sum^{n}_{i,j=1}\text{Cov}(h(X_i,\theta_0),h(X_j;\theta_0))
= \sum^{+\infty}_{h=-\infty}\text{Cov}(h(X_{h},\theta_0),h(X_0;\theta_0)),
\end{align*}
and the covariance between $U$ and $G_{\infty}(x)$ is given by
\begin{align*}
\text{Cov}(U,G_\infty(x))=&\lim_{n\rightarrow+\infty}
\frac{1}{n}\sum^{n}_{i,j=1}\text{Cov}(h(X_i,\theta_0),\mathbf{1}\{X_j\leq x\})
\\=&\sum^{+\infty}_{h=-\infty}\text{Cov}(h(X_{h},\theta_0),\mathbf{1}\{X_0\leq x\}).
\end{align*}
By the continuous mapping theorem, we obtain
\begin{align*}
T_n \overset{d}{\rightarrow} \sup_x |G_{\infty}(x)+f(x;\theta_0)U|.    
\end{align*}

\section{Bootstrap consistency}
\subsection{Preliminaries}
Denote by $\mathbb{E}^*$, $\text{Var}^*$ and $\text{Cov}^*$
the expectation, variance and covariance conditional on $X_{1:n}$ in the bootstrap world. Assuming that $n=kl$ with $l$ being the block size and $k$ being the number of blocks, the bootstrap marginal distribution is 
\begin{align*}
\rho_n^*=\frac{1}{n}\sum^{k}_{j=1}\sum^{S_j+l-1}_{i=S_j} \delta_{X_i},    
\end{align*}
where $\delta_x$ denotes a point mass at $x$, and $S_1,\dots,S_k$ are i.i.d uniform on $\{1,\dots,n-l+1\}$. 
Define $G_n^*(x)$ in the same way as $G_n(x)$ with $X_{1:n}$ being replaced by the bootstrap samples $X_{1:n}^*=\{X_1^*,\dots,X_n^*\}$.

\subsection{A sketch of the proof}

We want to show that
\begin{align}\label{eq-con-boot}
\begin{pmatrix}
G_n^*(x)  \\ 
\sqrt{n}(F(x;\hat{\theta}_n^*)-F(x;\hat{\theta}_0))
\end{pmatrix}\Rightarrow^{*}
\begin{pmatrix}
G_{\infty}(x) \\
f(x;\theta_0)U
\end{pmatrix}
\end{align}
where $\Rightarrow^*$ means convergence in distribution almost surely and $\hat{\theta}_0:=\mathbb{E}^*[\hat{\theta}_n^*]$. 
In the bootstrap world, we have an expansion similar to (\ref{eq-expan}):
\begin{align*}
\hat{\theta}_n^*-\hat{\theta}_0 = \frac{1}{n}\sum^{n}_{i=1}h(X_i^*;\hat{\theta}_0) + \frac{1}{\sqrt{n}}R_n^*,    
\end{align*}
where $R_n^* \overset{p^*}{\rightarrow} 0$, where $\overset{p^*}{\rightarrow}$ means convergence in probability almost surely. Note that 
\begin{align*}
\mathbb{E}^*\left[\frac{1}{n}\sum^{n}_{i=1}h(X_i^*;\hat{\theta}_0)\right]
=&\frac{1}{n}\sum^{k}_{j=1}\mathbb{E}^*\left[\sum^{S_j+l-1}_{i=S_j}h(X_{i};\hat{\theta}_0)\right]
\\=&\frac{k}{n^2}[\sum^{n - l + 1}_{j=1}\sum^{j+l-1}_{i=j}h(X_{i};\hat{\theta}_0) +
\sum^{n}_{j=n - l + 2}[\sum^{n}_{i=j}h(X_{i};\hat{\theta}_0) +
\sum^{j - n + l -1}_{i=1}h(X_{i};\hat{\theta}_0)]]
\\=&\frac{k}{n^2}\sum^{n}_{i=1}l h(X_{i};\hat{\theta}_0),
\end{align*}.
Moreover, we have
\begin{align*}
\text{var}^*\left(\frac{1}{\sqrt{n}}\sum^{n}_{i=1}h(X_i^*;\theta_0^*)\right)
=&\text{var}^*\left(\frac{1}{\sqrt{n}}\sum^{k}_{j=1}\sum^{S_j+l-1}_{i=S_j}h(X_{i};\hat{\theta}_0)\right)
\\=&\frac{1}{l}\text{var}^*\left(\sum^{S_1+l-1}_{i=S_1}h(X_{i};\hat{\theta}_0)\right)
\\=&\frac{1}{ln}\sum^{n}_{t=1}(W_t-\bar{W})^2
\end{align*}
with $W_t=
 \begin{cases}
\sum^{t+l-1}_{i=t}h(X_i;\hat{\theta}_0)  & \text{if } t \leq n - 1 + 1,\\
\sum^{n}_{i=t}h(X_{i};\hat{\theta}_0) +
\sum^{t - n + l -1}_{i=1}h(X_{i};\hat{\theta}_0)  & \text{if } t \geq n - 1 + 2
\end{cases}$
and $\bar{W}=\sum^{n}_{t=1}W_t/n$,
which is expected to converge to $s^2$ almost surely. Similar calculations apply to $G_n^*(x)$ and we expect that
\begin{align*}
&\text{Cov}^*(G_n^*(x),G_n^*(x'))\overset{a.s.}{\rightarrow}   \sum^{+\infty}_{h=-\infty}\text{Cov}(\mathbf{1}\{X_{h}\leq x\},\mathbf{1}\{X_0\leq x'\}),\\
&\text{Cov}^*\left(\frac{1}{\sqrt{n}}\sum^{n}_{i=1}h(X_i^*;\hat{\theta}_0), G_n^*(x)\right)\overset{a.s.}{\rightarrow} \sum^{+\infty}_{h=-\infty}\text{Cov}(h(X_{h},\theta_0),\mathbf{1}\{X_0\leq x\}).
\end{align*}
By showing the finite-dimensional convergence and tightness in the bootstrap world (conditional on the data $X_{1:n}$), we can establish \eqref{eq-con-boot}.
From the CLT, the process $G_n^*(x) = \sqrt{n}(F_n^*(x) - F_n(x))$ converges 
to 
$G_{\infty}(x)$.

For $\sqrt{n}(F(x;\hat{\theta}_n^*) - F(x;\hat{\theta}_0))$, using the first-
order Taylor 
expansion around $\hat{\theta}_0$, we have:
\[
F(x;\hat{\theta}_n^*) \approx F(x;\hat{\theta}_0) + f(x; 
\hat{\theta}_0) (\hat{\theta}_n^* - \hat{\theta}_0),
\] so
\[
\sqrt{n}(F(x;\hat{\theta}_n^*) - F(x;\hat{\theta}_0)) \approx \sqrt{n} 
(F(x;\hat{\theta}_0) + f(x; 
\hat{\theta}_0) (\hat{\theta}_n^* - \hat{\theta}_0) - F(x;\hat{\theta}_0)) 
\approx
f(x; 
\hat{\theta}_0) \sqrt{n} (\hat{\theta}_n^* - \hat{\theta}_0).
\].

Substituting the expansion of $\hat{\theta}_n^*$:
\[
\sqrt{n} (\hat{\theta}_n^* - \hat{\theta}_0) = \frac{1}{\sqrt{n}} \sum_{i=1}^{n} 
h(X_i^*; \hat{\theta}_0) + R_n^*.
\]

Since $R_n^* \overset{p^*}{\rightarrow} 0$, 
\[
\sqrt{n}(F(x;\hat{\theta}_n^*) - F(x;\hat{\theta}_0)) \approx 
f(x; \hat{\theta}_0) \left( \frac{1}{\sqrt{n}} \sum_{i=1}^{n} h(X_i^*; 
\hat{\theta}_0) \right).
\]

The term $\frac{1}{\sqrt{n}} \sum_{i=1}^{n} h(X_i^*; \hat{\theta}_0)$ 
converges in distribution to a normal random variable $U$ with variance 
$s^2$.
We can show tightness of $G_n^*(x)$ similarly to how we established 
tightness of $G_n(x)$
The results then follow from the continuous mapping theorem.

%\bibliographystyle{plain} 
%\bibliography{ref}

\end{document}

### 2024-06-13 manuscript/manuscript.tex
propositions in manuscript

@@
 \usepackage{natbib}
+\usepackage{lipsum}
 
@@
 
-\newcommand{\jy}[1]{\textcolor{blue}{JY: (#1)}}
-\newcommand{\eds}[1]{\textcolor{red}{EDS: (#1)}}
-\newcommand{\mc}[1]{\textcolor{green}{MC: (#1)}}
+\newcommand{\jy}[1]{}
+\newcommand{\eds}[1]{}
+\newcommand{\mc}[1]{}
 
@@
 function, the KS test statistic takes the form
-\begin{equation}
-  \label{eq:ks_standard}
+\[
   T_n = \sqrt{n} \sup_x | F_{n}(x) - F(x; \theta_0)|.
-\end{equation}
+\]
 As sample size $n\to \infty$, the distribution of $T_n$ converges to that of the
@@
 \citet{babu2004goodness} when the data are independent.
-As noted by 
-\citet{chandy2024sample}, a sample greater than 1600 may be necessary for 
-block bootstrap confidence intervals to have the right coverage 
-rates of parameters. 
-Therefore, although this study uses block bootstrap in a different setting,
-we expect that a large sample size may be required when the data is serially
-dependent.
 
@@
 NPBB KS test. Section~\ref{sec:simu} is divided 
-into two parts; initially, we evaluate the KS test's ability to maintain 
+into two parts; initially, we evaluate the NPBB KS test's ability to maintain 
 its size, i.e., its consistency in not rejecting the null hypothesis when 
-it is indeed true. Subsequently, we examine the test's power, assessing 
+it is indeed true. Subsequently, we examine the NPBB KS test's power, assessing 
 whether it can reject the null hypothesis when it is false. Practical 
@@
 fitted parameters, which can be obtained from any consistent estimator with
-asymptotic normality properties.  Let $F_n$ be the empirical distribution
+asymptotic normality property.  Let $F_n$ be the empirical distribution
 function based on $X_1,...,X_n$.
@@
 \begin{equation*}
-Y_n(x; \hat\theta) = \sqrt{n}(F_n(x) - F(x)) - 
-\sqrt{n}(F(x; \hat\theta_n) - F(x)).
+Y_n(x; \hat\theta) = \sqrt{n}(F_n(x) - F(x; \theta_0)) - 
+\sqrt{n}(F(x; \hat\theta_n) - F(x; \theta_0)),
 \end{equation*}
-When $\hat\theta_n$ is replaced with $\theta$, as in the standard KS testing
+where $\theta_0$ is the true parameter value of $\theta$ under~$H_0$.
+When $\hat\theta_n$ is replaced with $\theta_0$, as in the standard KS testing
 situation, the second term vanishes, and $T_n$ converges in distribution to that
-of $\sup_t | B(F(t)) |$, where $B(\cdot)$ is the standard Brownian bridge
+of $\sup_t | B(F(t; \theta_0)) |$, where $B(\cdot)$ is the standard Brownian bridge
 \citep{kolmogorov1933sulla}. With $\hat\theta_n$ in place of $\theta$, the
@@
 
-\eds{Please check consistency with how you refer to $F$.  In 
-Equation~\eqref{eq:ks_standard}, it is $F(x; \theta_0)$ where the data and 
-parameter arguments are separated by a semicolon.  At the beginning of 
-Section~\ref{sec:methods}, it is $F(\cdot \mid \theta)$, with the vertical bar
-separating the data argument from the parameter argument (and no 0 subscript
-either).   Then in this first 
-subsection it is $F(x; \hat\theta_n)$ with a semicolon separating the two 
-arguments.  Then immediately above its use is mixed with $F(x)$ without a 
-parameter argument (implying it is the true parameter $\theta$). This continues
-throughout the document. I suggest either using consistent notation throughout, 
-or explicitly defining any shortened/simplified notation at its first use.}
-\mc{switched everything to semicolons}
+%\eds{Please check consistency with how you refer to $F$.  In 
+%Equation~\eqref{eq:ks_standard}, it is $F(x; \theta_0)$ where the data and 
+%parameter arguments are separated by a semicolon.  At the beginning of 
+%Section~\ref{sec:methods}, it is $F(\cdot \mid \theta)$, with the vertical bar
+%separating the data argument from the parameter argument (and no 0 subscript
+%either).   Then in this first 
+%subsection it is $F(x; \hat\theta_n)$ with a semicolon separating the two 
+%arguments.  Then immediately above its use is mixed with $F(x)$ without a 
+%parameter argument (implying it is the true parameter $\theta$). This continues
+%throughout the document. I suggest either using consistent notation throughout, 
+%or explicitly defining any shortened/simplified notation at its first use.}
+%\mc{switched everything to semicolons}
+%\jy{replaced $F$ with $F(\cdot; \theta_0)$}
 
@@
 
-\subsection{Nonparametric bootstrap (NPB) for independent data}
+\subsection{NPB for independent data}
 
@@
 Using the bootstrap (asymptotic) theory, we can approximate the distribution of
-$\sqrt{n}(F_n(x) - F(x))$ and $\sqrt{n}(F(x; \hat\theta_n) - F(x))$
+$\sqrt{n}(F_n(x) - F(x; \theta_0))$ and
+$\sqrt{n}(F(x; \hat\theta_n) - F(x; \theta_0))$
 by that of $\sqrt{n}(F^{(b)}_n(x) - F_n(x))$ and
@@
 
-In summary, the procedure of the NPB KS test for independent
-sample is 
+In summary, the procedure of the NPB KS test for an independent sample is
 summarized as follows. Repeat the following steps for $b \in \{1, ..., B\}$.
@@
 \item
-  Generate $X^{(b)}_1,...,X^{(b)}_n$ by applying basic bootstrap 
-  on the original sample as
-  defined previously.
+  Generate $X^{(b)}_1,...,X^{(b)}_n$ by sampling $X_1, \ldots, X_n$
+  with replacement.
 \item
@@
 	$\hat\theta^{(b)}_n$ of $\theta$ from $X^{(b)}_1,...,X^{(b)}_n$.  
-	\eds{$F_\theta$ has not yet been defined.}\mc{addressed}
+	%\eds{$F_\theta$ has not yet been defined.}\mc{addressed}
 \item
@@
   \[
-    T^{(b)}_n = \sup_x | \sqrt{n}\left(F^{(b)}_n(x) 
-    - F(x; \hat\theta^{(b)}_n)\right) - B_n(x) |.
+    T^{(b)}_n = \sup_x \Big\vert \sqrt{n}\left(F^{(b)}_n(x) 
+    - F(x; \hat\theta^{(b)}_n)\right) - B_n(x) \Big\vert.
   \]
@@
 
-\subsection{Nonparametric block bootstrap (NPBB) for stationary series}
+\subsection{NPBB for stationary series}
+\label{sub:npbb}
 
@@
 the distribution of $T_n$. Therefore, the p-value of the observed statistic
-$T_n$ can be assessed by positioning it agains the empirical distribution of
+$T_n$ can be assessed by positioning it against the empirical distribution of
 $T_n^{(b)}$, $b = 1, \ldots, B$.
 
-\eds{Do we not define $Y^{(b)}_n(x)$ in terms of the $E_n(\cdot)$'s instead of 
-the $E(\cdot)$ above and below?}\mc{$E_n$ was a typo}
+%\eds{Do we not define $Y^{(b)}_n(x)$ in terms of the $E_n(\cdot)$'s instead of 
+%  the $E(\cdot)$ above and below?}\mc{$E_n$ was a typo}
+
+We will assume that the time series $\{X_t\}$ is stationary and strongly mixing, 
+and $1/l+l/n\rightarrow 0$. We aim to show that under suitable assumptions
+\begin{enumerate}
+    \item $T_n \overset{d}{\rightarrow} \sup_x |G_{\infty}(x)+f(x;\theta_0)U|$ 
+    for some Gaussian process $G_{\infty}(\cdot)$ and Gaussian random variable 
+    $U$ defined below.
+    \item $|\mathbb{P}(T_n^*\leq x|X_{1:n}) - 
+    \mathbb{P}(T_n\leq x)|\overset{a.s.}{\rightarrow} 0$ for any fixed $x,$ 
+    where $X_{1:n}:=\{X_1,\dots,X_n\}$ and $T_n^*$ is the the statistic computed 
+    based on the bootstrap sample $X_1^*,\dots,X_n^*$). 
+    Following the arguments in the proof of the Glivenko-Cantelli Theorem, we 
+    may further strengthen this result to allow uniform convergence over $x$: 
+    in other words, $\sup_x|\mathbb{P}(T_n^*\leq x|X_{1:n}) - 
+    \mathbb{P}(T_n\leq x)|\overset{a.s.}{\rightarrow} 0$.
+\end{enumerate}
+Sketches of the proofs for these propositions are shown as supporting 
+information.
 
@@
 \item
-  Fit $F_\theta$ to $X^{(b)}_1,...,X^{(b)}_n$ and obtain estimate 
-	$\hat\theta^{(b)}_n$ of $\theta$.
+  %Fit $F_\theta$ to $X^{(b)}_1,...,X^{(b)}_n$ and obtain estimate 
+	%$\hat\theta^{(b)}_n$ of $\theta$.
+	Obtain parametrically fitted parameters 
+	$\hat\theta^{(b)}_n$ of $\theta$ from $X^{(b)}_1,...,X^{(b)}_n$.  
+	\eds{changed this to remove $F_\theta$, please check}\mc{looks good}
 \item
@@
 The p-value of the block bootstrap KS test can be approximated
-as $p = \sum_{b=1}^N I\{T^{(b)}_n > T_n\} / B$.
+as $p = \sum_{b=1}^B I\{T^{(b)}_n > T_n\} / B$.
 
@@
 for some unspecified $\alpha$ and $\beta$.
-\eds{Vertical bar vs semicolon to separate data and parameter arguments.}
-\mc{changed everything to semicolon}
+%\eds{Vertical bar vs semicolon to separate data and parameter arguments.}
+%\mc{changed everything to semicolon}
 For the block
@@
 we used $B = 1000$ and $l = \lceil n^{1/3} \rceil$.
-For each setting for $F$, $\tau$, and $n$, we replicate the method 1000 times 
+For each setting for $F$, $\tau$, and $n$, we replicate the method 10000 times 
 to get the distribution of the p-values $p_r$ for
-$r \in \{1, \dots, 1000\}$
+$r \in \{1, \dots, 10000\}$
 for the test when applied to samples from the same data generating process.
-\eds{I assume $r$ is for replicate?  Please define and include how many 
-total replicates you are using.} \mc{addressed}
+%\eds{I assume $r$ is for replicate?  Please define and include how many 
+%total replicates you are using.} \mc{addressed}
 
@@
 $\tau$ is lower than 0.25. For Kendall's $\tau \geq 0.5$, a sample larger than
-$n = 200$ seems necessary for the p-values to be uniformly
-\eds{uniformly?}\mc{addressed} distributed. For
+$n = 200$ seems necessary for the p-values to be uniformly distributed. For
 Kendall's $\tau \geq 0.75$, a sample larger than $n = 800$ appears to be 
@@
 \centering
-\caption{Rejection rates or true size for test that sample follows its true
+\caption{Empirical sizes (ratio of rejection rate to significance level)
+for the test that sample follows its true
                     distribution family for
                    different values of AR(1) coefficient and for different 
-                   significance levels or estimated sizes.
+                   significance levels.
 		\eds{Not sure if it will help presentation or interpretation, but you could
 	consider presenting the values inside the table as estimated size/true size}
-	\mc{addressed}}
+	\mc{addressed}
+	\eds{I meant reporting the ratio, e.g, dividing all values currently in the    first row by 0.01, dividing all values in the second row by 0.05. Sometimes this
+	is helpful if there is a conservative or liberal pattern, which there seems
+	to be as $|\tau|$ increases away from zero, but it may be fine to leave it as
+	is.}\mc{how does this look?}}
 \label{table:size}
@@
   \midrule
-{$N(8,8)$} & {100} & 0.01 & 0.052 & 0.013& 0.007 & 0.011 & 0.009 & 0.013 & 0.058 \\ 
-& & 0.05 & 0.138 & 0.061 & 0.038 & 0.059 & 0.054 & 0.083 & 0.178 \\ 
-& & 0.10 & 0.238 & 0.125 & 0.089 & 0.124 & 0.102 & 0.152 & 0.272 \\ 
-& {200} & 0.01 & 0.043 & 0.009 & 0.006 & 0.017 & 0.011 & 0.018 & 0.062 \\ 
-& & 0.05 & 0.130 & 0.058 & 0.041 & 0.051 & 0.053 & 0.061 & 0.175 \\ 
-& & 0.10 & 0.202 & 0.120 & 0.101 & 0.107 & 0.110 & 0.125 & 0.266 \\ 
-& {400} & 0.01 & 0.037 & 0.011 & 0.009 & 0.014 & 0.013 & 0.009 & 0.043 \\ 
-& & 0.05 & 0.109 & 0.047 & 0.052 & 0.061 & 0.044 & 0.064 & 0.133 \\ 
-& & 0.10 & 0.174 & 0.099 & 0.098 & 0.108 & 0.099 & 0.123 & 0.212 \\ 
-& {800} & 0.01 & 0.023 & 0.011 & 0.008 & 0.011 & 0.011 & 0.011 & 0.038 \\ 
-& & 0.05 & 0.088 & 0.043 & 0.040 & 0.055 & 0.042 & 0.053 & 0.125 \\ 
-& & 0.10 & 0.166 & 0.097 & 0.095 & 0.102 & 0.107 & 0.109 & 0.196 \\ [1ex]
-{$\Gamma(8,1)$} & {100} & 0.01 & 0.056 & 0.014 & 0.006 & 0.011 & 0.009 & 0.015 & 0.063 \\
-  & & 0.05 & 0.144 & 0.063 & 0.037 & 0.059 & 0.053 & 0.083 & 0.180 \\ 
-  & & 0.10 & 0.239 & 0.125 & 0.092 & 0.126 & 0.103 & 0.150 & 0.273 \\ 
-  & {200} & 0.01 & 0.045 & 0.012 & 0.005 & 0.017 & 0.012 & 0.020 & 0.066 \\ 
-  & & 0.05 & 0.127 & 0.058 & 0.045 & 0.052 & 0.054 & 0.056 & 0.173 \\ 
-  & & 0.10 & 0.204 & 0.123 & 0.103 & 0.106 & 0.108 & 0.129 & 0.263 \\ 
-  & {400} & 0.01 & 0.038 & 0.012 & 0.010 & 0.014 & 0.010 & 0.010 & 0.045 \\ 
-  & & 0.05 & 0.106 & 0.049 & 0.051 & 0.062 & 0.042 & 0.063 & 0.128 \\ 
-  & & 0.10 & 0.175 & 0.097 & 0.098 & 0.107 & 0.100 & 0.122 & 0.211 \\ 
-  & {800} & 0.01 & 0.024 & 0.011 & 0.007 & 0.011 & 0.011 & 0.010 & 0.039 \\ 
-  & & 0.05 & 0.089 & 0.043 & 0.041 & 0.055 & 0.044 & 0.051 & 0.121 \\ 
-  & & 0.10 & 0.169 & 0.096 & 0.094 & 0.100 & 0.109 & 0.110 & 0.194 \\ 
+{$N(8,8)$} & {100} & 0.01 & 5.210 & 1.240 & 1.120 & 1.060 & 1.140 & 1.580 & 5.630 \\ 
+& & 0.05 & 2.940 & 1.256 & 1.090 & 1.096 & 1.150 & 1.450 & 3.410 \\ 
+& & 0.10 & 2.277 & 1.186 & 1.147 & 1.072 & 1.154 & 1.424 & 2.714 \\ 
+& {200} & 0.01 & 4.390 & 1.130 & 0.900 & 1.140 & 1.090 & 1.380 & 5.900 \\ 
+& & 0.05 & 2.556 & 1.120 & 1.020 & 1.064 & 1.092 & 1.382 & 3.452 \\ 
+& & 0.10 & 2.080 & 1.123 & 1.069 & 1.086 & 1.051 & 1.332 & 2.650 \\ 
+& {400} & 0.01 & 3.240 & 1.070 & 0.990 & 1.080 & 0.970 & 1.260 & 4.670 \\ 
+& & 0.05 & 2.032 & 1.000 & 0.994 & 1.120 & 0.978 & 1.184 & 2.836 \\ 
+& & 0.10 & 1.734 & 1.023 & 1.002 & 1.089 & 1.017 & 1.192 & 2.232 \\ 
+& {800} & 0.01 & 2.520 & 0.900 & 0.980 & 1.110 & 1.020 & 1.350 & 3.540 \\ 
+& & 0.05 & 1.766 & 1.008 & 0.972 & 0.956 & 0.962 & 1.236 & 2.438 \\ 
+& & 0.10 & 1.555 & 1.026 & 0.986 & 0.961 & 0.997 & 1.206 & 2.044 \\ [1ex]
+{$\Gamma(8,1)$} & {100} & 0.01 & 4.880 & 1.420 & 1.170 & 1.240 & 1.110 & 1.610 & 5.760 \\ 
+  & & 0.05 & 2.850 & 1.282 & 1.222 & 1.170 & 1.178 & 1.464 & 3.374 \\ 
+  & & 0.10 & 2.241 & 1.224 & 1.147 & 1.175 & 1.150 & 1.375 & 2.679 \\ 
+  & {200} & 0.01 & 4.080 & 1.000 & 0.890 & 1.220 & 1.160 & 1.430 & 6.080 \\ 
+  & & 0.05 & 2.510 & 1.118 & 1.014 & 1.068 & 1.116 & 1.290 & 3.380 \\ 
+  & & 0.10 & 1.991 & 1.105 & 1.022 & 1.048 & 1.072 & 1.233 & 2.664 \\ 
+  & {400} & 0.01 & 3.140 & 0.970 & 1.140 & 0.940 & 1.030 & 1.310 & 4.300 \\ 
+  & & 0.05 & 2.004 & 0.964 & 1.042 & 1.062 & 1.122 & 1.236 & 2.808 \\ 
+  & & 0.10 & 1.697 & 1.025 & 1.066 & 1.018 & 1.100 & 1.177 & 2.232 \\ 
+  & {800} & 0.01 & 2.490 & 0.920 & 1.130 & 1.120 & 1.000 & 1.130 & 3.810 \\ 
+  & & 0.05 & 1.804 & 0.976 & 1.064 & 1.022 & 1.086 & 1.196 & 2.474 \\ 
+  & & 0.10 & 1.561 & 1.024 & 1.072 & 1.034 & 1.067 & 1.177 & 1.997 \\ 
    \bottomrule
@@
 significance levels 0.01, 0.05, and 0.10, Table~\ref{table:size}
-summarizes the empirical sizes of the tests based on 1000 replicates.
-\eds{Number of replicates needs to be stated earlier.  Also, is 1000 enough
-to truly evaluate whether size is good at the 0.01 level?}
+summarizes the empirical sizes of the tests based on 10000 replicates.
+\eds{Is 1000 enough to truly evaluate whether size is good at the 0.01 level?}
 The agreement between the empirical sizes and the nominal size
-improves as sample size increases, as expected. For $\tau = -0.75$
+improves as sample size improves, as expected. For $\tau = -0.75$
 and $\tau = 0.75$, a sample size as large as 800 is still not sufficient for the
@@
 lower, it is still reasonable to recommend our method with $n \ge 400$.
+This recommendation echoes the high sample size requirement for
+confidence intervals constructed with block bootstrapping in
+estimating location, scale, and autocorrelation parameters of
+stationary series~\citep{chandy2024sample}.
 
@@
 from $\Gamma(8, 1)$. For each setting for $F$, $\tau$, and $n$, we replicate the 
-method $1000$ times 
+method $10000$ times 
 to obtain a p-value $p_r$ for each $r \in \{1, \ldots, 1000\}$.
@@
   \includegraphics[scale=1]{figures/rr}
-  \caption{Power curve as a function of $\tau$ for
+  \caption{Empirical power curve as a function of $\tau$ for
     $n \in \{100, 200, 400, 800\}$ and true marginal distribution 
@@
 with the proposed NPBB method.
-\eds{Introduce this acronym earlier (as early as in the intro), and use it 
-throughout the ms.}\mc{addressed}
 For comparison, we tested the same hypotheses using 1) the
@@
 \centering
-\caption{P-values for 4 years of S\&P 500 stock return 
-  data using different degrees of freedom for Student's $t$ distribution.
-	\eds{how are ``different durations'' reflected in this table?}\mc{addressed}
+\caption{P-values for testing marginal Student's $t$ distribution on  
+  4 years of daily returns of S\&P 500 with $B = 10,000$
+  using different degrees of freedom~$\nu$. 
   NPBB: nonparametric block bootstrap;
@@
 (I would expect a reviewer to ask for this comparison anyway.)}
+\jy{we could design scenarios where SPBB fails: some dependency
+  structure that cannot be well-approximated by ARMA.}
 
@@
 
-\eds{can Mathew's AJUR paper be cited somewhere in this document?}
-\mc{addressed}
-
 %\backmatter
@@
 studies are publicly available in a GitHub repo:
-\url{https://github.com/mathewchandy03/Bootstrap_KS_Test}
-\jy{Give the link}\mc{addressed}
+\url{https://github.com/mathewchandy03/Bootstrap_KS_Test}.
 
@@
 
+\section*{Supporting Information}
+
+Additional information for this article is available.
+A proof of our two propositions in \ref{sub:npbb} is provided.
+
 \end{document}

### 2024-06-14 manuscript/manuscript.tex
formal propositions

@@
 
-%\eds{Do we not define $Y^{(b)}_n(x)$ in terms of the $E_n(\cdot)$'s instead of 
-%  the $E(\cdot)$ above and below?}\mc{$E_n$ was a typo}
-
-We will assume that the time series $\{X_t\}$ is stationary and strongly mixing, 
-and $1/l+l/n\rightarrow 0$. We aim to show that under suitable assumptions
-\begin{enumerate}
-    \item $T_n \overset{d}{\rightarrow} \sup_x |G_{\infty}(x)+f(x;\theta_0)U|$ 
-    for some Gaussian process $G_{\infty}(\cdot)$ and Gaussian random variable 
-    $U$ defined below.
-    \item $|\mathbb{P}(T_n^*\leq x|X_{1:n}) - 
-    \mathbb{P}(T_n\leq x)|\overset{a.s.}{\rightarrow} 0$ for any fixed $x,$ 
-    where $X_{1:n}:=\{X_1,\dots,X_n\}$ and $T_n^*$ is the the statistic computed 
-    based on the bootstrap sample $X_1^*,\dots,X_n^*$). 
-    Following the arguments in the proof of the Glivenko-Cantelli Theorem, we 
-    may further strengthen this result to allow uniform convergence over $x$: 
-    in other words, $\sup_x|\mathbb{P}(T_n^*\leq x|X_{1:n}) - 
-    \mathbb{P}(T_n\leq x)|\overset{a.s.}{\rightarrow} 0$.
-\end{enumerate}
-Sketches of the proofs for these propositions are shown as supporting 
-information.
-
 In summary, the procedure of the NPBB test is 
@@
 \end{enumerate}
-
 The p-value of the block bootstrap KS test can be approximated
 as $p = \sum_{b=1}^B I\{T^{(b)}_n > T_n\} / B$.
+
+\jy{Cite Kunsch (1989)}
+
+\jy{In the supplement, use the proof environment to give proof
+  sketches; make the title ``Supplement to `paper title` by
+  authors''. No need to use their template for supp.}
+
+Assume that the time series $\{X_t\}$ is stationary and
+strongly mixing. The following results provides theoretical validity
+of the NPBB procedure of the KS test. Sketches of their proofs are
+in the Supplementary Information, with most arguments similar to those
+in \citet{kunsch1989jackknife}.
+
+\begin{proposition}\label{prop:Tn}
+  As $1/l+l/n\rightarrow 0$,
+  \[
+    T_n \overset{d}{\rightarrow}
+    \sup_x \big\vert G_{\infty}(x)+f(x;\theta_0)U \big\vert
+  \]
+  for some appropriately defined Gaussian process $G_{\infty}(\cdot)$
+  and Gaussian random variable  $U$.
+\end{proposition}
+
+\begin{proposition}\label{prop:Tnboot}
+  As $1/l+l/n\rightarrow 0$,
+  \[
+    \big\vert \mathbb{P}(T_n^*\leq x \mid \{X_t: t = 1, \ldots, n\}) -
+    \mathbb{P}(T_n\leq x) \big\vert
+    \overset{a.s.}{\rightarrow} 0
+  \]
+  for any fixed $x$, where and $T_n^*$ is the the statistic computed 
+  based on the bootstrap sample $\{X_t^*: t = 1, \ldots, n\}$.
+\end{proposition}
+
+Following the arguments in the proof of the Glivenko--Cantelli
+Theorem, the result in Proposition~\ref{prop:Tnboot} can be further
+strengthened to allow uniform convergence over $x$. That is,
+\[
+  \sup_x \big \vert
+  \mathbb{P}(T_n^*\leq x|X_{1:n}) - \mathbb{P}(T_n\leq x) \big\vert
+  \overset{a.s.}{\rightarrow} 0.
+\]
 

### 2024-06-14 manuscript/manuscript.tex
set up proof envion in supp

@@
 
-\author[1]{Elizabeth Schifano}
+\author[1]{Elizabeth D. Schifano}
 
@@
 	$\hat\theta^{(b)}_n$ of $\theta$ from $X^{(b)}_1,...,X^{(b)}_n$.  
-	%\eds{$F_\theta$ has not yet been defined.}\mc{addressed}
 \item
@@
 \item
-  %Fit $F_\theta$ to $X^{(b)}_1,...,X^{(b)}_n$ and obtain estimate 
-	%$\hat\theta^{(b)}_n$ of $\theta$.
   Obtain parametrically fitted parameters 
   $\hat\theta^{(b)}_n$ of $\theta$ from $X^{(b)}_1,...,X^{(b)}_n$.  
-	\eds{changed this to remove $F_\theta$, please check}\mc{looks good}
 \item
@@
 
-\jy{Cite Kunsch (1989)}
+\jy{Recover the definition of jy and eds for comments. Prepare two
+  definitions in the source so that one can be easily commented out.}
 
-\jy{In the supplement, use the proof environment to give proof
-  sketches; make the title ``Supplement to `paper title` by
-  authors''. No need to use their template for supp.}
+\jy{Cite Kunsch (1989) in the proof as appropriate}
+
+\jy{In the Supp: make sure notations are consistent (e.g., use
+  $\{X_t: t = 1, \ldots, n\}$ for observed data);
+  clean up the styles (linewidth etc.)}
 
@@
 of the NPBB procedure of the KS test. Sketches of their proofs are
-in the Supplementary Information, with most arguments similar to those
+in the Supporting Information, with most arguments similar to those
 in \citet{kunsch1989jackknife}.
@@
 $X_t \sim \Gamma(\cdot ; \alpha, \beta), \quad t = 1, \ldots, n$.
-for some unspecified $\alpha$ and $\beta$.
-%\eds{Vertical bar vs semicolon to separate data and parameter arguments.}
-%\mc{changed everything to semicolon}
-For the block
-bootstrap step,
+for some unspecified $\alpha$ and $\beta$. For the block bootstrap step,
 we used $B = 1000$ and $l = \lceil n^{1/3} \rceil$.
@@
 for the test when applied to samples from the same data generating process.
-%\eds{I assume $r$ is for replicate?  Please define and include how many 
-%total replicates you are using.} \mc{addressed}
 
@@
 \caption{Empirical sizes (ratio of rejection rate to significance level)
-for the test that sample follows its true
-                    distribution family for
+for the test that sample follows its true distribution family for
 different values of AR(1) coefficient and for different 
@@
 
-Additional information for this article is available.
-A proof of our two propositions in \ref{sub:npbb} is provided.
+The proofs of the two propositions in \ref{sub:npbb} are sketched in
+the supplement.
 

### 2024-06-14 manuscript/supplement.tex
set up proof envion in supp

--- 2024-06-13 manuscript/main.tex
@@
-\documentclass[11pt]{article}
+\documentclass[12pt]{article}
 
@@
 
+\title{Supporting Information for
+  ``Nonparametric Block Bootstrap Kolmogorov-Smirnov Goodness-of-Fit
+  Test''}
+\author{Mathew Chandy, Elizabeth D. Schifano, Jun Yan, and Xianyang
+  Zhang}
+
 \begin{document}
+\maketitle
 
-\section{Asymptotic limit of the KS-statistic}
+\section{Asymptotic Limit of the KS Statistic}
+
+\begin{proof}[Proof of Proposition~1]
 We first derive the limiting distribution of the KS statistic under the null. Suppose $\hat{\theta}_n$ admits the expansion:
@@
 
-\section{Bootstrap consistency}
-\subsection{Preliminaries}
+\end{proof}
+
+\section{Bootstrap Consistency}
+
 Denote by $\mathbb{E}^*$, $\text{Var}^*$ and $\text{Cov}^*$
@@
 
-\subsection{A sketch of the proof}
-
+\begin{proof}]Proof of Proposition~2]
     We want to show that
@@
 The results then follow from the continuous mapping theorem.
+\end{proof}
 

### 2024-06-16 manuscript/manuscript.tex
cleaning up of supplement

@@
 
-\newcommand{\jy}[1]{}
-\newcommand{\eds}[1]{}
-\newcommand{\mc}[1]{}
+\newcommand{\jy}[1]{\textcolor{blue}{JY: (#1)}}
+\newcommand{\eds}[1]{\textcolor{red}{EDS: (#1)}}
+\newcommand{\mc}[1]{\textcolor{green}{MC: (#1)}}
 
@@
 the KS statistic under $H_0$. In particular, we
-use the distribution of $\sqrt{n}(F^{(b)}_n(x) - E[F^{(b)}_n(x)])$
+use the distribution of $\sqrt{n}(F^{(b)}_n(x) - \mathbb{E}^{(b)}[F^{(b)}_n(x)])$
 as an approximation of the distribution of
-$\sqrt{n}(F_n(x) - F(x))$, and the distribution of 
-$\sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; E[\hat\theta^{(b)}_n]))$ as
-an approximation of the distribution of $\sqrt{n}(F(x; \theta_n) - F(x))$.
-The expected values $E[F^{(b)}_n(x)]$ and
-$E[\hat\theta^{(b)}_n]$ can be approximated by, respectively,
-$E[F^{(b)}_n(x)] = \frac{1}{B}\sum_{b = 1}^BF^{(b)}_n(x)$ and
-$E[\hat\theta^{(b)}_n]  =  \frac{1}{B}\sum_{b = 1}^B\hat\theta^{(b)}_n$.
+$\sqrt{n}(F_n(x) - F(x; \theta_0))$, and the distribution of 
+$\sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; \mathbb{E}^{(b)}[\hat\theta^{(b)}_n]))$ as
+an approximation of the distribution of 
+$\sqrt{n}(F(x; \hat\theta_n) - F(x; \theta_0))$.
+Here $\mathbb{E}^{(b)}$ denotes the expectation with respect to the bootstrap 
+distribution 
+(i.e., the randomness due
+to the resampling using block bootstrap) conditional on the observations 
+$X_1, \dots, X_n$.
+The expected values $\mathbb{E}^{(b)}[F^{(b)}_n(x)]$ and
+$\mathbb{E}^{(b)}[\hat\theta^{(b)}_n]$ can be approximated by, respectively,
+$\mathbb{E}^{(b)}[F^{(b)}_n(x)] = \frac{1}{B}\sum_{b = 1}^BF^{(b)}_n(x)$ and
+$\mathbb{E}^{(b)}[\hat\theta^{(b)}_n]  =  \frac{1}{B}\sum_{b = 1}^B\hat\theta^{(b)}_n$.
 
@@
 \begin{align*}
-  Y^{(b)}_n(x) &= \sqrt{n}(F^{(b)}_n(x) - E[F^{(b)}_n(x)]) - 
-             \sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; E[\hat\theta^{(b)}_n)]) \\
+  Y^{(b)}_n(x) &= \sqrt{n}(F^{(b)}_n(x) - \mathbb{E}^{(b)}[F^{(b)}_n(x)]) - 
+             \sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; \mathbb{E}^{(b)}[\hat\theta^{(b)}_n)]) \\
            &= \sqrt{n}(F^{(b)}_n(x) - F(x; \hat\theta^{(b)}_n)) -
-             \sqrt{n}(E[F^{(b)}_n(x)] - F(x; E[\hat\theta^{(b)}_n])),
+             \sqrt{n}(\mathbb{E}^{(b)}[F^{(b)}_n(x)] - F(x; \mathbb{E}^{(b)}[\hat\theta^{(b)}_n])),
 \end{align*}
@@
   where 
-  $B_{n}(x) = \sqrt{n}(E[F^{(b)}_n(x)] - 
-  F(x; E[\hat\theta^{(b)}_n]))$ is the known
+  $B_{n}(x) = \sqrt{n}(\mathbb{E}^{(b)}[F^{(b)}_n(x)] - 
+  F(x; \mathbb{E}^{(b)}[\hat\theta^{(b)}_n]))$ is the known
   bias term.
@@
   definitions in the source so that one can be easily commented out.}
+\mc{addressed}
 
@@
   clean up the styles (linewidth etc.)}
+\mc{addressed}
 
@@
   for any fixed $x$, where and $T_n^*$ is the the statistic computed 
-  based on the bootstrap sample $\{X_t^*: t = 1, \ldots, n\}$.
+  based on the bootstrap sample $\{X_t^{(b)}: t = 1, \ldots, n\}$.
 \end{proposition}

### 2024-06-16 manuscript/supplement.tex
cleaning up of supplement

@@
 \begin{proof}[Proof of Proposition~1]
-We first derive the limiting distribution of the KS statistic under the null. Suppose $\hat{\theta}_n$ admits the expansion:
+We first derive the limiting distribution of the KS statistic under the null. 
+Suppose $\hat{\theta}_n$ admits the expansion:
 \begin{align}\label{eq-expan}
-\hat{\theta}_n-\theta_0 = \frac{1}{n}\sum^{n}_{i=1}h(X_i;\theta_0) + \frac{1}{\sqrt{n}}R_n,    
+\hat{\theta}_n-\theta_0 = \frac{1}{n}\sum^{n}_{t=1}h(X_i;\theta_0) + 
+\frac{1}{\sqrt{n}}R_n,    
 \end{align}
-where $h(\cdot;\theta_0)$ is the influence function with $\mathbb{E}[h(X_i;\theta_0)]=0$ and $R_n$ is the remainder term satisfying that
-$R_n\overset{p}{\rightarrow} 0.$ Write $G_n(x):=\sqrt{n}(F_n(x)-F(x))$ and let $f(x;\theta)=\partial F(x;\theta)/\partial \theta$. We assume $\theta \in \mathbb{R}$ for ease of presentation.
+where $h(\cdot;\theta_0)$ is the influence function with 
+$\mathbb{E}[h(X_i;\theta_0)]=0$ and $R_n$ is the remainder term satisfying that
+$R_n\overset{p}{\rightarrow} 0.$ Write $G_n(x):=\sqrt{n}(F_n(x) - 
+F(x; \theta_0))$ 
+and let $f(x;\theta)=\partial F(x;\theta)/\partial \theta$. We assume 
+$\theta \in \mathbb{R}$ for ease of presentation.
 
-Given any $x_1,\dots,x_m$ in the domain of $F$, by the CLT for weakly dependent time series, we have the joint convergence of 
+Given any $x_1,\dots,x_m$ in the domain of $F$, by the CLT for weakly dependent 
+time series, we have the joint convergence of 
 $V_n:=(G_n(x_1),\dots,G_n(x_m),\sqrt{n}(\hat{\theta}_n-\theta_0))$
-to some Gaussian limit, with the covariance matrix being $\Sigma_{m+1}=\lim_{n\rightarrow+\infty}\text{Cov}(V_n)$.
+to some Gaussian limit, with the covariance matrix being 
+$\Sigma_{m+1}=\lim_{n\rightarrow+\infty}\text{Cov}(V_n)$.
 %\begin{align*}
@@
 \end{align*}
-jointly, where $G_{\infty}(x)$ is a Gaussian process with the covariance function defined as
+jointly, where $G_{\infty}(x)$ is a Gaussian process with the covariance 
+function defined as
 \begin{align*}
-\text{Cov}(G_{\infty}(x),G_{\infty}(x'))=& \lim_{n\rightarrow+\infty}\frac{1}{n}\sum^{n}_{i,j=1}\text{Cov}(\mathbf{1}\{X_i\leq x\},\mathbf{1}\{X_j\leq x'\})
-\\=& \sum^{+\infty}_{h=-\infty}\text{Cov}(\mathbf{1}\{X_{h}\leq x\},\mathbf{1}\{X_0\leq x'\}),
+\text{Cov}(G_{\infty}(x),G_{\infty}(x'))=& 
+\lim_{n\rightarrow+\infty}\frac{1}{n}\sum^{n}_{i,j=1}
+\text{Cov}(\mathbf{1}\{X_i\leq x\},\mathbf{1}\{X_j\leq x'\})
+\\=& \sum^{+\infty}_{h=-\infty}\text{Cov}(\mathbf{1}\{X_{h}\leq x\},
+\mathbf{1}\{X_0\leq x'\}),
 \end{align*}
@@
 \begin{align*}
-s^2=\lim_{n\rightarrow+\infty}\frac{1}{n}\sum^{n}_{i,j=1}\text{Cov}(h(X_i,\theta_0),h(X_j;\theta_0))
+s^2=\lim_{n\rightarrow+\infty}\frac{1}{n}\sum^{n}_{i,j=1}\text{Cov}(h(X_i,
+\theta_0),h(X_j;\theta_0))
 = \sum^{+\infty}_{h=-\infty}\text{Cov}(h(X_{h},\theta_0),h(X_0;\theta_0)),
@@
 \frac{1}{n}\sum^{n}_{i,j=1}\text{Cov}(h(X_i,\theta_0),\mathbf{1}\{X_j\leq x\})
-\\=&\sum^{+\infty}_{h=-\infty}\text{Cov}(h(X_{h},\theta_0),\mathbf{1}\{X_0\leq x\}).
+\\=&\sum^{+\infty}_{h=-\infty}
+\text{Cov}(h(X_{h},\theta_0),\mathbf{1}\{X_0\leq x\}).
 \end{align*}
@@
 
-Denote by $\mathbb{E}^*$, $\text{Var}^*$ and $\text{Cov}^*$
-the expectation, variance and covariance conditional on $X_{1:n}$ in the bootstrap world.
-Assuming that $n=kl$ with $l$ being the block size and $k$ being the number of blocks, the bootstrap marginal distribution is
+Denote by $\mathbb{E}^{(b)}$, $\text{Var}^{(b)}$ and $\text{Cov}^{(b)}$
+the expectation, variance and covariance conditional on 
+$\{X_t: t = 1, \ldots, n\}$ in 
+the bootstrap world. Assuming that $n=kl$ with $l$ being the block size and $k$ 
+being the number of blocks, the bootstrap marginal distribution is 
 \begin{align*}
-\rho_n^*=\frac{1}{n}\sum^{k}_{j=1}\sum^{S_j+l-1}_{i=S_j} \delta_{X_i},    
+\rho_n^{(b)}=\frac{1}{n}\sum^{k}_{j=1}\sum^{S_j+l-1}_{i=S_j} \delta_{X_i},    
 \end{align*}
-where $\delta_x$ denotes a point mass at $x$, and $S_1,\dots,S_k$ are i.i.d uniform on $\{1,\dots,n-l+1\}$. 
-Define $G_n^*(x)$ in the same way as $G_n(x)$ with $X_{1:n}$ being replaced by the bootstrap samples $X_{1:n}^*=\{X_1^*,\dots,X_n^*\}$.
+where $\delta_x$ denotes a point mass at $x$, and $S_1,\dots,S_k$ are i.i.d 
+uniform on $\{1,\dots,n-l+1\}$. 
+Define $G_n^{(b)}(x)$ in the same way as $G_n(x)$ with $X_1, \dots, X_n$ being 
+replaced by the bootstrap samples $X_{1:n}^{(b)}=\{X_1^{(b)},\dots,X_n^{(b)}\}$.
 
-\begin{proof}]Proof of Proposition~2]
+\begin{proof}[Proof of Proposition~2]
     We want to show that
@@
 \begin{pmatrix}
-G_n^*(x)  \\ 
-\sqrt{n}(F(x;\hat{\theta}_n^*)-F(x;\hat{\theta}_0))
+G_n^{(b)}(x)  \\ 
+\sqrt{n}(F(x;\hat{\theta}_n^{(b)})-F(x;\hat{\theta}_0))
 \end{pmatrix}\Rightarrow^{*}
@@
 \end{align}
-where $\Rightarrow^*$ means convergence in distribution almost surely and $\hat{\theta}_0:=\mathbb{E}^*[\hat{\theta}_n^*]$. 
+where $\Rightarrow^*$ means convergence in distribution almost surely and 
+$\hat{\theta}_0:=\mathbb{E}^{(b)}[\hat{\theta}_n^{(b)}]$. 
 In the bootstrap world, we have an expansion similar to (\ref{eq-expan}):
 \begin{align*}
-\hat{\theta}_n^*-\hat{\theta}_0 = \frac{1}{n}\sum^{n}_{i=1}h(X_i^*;\hat{\theta}_0) + \frac{1}{\sqrt{n}}R_n^*,    
+\hat{\theta}_n^{(b)}-\hat{\theta}_0 = \frac{1}{n}\sum^{n}_{i=1}h(X_i^{(b)};
+\hat{\theta}_0) + \frac{1}{\sqrt{n}}R_n^{(b)},    
 \end{align*}
-where $R_n^* \overset{p^*}{\rightarrow} 0$, where $\overset{p^*}{\rightarrow}$ means convergence in probability almost surely. Note that 
+where $R_n^{(b)} \overset{p^*}{\rightarrow} 0$, where 
+$\overset{p^*}{\rightarrow}$ means convergence in probability almost surely. 
+Note that 
 \begin{align*}
-\mathbb{E}^*\left[\frac{1}{n}\sum^{n}_{i=1}h(X_i^*;\hat{\theta}_0)\right]
-=&\frac{1}{n}\sum^{k}_{j=1}\mathbb{E}^*\left[\sum^{S_j+l-1}_{i=S_j}h(X_{i};\hat{\theta}_0)\right]
-\\=&\frac{k}{n^2}[\sum^{n - l + 1}_{j=1}\sum^{j+l-1}_{i=j}h(X_{i};\hat{\theta}_0) +
+\mathbb{E}^{(b)}\left[\frac{1}{n}\sum^{n}_{i=1}h(X_i^{(b)};
+\hat{\theta}_0)\right]
+=&\frac{1}{n}\sum^{k}_{j=1}\mathbb{E}^{(b)}\left[\sum^{S_j+l-1}_{i=S_j}h(X_{i};
+\hat{\theta}_0)\right]
+\\=&\frac{k}{n^2}[\sum^{n - l + 1}_{j=1}\sum^{j+l-1}_{i=j}h(X_{i};
+\hat{\theta}_0) +
 \sum^{n}_{j=n - l + 2}[\sum^{n}_{i=j}h(X_{i};\hat{\theta}_0) +
@@
 \begin{align*}
-\text{var}^*\left(\frac{1}{\sqrt{n}}\sum^{n}_{i=1}h(X_i^*;\theta_0^*)\right)
-=&\text{var}^*\left(\frac{1}{\sqrt{n}}\sum^{k}_{j=1}\sum^{S_j+l-1}_{i=S_j}h(X_{i};\hat{\theta}_0)\right)
-\\=&\frac{1}{l}\text{var}^*\left(\sum^{S_1+l-1}_{i=S_1}h(X_{i};\hat{\theta}_0)\right)
+\text{var}^{(b)}\left(\frac{1}{\sqrt{n}}\sum^{n}_{i=1}h(X_i^{(b)};
+\theta_0^{(b)})\right)
+=&\text{var}^{(b)}\left(\frac{1}{\sqrt{n}}\sum^{k}_{j=1}\sum^{S_j+l-1}_{i=S_j}
+h(X_{i};\hat{\theta}_0)\right)
+\\=&\frac{1}{l}\text{var}^{(b)}\left(\sum^{S_1+l-1}_{i=S_1}h(X_{i};
+\hat{\theta}_0)\right)
 \\=&\frac{1}{ln}\sum^{n}_{t=1}(W_t-\bar{W})^2
@@
 and $\bar{W}=\sum^{n}_{t=1}W_t/n$,
-which is expected to converge to $s^2$ almost surely. Similar calculations apply to $G_n^*(x)$ and we expect that
+which is expected to converge to $s^2$ almost surely. Similar calculations apply 
+to $G_n^{(b)}(x)$ and we expect that
 \begin{align*}
-&\text{Cov}^*(G_n^*(x),G_n^*(x'))\overset{a.s.}{\rightarrow}   \sum^{+\infty}_{h=-\infty}\text{Cov}(\mathbf{1}\{X_{h}\leq x\},\mathbf{1}\{X_0\leq x'\}),\\
-&\text{Cov}^*\left(\frac{1}{\sqrt{n}}\sum^{n}_{i=1}h(X_i^*;\hat{\theta}_0), G_n^*(x)\right)\overset{a.s.}{\rightarrow} \sum^{+\infty}_{h=-\infty}\text{Cov}(h(X_{h},\theta_0),\mathbf{1}\{X_0\leq x\}).
+&\text{Cov}^{(b)}(G_n^{(b)}(x),G_n^{(b)}(x'))\overset{a.s.}{\rightarrow}   
+\sum^{+\infty}_{h=-\infty}
+\text{Cov}(\mathbf{1}\{X_{h}\leq x\},\mathbf{1}\{X_0\leq x'\}),\\
+&\text{Cov}^{(b)}\left(\frac{1}{\sqrt{n}}\sum^{n}_{i=1}h(X_i^{(b)};
+\hat{\theta}_0), G_n^{(b)}(x)\right)\overset{a.s.}{\rightarrow} 
+\sum^{+\infty}_{h=-\infty}\text{Cov}(h(X_{h},\theta_0),\mathbf{1}\{X_0\leq x\}).
 \end{align*}
-By showing the finite-dimensional convergence and tightness in the bootstrap world (conditional on the data $X_{1:n}$), we can establish \eqref{eq-con-boot}.
-From the CLT, the process $G_n^*(x) = \sqrt{n}(F_n^*(x) - F_n(x))$ converges 
+By showing the finite-dimensional convergence and tightness in the bootstrap 
+world (conditional on the data $\{X_t: t = 1, \ldots, n\}$), we can establish 
+\eqref{eq-con-boot}.
+From the CLT, the process $G_n^{(b)}(x) = \sqrt{n}(F_n^{(b)}(x) - F_n(x))$ 
+converges 
 to 
@@
 
-For $\sqrt{n}(F(x;\hat{\theta}_n^*) - F(x;\hat{\theta}_0))$, using the first-
-order Taylor 
-expansion around $\hat{\theta}_0$, we have:
+For $\sqrt{n}(F(x;\hat{\theta}_n^{(b)}) - F(x;\hat{\theta}_0))$, using the 
+first-order Taylor 
+expansion around $\hat{\theta}_0$ similarly to what was done in 
+\citet{kunsch1989jackknife}, we have:
 \[
-F(x;\hat{\theta}_n^*) \approx F(x;\hat{\theta}_0) + f(x; 
-\hat{\theta}_0) (\hat{\theta}_n^* - \hat{\theta}_0),
+F(x;\hat{\theta}_n^{(b)}) \approx F(x;\hat{\theta}_0) + f(x; 
+\hat{\theta}_0) (\hat{\theta}_n^{(b)} - \hat{\theta}_0),
 \] so
 \[
-\sqrt{n}(F(x;\hat{\theta}_n^*) - F(x;\hat{\theta}_0)) \approx \sqrt{n} 
+\sqrt{n}(F(x;\hat{\theta}_n^{(b)}) - F(x;\hat{\theta}_0)) \approx \sqrt{n} 
 (F(x;\hat{\theta}_0) + f(x; 
-\hat{\theta}_0) (\hat{\theta}_n^* - \hat{\theta}_0) - F(x;\hat{\theta}_0)) 
+\hat{\theta}_0) (\hat{\theta}_n^{(b)} - \hat{\theta}_0) - F(x;\hat{\theta}_0)) 
 \approx
 f(x; 
-\hat{\theta}_0) \sqrt{n} (\hat{\theta}_n^* - \hat{\theta}_0).
-\].
-
-Substituting the expansion of $\hat{\theta}_n^*$:
-\[
-\sqrt{n} (\hat{\theta}_n^* - \hat{\theta}_0) = \frac{1}{\sqrt{n}} \sum_{i=1}^{n} 
-h(X_i^*; \hat{\theta}_0) + R_n^*.
+\hat{\theta}_0) \sqrt{n} (\hat{\theta}_n^{(b)} - \hat{\theta}_0).
 \]
 
-Since $R_n^* \overset{p^*}{\rightarrow} 0$, 
+Substituting the expansion of $\hat{\theta}_n^{(b)}$:
 \[
-\sqrt{n}(F(x;\hat{\theta}_n^*) - F(x;\hat{\theta}_0)) \approx 
-f(x; \hat{\theta}_0) \left( \frac{1}{\sqrt{n}} \sum_{i=1}^{n} h(X_i^*; 
+\sqrt{n} (\hat{\theta}_n^{(b)} - \hat{\theta}_0) = \frac{1}{\sqrt{n}} 
+\sum_{i=1}^{n} 
+h(X_i^{(b)}; \hat{\theta}_0) + R_n^{(b)}.
+\]
+
+Since $R_n^{(b)} \overset{p^{(b)}}{\rightarrow} 0$, 
+\[
+\sqrt{n}(F(x;\hat{\theta}_n^{(b)}) - F(x;\hat{\theta}_0)) \approx 
+f(x; \hat{\theta}_0) \left( \frac{1}{\sqrt{n}} \sum_{i=1}^{n} h(X_i^{(b)}; 
 \hat{\theta}_0) \right).
@@
 
-The term $\frac{1}{\sqrt{n}} \sum_{i=1}^{n} h(X_i^*; \hat{\theta}_0)$ 
+The term $\frac{1}{\sqrt{n}} \sum_{i=1}^{n} h(X_i^{(b)}; \hat{\theta}_0)$ 
 converges in distribution to a normal random variable $U$ with variance 
 $s^2$.
-We can show tightness of $G_n^*(x)$ similarly to how we established 
+We can show tightness of $G_n^{(b)}(x)$ similarly to how we established 
 tightness of $G_n(x)$
@@
 
-%\bibliographystyle{plain} 
-%\bibliography{ref}
+\bibliographystyle{plain} 
+\bibliography{ref}
 

### 2024-06-17 manuscript/manuscript.tex
addressed comments
minor polish

@@
 bias correction method employing a nonparametric block bootstrap, which
-approximates the distribution of the KS statistic accounting for unspecified
+approximates the distribution of the KS statistic in assessing the
+goodness-of-fit of the marginal distribution of a stationary series,
+accounting for unspecified
 serial dependence and unspecified parameters. We assess its effectiveness
@@
 
-\keywords{bias-correction, p-value, time series, finance}
+% alphabetical; no repeating anything in the title already
+\keywords{bias-correction, financial data, marginal distribution,
+  stationary series, time series}
 
@@
 
-%\eds{Please check consistency with how you refer to $F$.  In 
-%Equation~\eqref{eq:ks_standard}, it is $F(x; \theta_0)$ where the data and 
-%parameter arguments are separated by a semicolon.  At the beginning of 
-%Section~\ref{sec:methods}, it is $F(\cdot \mid \theta)$, with the vertical bar
-%separating the data argument from the parameter argument (and no 0 subscript
-%either).   Then in this first 
-%subsection it is $F(x; \hat\theta_n)$ with a semicolon separating the two 
-%arguments.  Then immediately above its use is mixed with $F(x)$ without a 
-%parameter argument (implying it is the true parameter $\theta$). This continues
-%throughout the document. I suggest either using consistent notation throughout, 
-%or explicitly defining any shortened/simplified notation at its first use.}
-%\mc{switched everything to semicolons}
-%\jy{replaced $F$ with $F(\cdot; \theta_0)$}
-
 When $\{X_t: t = 1, \ldots, n\}$ are further serially dependent, the statistic
@@
   where 
-  $B_{n}(x) = \sqrt{n}(F_n(x) - F(x; \hat\theta_n))$ is the known
+  $B_{n}(x) = \sqrt{n}(F_n(x) - F(x; \hat\theta_n))$ is the estimated
   bias term.
@@
 as $p = \sum_{b=1}^B I\{T^{(b)}_n > T_n\} / B$.
-
-\jy{Recover the definition of jy and eds for comments. Prepare two
-  definitions in the source so that one can be easily commented out.}
-\mc{addressed}
-
-\jy{Cite Kunsch (1989) in the proof as appropriate}
-
-\jy{In the Supp: make sure notations are consistent (e.g., use
-  $\{X_t: t = 1, \ldots, n\}$ for observed data);
-  clean up the styles (linewidth etc.)}
-\mc{addressed}
 
@@
 	to be as $|\tau|$ increases away from zero, but it may be fine to leave it as
-	is.}\mc{how does this look?}}
+	is.}\mc{how does this look?}
+\jy{Once finalized, don't forget to update the caption.}
+    }
 \label{table:size}
@@
 summarizes the empirical sizes of the tests based on 10000 replicates.
-\eds{Is 1000 enough to truly evaluate whether size is good at the 0.01 level?}
 The agreement between the empirical sizes and the nominal size
@@
 
-\eds{I think it would be better to show in simulation first (perhaps 
-in supplemental materials if we are concerned with paper length) that the other
-methods are not valid or unreliable under this setting, and then 
-further discredit those results here in the real data analysis.
-(I would expect a reviewer to ask for this comparison anyway.)}
-\jy{we could design scenarios where SPBB fails: some dependency
-  structure that cannot be well-approximated by ARMA.}
+% \eds{I think it would be better to show in simulation first (perhaps 
+% in supplemental materials if we are concerned with paper length) that the other
+% methods are not valid or unreliable under this setting, and then 
+% further discredit those results here in the real data analysis.
+% (I would expect a reviewer to ask for this comparison anyway.)}
+% \jy{We could design scenarios where SPBB fails: some dependency
+%   structure that cannot be well-approximated by ARMA. Could do this
+%   if requested.}
 
@@
 
-None reported.
+JY and XZ's research was partially supported by NSF grant
+DMS2210735.
 

### 2024-06-19 manuscript/manuscript.tex
bit about liberal test
added more to README.md

@@
 
-\author[1]{Mathew Chandy}
+\author[1,2]{Mathew Chandy}
 
@@
 
-\author[2]{Xianyang Zhang}
+\author[3]{Xianyang Zhang}
 
@@
 
-\address[2]{\orgdiv{Statistics}, \orgname{Texas A\&M University}, \orgaddress{\state{Texas}, \country{United States}}}
+\address[2]{\orgdiv{Statistics and Data Science}, \orgname{University of California,
+Los Angeles},
+\orgaddress{\state{California}, \country{United States}}}
+
+\address[3]{\orgdiv{Statistics}, \orgname{Texas A\&M University}, \orgaddress{\state{Texas}, \country{United States}}}
 
@@
 After the transformation
-to the marginal gamma distribution, the lag-1 autocorrelations are
+to the marginal gamma distribution, the lag-1 autocorrelations are approximately
 \[
-  \{-0.884, -0.686, -0.389, -0.033, 0.327, 0.639, 0.861\}.
+  \{-0.876, -0.674, -0.368, 0, 0.377, 0.701, 0.922\}.
 \]
@@
 particularly large sample size, whereas for moderate dependence, a larger sample
-size is required. For practical situations with a $\tau$ of magnitude 0.5 or
+size is required. When the agreement is not met, the empirical size is 
+usually larger than 1, which indicates that the test is too liberal. In
+other words, the test rejects the null hypothesis more often than it should.
+For practical situations with a $\tau$ of magnitude 0.5 or
 lower, it is still reasonable to recommend our method with $n \ge 400$.

### 2024-06-19 code/copula.R

@@ -19,7 +19,7 @@ cor(z[,1], z[,2])
 
 rho2phi <- function(rho) {
   mymvd <- copula::mvdc(copula::normalCopula(rho), margins = "gamma",
-                        paramMargins = list(rate=1, scale=1), marginsIdentical = TRUE)
+                        paramMargins = list(rate=8, scale=1), marginsIdentical = TRUE)
   EXY <- pracma::dblquad(function(x, y) x * y * copula::dMvdc(cbind(x, y), mymvd),
                          0, 20, 0, 20)
   phi <- (EXY - 1) / 1
@@ -30,3 +30,16 @@ uniroot(function(x) rho2phi(x) - 0.707, interval = c(0, 0.9))
 
 uniroot(function(x) rho2phi(x) + 0.707, interval = c(-.56, 0))
 
+# lag-1 AR for normal series
+for (i in c(-.75, -.5, -.25, 0, .25, .5, .75)) { 
+  print(iTau(normalCopula(), i))
+}
+
+# approximation of lag-1 AR for gamma series
+set.seed(123)
+for(phi in c(-0.924, -0.707, -0.383, 0, 0.383, 0.707, 0.924)) {
+  y <- arima.sim(list(ar = phi), n = 1000000) * 
+    sqrt(1 - phi^2)
+  y <- qgamma(pnorm(y), 8, 1)
+  print(cor(y[-1], y[-length(y)]))
+}

### 2024-06-19 manuscript/manuscript.tex
changed table to rejection rate instead of ratio

@@
 \centering
-\caption{Empirical sizes (ratio of rejection rate to significance level)
+\caption{Empirical sizes or rejection rates
 for the test that sample follows its true distribution family for
@@
   \midrule
-{$N(8,8)$} & {100} & 0.01 & 5.210 & 1.240 & 1.120 & 1.060 & 1.140 & 1.580 & 5.630 \\ 
-& & 0.05 & 2.940 & 1.256 & 1.090 & 1.096 & 1.150 & 1.450 & 3.410 \\ 
-& & 0.10 & 2.277 & 1.186 & 1.147 & 1.072 & 1.154 & 1.424 & 2.714 \\ 
-& {200} & 0.01 & 4.390 & 1.130 & 0.900 & 1.140 & 1.090 & 1.380 & 5.900 \\ 
-& & 0.05 & 2.556 & 1.120 & 1.020 & 1.064 & 1.092 & 1.382 & 3.452 \\ 
-& & 0.10 & 2.080 & 1.123 & 1.069 & 1.086 & 1.051 & 1.332 & 2.650 \\ 
-& {400} & 0.01 & 3.240 & 1.070 & 0.990 & 1.080 & 0.970 & 1.260 & 4.670 \\ 
-& & 0.05 & 2.032 & 1.000 & 0.994 & 1.120 & 0.978 & 1.184 & 2.836 \\ 
-& & 0.10 & 1.734 & 1.023 & 1.002 & 1.089 & 1.017 & 1.192 & 2.232 \\ 
-& {800} & 0.01 & 2.520 & 0.900 & 0.980 & 1.110 & 1.020 & 1.350 & 3.540 \\ 
-& & 0.05 & 1.766 & 1.008 & 0.972 & 0.956 & 0.962 & 1.236 & 2.438 \\ 
-& & 0.10 & 1.555 & 1.026 & 0.986 & 0.961 & 0.997 & 1.206 & 2.044 \\ [1ex]
-{$\Gamma(8,1)$} & {100} & 0.01 & 4.880 & 1.420 & 1.170 & 1.240 & 1.110 & 1.610 & 5.760 \\ 
-  & & 0.05 & 2.850 & 1.282 & 1.222 & 1.170 & 1.178 & 1.464 & 3.374 \\ 
-  & & 0.10 & 2.241 & 1.224 & 1.147 & 1.175 & 1.150 & 1.375 & 2.679 \\ 
-  & {200} & 0.01 & 4.080 & 1.000 & 0.890 & 1.220 & 1.160 & 1.430 & 6.080 \\ 
-  & & 0.05 & 2.510 & 1.118 & 1.014 & 1.068 & 1.116 & 1.290 & 3.380 \\ 
-  & & 0.10 & 1.991 & 1.105 & 1.022 & 1.048 & 1.072 & 1.233 & 2.664 \\ 
-  & {400} & 0.01 & 3.140 & 0.970 & 1.140 & 0.940 & 1.030 & 1.310 & 4.300 \\ 
-  & & 0.05 & 2.004 & 0.964 & 1.042 & 1.062 & 1.122 & 1.236 & 2.808 \\ 
-  & & 0.10 & 1.697 & 1.025 & 1.066 & 1.018 & 1.100 & 1.177 & 2.232 \\ 
-  & {800} & 0.01 & 2.490 & 0.920 & 1.130 & 1.120 & 1.000 & 1.130 & 3.810 \\ 
-  & & 0.05 & 1.804 & 0.976 & 1.064 & 1.022 & 1.086 & 1.196 & 2.474 \\ 
-  & & 0.10 & 1.561 & 1.024 & 1.072 & 1.034 & 1.067 & 1.177 & 1.997 \\ 
+{$N(8,8)$} & {100} & 0.01 & 0.0521 & 0.0124 & 0.0112 & 0.0106 & 0.0114 & 0.0158 & 0.0563 \\ 
+& & 0.05 & 0.1470 & 0.0628 & 0.0545 & 0.0548 & 0.0575 & 0.0725 & 0.1705 \\ 
+& & 0.10 & 0.2277 & 0.1186 & 0.1147 & 0.1072 & 0.1154 & 0.1424 & 0.2714 \\ 
+& {200} & 0.01 & 0.0439 & 0.0113 & 0.0090 & 0.0114 & 0.0109 & 0.0138 & 0.0590 \\ 
+& & 0.05 & 0.1278 & 0.0560 & 0.0510 & 0.0532 & 0.0546 & 0.0691 & 0.1726 \\ 
+& & 0.10 & 0.2080 & 0.1123 & 0.1069 & 0.1086 & 0.1051 & 0.1332 & 0.2650 \\ 
+& {400} & 0.01 & 0.0324 & 0.0107 & 0.0099 & 0.0108 & 0.0097 & 0.0126 & 0.0467 \\ 
+& & 0.05 & 0.1016 & 0.0500 & 0.0497 & 0.0560 & 0.0489 & 0.0592 & 0.1418 \\ 
+& & 0.10 & 0.1734 & 0.1023 & 0.1002 & 0.1089 & 0.1017 & 0.1192 & 0.2232 \\ 
+& {800} & 0.01 & 0.0252 & 0.0090 & 0.0098 & 0.0111 & 0.0102 & 0.0135 & 0.0354 \\ 
+& & 0.05 & 0.0883 & 0.0504 & 0.0486 & 0.0478 & 0.0481 & 0.0618 & 0.1219 \\ 
+& & 0.10 & 0.1555 & 0.1026 & 0.0986 & 0.0961 & 0.0997 & 0.1206 & 0.2044 \\ [1ex]
+{$\Gamma(8,1)$} & {100} & 0.01 & 0.0488 & 0.0142 & 0.0117 & 0.0124 & 0.0111 & 0.0161 & 0.0576 \\ 
+  & & .05 & 0.1425 & 0.0641 & 0.0611 & 0.0585 & 0.0589 & 0.0732 & 0.1687 \\ 
+  & & 0.10 & 0.2241 & 0.1224 & 0.1147 & 0.1175 & 0.1150 & 0.1375 & 0.2679 \\ 
+  & {200} & 0.01 & 0.0408 & 0.0100 & 0.0089 & 0.0122 & 0.0116 & 0.0143 & 0.0608 \\ 
+  & & 0.05 & 0.1255 & 0.0559 & 0.0507 & 0.0534 & 0.0558 & 0.0645 & 0.1690 \\ 
+  & & 0.10 & 0.1991 & 0.1105 & 0.1022 & 0.1048 & 0.1072 & 0.1233 & 0.2664 \\ 
+  & {400} & 0.01 & 0.0314 & 0.0097 & 0.0114 & 0.0094 & 0.0103 & 0.0131 & 0.0430 \\ 
+  & & 0.05 & 0.1002 & 0.0482 & 0.0521 & 0.0531 & 0.0561 & 0.0618 & 0.1404 \\ 
+  & & 0.10 & 0.1697 & 0.1025 & 0.1066 & 0.1018 & 0.1100 & 0.1177 & 0.2232 \\ 
+  & {800} & 0.01 & 0.0249 & 0.0092 & 0.0113 & 0.0112 & 0.0100 & 0.0113 & 0.0381 \\ 
+  & & 0.05 & 0.0902 & 0.0488 & 0.0532 & 0.0511 & 0.0543 & 0.0598 & 0.1237 \\ 
+  & & 0.10 & 0.1561 & 0.1024 & 0.1072 & 0.1034 & 0.1067 & 0.1177 & 0.1997 \\ 
    \bottomrule
@@
 size is required. When the agreement is not met, the empirical size is 
-usually larger than 1, which indicates that the test is too liberal. In
+usually larger than the nominal size, which indicates that the test is too liberal. 
+In
 other words, the test rejects the null hypothesis more often than it should.

### 2024-06-19 code/tables.R

@@ -5,7 +5,7 @@ df <- readRDS("../data/null_rejection_rates.RDS") %>%
          rr = round(as.numeric(rr), 4),
          rr_ub = round(as.numeric(rr_ub), 3),
          alpha = format(round(as.numeric(alpha), 2), nsmall = 2),
-         `Empirical Size` = rr / as.numeric(alpha))
+         `Empirical Size` = rr)
 
 df$tau <- factor(case_when(df$phi == "-0.9238795" ~ "$\\tau = -0.75$",
                            df$phi == "-0.7071068" ~ "$\\tau = -0.5$",

### 2024-06-19 manuscript/manuscript.tex
minor comments

@@
 then $T^{(b)}_n := \sup_x|Y^{(b)}_n(x)|$ is the bootstrap statistic that is 
-expected to approximate the distribution of $T_n$. We note that the term
+expected to approximate the distribution of $T_n$. 
+\eds{you have defined two $T_n$'s - perhaps different notation should be used
+to differentiate the $T_n$ in the Intro and the $T_n$ in Section 2.1?  At least
+clarify which $T_n$ you are referring to here.} 
+We note that the term
 $\sqrt{n}(F_n(x) - F(x; \hat\theta_n))$ is exactly the bias term considered in 
@@
 Assume that the time series $\{X_t\}$ is stationary and
-strongly mixing. The following results provides theoretical validity
+strongly mixing. The following results provide theoretical validity
 of the NPBB procedure of the KS test. Sketches of their proofs are
@@
 
+\eds{Is $T_n^*$ the same as $T_n^{(b)}$?  Can we replace the $t$ index with $i$ 
+to be consistent with earlier notation?  Or use $t$ earlier when introducing
+time-series data? ($t$ is used in the Simulation section below.)}
+
 Following the arguments in the proof of the Glivenko--Cantelli
@@
 
+\eds{Replace $X_{1:n}$ with $\{X_i: i = 1, \ldots, n\}$ or $\{X_t: t = 1, \ldots, n\}$?}
+
 \section{Simulation Studies}\label{sec:simu}
@@
 approximately at the specified size or significance level. Secondly, we aim to
-illustrate that under the alternate distribution, our test rejects
+illustrate that under the alternative hypothesis, our test rejects
 $H_0$ with substantial power. The fulfillment of both criteria would indicate
@@
 \jy{Once finalized, don't forget to update the caption.}
+\eds{Leaving it like this is fine, thanks!}
     }
@@
 to obtain a p-value $p_r$ for each $r \in \{1, \ldots, 1000\}$.  
+\eds{1000 or  10000?}
 The empirical rejection rates were obtained at a nominal significance level 0.05.
-Additionally, we constructed 95\% confidence intervals the actual rejection
-rejection rate.
+Additionally, we constructed 95\% confidence intervals of the actual rejection rate.
+\eds{what do you mean by `actual' rejection rate? True rejection rate?  
+I don't see the CI in Figure 2.}
 
@@
 2) NPB bias correction method of
-\citet{babu2004goodness}; and and 3) the parametric bootstrap (PB) method shown
+\citet{babu2004goodness}; and 3) the parametric bootstrap (PB) method shown
 by \citet{zeimbekakis2022misuses}. The latter of the two methods discard the
@@
 %   if requested.}
+\eds{I still think this section is weak without supporting simulation evidence.
+but I am okay with letting this be low-hanging-fruit for a reviewer to request 
+if we are confident that the SPB will not work well in this situation.}
 

### 2024-06-23 manuscript/manuscript.tex
addressed comments

@@
 \[
-  T_n = \sqrt{n} \sup_x | F_{n}(x) - F(x; \theta_0)|.
+  D_n = \sqrt{n} \sup_x | F_{n}(x) - F(x; \theta_0)|.
 \]
-As sample size $n\to \infty$, the distribution of $T_n$ converges to that of the
+As sample size $n\to \infty$, the distribution of $D_n$ converges to that of the
 absolute value of standard Brownian bridge, which is known as the Kolmogorov
@@
 
-Consider a stationary time series $\{X_t: t = 1, \ldots, n\}$ with length~$n$.
-We are interested in testing whether or not $X_t$ follows a distribution in a
+Consider a stationary time series $\{X_i: i = 1, \ldots, n\}$ with length~$n$.
+We are interested in testing whether or not $X_i$ follows a distribution in a
 parametric family of distribution~$F$ indexed by a parameter
@@
 \[
-  H_0: X_t \sim F(\cdot ; \theta), \quad t = 1, \ldots, n,
+  H_0: X_i \sim F(\cdot ; \theta), \quad i = 1, \ldots, n,
 \]
 for some unspecified parameter $\theta$.
-The alternative hypothesis $H_A$ is that the marginal distribution of $X_t$ does
+The alternative hypothesis $H_A$ is that the marginal distribution of $X_i$ does
 not follow~$F$ for any parameter value~$\theta$. This is a challenging situation
@@
 
-When $\{X_t: t = 1, \ldots, n\}$ are further serially dependent, the statistic
+When $\{X_i: i = 1, \ldots, n\}$ are further serially dependent, the statistic
 $T_n$ still provides a reasonable metric for deviation from the null
@@
 to differentiate the $T_n$ in the Intro and the $T_n$ in Section 2.1?  At least
-clarify which $T_n$ you are referring to here.} 
+clarify which $T_n$ you are referring to here.}\mc{addressed}
 We note that the term
@@
 
-Assume that the time series $\{X_t\}$ is stationary and
+Assume that the time series $\{X_i\}$ is stationary and
 strongly mixing. The following results provide theoretical validity
@@
   \[
-    \big\vert \mathbb{P}(T_n^*\leq x \mid \{X_t: t = 1, \ldots, n\}) -
+    \big\vert \mathbb{P}(T_n^{(b)}\leq x \mid \{X_i: i = 1, \ldots, n\}) -
     \mathbb{P}(T_n\leq x) \big\vert
@@
   for any fixed $x$, where and $T_n^*$ is the the statistic computed 
-  based on the bootstrap sample $\{X_t^{(b)}: t = 1, \ldots, n\}$.
+  based on the bootstrap sample $\{X_i^{(b)}: i = 1, \ldots, n\}$.
 \end{proposition}
@@
 to be consistent with earlier notation?  Or use $t$ earlier when introducing
-time-series data? ($t$ is used in the Simulation section below.)}
+time-series data? ($t$ is used in the Simulation section below.)}\mc{I replaced
+everything with $i$, I wasn't sure when to use $X_i$ or $\{X_i\}$}
 
@@
   \sup_x \big \vert
-  \mathbb{P}(T_n^*\leq x|X_{1:n}) - \mathbb{P}(T_n\leq x) \big\vert
+  \mathbb{P}(T_n^{(b)}\leq x|\{X_i: i = 1, \ldots, n\}) - \mathbb{P}(T_n\leq x) \big\vert
   \overset{a.s.}{\rightarrow} 0.
@@
 \eds{Replace $X_{1:n}$ with $\{X_i: i = 1, \ldots, n\}$ or $\{X_t: t = 1, \ldots, n\}$?}
+\mc{addressed}
 
@@
 To assess the actual size of the test, our strategy is to
-generate a large number of stationary time series $X_t$ with a certain marginal
+generate a large number of stationary time series $X_i$ with a certain marginal
 distribution $F(\cdot; \theta)$, and for each time series, use our method to
-test if $X_t$ follows a hypothesized marginal distribution $F(\cdot; \theta)$
+test if $X_i$ follows a hypothesized marginal distribution $F(\cdot; \theta)$
 with some unknown $\theta$. If the test holds its size, the p-value
@@
 To generate the samples to which our
-method would be applied, we simulated a time series $W_t$ from a 1st 
+method would be applied, we simulated a time series $W_i$ from a 1st 
 order autoregressive or AR(1) process:
 \begin{equation*}
-W_t = \phi W_{t-1} + \epsilon_t,
+W_i = \phi W_{i-1} + \epsilon_i,
 \end{equation*}
-where $\phi$ is an autoregressive coefficient, and $\epsilon_t$ is a series of
+where $\phi$ is an autoregressive coefficient, and $\epsilon_i$ is a series of
 independent errors from a normal distribution with mean zero and variance
@@
 correspond to the desired values for $\tau$. The 
-series $W_t$ has mean zero and variance 
+series $W_i$ has mean zero and variance 
 $\sigma_x^2 = \sigma_{\epsilon}^2 / (1 - \phi^2)$, so for each value of
@@
 First, we generated a
-marginal $N(8, 8)$ by marginally transforming $W_t$ by
+marginal $N(8, 8)$ by marginally transforming $W_i$ by
 \begin{equation*}
-X_t = F^{-1}[\Phi(W_t)],
+X_i = F^{-1}[\Phi(W_i)],
 \end{equation*}
@@
 For the purposes of 
-evaluating if the test holds it size, when $X_t \sim N(8, 8)$, we tested that the 
+evaluating if the test holds it size, when $X_i \sim N(8, 8)$, we tested that the 
 marginal distribution is from the
 Normal family, or 
-$X_t \sim N(\cdot ; \mu, \sigma^2), \quad t = 1, \ldots, n$
-for some unspecified $\mu$ and $\sigma$. When $X_t \sim \Gamma(8, 1)$, we tested
+$X_i \sim N(\cdot ; \mu, \sigma^2), \quad i = 1, \ldots, n$
+for some unspecified $\mu$ and $\sigma$. When $X_i \sim \Gamma(8, 1)$, we tested
 that the marginal distribution family is from the Gamma family,
 or
-$X_t \sim \Gamma(\cdot ; \alpha, \beta), \quad t = 1, \ldots, n$.
+$X_i \sim \Gamma(\cdot ; \alpha, \beta), \quad i = 1, \ldots, n$.
 for some unspecified $\alpha$ and $\beta$. For the block bootstrap step,
@@
 different values of AR(1) coefficient and for different 
-significance levels.
-\eds{Not sure if it will help presentation or interpretation, but you could
-  consider presenting the values inside the table as estimated size/true size}
-\mc{addressed}
-\eds{I meant reporting the ratio, e.g, dividing all values currently in the    first row by 0.01, dividing all values in the second row by 0.05. Sometimes this
-	is helpful if there is a conservative or liberal pattern, which there seems
-	to be as $|\tau|$ increases away from zero, but it may be fine to leave it as
-	is.}\mc{how does this look?}
-\jy{Once finalized, don't forget to update the caption.}
-\eds{Leaving it like this is fine, thanks!}
-    }
+significance levels.}
 \label{table:size}
@@
 method $10000$ times 
-to obtain a p-value $p_r$ for each $r \in \{1, \ldots, 1000\}$.  
-\eds{1000 or  10000?}
+to obtain a p-value $p_r$ for each $r \in \{1, \ldots, 10000\}$.  
+\eds{1000 or  10000?}\mc{addressed}
 The empirical rejection rates were obtained at a nominal significance level 0.05.
-Additionally, we constructed 95\% confidence intervals of the actual rejection rate.
 \eds{what do you mean by `actual' rejection rate? True rejection rate?  
-I don't see the CI in Figure 2.}
+I don't see the CI in Figure 2.}\mc{addressed}
 
@@
 %   if requested.}
-\eds{I still think this section is weak without supporting simulation evidence.
-but I am okay with letting this be low-hanging-fruit for a reviewer to request 
-if we are confident that the SPB will not work well in this situation.}
+%\eds{I still think this section is weak without supporting simulation evidence.
+%but I am okay with letting this be low-hanging-fruit for a reviewer to request 
+%if we are confident that the SPB will not work well in this situation.}
 

### 2024-06-23 manuscript/supplement.tex
fixed author name
addressed comments

@@
 \title{Supporting Information for
-  ``Nonparametric Block Bootstrap Kolmogorov-Smirnov Goodness-of-Fit
+  ``Nonparametric Block Bootstrap Kolmogorov--Smirnov Goodness-of-Fit
   Test''}
@@
 Define $G_n^{(b)}(x)$ in the same way as $G_n(x)$ with $X_1, \dots, X_n$ being 
-replaced by the bootstrap samples $X_{1:n}^{(b)}=\{X_1^{(b)},\dots,X_n^{(b)}\}$.
+replaced by the bootstrap samples $\{X_i: i = 1, \ldots, n\}^{(b)}=\{X_1^{(b)},\dots,X_n^{(b)}\}$.
 
@@
 
-\bibliographystyle{plain} 
+\bibliographystyle{chicago} 
 \bibliography{ref}

### 2024-06-24 manuscript/manuscript.tex
removed resolved, i vs t index

@@
 expected to approximate the distribution of $T_n$. 
-\eds{you have defined two $T_n$'s - perhaps different notation should be used
-to differentiate the $T_n$ in the Intro and the $T_n$ in Section 2.1?  At least
-clarify which $T_n$ you are referring to here.}\mc{addressed}
+%\eds{you have defined two $T_n$'s - perhaps different notation should be used
+%to differentiate the $T_n$ in the Intro and the $T_n$ in Section 2.1?  At least
+%clarify which $T_n$ you are referring to here.}\mc{addressed}
 We note that the term
@@
 
-\eds{Is $T_n^*$ the same as $T_n^{(b)}$?  Can we replace the $t$ index with $i$ 
+\eds{Is $T_n^*$ the same as $T_n^{(b)}$?}  
+\eds{Can we replace the $t$ index with $i$ 
 to be consistent with earlier notation?  Or use $t$ earlier when introducing
@@
 everything with $i$, I wasn't sure when to use $X_i$ or $\{X_i\}$}
+\eds{I think this is fine -- $t$ or $i$ would have worked, as long as it is 
+consistently used within the time series sections.}
 
@@
   \sup_x \big \vert
-  \mathbb{P}(T_n^{(b)}\leq x|\{X_i: i = 1, \ldots, n\}) - \mathbb{P}(T_n\leq x) \big\vert
+  \mathbb{P}(T_n^{(b)}\leq x \mid \{X_i: i = 1, \ldots, n\}) - \mathbb{P}(T_n\leq x) \big\vert
   \overset{a.s.}{\rightarrow} 0.
@@
 
-\eds{Replace $X_{1:n}$ with $\{X_i: i = 1, \ldots, n\}$ or $\{X_t: t = 1, \ldots, n\}$?}
-\mc{addressed}
+%\eds{Replace $X_{1:n}$ with $\{X_i: i = 1, \ldots, n\}$ or $\{X_t: t = 1, \ldots, n\}$?}
+%\mc{addressed}
 
@@
 to obtain a p-value $p_r$ for each $r \in \{1, \ldots, 10000\}$.  
-\eds{1000 or  10000?}\mc{addressed}
 The empirical rejection rates were obtained at a nominal significance level 0.05.
-\eds{what do you mean by `actual' rejection rate? True rejection rate?  
-I don't see the CI in Figure 2.}\mc{addressed}
 

### 2024-06-24 manuscript/supplement.tex
removed resolved, i vs t index

@@
 \begin{align}\label{eq-expan}
-\hat{\theta}_n-\theta_0 = \frac{1}{n}\sum^{n}_{t=1}h(X_i;\theta_0) + 
+\hat{\theta}_n-\theta_0 = \frac{1}{n}\sum^{n}_{i=1}h(X_i;\theta_0) + 
 \frac{1}{\sqrt{n}}R_n,    
@@
 the expectation, variance and covariance conditional on 
-$\{X_t: t = 1, \ldots, n\}$ in 
+$\{X_i: i = 1, \ldots, n\}$ in 
 the bootstrap world. Assuming that $n=kl$ with $l$ being the block size and $k$ 
@@
 Define $G_n^{(b)}(x)$ in the same way as $G_n(x)$ with $X_1, \dots, X_n$ being 
-replaced by the bootstrap samples $\{X_i: i = 1, \ldots, n\}^{(b)}=\{X_1^{(b)},\dots,X_n^{(b)}\}$.
+replaced by the bootstrap samples %$\{X_i: i = 1, \ldots, n\}^{(b)}=\{X_1^{(b)},\dots,X_n^{(b)}\}$.
+$X_1^{(b)},\dots,X_n^{(b)}.$
 
@@
 By showing the finite-dimensional convergence and tightness in the bootstrap 
-world (conditional on the data $\{X_t: t = 1, \ldots, n\}$), we can establish 
+world (conditional on the data $\{X_i: i = 1, \ldots, n\}$), we can establish 
 \eqref{eq-con-boot}.

### 2024-06-30 manuscript/manuscript.tex
removed addressed comments

@@
 expected to approximate the distribution of $T_n$. 
-%\eds{you have defined two $T_n$'s - perhaps different notation should be used
-%to differentiate the $T_n$ in the Intro and the $T_n$ in Section 2.1?  At least
-%clarify which $T_n$ you are referring to here.}\mc{addressed}
 We note that the term
@@
   \]
-  for any fixed $x$, where and $T_n^*$ is the the statistic computed 
+  for any fixed $x$, where and $T_n^b$ is the the statistic computed 
   based on the bootstrap sample $\{X_i^{(b)}: i = 1, \ldots, n\}$.
 \end{proposition}
-
-\eds{Is $T_n^*$ the same as $T_n^{(b)}$?}  
-\eds{Can we replace the $t$ index with $i$ 
-to be consistent with earlier notation?  Or use $t$ earlier when introducing
-time-series data? ($t$ is used in the Simulation section below.)}\mc{I replaced
-everything with $i$, I wasn't sure when to use $X_i$ or $\{X_i\}$}
-\eds{I think this is fine -- $t$ or $i$ would have worked, as long as it is 
-consistently used within the time series sections.}
 
@@
 \]
-
-%\eds{Replace $X_{1:n}$ with $\{X_i: i = 1, \ldots, n\}$ or $\{X_t: t = 1, \ldots, n\}$?}
-%\mc{addressed}
 

### 2024-06-30 manuscript/manuscript.tex
bib cleaning

@@
 misapplied when its foundational assumptions are overlooked. The KS test 
-assumes the data are independently and identically distributed and 
+assumes that the data are independently and identically distributed and 
 that the hypothesized distribution is continuous and fully specified without 
@@
 Developing a fully nonparametric solution for the KS 
-tests in the presence of serially dependent data presents a significant 
+tests in the presence of serial dependence presents a significant 
 challenge. The null distribution's characteristics are intricately linked to 
@@
 strengthened to allow uniform convergence over $x$. That is,
+as $1/l+l/n\rightarrow 0$,
 \[

### 2024-07-10 manuscript/manuscript.tex
finite dimensional convergence and tightness

--- 2024-06-30 manuscript/manuscript.tex
@@
 of the hypothesized distribution family.
-If we let $F_n(t) = \sum_{i=1}^n I(X_i \le t) / n$ be the empirical cumulative
-distribution function of the sample, where $I(\cdot)$ is the indicator
+If we let $F_n(t) = \sum_{i=1}^n \mathbf{1}(\{X_i \le t\} / n$ be the empirical cumulative
+distribution function of the sample, where $\mathbf{1}\{\cdot\}$ is the indicator
 function, the KS test statistic takes the form
@@
 expected to approximate the distribution of $T_n$. 
+\eds{you have defined two $T_n$'s - perhaps different notation should be used
+to differentiate the $T_n$ in the Intro and the $T_n$ in Section 2.1?  At least
+clarify which $T_n$ you are referring to here.}\mc{addressed}
 We note that the term
@@
   \]
-  for any fixed $x$, where and $T_n^b$ is the the statistic computed 
+  for any fixed $x$, where and $T_n^{(b)}$ is the the statistic computed 
   based on the bootstrap sample $\{X_i^{(b)}: i = 1, \ldots, n\}$.
 \end{proposition}
+
+\eds{Is $T_n^*$ the same as $T_n^{(b)}$?  Can we replace the $t$ index with $i$ 
+to be consistent with earlier notation?  Or use $t$ earlier when introducing
+time-series data? ($t$ is used in the Simulation section below.)}\mc{I replaced
+everything with $i$, I wasn't sure when to use $X_i$ or $\{X_i\}$}
 
@@
   \sup_x \big \vert
-  \mathbb{P}(T_n^{(b)}\leq x \mid \{X_i: i = 1, \ldots, n\}) - \mathbb{P}(T_n\leq x) \big\vert
+  \mathbb{P}(T_n^{(b)}\leq x|\{X_i: i = 1, \ldots, n\}) - \mathbb{P}(T_n\leq x) \big\vert
   \overset{a.s.}{\rightarrow} 0.
 \]
+
+\eds{Replace $X_{1:n}$ with $\{X_i: i = 1, \ldots, n\}$ or $\{X_t: t = 1, \ldots, n\}$?}
+\mc{addressed}
 
@@
 to obtain a p-value $p_r$ for each $r \in \{1, \ldots, 10000\}$.  
+\eds{1000 or  10000?}\mc{addressed}
 The empirical rejection rates were obtained at a nominal significance level 0.05.
+\eds{what do you mean by `actual' rejection rate? True rejection rate?  
+I don't see the CI in Figure 2.}\mc{addressed}
 

### 2024-07-10 manuscript/supplement.tex
finite dimensional convergence and tightness

@@
 \usepackage{fullpage}
+\usepackage[utf8]{inputenc}
 
@@
 \begin{align}\label{eq-expan}
-\hat{\theta}_n-\theta_0 = \frac{1}{n}\sum^{n}_{i=1}h(X_i;\theta_0) + 
+\hat{\theta}_n-\theta_0 = \frac{1}{n}\sum^{n}_{t=1}h(X_i;\theta_0) + 
 \frac{1}{\sqrt{n}}R_n,    
@@
 
+\subsection{Finite-Dimensional Convergence of $G_n(x_1),\dots,G_n(x_m)$}
+
+We assume that the sequence \(\{X_i\}\) is strictly stationary and satisfies a 
+strong mixing condition.This condition ensures that the dependence between 
+\(X_i\) and \(X_{i+h}\) weakens sufficiently fast as \(h\) increases.
+
+We aim to show that for any fixed \( x_1, \ldots, x_m \), the vector \( (G_n(x_1), \ldots, G_n(x_m)) \) converges in distribution to a multivariate normal vector \( (G_{\infty}(x_1), \ldots, G_{\infty}(x_m)) \) with mean zero and covariance structure given by:
+\[
+\text{Cov}(G_{\infty}(x_i), G_{\infty}(x_j)) = \sum_{h=-\infty}^{\infty} \text{Cov}(\mathbf{1}\{X_0 \leq x\}, \mathbf{1}\{X_h \leq x^{\prime}\}),
+\]
+where $ \mathbf{1}\{\cdot\}$ is the indicator
+function.
+
 Given any $x_1,\dots,x_m$ in the domain of $F$, by the CLT for weakly dependent 
@@
 $\Sigma_{m+1}=\lim_{n\rightarrow+\infty}\text{Cov}(V_n)$.
+Consider the empirical process $ G_n(x) = \sqrt{n} (F_n(x) - F(x)) $, where 
+$ F_n(x) $ is the empirical distribution function based on $ X_1, \ldots, 
+X_n $. To show finite-dimensional convergence, we need to establish that for 
+any fixed $ x_1, \ldots, x_m $, the vector $ (G_n(x_1), \ldots, G_n(x_m)) $ 
+converges in distribution to a multivariate normal distribution.
+The 
+empirical distribution function can be written as:
+$
+F_n(x) = \frac{1}{n} \sum_{t=1}^n \mathbf{1}\{X_i \leq x\}.
+$
+Therefore, the empirical process is:
+$
+G_n(x) = \sqrt{n} (F_n(x) - F(x)) = \frac{1}{\sqrt{n}} \sum_{i=1}^n 
+(\mathbf{1}\{X_i \leq x\} - 
+F(x)).
+$
+
+To establish the asymptotic distribution of $ G_n(x) $, we consider the vector 
+$ (G_n(x_1), \ldots, G_n(x_m)) $:
+$
+(G_n(x_1), \ldots, G_n(x_m)) = \frac{1}{\sqrt{n}} \sum_{i=1}^n (\mathbf{1}\{X_i \leq x_1\} - 
+F(x_1), \ldots, \mathbf{1}\{X_i \leq x_m\} - F(x_m)).
+$
+We calculate the covariance structure of the limiting distribution. The 
+covariance between $ G_n(x) $ and $ G_n(x^{\prime}) $ is:
+$
+\text{Cov}(G_n(x), G_n(x^{\prime})) = \frac{1}{n} \sum_{t=1}^n \sum_{s=1}^n 
+\text{Cov}(\mathbf{1}\{X_t \leq x\}, \mathbf{1}\{X_t \leq x^{\prime}\}).
+$
+Since $ \{X_i\} $ is strictly stationary, the covariance depends only on the 
+lag $ h = |t-s| $:
+$
+\text{Cov}(\mathbf{1}\{X_t \leq x\}, \mathbf{1}\{X_t \leq x^{\prime}\}) = \text{Cov}(\mathbf{1}\{X_h \leq x\}, 
+\mathbf{1}\{X_0 \leq x^{\prime}\}).
+$
+Thus, the covariance can be expressed as:
+$
+\text{Cov}(G_n(x), G_n(x')) = \frac{1}{n} \sum_{t=1}^n \sum_{h=-t+1}^{n-t} 
+\text{Cov}(\mathbf{1}\{X_h \leq x\}, 
+\mathbf{1}\{X_0 \leq x^{\prime}\}).
+$
+
+By the mixing condition, the covariances $ \text{Cov}(\mathbf{1}\{X_h \leq x\}, 
+\mathbf{1}\{X_0 \leq x^{\prime}\}) $ 
+decay sufficiently fast as $ h \to \infty $. Therefore, the sum converges to:
+$
+\lim_{n \to \infty} \text{Cov}(G_n(x), G_n(x')) = \sum_{h=-\infty}^{\infty} 
+\text{Cov}(\{X_h \leq x\}, 
+\mathbf{1}\{X_0 \leq x^{\prime}\}).
+$
+
 %\begin{align*}
@@
 %\end{align*}
-Moreover, we can show the tightness of the process $G_n(x)$. 
+
+\subsection{Tightness of $G_n(x)$}
+
+Moreover, we can show the tightness of the process $G_n(s)$. 
+We want to show that for every $\epsilon > 0$,
+$
+\lim_{\delta \to 0} \limsup_{n \to \infty} \mathbb{P}\left( \omega_{G_n}(\delta) 
+\geq \epsilon \right) = 0,
+$
+where the modulus of continuity $\omega_{G_n}(\delta)$ is defined as
+$
+\omega_{G_n}(\delta) = \sup_{|s - t| < \delta} |G_n(s) - G_n(t)|
+$
+\citep{billingsley2013convergence}.
 For sufficiently small $\delta$, and leveraging the properties of weakly 
 dependent sequences, we can show that
-\[ \sup_{|x - y| < \delta} |G_n(x) - G_n(y)| = \sup_{|x - y| < \delta} 
-\sqrt{n}|(F_n(x) - F(x)) - (F_n(y) - F(y))| \]
+$ \sup_{|s - t| < \delta} |G_n(s) - G_n(t)| = \sup_{|s - t| < \delta} 
+\sqrt{n}|(F_n(s) - F(s)) - (F_n(t) - F(t))| $
 is small with high probability.
-Specifically, since $F(x)$ is continuous, for small 
-$\delta$, $|F(x) - F(y)|$ is small. For the empirical 
-distribution function $F_n(x)$, the increments $|F_n(x) - F_n(y)|$ are 
-also controlled. 
-This implies that the process $G_n(x)$ does not exhibit large oscillations over 
-small intervals, thus satisfying the criterion for tightness.
+For $ |s - t| < \delta $,
+$
+|G_n(s) - G_n(t)| = \sqrt{n} \left| (F_n(s) - F(s; \theta_0)) - (F_n(t) - 
+F(t; \theta_0)) \right|.
+$
+This can be decomposed as:
+$
+|G_n(s) - G_n(t)| = \sqrt{n} \left| (F_n(s) - F_n(t)) - (F(s; \theta_0) - 
+F(t; \theta_0)) \right|.
+$
+
+Remember that $F_n(t) = \sum_{i=1}^n  \mathbf{1}\{X_i \le t\} / n$. Then, for 
+$ |s - t| < \delta $, the difference $ F_n(s) - F_n(t) $ can be written as:
+$ F_n(s) - F_n(t) = \frac{1}{n} \sum_{i=1}^n \left( \mathbf{1}\{X_i \leq s\} - 
+\mathbf{1}\{X_i \leq t\} \right), $ or as 
+$ \mathbb{E}\left[ \frac{1}{n} \sum_{i=1}^n \mathbf{1}\{ t < X_i \leq s \} 
+\right] $. To provide a more precise bound on $ F_n(s) - F_n(t) $, we use 
+Hoeffding's inequality, which states that for any $ t > 0 $,
+$ \mathbb{P}\left( \left| \frac{1}{n} \sum_{i=1}^n \mathbf{1}\{ t < X_i \leq s 
+\} - \\
+\mathbb{E}\left[ \frac{1}{n} \sum_{i=1}^n \mathbf{1}\{ t < X_i \leq s \} 
+\right] \right| > t \right) \leq 2 \exp\left( -2nt^2 \right). $
+
+Since 
+$ \mathbb{E}\left[ \frac{1}{n} \sum_{i=1}^n \mathbf{1}\{ t < X_i \leq s \} 
+\right] = F(s; \theta_0) - F(t; \theta_0), $
+we have:
+$ \mathbb{P}\left( \left| \frac{1}{n} \sum_{i=1}^n \mathbf{1}\{ t < X_i \leq s 
+\} - \\
+(F(s; \theta_0) - F(t; \theta_0)) \right| > t \right) \leq 2
+\exp\left( 
+-2nt^2 \right). $
+Because the true CDF is continuous, by definition, $ F(s; \theta_0) $, for any $ \epsilon > 0 
+$, there esists a $ \delta > 0 $ such that for $ |s - t| < \delta $,
+$ |F(s; \theta_0) - F(t; \theta_0)| < \epsilon. $ Using the bound from Hoeffding's inequality, we have:
+$ \mathbb{P}\left( |F_n(s) - F_n(t) - (F(s; \theta_0) - F(t; \theta_0))| \geq 
+\epsilon \right) \leq 2 \exp\left( -2n\epsilon^2 \right). $ Then, for sufficiently large $ n $ and small $ \delta $,
+$ \mathbb{P}\left( \omega_{G_n}(\delta) \geq \epsilon \right) \leq 2 
+\exp\left( -2n\epsilon^2 \right). $ Taking limits, we conclude:
+$ \lim_{\delta \to 0} \limsup_{n \to \infty} \mathbb{P}\left( 
+\omega_{G_n}(\delta) \geq \epsilon \right) = 0. $
+
 Therefore, we have
@@
 Define $G_n^{(b)}(x)$ in the same way as $G_n(x)$ with $X_1, \dots, X_n$ being 
-replaced by the bootstrap samples %$\{X_i: i = 1, \ldots, n\}^{(b)}=\{X_1^{(b)},\dots,X_n^{(b)}\}$.
-$X_1^{(b)},\dots,X_n^{(b)}.$
+replaced by the bootstrap samples $\{X_i: i = 1, \ldots, n\}^{(b)}=\{X_1^{(b)},\dots,X_n^{(b)}\}$.
 
@@
 
+\subsection{Finite-Dimensional Convergence in the Bootstrap World}
+
 For $\sqrt{n}(F(x;\hat{\theta}_n^{(b)}) - F(x;\hat{\theta}_0))$, using the 
@@
 \citet{kunsch1989jackknife}, we have:
-\[
+$
 F(x;\hat{\theta}_n^{(b)}) \approx F(x;\hat{\theta}_0) + f(x; 
 \hat{\theta}_0) (\hat{\theta}_n^{(b)} - \hat{\theta}_0),
-\] so
-\[
+$ so
+$
 \sqrt{n}(F(x;\hat{\theta}_n^{(b)}) - F(x;\hat{\theta}_0)) \approx \sqrt{n} 
@@
 \hat{\theta}_0) \sqrt{n} (\hat{\theta}_n^{(b)} - \hat{\theta}_0).
-\]
+$
 
 Substituting the expansion of $\hat{\theta}_n^{(b)}$:
-\[
+$
 \sqrt{n} (\hat{\theta}_n^{(b)} - \hat{\theta}_0) = \frac{1}{\sqrt{n}} 
@@
 h(X_i^{(b)}; \hat{\theta}_0) + R_n^{(b)}.
-\]
+$
 
 Since $R_n^{(b)} \overset{p^{(b)}}{\rightarrow} 0$, 
-\[
+$
 \sqrt{n}(F(x;\hat{\theta}_n^{(b)}) - F(x;\hat{\theta}_0)) \approx 
@@
 \hat{\theta}_0) \right).
-\]
+$
 
@@
 $s^2$.
-We can show tightness of $G_n^{(b)}(x)$ similarly to how we established 
-tightness of $G_n(x)$
-The results then follow from the continuous mapping theorem.
+
+\subsection{Tightness in Bootstrap World}
+
 \end{proof}

### 2024-07-10 manuscript/manuscript.tex

--- 2024-06-30 manuscript/manuscript.tex
@@
   \]
-  for any fixed $x$, where and $T_n^b$ is the the statistic computed 
+  for any fixed $x$, where $T_n^{(b)}$ is the statistic computed 
   based on the bootstrap sample $\{X_i^{(b)}: i = 1, \ldots, n\}$.

### 2024-07-11 manuscript/supplement.tex
added indicator function
stylish edits

--- 2024-06-24 manuscript/supplement.tex
@@
 
+\paragraph{Finite-dimensional convergence of $G_n(x_1),\dots,G_n(x_m)$}
+
+We assume that the sequence \(\{X_i\}\) is strictly stationary and satisfies a 
+strong mixing condition. This condition ensures that the dependence between 
+\(X_i\) and \(X_{i+h}\) weakens sufficiently fast as \(h\) increases.
+
+We aim to show that for any fixed \( x_1, \ldots, x_m \), the vector
+\( (G_n(x_1), \ldots, G_n(x_m)) \) converges in distribution to a
+multivariate normal vector \( (G_{\infty}(x_1), \ldots,
+G_{\infty}(x_m)) \) with mean zero and covariance structure given by:
+\[
+\text{Cov}(G_{\infty}(x_i), G_{\infty}(x_j)) = \sum_{h=-\infty}^{\infty} \text{Cov}(\mathbf{1}\{X_0 \leq x\}, \mathbf{1}\{X_h \leq x^{\prime}\}),
+\]
+where $ \mathbf{1}\{\cdot\}$ is the indicator
+function.
+
 Given any $x_1,\dots,x_m$ in the domain of $F$, by the CLT for weakly dependent 
@@
 $\Sigma_{m+1}=\lim_{n\rightarrow+\infty}\text{Cov}(V_n)$.
-%\begin{align*}
-%\Sigma_{m+1}=\begin{pmatrix}
-%df & df & \cdots & df\\   
-%df & df & \cdots & df\\ 
-%\cdots & \cdots & \ddots & \cdots  \\ 
-%df & df & \cdots & df
-%\end{pmatrix}    
-%\end{align*} 
-Moreover, we can show the tightness of the process $G_n(x)$. 
+Consider the empirical process $ G_n(x) = \sqrt{n} (F_n(x) - F(x)) $, where 
+$ F_n(x) $ is the empirical distribution function based on $ X_1, \ldots, 
+X_n $. To show finite-dimensional convergence, we need to establish that for 
+any fixed $ x_1, \ldots, x_m $, the vector $ (G_n(x_1), \ldots, G_n(x_m)) $ 
+converges in distribution to a multivariate normal distribution.
+The empirical distribution function can be written as
+$
+F_n(x) = \frac{1}{n} \sum_{t=1}^n \mathbf{1}\{X_i \leq x\}.
+$
+Therefore, the empirical process is:
+\[
+G_n(x) = \sqrt{n} (F_n(x) - F(x)) = \frac{1}{\sqrt{n}} \sum_{i=1}^n 
+(\mathbf{1}\{X_i \leq x\} - F(x)).
+\]
+
+To establish the asymptotic distribution of $ G_n(x) $, we consider the vector 
+\[
+(G_n(x_1), \ldots, G_n(x_m)) = \frac{1}{\sqrt{n}} \sum_{i=1}^n (\mathbf{1}\{X_i \leq x_1\} - 
+F(x_1), \ldots, \mathbf{1}\{X_i \leq x_m\} - F(x_m)).
+\]
+We calculate the covariance structure of the limiting distribution. The 
+covariance between $ G_n(x) $ and $ G_n(x^{\prime}) $ is:
+\[
+\text{Cov}(G_n(x), G_n(x^{\prime})) = \frac{1}{n} \sum_{t=1}^n \sum_{s=1}^n 
+\text{Cov}(\mathbf{1}\{X_t \leq x\}, \mathbf{1}\{X_t \leq x^{\prime}\}).
+\]
+Since $ \{X_i\} $ is strictly stationary, the covariance depends only on the 
+lag $ h = |t-s| $:
+\[
+\text{Cov}(\mathbf{1}\{X_t \leq x\}, \mathbf{1}\{X_t \leq x^{\prime}\}) = \text{Cov}(\mathbf{1}\{X_h \leq x\}, 
+\mathbf{1}\{X_0 \leq x^{\prime}\}).
+\]
+Thus, the covariance can be expressed as
+\[
+\text{Cov}(G_n(x), G_n(x')) = \frac{1}{n} \sum_{t=1}^n \sum_{h=-t+1}^{n-t} 
+\text{Cov}(\mathbf{1}\{X_h \leq x\}, 
+\mathbf{1}\{X_0 \leq x^{\prime}\}).
+\]
+
+By the mixing condition, the covariances
+$ \text{Cov}(\mathbf{1}\{X_h \leq x\}, \mathbf{1}\{X_0 \leq x^{\prime}\}) $ 
+decay sufficiently fast as $ h \to \infty $. Therefore, the sum converges to:
+\[
+  \lim_{n \to \infty} \text{Cov}(G_n(x), G_n(x'))
+  = \sum_{h=-\infty}^{\infty} \text{Cov}(\mathbf{1}\{X_h \leq x\}, 
+  \mathbf{1}\{X_0 \leq x^{\prime}\}).
+\]
+
+\paragraph{Tightness of $G_n(x)$}
+
+Moreover, we can show the tightness of the process $G_n(s)$. 
+We want to show that for every $\epsilon > 0$,
+\[
+\lim_{\delta \to 0} \limsup_{n \to \infty} \mathbb{P}\left( \omega_{G_n}(\delta) 
+\geq \epsilon \right) = 0,
+\]
+where the modulus of continuity $\omega_{G_n}(\delta)$ is defined as
+\citep{billingsley2013convergence}.
+\[
+\omega_{G_n}(\delta) = \sup_{|s - t| < \delta} |G_n(s) - G_n(t)|.
+\]
 For sufficiently small $\delta$, and leveraging the properties of weakly 
 dependent sequences, we can show that
-\[ \sup_{|x - y| < \delta} |G_n(x) - G_n(y)| = \sup_{|x - y| < \delta} 
-\sqrt{n}|(F_n(x) - F(x)) - (F_n(y) - F(y))| \]
+\[
+  \sup_{|s - t| < \delta} |G_n(s) - G_n(t)|
+  = \sup_{|s - t| < \delta}  \sqrt{n}|(F_n(s) - F(s)) - (F_n(t) - F(t))|
+\]
 is small with high probability.
-Specifically, since $F(x)$ is continuous, for small 
-$\delta$, $|F(x) - F(y)|$ is small. For the empirical 
-distribution function $F_n(x)$, the increments $|F_n(x) - F_n(y)|$ are 
-also controlled. 
-This implies that the process $G_n(x)$ does not exhibit large oscillations over 
-small intervals, thus satisfying the criterion for tightness.
+For $ |s - t| < \delta $,
+\[
+|G_n(s) - G_n(t)| = \sqrt{n} \left| (F_n(s) - F(s; \theta_0)) - (F_n(t) - 
+F(t; \theta_0)) \right|.
+\]
+This can be decomposed as:
+\[
+|G_n(s) - G_n(t)| = \sqrt{n} \left| (F_n(s) - F_n(t)) - (F(s; \theta_0) - 
+F(t; \theta_0)) \right|.
+\]
+
+Remember that $F_n(t) = \sum_{i=1}^n  \mathbf{1}\{X_i \le t\} / n$. Then, for 
+$ |s - t| < \delta $, the difference $ F_n(s) - F_n(t) $ can be written as
+\[
+  F_n(s) - F_n(t) = \frac{1}{n}
+  \sum_{i=1}^n \left( \mathbf{1}\{X_i \leq s\} - \mathbf{1}\{X_i \leq t\} \right),
+\]
+or as 
+$ \mathbb{E}\left[ \frac{1}{n} \sum_{i=1}^n \mathbf{1}\{ t < X_i \leq s \} 
+\right] $. To provide a more precise bound on $ F_n(s) - F_n(t) $, we use 
+Hoeffding's inequality, which states that for any $ t > 0 $,
+\[
+  \mathbb{P}\left( \left| \frac{1}{n} \sum_{i=1}^n \mathbf{1}\{ t < X_i \leq s \} - 
+      \mathbb{E}\left[ \frac{1}{n} \sum_{i=1}^n \mathbf{1}\{ t < X_i \leq s \} 
+      \right] \right| > t \right) \leq 2 \exp\left( -2nt^2 \right).
+\]
+
+Since 
+\[ \mathbb{E}\left[ \frac{1}{n} \sum_{i=1}^n \mathbf{1}\{ t < X_i \leq s \} 
+\right] = F(s; \theta_0) - F(t; \theta_0),
+\]
+we have:
+\[
+  \mathbb{P}\left( \left| \frac{1}{n} \sum_{i=1}^n \mathbf{1}\{ t < X_i \leq s \} - 
+      (F(s; \theta_0) - F(t; \theta_0)) \right| > t \right) \leq
+  2\exp\left( -2nt^2 \right).
+\]
+Because the true CDF is continuous, by definition,
+$ F(s; \theta_0) $, for any $ \epsilon > 0 $,
+there exists a $ \delta > 0 $ such that for $ |s - t| < \delta $,
+$ |F(s; \theta_0) - F(t; \theta_0)| < \epsilon. $
+Using the bound from Hoeffding's inequality, we have:
+\[
+  \mathbb{P}\left( |F_n(s) - F_n(t) - (F(s; \theta_0) - F(t; \theta_0))| \geq 
+    \epsilon \right) \leq 2 \exp\left( -2n\epsilon^2 \right).
+\]
+Then, for sufficiently large $ n $ and small $ \delta $,
+$ \mathbb{P}\left( \omega_{G_n}(\delta) \geq \epsilon \right) \leq 2 
+\exp\left( -2n\epsilon^2 \right). $ Taking limits, we conclude:
+$ \lim_{\delta \to 0} \limsup_{n \to \infty} \mathbb{P}\left( 
+\omega_{G_n}(\delta) \geq \epsilon \right) = 0. $
+
+\paragraph{Convergence in distribution}
 Therefore, we have
@@
 Define $G_n^{(b)}(x)$ in the same way as $G_n(x)$ with $X_1, \dots, X_n$ being 
-replaced by the bootstrap samples %$\{X_i: i = 1, \ldots, n\}^{(b)}=\{X_1^{(b)},\dots,X_n^{(b)}\}$.
-$X_1^{(b)},\dots,X_n^{(b)}.$
+replaced by the bootstrap samples $X_1^{(b)},\dots,X_n^{(b)}.$
 
@@
 \sum^{j - n + l -1}_{i=1}h(X_{i};\hat{\theta}_0)]]
-\\=&\frac{k}{n^2}\sum^{n}_{i=1}l h(X_{i};\hat{\theta}_0),
-\end{align*}.
+\\=&\frac{k}{n^2}\sum^{n}_{i=1}l h(X_{i};\hat{\theta}_0).
+\end{align*}
+
 Moreover, we have
@@
 \end{align*}
-with $W_t=
+with
+\[
+  W_t=
  \begin{cases}
@@
 \sum^{t - n + l -1}_{i=1}h(X_{i};\hat{\theta}_0)  & \text{if } t \geq n - 1 + 2
-\end{cases}$
+\end{cases}
+\]
 and $\bar{W}=\sum^{n}_{t=1}W_t/n$,
-which is expected to converge to $s^2$ almost surely. Similar calculations apply 
+which is expected to converge to $s^2$ almost surely.
+
+Similar calculations apply 
 to $G_n^{(b)}(x)$ and we expect that
@@
 From the CLT, the process $G_n^{(b)}(x) = \sqrt{n}(F_n^{(b)}(x) - F_n(x))$ 
-converges 
-to 
-$G_{\infty}(x)$.
+converges  to $G_{\infty}(x)$.
+
+\paragraph{Finite-Dimensional Convergence in the Bootstrap World}
 
@@
 $s^2$.
-We can show tightness of $G_n^{(b)}(x)$ similarly to how we established 
-tightness of $G_n(x)$
-The results then follow from the continuous mapping theorem.
+
+\paragraph{Tightness in Bootstrap World}
+
 \end{proof}
@@
 \bibliographystyle{chicago} 
-\bibliography{ref}
+\bibliography{citations}
 

### 2024-07-11 manuscript/supplement.tex
question on theta0 hat

@@
 \newcommand{\mc}[1]{\textcolor{blue}{MC: (#1)}}
+\newcommand{\jy}[1]{\textcolor{purple}{JY: (#1)}}
 
@@
 \[
-\text{Cov}(G_{\infty}(x_i), G_{\infty}(x_j)) = \sum_{h=-\infty}^{\infty} \text{Cov}(\mathbf{1}\{X_0 \leq x\}, \mathbf{1}\{X_h \leq x^{\prime}\}),
+  \text{Cov}(G_{\infty}(x_i), G_{\infty}(x_j)) =
+  \sum_{h=-\infty}^{\infty}
+  \text{Cov}(\mathbf{1}\{X_0 \leq x\}, \mathbf{1}\{X_h \leq x^{\prime}\}),
 \]
@@
 $
-Therefore, the empirical process is:
+Therefore, the empirical process is
 \[
@@
 \[
-(G_n(x_1), \ldots, G_n(x_m)) = \frac{1}{\sqrt{n}} \sum_{i=1}^n (\mathbf{1}\{X_i \leq x_1\} - 
-F(x_1), \ldots, \mathbf{1}\{X_i \leq x_m\} - F(x_m)).
+  (G_n(x_1), \ldots, G_n(x_m)) =
+  \frac{1}{\sqrt{n}} \sum_{i=1}^n
+  \left(\mathbf{1}\{X_i \leq x_1\} - 
+    F(x_1), \ldots, \mathbf{1}\{X_i \leq x_m\} - F(x_m)\right).
 \]
@@
 \text{Cov}(G_n(x), G_n(x^{\prime})) = \frac{1}{n} \sum_{t=1}^n \sum_{s=1}^n 
-\text{Cov}(\mathbf{1}\{X_t \leq x\}, \mathbf{1}\{X_t \leq x^{\prime}\}).
+\text{Cov}\left(\mathbf{1}\{X_t \leq x\}, \mathbf{1}\{X_t \leq x^{\prime}\}\right).
 \]
@@
 \end{align*}
-and $U\sim N(0,s^2)$ with 
+and $U\sim N(0, s^2)$ with 
 \begin{align*}
@@
   We want to show that
+  \jy{What is $\hat\theta_0$? Should it be $\hat\theta_n$?}
 \begin{align}\label{eq-con-boot}
@@
  \begin{cases}
-\sum^{t+l-1}_{i=t}h(X_i;\hat{\theta}_0)  & \text{if } t \leq n - 1 + 1,\\
+\sum^{t+l-1}_{i=t}h(X_i;\hat{\theta}_0)  , & \text{if } t \leq n - 1 + 1,\\
 \sum^{n}_{i=t}h(X_{i};\hat{\theta}_0) +
-\sum^{t - n + l -1}_{i=1}h(X_{i};\hat{\theta}_0)  & \text{if } t \geq n - 1 + 2
+\sum^{t - n + l -1}_{i=1}h(X_{i};\hat{\theta}_0) , & \text{if } t \geq n - 1 + 2,
 \end{cases}
@@
 $ so
-$
-\sqrt{n}(F(x;\hat{\theta}_n^{(b)}) - F(x;\hat{\theta}_0)) \approx \sqrt{n} 
-(F(x;\hat{\theta}_0) + f(x; 
-\hat{\theta}_0) (\hat{\theta}_n^{(b)} - \hat{\theta}_0) - F(x;\hat{\theta}_0)) 
-\approx
-f(x; 
-\hat{\theta}_0) \sqrt{n} (\hat{\theta}_n^{(b)} - \hat{\theta}_0).
-$
+\begin{align*}
+  \sqrt{n}(F(x;\hat{\theta}_n^{(b)}) - F(x;\hat{\theta}_0))
+  &\approx \sqrt{n} (F(x;\hat{\theta}_0) +
+  f(x; \hat{\theta}_0) (\hat{\theta}_n^{(b)} - \hat{\theta}_0) - F(x;\hat{\theta}_0)) \\
+  &\approx  f(x; \hat{\theta}_0) \sqrt{n} (\hat{\theta}_n^{(b)} - \hat{\theta}_0).
+\end{align*}
 
 Substituting the expansion of $\hat{\theta}_n^{(b)}$:
-$
+\[
 \sqrt{n} (\hat{\theta}_n^{(b)} - \hat{\theta}_0) = \frac{1}{\sqrt{n}} 
@@
 h(X_i^{(b)}; \hat{\theta}_0) + R_n^{(b)}.
-$
+\]
 
 Since $R_n^{(b)} \overset{p^{(b)}}{\rightarrow} 0$, 
-$
+\[
 \sqrt{n}(F(x;\hat{\theta}_n^{(b)}) - F(x;\hat{\theta}_0)) \approx 
@@
 \hat{\theta}_0) \right).
-$
-
+\]
 The term $\frac{1}{\sqrt{n}} \sum_{i=1}^{n} h(X_i^{(b)}; \hat{\theta}_0)$ 

### 2024-07-12 manuscript/manuscript.tex
hat theta_0

@@
 We then use block bootstrap to approximate the asymptotic distribution of
-the KS statistic under $H_0$. In particular, we
+the KS statistic under $H_0$. Let $\hat{\theta}_0 = 
+\mathbb{E}^{(b)}[\hat\theta^{(b)}_n]$. In particular, we
 use the distribution of $\sqrt{n}(F^{(b)}_n(x) - \mathbb{E}^{(b)}[F^{(b)}_n(x)])$
@@
 $\sqrt{n}(F_n(x) - F(x; \theta_0))$, and the distribution of 
-$\sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; \mathbb{E}^{(b)}[\hat\theta^{(b)}_n]))$ as
+$\sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; \hat{\theta}_0))$ as
 an approximation of the distribution of 
@@
 The expected values $\mathbb{E}^{(b)}[F^{(b)}_n(x)]$ and
-$\mathbb{E}^{(b)}[\hat\theta^{(b)}_n]$ can be approximated by, respectively,
+$\hat{\theta}_0 = \mathbb{E}^{(b)}[\hat\theta^{(b)}_n]$ can be approximated by, respectively,
 $\mathbb{E}^{(b)}[F^{(b)}_n(x)] = \frac{1}{B}\sum_{b = 1}^BF^{(b)}_n(x)$ and
@@
   Y^{(b)}_n(x) &= \sqrt{n}(F^{(b)}_n(x) - \mathbb{E}^{(b)}[F^{(b)}_n(x)]) - 
-             \sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; \mathbb{E}^{(b)}[\hat\theta^{(b)}_n)]) \\
+             \sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; \hat{\theta}_0) \\
            &= \sqrt{n}(F^{(b)}_n(x) - F(x; \hat\theta^{(b)}_n)) -
-             \sqrt{n}(\mathbb{E}^{(b)}[F^{(b)}_n(x)] - F(x; \mathbb{E}^{(b)}[\hat\theta^{(b)}_n])),
+             \sqrt{n}(\mathbb{E}^{(b)}[F^{(b)}_n(x)] - F(x; \hat{\theta}_0)),
 \end{align*}
@@
   $B_{n}(x) = \sqrt{n}(\mathbb{E}^{(b)}[F^{(b)}_n(x)] - 
-  F(x; \mathbb{E}^{(b)}[\hat\theta^{(b)}_n]))$ is the known
+  F(x; \hat{\theta}_0))$ is the known
   bias term.

### 2024-07-18 manuscript/manuscript.tex
notation suggestions for expectation in bootstrap world

@@
 
-Continuing using the notation in the independent case,
+As in the independent case,
 we use $F^{(b)}_n$ and $\hat\theta^{(b)}_n$ for the empirical distribution and
@@
 We then use block bootstrap to approximate the asymptotic distribution of
-the KS statistic under $H_0$. Let $\hat{\theta}_0 = 
-\mathbb{E}^{(b)}[\hat\theta^{(b)}_n]$. In particular, we
+the KS statistic under $H_0$. Let
+$\hat{\theta}_0 = \mathbb{E}^{(b)}[\hat\theta^{(b)}_n]$, where
+$\mathbb{E}^{(b)}$ denotes the expectation with respect to the
+\jy{The superscript $(b)$ is unclear to me: we already used $b$ to
+  index $1,  \ldots, B$. Can we use a star for this superscript?}
+bootstrap distribution (i.e., the randomness due
+to the resampling using block bootstrap) conditional on the observations 
+$X_1, \dots, X_n$.
+\jy{Specifically, how about using
+  $\mathbb{E}^*$ denote the expectation in the bootstrap world?
+  Then we can use
+  $\mathbb{E}^*_B (F^{(b)}_n (x))= \frac{1}{B} \sum_{b = 1}^B
+  F^{(b)}_n(x)$ to denote an approximator
+  of $\mathbb{E}^* (F^{(b)}_n (x))$, and use
+  $\mathbb{E}^*_B(\hat\theta_n^{(b)}) =
+  \frac{1}{B}\sum_{b = 1}^B\hat\theta^{(b)}_n$ to
+  denote an approximator of  
+  $\hat{\theta}_0 = \mathbb{E}^*[\hat\theta^{(b)}_n]$?
+}
+In particular, we
 use the distribution of $\sqrt{n}(F^{(b)}_n(x) - \mathbb{E}^{(b)}[F^{(b)}_n(x)])$
@@
 $\sqrt{n}(F_n(x) - F(x; \theta_0))$, and the distribution of 
-$\sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; \hat{\theta}_0))$ as
+$\sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; \hat\theta_0))$ as
 an approximation of the distribution of 
 $\sqrt{n}(F(x; \hat\theta_n) - F(x; \theta_0))$.
-Here $\mathbb{E}^{(b)}$ denotes the expectation with respect to the bootstrap 
-distribution 
-(i.e., the randomness due
-to the resampling using block bootstrap) conditional on the observations 
-$X_1, \dots, X_n$.
+Here 
 The expected values $\mathbb{E}^{(b)}[F^{(b)}_n(x)]$ and
-$\hat{\theta}_0 = \mathbb{E}^{(b)}[\hat\theta^{(b)}_n]$ can be approximated by, respectively,
-$\mathbb{E}^{(b)}[F^{(b)}_n(x)] = \frac{1}{B}\sum_{b = 1}^BF^{(b)}_n(x)$ and
+$\hat{\theta}_0 = \mathbb{E}^{(b)}[\hat\theta^{(b)}_n]$ can be
+approximated by, respectively,
+$\mathbb{E}^{(b)}[F^{(b)}_n(x)] = \frac{1}{B}\sum_{b = 1}^B F^{(b)}_n(x)$ and
 $\mathbb{E}^{(b)}[\hat\theta^{(b)}_n]  =  \frac{1}{B}\sum_{b = 1}^B\hat\theta^{(b)}_n$.

### 2024-08-18 manuscript/supplement.tex
hat theta_0
minor comments on notation
an  attempt to complete the proof of proposition 2

@@
   We want to show that
-  \jy{What is $\hat\theta_0$? Should it be $\hat\theta_n$?}
 \begin{align}\label{eq-con-boot}
@@
 
+To establish tightness, we need to demonstrate that for any \(\epsilon > 0\),
+\[
+\lim_{\delta \to 0} \limsup_{n \to \infty} \mathbb{P}^*\left( \sup_{|x - y| < \delta} |G_n^{(b)}(x) - G_n^{(b)}(y)| \geq \epsilon \right) = 0.
+\]
+
+Consider the difference
+\[
+G_n^{(b)}(x) - G_n^{(b)}(y) = \sqrt{n} \left( F_n^{(b)}(x) - F_n^{(b)}(y) - (F_n(x) - F_n(y)) \right).
+\]
+This difference can be further decomposed as
+\[
+G_n^{(b)}(x) - G_n^{(b)}(y) = \sqrt{n} \left( \frac{1}{n} \sum_{i=1}^n \left[ 1\{X_i^{(b)} \leq x\} - 1\{X_i^{(b)} \leq y\} \right] - (F(x) - F(y)) \right).
+\]
+
+Given that \(F(x)\) is continuous, and using the fact that bootstrap
+samples maintain the mixing properties of the original data (Politis,
+Romano, and Wolf, 1999), we can apply a concentration inequality such
+as Hoeffding's inequality to the bootstrap samples. This yields that
+for any small \(\delta > 0\),
+\[
+\mathbb{P}^*\left( \sup_{|x - y| < \delta} |G_n^{(b)}(x) - G_n^{(b)}(y)| \geq \epsilon \right) \leq 2 \exp\left( -2n \epsilon^2 \right).
+\]
+Taking the limit as \(\delta \to 0\) and \(n \to \infty\), we conclude that
+\[
+\lim_{\delta \to 0} \limsup_{n \to \infty} \mathbb{P}^*\left( \sup_{|x - y| < \delta} |G_n^{(b)}(x) - G_n^{(b)}(y)| \geq \epsilon \right) = 0,
+\]
+which establishes tightness for \(G_n^{(b)}(x)\).
+
+\bigskip
+
+Given the finite-dimensional convergence and tightness established
+above, by the continuous mapping theorem, we have
+\[
+T_n^{(b)} = \sup_x \left| G_n^{(b)}(x) + f(x; \theta_0) U \right| \Rightarrow^* \sup_x \left| G_\infty(x) + f(x; \theta_0) U \right|,
+\]
+completing the proof.
+
 \end{proof}

### 2024-08-18 manuscript/manuscript.tex
minor comments on notation
use png figures for the qq plot with much smaller sizes
notation cleaning and proposition removal

--- 2024-07-12 manuscript/manuscript.tex
@@
 We then use block bootstrap to approximate the asymptotic distribution of
-the KS statistic under $H_0$. Let $\hat{\theta}_0 = 
-\mathbb{E}^{(b)}[\hat\theta^{(b)}_n]$. In particular, we
-use the distribution of $\sqrt{n}(F^{(b)}_n(x) - \mathbb{E}^{(b)}[F^{(b)}_n(x)])$
+the KS statistic under $H_0$. Let
+$\theta_0^* = \mathbb{E}^{*}[\hat\theta^{(b)}_n]$, where
+$\mathbb{E}^{*}$ denotes the expectation with respect to the
+bootstrap distribution (i.e., the randomness due
+to the resampling using block bootstrap) conditional on the observations 
+$X_1, \dots, X_n$. In particular, we
+use the distribution of $\sqrt{n}(F^{(b)}_n(x) - \mathbb{E}^{*}[F^{(b)}_n(x)])$
 as an approximation of the distribution of
 $\sqrt{n}(F_n(x) - F(x; \theta_0))$, and the distribution of 
-$\sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; \hat{\theta}_0))$ as
+$\sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; \theta_0^*))$ as
 an approximation of the distribution of 
 $\sqrt{n}(F(x; \hat\theta_n) - F(x; \theta_0))$.
-Here $\mathbb{E}^{(b)}$ denotes the expectation with respect to the bootstrap 
-distribution 
-(i.e., the randomness due
-to the resampling using block bootstrap) conditional on the observations 
-$X_1, \dots, X_n$.
-The expected values $\mathbb{E}^{(b)}[F^{(b)}_n(x)]$ and
-$\hat{\theta}_0 = \mathbb{E}^{(b)}[\hat\theta^{(b)}_n]$ can be approximated by, respectively,
-$\mathbb{E}^{(b)}[F^{(b)}_n(x)] = \frac{1}{B}\sum_{b = 1}^BF^{(b)}_n(x)$ and
-$\mathbb{E}^{(b)}[\hat\theta^{(b)}_n]  =  \frac{1}{B}\sum_{b = 1}^B\hat\theta^{(b)}_n$.
+Here, the expected values $\mathbb{E}^{*}[F^{(b)}_n(x)]$ and
+$\theta_0^* = \mathbb{E}^{*}[\hat\theta^{(b)}_n]$ can be
+approximated by, respectively,
+$\mathbb{E}_B^{*}[F^{(b)}_n(x)] = \frac{1}{B}\sum_{b = 1}^B F^{(b)}_n(x)$ and
+$\mathbb{E}_B{*}[\hat\theta^{(b)}_n]  =  \frac{1}{B}\sum_{b = 1}^B\hat\theta^{(b)}_n$.
 
-Then, we can define
+Then, for each $b \in \{1, \dots, B\}$, we can define
 \begin{align*}
-  Y^{(b)}_n(x) &= \sqrt{n}(F^{(b)}_n(x) - \mathbb{E}^{(b)}[F^{(b)}_n(x)]) - 
-             \sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; \hat{\theta}_0) \\
+  Y^{(b)}_n(x) &= \sqrt{n}(F^{(b)}_n(x) - \mathbb{E}^{*}[F^{(b)}_n(x)]) - 
+             \sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; \theta_0^*) \\
            &= \sqrt{n}(F^{(b)}_n(x) - F(x; \hat\theta^{(b)}_n)) -
-             \sqrt{n}(\mathbb{E}^{(b)}[F^{(b)}_n(x)] - F(x; \hat{\theta}_0)),
+             \sqrt{n}(\mathbb{E}^{*}[F^{(b)}_n(x)] - F(x; \theta_0^*)),
 \end{align*}
@@
   where 
-  $B_{n}(x) = \sqrt{n}(\mathbb{E}^{(b)}[F^{(b)}_n(x)] - 
-  F(x; \hat{\theta}_0))$ is the known
-  bias term.
+  $B_{n}(x) = \sqrt{n}(\mathbb{E}^{*}[F^{(b)}_n(x)] - 
+  F(x; \theta_0^*))$ is the approximated bias term.
 \end{enumerate}
@@
 Assume that the time series $\{X_i\}$ is stationary and
-strongly mixing. The following results provide theoretical validity
-of the NPBB procedure of the KS test. Sketches of their proofs are
-in the Supporting Information, with most arguments similar to those
-in \citet{kunsch1989jackknife}.
-
-\begin{proposition}\label{prop:Tn}
+strongly mixing. Using arguments similar to those
+in \citet{kunsch1989jackknife}, we conjecture the following results
+justifying the validity of the NPBB procedure of the KS test.
 As $1/l+l/n\rightarrow 0$,
@@
 and Gaussian random variable  $U$.
-\end{proposition}
-
-\begin{proposition}\label{prop:Tnboot}
-  As $1/l+l/n\rightarrow 0$,
+Further,  as $1/l+l/n\rightarrow 0$,
 \[
@@
 based on the bootstrap sample $\{X_i^{(b)}: i = 1, \ldots, n\}$.
-\end{proposition}
-
 Following the arguments in the proof of the Glivenko--Cantelli
-Theorem, the result in Proposition~\ref{prop:Tnboot} can be further
+Theorem, the bootstrap consistency result could be further
 strengthened to allow uniform convergence over $x$. That is,
@@
   \centering
-  \includegraphics[width = .9\textwidth]{figures/normal}
-  \includegraphics[width = .9\textwidth]{figures/gamma}
+  \includegraphics[width = .9\textwidth]{figures/normal.png}
+  \includegraphics[width = .9\textwidth]{figures/gamma.png}
   \caption{Q-Q plots of the p-values testing that a time series
@@
 of \citet{zeimbekakis2022misuses}, which requires a working dependence model, it
-is reliable regardless of whether the working dependence model approximates the
-true dependence model.
+is reliable with no need to worry about whether the working dependence
+model approximates the true dependence model.
 
@@
 either sample, maintaining the advantageous feature of the original method.
+Finally, a rigorous theoretical justification of the NPBB method for
+stationary series is of significant academic interest. Establishing
+precise conditions for the asymptotic behavior of the KS statistic and
+the consistency of the bootstrap procedure would offer valuable
+practical insights into the scenarios where the NPBB approach is
+expected to perform optimally.
 
@@
 
-% \nocite{*}% Show all bib entries - both cited and uncited; comment this line to view only cited bib entries;
-
-\section*{Supporting Information}
-
-The proofs of the two propositions in \ref{sub:npbb} are sketched in
-the supplement.
-
 \end{document}

### 2024-08-19 manuscript/manuscript.tex
minor

@@
 $\sqrt{n}(F(x; \hat\theta_n) - F(x; \theta_0))$.
-Here, the expected values $\mathbb{E}^{*}[F^{(b)}_n(x)]$ and
-$\theta_0^* = \mathbb{E}^{*}[\hat\theta^{(b)}_n]$ can be
-approximated by, respectively,
-$\mathbb{E}_B^{*}[F^{(b)}_n(x)] = \frac{1}{B}\sum_{b = 1}^B F^{(b)}_n(x)$ and
-$\mathbb{E}_B{*}[\hat\theta^{(b)}_n]  =  \frac{1}{B}\sum_{b = 1}^B\hat\theta^{(b)}_n$.
 
@@
   $B_{n}(x) = \sqrt{n}(\mathbb{E}^{*}[F^{(b)}_n(x)] - 
-  F(x; \theta_0^*))$ is the approximated bias term.
+  F(x; \theta_0^*))$ is the bias term, and
+  the expected values $\mathbb{E}^{*}[F^{(b)}_n(x)]$ and
+$\theta_0^* = \mathbb{E}^{*}[\hat\theta^{(b)}_n]$ can be
+approximated by, respectively,
+$\mathbb{E}_B^{*}[F^{(b)}_n(x)] = \frac{1}{B}\sum_{b = 1}^B F^{(b)}_n(x)$ and
+$\mathbb{E}_B{*}[\hat\theta^{(b)}_n]  =  \frac{1}{B}\sum_{b = 1}^B\hat\theta^{(b)}_n$.
 \end{enumerate}

### 2024-08-19 manuscript/manuscript.tex
fixed small typo

--- 2024-08-18 manuscript/manuscript.tex
@@
 $\mathbb{E}_B^{*}[F^{(b)}_n(x)] = \frac{1}{B}\sum_{b = 1}^B F^{(b)}_n(x)$ and
-$\mathbb{E}_B{*}[\hat\theta^{(b)}_n]  =  \frac{1}{B}\sum_{b = 1}^B\hat\theta^{(b)}_n$.
+$\mathbb{E}_B^{*}[\hat\theta^{(b)}_n]  =  \frac{1}{B}\sum_{b = 1}^B\hat\theta^{(b)}_n$.
 

### 2024-08-19 manuscript/manuscript.tex

--- 2024-08-19 manuscript/manuscript.tex
@@
 $\mathbb{E}_B^{*}[F^{(b)}_n(x)] = \frac{1}{B}\sum_{b = 1}^B F^{(b)}_n(x)$ and
-$\mathbb{E}_B{*}[\hat\theta^{(b)}_n]  =  \frac{1}{B}\sum_{b = 1}^B\hat\theta^{(b)}_n$.
+$\mathbb{E}_B^{*}[\hat\theta^{(b)}_n]  =  \frac{1}{B}\sum_{b = 1}^B\hat\theta^{(b)}_n$.
 \end{enumerate}

### 2024-08-19 manuscript/manuscript.tex
bias term notation change

--- 2024-08-19 manuscript/manuscript.tex
@@
     T^{(b)}_n = \sup_x \Big\vert \sqrt{n}\left(F^{(b)}_n(x) 
-    - F(x; \hat\theta^{(b)}_n)\right) - B_n(x) \Big\vert.
+    - F(x; \hat\theta^{(b)}_n)\right) - C_n(x) \Big\vert.
   \]
   where 
-  $B_{n}(x) = \sqrt{n}(F_n(x) - F(x; \hat\theta_n))$ is the estimated
+  $C_{n}(x) = \sqrt{n}(F_n(x) - F(x; \hat\theta_n))$ is the estimated
   bias term.
@@
     T^{(b)}_n = \sup_x \Big\vert \sqrt{n}\left(F^{(b)}_n(x) 
-    - F(x; \hat\theta^{(b)}_n)\right) - B_n(x) \Big\vert.
+    - F(x; \hat\theta^{(b)}_n)\right) - C_n(x) \Big\vert.
   \]
   where 
-  $B_{n}(x) = \sqrt{n}(\mathbb{E}^{*}[F^{(b)}_n(x)] - 
+  $C_{n}(x) = \sqrt{n}(\mathbb{E}^{*}[F^{(b)}_n(x)] - 
   F(x; \theta_0^*))$ is the bias term, and
@@
 strongly mixing. Using arguments similar to those
-in \citet{kunsch1989jackknife}, we conjecture the following results
-justifying the validity of the NPBB procedure of the KS test.
+in \citet{kunsch1989jackknife}, under certain conditions, the 
+following results can be shown to
+justify the validity of the NPBB procedure of the KS test.
 As $1/l+l/n\rightarrow 0$,

### 2024-08-19 manuscript/manuscript.tex
changed brownian bridge notation

@@
 situation, the second term vanishes, and $T_n$ converges in distribution to that
-of $\sup_t | B(F(t; \theta_0)) |$, where $B(\cdot)$ is the standard Brownian bridge
+of $\sup_t | J(F(t; \theta_0)) |$, where $J(\cdot)$ is the standard Brownian bridge
 \citep{kolmogorov1933sulla}. With $\hat\theta_n$ in place of $\theta$, the

### 2024-09-02 manuscript/manuscript.tex
changed email
cover letter and reformmating

@@
-\documentclass[APA,Times1COL]{WileyNJDv5} %STIX1COL,STIX2COL,STIXSMALL
+%&latex
+\documentclass[12pt]{article}
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{booktabs}
+\usepackage{graphicx}
+\usepackage{psfrag,epsf}
+\usepackage{enumerate}
+\usepackage{natbib}
+\usepackage{url} % not crucial - just used below for the URL 
+\usepackage{comment}
 
-\usepackage{natbib}
-\usepackage{lipsum}
+%\pdfminorversion=4
+% NOTE: To produce blinded version, replace "0" with "1" below.
+\newcommand{\blind}{0}
 
-\articletype{Article Type}%
-
-\received{Date Month Year}
-\revised{Date Month Year}
-\accepted{Date Month Year}
-\journal{Journal}
-\volume{00}
-\copyyear{2023}
-\startpage{1}
-
-\raggedbottom
-
-\newcommand{\jy}[1]{\textcolor{blue}{JY: (#1)}}
-\newcommand{\eds}[1]{\textcolor{red}{EDS: (#1)}}
-\newcommand{\mc}[1]{\textcolor{green}{MC: (#1)}}
-
-% NOTE: To produce blinded version, replace "0" with "1" below.
-\newcommand{\blind}{1]}
+% DON'T change margins - should be 1 inch all around.
+\addtolength{\oddsidemargin}{-.5in}%
+\addtolength{\evensidemargin}{-.5in}%
+\addtolength{\textwidth}{1in}%
+\addtolength{\textheight}{1.3in}%
+\addtolength{\topmargin}{-.8in}%
 
@@
 
-\title{Nonparametric Block Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test}
+%\bibliographystyle{natbib}
 
-\author[1,2]{Mathew Chandy}
+\def\spacingset#1{\renewcommand{\baselinestretch}%
+{#1}\small\normalsize} \spacingset{1}
 
-\author[1]{Elizabeth D. Schifano}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\author[1]{Jun Yan}
+\if0\blind
+{
+  \title{\bf Nonparametric Block Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test}
+  \author{Mathew Chandy\\
+    Department of Statistics, University of Connecticut\\
+    Department of Statistics and Data Science, University of California, Los Angeles,\\
+    Elizabeth D. Schifano\\
+    Department of Statistics, University of Connecticut,\\
+    Jun Yan\thanks{
+    The authors gratefully acknowledge the National Science Foundation (NSF).}\hspace{.2cm}\\
+    Department of Statistics, University of Connecticut,\\
+    and\\
+    Xianyang Zhang\\
+    Department of Statistics, Texas A\&M University}
+  \maketitle
+} \fi
 
-\author[3]{Xianyang Zhang}
+\if1\blind
+{
+  \bigskip
+  \bigskip
+  \bigskip
+  \begin{center}
+    {\LARGE\bf Title}
+\end{center}
+  \medskip
+} \fi
 
-\authormark{CHANDY \textsc{et al.}}
-\titlemark{NONPARAMETRIC BLOCK BOOTSTRAP KOLMOGOROV-SMIRNOV GOODNESS-OF-FIT TEST}
-
-\address[1]{\orgdiv{Statistics}, \orgname{University of Connecticut},
-\orgaddress{\state{Connecticut}, \country{United States}}}
-
-\address[2]{\orgdiv{Statistics and Data Science}, \orgname{University of California,
-Los Angeles},
-\orgaddress{\state{California}, \country{United States}}}
-
-\address[3]{\orgdiv{Statistics}, \orgname{Texas A\&M University}, \orgaddress{\state{Texas}, \country{United States}}}
-
-\corres{\email{mathewchandy03@gmail.com}
-\email{elizabeth.schifano@uconn.edu}
-\email{jun.yan@uconn.edu} 
-\email{zhangxiany@stat.tamu.edu} }
-
-\presentaddress{215 Glenbrook Road, Unit 4120
-Storrs, Connecticut 06269-4120}
-
-%\fundingInfo{Text}
-%\JELinfo{ejlje}
-
-\abstract[Abstract]{The Kolmogorov--Smirnov (KS) test is a widely used 
+\bigskip
+\begin{abstract}
+The Kolmogorov--Smirnov (KS) test is a widely used 
 statistical test that
@@
 S\&P 500 index, showcasing its utility in real-world
-applications.}
+applications.
+\end{abstract}
 
-% alphabetical; no repeating anything in the title already
-\keywords{bias-correction, financial data, marginal distribution,
-  stationary series, time series}
+\noindent%
+{\it Keywords:}  bias-correction, financial data, marginal distribution,
+  stationary series, time series
+\vfill
 
-\jnlcitation{\cname{%
-\author{Chandy M.},
-\author{Schifano E},
-\author{Yan J}, and
-\author{Zhang X}}.
-\ctitle{Nonparametric block bootstrap Kolmogorov-Smirnov goodness-of-fit test.} \cjournal{\it Stat.} \cvol{2024;}.}
-
-\maketitle
-
-\renewcommand\thefootnote{}
-\footnotetext{\textbf{Abbreviations:} }
-
-\renewcommand\thefootnote{\fnsymbol{footnote}}
-\setcounter{footnote}{1}
-
+\newpage
+\spacingset{1.45} % DON'T change the spacing!
 \section{Introduction}\label{sec:intro}
@@
 The p-value of the basic bootstrap KS test can be approximated
-as $p = \sum_{b=1}^B I\{T^{(b)}_n > T_n\} / B$.
+as $p = \sum_{b=1}^B \mathbf{1}\{T^{(b)}_n > T_n\} / B$.
 
@@
 The p-value of the block bootstrap KS test can be approximated
-as $p = \sum_{b=1}^B I\{T^{(b)}_n > T_n\} / B$.
+as $p = \sum_{b=1}^B \mathbf{1}\{T^{(b)}_n > T_n\} / B$.
 
@@
   \centering
-  \includegraphics[width = .9\textwidth]{figures/normal.png}
-  \includegraphics[width = .9\textwidth]{figures/gamma.png}
+  \includegraphics[width = .9\textwidth]{figures/normal}
+  \includegraphics[width = .9\textwidth]{figures/gamma}
   \caption{Q-Q plots of the p-values testing that a time series
@@
 
-%\backmatter
+\bigskip
+\begin{center}
+{\large\bf SUPPLEMENTARY MATERIAL}
+\end{center}
 
-\bmsection*{Data availability statement}
-The data and code used in the real data analysis and simulation
+\begin{description}
+
+\item[Funding statement:]JY and XZ's research was partially supported by NSF grant
+DMS2210735.
+
+\item[Conflict of interest disclosure:]The authors declare no potential conflict 
+of interests.
+
+\item[Data availability statement:] The data and code used in the real data analysis and simulation
 studies are publicly available in a GitHub repo:
@@
 
-\bmsection*{Funding statement}
+\end{description}
 
-JY and XZ's research was partially supported by NSF grant
-DMS2210735.
-
-\bmsection*{Conflict of interest disclosure}
-
-The authors declare no potential conflict of interests.
-
-% \bmsection*{Ethics approval statement}
+\bibliographystyle{agsm}
 
 \bibliography{citations}
-
 \end{document}

### 2024-09-02 manuscript/statistical_practice_cover_letter.tex
cover letter and reformmating

\documentclass{article}
\usepackage{charter}
\usepackage[margin=1in]{geometry}
\usepackage{fancyhdr,graphicx}
\usepackage{xspace}

\fancypagestyle{firstpage}{%
  \fancyhf{} % Clear header/footer
  \renewcommand{\headrulewidth}{0pt}%
  \renewcommand{\footrulewidth}{1pt}%
  % Add more detail here if needed
}
\fancypagestyle{otherpages}{%
  \fancyhf{}% Clear header/footer
  \renewcommand{\headrulewidth}{1pt}%
  \renewcommand{\footrulewidth}{1pt}%
  % Add more detail here if needed
}

\AtBeginDocument{\thispagestyle{firstpage}}
\pagestyle{otherpages}

\setlength{\parindent}{0pt}
\setlength{\parskip}{1ex}

\begin{document}

\vspace*{\dimexpr-\headsep-\headheight-1pt}

% \includegraphics[width=1in]{logo.jpg}

\rule{\linewidth}{1pt}

\bigskip

%----------------------------------------------------------------------------------------
%	YOU ONLY NEED TO FILL IN THE FOLLOWING LATEX MACROS
%----------------------------------------------------------------------------------------

% Title of the paper
\newcommand{\PaperTitle}{Nonparametric Block Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test\xspace}

% Full name of the authors
\newcommand{\AuthorOne}{Mathew Chandy\xspace}
\newcommand{\AuthorTwo}{Elizabeth D. Schifano\xspace}
\newcommand{\AuthorThree}{Jun Yan\xspace}
\newcommand{\AuthorFour}{Xianyang Zhang\xspace}

% Full name of the Journal's Editor in Chief
\newcommand{\EditorInChief}{Min-ge Xie\xspace}

% Journal
\newcommand{\Journal}{The American Statistician\xspace}

% Body
\newcommand{\Contribution}{X\xspace}
\newcommand{\Problem}{Y\xspace}
\newcommand{\Solution}{Z\xspace}
\newcommand{\Evaluation}{D\xspace}
\newcommand{\NoveltyClaim}{E\xspace}

% List of contributions
\newcommand{\ContributionOne}{Contribution A.\xspace}
\newcommand{\ContributionTwo}{Contribution B.\xspace}
\newcommand{\ContributionThree}{Contribution C.\xspace}
\newcommand{\ContributionFour}{Contribution D.\xspace}

% Suggested editors
\newcommand{\EditorOne}{Editor \#1\xspace}
\newcommand{\EditorOneExpertise}{A\xspace}

\newcommand{\EditorTwo}{Editor \#2\xspace}
\newcommand{\EditorTwoExpertise}{B\xspace}

\newcommand{\EditorThree}{Editor \#3\xspace}
\newcommand{\EditorThreeExpertise}{C\xspace}

%----------------------------------------------------------------------------------------
%	YOUR NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\hfill
\begin{tabular}{ l @{} }
  \today \\[12pt] % Date
  Department of Statistics,\\
  University of Connecticut\\
  Room 323, Philip E. Austin Building\\
  215 Glenbrook Road, Unit 4120\\
  Storrs, CT 06269-4120\\
  \\
  Department of Statistics and Data Science,\\
  University of California, Los Angeles\\
  8125 Math Sciences Bldg. Box 951554\\
  Los Angeles, CA 90095-1554\\
  \\
  Department of Statistics,\\
  Texas A\&M University\\
  447 Blocker Building (BLOC)\\
  3143 TAMU | 155 Ireland St\\
  College Station, TX 77843-3143
\end{tabular}

%----------------------------------------------------------------------------------------
%	LETTER CONTENT
%----------------------------------------------------------------------------------------

\bigskip

Dear Dr. Xie,

\bigskip

We are pleased to submit the manuscript entitled ``Nonparametric Block Bootstrap 
Kolmogorov-Smirnov Goodness-of-Fit Test" for 
consideration in the Statistical Practice section of 
\textit{American Statistician}. We certify that this 
manuscript has neither been published nor is under consideration by another 
journal.

Our paper introduces a novel approach
which can widen the applications of the Kolmogorov--Smirnov (KS) test, a 
goodness-of-fit test which relies on the data
being serially dependent and the parameters for the hypothesized distribution
being specified.

This paper introduces a bias correction for the test based on the non-parametric 
block bootstrap that accounts for serial dependence and does not require
specification of parameters.
The main contribution is a new methodological development which is useful
for addressing a broad array of
practical problems in financial analysis, environmental science, as 
well as other situations that require goodness-of-fit tests on serially
dependent data. An application of our method to test the distribution
of S\&P 500 index stock returns is shown in the manuscript.

This article will prove to be a valuable expansion to statistical practice.
Please feel free to reach out to us if you need any other information concerning 
this manuscript.

\bigskip

Sincerely yours,

\vspace{50pt}

Mathew Chandy\\ \\On behalf of Elizabeth D. Schifano, Jun Yan, and 
Xianyang Zhang

\end{document}

### 2024-09-16 manuscript/manuscript.tex
author format

@@
 \documentclass[12pt]{article}
+\usepackage{authblk}
 \usepackage{amsmath}
@@
   \title{\bf Nonparametric Block Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test}
-  \author{Mathew Chandy\\
-    Department of Statistics, University of Connecticut\\
-    Department of Statistics and Data Science, University of California, Los Angeles,\\
-    Elizabeth D. Schifano\\
-    Department of Statistics, University of Connecticut,\\
-    Jun Yan\thanks{
-    The authors gratefully acknowledge the National Science Foundation (NSF).}\hspace{.2cm}\\
-    Department of Statistics, University of Connecticut,\\
-    and\\
-    Xianyang Zhang\\
-    Department of Statistics, Texas A\&M University}
+  \author[1,2]{Mathew Chandy}
+  \author[1]{Elizabeth D. Schifano}
+  \author[1]{Jun Yan\thanks{
+    The authors gratefully acknowledge the National Science Foundation (NSF).}\hspace{.2cm}}
+  \author[3]{Xianyang Zhang$^{\ast}$ }
+  \affil[1]{Department of Statistics, University of Connecticut}
+  \affil[2]{Department of Statistics and Data Science, University of California, Los Angeles}
+  \affil[3]{Department of Statistics, Texas A\&M University}
   \maketitle

### 2024-09-17 manuscript/cov.tex
cover letter for General section of TAS

--- 2024-09-02 manuscript/statistical_practice_cover_letter.tex
@@
-\documentclass{article}
+\documentclass[12pt]{article}
 \usepackage{charter}
@@
   \today \\[12pt] % Date
-  Department of Statistics,\\
-  University of Connecticut\\
-  Room 323, Philip E. Austin Building\\
-  215 Glenbrook Road, Unit 4120\\
-  Storrs, CT 06269-4120\\
-  \\
   Department of Statistics and Data Science,\\
@@
   8125 Math Sciences Bldg. Box 951554\\
-  Los Angeles, CA 90095-1554\\
-  \\
-  Department of Statistics,\\
-  Texas A\&M University\\
-  447 Blocker Building (BLOC)\\
-  3143 TAMU | 155 Ireland St\\
-  College Station, TX 77843-3143
+  Los Angeles, CA 90095-1554
 \end{tabular}
@@
 
-\bigskip
-
-We are pleased to submit the manuscript entitled ``Nonparametric Block Bootstrap 
-Kolmogorov-Smirnov Goodness-of-Fit Test" for 
-consideration in the Statistical Practice section of 
-\textit{American Statistician}. We certify that this 
-manuscript has neither been published nor is under consideration by another 
+We are pleased to submit our manuscript entitled 
+``Nonparametric Block Bootstrap Kolmogorov-Smirnov Goodness-of-Fit
+Test"  for consideration in the \emph{General} Section of the
+\textit{American Statistician}. We certify that this manuscript has
+neither been published nor is under consideration by any other
 journal.
 
-Our paper introduces a novel approach
-which can widen the applications of the Kolmogorov--Smirnov (KS) test, a 
-goodness-of-fit test which relies on the data
-being serially dependent and the parameters for the hypothesized distribution
-being specified.
+Our paper addresses a gap in the application of the Kolmogorov-Smirnov
+(KS) test for assessing the marginal goodness-of-fit of hypothesized
+distributions in the context of serially dependent stationary
+observations. While parametric block bootstrap procedures typically
+require specification of the serial dependence structure, a
+nonparametric block bootstrap procedure is advantageous as it avoids
+this requirement. The nonparametric block bootstrap version of the KS
+test extends the nonparametric approach studied by Basu and Rao
+(2004) to cases of serial dependence. However, such a version does not
+yet exist, and our paper fills this gap. The proposed test has wide
+applications in time series modeling, particularly in scenarios where
+marginal distributions are of interest, such as in financial time series.
 
-This paper introduces a bias correction for the test based on the non-parametric 
-block bootstrap that accounts for serial dependence and does not require
-specification of parameters.
-The main contribution is a new methodological development which is useful
-for addressing a broad array of
-practical problems in financial analysis, environmental science, as 
-well as other situations that require goodness-of-fit tests on serially
-dependent data. An application of our method to test the distribution
-of S\&P 500 index stock returns is shown in the manuscript.
+We believe that the methodological developments in this manuscript are
+of broad interest and are generally not highly technical, making it a
+suitable fit for the \emph{General} Section of your journal.
 
-This article will prove to be a valuable expansion to statistical practice.
-Please feel free to reach out to us if you need any other information concerning 
-this manuscript.
+Thank you for your consideration, and we look forward to your feedback.
 
@@
 
-\vspace{50pt}
+\vspace{2cm}
 

### 2024-09-17 manuscript/cov.tex
switch sentence order

@@
 nonparametric block bootstrap procedure is advantageous as it avoids
-this requirement. The nonparametric block bootstrap version of the KS
-test extends the nonparametric approach studied by Basu and Rao
-(2004) to cases of serial dependence. However, such a version does not
-yet exist, and our paper fills this gap. The proposed test has wide
+this requirement. However, such a nonparametric block bootstrap procedure does 
+not yet exist, and our paper fills this gap. The proposed nonparametric block 
+bootstrap version of the KS test extends the nonparametric approach studied by 
+Basu and Rao (2004) to cases of serial dependence.  The proposed test has wide
 applications in time series modeling, particularly in scenarios where

### 2024-09-18 manuscript/anon.tex
anonymous article

--- 2024-09-16 manuscript/manuscript.tex
@@
   \title{\bf Nonparametric Block Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test}
-  \author[1,2]{Mathew Chandy}
-  \author[1]{Elizabeth D. Schifano}
-  \author[1]{Jun Yan\thanks{
-    The authors gratefully acknowledge the National Science Foundation (NSF).}\hspace{.2cm}}
-  \author[3]{Xianyang Zhang$^{\ast}$ }
-  \affil[1]{Department of Statistics, University of Connecticut}
-  \affil[2]{Department of Statistics and Data Science, University of California, Los Angeles}
-  \affil[3]{Department of Statistics, Texas A\&M University}
+  \author{}
   \maketitle
@@
 
-\item[Funding statement:]JY and XZ's research was partially supported by NSF grant
-DMS2210735.
-
 \item[Conflict of interest disclosure:]The authors declare no potential conflict 
 of interests.
-
-\item[Data availability statement:] The data and code used in the real data analysis and simulation
-studies are publicly available in a GitHub repo:
-\url{https://github.com/mathewchandy03/Bootstrap_KS_Test}.
 

### 2024-09-18 manuscript/cov.tex
added challenge to cov letter
Basu to Babu

@@
 bootstrap version of the KS test extends the nonparametric approach studied by 
-Basu and Rao (2004) to cases of serial dependence.  The proposed test has wide
+Babu and Rao (2004) to cases of serial dependence. The challenge lides
+in approximating the bias term, which has a closed-form in the
+independent data case studied by Babu and Rao (2004), using the
+bootstrap samples. The proposed test has wide
 applications in time series modeling, particularly in scenarios where

### 2024-09-18 manuscript/anon.tex
pdf minor version = 4
fixed image overlap

@@
 
-%\pdfminorversion=4
+\pdfminorversion=4
 % NOTE: To produce blinded version, replace "0" with "1" below.
@@
 \begin{figure}[tbp]
+  \includegraphics[width = .9\textwidth]{figures/normal}
   \centering
-  \includegraphics[width = .9\textwidth]{figures/normal}
+  \caption{Q-Q plots of the p-values testing that a time series
+    have marginal normal distribution with true data generating distribution
+    being $N(8,8)$.}
+    \hspace{5cm}
   \includegraphics[width = .9\textwidth]{figures/gamma}
   \caption{Q-Q plots of the p-values testing that a time series
-    have marginal normal distribution with true data generating distribution
-    being $N(8,8)$ (upper) and marginal gamma distribution with true data
-    generating distribution $\Gamma(8,1)$ (lower).}
+    have marginal gamma distribution with true data
+    generating distribution $\Gamma(8,1)$.}
   \label{fig:qq}

### 2024-12-30 manuscript/reply.tex
set up reply unfininished

\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{natbib}
\usepackage{hyperref}

\usepackage{listings}
\usepackage{rotating, graphicx}
\graphicspath{{./}, {./image/}}
\usepackage{booktabs, natbib}
% \usepackage{breakurl}
% \usepackage [english]{babel}
\usepackage{amsmath, amsbsy, amsthm, epsfig, epsf, psfrag, graphicx, 
amssymb, enumerate}
\usepackage{bm}
\usepackage{multirow, multicol}

\usepackage[dvipsnames]{color}
\definecolor{darkblue}{rgb}{0.1, 0.2, 0.6}

\newcommand{\jy}[1]{\textcolor{red}{JY: #1}}
\newcommand{\eds}[1]{\textcolor{blue}{(EDS: #1)}}
\newcommand{\mc}[1]{\textcolor{green}{(MC: #1)}}
\newcommand{\xz}[1]{\textcolor{cyan}{(XZ: #1)}}

\sloppy

% \usepackage{csquotes}
% \usepackage [autostyle, english = american]{csquotes}
% \MakeOuterQuote{"}

% \usepackage{bibentry}
\newenvironment{comment}%
{\begin{quotation}\noindent\small\it\color{darkblue}\ignorespaces%
}{\end{quotation}}

\begin{document}

\begin{center}
  {\Large\bf Response to the Comments}
\end{center}

We extend our gratitude to the editor and the Associate Editor for
granting us the opportunity to revise this manuscript. We also want to
express our appreciation to the two referees for their valuable and
constructive comments. The reviewers have highlighted crucial
discussion areas that have not only enhanced the quality of this paper
but have also set a clear direction for our future research
endeavors.

The manuscript has been
revised accordingly with the following notable changes:
\begin{enumerate}
\item 
\item 
\item 
\item 
\end{enumerate}

Point-by-point responses to the comments are as follows, with the
comments quoted in \emph{\color{darkblue} italic and blue}.

\subsection*{To Referee 1}

\begin{comment}
1. The main contribution is presented as an extension of the bias-corrected 
nonparametric
bootstrap (NPB) KS test, which was already established by Babu and Rao (2004) 
for independent data, to serially dependent time series. However, the 
methodological advancements
here are minimal; the approach essentially adapts existing block bootstrap 
methods and applies them without significant theoretical innovation or novel 
insights into the performance
of the KS statistic under these conditions. Notably, the numerical results 
suggest that the
proposed method struggles to control the size, which most likely stems from the 
uniform
choice of block size across different dependence structures. Intuitively, the 
block size should
vary with the level of dependence in the data; however, the manuscript lacks 
consideration
for this crucial aspect. I highly suggest the authors to include some 
discussions on this, see
some existing literature below.

\citep{hall1995blocking}

\citep{lahiri1999theoretical}

\citep{buhlmann2002bootstraps}

\citep{politis2004automatic}

\citep{lahiri2013resampling}

\end{comment}

Thank you for your suggestion. The primary methodological 
advancement in this study is a new bias correction - which is different than 
that introduced by \citet{babu2004goodness} - for cases where the data are
serially dependent...

\begin{comment}
2. I understand that the paper’s intended scope may not require high 
technicality. However,
since the core methodology is based on bootstrap techniques, a more detailed 
heuristic
explanation of the procedure is essential, especially regarding the bias 
correction term.
\end{comment}

Thank you for your comment...

\begin{comment}
3. For time series data, there are many variants of bootstrap, such as circular 
block bootstrap,
stationary bootstrap, dependent wild bootstrap. I wonder how other methods 
perform in
your setting.
\end{comment}

This is an interesting direction to investigate...

\subsection*{To Referee 2}

\begin{comment}
1. In Section 3.1, it seems that Kendall's tau is being used as a measure
dependence between $X_t$ and $X_{t+1}$. It may be useful to make that explicit 
in the
second pararaph of Section 3.1.
\end{comment}

Thank you for pointing this out, we have added that the
serial dependence is specifically between $X_i$ and $X_{i+1}$.

\begin{comment}
2. The work presented here is useful, however I have believe the explanations
for the correction term may need modification. Here the entire justification is
based on the null case which does not cover the case when the null is not true.
Justification for the correction term in Babu and Rao is not based on just the
null case. The same seems to be true here, and in that case, Section 2 needs
rewriting.
\end{comment}

Thank you for drawing this to our attention...

\bibliographystyle{chicago}
\bibliography{citations}

\end{document}

### 2024-12-31 manuscript/manuscript.tex
set up blind version creation
set up reply unfininished
comments in discussion

@@
 
+\title{\bf Nonparametric Block Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test}
 \if0\blind
 {
-  \title{\bf Nonparametric Block Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test}
   \author[1,2]{Mathew Chandy}
@@
   \bigskip
-  \begin{center}
-    {\LARGE\bf Title}
-\end{center}
-  \medskip
+  \author{Anonymous Author}
 } \fi
+
+\maketitle
 
@@
 
+\citet{babu2004goodness} proves that $T^{(b)}_n$ and $T_n$ have the same 
+limiting distribution for almost all samples $X_1, \ldots, X_n$.
 The p-value of the basic bootstrap KS test can be approximated
@@
 Block-bootstrap can be done with overlapping or moving blocks.
-Define moving blocks (assuming $l > 1$) as:
+Define moving blocks (assuming block size $l > 1$) as:
 \begin{equation*}
@@
 $l = \lceil n^{1/3} \rceil$ \citep{buhlmann1999block},  
-which was adopted in this study.
+which was adopted in this study. \citet{hall1995blocking} and 
+\citet{politis2004automatic} note that
+the selection of block size should ideally take into account the strength
+and direction of serial dependence. However,
+because this method is intended for cases where the dependence structure is 
+unknown, the block size choice will not vary with the level of dependence.
 Now we draw $k$ blocks from the $(n - l + 1)$ blocks 
@@
 sample size $n \in \{100, 200, 400, 800\}$. Kendall's $\tau$ was chosen as a
-measure of serial dependence as it is invariant to monotone marginal
+measure of serial dependence between $X_i$ and 
+$X_{i+1}$ as it is invariant to monotone marginal
 transformations. 
@@
 Several promising directions for further research emerge from the findings of
-this study. Firstly, analogous methodologies for other goodness-of-fit tests
+this study. Firstly, there are many other variants of bootstrap besides
+moving block bootstrap which
+can be used for serially dependent data such as the circular block boostrap \citep{romano1992circular}, the 
+stationary bootstrap \citep{politis1994stationary}, and the dependent wild 
+bootstrap \citep{shao2010dependent}. It would be interesting to investigate how
+these methods perform using our correction. Secondly, analogous 
+methodologies for other goodness-of-fit tests
 based on empirical distributions, such as the Anderson--Darling and Cramér--von
@@
 environmental studies, such as extreme value modeling, where observations are
-often serially dependent. Secondly, an extension of the proposed NPBB
+often serially dependent. Thirdly, an extension of the proposed NPBB
 one-sample KS test to a two-sample setting would be

### 2024-12-31 manuscript/reply.tex
comments in discussion

@@
 nonparametric
-bootstrap (NPB) KS test, which was already established by Babu and Rao (2004) 
+bootstrap (NPB) KS test, which was already established by 
+\citet{babu2004goodness}
 for independent data, to serially dependent time series. However, the 
@@
 
-Thank you for your suggestion. The primary methodological 
+Thank you for your comment and the suggested literature. The primary 
+methodological 
 advancement in this study is a new bias correction - which is different than 
-that introduced by \citet{babu2004goodness} - for cases where the data are
-serially dependent...
+that introduced by \citet{babu2004goodness} - for cases where the dependence
+structure of the data is not known. Therefore, in practical application,
+the level of dependence may not be available to inform our choice of block
+size. We have added a discussion of this limitation in the first paragraph of 
+the NPBB for stationary
+series subsection.
 
@@
 
-This is an interesting direction to investigate...
+Thank you. This is an interesting direction to investigate. We have added few
+sentences concerning potential future investigation into evaluating a bias 
+correction for these variants in the second paragraph of the Discussion 
+section.
 
@@
 in the
-second pararaph of Section 3.1.
+second pararaph of the Size subsection.
 \end{comment}
 
-Thank you for pointing this out, we have added that the
+Thank you for pointing this out. In the second paragraph of Section 3.1, 
+we have added that the
 serial dependence is specifically between $X_i$ and $X_{i+1}$.
@@
 based on the null case which does not cover the case when the null is not true.
-Justification for the correction term in Babu and Rao is not based on just the
+Justification for the correction term in \citet{babu2004goodness} is not based 
+on just the
 null case. The same seems to be true here, and in that case, Section 2 needs

### 2025-02-18 manuscript/manuscript.tex
politis2004blksize

@@
 $b \in \{1, \ldots, B\}$.  
-Block-bootstrap can be done with overlapping or moving blocks.
-Define moving blocks (assuming block size $l > 1$) as:
+Circular block-bootstrap can be done with overlapping blocks that can
+wrap around the end of the series \citet{romano1992circular}.
+Define blocks (assuming block size $l > 1$) as:
 \begin{equation*}
@@
 \item
-  Generate $X^{(b)}_1,...,X^{(b)}_n$ by applying moving block bootstrap 
+  Generate $X^{(b)}_1,...,X^{(b)}_n$ by applying circular block bootstrap 
   on the original sample as
@@
 this study. Firstly, there are many other variants of bootstrap besides
-moving block bootstrap which
-can be used for serially dependent data such as the circular block boostrap \citep{romano1992circular}, the 
-stationary bootstrap \citep{politis1994stationary}, and the dependent wild 
+circular block bootstrap which
+can be used for serially dependent data such as the
+stationary bootstrap \citep{politis1994stationary} and the dependent wild 
 bootstrap \citep{shao2010dependent}. It would be interesting to investigate how

### 2025-02-18 manuscript/reply.tex
politis2004blksize

@@
 
-Thank you. This is an interesting direction to investigate. We have added few
+Thank you. This is an interesting direction to investigate. We have added a few
 sentences concerning potential future investigation into evaluating a bias 

### 2025-02-18 code/functions.R

@@ -382,3 +382,71 @@ app_scheme <- function(start, end, years, stock) {
   return(pval)
 }
 
+
+R <- function(x, k) {
+  N <- length(x)
+  a <- x[-(1:abs(k))]
+  b <- x[-((N - abs(k) + 1):N)]
+  sum = 0
+  for (i in 1:length(a)) {
+    sum = sum + (a[i] - mean(x)) * (b[i] - mean(x))
+  }
+  return(sum / N)
+}
+
+rho <- function(x, k) {
+  R(x, k) / R(x, 0)
+}
+
+politis_test <- function(x, C = 2, K = NULL) {
+  N <- length(x)
+  if (is.null(K)) {
+    K = max(c(5, sqrt(log10(N))))
+  } 
+  
+  condition = TRUE
+  m = 1
+  while (condition == TRUE) {
+    condition = FALSE
+    for (k in 1:K) {
+      if (abs(rho(x, m + k)) >= C * sqrt(log(N) / N)) {
+        condition = TRUE
+        break
+      }
+    }
+    m = m + 1
+  }
+  return(m)
+}
+
+lambda <- function(t) {
+  if (abs(t) >= 0 & abs(t) <= 1/2) {
+    return(1)
+  } else if (abs(t) >= 1/2 & abs(t) <= 1) {
+    return(2 * (1 - abs(t)))
+  } else return(0)
+}
+
+g <- function(x, w, M) {
+  sum = 0
+  for (k in (-M):M) {
+    sum = sum + lambda(k / M) * R(x, k) * cos(w * k)
+  }
+  return(sum)
+}
+
+G <- function(x, M) {
+  sum = 0
+  for (k in (-M):M) {
+    sum = sum + lambda(k / M) * abs(k) * R(x, k)
+  }
+  return(sum)
+}
+politis2004blksize <- function(x) {
+  N <- length(x)
+  m <- politis_test(x)
+  M <- 2*m
+  D <- 4 / 3 * g(x, 0, M) ^ 2
+  G <- G(x, M)
+  return( (2 * G ^ 2 / D) ^ (1 / 3) * N ^ (1 / 3) )
+}

### 2025-05-22 manuscript/manuscript.tex
blk2004 results

@@
 function for block size that is considered optimal is
-$l = \lceil n^{1/3} \rceil$ \citep{buhlmann1999block},  
-which was adopted in this study. \citet{hall1995blocking} and 
+$l = \lceil n^{1/3} \rceil$ \citep{buhlmann1999block}... \citet{hall1995blocking}
+and
 \citet{politis2004automatic} note that
 the selection of block size should ideally take into account the strength
-and direction of serial dependence. However,
-because this method is intended for cases where the dependence structure is 
-unknown, the block size choice will not vary with the level of dependence.
+and direction of serial dependence. The plug-in approach for circular
+bootstrap introduced in \citet{politis2004automatic}...
 Now we draw $k$ blocks from the $(n - l + 1)$ blocks
@@
 
+\section{Appendix}\label{sec:appendix}
+In our original setting, we used a block size of $l = \lceil n^{1/3} \rceil$.
+However, the optimal block size may vary according to the dependence structure.
+To address this, we considered  using the automatic block-length selection
+scheme
+for
+circular block boostrap as described in Section 3.3 of
+\citet{politis2004automatic}. Unfortunately, using this setting results in
+the selection of
+block
+sizes that can be quite large (sometimes as large or larger than $n$), leading
+to less variation between the bootstrapped
+samples. Figures~\ref{fig:large_block_normal} and \ref{fig:large_block_gamma}
+demonstrate that for highly temporally
+dependent samples (especially when the autocorrelation is negative),
+the block size is frequently larger than $\sqrt{n}$.
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[scale=1]{figures/large_block_normal}
+  \caption{Proportion of selected block sizes using
+  \citet{politis2004automatic}'s procedure that are larger than the sample size
+    $n$ for $n \in \{100, 200, 400, 800\}$,
+    $\tau \in \{-0.75, -0.5, -0.25, 0, 0.25, 0.5, 0.75\}$, and true marginal distribution
+    $N(8,8)$.
+  }
+  \label{fig:large_block_normal}
+\end{figure}
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[scale=1]{figures/large_block_gamma}
+  \caption{Proportion of selected block sizes using
+  \citet{politis2004automatic}'s procedure that are larger than the sample size
+    $n$ for $n \in \{100, 200, 400, 800\}$,
+    $\tau \in \{-0.75, -0.5, -0.25, 0, 0.25, 0.5, 0.75\}$, and true marginal distribution
+    $\Gamma(8,1)$.
+  }
+  \label{fig:large_block_gamma}
+\end{figure}
+
 \bigskip

### 2025-05-22 manuscript/reply.tex
blk2004 results

@@
 \begin{enumerate}
-\item 
-\item 
-\item 
-\item 
+\item An appendix outlining trial and issues with automatic block size selection
+for circular block bootstrap.
+\item Stronger justification of the bias term
+
 \end{enumerate}
@@
 
-Thank you for your comment and the suggested literature. The primary 
-methodological 
-advancement in this study is a new bias correction - which is different than 
-that introduced by \citet{babu2004goodness} - for cases where the dependence
-structure of the data is not known. Therefore, in practical application,
-the level of dependence may not be available to inform our choice of block
-size. We have added a discussion of this limitation in the first paragraph of 
-the NPBB for stationary
-series subsection.
+Thank you for your comment and the suggested literature. We 
+tried selecting block sizes using the plug-in approach 
+from \citet{politis2004automatic}, which is outlined in the Appendix. 
+Unfortunately, the procedure can result
+in quite large block sizes that would result in the failure of the block
+bootstrap step.
 
@@
 
-Thank you. This is an interesting direction to investigate. We have added a few
+Thank you. Our investigation actually used circular block bootstrap which
+is a variant of moving block bootstrap, and we have appropriately changed
+the terminology. Performance of other variants of 
+bootstrap in our setting is an interesting direction to explore. We have added a 
+few
 sentences concerning potential future investigation into evaluating a bias 

### 2025-05-22 code/functions.R

@@ -4,7 +4,9 @@ library(truncdist)
 library(qqplotr)
 library(copula)
 library(tseries)
+library(latex2exp)
 source("ksfitted.R")
+
 
 mystat <- function(x, dist, df = NULL) {
   # Bootstrap will return actual pseudo-sample, mean, and standard deviation

### 2025-05-22 code/hpc_functions.R

@@ -224,7 +224,7 @@ subsampling_interval <- function(b, x, B) {
 
 politis1999subsampling <- function(x, B = 100) {
   b_small <- 1
-  b_big <- length(x)
+  b_big <- sqrt(length(x))
   bs <- seq(b_small, b_big, 3)
   intervals <- lapply(bs, subsampling_interval, x, B)
   intervals <- t(do.call(rbind, intervals))

### 2025-05-22 code/test_functions.R

@@ -1,0 +1,320 @@
+library(tidyverse)
+library(truncdist)
+library(doRNG)
+library(foreach)
+library(doSNOW)
+doFuture::registerDoFuture()
+future::plan("multisession", workers=20)
+doRNG::registerDoRNG(123)
+# cl <- makeCluster(20)
+# registerDoSNOW(cl)
+# pb <- txtProgressBar(max = 40, style = 3)
+# progress <- function(n) setTxtProgressBar(pb, n)
+# opts <- list(progress = progress)
+mystat <- function(x, dist, type = 1) {
+  if (type == 1) {
+    vec <- x
+  } else if (type == 2) {
+    vec <- c()
+  }
+  # Bootstrap will return actual pseudo-sample, mean, and standard deviation
+  if (dist == 'normal') {
+    n <- length(x)
+    sd0 <- sqrt((n - 1) / n) * sd(x)
+    mx <- mean(x)
+    c(c(vec), c(mx, sd0))
+  } else if (dist == 'gamma') {
+    mx <- mean(x)
+    a <- 0.5 / (log(mx) - mean(log(x)))
+    a <- 1 / (1/a + (mean(log(x)) - log(mx) + log(a) - digamma(a)) /
+                (a - a^2 * trigamma(a)))
+    rate <- a / mx
+    
+    c(c(vec), c(a, rate))
+  } else {
+    c(c(vec), MASS::fitdistr(x, dist)$estimate)
+  }
+}
+
+
+
+bs_ks <- function(y, B, h0_dist, f0, blk, method, rgen = NULL) {
+  n <- length(y)
+  emp <- ecdf(y)(sort(y)) # observed empirical distribution
+  fit_theta <- mystat(y, h0_dist, type = 2) # observed fitted values
+  fit <- do.call(f0, c(list(sort(y)), as.list(fit_theta))) # observed fitted distribution
+  obsv_ks <- sqrt(n) * max(abs(emp - fit)) # observed ks statistic
+  # print(blk)
+  if (method == "npbb") {
+    bts <- cbb(y, mystat, l = blk, R = B, dist = h0_dist)
+  } else if (method == "npb") {
+    bts <- boot::tsboot(y, mystat, l = 1, sim = "fixed", R = B, 
+                        dist = h0_dist)$t
+  } else if (method == "pb") {
+    bts <- t(replicate(B, c(
+      do.call(rgen, c(n, as.list(c(fit_theta)))))))
+    theta <- c()
+    for(row in 1:nrow(bts)) {
[…]

### 2025-05-23 manuscript/manuscript.tex
bias term justification also changed notation for NPBB bias correction kappa instead of C to avoid confusion

@@
     T^{(b)}_n = \sup_x \Big\vert \sqrt{n}\left(F^{(b)}_n(x)
-    - F(x; \hat\theta^{(b)}_n)\right) - C_n(x) \Big\vert.
+    - F(x; \hat\theta^{(b)}_n)\right) - \kappa_n(x) \Big\vert.
   \]
   where
-  $C_{n}(x) = \sqrt{n}(\mathbb{E}^{*}[F^{(b)}_n(x)] -
+  $\kappa_{n}(x) = \sqrt{n}(\mathbb{E}^{*}[F^{(b)}_n(x)] -
   F(x; \theta_0^*))$ is the bias term, and
@@
 \]
+
+When parameters of a hypothesized distribution $F(x;\theta)$ are estimated from 
+the data (yielding $\hat\theta_n$), the null distribution of the KS statistic 
+$T_n = \sup_x |\sqrt{n}(F_n(x) - F(x;\hat\theta_n))|$ is altered from its 
+standard form. The NPBB procedure aims to replicate this complex null 
+distribution.
+
+In the ``bootstrap world,'' each resample yields an empirical distribution 
+$F_n^{(b)}$ and a parameter estimate $\hat\theta^{(b)}_n$. The term 
+$\sqrt{n}(F_n^{(b)}(x) - F(x;\hat\theta^{(b)}_n))$ is the bootstrap analog of 
+the KS process. However, this bootstrap process inherently possesses its own 
+mean or systematic deviation. The bias correction $\kappa_n(x)$ estimates this mean. 
+Specifically, $E^*[F_n^{(b)}(x)]$ is the average empirical CDF over all 
+bootstrap samples, and $\theta^*_0 = E^*[\hat\theta^{(b)}_n]$ is the average of 
+the parameter estimates from these bootstrap samples. Thus, $\kappa_n(x)$ 
+quantifies 
+the expected difference, in the bootstrap world, between the empirical CDF and 
+the hypothesized CDF (evaluated at the average bootstrap parameter estimate). 
+Subtracting $\kappa_n(x)$ from 
+$\sqrt{n}(F_n^{(b)}(x) - F(x;\hat\theta^{(b)}_n))$ centers 
+the 
+bootstrap KS process. This ensures that the variability of the resulting 
+bootstrap statistics $T_n^{(b)}$ more faithfully reflects the variability of 
+the original $T_n$ statistic around its true but complex null distribution. 
+This approach extends the logic of \citet{babu2004goodness}, who introduced a 
+similar correction for independent data to the context of serially dependent 
+time series via block bootstrapping.
 

### 2025-05-24 manuscript/manuscript.tex
put heuristics into a subsection with further edits

--- 2025-05-22 manuscript/manuscript.tex
@@
 \usepackage{comment}
+\RequirePackage[colorlinks,citecolor=blue,urlcolor=blue]{hyperref}
+
+\allowdisplaybreaks
+
+\usepackage[pagewise]{lineno}
+\linenumbers*[1]
+% patches to make lineno work better with amsmath
+\newcommand*\patchAmsMathEnvironmentForLineno[1]{%
+        \expandafter\let\csname old#1\expandafter\endcsname\csname 
+        #1\endcsname
+        \expandafter\let\csname oldend#1\expandafter\endcsname\csname 
+        end#1\endcsname
+        \renewenvironment{#1}%
+        {\linenomath\csname old#1\endcsname}%
+        {\csname oldend#1\endcsname\endlinenomath}}%
+\newcommand*\patchBothAmsMathEnvironmentsForLineno[1]{%
+        \patchAmsMathEnvironmentForLineno{#1}%
+        \patchAmsMathEnvironmentForLineno{#1*}}%
+\AtBeginDocument{%
+        \patchBothAmsMathEnvironmentsForLineno{equation}%
+        \patchBothAmsMathEnvironmentsForLineno{align}%
+        \patchBothAmsMathEnvironmentsForLineno{flalign}%
+        \patchBothAmsMathEnvironmentsForLineno{alignat}%
+        \patchBothAmsMathEnvironmentsForLineno{gather}%
+        \patchBothAmsMathEnvironmentsForLineno{multline}%
+}
 
@@
   where
-  $C_{n}(x) = \sqrt{n}(F_n(x) - F(x; \hat\theta_n))$ is the estimated
-  bias term.
+  \[
+    C_{n}(x) = \sqrt{n}(F_n(x) - F(x; \hat\theta_n))
+  \]
+  is the estimated bias term.
 \end{enumerate}
@@
     T^{(b)}_n = \sup_x \Big\vert \sqrt{n}\left(F^{(b)}_n(x)
-    - F(x; \hat\theta^{(b)}_n)\right) - C_n(x) \Big\vert.
+    - F(x; \hat\theta^{(b)}_n)\right) - K_n(x) \Big\vert.
   \]
   where
-  $C_{n}(x) = \sqrt{n}(\mathbb{E}^{*}[F^{(b)}_n(x)] -
-  F(x; \theta_0^*))$ is the bias term, and
+  \[
+    K_{n}(x) = \sqrt{n}(\mathbb{E}^{*}[F^{(b)}_n(x)] -
+    F(x; \theta_0^*))
+  \]
+  is the bias term, and
   the expected values $\mathbb{E}^{*}[F^{(b)}_n(x)]$ and
@@
 \]
+
+\subsection{Heuristic justification for the bias correction term in NPBB}
+
+A clear understanding of the bias correction term $K_n(x)$ is 
+essential for appreciating how the NPBB procedure effectively replicates 
+the null distribution of the KS statistic in the presence of serial 
+dependence and estimated parameters. When the parameters~$\theta$ of a
+hypothesized distribution $F(x;\theta)$ are estimated from
+the data with $\hat\theta_n$, the null distribution of the KS statistic 
+$T_n = \sup_x |\sqrt{n}(F_n(x) - F(x;\hat\theta_n))|$ is altered from its 
+standard form. The NPBB procedure aims to replicate this complex null 
+distribution.
+
+In the ``bootstrap world,'' each resample yields an empirical distribution 
+$F_n^{(b)}$ and a parameter estimate $\hat\theta^{(b)}_n$. The term 
+$\sqrt{n}(F_n^{(b)}(x) - F(x;\hat\theta^{(b)}_n))$ is the bootstrap analog of 
+the KS process. However, this bootstrap process inherently possesses its own 
+mean or systematic deviation. The bias correction $K_n(x)$
+estimates this mean.
+Specifically, $\mathbb{E}^*[F_n^{(b)}(x)]$ is the average empirical
+GXSdistribution function over all bootstrap samples, and
+$\theta^*_0 = \mathbb{E}^*[\hat\theta^{(b)}_n]$ is the average of 
+the parameter estimates from these bootstrap samples. Thus,
+$K_n(x)$ quantifies 
+the expected difference, in the bootstrap world, between the empirical
+distribution function and the hypothesized distribution function
+(evaluated at the average bootstrap parameter estimate).
+Subtracting $K_n(x)$ from
+$\sqrt{n}(F_n^{(b)}(x) - F(x;\hat\theta^{(b)}_n))$ centers the 
+bootstrap KS process. This ensures that the variability of the resulting 
+bootstrap statistics $T_n^{(b)}$ more faithfully reflects the variability of 
+the original $T_n$ statistic around its true but complex null
+distribution.
+
+This approach extends the logic of \citet{babu2004goodness}, who
+introduced a similar correction for independent data, to the context
+of serially dependent time series via block bootstrapping.
+The bias correction term $C_n(x)$ used in the NPB method for
+independent data could, in principle, also be approximated by a
+bootstrap expectation in the same way as $K_n(x)$.
+Nonetheless, under independence, the empirical distribution $F_n(x)$
+and the parameter estimate $\hat{\theta}_n$ are already reliable, so
+direct calculation of $C_n(x)$ is both simpler and sufficient. The use
+of bootstrap expectations as in $K_n(x)$ becomes necessary only when
+serial dependence distorts the properties of $F_n(x)$, making
+block-bootstrapping-based bias estimation essential.
 
@@
 for
-circular block boostrap as described in Section 3.3 of
+circular block bootstrap as described in Section 3.3 of
 \citet{politis2004automatic}. Unfortunately, using this setting results in
@@
 
-\bibliographystyle{agsm}
-
+\bibliographystyle{asa}
 \bibliography{citations}

### 2025-05-24 manuscript/manuscript.tex
tidied table
went over 2nd paragraph in conclusion

@@
 \RequirePackage[colorlinks,citecolor=blue,urlcolor=blue]{hyperref}
+\usepackage{setspace}
 
@@
 \newpage
-\spacingset{1.45} % DON'T change the spacing!
+
+\doublespacing
+
 \section{Introduction}\label{sec:intro}
@@
 \label{table:size}
-\begin{tabular}{lllrrrrrrr}
+\begin{tabular}{ccc ccc c ccc}
   \toprule
-$F(\cdot; \theta)$ & $n$ & $\alpha$ & $\tau = -0.75$ & $\tau = -0.5$ & $\tau = -0.25$
-& $\tau = 0$ & $\tau = 0.25$ & $\tau = 0.5$ & $\tau = 0.75$ \\
+$F(\cdot; \theta)$ & $n$ & $\alpha$ & \multicolumn{7}{c}{Kendall's $\tau$}\\
+\cmidrule(lr){4-10}
+   &  &  & $-0.75$ & $ -0.50$ & $-0.25$ & $0.00$ & $0.25$ & $0.50$ & $ 0.75$ \\
   \midrule
@@
 Overall, the test provides an analog of the bias-corrected NPB KS test of
-\citet{babu2004goodness} in the context of stationaly time
+\citet{babu2004goodness} in the context of stationary time
 series with unspecified serial dependence. Compared to the SPB method
@@
 
-Several promising directions for further research emerge from the findings of
-this study. Firstly, there are many other variants of bootstrap besides
-circular block bootstrap which
-can be used for serially dependent data such as the
+Several promising directions for further research emerge from
+this study. Firstly, while we used circular block bootstrap, many
+other bootstrap variants for serially dependent data, such as the
 stationary bootstrap \citep{politis1994stationary} and the dependent wild
-bootstrap \citep{shao2010dependent}. It would be interesting to investigate how
-these methods perform using our correction. Secondly, analogous
-methodologies for other goodness-of-fit tests
-based on empirical distributions, such as the Anderson--Darling and Cramér--von
-Mises tests---which have been shown to outperform the KS test in certain scenarios
-\citep{stephens2017tests}---could be explored. The application of block
-bootstrapping bias correction to these tests could be particularly beneficial in
-environmental studies, such as extreme value modeling, where observations are
-often serially dependent. Thirdly, an extension of the proposed NPBB
-one-sample KS test to a two-sample setting would be
-intriguing. This adaptation would test whether two samples originate from the
-same distribution without requiring specification of serial dependencies in
-either sample, maintaining the advantageous feature of the original method.
-Finally, a rigorous theoretical justification of the NPBB method for
-stationary series is of significant academic interest. Establishing
-precise conditions for the asymptotic behavior of the KS statistic and
-the consistency of the bootstrap procedure would offer valuable
-practical insights into the scenarios where the NPBB approach is
-expected to perform optimally.
+bootstrap \citep{shao2010dependent}, could be evaluated under our
+correction framework. Secondly, analogous methodologies could be
+developed for other goodness-of-fit tests based on empirical
+distributions, including the Anderson---Darling and Cramér--von
+Mises tests, which are known to outperform the KS test in certain scenarios
+\citep{stephens2017tests}. Applying block bootstrap bias correction to
+these tests may be particularly beneficial in contexts like extreme
+value modeling, where serial dependence is common. Third, it would be
+intriguing to extend the proposed NPBB
+one-sample KS test to a two-sample setting, allowing for comparison of
+marginal distributions without specifying serial dependencies in
+either sample. Finally, a rigorous theoretical justification of the
+NPBB procedure, including precise conditions for the asymptotic
+behavior of the test statistic and the consistency of the bootstrap
+approximation, would offer valuable practical insights into the
+scenarios where the NPBB approach is expected to perform optimally.
 

### 2025-05-24 manuscript/reply.tex
went over replies

--- 2024-12-31 manuscript/reply.tex
@@
 
-We extend our gratitude to the editor and the Associate Editor for
-granting us the opportunity to revise this manuscript. We also want to
-express our appreciation to the two referees for their valuable and
-constructive comments. The reviewers have highlighted crucial
-discussion areas that have not only enhanced the quality of this paper
-but have also set a clear direction for our future research
-endeavors.
+We thank the Editor and Associate Editor for the encouraging decision
+and the opportunity to revise our manuscript. We are also grateful to
+the two referees for their thoughtful and constructive comments. Their
+suggestions have clarified important aspects of our work and have
+helped sharpen the presentation. We appreciate the confidence shown in
+our manuscript and have taken the revision process seriously in order
+to meet the expectations for final acceptance.
 
-The manuscript has been
-revised accordingly with the following notable changes:
+The revised manuscript incorporates the following notable changes:
 \begin{enumerate}
-\item 
-\item 
-\item 
-\item 
+\item An appendix has been added documenting our exploration of
+  automatic block size selection for circular block bootstrap,
+  including observed limitations in practice.
+\item  A paragraph has been added to the Discussion section to
+  discuss the impact of block size on test performance and to
+  contextualize our findings in light of existing literature on
+  optimal block length
+\item A stronger and more detailed justification of the bias
+  correction term is now provided in a newly added Section~2.4.
 \end{enumerate}
@@
 comments quoted in \emph{\color{darkblue} italic and blue}.
+
+\jy{Make sure you've included all the comments from the reviewers,
+  including their openning summaries.}
+
+\subsection*{To AE}
+
+\begin{comment}
+
+Two reviewers have carefully read the paper and have provided detailed feedback.
+Both reviewers would like to see some additional discussion and justifications for the bias correction term, where one could closely follow the Babu and Rao (2004) paper, and one reviewer mentioned the importance of considering different block sizes (I recommend possibly trying some data-based block size selection method and checking how it performs).
+A successful revision will require that the authors give serious consideration to these points.
+
+I also noticed that on Page 3 it says “Employing a nonparametric method would necessitate defining a specific model for this dependence”, but I think here “nonparametric” should be “parametric”.
+\end{comment}
 
@@
 
-\citep{hall1995blocking}
+\citet{hall1995blocking}
 
-\citep{lahiri1999theoretical}
+\citet{lahiri1999theoretical}
 
-\citep{buhlmann2002bootstraps}
+\citet{buhlmann2002bootstraps}
 
-\citep{politis2004automatic}
+\citet{politis2004automatic}
 
-\citep{lahiri2013resampling}
+\citet{lahiri2013resampling}
 
@@
 
-Thank you for your comment and the suggested literature. The primary 
-methodological 
-advancement in this study is a new bias correction - which is different than 
-that introduced by \citet{babu2004goodness} - for cases where the dependence
-structure of the data is not known. Therefore, in practical application,
-the level of dependence may not be available to inform our choice of block
-size. We have added a discussion of this limitation in the first paragraph of 
-the NPBB for stationary
-series subsection.
+We thank the reviewer for this thoughtful and constructive comment. 
+We agree that block size selection is a critical component in the 
+performance of block bootstrap procedures, particularly under varying 
+levels of serial dependence. In response to this suggestion, we have 
+made the following revisions:
+
+\begin{itemize}
+\item We have added a discussion to the conclusion section (Section~5) 
+that explicitly addresses the role of block size and its effect on the 
+performance of the NPBB test. This includes a review of relevant literature, 
+as suggested by the reviewer, including works by 
+\citet{hall1995blocking}, \citet{lahiri1999theoretical}, 
+\citet{buhlmann2002bootstraps}, \citet{politis2004automatic}, and 
+\citet{lahiri2013resampling}.
+
+\item Motivated by these references, we implemented the automatic block 
+length selection method proposed by \citet{politis2004automatic} for 
+circular block bootstrap and reported our findings in a new appendix. 
+While this method is attractive in principle, our empirical results show 
+that it often selects overly large block sizes---especially under strong 
+dependence---resulting in limited variability among bootstrap replicates 
+and diminished test performance. These observations echo the theoretical 
+concerns raised in the literature and underscore the practical limitations 
+of fully automatic block length selection in the context of 
+goodness-of-fit testing.
+\end{itemize}
+
+We hope these additions clarify our awareness of the issue and reflect 
+our effort to better contextualize the finite-sample limitations of the 
+NPBB method.
+
+\jy{Make sure all references here are cited at appropriate places in the paper.}
 
@@
 
-Thank you for your comment...
+We appreciate the reviewer’s suggestion and agree that a more accessible, 
+heuristic explanation enhances the clarity of the methodology. In response, 
+we have added a new subsection (Section~2.4). It gives an intuitive
+discussion of the role of the bias correction term $ K_n(x)$, explains
+how it arises in the bootstrap world, and clarifies how it relates to
+its counterpart $C_n(x)$ in the independent case. We hope this
+addition helps readers gain a better understanding of the underlying
+structure and motivation of the proposed method.
 
@@
 
-Thank you. This is an interesting direction to investigate. We have added few
-sentences concerning potential future investigation into evaluating a bias 
-correction for these variants in the second paragraph of the Discussion 
-section.
+Our method is indeed based on the circular block bootstrap, a variant
+of the moving block bootstrap originally proposed by
+\citet{romano1992circular}, and this is now clearly stated throughout
+the manuscript. We agree that investigating how other bootstrap
+variants, such as the stationary bootstrap
+\citep{politis1994stationary} and the dependent wild
+bootstrap \citep{shao2010dependent}, perform in conjunction with our
+bias correction scheme is a valuable direction for future work. In
+response to this comment, we have added a discussion in the third
+paragraph of the \emph{Discussion} Section, highlighting this
+extension as a promising avenue for further investigation.
 
@@
 
-Thank you for drawing this to our attention...
+Thank you for drawing this to our attention. As is standard in hypothesis 
+testing, our development of the bootstrap procedure is focused on accurately 
+approximating the distribution of the test statistic under the null hypothesis. 
+This is consistent with the goal of using the bootstrap to construct valid
+ p-values and rejection regions. While the same bias correction is applied 
+regardless of whether the null is true, its purpose is to replicate the 
+behavior of the statistic under the null, which is the basis for valid inference.
+
+To better explain the rationale for the correction term, and in response to both 
+this comment and Reviewer 1’s request for clearer heuristic explanation, we have 
+added a dedicated subsection (Section~2.4) titled \emph{Heuristic justification 
+of the bias correction in NPBB}. This subsection provides an intuitive discussion 
+of the role of the bias correction term, its construction, and its relation to 
+the version used in the independent case. The revised text aims to clarify that 
+the correction is justified by its ability to improve bootstrap calibration under 
+the null hypothesis, which is the relevant distribution for hypothesis testing.
 

### 2025-05-25 manuscript/manuscript.tex

@@
 recognized as an effective good-of-fit test for continuous distributions.
-Consider $X_1, ..., X_n$, a random sample of size~$n$ from some continuous
+Consider $X_1,  \cdots , X_n$, a random sample of size~$n$ from some continuous
 distribution and the null hypothesis $H_0$ that $X_i$'s follow a specific
@@
 asymptotic normality property.  Let $F_n$ be the empirical distribution
-function based on $X_1,...,X_n$.
+function based on $X_1, \cdots ,X_n$.
 Define
@@
 In summary, the procedure of the NPB KS test for an independent sample is
-summarized as follows. Repeat the following steps for $b \in \{1, ..., B\}$.
+summarized as follows. Repeat the following steps for $b \in \{1,  \cdots , B\}$.
 \begin{enumerate}
 \item
-  Generate $X^{(b)}_1,...,X^{(b)}_n$ by sampling $X_1, \ldots, X_n$
+  Generate $X^{(b)}_1, \cdots ,X^{(b)}_n$ by sampling $X_1, \ldots, X_n$
   with replacement.
@@
   fitted parameters
-	$\hat\theta^{(b)}_n$ of $\theta$ from $X^{(b)}_1,...,X^{(b)}_n$.
+	$\hat\theta^{(b)}_n$ of $\theta$ from $X^{(b)}_1, \cdots ,X^{(b)}_n$.
 \item
   Obtain the empirical distribution function $F^{(b)}_n$ of
-  $X^{(b)}_1,...,X^{(b)}_n$.
+  $X^{(b)}_1, \cdots ,X^{(b)}_n$.
 \item
@@
 We now consider the case where $X_i$'s are realizations from a time series and
-$X^{(b)}_1,...,X^{(b)}_n$ are generated by block bootstrap for
+$X^{(b)}_1, \cdots ,X^{(b)}_n$ are generated by block bootstrap for
 $b \in \{1, \ldots, B\}$.
@@
 function for block size that is considered optimal is
-$l = \lceil n^{1/3} \rceil$ \citep{buhlmann1999block}... \citet{hall1995blocking}
-and
+$l = \lceil n^{1/3} \rceil$ \citep{buhlmann1999block}.
+\citet{hall1995blocking} and
 \citet{politis2004automatic} note that
@@
 and direction of serial dependence. The plug-in approach for circular
-bootstrap introduced in \citet{politis2004automatic}...
+bootstrap introduced in \citet{politis2004automatic}.
 Now we draw $k$ blocks from the $(n - l + 1)$ blocks
@@
 In summary, the procedure of the NPBB test is
-summarized as follows. Repeat the following steps for $b \in \{1, ..., B\}$.
+summarized as follows. Repeat the following steps for $b \in \{1,  \cdots , B\}$.
 \begin{enumerate}
 \item
-  Generate $X^{(b)}_1,...,X^{(b)}_n$ by applying circular block bootstrap
+  Generate $X^{(b)}_1, \cdots ,X^{(b)}_n$ by applying circular block bootstrap
   on the original sample as
@@
   Obtain parametrically fitted parameters
-  $\hat\theta^{(b)}_n$ of $\theta$ from $X^{(b)}_1,...,X^{(b)}_n$.
+  $\hat\theta^{(b)}_n$ of $\theta$ from $X^{(b)}_1, \cdots ,X^{(b)}_n$.
 \item
   Obtain the empirical distribution function $F^{(b)}_n$ of
-  $X^{(b)}_1,...,X^{(b)}_n$.
+  $X^{(b)}_1, \cdots ,X^{(b)}_n$.
 \item
@@
 
-\section{Conclusions}\label{sec:conclusion}
+\section{Discussion}\label{sec:conclusion}
 
@@
 model approximates the true dependence model.
+
+The choice of block size is well known to influence the performance of
+block bootstrap methods, particularly for inference on dependent
+data. As pointed out by \citet{hall1995blocking} and
+\citet{lahiri1999theoretical}, the optimal block length depends on the
+strength of serial dependence, and using a uniform choice across
+different dependence settings can lead to size distortion. Several
+data-driven procedures for selecting block size have been proposed,
+including plug-in and cross-validation methods
+\citep{buhlmann2002bootstraps, politis2004automatic}. A more
+comprehensive treatment is given in
+\citet{lahiri2013resampling}. Following these suggestions, we applied
+the automatic block length selection method of
+\citet{politis2004automatic} for circular block bootstrap in our
+context. As reported in the Appendix, the method frequently selected
+block sizes that were overly large—sometimes exceeding the sample
+size—especially under strong serial dependence. This reduced the
+variability of the bootstrap replicates and affected the reliability
+of the test. These observations highlight that while automatic methods
+are attractive in principle, their performance in small to moderate
+samples and in goodness-of-fit settings like ours may be limited.
 

### 2025-05-29 manuscript/manuscript.tex
figure code updated but data not updated yet so figures are not yet correct

@@
 to less variation between the bootstrapped
-samples. Figures~\ref{fig:large_block_normal} and \ref{fig:large_block_gamma}
+samples. Figures~\ref{fig:large_block} and \ref{fig:large_block}
 demonstrate that for highly temporally
@@
   \centering
-  \includegraphics[scale=1]{figures/large_block_normal}
+  \includegraphics[scale=1]{figures/large_block}
   \caption{Proportion of selected block sizes using
@@
     $\tau \in \{-0.75, -0.5, -0.25, 0, 0.25, 0.5, 0.75\}$, and true marginal distribution
-    $N(8,8)$.
+    $N(8,8)$ and $\Gamma(8,1)$.
   }
-  \label{fig:large_block_normal}
+  \label{fig:large_block}
+\end{figure}
+
+Even for the settings with block sizes that are typically less than
+$\sqrt{n}$ such as for $n = 800, X_i \sim N(8, 8)$, and $\tau = 0.5$, our 
+algorithm still does not hold its size as demonstrated in 
+Figure~\ref{fig:my_setting}, and the block
+sizes are still much larger than $l = \lceil n^{1/3} \rceil$, which is often
+considered optimal in general.
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[scale=1]{figures/my_setting}
+  \caption{Q-Q plot of the p-values testing that a length-800 time series with
+    Kendall's $\tau = 0.5$
+    have marginal normal distribution with true data generating distribution
+    being $N(8,8)$.
+  }
+  \label{fig:my_setting}
 \end{figure}
@@
   \centering
-  \includegraphics[scale=1]{figures/large_block_gamma}
-  \caption{Proportion of selected block sizes using
-  \citet{politis2004automatic}'s procedure that are larger than the sample size
-    $n$ for $n \in \{100, 200, 400, 800\}$,
-    $\tau \in \{-0.75, -0.5, -0.25, 0, 0.25, 0.5, 0.75\}$, and true marginal distribution
-    $\Gamma(8,1)$.
+  \includegraphics[scale=1]{figures/block_dist}
+  \caption{Distribution of the selected block sizes using
+  \citet{politis2004automatic}'s procedure applied to a length-800 time series with
+    Kendall's $\tau = 0.5$ data generating distribution $N(8,8)$.
   }
-  \label{fig:large_block_gamma}
+  \label{fig:block_dist}
 \end{figure}

### 2025-05-29 code/blk2004_analysis.R

@@ -30,26 +30,12 @@ gg.f <- ggplot(my_freq, aes(x = tau, y = freq)) +
 ggsave(filename = 'large_block.pdf', plot = gg.f, 
        path = "../manuscript/figures", height = 3, width = 6)
 
+my_setting1 <- my_data %>% filter(n == 800, true_dist == 'normal', 
+                                 tau == 0.5)
 
-my_data$large_block <- ifelse(my_data$blk > sqrt(my_data$n), 'T', 'F')
-table(my_data$large_block)
+my_setting2 <- my_setting1 %>% filter(truth == 'null')
 
-
-
-
-)
-
-
-
-
-  
-
-
-
-
-normal_null <- normal %>% filter(truth == 'null')
-
-ggplot(data = normal_null, mapping = aes(sample = p)) +
+gg.f <- ggplot(data = my_setting2, mapping = aes(sample = p)) +
   scale_x_continuous(breaks=c(0, 1)) +
   scale_y_continuous(breaks=c(0, 1)) + 
   stat_pp_band(distribution = "unif") +
@@ -61,4 +47,13 @@ ggplot(data = normal_null, mapping = aes(sample = p)) +
        y = "Empirical Cumulative Distribution") +
   coord_fixed() +
   theme(strip.text.x = element_text(size = 8))
+ggsave(filename = 'my_setting.pdf', plot = gg.f, 
+       path = "../manuscript/figures", height = 3, width = 6)
 
+
+gg.f <- ggplot(data = my_setting1, mapping = aes(x = blk)) +
+  geom_histogram() +
+  geom_vline(xintercept = ceiling(800^(1/3)),linetype="dashed") +
+  labs(x = "Block Size")
+ggsave(filename = 'block_dist.pdf', plot = gg.f, 
+       path = "../manuscript/figures", height = 3, width = 6)

### 2025-05-29 manuscript/manuscript.tex
quick comments

@@
 
-\section{Appendix}\label{sec:appendix}
+\appendix
+
+\section{Block Size Investigation}\label{sec:appendix}
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[scale=1]{figures/large_block}
+  \caption{Proportion of selected block sizes using the method of
+  \citet{politis2004automatic} that are larger than the sample size
+    $n$ for $n \in \{100, 200, 400, 800\}$,
+    $\tau \in \{-0.75, -0.5, -0.25, 0, 0.25, 0.5, 0.75\}$, and true marginal distribution
+    $N(8,8)$ and $\Gamma(8,1)$.
+  }
+  \label{fig:large_block}
+\end{figure}
 In our original setting, we used a block size of $l = \lceil n^{1/3} \rceil$.
@@
 \citet{politis2004automatic}. Unfortunately, using this setting results in
-the selection of
-block
+the selection of block
 sizes that can be quite large (sometimes as large or larger than $n$), leading
 to less variation between the bootstrapped
-samples. Figures~\ref{fig:large_block} and \ref{fig:large_block}
+samples. Figures~\ref{fig:large_block}
 demonstrate that for highly temporally
@@
 the block size is frequently larger than $\sqrt{n}$.
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[scale=1]{figures/large_block}
-  \caption{Proportion of selected block sizes using
-  \citet{politis2004automatic}'s procedure that are larger than the sample size
-    $n$ for $n \in \{100, 200, 400, 800\}$,
-    $\tau \in \{-0.75, -0.5, -0.25, 0, 0.25, 0.5, 0.75\}$, and true marginal distribution
-    $N(8,8)$ and $\Gamma(8,1)$.
-  }
-  \label{fig:large_block}
-\end{figure}
-
-Even for the settings with block sizes that are typically less than
-$\sqrt{n}$ such as for $n = 800, X_i \sim N(8, 8)$, and $\tau = 0.5$, our 
-algorithm still does not hold its size as demonstrated in 
-Figure~\ref{fig:my_setting}, and the block
-sizes are still much larger than $l = \lceil n^{1/3} \rceil$, which is often
-considered optimal in general.
+\jy{add discussions about the figure}
 
@@
 
+Even for the settings with block sizes that are typically less than
+$\sqrt{n}$ such as for $n = 800, X_i \sim N(8, 8)$, and $\tau = 0.5$, our 
+algorithm still does not hold its size as demonstrated in 
+Figure~\ref{fig:my_setting}, and the block
+sizes are still much larger than $l = \lceil n^{1/3} \rceil$, which is often
+considered optimal in general.
+\jy{How do you interpret the flat lines in the plot? Why are the
+  empirical cdf step functions? That means your empirical p-values are
+  discrete with point masses at a few points. Check the p-values from
+  the simulations.}
+
 \begin{figure}[tbp]
@@
 \end{figure}
+
+\jy{Discuss the figure}
 
@@
 \item[Data availability statement:] The data and code used in the real data analysis and simulation
-studies are publicly available in a GitHub repo:
+studies are publicly available in a GitHub repo:\\
 \url{https://github.com/mathewchandy03/Bootstrap_KS_Test}.

### 2025-05-30 manuscript/manuscript.tex
fixed plots still need to finish reply letter

--- 2025-05-29 manuscript/manuscript.tex
@@
 
-Even for the settings with block sizes that are typically less than
-$\sqrt{n}$ such as for $n = 800, X_i \sim N(8, 8)$, and $\tau = 0.5$, our 
-algorithm still does not hold its size as demonstrated in 
-Figure~\ref{fig:my_setting}, and the block
-sizes are still much larger than $l = \lceil n^{1/3} \rceil$, which is often
-considered optimal in general.
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[scale=1]{figures/my_setting}
-  \caption{Q-Q plot of the p-values testing that a length-800 time series with
-    Kendall's $\tau = 0.5$
-    have marginal normal distribution with true data generating distribution
-    being $N(8,8)$.
-  }
-  \label{fig:my_setting}
-\end{figure}
+Even for settings where the block sizes are usually less than $\sqrt{n}$ -
+such as for $n = 800$, $\tau = 0.5$, and $X_i \sim N(8, 8)$ - the 
+block
+sizes are almost always larger than $l = \lceil n^{1/3} \rceil$.
 
@@
   \caption{Distribution of the selected block sizes using
-  \citet{politis2004automatic}'s procedure applied to a length-800 time series with
+  \citet{politis2004automatic}'s procedure applied to 20000 length-800 time 
+  series with
     Kendall's $\tau = 0.5$ data generating distribution $N(8,8)$.
@@
   \label{fig:block_dist}
+\end{figure}
+
+Despite this, our 
+algorithm holds its size somewhat well for moderately dependent
+series as demonstrated in 
+Figures~\ref{fig:alt_normal} and \ref{fig:alt_gamma}. Both 
+\citet{politis2004automatic}'s setting and the cubic root setting result
+in the method not holding its size for $|\tau| > 0.5$. 
+Figure~\ref{fig:alt_rr} also shows that the two setting are comparably
+powerful for $|\tau| <= 0.5$. However, we still
+recommend the cubic root setting over that introduced by 
+\citet{politis2004automatic} because the latter fails to hold its size
+for negative $\tau$, particularly for smaller sample sizes. It is important to 
+note that another block size selection rationale could yield better results.
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[scale=1]{figures/alt_normal}
+  \caption{Q-Q plots of the p-values testing that a time series
+    have marginal normal distribution with true data generating distribution
+    being $N(8,8)$, when using \citet{politis2004automatic}'s procedure
+    to select block sizes.
+  }
+  \label{fig:alt_normal}
+\end{figure}
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[scale=1]{figures/alt_gamma}
+  \caption{Q-Q plots of the p-values testing that a time series
+    have marginal gamma distribution with true data generating distribution
+    being $\Gamma(8,1)$, when using \citet{politis2004automatic}'s procedure
+    to select block sizes.
+  }
+  \label{fig:alt_gamma}
+\end{figure}
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[scale=1]{figures/alt_rr}
+  \caption{Empirical power curve as a function of $\tau$ for
+    $n \in \{100, 200, 400, 800\}$ and true marginal distribution
+    $\in \{N(8,8), \Gamma(8,1)\}$, when using \citet{politis2004automatic}'s 
+    procedure
+    to select block sizes. When the data was generated from $N(8,8)$,
+    we tested for the gamma family. When the data was generated from
+    $\Gamma(8,1)$, we tested for the normal family.
+  }
+  \label{fig:alt_rr}
 \end{figure}
@@
 
-\item[Data availability statement:] The data and code used in the real data analysis and simulation
-studies are publicly available in a GitHub repo:
+\item[Data availability statement:] The data and code used in the real data analysis and simulation studies are publicly available in a GitHub repo:
+
 \url{https://github.com/mathewchandy03/Bootstrap_KS_Test}.

### 2025-05-30 manuscript/reply.tex
fixed plots still need to finish reply letter

@@
 \subsection*{To Referee 1}
+
+\begin{comment}
+This manuscript proposes a nonparametric block bootstrap (NPBB) method for applying the
+
+Kolmogorov-Smirnov (KS) test to stationary time series data with unknown parameters and un-
+specified serial dependence. The authors claim that the method offers a robust nonparametric
+
+solution for evaluating the fit of marginal distributions when data are serially dependent, without
+requiring assumptions about the form of this dependence. The paper is well-written and smooth
+to read. However, upon review, I find that it lacks methodological and theoretical innovation.
+\end{comment}
 
@@
 \begin{comment}
+This paper focuses on approximating the distribution of the Kolmogorov-
+Smirnov (KS) statistic for stationary time series. SpeciÖcally, it deals with the
+
+distribution of KS statistic for testing if the marginal distribution belongs to
+a speciÖed parametric family. Parametric bootstrap requires knowledge of the
+
+nature of serial dependence, and for this reason, nonparametric bootstrap is em-
+plyed here. For the iid case, \citet{babu2004goodness} obtained a correction term
+
+so that the corrected bootstraped statistic can be used to approximate distribu-
+tion of the KS statistic. This paper does the same except it uses nonparametric
+
+bootstrap developed by Kunsch and others. Finally the author(s) present some
+empirical work in support of their proposed procedure. Simulations indicate
+
+that the proposed procedure may work for large samples and moderate depen-
+dence.
+\end{comment}
+
+\begin{comment}
 1. In Section 3.1, it seems that Kendall's tau is being used as a measure
@@
 rewriting.
+
+\mc{I will insert the rest of the comment here}
 \end{comment}

### 2025-05-30 manuscript/manuscript.tex

@@
 \usepackage{setspace}
+
+\newcommand{\jy}[1]{\textcolor{red}{JY: #1}}
+\newcommand{\eds}[1]{\textcolor{blue}{(EDS: #1)}}
+\newcommand{\mc}[1]{\textcolor{green}{(MC: #1)}}
+\newcommand{\xz}[1]{\textcolor{cyan}{(XZ: #1)}}
 
@@
 
-\section{Appendix}\label{sec:appendix}
+\appendix
+
+\section{Block Size Investigation}\label{sec:appendix}
+
 In our original setting, we used a block size of $l = \lceil n^{1/3} \rceil$.
@@
   \includegraphics[scale=1]{figures/large_block}
-  \caption{Proportion of selected block sizes using
-  \citet{politis2004automatic}'s procedure that are larger than the sample size
+  \caption{Proportion of selected block sizes using the method of
+  \citet{politis2004automatic} that are larger than the sample size
     $n$ for $n \in \{100, 200, 400, 800\}$,
@@
 sizes are almost always larger than $l = \lceil n^{1/3} \rceil$.
+
+\jy{How do you interpret the flat lines in the plot? Why are the
+  empirical cdf step functions? That means your empirical p-values are
+  discrete with point masses at a few points. Check the p-values from
+  the simulations.}
+\mc{this was a result of erroneous data, it is fixed now}
 
@@
 in the method not holding its size for $|\tau| > 0.5$. 
-Figure~\ref{fig:alt_rr} also shows that the two setting are comparably
+Figure~\ref{fig:alt_rr} also shows that the two settings are comparably
 powerful for $|\tau| <= 0.5$. However, we still
@@
 
-\item[Data availability statement:] The data and code used in the real data analysis and simulation studies are publicly available in a GitHub repo:
-
+\item[Data availability statement:] The data and code used in the real data analysis and simulation
+studies are publicly available in a GitHub repo:\\
 \url{https://github.com/mathewchandy03/Bootstrap_KS_Test}.

### 2025-05-30 manuscript/manuscript.tex
addressed the AE's comment

@@
 the structure of the serial dependence, which can vary widely in practical
-situations. Employing a nonparametric method would necessitate defining a
+situations. Employing a parametric method would necessitate defining a
 specific model for this dependence, despite the primary focus being on

### 2025-05-30 manuscript/reply.tex
addressed the AE's comment

--- 2025-05-24 manuscript/reply.tex
@@
 A successful revision will require that the authors give serious consideration to these points.
-
-I also noticed that on Page 3 it says “Employing a nonparametric method would necessitate defining a specific model for this dependence”, but I think here “nonparametric” should be “parametric”.
 \end{comment}
 
+\begin{comment}
+1. I also noticed that on Page 3 it says “Employing a nonparametric method would necessitate defining a specific model for this dependence”, but I think here “nonparametric” should be “parametric”.
+\end{comment}
+
+Thank you for pointing out this error in our manuscript. We have corrected
+it from "nonparametric" to "parametric" accordingly.
+
 \subsection*{To Referee 1}
+
+\begin{comment}
+This manuscript proposes a nonparametric block bootstrap (NPBB) method for applying the
+Kolmogorov-Smirnov (KS) test to stationary time series data with unknown parameters and unspecified serial dependence.
+The authors claim that the method offers a robust nonparametric solution for evaluating the fit of marginal distributions when data are serially dependent, without
+requiring assumptions about the form of this dependence. The paper is well-written and smooth
+to read. However, upon review, I find that it lacks methodological and theoretical innovation.
+\end{comment}
 
@@
 \begin{comment}
+This paper focuses on approximating the distribution of the Kolmogorov-
+Smirnov (KS) statistic for stationary time series. Specifically, it deals with the
+distribution of KS statistic for testing if the marginal distribution belongs to
+a specified parametric family. Parametric bootstrap requires knowledge of the
+nature of serial dependence, and for this reason, nonparametric bootstrap is 
+employed here. For the iid case, \citet{babu2004goodness} obtained a correction 
+term so that the corrected bootstraped statistic can be used to approximate 
+distribution of the KS statistic. This paper does the same except it uses 
+nonparametric bootstrap developed by Kunsch and others. Finally the author(s) 
+present some empirical work in support of their proposed procedure. Simulations 
+indicate that the proposed procedure may work for large samples and moderate depen-
+dence.
+\end{comment}
+
+\begin{comment}
 1. In Section 3.1, it seems that Kendall's tau is being used as a measure
@@
 rewriting.
+
+Here is what I am able to understand after reading this paper, the papers
+by Babu and Rao, and Kunsch and others.
+
+Following the notations in this paper (the same notations have been used in
+Babu and Rao), let
+
+\mc{I will insert the rest of the comment here}
 \end{comment}

### 2025-05-30 manuscript/reply.tex
response to opening summaries of AE and reviewers

@@
 \begin{comment}
-
 Two reviewers have carefully read the paper and have provided detailed feedback.
@@
 
+We thank the AE for the careful reading and encouraging feedback. The
+reviewers’ comments have been addressed to the best of our ability in
+the revised manuscript. We have added a heuristic justification for
+the bias correction term in Section~2.4, following the logic of
+\citet{babu2004goodness}, and clarified its extension to the block
+bootstrap setting. As suggested, we also implemented a data-driven
+block size selection method based on \citet{politis2004automatic} and
+evaluated its performance. The results are included in the Appendix,
+along with a discussion of the challenges posed by automatic block
+length selection under strong serial dependence. Please find our
+detailed point-by-point responses below.
+
 \begin{comment}
@@
 
-Thank you for pointing out this error in our manuscript. We have corrected
-it from "nonparametric" to "parametric" accordingly.
+Fixed.
+
+\jy{Is there a second point from the AE?}
 
@@
 
+We thank the reviewer for the thoughtful comments and for recognizing
+the clarity of the manuscript. While the methodological foundation
+builds on existing work, the extension of the bias-corrected
+nonparametric bootstrap of \citet{babu2004goodness} to stationary time
+series with unspecified serial dependence is, to our knowledge, new
+and practically valuable. As the reviewer noted, the paper targets a
+general audience; accordingly, we added for a heuristic justification
+of the bias correction term in Section~2.4 and clarified how the
+approach adapts and differs from the i.i.d. setting in the presence of
+serial dependence. We have revised the Introduction and Discussion
+sections to better emphasize the scope and contribution.
+
 \begin{comment}
 1. The main contribution is presented as an extension of the bias-corrected 
-nonparametric
-bootstrap (NPB) KS test, which was already established by 
+nonparametric bootstrap (NPB) KS test, which was already established by 
 \citet{babu2004goodness}
@@
 
+We thank the reviewer for their accurate and concise summary of our
+contribution.
+
 \begin{comment}
@@
 dependence between $X_t$ and $X_{t+1}$. It may be useful to make that explicit 
-in the
-second pararaph of the Size subsection.
+in the second pararaph of the Size subsection.
 \end{comment}
 
-Thank you for pointing this out. In the second paragraph of Section 3.1, 
-we have added that the
-serial dependence is specifically between $X_i$ and $X_{i+1}$.
+Thank you for pointing this out. In the second paragraph of
+Section~3.1, we have added that the serial dependence is specifically
+between $X_t$ and $X_{t+1}$.
 

### 2025-06-10 manuscript/manuscript.tex
cleaned up figures

@@
 Circular block-bootstrap can be done with overlapping blocks that can
-wrap around the end of the series \citet{romano1992circular}.
+wrap around the end of the series \citep{romano1992circular}.
 Define blocks (assuming block size $l > 1$) as:
@@
 A common
-function for block size that is considered optimal is
-$l = \lceil n^{1/3} \rceil$ \citep{buhlmann1999block}.
+function for block size that is often considered optimal is
+$l = \lceil n^{1/3} \rceil$ \citep{buhlmann1999block},
+although
 \citet{hall1995blocking} and
@@
 the selection of block size should ideally take into account the strength
-and direction of serial dependence. The plug-in approach for circular
-bootstrap introduced in \citet{politis2004automatic}.
+and direction of serial dependence. 
 Now we draw $k$ blocks from the $(n - l + 1)$ blocks
@@
 we used $B = 1000$ and $l = \lceil n^{1/3} \rceil$.
+As noted in Subsection~\ref{sub:npbb}, previous literature
+suggests varying block size based on the dependence structure of the series.
+For this reason,
+we also tried implementing our algorithm using the plug-in approach for circular
+bootstrap block size introduced in \citet{politis2004automatic}. Results and
+a discussion of this additional simulation are provided in the Appendix.
 For each setting for $F$, $\tau$, and $n$, we replicate the method 10000 times
@@
 dependent samples (especially when the autocorrelation is negative),
-the block size is frequently larger than $\sqrt{n}$.
+the block size is frequently larger than $\sqrt{n}$. For more moderate 
+positive temporal dependence, the block size may not be overly large
+as frequently.
 
@@
 
-Even for settings where the block sizes are usually less than $\sqrt{n}$ -
+Still, even for settings where the block sizes are usually less than $\sqrt{n}$ -
 such as for $n = 800$, $\tau = 0.5$, and $X_i \sim N(8, 8)$ - the 
-block
-sizes are almost always larger than $l = \lceil n^{1/3} \rceil$.
-
-\jy{How do you interpret the flat lines in the plot? Why are the
-  empirical cdf step functions? That means your empirical p-values are
-  discrete with point masses at a few points. Check the p-values from
-  the simulations.}
-\mc{this was a result of erroneous data, it is fixed now}
+block sizes are almost always larger than $l = \lceil n^{1/3} \rceil$, a setting
+which was considered optimal by \citep{buhlmann1999block}. This
+is demonstrated in Figure~\ref{fig:block_dist} with a histogram
+of the selected block sizes for this setting.
 
@@
   series with
-    Kendall's $\tau = 0.5$ data generating distribution $N(8,8)$.
+    Kendall's $\tau = 0.5$ data generating distribution $N(8,8)$. The vertical
+    dashed line is $l = \lceil n^{1/3} \rceil$ for $n = 800$, which is equivalent 
+    to 10.
   }
@@
 
-Despite this, our 
-algorithm holds its size somewhat well for moderately dependent
+Despite this, the
+algorithm with \citet{politis2004automatic}'s setting holds its size somewhat 
+well for moderately 
+positively dependent
 series as demonstrated in 
-Figures~\ref{fig:alt_normal} and \ref{fig:alt_gamma}. Both 
+Figure~\ref{fig:alt_qq}. Both 
 \citet{politis2004automatic}'s setting and the cubic root setting result
@@
 Figure~\ref{fig:alt_rr} also shows that the two settings are comparably
-powerful for $|\tau| <= 0.5$. However, we still
-recommend the cubic root setting over that introduced by 
+powerful for $|\tau| <= 0.5$, with \citet{politis2004automatic}'s
+setting perhaps even having higher rejection rates for smaller negatively
+dependent sample sizes. 
+However, we still
+recommend the original cubic root setting over that introduced by 
 \citet{politis2004automatic} because the latter fails to hold its size
-for negative $\tau$, particularly for smaller sample sizes. It is important to 
-note that another block size selection rationale could yield better results.
+for negative $\tau$, particularly for smaller sample sizes.
 
 \begin{figure}[tbp]
+  \includegraphics[width = .9\textwidth]{figures/alt_normal}
   \centering
-  \includegraphics[scale=1]{figures/alt_normal}
+  \vspace{-10pt}
   \caption{Q-Q plots of the p-values testing that a time series
@@
     being $N(8,8)$, when using \citet{politis2004automatic}'s procedure
-    to select block sizes.
-  }
-  \label{fig:alt_normal}
-\end{figure}
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[scale=1]{figures/alt_gamma}
+    to select block sizes.}
+    \hspace{3cm}
+  \includegraphics[width = .9\textwidth]{figures/alt_gamma}
+  \vspace{-5pt}
   \caption{Q-Q plots of the p-values testing that a time series
@@
     being $\Gamma(8,1)$, when using \citet{politis2004automatic}'s procedure
-    to select block sizes.
-  }
-  \label{fig:alt_gamma}
+    to select block sizes.}
+  \label{fig:alt_qq}
 \end{figure}

### 2025-06-10 manuscript/reply.tex
typo fix
cleaned up figures

@@
 
-\jy{Make sure you've included all the comments from the reviewers,
-  including their openning summaries.}
-
 \subsection*{To AE}
@@
 Two reviewers have carefully read the paper and have provided detailed feedback.
-Both reviewers would like to see some additional discussion and justifications for the bias correction term, where one could closely follow the Babu and Rao (2004) paper, and one reviewer mentioned the importance of considering different block sizes (I recommend possibly trying some data-based block size selection method and checking how it performs).
+Both reviewers would like to see some additional discussion and justifications for the bias correction term, where one could closely follow the \citet{babu2004goodness} paper, and one reviewer mentioned the importance of considering different block sizes (I recommend possibly trying some data-based block size selection method and checking how it performs).
 A successful revision will require that the authors give serious consideration to these points.
@@
 Fixed.
-
-\jy{Is there a second point from the AE?}
 
@@
 
-\jy{Make sure all references here are cited at appropriate places in the paper.}
-
 \begin{comment}
@@
 present some empirical work in support of their proposed procedure. Simulations 
-indicate that the proposed procedure may work for large samples and moderate depen-
-dence.
+indicate that the proposed procedure may work for large samples and
+moderate dependence.
 \end{comment}
@@
 dependence between $X_t$ and $X_{t+1}$. It may be useful to make that explicit 
-in the second pararaph of the Size subsection.
+in the second paragraph of Section 3.1.
 \end{comment}
@@
 Here is what I am able to understand after reading this paper, the papers
-by Babu and Rao, and Kunsch and others.
+by \citet{babu2004goodness}, and \citet{kunsch1989jackknife} and others.
 
 Following the notations in this paper (the same notations have been used in
-Babu and Rao), let
+\citet{babu2004goodness}), let
 
-\mc{I will insert the rest of the comment here}
+\begin{align*}
+Y_n(x, \hat \theta_n) &= \sqrt{n}[F_n(x) - F(x; \hat \theta_n)],\\
+Y_n^{(b)}(x, \hat \theta_n^{(b)}) &= \sqrt{n}[F_n^{(b)}(x) - F(x; \hat \theta_n^{(b)})],
+\end{align*}
+
+where the second quantity is based on the $b$th bootstrap sample. In the iid 
+case, \citet{babu2004goodness} introduced a correction term for the nonparametric bootstrap
+$$B_n(x) = \sqrt{n}[F_n(x) - F(x; \hat \theta_n)],$$
+so that
+\begin{align*}
+Y_{n,corr}^{(b)}(x) &= Y_n^{(b)}(x; \hat\theta_n^{(b)}) - B_n(x)\\
+                    &= \sqrt{n}[F_n^{(b)}(x) - F_n(x)] -
+                    \sqrt{n}[F(x; \hat \theta_n^{(b)}) -  F(x; \hat\theta_n)].
+\end{align*}
+It was proved in \citet{babu2004goodness} that the distribution of the KS
+statistic is approximated by that of the corrected bootstrap under the null as
+well as for contiguous alternatives.
+
+The work under consideration uses nonparametric block bootstrap. Let 
+$\theta^*_n = E^*[\hat \theta_n ^{(b)}]$ and $F^*_n(x) = E^*[F_n^{(b)}(x)]$,
+where $E^*$ represents average over bootstrap samples. In this paper the 
+correction term is
+$$C_n(x) = \sqrt{n}[F^*_n(x)-F(x;\theta^*_n)],$$
+so that
+\begin{align*}
+Y^{(b)}_{n,corr}(x) &= Y^{(b)}_n(x;\hat \theta_n^{(b)})-C_n(x)\\
+                    &= \sqrt{n}[F_n^{(b)}(x) - F^*_n(x)] 
+                    - \sqrt{n}[F(x; \hat\theta_n^{(b)}) - F(x; \theta^*_n)].
+\end{align*}
+So the corrected bootstrap proposed here has the same form as in Babu and Rao,
+and the justifications for the procedure proposed here should also be similar.
 \end{comment}

### 2025-06-10 code/blk2004_analysis.R

@@ -30,11 +30,6 @@ gg.f <- ggplot(my_freq, aes(x = tau, y = freq)) +
 ggsave(filename = 'large_block.pdf', plot = gg.f, 
        path = "../manuscript/figures", height = 4, width = 6)
 
-# my_setting1 <- my_data %>% filter(n == 800, true_dist == 'normal', 
-#                                  tau == 0.5)
-# 
-# my_setting2 <- my_setting1 %>% filter(truth == 'null')
-
 gg.f <- ggplot(data = my_data %>% 
                  filter(truth == 'null', true_dist == 'normal'), 
                mapping = aes(sample = p)) +

### 2025-06-10 code/blk2004_jobs.R

@@ -1,4 +1,0 @@
-source("hpc_functions.R")
-library(parallel)
-
-mclapply(1:20, my_job, mc.cores = 20)

### 2025-06-10 code/test_functions.R

@@ -202,12 +202,12 @@ my_job <- function(i, nrep = 1, blksize = 'a') {
     c(-0.9238795, -0.7071068, -0.3826834, 0, 0.3826834, 0.7071068, 0.9238795)
   # 1-2500, to run it locally select one seed
   doRNGseed(i)
-  my_data <- foreach(rep = 1:nrep, .packages=c('rpm'), .combine = 'rbind') %dorng% {
+  my_data <- foreach(rep = 1:nrep, .combine = 'rbind') %dorng% {
     # if (rep %% 4 == 0) print(rep)
-    foreach(phi = phis, .packages=c('rpm'), .combine = 'rbind') %dorng% {
-      foreach(n = c(100, 200, 400, 800), .packages=c('rpm'), .combine = 'rbind') %dorng% {
-        foreach(true_dist = c("normal", "gamma"), .packages=c('rpm'), .combine = 'rbind') %dorng% {
-          foreach(truth = c("null", "alt"), .packages=c('rpm'), .combine = 'rbind') %dorng% {
+    foreach(phi = phis, .combine = 'rbind') %dorng% {
+      foreach(n = c(100, 200, 400, 800), .combine = 'rbind') %dorng% {
+        foreach(true_dist = c("normal", "gamma"), .combine = 'rbind') %dorng% {
+          foreach(truth = c("null", "alt"), .combine = 'rbind') %dorng% {
             if (true_dist == "normal" & truth == "null") {
               h0_dist <- "normal"
               f0 <- pnorm
@@ -312,14 +312,12 @@ my_data <- data.frame(
   rep = integer(),
   stringsAsFactors = FALSE
 )
-# for(i in 1:10) {
-#   print(i)
-# 
-# }
-my_data <- rbind(my_data, my_job(1, 1))
-# close(pb)
-# stopCluster(cl) 
+for(i in 1:10) {
+  print(i)
+  my_data <- rbind(my_data, my_job(i, 1000))
+}
+
 end.time <- Sys.time()
 time.taken <- end.time - start.time
 time.taken
-# saveRDS(my_data, '../data/blk2004_results_10000.RDS')
+saveRDS(my_data, '../data/blk2004_results_10000.RDS')

### 2025-06-10 manuscript/manuscript.tex
edits and comments

@@
 the structure of the serial dependence, which can vary widely in practical
-situations. Employing a parametric method would necessitate defining a
+situations. Employing a semiparametric method
+\citep{zeimbakakis2024misuses} would necessitate defining a
 specific model for this dependence, despite the primary focus being on
@@
 \]
+\jy{What is $f$? Be careful with the dimension of $U$ and $f$.}
 for some appropriately defined Gaussian process $G_{\infty}(\cdot)$
@@
 For comparison, we tested the same hypotheses using 1) the
-SPB method of \citet{zeimbekakis2022misuses},
+SPB method of \citet{zeimbekakis2024misuses},
 which accounts for both serial dependence and unspecified parameters;
@@
 \citet{babu2004goodness}; and 3) the parametric bootstrap (PB) method shown
-by \citet{zeimbekakis2022misuses}. The latter of the two methods discard the
+by \citet{zeimbekakis2024misuses}. The latter of the two methods discard the
 serial dependence. In all methods, we used $B = 10,000$ bootstrap replicates.
@@
 using our method differ from those obtained using the methods proposed by
-\citet{babu2004goodness} and \citet{zeimbekakis2022misuses}.
+\citet{babu2004goodness} and \citet{zeimbekakis2024misuses}.
 For example, our NPBB method fails to reject the
@@
 the SPB result is also not reliable here because the working dependence model is
-in the class of ARMA dependence as specified in \citet{zeimbekakis2022misuses},
+in the class of ARMA dependence as specified in \citet{zeimbekakis2024misuses},
 which does not cover nonlinear dependence usually captured by autoregressive
@@
 series with unspecified serial dependence. Compared to the SPB method
-of \citet{zeimbekakis2022misuses}, which requires a working dependence model, it
+of \citet{zeimbekakis2024misuses}, which requires a working dependence model, it
 is reliable with no need to worry about whether the working dependence
@@
 
-\section{Block Size Investigation}\label{sec:appendix}
+\section{Block Size Investigation}\label{sec:blocksize}
 
@@
 
+\jy{Watch proper usage of dashes.}
 Still, even for settings where the block sizes are usually less than $\sqrt{n}$ -
@@
 of the selected block sizes for this setting.
+\jy{What's the logical connection of this paragraph with the
+  surrounding paragraphs?}
 
@@
 setting perhaps even having higher rejection rates for smaller negatively
-dependent sample sizes. 
-However, we still
+dependent sample sizes. However, we still
+\jy{too strong. soften it.}
 recommend the original cubic root setting over that introduced by 

### 2025-06-10 manuscript/reply.tex
edits and comments

@@
   contextualize our findings in light of existing literature on
-  optimal block length
+  optimal block size.
 \item A stronger and more detailed justification of the bias
-  correction term is now provided in a newly added Section~2.4.
+  correction term is provided in a newly added Section~2.4.
 \end{enumerate}
@@
 \begin{comment}
-1. I also noticed that on Page 3 it says “Employing a nonparametric method would necessitate defining a specific model for this dependence”, but I think here “nonparametric” should be “parametric”.
+I also noticed that on Page 3 it says “Employing a nonparametric method would necessitate defining a specific model for this dependence”, but I think here “nonparametric” should be “parametric”.
 \end{comment}
 
-Fixed.
+We intended to refer to the semiparametric bootstrap method as
+discussed in \citep{zeimbekakis2024misuses}. The sentence has been
+revised to clarify this point and to correctly distinguish it from a
+fully nonparametric approach.
 
@@
 \begin{itemize}
-\item We have added a discussion to the conclusion section (Section~5) 
-that explicitly addresses the role of block size and its effect on the 
-performance of the NPBB test. This includes a review of relevant literature, 
-as suggested by the reviewer, including works by 
-\citet{hall1995blocking}, \citet{lahiri1999theoretical}, 
-\citet{buhlmann2002bootstraps}, \citet{politis2004automatic}, and 
-\citet{lahiri2013resampling}.
+\item We have added a discussion to the \emph{Discussion} section
+  (paragraph~2, Section~5) to explicitly discuss
+  the role of block size and its effect on the 
+  performance of the NPBB test, citing the literature suggested by the
+  reviewer.
 
@@
 length selection method proposed by \citet{politis2004automatic} for 
-circular block bootstrap and reported our findings in a new appendix. 
+circular block bootstrap and reported our findings in a newly added
+section in the Appendix. 
 While this method is attractive in principle, our empirical results show 
@@
 on just the
-null case. The same seems to be true here, and in that case, Section 2 needs
+null case. The same seems to be true here, and in that case, Section~2 needs
 rewriting.
@@
 \end{align*}
-
 where the second quantity is based on the $b$th bootstrap sample. In the iid 
@@
 
-Thank you for drawing this to our attention. As is standard in hypothesis 
+Thank you for the detailed demonstration. As is standard in hypothesis 
 testing, our development of the bootstrap procedure is focused on accurately 

### 2025-06-11 manuscript/manuscript.tex
addressed comments

@@
 that the hypothesized distribution is continuous and fully specified without
-the need for parameter estimation. \citet{zeimbekakis2022misuses} examines
+the need for parameter estimation. \citet{zeimbekakis2024misuses} examines
 common misapplications of the one-sample KS test. One notable inappropriate
@@
 the unknown parameters and unknown serial dependence.
-\citet{zeimbekakis2022misuses} recommend a semiparametric bootstrap (SPB)
+\citet{zeimbekakis2024misuses} recommend a semiparametric bootstrap (SPB)
 approach, where the parameters of the hypothesized distribution and the serial
@@
 situations. Employing a semiparametric method
-\citep{zeimbakakis2024misuses} would necessitate defining a
+\citep{zeimbekakis2024misuses} would necessitate defining a
 specific model for this dependence, despite the primary focus being on
@@
 justify the validity of the NPBB procedure of the KS test.
+Let $f(x; \theta) = \frac{\partial F(x; \theta)}{\partial \theta}$,
+for some hypothesized distribution $F(x; \theta)$, and let $f(x; \theta_0)$
+be its evaluation at $\theta = \theta_0$, and we define $d$ as the 
+dimension of $\theta$.
 As $1/l+l/n\rightarrow 0$,
@@
 \jy{What is $f$? Be careful with the dimension of $U$ and $f$.}
+\mc{addressed}
 for some appropriately defined Gaussian process $G_{\infty}(\cdot)$
-and Gaussian random variable  $U$.
+and $d$-dimensional Gaussian random vector $U$.
 Further,  as $1/l+l/n\rightarrow 0$,
@@
 positive temporal dependence, the block size may not be overly large
-as frequently.
+as frequently. \jy{Watch proper usage of dashes.}\mc{addressed}
+Still, even for these moderately dependent samples, the 
+block sizes are almost always larger than $l = \lceil n^{1/3} \rceil$, a setting
+which was considered optimal by \citep{buhlmann1999block}. This
+is demonstrated in Figure~\ref{fig:block_dist} with a histogram
+of the selected block sizes for the 20000 samples with $n = 800$, $\tau = 0.5$, 
+and $X_i \sim N(8, 8)$.
+\jy{What's the logical connection of this paragraph with the
+  surrounding paragraphs?}
+\mc{highlighting that even samples with moderate positive temporal dependence
+have block sizes larger than expected}
 
@@
 \end{figure}
-
-\jy{Watch proper usage of dashes.}
-Still, even for settings where the block sizes are usually less than $\sqrt{n}$ -
-such as for $n = 800$, $\tau = 0.5$, and $X_i \sim N(8, 8)$ - the 
-block sizes are almost always larger than $l = \lceil n^{1/3} \rceil$, a setting
-which was considered optimal by \citep{buhlmann1999block}. This
-is demonstrated in Figure~\ref{fig:block_dist} with a histogram
-of the selected block sizes for this setting.
-\jy{What's the logical connection of this paragraph with the
-  surrounding paragraphs?}
 
@@
 
-Despite this, the
+Despite the unexpected large block sizes, the
 algorithm with \citet{politis2004automatic}'s setting holds its size somewhat 
@@
 dependent sample sizes. However, we still
-\jy{too strong. soften it.}
-recommend the original cubic root setting over that introduced by 
-\citet{politis2004automatic} because the latter fails to hold its size
+\jy{too strong. soften it.}\mc{addressed}
+caution using
+\citet{politis2004automatic}'s setting because it fails to hold its size
 for negative $\tau$, particularly for smaller sample sizes.

### 2025-06-11 manuscript/manuscript.tex
smoothed appendix, with questions

@@
 \begin{abstract}
-The Kolmogorov--Smirnov (KS) test is a widely used
-statistical test that
+The Kolmogorov--Smirnov (KS) test is a widely used statistical test that
 assesses the conformity of a sample to a specified distribution. Its efficacy,
@@
 $l = \lceil n^{1/3} \rceil$ \citep{buhlmann1999block},
-although
-\citet{hall1995blocking} and
-\citet{politis2004automatic} note that
+although \citet{hall1995blocking} and \citet{politis2004automatic} note that
 the selection of block size should ideally take into account the strength
@@
 justify the validity of the NPBB procedure of the KS test.
-Let $f(x; \theta) = \frac{\partial F(x; \theta)}{\partial \theta}$,
-for some hypothesized distribution $F(x; \theta)$, and let $f(x; \theta_0)$
-be its evaluation at $\theta = \theta_0$, and we define $d$ as the 
-dimension of $\theta$.
+Let $f(x; \theta) = {\partial F(x; \theta)} / {\partial \theta}$
+and $f(x, \theta_0)$ be its evaluation at $\theta = \theta_0$.
+Let $d$ be the  dimension of~$\theta$.
 As $1/l+l/n\rightarrow 0$,
@@
   T_n \overset{d}{\rightarrow}
-  \sup_x \big\vert G_{\infty}(x)+f(x;\theta_0)U \big\vert
+  \sup_x \big\vert G_{\infty}(x)+f^\top (x;\theta_0)U \big\vert
 \]
-\jy{What is $f$? Be careful with the dimension of $U$ and $f$.}
-\mc{addressed}
 for some appropriately defined Gaussian process $G_{\infty}(\cdot)$
@@
 replacing $F^{-1}(p)$ with the quantile function for the $\Gamma(8, 1)$
-distribution.
-After the transformation
+distribution. After the transformation
 to the marginal gamma distribution, the lag-1 autocorrelations are approximately
@@
 error structures. The specific parameters were chosen because the distributions
-are very similar and their
-first two moments are the same.
-For the purposes of
+are very similar and their first two moments are the same. For the purposes of
 evaluating if the test holds it size, when $X_i \sim N(8, 8)$, we tested that the
@@
     being $N(8,8)$.}
+  \label{fig:qq_n}
     \hspace{5cm}
@@
     generating distribution $\Gamma(8,1)$.}
-  \label{fig:qq}
+  \label{fig:qq_g}
 \end{figure}
 
-Figure~\ref{fig:qq} shows the Quantile-Quantile (Q-Q)
+Figures~\ref{fig:qq_n}--\ref{fig:qq_g} show the Quantile-Quantile (Q-Q)
 plots of the p-values testing the marginal distribution of the stationary time
@@
 necessary, as the p-values are not aligned with the line in any of the Q-Q
-plots. This
-is not necessarily a cause for concern, as (for normal margins)
-a Kendall's $\tau$ corresponds to
-a $\phi$ of 0.924, which is very high.
+plots. This is not necessarily a cause for concern, as (for normal margins)
+a Kendall's $\tau$ corresponds to a $\phi$ of 0.924, which is very high.
 Additionally, positive serial dependence appears to misalign the distribution
@@
 usually larger than the nominal size, which indicates that the test is too liberal.
-In
-other words, the test rejects the null hypothesis more often than it should.
+In other words, the test rejects the null hypothesis more often than it should.
 For practical situations with a $\tau$ of magnitude 0.5 or
@@
 
-In our original setting, we used a block size of $l = \lceil n^{1/3} \rceil$.
-However, the optimal block size may vary according to the dependence structure.
-To address this, we considered  using the automatic block-length selection
-scheme
-for
-circular block bootstrap as described in Section 3.3 of
-\citet{politis2004automatic}. Unfortunately, using this setting results in
-the selection of block
-sizes that can be quite large (sometimes as large or larger than $n$), leading
-to less variation between the bootstrapped
-samples. Figures~\ref{fig:large_block}
-demonstrate that for highly temporally
-dependent samples (especially when the autocorrelation is negative),
-the block size is frequently larger than $\sqrt{n}$. For more moderate 
-positive temporal dependence, the block size may not be overly large
-as frequently. \jy{Watch proper usage of dashes.}\mc{addressed}
-Still, even for these moderately dependent samples, the 
-block sizes are almost always larger than $l = \lceil n^{1/3} \rceil$, a setting
-which was considered optimal by \citep{buhlmann1999block}. This
-is demonstrated in Figure~\ref{fig:block_dist} with a histogram
-of the selected block sizes for the 20000 samples with $n = 800$, $\tau = 0.5$, 
-and $X_i \sim N(8, 8)$.
-\jy{What's the logical connection of this paragraph with the
-  surrounding paragraphs?}
-\mc{highlighting that even samples with moderate positive temporal dependence
-have block sizes larger than expected}
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[scale=1]{figures/large_block}
-  \caption{Proportion of selected block sizes using the method of
-  \citet{politis2004automatic} that are larger than the sample size
-    $n$ for $n \in \{100, 200, 400, 800\}$,
-    $\tau \in \{-0.75, -0.5, -0.25, 0, 0.25, 0.5, 0.75\}$, and true marginal distribution
-    $N(8,8)$ and $\Gamma(8,1)$.
-  }
-  \label{fig:large_block}
-\end{figure}
+The choice of block size is a key factor influencing the performance
+of block bootstrap methods, particularly in settings with serial
+dependence. While our main simulations used a fixed block size
+$l = \lceil n^{1/3} \rceil$, the optimal block size depends on the
+stength and structure of dependence \citep{hall1995blocking,
+  buhlmann1999block,  politis2004automatic}. Motivated by this, we
+further examined the use of an automatic block-length selection scheme
+as proposed by \citet{politis2004automatic}, which aims to adaptively
+choose the block size based on the data. The simulation settings
+remain the same as in the study reported earlier.
+
+% To address this, we considered  using the automatic block-length selection
+% scheme for circular block bootstrap as described in Section~3.3 of
+% \citet{politis2004automatic}. Unfortunately, using this setting results in
+% the selection of block
+% sizes that can be quite large (sometimes as large or larger than $n$), leading
+% to less variation between the bootstrapped
+% samples. Figures~\ref{fig:large_block}
+% demonstrate that for highly temporally
+% dependent samples (especially when the autocorrelation is negative),
+% the block size is frequently larger than $\sqrt{n}$. For more moderate 
+% positive temporal dependence, the block size may not be overly large
+% as frequently. Still, even for these moderately dependent samples, the 
+% block sizes are almost always larger than $l = \lceil n^{1/3} \rceil$, a setting
+% which was considered optimal by \citep{buhlmann1999block}. This
+% is demonstrated in Figure~\ref{fig:block_dist} with a histogram
+% of the selected block sizes for the 20000 samples with $n = 800$, $\tau = 0.5$, 
+% and $X_i \sim N(8, 8)$.
 
@@
   \label{fig:block_dist}
+% \end{figure}
+
+% \begin{figure}[tbp]
+  \centering
+  \includegraphics[scale=1]{figures/large_block}
+  \caption{Proportion of selected block sizes using the method of
+  \citet{politis2004automatic} that are larger than the sample size
+    $n$ for $n \in \{100, 200, 400, 800\}$,
+    $\tau \in \{-0.75, -0.5, -0.25, 0, 0.25, 0.5, 0.75\}$, and true marginal distribution
+    $N(8,8)$ and $\Gamma(8,1)$.
+  }
+  \label{fig:large_block}
 \end{figure}
 
-Despite the unexpected large block sizes, the
-algorithm with \citet{politis2004automatic}'s setting holds its size somewhat 
-well for moderately 
-positively dependent
-series as demonstrated in 
-Figure~\ref{fig:alt_qq}. Both 
-\citet{politis2004automatic}'s setting and the cubic root setting result
-in the method not holding its size for $|\tau| > 0.5$. 
-Figure~\ref{fig:alt_rr} also shows that the two settings are comparably
-powerful for $|\tau| <= 0.5$, with \citet{politis2004automatic}'s
-setting perhaps even having higher rejection rates for smaller negatively
-dependent sample sizes. However, we still
-\jy{too strong. soften it.}\mc{addressed}
-caution using
-\citet{politis2004automatic}'s setting because it fails to hold its size
-for negative $\tau$, particularly for smaller sample sizes.
+Automatic block size selection tends to yield larger block sizes than our
+fixed choice $l = \lceil n^{1/3} \rceil$, as expected, but under strong
+negative or very strong positive dependence it systematically produces
+block sizes that are excessively large, sometimes as large as or larger
+than $n$. Figure~\ref{fig:block_dist} illustrates the typical behavior by
+showing the distribution of block sizes selected by \citet{politis2004automatic}
+for $n = 800$, $\tau = 0.5$, and $X_i \sim N(8,8)$. The majority of selected
+block sizes exceed $\lceil n^{1/3} \rceil$, and many approach or exceed
+$\sqrt{n}$. Figure~\ref{fig:large_block} presents the proportion of selected
+block sizes exceeding $n$ across varying levels of dependence and sample sizes.
+The selection of block sizes larger than $n$ occurs systematically under strong
+negative dependence, and is also frequent under very strong positive dependence.
 
@@
     to select block sizes.}
+  \label{fig:alt_qq_n}
     \hspace{3cm}
@@
     to select block sizes.}
-  \label{fig:alt_qq}
+  \label{fig:alt_qq_g}
 \end{figure}
+\jy{Watch for missing figure labels}
 
@@
 
+We evaluated the size and power performance of the NPBB test under automatic
+\jy{How was the block size set when the chosen one is as big as $n$?
+  Excluded? Or settting it as the minimum of the auto-selected and $\sqrt{n}$?}
+block length selection by restricting attention to those replicates where
+the selected block size was $\sqrt{n}$ or lower. The size performane is shown
+in Figures~\ref{fig:alt_qq_n} and \ref{fig:alt_qq_g}, which display Q-Q plots
+of the $p$-values under the null for Normal and Gamma margins, respectively.
+Under this restriction, the method with block size selected by
+\citet{politis2004automatic} maintains reasonable size for moderately positively
+dependent series. However, for $|\tau| > 0.5$, neither the automatic selection
+\jy{refer to Figures 1-2}
+nor the cubic root setting holds its size. The power results are shown in
+Figure~\ref{fig:alt_rr}. For $|\tau| \leq 0.5$, the two settings exhibit
+\jy{comparing with the power figure in the simulation section. Right? Clarify.}
+comparable power, with the automatic selection sometimes yielding higher
+rejection rates, particularly for smaller negatively dependent samples.
+Overall, while the automatic selection from \citet{politis2004automatic}
+performs reasonably well in some settings, we recommend caution when using
+it under negative~$\tau$ and smaller sample sizes, where maintaining nominal
+size may be more challenging.
+
 \bigskip

### 2025-06-11 manuscript/manuscript.tex
addressed question on correction term under H1

@@
 scenarios where the NPBB approach is expected to perform optimally.
+In particular, while the
+correction term is designed to calibrate the null distribution of the
+test statistic, studying its behavior under alternatives, including
+contiguous alternatives, would further inform the power properties of
+the method and remains an interesting direction for future research.
 

### 2025-06-11 manuscript/reply.tex
addressed question on correction term under H1

@@
 
-Thank you for the detailed demonstration. As is standard in hypothesis 
-testing, our development of the bootstrap procedure is focused on accurately 
-approximating the distribution of the test statistic under the null hypothesis. 
-This is consistent with the goal of using the bootstrap to construct valid
-p-values and rejection regions. While the same bias correction is applied 
-regardless of whether the null is true, its purpose is to replicate the 
-behavior of the statistic under the null, which is the basis for valid inference.
+We thank the reviewer for the detailed demonstration. We would like
+clarify that the correction term has the same form as that in
+\citet{babu2004goodness}, which is needed in the distribution of the
+testing statistic under the null hypothesis. The validity of the test
+relies on controlling the Type I error, and thus the justification of
+the correction term pertains to the behavior of the statistic
+under~$H_0$. The bootstrapping method in \citet{babu2004goodness},
+however, cannot be used approximatae the distribution of the null
+distribution of the statistic under serial dependence. The
+distribution under~$H_1$, particularly under contiguous alternatives,
+governs the power of the test but does not affect the correctness of
+the null calibration. Our current focus is on ensuring valid inference
+under $H_0$, for which the proposed correction is justified. To
+address this point, we have added a remark in the \emph{Discussion}
+Section, last paragraph, noting that investigation of the test’s
+behavior under contiguous alternatives remains of interest but is
+distinct from the justification of the correction term.
 

### 2025-06-11 manuscript/manuscript.tex
addressed comments

@@
 block sizes that are excessively large, sometimes as large as or larger
-than $n$. Figure~\ref{fig:block_dist} illustrates the typical behavior by
+than $n$. Note that in our simulations, we set the block size to 
+$\min \{n, \hat l\}$, where
+$\hat l$ is the block size selected by \citet{politis2004automatic}'s
+procedure. Figure~\ref{fig:block_dist} illustrates the typical behavior by
 showing the distribution of block sizes selected by \citet{politis2004automatic}
@@
 \end{figure}
-\jy{Watch for missing figure labels}
 
@@
   Excluded? Or settting it as the minimum of the auto-selected and $\sqrt{n}$?}
+\mc{the block size was set to $n$, I added a sentence in the previous paragraph}
 block length selection by restricting attention to those replicates where
-the selected block size was $\sqrt{n}$ or lower. The size performane is shown
+the selected block size was $\sqrt{n}$ or lower. The size performance is shown
 in Figures~\ref{fig:alt_qq_n} and \ref{fig:alt_qq_g}, which display Q-Q plots
@@
 \jy{refer to Figures 1-2}
-nor the cubic root setting holds its size. The power results are shown in
-Figure~\ref{fig:alt_rr}. For $|\tau| \leq 0.5$, the two settings exhibit
+\mc{addressed}
+nor the cubic root setting (as shown in Figures~\ref{fig:qq_n} and 
+\ref{fig:qq_g}) holds its size. The power results are shown in
+Figure~\ref{fig:alt_rr}. For $|\tau| \leq 0.5$, when comparing 
+with Figure~\ref{fig:rr}, the two settings exhibit
 \jy{comparing with the power figure in the simulation section. Right? Clarify.}
-comparable power, with the automatic selection sometimes yielding higher
+\mc{addressed}
+similar power, with the automatic selection sometimes yielding higher
 rejection rates, particularly for smaller negatively dependent samples.

### 2025-06-11 manuscript/manuscript.tex
last paragraph fixes also added absolute value earlier in paper

@@
 A small sample size like $n = 100$ or $200$ seems adequate when Kendall's
-$\tau$ is lower than 0.25. For Kendall's $\tau \geq 0.5$, a sample larger than
+$\tau$ has an absolute value $|\tau| \leq 0.25$. For $|\tau| \geq 0.5$, 
+a sample larger than
 $n = 200$ seems necessary for the p-values to be uniformly distributed. For
-Kendall's $\tau \geq 0.75$, a sample larger than $n = 800$ appears to be
+$|\tau| \geq 0.75$, a sample larger than $n = 800$ appears to be
 necessary, as the p-values are not aligned with the line in any of the Q-Q
 plots. This is not necessarily a cause for concern, as (for normal margins)
-a Kendall's $\tau$ corresponds to a $\phi$ of 0.924, which is very high.
+a Kendall's $\tau$ of 0.75 corresponds to a $\phi$ of 0.924, which is very high.
 Additionally, positive serial dependence appears to misalign the distribution
@@
   \caption{Proportion of selected block sizes using the method of
-  \citet{politis2004automatic} that are larger than the sample size
-    $n$ for $n \in \{100, 200, 400, 800\}$,
+  \citet{politis2004automatic} that are larger than
+    $\sqrt{n}$ for $n \in \{100, 200, 400, 800\}$,
     $\tau \in \{-0.75, -0.5, -0.25, 0, 0.25, 0.5, 0.75\}$, and true marginal distribution
@@
 block sizes that are excessively large, sometimes as large as or larger
-than $n$. Note that in our simulations, we set the block size to 
+than $n$. Note that in our simulations, we set the final block size to 
 $\min \{n, \hat l\}$, where
@@
 $\sqrt{n}$. Figure~\ref{fig:large_block} presents the proportion of selected
-block sizes exceeding $n$ across varying levels of dependence and sample sizes.
-The selection of block sizes larger than $n$ occurs systematically under strong
+block sizes exceeding $\sqrt{n}$ across varying levels of dependence and sample 
+sizes.
+The selection of block sizes larger than $\sqrt{n}$ occurs systematically under 
+strong
 negative dependence, and is also frequent under very strong positive dependence.
@@
 We evaluated the size and power performance of the NPBB test under automatic
-\jy{How was the block size set when the chosen one is as big as $n$?
-  Excluded? Or settting it as the minimum of the auto-selected and $\sqrt{n}$?}
-\mc{the block size was set to $n$, I added a sentence in the previous paragraph}
-block length selection by restricting attention to those replicates where
-the selected block size was $\sqrt{n}$ or lower. The size performance is shown
+block length selection. The size performance is shown
 in Figures~\ref{fig:alt_qq_n} and \ref{fig:alt_qq_g}, which display Q-Q plots
 of the $p$-values under the null for Normal and Gamma margins, respectively.
-Under this restriction, the method with block size selected by
+Recall from Figures~\ref{fig:qq_n} and \ref{fig:qq_g} that the cubic root 
+setting held its size quite well with small $n$ for $|\tau| \leq 0.25$, whereas
+$|\tau| \geq 0.5$ may require $n > 200$, and $|\tau| \geq 0.75$ may 
+require $n > 800$.
+Similarly, for $|\tau| > 0.5$, the automatic selection
+does not hold its size. In addition, the automatic selection actually seems
+to have larger deviations from the line for negative $\tau$, which
+may be a result of the overly large block sizes. Notably, while the
+cubic root setting held its size for $\tau = -0.25$ for small $n$, the automatic
+selection does not.
+Still, under $\tau = 0$ and $\tau = 0.25$, the method with block size 
+selected by
 \citet{politis2004automatic} maintains reasonable size for moderately positively
-dependent series. However, for $|\tau| > 0.5$, neither the automatic selection
-\jy{refer to Figures 1-2}
-\mc{addressed}
-nor the cubic root setting (as shown in Figures~\ref{fig:qq_n} and 
-\ref{fig:qq_g}) holds its size. The power results are shown in
+dependent series.
+
+The power results are shown in
 Figure~\ref{fig:alt_rr}. For $|\tau| \leq 0.5$, when comparing 
 with Figure~\ref{fig:rr}, the two settings exhibit
-\jy{comparing with the power figure in the simulation section. Right? Clarify.}
-\mc{addressed}
 similar power, with the automatic selection sometimes yielding higher
@@
 it under negative~$\tau$ and smaller sample sizes, where maintaining nominal
-size may be more challenging.
+size may be more challenging. In such cases, it may be sensible to be more
+restrictive when setting the final block size --- for example, using
+$\min \{\sqrt{n}, \hat l\}$.
 

### 2025-06-12 manuscript/manuscript.tex
touch up

@@
 
-Figures~\ref{fig:qq_n}--\ref{fig:qq_g} show the Quantile-Quantile (Q-Q)
-plots of the p-values testing the marginal distribution of the stationary time
-series generated from the null hypothesis, created with R packages
+Figures~\ref{fig:qq_n}--\ref{fig:qq_g} show Quantile-Quantile (Q--Q) plots
+of the $p$-values testing the marginal distribution of the stationary time
+series generated under the null hypothesis. Figure~\ref{fig:qq_n} corresponds
+to the case where the true data generating distribution is $N(8,8)$, and
+Figure~\ref{fig:qq_g} corresponds to the case where the true data generating
+distribution is $\Gamma(8,1)$. The plots were created using the R packages
 \textsl{qqplotr} and \textsl{ggplot2} \citep{qqplotr, ggplot2}. If the
 distribution of the p-values is uniform, the points will be aligned with the
-diagonal line. The plots suggest that the extent to which the p-values are
-uniformly distributed is dependent on the sample size and the level of serial
-dependence.
+diagonal line.
+
+The plots suggest that the extent to which the p-values are uniformly
+distributed is dependent on the sample size and the level of serial dependence.
 A small sample size like $n = 100$ or $200$ seems adequate when Kendall's
@@
 Recall from Figures~\ref{fig:qq_n} and \ref{fig:qq_g} that the cubic root 
-setting held its size quite well with small $n$ for $|\tau| \leq 0.25$, whereas
-$|\tau| \geq 0.5$ may require $n > 200$, and $|\tau| \geq 0.75$ may 
-require $n > 800$.
-Similarly, for $|\tau| > 0.5$, the automatic selection
-does not hold its size. In addition, the automatic selection actually seems
-to have larger deviations from the line for negative $\tau$, which
-may be a result of the overly large block sizes. Notably, while the
-cubic root setting held its size for $\tau = -0.25$ for small $n$, the automatic
-selection does not.
-Still, under $\tau = 0$ and $\tau = 0.25$, the method with block size 
-selected by
-\citet{politis2004automatic} maintains reasonable size for moderately positively
-dependent series.
-
-The power results are shown in
-Figure~\ref{fig:alt_rr}. For $|\tau| \leq 0.5$, when comparing 
-with Figure~\ref{fig:rr}, the two settings exhibit
-similar power, with the automatic selection sometimes yielding higher
+setting holds its size quite well with small $n$ for $|\tau| \leq 0.25$,
+whereas achieving nominal size for $|\tau| \geq 0.5$ require
+$n > 200$, and for $|\tau| \geq 0.75$ require $n > 800$. The automatic
+selection shows similar limitations for $|\tau| > 0.5$, where it does
+not hold its size. Moreover, deviations from the diagonal line appear
+larger for negative $\tau$, likely due to the high proportion of
+occurrence of overly large block sizes. For example, while the cubic
+root setting held its size well at $\tau = -0.25$ with small~$n$, the
+automatic selection does not. At the same time, under $\tau = 0$ or
+$\tau = 0.25$, the method with block size selected by
+\citep{politis2004automatic} maintains reasonable size for moderately
+positively dependent series.
+
+Figure~\ref{fig:alt_rr} shows the power results under automatic selection.
+When compared to Figure~\ref{fig:rr}, the two settings exhibit similar power
+for $|\tau| \leq 0.5$, with the automatic selection sometimes yielding higher
 rejection rates, particularly for smaller negatively dependent samples.
-Overall, while the automatic selection from \citet{politis2004automatic}
-performs reasonably well in some settings, we recommend caution when using
+Overall, while the automatic selection from \citep{politis2004automatic}
+performs reasonably well in certain settings, we recommend caution when using
 it under negative~$\tau$ and smaller sample sizes, where maintaining nominal
-size may be more challenging. In such cases, it may be sensible to be more
-restrictive when setting the final block size --- for example, using
-$\min \{\sqrt{n}, \hat l\}$.
+size may be more difficult. In such cases, it may be sensible to apply a more
+restrictive rule when setting the final block size---for example, using
+$\min \{\sqrt{n}, \hat{l}\}$.
 

### 2025-06-12 manuscript/anon.tex
fixed typo in Readme

@@
 \usepackage{comment}
+\RequirePackage[colorlinks,citecolor=blue,urlcolor=blue]{hyperref}
+\usepackage{setspace}
+
+\allowdisplaybreaks
+
+\usepackage[pagewise]{lineno}
+\linenumbers*[1]
+% patches to make lineno work better with amsmath
+\newcommand*\patchAmsMathEnvironmentForLineno[1]{%
+        \expandafter\let\csname old#1\expandafter\endcsname\csname 
+        #1\endcsname
+        \expandafter\let\csname oldend#1\expandafter\endcsname\csname 
+        end#1\endcsname
+        \renewenvironment{#1}%
+        {\linenomath\csname old#1\endcsname}%
+        {\csname oldend#1\endcsname\endlinenomath}}%
+\newcommand*\patchBothAmsMathEnvironmentsForLineno[1]{%
+        \patchAmsMathEnvironmentForLineno{#1}%
+        \patchAmsMathEnvironmentForLineno{#1*}}%
+\AtBeginDocument{%
+        \patchBothAmsMathEnvironmentsForLineno{equation}%
+        \patchBothAmsMathEnvironmentsForLineno{align}%
+        \patchBothAmsMathEnvironmentsForLineno{flalign}%
+        \patchBothAmsMathEnvironmentsForLineno{alignat}%
+        \patchBothAmsMathEnvironmentsForLineno{gather}%
+        \patchBothAmsMathEnvironmentsForLineno{multline}%
+}
 
@@
 \begin{abstract}
-The Kolmogorov--Smirnov (KS) test is a widely used 
-statistical test that
+The Kolmogorov--Smirnov (KS) test is a widely used statistical test that
 assesses the conformity of a sample to a specified distribution. Its efficacy,
@@
 the structure of the serial dependence, which can vary widely in practical
-situations. Employing a nonparametric method would necessitate defining a 
+situations. Employing a semiparametric method
+\citep{zeimbekakis2024misuses} would necessitate defining a
 specific model for this dependence, despite the primary focus being on
@@
   fitted parameters
-	$\hat\theta^{(b)}_n$ of $\theta$ from $X^{(b)}_1,...,X^{(b)}_n$.  
+	$\hat\theta^{(b)}_n$ of $\theta$ from $X^{(b)}_1, \cdots ,X^{(b)}_n$.
 \item
   Obtain the empirical distribution function $F^{(b)}_n$ of
-  $X^{(b)}_1,...,X^{(b)}_n$. 
+  $X^{(b)}_1, \cdots ,X^{(b)}_n$.
 \item
@@
   where
-  $C_{n}(x) = \sqrt{n}(F_n(x) - F(x; \hat\theta_n))$ is the estimated
-  bias term.
+  \[
+    C_{n}(x) = \sqrt{n}(F_n(x) - F(x; \hat\theta_n))
+  \]
+  is the estimated bias term.
 \end{enumerate}
 
+\citet{babu2004goodness} proves that $T^{(b)}_n$ and $T_n$ have the same
+limiting distribution for almost all samples $X_1, \ldots, X_n$.
 The p-value of the basic bootstrap KS test can be approximated
@@
 We now consider the case where $X_i$'s are realizations from a time series and
-$X^{(b)}_1,...,X^{(b)}_n$ are generated by block bootstrap for 
+$X^{(b)}_1, \cdots ,X^{(b)}_n$ are generated by block bootstrap for
 $b \in \{1, \ldots, B\}$.
-Block-bootstrap can be done with overlapping or moving blocks.
-Define moving blocks (assuming $l > 1$) as:
+Circular block-bootstrap can be done with overlapping blocks that can
+wrap around the end of the series \citep{romano1992circular}.
+Define blocks (assuming block size $l > 1$) as:
 \begin{equation*}
@@
 A common
-function for block size that is considered optimal is 
+function for block size that is often considered optimal is
 $l = \lceil n^{1/3} \rceil$ \citep{buhlmann1999block},
-which was adopted in this study.
+although \citet{hall1995blocking} and \citet{politis2004automatic} note that
+the selection of block size should ideally take into account the strength
+and direction of serial dependence. 
 Now we draw $k$ blocks from the $(n - l + 1)$ blocks
@@
 In summary, the procedure of the NPBB test is
-summarized as follows. Repeat the following steps for $b \in \{1, ..., B\}$.
+summarized as follows. Repeat the following steps for $b \in \{1,  \cdots , B\}$.
 \begin{enumerate}
 \item
-  Generate $X^{(b)}_1,...,X^{(b)}_n$ by applying moving block bootstrap 
+  Generate $X^{(b)}_1, \cdots ,X^{(b)}_n$ by applying circular block bootstrap
   on the original sample as
@@
   Obtain parametrically fitted parameters
-  $\hat\theta^{(b)}_n$ of $\theta$ from $X^{(b)}_1,...,X^{(b)}_n$.  
+  $\hat\theta^{(b)}_n$ of $\theta$ from $X^{(b)}_1, \cdots ,X^{(b)}_n$.
 \item
   Obtain the empirical distribution function $F^{(b)}_n$ of
-  $X^{(b)}_1,...,X^{(b)}_n$. 
+  $X^{(b)}_1, \cdots ,X^{(b)}_n$.
 \item
@@
     T^{(b)}_n = \sup_x \Big\vert \sqrt{n}\left(F^{(b)}_n(x)
-    - F(x; \hat\theta^{(b)}_n)\right) - C_n(x) \Big\vert.
+    - F(x; \hat\theta^{(b)}_n)\right) - K_n(x) \Big\vert.
   \]
   where
-  $C_{n}(x) = \sqrt{n}(\mathbb{E}^{*}[F^{(b)}_n(x)] - 
-  F(x; \theta_0^*))$ is the bias term, and
+  \[
+    K_{n}(x) = \sqrt{n}(\mathbb{E}^{*}[F^{(b)}_n(x)] -
+    F(x; \theta_0^*))
+  \]
+  is the bias term, and
   the expected values $\mathbb{E}^{*}[F^{(b)}_n(x)]$ and
@@
 justify the validity of the NPBB procedure of the KS test.
+Let $f(x; \theta) = {\partial F(x; \theta)} / {\partial \theta}$
+and $f(x, \theta_0)$ be its evaluation at $\theta = \theta_0$.
+Let $d$ be the  dimension of~$\theta$.
 As $1/l+l/n\rightarrow 0$,
@@
   T_n \overset{d}{\rightarrow}
-  \sup_x \big\vert G_{\infty}(x)+f(x;\theta_0)U \big\vert
+  \sup_x \big\vert G_{\infty}(x)+f^\top (x;\theta_0)U \big\vert
 \]
 for some appropriately defined Gaussian process $G_{\infty}(\cdot)$
-and Gaussian random variable  $U$.
+and $d$-dimensional Gaussian random vector $U$.
 Further,  as $1/l+l/n\rightarrow 0$,
@@
 sample size $n \in \{100, 200, 400, 800\}$. Kendall's $\tau$ was chosen as a
-measure of serial dependence as it is invariant to monotone marginal
+measure of serial dependence between $X_i$ and
+$X_{i+1}$ as it is invariant to monotone marginal
 transformations.
@@
 error structures. The specific parameters were chosen because the distributions
-are very similar and their
-first two moments are the same. 
-For the purposes of 
+are very similar and their first two moments are the same. For the purposes of
 evaluating if the test holds it size, when $X_i \sim N(8, 8)$, we tested that the
@@
     generating distribution $\Gamma(8,1)$.}
-  \label{fig:qq}
+  \label{fig:qq_g}
 \end{figure}
 
-Figure~\ref{fig:qq} shows the Quantile-Quantile (Q-Q)
-plots of the p-values testing the marginal distribution of the stationary time
-series generated from the null hypothesis, created with R packages
+Figures~\ref{fig:qq_n}--\ref{fig:qq_g} show Quantile-Quantile (Q--Q) plots
+of the $p$-values testing the marginal distribution of the stationary time
+series generated under the null hypothesis. Figure~\ref{fig:qq_n} corresponds
+to the case where the true data generating distribution is $N(8,8)$, and
+Figure~\ref{fig:qq_g} corresponds to the case where the true data generating
+distribution is $\Gamma(8,1)$. The plots were created using the R packages
 \textsl{qqplotr} and \textsl{ggplot2} \citep{qqplotr, ggplot2}. If the
 distribution of the p-values is uniform, the points will be aligned with the
-diagonal line. The plots suggest that the extent to which the p-values are
-uniformly distributed is dependent on the sample size and the level of serial 
-dependence.
+diagonal line.
+
+The plots suggest that the extent to which the p-values are uniformly
+distributed is dependent on the sample size and the level of serial dependence.
 A small sample size like $n = 100$ or $200$ seems adequate when Kendall's
-$\tau$ is lower than 0.25. For Kendall's $\tau \geq 0.5$, a sample larger than
+$\tau$ has an absolute value $|\tau| \leq 0.25$. For $|\tau| \geq 0.5$, 
+a sample larger than
 $n = 200$ seems necessary for the p-values to be uniformly distributed. For
-Kendall's $\tau \geq 0.75$, a sample larger than $n = 800$ appears to be 
+$|\tau| \geq 0.75$, a sample larger than $n = 800$ appears to be
 necessary, as the p-values are not aligned with the line in any of the Q-Q
-plots. This
-is not necessarily a cause for concern, as (for normal margins)
-a Kendall's $\tau$ corresponds to
-a $\phi$ of 0.924, which is very high.
+plots. This is not necessarily a cause for concern, as (for normal margins)
+a Kendall's $\tau$ of 0.75 corresponds to a $\phi$ of 0.924, which is very high.
 Additionally, positive serial dependence appears to misalign the distribution
@@
 \label{table:size}
-\begin{tabular}{lllrrrrrrr}
+\begin{tabular}{ccc ccc c ccc}
   \toprule
-$F(\cdot; \theta)$ & $n$ & $\alpha$ & $\tau = -0.75$ & $\tau = -0.5$ & $\tau = -0.25$ 
-& $\tau = 0$ & $\tau = 0.25$ & $\tau = 0.5$ & $\tau = 0.75$ \\ 
+$F(\cdot; \theta)$ & $n$ & $\alpha$ & \multicolumn{7}{c}{Kendall's $\tau$}\\
+\cmidrule(lr){4-10}
+   &  &  & $-0.75$ & $ -0.50$ & $-0.25$ & $0.00$ & $0.25$ & $0.50$ & $ 0.75$ \\
   \midrule
@@
 
-% \eds{I think it would be better to show in simulation first (perhaps 
-% in supplemental materials if we are concerned with paper length) that the other
-% methods are not valid or unreliable under this setting, and then 
-% further discredit those results here in the real data analysis.
-% (I would expect a reviewer to ask for this comparison anyway.)}
-% \jy{We could design scenarios where SPBB fails: some dependency
-%   structure that cannot be well-approximated by ARMA. Could do this
-%   if requested.}
-%\eds{I still think this section is weak without supporting simulation evidence.
-%but I am okay with letting this be low-hanging-fruit for a reviewer to request 
-%if we are confident that the SPB will not work well in this situation.}
-
-\section{Conclusions}\label{sec:conclusion}
+\section{Discussion}\label{sec:conclusion}
 
@@
 Overall, the test provides an analog of the bias-corrected NPB KS test of
-\citet{babu2004goodness} in the context of stationaly time
+\citet{babu2004goodness} in the context of stationary time
 series with unspecified serial dependence. Compared to the SPB method
-of \citet{zeimbekakis2022misuses}, which requires a working dependence model, it
+of \citet{zeimbekakis2024misuses}, which requires a working dependence model, it
 is reliable with no need to worry about whether the working dependence
@@
 
-Several promising directions for further research emerge from the findings of
-this study. Firstly, analogous methodologies for other goodness-of-fit tests
-based on empirical distributions, such as the Anderson--Darling and Cramér--von
-Mises tests---which have been shown to outperform the KS test in certain scenarios
-\citep{stephens2017tests}---could be explored. The application of block
-bootstrapping bias correction to these tests could be particularly beneficial in
-environmental studies, such as extreme value modeling, where observations are
-often serially dependent. Secondly, an extension of the proposed NPBB
-one-sample KS test to a two-sample setting would be
-intriguing. This adaptation would test whether two samples originate from the
-same distribution without requiring specification of serial dependencies in
-either sample, maintaining the advantageous feature of the original method.
-Finally, a rigorous theoretical justification of the NPBB method for
-stationary series is of significant academic interest. Establishing
-precise conditions for the asymptotic behavior of the KS statistic and
-the consistency of the bootstrap procedure would offer valuable
-practical insights into the scenarios where the NPBB approach is
-expected to perform optimally.
+The choice of block size is well known to influence the performance of
+block bootstrap methods, particularly for inference on dependent
+data. As pointed out by \citet{hall1995blocking} and
+\citet{lahiri1999theoretical}, the optimal block length depends on the
+strength of serial dependence, and using a uniform choice across
+different dependence settings can lead to size distortion. Several
+data-driven procedures for selecting block size have been proposed,
+including plug-in and cross-validation methods
+\citep{buhlmann2002bootstraps, politis2004automatic}. A more
+comprehensive treatment is given in
+\citet{lahiri2013resampling}. Following these suggestions, we applied
+the automatic block length selection method of
+\citet{politis2004automatic} for circular block bootstrap in our
+context. As reported in the Appendix, the method frequently selected
+block sizes that were overly large—sometimes exceeding the sample
+size—especially under strong serial dependence. This reduced the
+variability of the bootstrap replicates and affected the reliability
+of the test. These observations highlight that while automatic methods
+are attractive in principle, their performance in small to moderate
+samples and in goodness-of-fit settings like ours may be limited.
+
+Several promising directions for further research emerge from
+this study. Firstly, while we used circular block bootstrap, many
+other bootstrap variants for serially dependent data, such as the
+stationary bootstrap \citep{politis1994stationary} and the dependent wild
+bootstrap \citep{shao2010dependent}, could be evaluated under our
+correction framework. Secondly, analogous methodologies could be
+developed for other goodness-of-fit tests based on empirical
+distributions, including the Anderson---Darling and Cramér--von
+Mises tests, which are known to outperform the KS test in certain scenarios
+\citep{stephens2017tests}. Applying block bootstrap bias correction to
+these tests may be particularly beneficial in contexts like extreme
+value modeling, where serial dependence is common. Third, it would be
+intriguing to extend the proposed NPBB
+one-sample KS test to a two-sample setting, allowing for comparison of
+marginal distributions without specifying serial dependencies in
+either sample. Finally, a rigorous theoretical justification of the
+NPBB procedure, including precise conditions for the asymptotic
+behavior of the test statistic and the consistency of the bootstrap
+approximation, would offer valuable practical insights into the
+scenarios where the NPBB approach is expected to perform optimally.
+In particular, while the
+correction term is designed to calibrate the null distribution of the
+test statistic, studying its behavior under alternatives, including
+contiguous alternatives, would further inform the power properties of
+the method and remains an interesting direction for future research.
+
+\appendix
+
+\section{Block Size Investigation}\label{sec:blocksize}
+
+The choice of block size is a key factor influencing the performance
+of block bootstrap methods, particularly in settings with serial
+dependence. While our main simulations used a fixed block size
+$l = \lceil n^{1/3} \rceil$, the optimal block size depends on the
+stength and structure of dependence \citep{hall1995blocking,
+  buhlmann1999block,  politis2004automatic}. Motivated by this, we
+further examined the use of an automatic block-length selection scheme
+as proposed by \citet{politis2004automatic}, which aims to adaptively
+choose the block size based on the data. The simulation settings
+remain the same as in the study reported earlier.
+
+% To address this, we considered  using the automatic block-length selection
+% scheme for circular block bootstrap as described in Section~3.3 of
+% \citet{politis2004automatic}. Unfortunately, using this setting results in
+% the selection of block
+% sizes that can be quite large (sometimes as large or larger than $n$), leading
+% to less variation between the bootstrapped
+% samples. Figures~\ref{fig:large_block}
+% demonstrate that for highly temporally
+% dependent samples (especially when the autocorrelation is negative),
+% the block size is frequently larger than $\sqrt{n}$. For more moderate 
+% positive temporal dependence, the block size may not be overly large
+% as frequently. Still, even for these moderately dependent samples, the 
+% block sizes are almost always larger than $l = \lceil n^{1/3} \rceil$, a setting
+% which was considered optimal by \citep{buhlmann1999block}. This
+% is demonstrated in Figure~\ref{fig:block_dist} with a histogram
+% of the selected block sizes for the 20000 samples with $n = 800$, $\tau = 0.5$, 
+% and $X_i \sim N(8, 8)$.
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[scale=1]{figures/block_dist}
+  \caption{Distribution of the selected block sizes using
+  \citet{politis2004automatic}'s procedure applied to 20000 length-800 time 
+  series with
+    Kendall's $\tau = 0.5$ data generating distribution $N(8,8)$. The vertical
+    dashed line is $l = \lceil n^{1/3} \rceil$ for $n = 800$, which is equivalent 
+    to 10.
+  }
+  \label{fig:block_dist}
+% \end{figure}
+
+% \begin{figure}[tbp]
+  \centering
+  \includegraphics[scale=1]{figures/large_block}
+  \caption{Proportion of selected block sizes using the method of
+  \citet{politis2004automatic} that are larger than
+    $\sqrt{n}$ for $n \in \{100, 200, 400, 800\}$,
+    $\tau \in \{-0.75, -0.5, -0.25, 0, 0.25, 0.5, 0.75\}$, and true marginal distribution
+    $N(8,8)$ and $\Gamma(8,1)$.
+  }
+  \label{fig:large_block}
+\end{figure}
+
+Automatic block size selection tends to yield larger block sizes than our
+fixed choice $l = \lceil n^{1/3} \rceil$, as expected, but under strong
+negative or very strong positive dependence it systematically produces
+block sizes that are excessively large, sometimes as large as or larger
+than $n$. Note that in our simulations, we set the final block size to 
+$\min \{n, \hat l\}$, where
+$\hat l$ is the block size selected by \citet{politis2004automatic}'s
+procedure. Figure~\ref{fig:block_dist} illustrates the typical behavior by
+showing the distribution of block sizes selected by \citet{politis2004automatic}
+for $n = 800$, $\tau = 0.5$, and $X_i \sim N(8,8)$. The majority of selected
+block sizes exceed $\lceil n^{1/3} \rceil$, and many approach or exceed
+$\sqrt{n}$. Figure~\ref{fig:large_block} presents the proportion of selected
+block sizes exceeding $\sqrt{n}$ across varying levels of dependence and sample 
+sizes.
+The selection of block sizes larger than $\sqrt{n}$ occurs systematically under 
+strong
+negative dependence, and is also frequent under very strong positive dependence.
+
+\begin{figure}[tbp]
+  \includegraphics[width = .9\textwidth]{figures/alt_normal}
+  \centering
+  \vspace{-10pt}
+  \caption{Q-Q plots of the p-values testing that a time series
+    have marginal normal distribution with true data generating distribution
+    being $N(8,8)$, when using \citet{politis2004automatic}'s procedure
+    to select block sizes.}
+  \label{fig:alt_qq_n}
+    \hspace{3cm}
+  \includegraphics[width = .9\textwidth]{figures/alt_gamma}
+  \vspace{-5pt}
+  \caption{Q-Q plots of the p-values testing that a time series
+    have marginal gamma distribution with true data generating distribution
+    being $\Gamma(8,1)$, when using \citet{politis2004automatic}'s procedure
+    to select block sizes.}
+  \label{fig:alt_qq_g}
+\end{figure}
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[scale=1]{figures/alt_rr}
+  \caption{Empirical power curve as a function of $\tau$ for
+    $n \in \{100, 200, 400, 800\}$ and true marginal distribution
+    $\in \{N(8,8), \Gamma(8,1)\}$, when using \citet{politis2004automatic}'s 
+    procedure
+    to select block sizes. When the data was generated from $N(8,8)$,
+    we tested for the gamma family. When the data was generated from
+    $\Gamma(8,1)$, we tested for the normal family.
+  }
+  \label{fig:alt_rr}
+\end{figure}
+
+We evaluated the size and power performance of the NPBB test under automatic
+block length selection. The size performance is shown
+in Figures~\ref{fig:alt_qq_n} and \ref{fig:alt_qq_g}, which display Q-Q plots
+of the $p$-values under the null for Normal and Gamma margins, respectively.
+Recall from Figures~\ref{fig:qq_n} and \ref{fig:qq_g} that the cubic root 
+setting holds its size quite well with small $n$ for $|\tau| \leq 0.25$,
+whereas achieving nominal size for $|\tau| \geq 0.5$ require
+$n > 200$, and for $|\tau| \geq 0.75$ require $n > 800$. The automatic
+selection shows similar limitations for $|\tau| > 0.5$, where it does
+not hold its size. Moreover, deviations from the diagonal line appear
+larger for negative $\tau$, likely due to the high proportion of
+occurrence of overly large block sizes. For example, while the cubic
+root setting held its size well at $\tau = -0.25$ with small~$n$, the
+automatic selection does not. At the same time, under $\tau = 0$ or
+$\tau = 0.25$, the method with block size selected by
+\citep{politis2004automatic} maintains reasonable size for moderately
+positively dependent series.
+
+Figure~\ref{fig:alt_rr} shows the power results under automatic selection.
+When compared to Figure~\ref{fig:rr}, the two settings exhibit similar power
+for $|\tau| \leq 0.5$, with the automatic selection sometimes yielding higher
+rejection rates, particularly for smaller negatively dependent samples.
+Overall, while the automatic selection from \citep{politis2004automatic}
+performs reasonably well in certain settings, we recommend caution when using
+it under negative~$\tau$ and smaller sample sizes, where maintaining nominal
+size may be more difficult. In such cases, it may be sensible to apply a more
+restrictive rule when setting the final block size---for example, using
+$\min \{\sqrt{n}, \hat{l}\}$.
 

### 2025-07-22 manuscript/manuscript.tex
addressed minor comments

@@
 estimates this mean.
-Specifically, $\mathbb{E}^*[F_n^{(b)}(x)]$ is the average empirical
-GXSdistribution function over all bootstrap samples, and
+Specifically, $\mathbb{E}^*[F_n^{(b)}(x)]$ is the average empirical distribution function over all bootstrap samples, and
 $\theta^*_0 = \mathbb{E}^*[\hat\theta^{(b)}_n]$ is the average of 
@@
 bootstrap block size introduced in \citet{politis2004automatic}. Results and
-a discussion of this additional simulation are provided in the Appendix.
+a discussion of this additional simulation are provided in a supplement.
 For each setting for $F$, $\tau$, and $n$, we replicate the method 10000 times
@@
 
-% \eds{I think it would be better to show in simulation first (perhaps
-% in supplemental materials if we are concerned with paper length) that the other
-% methods are not valid or unreliable under this setting, and then
-% further discredit those results here in the real data analysis.
-% (I would expect a reviewer to ask for this comparison anyway.)}
-% \jy{We could design scenarios where SPBB fails: some dependency
-%   structure that cannot be well-approximated by ARMA. Could do this
-%   if requested.}
-%\eds{I still think this section is weak without supporting simulation evidence.
-%but I am okay with letting this be low-hanging-fruit for a reviewer to request
-%if we are confident that the SPB will not work well in this situation.}
-
 \section{Discussion}\label{sec:conclusion}
@@
 \citet{politis2004automatic} for circular block bootstrap in our
-context. As reported in the Appendix, the method frequently selected
+context. As reported in the supplement, the method frequently selected
 block sizes that were overly large—sometimes exceeding the sample
@@
 
-\appendix
-
-\section{Block Size Investigation}\label{sec:blocksize}
-
-The choice of block size is a key factor influencing the performance
-of block bootstrap methods, particularly in settings with serial
-dependence. While our main simulations used a fixed block size
-$l = \lceil n^{1/3} \rceil$, the optimal block size depends on the
-stength and structure of dependence \citep{hall1995blocking,
-  buhlmann1999block,  politis2004automatic}. Motivated by this, we
-further examined the use of an automatic block-length selection scheme
-as proposed by \citet{politis2004automatic}, which aims to adaptively
-choose the block size based on the data. The simulation settings
-remain the same as in the study reported earlier.
-
-% To address this, we considered  using the automatic block-length selection
-% scheme for circular block bootstrap as described in Section~3.3 of
-% \citet{politis2004automatic}. Unfortunately, using this setting results in
-% the selection of block
-% sizes that can be quite large (sometimes as large or larger than $n$), leading
-% to less variation between the bootstrapped
-% samples. Figures~\ref{fig:large_block}
-% demonstrate that for highly temporally
-% dependent samples (especially when the autocorrelation is negative),
-% the block size is frequently larger than $\sqrt{n}$. For more moderate 
-% positive temporal dependence, the block size may not be overly large
-% as frequently. Still, even for these moderately dependent samples, the 
-% block sizes are almost always larger than $l = \lceil n^{1/3} \rceil$, a setting
-% which was considered optimal by \citep{buhlmann1999block}. This
-% is demonstrated in Figure~\ref{fig:block_dist} with a histogram
-% of the selected block sizes for the 20000 samples with $n = 800$, $\tau = 0.5$, 
-% and $X_i \sim N(8, 8)$.
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[scale=1]{figures/block_dist}
-  \caption{Distribution of the selected block sizes using
-  \citet{politis2004automatic}'s procedure applied to 20000 length-800 time 
-  series with
-    Kendall's $\tau = 0.5$ data generating distribution $N(8,8)$. The vertical
-    dashed line is $l = \lceil n^{1/3} \rceil$ for $n = 800$, which is equivalent 
-    to 10.
-  }
-  \label{fig:block_dist}
-% \end{figure}
-
-% \begin{figure}[tbp]
-  \centering
-  \includegraphics[scale=1]{figures/large_block}
-  \caption{Proportion of selected block sizes using the method of
-  \citet{politis2004automatic} that are larger than
-    $\sqrt{n}$ for $n \in \{100, 200, 400, 800\}$,
-    $\tau \in \{-0.75, -0.5, -0.25, 0, 0.25, 0.5, 0.75\}$, and true marginal distribution
-    $N(8,8)$ and $\Gamma(8,1)$.
-  }
-  \label{fig:large_block}
-\end{figure}
-
-Automatic block size selection tends to yield larger block sizes than our
-fixed choice $l = \lceil n^{1/3} \rceil$, as expected, but under strong
-negative or very strong positive dependence it systematically produces
-block sizes that are excessively large, sometimes as large as or larger
-than $n$. Note that in our simulations, we set the final block size to 
-$\min \{n, \hat l\}$, where
-$\hat l$ is the block size selected by \citet{politis2004automatic}'s
-procedure. Figure~\ref{fig:block_dist} illustrates the typical behavior by
-showing the distribution of block sizes selected by \citet{politis2004automatic}
-for $n = 800$, $\tau = 0.5$, and $X_i \sim N(8,8)$. The majority of selected
-block sizes exceed $\lceil n^{1/3} \rceil$, and many approach or exceed
-$\sqrt{n}$. Figure~\ref{fig:large_block} presents the proportion of selected
-block sizes exceeding $\sqrt{n}$ across varying levels of dependence and sample 
-sizes.
-The selection of block sizes larger than $\sqrt{n}$ occurs systematically under 
-strong
-negative dependence, and is also frequent under very strong positive dependence.
-
-\begin{figure}[tbp]
-  \includegraphics[width = .9\textwidth]{figures/alt_normal}
-  \centering
-  \vspace{-10pt}
-  \caption{Q-Q plots of the p-values testing that a time series
-    have marginal normal distribution with true data generating distribution
-    being $N(8,8)$, when using \citet{politis2004automatic}'s procedure
-    to select block sizes.}
-  \label{fig:alt_qq_n}
-    \hspace{3cm}
-  \includegraphics[width = .9\textwidth]{figures/alt_gamma}
-  \vspace{-5pt}
-  \caption{Q-Q plots of the p-values testing that a time series
-    have marginal gamma distribution with true data generating distribution
-    being $\Gamma(8,1)$, when using \citet{politis2004automatic}'s procedure
-    to select block sizes.}
-  \label{fig:alt_qq_g}
-\end{figure}
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[scale=1]{figures/alt_rr}
-  \caption{Empirical power curve as a function of $\tau$ for
-    $n \in \{100, 200, 400, 800\}$ and true marginal distribution
-    $\in \{N(8,8), \Gamma(8,1)\}$, when using \citet{politis2004automatic}'s 
-    procedure
-    to select block sizes. When the data was generated from $N(8,8)$,
-    we tested for the gamma family. When the data was generated from
-    $\Gamma(8,1)$, we tested for the normal family.
-  }
-  \label{fig:alt_rr}
-\end{figure}
-
-We evaluated the size and power performance of the NPBB test under automatic
-block length selection. The size performance is shown
-in Figures~\ref{fig:alt_qq_n} and \ref{fig:alt_qq_g}, which display Q-Q plots
-of the $p$-values under the null for Normal and Gamma margins, respectively.
-Recall from Figures~\ref{fig:qq_n} and \ref{fig:qq_g} that the cubic root 
-setting holds its size quite well with small $n$ for $|\tau| \leq 0.25$,
-whereas achieving nominal size for $|\tau| \geq 0.5$ require
-$n > 200$, and for $|\tau| \geq 0.75$ require $n > 800$. The automatic
-selection shows similar limitations for $|\tau| > 0.5$, where it does
-not hold its size. Moreover, deviations from the diagonal line appear
-larger for negative $\tau$, likely due to the high proportion of
-occurrence of overly large block sizes. For example, while the cubic
-root setting held its size well at $\tau = -0.25$ with small~$n$, the
-automatic selection does not. At the same time, under $\tau = 0$ or
-$\tau = 0.25$, the method with block size selected by
-\citep{politis2004automatic} maintains reasonable size for moderately
-positively dependent series.
-
-Figure~\ref{fig:alt_rr} shows the power results under automatic selection.
-When compared to Figure~\ref{fig:rr}, the two settings exhibit similar power
-for $|\tau| \leq 0.5$, with the automatic selection sometimes yielding higher
-rejection rates, particularly for smaller negatively dependent samples.
-Overall, while the automatic selection from \citep{politis2004automatic}
-performs reasonably well in certain settings, we recommend caution when using
-it under negative~$\tau$ and smaller sample sizes, where maintaining nominal
-size may be more difficult. In such cases, it may be sensible to apply a more
-restrictive rule when setting the final block size---for example, using
-$\min \{\sqrt{n}, \hat{l}\}$.
-
 \bigskip

### 2025-07-22 manuscript/supplement.tex
addressed minor comments

--- 2024-07-11 manuscript/supplement.tex
@@
+%&latex
 \documentclass[12pt]{article}
+\usepackage{authblk}
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{booktabs}
+\usepackage{graphicx}
+\usepackage{psfrag,epsf}
+\usepackage{enumerate}
+\usepackage{natbib}
+\usepackage{url} % not crucial - just used below for the URL
+\usepackage{comment}
+\RequirePackage[colorlinks,citecolor=blue,urlcolor=blue]{hyperref}
+\usepackage{setspace}
 
-\usepackage{amsmath}
-\usepackage{graphicx}
-\usepackage{authblk}
-\usepackage{algorithm}
-\usepackage{amsthm}
-\usepackage{amsfonts}
-\usepackage{amssymb}
-\usepackage{algpseudocode}
-\usepackage{bbm}
-\usepackage{bm}
-\usepackage{caption}
-\usepackage{color}
-\usepackage{enumerate}
-\usepackage{enumitem}
-\usepackage{float}
-\usepackage{mathtools}
-\usepackage{makecell}
-\usepackage{multirow}
-\usepackage{hyperref}
-\usepackage{natbib}
-\usepackage{comment}
-\usepackage{longtable}
-\usepackage{rotating}
-\usepackage{xcolor}
-\usepackage{fullpage}
-\usepackage[utf8]{inputenc}
+\newcommand{\jy}[1]{\textcolor{red}{JY: #1}}
+\newcommand{\eds}[1]{\textcolor{blue}{(EDS: #1)}}
+\newcommand{\mc}[1]{\textcolor{green}{(MC: #1)}}
+\newcommand{\xz}[1]{\textcolor{cyan}{(XZ: #1)}}
 
-\newcommand{\mc}[1]{\textcolor{blue}{MC: (#1)}}
+\allowdisplaybreaks
 
-\title{Supporting Information for
-  ``Nonparametric Block Bootstrap Kolmogorov--Smirnov Goodness-of-Fit
-  Test''}
-\author{Mathew Chandy, Elizabeth D. Schifano, Jun Yan, and Xianyang
-  Zhang}
+\usepackage[pagewise]{lineno}
+\linenumbers*[1]
+% patches to make lineno work better with amsmath
+\newcommand*\patchAmsMathEnvironmentForLineno[1]{%
+        \expandafter\let\csname old#1\expandafter\endcsname\csname 
+        #1\endcsname
+        \expandafter\let\csname oldend#1\expandafter\endcsname\csname 
+        end#1\endcsname
+        \renewenvironment{#1}%
+        {\linenomath\csname old#1\endcsname}%
+        {\csname oldend#1\endcsname\endlinenomath}}%
+\newcommand*\patchBothAmsMathEnvironmentsForLineno[1]{%
+        \patchAmsMathEnvironmentForLineno{#1}%
+        \patchAmsMathEnvironmentForLineno{#1*}}%
+\AtBeginDocument{%
+        \patchBothAmsMathEnvironmentsForLineno{equation}%
+        \patchBothAmsMathEnvironmentsForLineno{align}%
+        \patchBothAmsMathEnvironmentsForLineno{flalign}%
+        \patchBothAmsMathEnvironmentsForLineno{alignat}%
+        \patchBothAmsMathEnvironmentsForLineno{gather}%
+        \patchBothAmsMathEnvironmentsForLineno{multline}%
+}
+
+\pdfminorversion=4
+% NOTE: To produce blinded version, replace "0" with "1" below.
+\newcommand{\blind}{0}
+
+% DON'T change margins - should be 1 inch all around.
+\addtolength{\oddsidemargin}{-.5in}%
+\addtolength{\evensidemargin}{-.5in}%
+\addtolength{\textwidth}{1in}%
+\addtolength{\textheight}{1.3in}%
+\addtolength{\topmargin}{-.8in}%
 
 \begin{document}
+
+%\bibliographystyle{natbib}
+
+\def\spacingset#1{\renewcommand{\baselinestretch}%
+{#1}\small\normalsize} \spacingset{1}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\title{\bf Supplement: Performance of Nonparametric
+Block Bootstrap Kolmogorov-Smirnov Test with Block Size Calibration}
+\if0\blind
+{
+  \author[1,2]{Mathew Chandy}
+  \author[1]{Elizabeth D. Schifano}
+  \author[1]{Jun Yan\thanks{
+    The authors gratefully acknowledge the National Science Foundation (NSF).}\hspace{.2cm}}
+  \author[3]{Xianyang Zhang$^{\ast}$ }
+  \affil[1]{Department of Statistics, University of Connecticut}
+  \affil[2]{Department of Statistics and Data Science, University of California, Los Angeles}
+  \affil[3]{Department of Statistics, Texas A\&M University}
+  \maketitle
+} \fi
+
+\if1\blind
+{
+  \bigskip
+  \bigskip
+  \bigskip
+  \author{Anonymous Author}
+} \fi
+
 \maketitle
 
-\section{Asymptotic Limit of the KS Statistic}
+The choice of block size is a key factor influencing the performance
+of block bootstrap methods, particularly in settings with serial
+dependence. While our main simulations used a fixed block size
+$l = \lceil n^{1/3} \rceil$, the optimal block size depends on the
+stength and structure of dependence \citep{hall1995blocking,
+  buhlmann1999block,  politis2004automatic}. Motivated by this, we
+further examined the use of an automatic block-length selection scheme
+as proposed by \citet{politis2004automatic}, which aims to adaptively
+choose the block size based on the data. The simulation settings
+remain the same as in the study reported earlier.
 
-\begin{proof}[Proof of Proposition~1]
-We first derive the limiting distribution of the KS statistic under the null. 
-Suppose $\hat{\theta}_n$ admits the expansion:
-\begin{align}\label{eq-expan}
-\hat{\theta}_n-\theta_0 = \frac{1}{n}\sum^{n}_{i=1}h(X_i;\theta_0) + 
-\frac{1}{\sqrt{n}}R_n,    
-\end{align}
-where $h(\cdot;\theta_0)$ is the influence function with 
-$\mathbb{E}[h(X_i;\theta_0)]=0$ and $R_n$ is the remainder term satisfying that
-$R_n\overset{p}{\rightarrow} 0.$ Write $G_n(x):=\sqrt{n}(F_n(x) - 
-F(x; \theta_0))$ 
-and let $f(x;\theta)=\partial F(x;\theta)/\partial \theta$. We assume 
-$\theta \in \mathbb{R}$ for ease of presentation.
+% To address this, we considered  using the automatic block-length selection
+% scheme for circular block bootstrap as described in Section~3.3 of
+% \citet{politis2004automatic}. Unfortunately, using this setting results in
+% the selection of block
+% sizes that can be quite large (sometimes as large or larger than $n$), leading
+% to less variation between the bootstrapped
+% samples. Figures~\ref{fig:large_block}
+% demonstrate that for highly temporally
+% dependent samples (especially when the autocorrelation is negative),
+% the block size is frequently larger than $\sqrt{n}$. For more moderate 
+% positive temporal dependence, the block size may not be overly large
+% as frequently. Still, even for these moderately dependent samples, the 
+% block sizes are almost always larger than $l = \lceil n^{1/3} \rceil$, a setting
+% which was considered optimal by \citep{buhlmann1999block}. This
+% is demonstrated in Figure~\ref{fig:block_dist} with a histogram
+% of the selected block sizes for the 20000 samples with $n = 800$, $\tau = 0.5$, 
+% and $X_i \sim N(8, 8)$.
 
-\paragraph{Finite-dimensional convergence of $G_n(x_1),\dots,G_n(x_m)$}
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[scale=1]{figures/block_dist}
+  \caption{Distribution of the selected block sizes using
+  \citet{politis2004automatic}'s procedure applied to 20000 length-800 time 
+  series with
+    Kendall's $\tau = 0.5$ data generating distribution $N(8,8)$. The vertical
+    dashed line is $l = \lceil n^{1/3} \rceil$ for $n = 800$, which is equivalent 
+    to 10.
+  }
+  \label{fig:block_dist}
+% \end{figure}
 
-We assume that the sequence \(\{X_i\}\) is strictly stationary and satisfies a 
-strong mixing condition. This condition ensures that the dependence between 
-\(X_i\) and \(X_{i+h}\) weakens sufficiently fast as \(h\) increases.
+% \begin{figure}[tbp]
+  \centering
+  \includegraphics[scale=1]{figures/large_block}
+  \caption{Proportion of selected block sizes using the method of
+  \citet{politis2004automatic} that are larger than
+    $\sqrt{n}$ for $n \in \{100, 200, 400, 800\}$,
+    $\tau \in \{-0.75, -0.5, -0.25, 0, 0.25, 0.5, 0.75\}$, and true marginal distribution
+    $N(8,8)$ and $\Gamma(8,1)$.
+  }
+  \label{fig:large_block}
+\end{figure}
 
-We aim to show that for any fixed \( x_1, \ldots, x_m \), the vector
-\( (G_n(x_1), \ldots, G_n(x_m)) \) converges in distribution to a
-multivariate normal vector \( (G_{\infty}(x_1), \ldots,
-G_{\infty}(x_m)) \) with mean zero and covariance structure given by:
-\[
-\text{Cov}(G_{\infty}(x_i), G_{\infty}(x_j)) = \sum_{h=-\infty}^{\infty} \text{Cov}(\mathbf{1}\{X_0 \leq x\}, \mathbf{1}\{X_h \leq x^{\prime}\}),
-\]
-where $ \mathbf{1}\{\cdot\}$ is the indicator
-function.
+Automatic block size selection tends to yield larger block sizes than our
+fixed choice $l = \lceil n^{1/3} \rceil$, as expected, but under strong
+negative or very strong positive dependence it systematically produces
+block sizes that are excessively large, sometimes as large as or larger
+than $n$. Note that in our simulations, we set the final block size to 
+$\min \{n, \hat l\}$, where
+$\hat l$ is the block size selected by \citet{politis2004automatic}'s
+procedure. Figure~\ref{fig:block_dist} illustrates the typical behavior by
+showing the distribution of block sizes selected by \citet{politis2004automatic}
+for $n = 800$, $\tau = 0.5$, and $X_i \sim N(8,8)$. The majority of selected
+block sizes exceed $\lceil n^{1/3} \rceil$, and many approach or exceed
+$\sqrt{n}$. Figure~\ref{fig:large_block} presents the proportion of selected
+block sizes exceeding $\sqrt{n}$ across varying levels of dependence and sample 
+sizes.
+The selection of block sizes larger than $\sqrt{n}$ occurs systematically under 
+strong
+negative dependence, and is also frequent under very strong positive dependence.
 
-Given any $x_1,\dots,x_m$ in the domain of $F$, by the CLT for weakly dependent 
-time series, we have the joint convergence of 
-$V_n:=(G_n(x_1),\dots,G_n(x_m),\sqrt{n}(\hat{\theta}_n-\theta_0))$
-to some Gaussian limit, with the covariance matrix being 
-$\Sigma_{m+1}=\lim_{n\rightarrow+\infty}\text{Cov}(V_n)$.
-Consider the empirical process $ G_n(x) = \sqrt{n} (F_n(x) - F(x)) $, where 
-$ F_n(x) $ is the empirical distribution function based on $ X_1, \ldots, 
-X_n $. To show finite-dimensional convergence, we need to establish that for 
-any fixed $ x_1, \ldots, x_m $, the vector $ (G_n(x_1), \ldots, G_n(x_m)) $ 
-converges in distribution to a multivariate normal distribution.
-The empirical distribution function can be written as
-$
-F_n(x) = \frac{1}{n} \sum_{t=1}^n \mathbf{1}\{X_i \leq x\}.
-$
-Therefore, the empirical process is:
-\[
-G_n(x) = \sqrt{n} (F_n(x) - F(x)) = \frac{1}{\sqrt{n}} \sum_{i=1}^n 
-(\mathbf{1}\{X_i \leq x\} - F(x)).
-\]
+\begin{figure}[tbp]
+  \includegraphics[width = .9\textwidth]{figures/alt_normal}
+  \centering
+  \vspace{-10pt}
+  \caption{Q-Q plots of the p-values testing that a time series
+    have marginal normal distribution with true data generating distribution
+    being $N(8,8)$, when using \citet{politis2004automatic}'s procedure
+    to select block sizes.}
+  \label{fig:alt_qq_n}
+    \hspace{3cm}
+  \includegraphics[width = .9\textwidth]{figures/alt_gamma}
+  \vspace{-5pt}
+  \caption{Q-Q plots of the p-values testing that a time series
+    have marginal gamma distribution with true data generating distribution
+    being $\Gamma(8,1)$, when using \citet{politis2004automatic}'s procedure
+    to select block sizes.}
+  \label{fig:alt_qq_g}
+\end{figure}
 
-To establish the asymptotic distribution of $ G_n(x) $, we consider the vector 
-\[
-(G_n(x_1), \ldots, G_n(x_m)) = \frac{1}{\sqrt{n}} \sum_{i=1}^n (\mathbf{1}\{X_i \leq x_1\} - 
-F(x_1), \ldots, \mathbf{1}\{X_i \leq x_m\} - F(x_m)).
-\]
-We calculate the covariance structure of the limiting distribution. The 
-covariance between $ G_n(x) $ and $ G_n(x^{\prime}) $ is:
-\[
-\text{Cov}(G_n(x), G_n(x^{\prime})) = \frac{1}{n} \sum_{t=1}^n \sum_{s=1}^n 
-\text{Cov}(\mathbf{1}\{X_t \leq x\}, \mathbf{1}\{X_t \leq x^{\prime}\}).
-\]
-Since $ \{X_i\} $ is strictly stationary, the covariance depends only on the 
-lag $ h = |t-s| $:
-\[
-\text{Cov}(\mathbf{1}\{X_t \leq x\}, \mathbf{1}\{X_t \leq x^{\prime}\}) = \text{Cov}(\mathbf{1}\{X_h \leq x\}, 
-\mathbf{1}\{X_0 \leq x^{\prime}\}).
-\]
-Thus, the covariance can be expressed as
-\[
-\text{Cov}(G_n(x), G_n(x')) = \frac{1}{n} \sum_{t=1}^n \sum_{h=-t+1}^{n-t} 
-\text{Cov}(\mathbf{1}\{X_h \leq x\}, 
-\mathbf{1}\{X_0 \leq x^{\prime}\}).
-\]
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[scale=1]{figures/alt_rr}
+  \caption{Empirical power curve as a function of $\tau$ for
+    $n \in \{100, 200, 400, 800\}$ and true marginal distribution
+    $\in \{N(8,8), \Gamma(8,1)\}$, when using \citet{politis2004automatic}'s 
+    procedure
+    to select block sizes. When the data was generated from $N(8,8)$,
+    we tested for the gamma family. When the data was generated from
+    $\Gamma(8,1)$, we tested for the normal family.
+  }
+  \label{fig:alt_rr}
+\end{figure}
 
-By the mixing condition, the covariances
-$ \text{Cov}(\mathbf{1}\{X_h \leq x\}, \mathbf{1}\{X_0 \leq x^{\prime}\}) $ 
-decay sufficiently fast as $ h \to \infty $. Therefore, the sum converges to:
-\[
-  \lim_{n \to \infty} \text{Cov}(G_n(x), G_n(x'))
-  = \sum_{h=-\infty}^{\infty} \text{Cov}(\mathbf{1}\{X_h \leq x\}, 
-  \mathbf{1}\{X_0 \leq x^{\prime}\}).
-\]
+We evaluated the size and power performance of the NPBB test under automatic
+block length selection. The size performance is shown
+in Figures~\ref{fig:alt_qq_n} and \ref{fig:alt_qq_g}, which display Q-Q plots
+of the $p$-values under the null for Normal and Gamma margins, respectively.
+Recall from Figures~\ref{fig:qq_n} and \ref{fig:qq_g} that the cubic root 
+setting holds its size quite well with small $n$ for $|\tau| \leq 0.25$,
+whereas achieving nominal size for $|\tau| \geq 0.5$ require
+$n > 200$, and for $|\tau| \geq 0.75$ require $n > 800$. The automatic
+selection shows similar limitations for $|\tau| > 0.5$, where it does
+not hold its size. Moreover, deviations from the diagonal line appear
+larger for negative $\tau$, likely due to the high proportion of
+occurrence of overly large block sizes. For example, while the cubic
+root setting held its size well at $\tau = -0.25$ with small~$n$, the
+automatic selection does not. At the same time, under $\tau = 0$ or
+$\tau = 0.25$, the method with block size selected by
+\citep{politis2004automatic} maintains reasonable size for moderately
+positively dependent series.
 
-\paragraph{Tightness of $G_n(x)$}
+Figure~\ref{fig:alt_rr} shows the power results under automatic selection.
+When compared to Figure~\ref{fig:rr}, the two settings exhibit similar power
+for $|\tau| \leq 0.5$, with the automatic selection sometimes yielding higher
+rejection rates, particularly for smaller negatively dependent samples.
+Overall, while the automatic selection from \citep{politis2004automatic}
+performs reasonably well in certain settings, we recommend caution when using
+it under negative~$\tau$ and smaller sample sizes, where maintaining nominal
+size may be more difficult. In such cases, it may be sensible to apply a more
+restrictive rule when setting the final block size---for example, using
+$\min \{\sqrt{n}, \hat{l}\}$.
 
-Moreover, we can show the tightness of the process $G_n(s)$. 
-We want to show that for every $\epsilon > 0$,
-\[
-\lim_{\delta \to 0} \limsup_{n \to \infty} \mathbb{P}\left( \omega_{G_n}(\delta) 
-\geq \epsilon \right) = 0,
-\]
-where the modulus of continuity $\omega_{G_n}(\delta)$ is defined as
-\citep{billingsley2013convergence}.
-\[
-\omega_{G_n}(\delta) = \sup_{|s - t| < \delta} |G_n(s) - G_n(t)|.
-\]
-For sufficiently small $\delta$, and leveraging the properties of weakly 
-dependent sequences, we can show that
-\[
-  \sup_{|s - t| < \delta} |G_n(s) - G_n(t)|
-  = \sup_{|s - t| < \delta}  \sqrt{n}|(F_n(s) - F(s)) - (F_n(t) - F(t))|
-\]
-is small with high probability.
-For $ |s - t| < \delta $,
-\[
-|G_n(s) - G_n(t)| = \sqrt{n} \left| (F_n(s) - F(s; \theta_0)) - (F_n(t) - 
-F(t; \theta_0)) \right|.
-\]
-This can be decomposed as:
-\[
-|G_n(s) - G_n(t)| = \sqrt{n} \left| (F_n(s) - F_n(t)) - (F(s; \theta_0) - 
-F(t; \theta_0)) \right|.
-\]
-
-Remember that $F_n(t) = \sum_{i=1}^n  \mathbf{1}\{X_i \le t\} / n$. Then, for 
-$ |s - t| < \delta $, the difference $ F_n(s) - F_n(t) $ can be written as
-\[
-  F_n(s) - F_n(t) = \frac{1}{n}
-  \sum_{i=1}^n \left( \mathbf{1}\{X_i \leq s\} - \mathbf{1}\{X_i \leq t\} \right),
-\]
-or as 
-$ \mathbb{E}\left[ \frac{1}{n} \sum_{i=1}^n \mathbf{1}\{ t < X_i \leq s \} 
-\right] $. To provide a more precise bound on $ F_n(s) - F_n(t) $, we use 
-Hoeffding's inequality, which states that for any $ t > 0 $,
-\[
-  \mathbb{P}\left( \left| \frac{1}{n} \sum_{i=1}^n \mathbf{1}\{ t < X_i \leq s \} - 
-      \mathbb{E}\left[ \frac{1}{n} \sum_{i=1}^n \mathbf{1}\{ t < X_i \leq s \} 
-      \right] \right| > t \right) \leq 2 \exp\left( -2nt^2 \right).
-\]
-
-Since 
-\[ \mathbb{E}\left[ \frac{1}{n} \sum_{i=1}^n \mathbf{1}\{ t < X_i \leq s \} 
-\right] = F(s; \theta_0) - F(t; \theta_0),
-\]
-we have:
-\[
-  \mathbb{P}\left( \left| \frac{1}{n} \sum_{i=1}^n \mathbf{1}\{ t < X_i \leq s \} - 
-      (F(s; \theta_0) - F(t; \theta_0)) \right| > t \right) \leq
-  2\exp\left( -2nt^2 \right).
-\]
-Because the true CDF is continuous, by definition,
-$ F(s; \theta_0) $, for any $ \epsilon > 0 $,
-there exists a $ \delta > 0 $ such that for $ |s - t| < \delta $,
-$ |F(s; \theta_0) - F(t; \theta_0)| < \epsilon. $
-Using the bound from Hoeffding's inequality, we have:
-\[
-  \mathbb{P}\left( |F_n(s) - F_n(t) - (F(s; \theta_0) - F(t; \theta_0))| \geq 
-    \epsilon \right) \leq 2 \exp\left( -2n\epsilon^2 \right).
-\]
-Then, for sufficiently large $ n $ and small $ \delta $,
-$ \mathbb{P}\left( \omega_{G_n}(\delta) \geq \epsilon \right) \leq 2 
-\exp\left( -2n\epsilon^2 \right). $ Taking limits, we conclude:
-$ \lim_{\delta \to 0} \limsup_{n \to \infty} \mathbb{P}\left( 
-\omega_{G_n}(\delta) \geq \epsilon \right) = 0. $
-
-\paragraph{Convergence in distribution}
-Therefore, we have
-\begin{align*}
-\begin{pmatrix}
-G_n(x)  \\ 
-\sqrt{n}(F(x;\hat{\theta}_n)-F(x;\theta_0))
-\end{pmatrix}\Rightarrow
-\begin{pmatrix}
-G_{\infty}(x) \\
-f(x;\theta_0)U
-\end{pmatrix}
-\end{align*}
-jointly, where $G_{\infty}(x)$ is a Gaussian process with the covariance 
-function defined as
-\begin{align*}
-\text{Cov}(G_{\infty}(x),G_{\infty}(x'))=& 
-\lim_{n\rightarrow+\infty}\frac{1}{n}\sum^{n}_{i,j=1}
-\text{Cov}(\mathbf{1}\{X_i\leq x\},\mathbf{1}\{X_j\leq x'\})
-\\=& \sum^{+\infty}_{h=-\infty}\text{Cov}(\mathbf{1}\{X_{h}\leq x\},
-\mathbf{1}\{X_0\leq x'\}),
-\end{align*}
-and $U\sim N(0,s^2)$ with 
-\begin{align*}
-s^2=\lim_{n\rightarrow+\infty}\frac{1}{n}\sum^{n}_{i,j=1}\text{Cov}(h(X_i,
-\theta_0),h(X_j;\theta_0))
-= \sum^{+\infty}_{h=-\infty}\text{Cov}(h(X_{h},\theta_0),h(X_0;\theta_0)),
-\end{align*}
-and the covariance between $U$ and $G_{\infty}(x)$ is given by
-\begin{align*}
-\text{Cov}(U,G_\infty(x))=&\lim_{n\rightarrow+\infty}
-\frac{1}{n}\sum^{n}_{i,j=1}\text{Cov}(h(X_i,\theta_0),\mathbf{1}\{X_j\leq x\})
-\\=&\sum^{+\infty}_{h=-\infty}
-\text{Cov}(h(X_{h},\theta_0),\mathbf{1}\{X_0\leq x\}).
-\end{align*}
-By the continuous mapping theorem, we obtain
-\begin{align*}
-T_n \overset{d}{\rightarrow} \sup_x |G_{\infty}(x)+f(x;\theta_0)U|.    
-\end{align*}
-
-\end{proof}
-
-\section{Bootstrap Consistency}
-
-Denote by $\mathbb{E}^{(b)}$, $\text{Var}^{(b)}$ and $\text{Cov}^{(b)}$
-the expectation, variance and covariance conditional on 
-$\{X_i: i = 1, \ldots, n\}$ in 
-the bootstrap world. Assuming that $n=kl$ with $l$ being the block size and $k$ 
-being the number of blocks, the bootstrap marginal distribution is 
-\begin{align*}
-\rho_n^{(b)}=\frac{1}{n}\sum^{k}_{j=1}\sum^{S_j+l-1}_{i=S_j} \delta_{X_i},    
-\end{align*}
-where $\delta_x$ denotes a point mass at $x$, and $S_1,\dots,S_k$ are i.i.d 
-uniform on $\{1,\dots,n-l+1\}$. 
-Define $G_n^{(b)}(x)$ in the same way as $G_n(x)$ with $X_1, \dots, X_n$ being 
-replaced by the bootstrap samples $X_1^{(b)},\dots,X_n^{(b)}.$
-
-\begin{proof}[Proof of Proposition~2]
-    We want to show that
-\begin{align}\label{eq-con-boot}
-\begin{pmatrix}
-G_n^{(b)}(x)  \\ 
-\sqrt{n}(F(x;\hat{\theta}_n^{(b)})-F(x;\hat{\theta}_0))
-\end{pmatrix}\Rightarrow^{*}
-\begin{pmatrix}
-G_{\infty}(x) \\
-f(x;\theta_0)U
-\end{pmatrix}
-\end{align}
-where $\Rightarrow^*$ means convergence in distribution almost surely and 
-$\hat{\theta}_0:=\mathbb{E}^{(b)}[\hat{\theta}_n^{(b)}]$. 
-In the bootstrap world, we have an expansion similar to (\ref{eq-expan}):
-\begin{align*}
-\hat{\theta}_n^{(b)}-\hat{\theta}_0 = \frac{1}{n}\sum^{n}_{i=1}h(X_i^{(b)};
-\hat{\theta}_0) + \frac{1}{\sqrt{n}}R_n^{(b)},    
-\end{align*}
-where $R_n^{(b)} \overset{p^*}{\rightarrow} 0$, where 
-$\overset{p^*}{\rightarrow}$ means convergence in probability almost surely. 
-Note that 
-\begin{align*}
-\mathbb{E}^{(b)}\left[\frac{1}{n}\sum^{n}_{i=1}h(X_i^{(b)};
-\hat{\theta}_0)\right]
-=&\frac{1}{n}\sum^{k}_{j=1}\mathbb{E}^{(b)}\left[\sum^{S_j+l-1}_{i=S_j}h(X_{i};
-\hat{\theta}_0)\right]
-\\=&\frac{k}{n^2}[\sum^{n - l + 1}_{j=1}\sum^{j+l-1}_{i=j}h(X_{i};
-\hat{\theta}_0) +
-\sum^{n}_{j=n - l + 2}[\sum^{n}_{i=j}h(X_{i};\hat{\theta}_0) +
-\sum^{j - n + l -1}_{i=1}h(X_{i};\hat{\theta}_0)]]
-\\=&\frac{k}{n^2}\sum^{n}_{i=1}l h(X_{i};\hat{\theta}_0).
-\end{align*}
-
-Moreover, we have
-\begin{align*}
-\text{var}^{(b)}\left(\frac{1}{\sqrt{n}}\sum^{n}_{i=1}h(X_i^{(b)};
-\theta_0^{(b)})\right)
-=&\text{var}^{(b)}\left(\frac{1}{\sqrt{n}}\sum^{k}_{j=1}\sum^{S_j+l-1}_{i=S_j}
-h(X_{i};\hat{\theta}_0)\right)
-\\=&\frac{1}{l}\text{var}^{(b)}\left(\sum^{S_1+l-1}_{i=S_1}h(X_{i};
-\hat{\theta}_0)\right)
-\\=&\frac{1}{ln}\sum^{n}_{t=1}(W_t-\bar{W})^2
-\end{align*}
-with
-\[
-  W_t=
- \begin{cases}
-\sum^{t+l-1}_{i=t}h(X_i;\hat{\theta}_0)  & \text{if } t \leq n - 1 + 1,\\
-\sum^{n}_{i=t}h(X_{i};\hat{\theta}_0) +
-\sum^{t - n + l -1}_{i=1}h(X_{i};\hat{\theta}_0)  & \text{if } t \geq n - 1 + 2
-\end{cases}
-\]
-and $\bar{W}=\sum^{n}_{t=1}W_t/n$,
-which is expected to converge to $s^2$ almost surely.
-
-Similar calculations apply 
-to $G_n^{(b)}(x)$ and we expect that
-\begin{align*}
-&\text{Cov}^{(b)}(G_n^{(b)}(x),G_n^{(b)}(x'))\overset{a.s.}{\rightarrow}   
-\sum^{+\infty}_{h=-\infty}
-\text{Cov}(\mathbf{1}\{X_{h}\leq x\},\mathbf{1}\{X_0\leq x'\}),\\
-&\text{Cov}^{(b)}\left(\frac{1}{\sqrt{n}}\sum^{n}_{i=1}h(X_i^{(b)};
-\hat{\theta}_0), G_n^{(b)}(x)\right)\overset{a.s.}{\rightarrow} 
-\sum^{+\infty}_{h=-\infty}\text{Cov}(h(X_{h},\theta_0),\mathbf{1}\{X_0\leq x\}).
-\end{align*}
-By showing the finite-dimensional convergence and tightness in the bootstrap 
-world (conditional on the data $\{X_i: i = 1, \ldots, n\}$), we can establish 
-\eqref{eq-con-boot}.
-From the CLT, the process $G_n^{(b)}(x) = \sqrt{n}(F_n^{(b)}(x) - F_n(x))$ 
-converges  to $G_{\infty}(x)$.
-
-\paragraph{Finite-Dimensional Convergence in the Bootstrap World}
-
-For $\sqrt{n}(F(x;\hat{\theta}_n^{(b)}) - F(x;\hat{\theta}_0))$, using the 
-first-order Taylor 
-expansion around $\hat{\theta}_0$ similarly to what was done in 
-\citet{kunsch1989jackknife}, we have:
-$
-F(x;\hat{\theta}_n^{(b)}) \approx F(x;\hat{\theta}_0) + f(x; 
-\hat{\theta}_0) (\hat{\theta}_n^{(b)} - \hat{\theta}_0),
-$ so
-$
-\sqrt{n}(F(x;\hat{\theta}_n^{(b)}) - F(x;\hat{\theta}_0)) \approx \sqrt{n} 
-(F(x;\hat{\theta}_0) + f(x; 
-\hat{\theta}_0) (\hat{\theta}_n^{(b)} - \hat{\theta}_0) - F(x;\hat{\theta}_0)) 
-\approx
-f(x; 
-\hat{\theta}_0) \sqrt{n} (\hat{\theta}_n^{(b)} - \hat{\theta}_0).
-$
-
-Substituting the expansion of $\hat{\theta}_n^{(b)}$:
-$
-\sqrt{n} (\hat{\theta}_n^{(b)} - \hat{\theta}_0) = \frac{1}{\sqrt{n}} 
-\sum_{i=1}^{n} 
-h(X_i^{(b)}; \hat{\theta}_0) + R_n^{(b)}.
-$
-
-Since $R_n^{(b)} \overset{p^{(b)}}{\rightarrow} 0$, 
-$
-\sqrt{n}(F(x;\hat{\theta}_n^{(b)}) - F(x;\hat{\theta}_0)) \approx 
-f(x; \hat{\theta}_0) \left( \frac{1}{\sqrt{n}} \sum_{i=1}^{n} h(X_i^{(b)}; 
-\hat{\theta}_0) \right).
-$
-
-The term $\frac{1}{\sqrt{n}} \sum_{i=1}^{n} h(X_i^{(b)}; \hat{\theta}_0)$ 
-converges in distribution to a normal random variable $U$ with variance 
-$s^2$.
-
-\paragraph{Tightness in Bootstrap World}
-
-\end{proof}
-
-\bibliographystyle{chicago} 
+\bibliographystyle{asa}
 \bibliography{citations}
-
 \end{document}

### 2025-07-28 manuscript/manuscript.tex
plots with different bias correction

@@
 
-This approach extends the logic of \citet{babu2004goodness}, who
-introduced a similar correction for independent data, to the context
-of serially dependent time series via block bootstrapping.
-The bias correction term $C_n(x)$ used in the NPB method for
-independent data could, in principle, also be approximated by a
-bootstrap expectation in the same way as $K_n(x)$.
-Nonetheless, under independence, the empirical distribution $F_n(x)$
-and the parameter estimate $\hat{\theta}_n$ are already reliable, so
-direct calculation of $C_n(x)$ is both simpler and sufficient. The use
-of bootstrap expectations as in $K_n(x)$ becomes necessary only when
-serial dependence distorts the properties of $F_n(x)$, making
-block-bootstrapping-based bias estimation essential.
+To show that better performance is achieved when using the $K_n(x)$ correction
+instead of the $C_n(x)$, we have ad
+
+% This approach extends the logic of \citet{babu2004goodness}, who
+% introduced a similar correction for independent data, to the context
+% of serially dependent time series via block bootstrapping.
+% The bias correction term $C_n(x)$ used in the NPB method for
+% independent data could, in principle, also be approximated by a
+% bootstrap expectation in the same way as $K_n(x)$.
+% Nonetheless, under independence, the empirical distribution $F_n(x)$
+% and the parameter estimate $\hat{\theta}_n$ are already reliable, so
+% direct calculation of $C_n(x)$ is both simpler and sufficient. The use
+% of bootstrap expectations as in $K_n(x)$ becomes necessary only when
+% serial dependence distorts the properties of $F_n(x)$, making
+% block-bootstrapping-based bias estimation essential.
 

### 2025-07-28 code/bias_correction_analysis.R

@@ -1,0 +1,74 @@
+source('functions.R')
+my_data <- readRDS('../data/results_10000_C_n.RDS')
+
+my_data$tau <- case_when(my_data$phi == -0.9238795 ~ -0.75,
+                         my_data$phi == -0.7071068 ~ -0.5,
+                         my_data$phi == -0.3826834 ~ -0.25,
+                         my_data$phi == 0 ~ 0,
+                         my_data$phi == 0.9238795 ~ 0.75,
+                         my_data$phi == 0.7071068 ~ 0.5,
+                         my_data$phi == 0.3826834 ~ 0.25)
+
+my_data$dist <- factor(case_when(my_data$true_dist == "normal" ~ "N(8,8)",
+                                 my_data$true_dist == "gamma" ~ "Gamma(8,1)"))
+
+my_data$my_n <- factor(case_when(my_data$n == 100 ~ "n == 100",
+                                 my_data$n == 200 ~ "n == 200",
+                                 my_data$n == 400 ~ "n == 400",
+                                 my_data$n == 800 ~ "n == 800"))
+
+
+gg.f <- ggplot(data = my_data %>% 
+                 filter(truth == 'null', true_dist == 'normal'), 
+               mapping = aes(sample = p)) +
+  scale_x_continuous(breaks=c(0, 1)) +
+  scale_y_continuous(breaks=c(0, 1)) + 
+  stat_pp_band(distribution = "unif") +
+  stat_pp_line() +
+  stat_pp_point(distribution = "unif", cex = .1) +
+  facet_grid(rows = vars(n), cols = vars(tau),
+             labeller = label_parsed) +
+  labs(x = "Theoretical Cumulative Distribution", 
+       y = "Empirical Cumulative Distribution") +
+  coord_fixed() +
+  theme(strip.text.x = element_text(size = 8))
+ggsave(filename = 'normal_C_n.pdf', plot = gg.f, 
+       path = "../manuscript/figures", height = 4, width = 6)
+
+gg.f <- ggplot(data = my_data %>% 
+                 filter(truth == 'null', true_dist == 'gamma'), 
+               mapping = aes(sample = p)) +
+  scale_x_continuous(breaks=c(0, 1)) +
+  scale_y_continuous(breaks=c(0, 1)) + 
+  stat_pp_band(distribution = "unif") +
+  stat_pp_line() +
[…]

### 2025-09-22 manuscript/manuscript.tex
new reply letter

@@
 
-To show that better performance is achieved when using the $K_n(x)$ correction
-instead of the $C_n(x)$, we have ad
-
 % This approach extends the logic of \citet{babu2004goodness}, who
@@
 a discussion of this additional simulation are provided in a supplement.
+We also compared empirical performance for the block bootstrap KS test when using the $K_n(x)$ correction
+versus the $C_n(x)$. The $K_n(x)$ correction was used
+in the main manuscript whereas results and a discussion for the
+$C_n(x)$ correction is included in the supplement.
 For each setting for $F$, $\tau$, and $n$, we replicate the method 10000 times

### 2025-09-22 manuscript/reply2.tex
new reply letter

\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{natbib}
\usepackage{hyperref}

\usepackage{listings}
\usepackage{rotating, graphicx}
\graphicspath{{./}, {./image/}}
\usepackage{booktabs, natbib}
% \usepackage{breakurl}
% \usepackage [english]{babel}
\usepackage{amsmath, amsbsy, amsthm, epsfig, epsf, psfrag, graphicx, 
amssymb, enumerate}
\usepackage{bm}
\usepackage{multirow, multicol}

\usepackage[dvipsnames]{color}
\definecolor{darkblue}{rgb}{0.1, 0.2, 0.6}

\newcommand{\jy}[1]{\textcolor{red}{JY: #1}}
\newcommand{\eds}[1]{\textcolor{blue}{(EDS: #1)}}
\newcommand{\mc}[1]{\textcolor{green}{(MC: #1)}}
\newcommand{\xz}[1]{\textcolor{cyan}{(XZ: #1)}}

\sloppy

% \usepackage{csquotes}
% \usepackage [autostyle, english = american]{csquotes}
% \MakeOuterQuote{"}

% \usepackage{bibentry}
\newenvironment{comment}%
{\begin{quotation}\noindent\small\it\color{darkblue}\ignorespaces%
}{\end{quotation}}

\begin{document}

\begin{center}
  {\Large\bf Response to the Comments}
\end{center}

We thank the Editor and Associate Editor for the opportunity to add further detail to our manuscript.
We have taken the revision process seriously in order
to meet the expectations for final acceptance.

The revised manuscript incorporates the following notable change:
\begin{enumerate}
\item A supplement has been added, which includes both
our previous exploration of automatic block size selection as
well as our new simulations for block bootstrap under
\citet{babu2004goodness}'s bias correction.
\end{enumerate}

Point-by-point responses to the comments are as follows, with the
comments quoted in \emph{\color{darkblue} italic and blue}.

\subsection*{To AE}

\begin{comment}
The paper is improved from the first submission.

I would still like a little bit of clarification about the bias correction $K_n(x)$ versus the bias correction $C_n(x)$. I understand that $K_n(x)$, which the authors prescribe under the circular blocks bootstrap, is based on bootstrap expectations $E_*$ of the bootstrap parameter estimate as well as of the bootstrap empirical cdf. In contract, the bias term $C_n(x)$ is constructed using the empirical cdf and by plugging in the sample estimator of the parameter (so it does not involve bootstrap expectations).  This is explained in the added section, Section 2.4.  This much is clear. However, what is still not clear to me is WHY one should use the correction $K_n(x)$ instead of $C_n(x)$. The explanation in Section 2.4 is that the bootstrap expectations become "necessary only when serial dependence distorts the properties of $F_n(x)$".  But this statement is quite vague.  Also vague is the statement in the preceding sentence which says that the empirical cdf and the parameter estimate are "reliable" under independence -- suggesting that they are not "reliable" when there is serial dependence in the data.  But what does "reliable" mean? These estimators should be consistent (under mild conditions) in both settings.

So I am wondering: Does the performance of the NPBB method suffer when the correction $C_n(x)$ is used instead of the correction $K_n(x)$?  Perhaps it is quite difficult to rigorously prove that it is necessary or advantageous to use $K_n(x)$ instead of $C_n(x)$, but can you show a difference in performance via simulation?  It may be that there is a good reason to use $K_n(x)$ instead of $C_n(x)$, but the statements given in the paper are not fully convincing.   It would suffice, in my opinion, to run a simulation in which it is shown that using $C_n(x)$ instead of $K_n(x)$ results in worse performance.  Then one could simply say that better performance is demonstrated when the correction $K_n(x)$ is used (this would back up the heuristics given in added section 2.4). Might it be that using $C_n(x)$ works out just as well as using $K_n(x)$?  I think it is important to look into this, and I don't believe it will take too much time. A simulation investigating this could be placed in supplementary material.
\end{comment}

\begin{comment}
The investigations into the performance of the NPBB under a data-driven selection of the block size are appreciated.  If the paper needs to be shortened, this part could be placed into a supplement, and the results simply alluded to in the manuscript.
\end{comment}

Thank you for the suggestion, these investigations have now been placed in a supplement, and they are still referred to in
the main manuscript.

\begin{comment}
There is an odd typo on the bottom of page 9. It says "average empirical GXSdistribution function".
\end{comment}

Thank you for pointing this out. It has been
corrected to "average empirical distribution function" in the manuscript.

\bibliographystyle{chicago}
\bibliography{citations}

\end{document}

### 2025-09-22 manuscript/supplement.tex
new reply letter

@@
 
-\title{\bf Supplement: Performance of Nonparametric
-Block Bootstrap Kolmogorov-Smirnov Test with Block Size Calibration}
+\title{\bf Supplementary Material}
 \if0\blind
@@
 \maketitle
+
+\section{Performance of Nonparametric
+Block Bootstrap Kolmogorov-Smirnov Test with Block Size Calibration}
 
@@
 
+\section{Performance of Nonparametric
+Block Bootstrap Kolmogorov-Smirnov Test with \citet{babu2004goodness} Bias Correction}
+
+A heuristic justification for the $K_n(x)$ bias correction term was provided in the main manuscript. It may also help to demonstrate
+empirically that this the block bootstrap KS test with the $K_n$ bias correction holds its size at least as
+well as the block boostrap KS test with the \citet{babu2004goodness} bias correction and is at
+least as powerful. For this reason, we conducted a simulation study
+with parameter settings identical to the main study in the paper except
+for the choice of bias correction.
+
+\begin{figure}[tbp]
+  \includegraphics[width = .9\textwidth]{figures/normal_C_n}
+  \centering
+  \vspace{-10pt}
+  \caption{Q-Q plots of the p-values testing that a time series
+    have marginal normal distribution with true data generating distribution
+    being $N(8,8)$ when using \citet{babu2004goodness}'s bias correction term.}
+  \label{fig:qq_n_C_n}
+    \hspace{3cm}
+  \includegraphics[width = .9\textwidth]{figures/gamma_C_n}
+  \vspace{-5pt}
+  \caption{Q-Q plots of the p-values testing that a time series
+    have marginal gamma distribution with true data generating distribution
+    being $\Gamma(8,1)$ when using \citet{babu2004goodness}'s bias correction term.}
+  \label{fig:qq_g_C_n}
+\end{figure}
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[scale=1]{figures/rr_C_n}
+  \caption{Empirical power curve as a function of $\tau$ for
+    $n \in \{100, 200, 400, 800\}$ and true marginal distribution
+    $\in \{N(8,8), \Gamma(8,1)\}$, when using \citet{babu2004goodness}'s bias correction term. When the data was generated from $N(8,8)$,
+    we tested for the gamma family. When the data was generated from
+    $\Gamma(8,1)$, we tested for the normal family.
+  }
+  \label{fig:rr_C_n}
+\end{figure}
+
+Based on Figures~\ref{fig:qq_n_C_n, fig:qq_g_C_n, fig:rr_C_n}, the empirical performance is very similar under either choice of bias correction term.
+
 \bibliographystyle{asa}

### 2025-09-22 code/bias_correction_analysis.R

@@ -1,5 +1,9 @@
 source('functions.R')
 my_data <- readRDS('../data/results_10000_C_n.RDS')
+my_data_50 <- readRDS('../data/results_10000_C_n_50.RDS')
+
+my_data <- rbind(my_data, my_data_50)
+
 
 my_data$tau <- case_when(my_data$phi == -0.9238795 ~ -0.75,
                          my_data$phi == -0.7071068 ~ -0.5,
@@ -72,3 +76,79 @@ gg.f <- ggplot(data = alt_data, mapping = aes(x = tau, y = as.numeric(rr),
 ggsave(filename = 'rr_C_n.pdf', plot = gg.f, 
        path = "../manuscript/figures", height = 3, width = 6)
 
+
+
+
+my_data <- readRDS('../data/results_10000_K_n.RDS')
+
+
+my_data$tau <- case_when(my_data$phi == -0.9238795 ~ -0.75,
+                         my_data$phi == -0.7071068 ~ -0.5,
+                         my_data$phi == -0.3826834 ~ -0.25,
+                         my_data$phi == 0 ~ 0,
+                         my_data$phi == 0.9238795 ~ 0.75,
+                         my_data$phi == 0.7071068 ~ 0.5,
+                         my_data$phi == 0.3826834 ~ 0.25)
+
+my_data$dist <- factor(case_when(my_data$true_dist == "normal" ~ "N(8,8)",
+                                 my_data$true_dist == "gamma" ~ "Gamma(8,1)"))
+
+my_data$my_n <- factor(case_when(my_data$n == 100 ~ "n == 100",
+                                 my_data$n == 200 ~ "n == 200",
+                                 my_data$n == 400 ~ "n == 400",
+                                 my_data$n == 800 ~ "n == 800"))
+
+
+gg.f <- ggplot(data = my_data %>% 
+                 filter(truth == 'null', true_dist == 'normal'), 
+               mapping = aes(sample = p)) +
+  scale_x_continuous(breaks=c(0, 1)) +
+  scale_y_continuous(breaks=c(0, 1)) + 
+  stat_pp_band(distribution = "unif") +
+  stat_pp_line() +
+  stat_pp_point(distribution = "unif", cex = .1) +
+  facet_grid(rows = vars(n), cols = vars(tau),
+             labeller = label_parsed) +
+  labs(x = "Theoretical Cumulative Distribution", 
[…]

### 2025-09-23 manuscript/reply2.tex
described investigation in reply letter

@@
 
-The revised manuscript incorporates the following notable change:
+The revised manuscript includes one notable change:
 \begin{enumerate}
@@
 
+We thank the AE for this helpful comment. We have added a supplement
+which includes a section on "Performance of Nonparametric
+Block Bootstrap Kolmogorov-Smirnov Test with \citet{babu2004goodness} Bias Correction". We re-ran the simulation study from the main
+manuscript, but we replaced the $K_n(x)$ bias correction with $C_n(x)$.
+The results are discussed in the supplement, and are alluded to in the main paper. Overall,
+we find that there is no noticeable improvement in either size
+or power when using the $K_n(x)$ bias correction, even for small sample
+sizes. With these results, we recommend ........
+
 \begin{comment}
@@
 
-Thank you for the suggestion, these investigations have now been placed in a supplement, and they are still referred to in
+Thank you for the suggestion, these investigations have now been placed in the "Performance of Nonparametric
+Block Bootstrap Kolmogorov-Smirnov Test with Block Size Calibration" of
+the new supplement, and they are still referred to in
 the main manuscript.
@@
 
-Thank you for pointing this out. It has been
+Thank you for pointing this out. This typo has been
 corrected to "average empirical distribution function" in the manuscript.

### 2025-10-04 manuscript/supplement.tex
described investigation in reply letter
style cleaning

@@
 
-\title{\bf Supplementary Material}
+\title{\bf Supplementary Material to\\
+  ``Nonparametric Block Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test''
+}
 \if0\blind
@@
 
-\section{Performance of Nonparametric
-Block Bootstrap Kolmogorov-Smirnov Test with Block Size Calibration}
+\section{Block Size Selection}
 
@@
 
-\section{Performance of Nonparametric
-Block Bootstrap Kolmogorov-Smirnov Test with \citet{babu2004goodness} Bias Correction}
+\section{Comparison of Two Bias Corrections}
 
-A heuristic justification for the $K_n(x)$ bias correction term was provided in the main manuscript. It may also help to demonstrate
-empirically that this the block bootstrap KS test with the $K_n$ bias correction holds its size at least as
-well as the block boostrap KS test with the \citet{babu2004goodness} bias correction and is at
+A heuristic justification for the $K_n(x)$ bias correction term was
+provided in the main manuscript. It may also help to demonstrate
+empirically that this the block bootstrap KS test with the $K_n$ bias
+correction holds its size at least as well as the block boostrap KS
+test with the \citet{babu2004goodness} bias correction and is at
 least as powerful. For this reason, we conducted a simulation study
-with parameter settings identical to the main study in the paper except
-for the choice of bias correction.
+with parameter settings identical to the main study in the paper
+except for the choice of bias correction.
 
 \begin{figure}[tbp]
-  \includegraphics[width = .9\textwidth]{figures/normal_C_n}
+  %\includegraphics[width = .9\textwidth]{figures/normal_C_n}
   \centering
@@
     \hspace{3cm}
-  \includegraphics[width = .9\textwidth]{figures/gamma_C_n}
+  %\includegraphics[width = .9\textwidth]{figures/gamma_C_n}
   \vspace{-5pt}
@@
   \centering
-  \includegraphics[scale=1]{figures/rr_C_n}
+  %\includegraphics[scale=1]{figures/rr_C_n}
   \caption{Empirical power curve as a function of $\tau$ for
@@
 
-Based on Figures~\ref{fig:qq_n_C_n, fig:qq_g_C_n, fig:rr_C_n}, the empirical performance is very similar under either choice of bias correction term.
+Based on Figures~\ref{fig:qq_n_C_n, fig:qq_g_C_n, fig:rr_C_n}, the empirical performance is very similar under either choice of bias correction term. For practical applications, we recommend.....
 

### 2025-10-04 manuscript/reply2.tex

@@
 
-I would still like a little bit of clarification about the bias correction $K_n(x)$ versus the bias correction $C_n(x)$.
-I understand that $K_n(x)$, which the authors prescribe under the circular blocks bootstrap, is based on bootstrap expectations $E_*$ of the bootstrap parameter estimate as well as of the bootstrap empirical cdf.
-In contract, the bias term $C_n(x)$ is constructed using the empirical cdf and by plugging in the sample estimator of the parameter (so it does not involve bootstrap expectations).
-This is explained in the added section, Section 2.4.
-This much is clear.
-However, what is still not clear to me is WHY one should use the correction $K_n(x)$ instead of $C_n(x)$.
-The explanation in Section 2.4 is that the bootstrap expectations become "necessary only when serial dependence distorts the properties of $F_n(x)$".
-But this statement is quite vague.
-Also vague is the statement in the preceding sentence which says that the empirical cdf and the parameter estimate are "reliable" under independence -- suggesting that they are not "reliable" when there is serial dependence in the data.
-But what does "reliable" mean?
-These estimators should be consistent (under mild conditions) in both settings.
+I would still like a little bit of clarification about the bias
+correction $K_n(x)$ versus the bias correction $C_n(x)$. I understand
+that $K_n(x)$, which the authors prescribe under the circular blocks
+bootstrap, is based on bootstrap expectations $E_*$ of the bootstrap
+parameter estimate as well as of the bootstrap empirical cdf. In
+contract, the bias term $C_n(x)$ is constructed using the empirical
+cdf and by plugging in the sample estimator of the parameter (so it
+does not involve bootstrap expectations).  This is explained in the
+added section, Section 2.4.  This much is clear. However, what is
+still not clear to me is WHY one should use the correction $K_n(x)$
+instead of $C_n(x)$. The explanation in Section 2.4 is that the
+bootstrap expectations become ``necessary only when serial dependence
+distorts the properties of $F_n(x)$''.  But this statement is quite
+vague.  Also vague is the statement in the preceding sentence which
+says that the empirical cdf and the parameter estimate are ``reliable''
+under independence -- suggesting that they are not ``reliable'' when
+there is serial dependence in the data.  But what does ``reliable''
+mean? These estimators should be consistent (under mild conditions) in
+both settings.
 
-So I am wondering: Does the performance of the NPBB method suffer when the correction $C_n(x)$ is used instead of the correction $K_n(x)$?
-Perhaps it is quite difficult to rigorously prove that it is necessary or advantageous to use $K_n(x)$ instead of $C_n(x)$, but can you show a difference in performance via simulation?
-It may be that there is a good reason to use $K_n(x)$ instead of $C_n(x)$, but the statements given in the paper are not fully convincing.
-It would suffice, in my opinion, to run a simulation in which it is shown that using $C_n(x)$ instead of $K_n(x)$ results in worse performance.
-Then one could simply say that better performance is demonstrated when the correction $K_n(x)$ is used (this would back up the heuristics given in added section 2.4).
-Might it be that using $C_n(x)$ works out just as well as using $K_n(x)$?
-I think it is important to look into this, and I don't believe it will take too much time.
-A simulation investigating this could be placed in supplementary material.
+So I am wondering: Does the performance of the NPBB method suffer when
+the correction $C_n(x)$ is used instead of the correction $K_n(x)$?
+Perhaps it is quite difficult to rigorously prove that it is necessary
+or advantageous to use $K_n(x)$ instead of $C_n(x)$, but can you show
+a difference in performance via simulation?  It may be that there is a
+good reason to use $K_n(x)$ instead of $C_n(x)$, but the statements
+given in the paper are not fully convincing.   It would suffice, in my
+opinion, to run a simulation in which it is shown that using $C_n(x)$
+instead of $K_n(x)$ results in worse performance.  Then one could
+simply say that better performance is demonstrated when the correction
+$K_n(x)$ is used (this would back up the heuristics given in added
+section 2.4). Might it be that using $C_n(x)$ works out just as well
+as using $K_n(x)$?  I think it is important to look into this, and I
+don't believe it will take too much time. A simulation investigating
+this could be placed in supplementary material.
 \end{comment}
@@
 We thank the AE for this helpful comment. We have added a supplement
-which includes a section on "Performance of Nonparametric
-Block Bootstrap Kolmogorov-Smirnov Test with \citet{babu2004goodness} Bias Correction". We re-ran the simulation study from the main
+which includes a section on ``Performance of Nonparametric
+Block Bootstrap Kolmogorov-Smirnov Test with \citet{babu2004goodness}
+Bias Correction''. We re-ran the simulation study from the main
 manuscript, but we replaced the $K_n(x)$ bias correction with $C_n(x)$.
-The results are discussed in the supplement, and are alluded to in the main paper. Overall,
-we find that there is no noticeable improvement in either size
-or power when using the $K_n(x)$ bias correction, even for small sample
-sizes. With these results, we recommend ........
+The results are discussed in the supplement, and are alluded to in the
+main paper. Overall, we find that there is no noticeable improvement
+in either size or power when using the $K_n(x)$ bias correction, even
+for small sample sizes. With these results, we recommend ........
 
 \begin{comment}
-The investigations into the performance of the NPBB under a data-driven selection of the block size are appreciated.
-If the paper needs to be shortened, this part could be placed into a supplement, and the results simply alluded to in the manuscript.
+The investigations into the performance of the NPBB under a
+data-driven selection of the block size are appreciated.  If the paper
+needs to be shortened, this part could be placed into a supplement,
+and the results simply alluded to in the manuscript.
 \end{comment}
 
-Thank you for the suggestion, these investigations have now been placed in the "Performance of Nonparametric
-Block Bootstrap Kolmogorov-Smirnov Test with Block Size Calibration" of
-the new supplement, and they are still referred to in
-the main manuscript.
+Thank you for the suggestion, these investigations have now been
+placed in the ``Performance of Nonparametric Block Bootstrap
+Kolmogorov-Smirnov Test with Block Size Calibration'' of the new
+supplement, and they are still referred to in the main manuscript.
 
 \begin{comment}
-There is an odd typo on the bottom of page 9. It says "average empirical GXSdistribution function".
+There is an odd typo on the bottom of page 9. It says ``average
+empirical GXSdistribution function''
 \end{comment}
@@
 Thank you for pointing this out. This typo has been
-corrected to "average empirical distribution function" in the manuscript.
+corrected to ``average empirical distribution function'' in the manuscript.
 

### 2025-10-04 manuscript/manuscript.tex
described investigation in reply letter
revixed section 2.4 and replied AE

@@
 
-\subsection{Heuristic justification for the bias correction term in NPBB}
+\subsection{Heuristic justification for the NPBB bias correction}
 
@@
 $\sqrt{n}(F_n^{(b)}(x) - F(x;\hat\theta^{(b)}_n))$ is the bootstrap analog of
-the KS process. However, this bootstrap process inherently possesses its own 
-mean or systematic deviation. The bias correction $K_n(x)$
+the KS process. However, this bootstrap process inherently possesses
+its own mean or systematic deviation. The bias correction $K_n(x)$
 estimates this mean.
-Specifically, $\mathbb{E}^*[F_n^{(b)}(x)]$ is the average empirical distribution function over all bootstrap samples, and
+Specifically, $\mathbb{E}^*[F_n^{(b)}(x)]$ is the average empirical
+distribution function over all bootstrap samples, and
 $\theta^*_0 = \mathbb{E}^*[\hat\theta^{(b)}_n]$ is the average of 
@@
 
-% This approach extends the logic of \citet{babu2004goodness}, who
-% introduced a similar correction for independent data, to the context
-% of serially dependent time series via block bootstrapping.
-% The bias correction term $C_n(x)$ used in the NPB method for
-% independent data could, in principle, also be approximated by a
-% bootstrap expectation in the same way as $K_n(x)$.
-% Nonetheless, under independence, the empirical distribution $F_n(x)$
-% and the parameter estimate $\hat{\theta}_n$ are already reliable, so
-% direct calculation of $C_n(x)$ is both simpler and sufficient. The use
-% of bootstrap expectations as in $K_n(x)$ becomes necessary only when
-% serial dependence distorts the properties of $F_n(x)$, making
-% block-bootstrapping-based bias estimation essential.
+Theoretically, $K_n(x)$ and the simpler plug--in correction
+$C_n(x)=\sqrt{n}\{F_n(x)-F(x;\hat\theta_n)\}$ are asymptotically
+equivalent when the series is independent or exhibits only
+short--memory dependence.  The joint process of $(F_n,\hat\theta_n)$
+converges to a mean--zero Gaussian limit whose long--run covariance
+aggregates auto--covariances across lags.  When the circular block
+bootstrap reproduces this long--run covariance, the conditional bias of
+the plug--in statistic is of smaller order $O_p(l/n)$, where $l$ is the
+block length.  The expectation centering in $K_n(x)$ removes this minor
+bias exactly but does not alter the first--order limit.  Consequently,
+both corrections yield the same asymptotic distribution, and differences
+appear only through higher--order terms that vanish as the sample size
+increases.
+
+To evaluate the finite--sample impact, we compared the two corrections
+through additional simulations; see results in Section~2 in the
+Supplement.  Across all sample sizes and dependence
+levels considered, the empirical sizes and powers were nearly identical.
+This finding supports the theoretical argument that the circular block
+bootstrap already captures the leading effects of serial correlation,
+leaving little residual bias for the expectation centering to remove.
+The comparable results of $K_n(x)$ and $C_n(x)$ suggest that the choice
+between them is largely immaterial in practice.  We therefore retain
+$K_n(x)$ for theoretical completeness and consistency of presentation,
+while acknowledging that either correction performs similarly in finite
+samples.
 
@@
 $\Gamma(8, 1)$ with seven levels of Kendall's
-$\tau \in \{-.75, -.5, -.25, 0, .25, .5, 75\}$, and
+$\tau \in \{-.75, -.50, -.25, 0, .25, .50, .75\}$, and
 sample size $n \in \{100, 200, 400, 800\}$. Kendall's $\tau$ was chosen as a
@@
 suggests varying block size based on the dependence structure of the series.
-For this reason,
-we also tried implementing our algorithm using the plug-in approach for circular
-bootstrap block size introduced in \citet{politis2004automatic}. Results and
-a discussion of this additional simulation are provided in a supplement.
-We also compared empirical performance for the block bootstrap KS test when using the $K_n(x)$ correction
+
+For this reason, we also tried implementing our algorithm using the
+plug-in approach for circular bootstrap block size introduced in
+\citet{politis2004automatic}. Results and a discussion of this
+additional simulation are provided in Section~2
+in the Supplement. We also compared empirical performance for the
+block bootstrap KS test when using the $K_n(x)$ correction
 versus the $C_n(x)$. The $K_n(x)$ correction was used
@@
 $C_n(x)$ correction is included in the supplement.
-For each setting for $F$, $\tau$, and $n$, we replicate the method 10000 times
-to get the distribution of the p-values $p_r$ for
+For each setting for $F$, $\tau$, and $n$, we replicate the method
+10000 times to get the distribution of the p-values $p_r$ for
 $r \in \{1, \dots, 10000\}$
-for the test when applied to samples from the same data generating process.
+for the test when applied to samples from the same data generating
+process.
 
@@
 significance level 0.05 as the lag-1 Kendall's~$\tau$ increases from
-$-0.5$ to $0.5$. We omitted -0.75 and 0.75 from this study because we already
+$-0.5$ to $0.5$. We omitted $-0.75$ and 0.75 from this study because we already
 found that our method doesn't work under the null hypothesis for such high
@@
 if $\tau < 0.5$, but using a $n \geq 800$ will result in
+\jy{This inequality does not make sense.}
 rejection rates close to 1 for $0.5 < \tau < 0.5$. 
@@
 
+***Section here describing practical conclusions/recommendations for
+bias correction***
+
 Several promising directions for further research emerge from

### 2025-10-04 manuscript/reply2.tex
revixed section 2.4 and replied AE

@@
 
-We thank the AE for this helpful comment. We have added a supplement
-which includes a section on ``Performance of Nonparametric
-Block Bootstrap Kolmogorov-Smirnov Test with \citet{babu2004goodness}
-Bias Correction''. We re-ran the simulation study from the main
-manuscript, but we replaced the $K_n(x)$ bias correction with $C_n(x)$.
-The results are discussed in the supplement, and are alluded to in the
-main paper. Overall, we find that there is no noticeable improvement
-in either size or power when using the $K_n(x)$ bias correction, even
-for small sample sizes. With these results, we recommend ........
+\textbf{Response to Comment on the Bias Correction Term.}
+
+We thank the reviewer for raising this insightful question and for the
+helpful suggestion to clarify the motivation for using $K_n(x)$ rather
+than $C_n(x)$.  The previously confusing paragraph about the
+``reliability'' of $F_n(x)$ and $\hat\theta_n$ has already been removed.
+Section~2.4 now presents a streamlined discussion that first explains how
+$K_n(x)$ centers the bootstrap KS process, then outlines the theoretical
+justification for its use, and finally summarizes new simulation results.
+
+A newly added paragraph clarifies that two bias corrections$C_n$ and
+$K_n$ are asymptotically equivalent under independence and
+short--memory dependence.  The preference for $K_n(x)$ arises from
+theoretical considerations: under serial dependence, the bootstrap
+analogue of $C_n(x)$ can exhibit a small $O_p(l/n)$ conditional bias
+due to cross--lag covariances between $F_n(x)$ and $\hat\theta_n$,
+where $l$ is the block length.  The expectation centering in $K_n(x)$
+removes this bias without changing the first--order limit, yielding a
+cleaner asymptotic argument.
+
+To examine whether this refinement provides tangible benefits, we added
+simulations comparing the two corrections.  Across all dependence levels
+and sample sizes considered, the empirical sizes and powers were nearly
+identical.  This outcome supports the theoretical result that both
+methods converge to the same limit distribution and that the additional
+expectation centering in $K_n(x)$ mainly improves conceptual symmetry
+rather than finite--sample performance.  We have revised
+Section~2.4 accordingly and added a brief reference in the Supplement to
+document these findings.
 
@@
 Thank you for the suggestion, these investigations have now been
-placed in the ``Performance of Nonparametric Block Bootstrap
-Kolmogorov-Smirnov Test with Block Size Calibration'' of the new
+placed in the ``Selection of Block Size'' of the newly added
 supplement, and they are still referred to in the main manuscript.

### 2025-10-04 manuscript/supplement.tex
revixed section 2.4 and replied AE

@@
 \maketitle
+
+\section{Comparison of Two Bias Corrections}
+
+A heuristic justification for the $K_n(x)$ bias correction term was
+provided in the main manuscript. It may also help to demonstrate
+empirically that this the block bootstrap KS test with the $K_n$ bias
+correction holds its size at least as well as the block boostrap KS
+test with the \citet{babu2004goodness} bias correction and is at
+least as powerful. For this reason, we conducted a simulation study
+with parameter settings identical to the main study in the paper
+except for the choice of bias correction.
+
+\begin{figure}[tbp]
+  %\includegraphics[width = .9\textwidth]{figures/normal_C_n}
+  \centering
+  \vspace{-10pt}
+  \caption{Q-Q plots of the p-values testing that a time series
+    have marginal normal distribution with true data generating distribution
+    being $N(8,8)$ when using \citet{babu2004goodness}'s bias correction term.}
+  \label{fig:qq_n_C_n}
+    \hspace{3cm}
+  %\includegraphics[width = .9\textwidth]{figures/gamma_C_n}
+  \vspace{-5pt}
+  \caption{Q-Q plots of the p-values testing that a time series
+    have marginal gamma distribution with true data generating distribution
+    being $\Gamma(8,1)$ when using \citet{babu2004goodness}'s bias correction term.}
+  \label{fig:qq_g_C_n}
+\end{figure}
+
+\begin{figure}[tbp]
+  \centering
+  %\includegraphics[scale=1]{figures/rr_C_n}
+  \caption{Empirical power curve as a function of $\tau$ for
+    $n \in \{100, 200, 400, 800\}$ and true marginal distribution
+    $\in \{N(8,8), \Gamma(8,1)\}$, when using \citet{babu2004goodness}'s bias correction term. When the data was generated from $N(8,8)$,
+    we tested for the gamma family. When the data was generated from
+    $\Gamma(8,1)$, we tested for the normal family.
+  }
+  \label{fig:rr_C_n}
+\end{figure}
+
+Based on Figures~\ref{fig:qq_n_C_n, fig:qq_g_C_n, fig:rr_C_n}, the empirical performance is very similar under either choice of bias correction term. For practical applications, we recommend.....
 
@@
 restrictive rule when setting the final block size---for example, using
-$\min \{\sqrt{n}, \hat{l}\}$.
-
-\section{Comparison of Two Bias Corrections}
-
-A heuristic justification for the $K_n(x)$ bias correction term was
-provided in the main manuscript. It may also help to demonstrate
-empirically that this the block bootstrap KS test with the $K_n$ bias
-correction holds its size at least as well as the block boostrap KS
-test with the \citet{babu2004goodness} bias correction and is at
-least as powerful. For this reason, we conducted a simulation study
-with parameter settings identical to the main study in the paper
-except for the choice of bias correction.
-
-\begin{figure}[tbp]
-  %\includegraphics[width = .9\textwidth]{figures/normal_C_n}
-  \centering
-  \vspace{-10pt}
-  \caption{Q-Q plots of the p-values testing that a time series
-    have marginal normal distribution with true data generating distribution
-    being $N(8,8)$ when using \citet{babu2004goodness}'s bias correction term.}
-  \label{fig:qq_n_C_n}
-    \hspace{3cm}
-  %\includegraphics[width = .9\textwidth]{figures/gamma_C_n}
-  \vspace{-5pt}
-  \caption{Q-Q plots of the p-values testing that a time series
-    have marginal gamma distribution with true data generating distribution
-    being $\Gamma(8,1)$ when using \citet{babu2004goodness}'s bias correction term.}
-  \label{fig:qq_g_C_n}
-\end{figure}
-
-\begin{figure}[tbp]
-  \centering
-  %\includegraphics[scale=1]{figures/rr_C_n}
-  \caption{Empirical power curve as a function of $\tau$ for
-    $n \in \{100, 200, 400, 800\}$ and true marginal distribution
-    $\in \{N(8,8), \Gamma(8,1)\}$, when using \citet{babu2004goodness}'s bias correction term. When the data was generated from $N(8,8)$,
-    we tested for the gamma family. When the data was generated from
-    $\Gamma(8,1)$, we tested for the normal family.
-  }
-  \label{fig:rr_C_n}
-\end{figure}
-
-Based on Figures~\ref{fig:qq_n_C_n, fig:qq_g_C_n, fig:rr_C_n}, the empirical performance is very similar under either choice of bias correction term. For practical applications, we recommend.....
-
-\bibliographystyle{asa}
+$\min \{\sqrt{n}, \hat{l}\}$.\bibliographystyle{asa}
 \bibliography{citations}

### 2025-10-04 manuscript/supplement.tex
uncommented figures inclusion in supp

--- 2025-10-04 manuscript/supplement.tex
@@
 
+\section{Comparison of Two Bias Corrections}
+
+A heuristic justification for the $K_n(x)$ bias correction term was
+provided in the main manuscript. It may also help to demonstrate
+empirically that this the block bootstrap KS test with the $K_n$ bias
+correction holds its size at least as well as the block boostrap KS
+test with the \citet{babu2004goodness} bias correction and is at
+least as powerful. For this reason, we conducted a simulation study
+with parameter settings identical to the main study in the paper
+except for the choice of bias correction.
+
+\begin{figure}[tbp]
+  \includegraphics[width = .9\textwidth]{figures/normal_C_n}
+  \centering
+  \vspace{-10pt}
+  \caption{Q-Q plots of the p-values testing that a time series
+    have marginal normal distribution with true data generating distribution
+    being $N(8,8)$ when using \citet{babu2004goodness}'s bias correction term.}
+  \label{fig:qq_n_C_n}
+    \hspace{3cm}
+  \includegraphics[width = .9\textwidth]{figures/gamma_C_n}
+  \vspace{-5pt}
+  \caption{Q-Q plots of the p-values testing that a time series
+    have marginal gamma distribution with true data generating distribution
+    being $\Gamma(8,1)$ when using \citet{babu2004goodness}'s bias correction term.}
+  \label{fig:qq_g_C_n}
+\end{figure}
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[scale=1]{figures/rr_C_n}
+  \caption{Empirical power curve as a function of $\tau$ for
+    $n \in \{100, 200, 400, 800\}$ and true marginal distribution
+    $\in \{N(8,8), \Gamma(8,1)\}$, when using \citet{babu2004goodness}'s bias correction term. When the data was generated from $N(8,8)$,
+    we tested for the gamma family. When the data was generated from
+    $\Gamma(8,1)$, we tested for the normal family.
+  }
+  \label{fig:rr_C_n}
+\end{figure}
+
+Based on Figures~\ref{fig:qq_n_C_n, fig:qq_g_C_n, fig:rr_C_n}, the empirical performance is very similar under either choice of bias correction term. For practical applications, we recommend.....
+
 \section{Block Size Selection}
@@
     $\sqrt{n}$ for $n \in \{100, 200, 400, 800\}$,
-    $\tau \in \{-0.75, -0.5, -0.25, 0, 0.25, 0.5, 0.75\}$, and true marginal distribution
-    $N(8,8)$ and $\Gamma(8,1)$.
+    $\tau \in \{-0.75, -0.50, -0.25, 0, 0.25, 0.50, 0.75\}$, and true
+    marginal distribution $N(8,8)$ and $\Gamma(8,1)$.
   }
@@
 
-\section{Comparison of Two Bias Corrections}
-
-A heuristic justification for the $K_n(x)$ bias correction term was
-provided in the main manuscript. It may also help to demonstrate
-empirically that this the block bootstrap KS test with the $K_n$ bias
-correction holds its size at least as well as the block boostrap KS
-test with the \citet{babu2004goodness} bias correction and is at
-least as powerful. For this reason, we conducted a simulation study
-with parameter settings identical to the main study in the paper
-except for the choice of bias correction.
-
-\begin{figure}[tbp]
-  %\includegraphics[width = .9\textwidth]{figures/normal_C_n}
-  \centering
-  \vspace{-10pt}
-  \caption{Q-Q plots of the p-values testing that a time series
-    have marginal normal distribution with true data generating distribution
-    being $N(8,8)$ when using \citet{babu2004goodness}'s bias correction term.}
-  \label{fig:qq_n_C_n}
-    \hspace{3cm}
-  %\includegraphics[width = .9\textwidth]{figures/gamma_C_n}
-  \vspace{-5pt}
-  \caption{Q-Q plots of the p-values testing that a time series
-    have marginal gamma distribution with true data generating distribution
-    being $\Gamma(8,1)$ when using \citet{babu2004goodness}'s bias correction term.}
-  \label{fig:qq_g_C_n}
-\end{figure}
-
-\begin{figure}[tbp]
-  \centering
-  %\includegraphics[scale=1]{figures/rr_C_n}
-  \caption{Empirical power curve as a function of $\tau$ for
-    $n \in \{100, 200, 400, 800\}$ and true marginal distribution
-    $\in \{N(8,8), \Gamma(8,1)\}$, when using \citet{babu2004goodness}'s bias correction term. When the data was generated from $N(8,8)$,
-    we tested for the gamma family. When the data was generated from
-    $\Gamma(8,1)$, we tested for the normal family.
-  }
-  \label{fig:rr_C_n}
-\end{figure}
-
-Based on Figures~\ref{fig:qq_n_C_n, fig:qq_g_C_n, fig:rr_C_n}, the empirical performance is very similar under either choice of bias correction term. For practical applications, we recommend.....
-
 \bibliographystyle{asa}

### 2025-10-08 manuscript/manuscript.tex
figures fixed

@@
 To evaluate the finite--sample impact, we compared the two corrections
-through additional simulations; see results in Section~2 in the
+through additional simulations; see results in Section~1 in the
 Supplement.  Across all sample sizes and dependence
@@
 if $\tau < 0.5$, but using a $n \geq 800$ will result in
-\jy{This inequality does not make sense.}
-rejection rates close to 1 for $0.5 < \tau < 0.5$. 
+rejection rates close to 1 for $-0.5 < \tau < 0.5$. 
 Results for $n \geq 400$
@@
 is reliable with no need to worry about whether the working dependence
-model approximates the true dependence model.
+model approximates the true dependence model. We note that while the
+expectation centering in our paper removes a minor bias term, it is identical
+in asymptotic performance to \citet{babu2004goodness}'s correction under 
+short--range dependence.
 
@@
 samples and in goodness-of-fit settings like ours may be limited.
-
-***Section here describing practical conclusions/recommendations for
-bias correction***
 

### 2025-10-08 manuscript/supplement.tex
figures fixed

@@
 
-Based on Figures~\ref{fig:qq_n_C_n, fig:qq_g_C_n, fig:rr_C_n}, the empirical performance is very similar under either choice of bias correction term. For practical applications, we recommend.....
+Based on Figures~\ref{fig:qq_n_C_n, fig:qq_g_C_n, fig:rr_C_n}, 
+the empirical performance in both size and power analysis is very similar under 
+either choice of bias correction 
+term. This suggests that the circular block bootstrap already corrects for
+much of the temporal dependence, and that the choice of centering
+has a very small effect on residual bias. Using $C_n(x)$ has the advantage
+of requiring slightly less computation, but we 
+still recommend $K_n(x)$ for its theoretical qualities, but acknowledge that
+performance may be indistinguishable in practical application, especially
+with large sample size and dependence that decays rapidly.
 
@@
 of the $p$-values under the null for Normal and Gamma margins, respectively.
-Recall from Figures~\ref{fig:qq_n} and \ref{fig:qq_g} that the cubic root 
+Recall from the Q-Q plots in the main paper that the cubic root 
 setting holds its size quite well with small $n$ for $|\tau| \leq 0.25$,
@@
 Figure~\ref{fig:alt_rr} shows the power results under automatic selection.
-When compared to Figure~\ref{fig:rr}, the two settings exhibit similar power
+When compared to the power curve in the main paper, the two settings exhibit 
+similar power
 for $|\tau| \leq 0.5$, with the automatic selection sometimes yielding higher

### 2025-10-08 code/bias_correction_analysis.R

@@ -2,7 +2,7 @@ source('functions.R')
 my_data <- readRDS('../data/results_10000_C_n.RDS')
 my_data_50 <- readRDS('../data/results_10000_C_n_50.RDS')
 
-my_data <- rbind(my_data, my_data_50)
+# my_data <- rbind(my_data, my_data_50)
 
 
 my_data$tau <- case_when(my_data$phi == -0.9238795 ~ -0.75,

### 2025-10-12 manuscript/manuscript.tex
minor

@@
 
-Theoretically, $K_n(x)$ and the simpler plug--in correction
-$C_n(x)=\sqrt{n}\{F_n(x)-F(x;\hat\theta_n)\}$ are asymptotically
-equivalent when the series is independent or exhibits only
-short--memory dependence.  The joint process of $(F_n,\hat\theta_n)$
-converges to a mean--zero Gaussian limit whose long--run covariance
-aggregates auto--covariances across lags.  When the circular block
-bootstrap reproduces this long--run covariance, the conditional bias of
-the plug--in statistic is of smaller order $O_p(l/n)$, where $l$ is the
+Theoretically, $K_n(x)$ and the simpler correction $C_n(x)$ are
+asymptotically equivalent when the series is independent or exhibits
+only short-memory dependence.  The joint process of
+$(F_n,\hat\theta_n)$
+converges to a mean-zero Gaussian limit whose long-run covariance
+aggregates autocovariances across lags.  When the circular block
+bootstrap reproduces this long-run covariance, the conditional bias of
+$C_n$ is of smaller order $O_p(l/n)$, where $l$ is the
 block length.  The expectation centering in $K_n(x)$ removes this minor
-bias exactly but does not alter the first--order limit.  Consequently,
+bias exactly but does not alter the first-order limit.  Consequently,
 both corrections yield the same asymptotic distribution, and differences
-appear only through higher--order terms that vanish as the sample size
+appear only through higher-order terms that vanish as the sample size
 increases.
 
-To evaluate the finite--sample impact, we compared the two corrections
+To evaluate the finite sample impact, we compared the two corrections
 through additional simulations; see results in Section~1 in the
@@
 in asymptotic performance to \citet{babu2004goodness}'s correction under 
-short--range dependence.
+short-range dependence.
 
@@
 developed for other goodness-of-fit tests based on empirical
-distributions, including the Anderson---Darling and Cramér--von
+distributions, including the Anderson--Darling and Cramér--von
 Mises tests, which are known to outperform the KS test in certain scenarios
@@
 
+\item[Additional simulation results:] Simulation studies on compariong
+of two bias corrections and block size selection are reported in an
+online pdf Supplement.
+
 \end{description}

### 2025-10-12 manuscript/reply2.tex
minor

@@
 
-\textbf{Response to Comment on the Bias Correction Term.}
-
 We thank the reviewer for raising this insightful question and for the
@@
 
-A newly added paragraph clarifies that two bias corrections$C_n$ and
+A newly added paragraph clarifies that two bias corrections $C_n$ and
 $K_n$ are asymptotically equivalent under independence and

### 2025-10-12 manuscript/supplement.tex
minor

@@
 empirically that this the block bootstrap KS test with the $K_n$ bias
-correction holds its size at least as well as the block boostrap KS
-test with the \citet{babu2004goodness} bias correction and is at
-least as powerful. For this reason, we conducted a simulation study
+correction holds its size at least as well as the block bootstrap KS
+test with the bias correction $C_n$ in \citet{babu2004goodness} and is
+at least as powerful. For this reason, we conducted a simulation study
 with parameter settings identical to the main study in the paper
@@
 
-Based on Figures~\ref{fig:qq_n_C_n, fig:qq_g_C_n, fig:rr_C_n}, 
+Based on Figures~\ref{fig:qq_n_C_n}--\ref{fig:rr_C_n}, 
 the empirical performance in both size and power analysis is very similar under 
@@
 $\tau = 0.25$, the method with block size selected by
-\citep{politis2004automatic} maintains reasonable size for moderately
+\citet{politis2004automatic} maintains reasonable size for moderately
 positively dependent series.
@@
 rejection rates, particularly for smaller negatively dependent samples.
-Overall, while the automatic selection from \citep{politis2004automatic}
+Overall, while the automatic selection from \citet{politis2004automatic}
 performs reasonably well in certain settings, we recommend caution when using

### 2025-10-16 manuscript/manuscript.tex
completed verson with convergence rate

@@
 only short-memory dependence.  The joint process of
-$(F_n,\hat\theta_n)$
-converges to a mean-zero Gaussian limit whose long-run covariance
+$\sqrt{n}(F_n, \hat\theta_n)$ converges to an $O_p(1)$
+mean-zero Gaussian limit whose long-run covariance
 aggregates autocovariances across lags.  When the circular block
 bootstrap reproduces this long-run covariance, the conditional bias of
-$C_n$ is of smaller order $O_p(l/n)$, where $l$ is the
-block length.  The expectation centering in $K_n(x)$ removes this minor
+the $\sqrt{n}$-scaled process associated with
+$C_n$ is of smaller order $O_p(l/\sqrt{n})$ as long as $l$ is
+$o(\sqrt{n})$ \citep{buhlmann1994blockwise, lahiri1999theoretical}.
+The expectation centering in $K_n(x)$ removes this minor
 bias exactly but does not alter the first-order limit.  Consequently,
@@
 leaving little residual bias for the expectation centering to remove.
-The comparable results of $K_n(x)$ and $C_n(x)$ suggest that the choice
-between them is largely immaterial in practice.  We therefore retain
-$K_n(x)$ for theoretical completeness and consistency of presentation,
-while acknowledging that either correction performs similarly in finite
-samples.
+The comparable results of $K_n(x)$ and $C_n(x)$ incidate that, under
+the examined settings, the difference between the corrections is
+small. However, this may not hold under stronger dependence, longer
+block lengths, or more complex statistics, where expectation centering
+could have a more noticeable effect. We retain $K_n(x)$ for theoretical
+completeness and consistency of presentation, while noting that either
+correction performs similarly in our simulation settings.
 
@@
 \citet{politis2004automatic}. Results and a discussion of this
-additional simulation are provided in Section~2
+additional simulation study are provided in Section~2
 in the Supplement. We also compared empirical performance for the

### 2025-10-16 manuscript/reply2.tex
completed verson with convergence rate

@@
 
-We thank the Editor and Associate Editor for the opportunity to add further detail to our manuscript.
+We thank the Editor and Associate Editor for the opportunity to add
+further detail to our manuscript.
 We have taken the revision process seriously in order
@@
 
-A newly added paragraph clarifies that two bias corrections $C_n$ and
+A newly added paragraph~3 in Section~2.4
+clarifies that two bias corrections $C_n$ and
 $K_n$ are asymptotically equivalent under independence and
-short--memory dependence.  The preference for $K_n(x)$ arises from
+short-memory dependence.  The preference for $K_n(x)$ arises from
 theoretical considerations: under serial dependence, the bootstrap
-analogue of $C_n(x)$ can exhibit a small $O_p(l/n)$ conditional bias
-due to cross--lag covariances between $F_n(x)$ and $\hat\theta_n$,
-where $l$ is the block length.  The expectation centering in $K_n(x)$
-removes this bias without changing the first--order limit, yielding a
-cleaner asymptotic argument.
+analogue of $C_n(x)$ can exhibit a small $O_p(l/\sqrt{n})$ conditional bias
+due to cross-lag covariances between $F_n(x)$ and $\hat\theta_n$,
+where $l = o(\sqrt{n})$ \citep{buhlmann1994blockwise,
+  lahiri1999theoretical}.  The expectation centering in $K_n(x)$
+removes this bias without changing the first-order limit, yielding a
+cleaner asymptotic formulation.
 
 To examine whether this refinement provides tangible benefits, we added
-simulations comparing the two corrections.  Across all dependence levels
+simulations comparing the two corrections; see Section~1 of the
+Supplement. Across all dependence levels
 and sample sizes considered, the empirical sizes and powers were nearly
 identical.  This outcome supports the theoretical result that both
-methods converge to the same limit distribution and that the additional
-expectation centering in $K_n(x)$ mainly improves conceptual symmetry
-rather than finite--sample performance.  We have revised
-Section~2.4 accordingly and added a brief reference in the Supplement to
-document these findings.
+methods converge to the same limit distribution under the examined
+conditions. However, we note that differences could become more
+pronounced under stronger dependence, longer block lengths, or more
+complex statistics. The last paragraph of Section~2.4 summarizes the
+results, with a brief reference to the Supplement.
 
@@
 
-\bibliographystyle{chicago}
+\bibliographystyle{asa}
 \bibliography{citations}

### 2025-10-17 manuscript/manuscript.tex
removed asymptotic rate languages

--- 2025-10-12 manuscript/manuscript.tex
@@
 
-When $\{X_i: i = 1, \ldots, n\}$ are further serially dependent, the statistic
-$T_n$ still provides a reasonable metric for deviation from the null
-hypothesis. Nonetheless, the asymptotic distribution of $T_n$ cannot be fixed
-even with the bias correction of \citet{babu2004goodness}, because the
-correction requires an independent sample.
+When $\{X_i: i = 1, \ldots, n\}$ are stationary with serial
+dependence, the statistic
+$T_n$ still provides a reasonable measure for deviation from the null
+hypothesis. In the next subsection, we review the NPB approach of
+\citet{babu2004goodness} for independent data, which serves as the
+basis for our extension to dependent series.
 
@@
 Continue with the case where $X_i$'s are independent but the parameters
-are unspecified. Denote by
-$F^{(b)}_n$ the empirical distribution of the $b$th bootstrap sample and let
+are unspecified. Denote by$F^{(b)}_n$ the empirical distribution of the $b$th bootstrap sample and let
 $\hat\theta^{(b)}_n$ be the parameter estimate based on the $b$th bootstrap
@@
   \[
-    C_{n}(x) = \sqrt{n}(F_n(x) - F(x; \hat\theta_n))
+    C_{n}(x) = \sqrt{n}\bigl(F_n(x) - F(x; \hat\theta_n)bigr)
   \]
@@
   \[
-    K_{n}(x) = \sqrt{n}(\mathbb{E}^{*}[F^{(b)}_n(x)] -
-    F(x; \theta_0^*))
+    K_{n}(x) = \sqrt{n}\bigl(\mathbb{E}^{*}[F^{(b)}_n(x)] -
+    F(x; \theta_0^*)\bigr)
   \]
@@
 the data with $\hat\theta_n$, the null distribution of the KS statistic 
-$T_n = \sup_x |\sqrt{n}(F_n(x) - F(x;\hat\theta_n))|$ is altered from its 
-standard form. The NPBB procedure aims to replicate this complex null 
-distribution.
+$T_n = \sup_x |\sqrt{n}(F_n(x) - F(x;\hat\theta_n))|$ is altered from
+the Kolmogorov distribution under independence and known parameters.
+The NPBB procedure aims to replicate this complex null distribution.
 
@@
 $\sqrt{n}(F_n^{(b)}(x) - F(x;\hat\theta^{(b)}_n))$ is the bootstrap analog of
-the KS process. However, this bootstrap process inherently possesses
-its own mean or systematic deviation. The bias correction $K_n(x)$
-estimates this mean.
+the goodness-of-fit process. However, this bootstrap process
+inherently possesses its own mean or systematic deviation. The bias
+correction $K_n(x)$ estimates this mean.
 Specifically, $\mathbb{E}^*[F_n^{(b)}(x)]$ is the average empirical
@@
 $\theta^*_0 = \mathbb{E}^*[\hat\theta^{(b)}_n]$ is the average of 
-the parameter estimates from these bootstrap samples. Thus,
-$K_n(x)$ quantifies 
-the expected difference, in the bootstrap world, between the empirical
-distribution function and the hypothesized distribution function
-(evaluated at the average bootstrap parameter estimate).
+the parameter estimates from these bootstrap samples. Thus, $K_n(x)$
+quantifies the expected difference, in the bootstrap world, between
+the empirical distribution function and the hypothesized distribution
+function (evaluated at the average bootstrap parameter estimate).
 Subtracting $K_n(x)$ from
 $\sqrt{n}(F_n^{(b)}(x) - F(x;\hat\theta^{(b)}_n))$ centers the 
-bootstrap KS process. This ensures that the variability of the resulting 
+bootstrap goodness-of-fit process. This ensures that the variability of the resulting 
 bootstrap statistics $T_n^{(b)}$ more faithfully reflects the variability of 
@@
 
-Theoretically, $K_n(x)$ and the simpler correction $C_n(x)$ are
-asymptotically equivalent when the series is independent or exhibits
-only short-memory dependence.  The joint process of
-$(F_n,\hat\theta_n)$
-converges to a mean-zero Gaussian limit whose long-run covariance
-aggregates autocovariances across lags.  When the circular block
-bootstrap reproduces this long-run covariance, the conditional bias of
-$C_n$ is of smaller order $O_p(l/n)$, where $l$ is the
-block length.  The expectation centering in $K_n(x)$ removes this minor
-bias exactly but does not alter the first-order limit.  Consequently,
-both corrections yield the same asymptotic distribution, and differences
-appear only through higher-order terms that vanish as the sample size
-increases.
-
-To evaluate the finite sample impact, we compared the two corrections
-through additional simulations; see results in Section~1 in the
-Supplement.  Across all sample sizes and dependence
-levels considered, the empirical sizes and powers were nearly identical.
-This finding supports the theoretical argument that the circular block
-bootstrap already captures the leading effects of serial correlation,
-leaving little residual bias for the expectation centering to remove.
-The comparable results of $K_n(x)$ and $C_n(x)$ suggest that the choice
-between them is largely immaterial in practice.  We therefore retain
-$K_n(x)$ for theoretical completeness and consistency of presentation,
-while acknowledging that either correction performs similarly in finite
-samples.
+In theory, both $K_n(x)$ and $C_n(x)$ serve the same purpose of
+centering the bootstrap goodness-of-fit process, and the circular
+block bootstrap reproduces the temporal dependence structure of the
+data. The two corrections aims the same centering, differing only in
+whether the centering uses bootstrap expectations or sample-based
+estimates. Additional simulations (see Section~1 of the Supplement)
+show that, across all dependence levels and sample sizes considered,
+the empirical sizes and powers were nearly identical. For the settings
+studied, the two corrections performed nearly identically; we retain
+$K_n(x)$ for conceptual clarity and consistency of presentation.
 
@@
 $\sigma_{\epsilon}^2$. The strength of the serial dependence is controlled by
-$\phi$, which was set to five levels:
+$\phi$, which was set to seven levels:
 $\{-0.924, -0.707, -0.383, 0, 0.383, 0.707, 0.924\}$, as these
@@
 lower, it is still reasonable to recommend our method with $n \ge 400$.
-This recommendation echoes the high sample size requirement for
-confidence intervals constructed with block bootstrapping in
-estimating location, scale, and autocorrelation parameters of
-stationary series~\citep{chandy2024sample}.
+This aligns with the high sample size requirement obverved for block
+bootstrapping confidence intervals~\citep{chandy2024sample}.
 
@@
 hypothesis that the series follows a Student's $t$ distribution with degrees of
-freedom $v = 5$ with a p-value of 0.061. In contrast,
+freedom $\nu = 5$ with a p-value of 0.061. In contrast,
 the SPB method yields a p-value of 0.0192,
@@
 NPBB variant of the KS test tailored for data with
-serial dependencies, which eliminates the need for explicit modeling serial
+serial dependencies, which eliminates the need for explicit modeling of serial
 dependence in addition to parameter specification within the hypothesized
@@
 
-The choice of block size is well known to influence the performance of
-block bootstrap methods, particularly for inference on dependent
-data. As pointed out by \citet{hall1995blocking} and
-\citet{lahiri1999theoretical}, the optimal block length depends on the
+The choice of block size strongly influences the performance of
+block-bootstrap methods for dependent data.
+As pointed out by \citet{hall1995blocking} and
+\citet{lahiri1999theoretical}, the optimal block size depends on the
 strength of serial dependence, and using a uniform choice across
@@
 \citet{lahiri2013resampling}. Following these suggestions, we applied
-the automatic block length selection method of
+the automatic block size selection method of
 \citet{politis2004automatic} for circular block bootstrap in our

### 2025-10-17 manuscript/reply2.tex
removed asymptotic rate languages

--- 2025-10-12 manuscript/reply2.tex
@@
 than $C_n(x)$.  The previously confusing paragraph about the
-``reliability'' of $F_n(x)$ and $\hat\theta_n$ has already been removed.
+``reliability'' of $F_n(x)$ and $\hat\theta_n$ has been removed.
 Section~2.4 now presents a streamlined discussion that first explains how
 $K_n(x)$ centers the bootstrap KS process, then outlines the theoretical
-justification for its use, and finally summarizes new simulation results.
+justification for its use, and finally summarizes new simulation
+results comparing the performance of $K_n$ and $C_n$.
 
-A newly added paragraph clarifies that two bias corrections $C_n$ and
-$K_n$ are asymptotically equivalent under independence and
-short--memory dependence.  The preference for $K_n(x)$ arises from
-theoretical considerations: under serial dependence, the bootstrap
-analogue of $C_n(x)$ can exhibit a small $O_p(l/n)$ conditional bias
-due to cross--lag covariances between $F_n(x)$ and $\hat\theta_n$,
-where $l$ is the block length.  The expectation centering in $K_n(x)$
-removes this bias without changing the first--order limit, yielding a
-cleaner asymptotic argument.
-
-To examine whether this refinement provides tangible benefits, we added
-simulations comparing the two corrections.  Across all dependence levels
-and sample sizes considered, the empirical sizes and powers were nearly
-identical.  This outcome supports the theoretical result that both
-methods converge to the same limit distribution and that the additional
-expectation centering in $K_n(x)$ mainly improves conceptual symmetry
-rather than finite--sample performance.  We have revised
-Section~2.4 accordingly and added a brief reference in the Supplement to
-document these findings.
+The revision clarifies that the circular block bootstrap reproduces
+the dependence structure of the data in the goodness-of-fit process.
+Both $K_n(x)$ and $C_n(x)$ serve to remove systematic bias by
+centering the process, differing only in whether the centering uses
+bootstrap expectations or sample-based estimates.
+Additional simulations (Section~1 of the Supplement) show
+that, across all dependence levels and sample sizes considered, the
+empirical sizes and powers are nearly identical. For the settings
+studied, the choice between the two corrections is therefore
+practically inconsequential. See paragraph~3 of Section~2.4 for this
+clarification and for a summary of the new simulation results.
 

### 2025-10-20 manuscript/manuscript.tex
minor
smoothed supplement

@@
 whether the centering uses bootstrap expectations or sample-based
-estimates. Additional simulations (see Section~1 of the Supplement)
+estimates. Additional simulations (see Section~S-1 of the Supplement)
 show that, across all dependence levels and sample sizes considered,
@@
 where $\phi$ is an autoregressive coefficient, and $\epsilon_i$ is a series of
-independent errors from a normal distribution with mean zero and variance
+independent errors from a Normal distribution with mean zero and variance
 $\sigma_{\epsilon}^2$. The strength of the serial dependence is controlled by
@@
 where $F^{-1}(p)$ is the quantile function for the $N(8, 8)$
-distribution and $\Phi$ is the distribution function of the standard normal
+distribution and $\Phi$ is the distribution function of the standard Normal
 distribution.
-Then we generated a marginal gamma series by the same procedure, but
+Then we generated a marginal Gamma series by the same procedure, but
 replacing $F^{-1}(p)$ with the quantile function for the $\Gamma(8, 1)$
 distribution. After the transformation
-to the marginal gamma distribution, the lag-1 autocorrelations are approximately
+to the marginal Gamma distribution, the lag-1 autocorrelations are approximately
 \[
@@
 These distributions
-were chosen to compare results on normal and non-normal
+were chosen to compare results on Normal and non-Normal
 error structures. The specific parameters were chosen because the distributions
@@
 \citet{politis2004automatic}. Results and a discussion of this
-additional simulation study are provided in Section~2
+additional simulation study are provided in Section~S-2
 in the Supplement. We also compared empirical performance for the
@@
   \caption{Q-Q plots of the p-values testing that a time series
-    have marginal normal distribution with true data generating distribution
+    have marginal Normal distribution with true data generating distribution
     being $N(8,8)$.}
@@
   \caption{Q-Q plots of the p-values testing that a time series
-    have marginal gamma distribution with true data
+    have marginal Gamma distribution with true data
     generating distribution $\Gamma(8,1)$.}
@@
 necessary, as the p-values are not aligned with the line in any of the Q-Q
-plots. This is not necessarily a cause for concern, as (for normal margins)
+plots. This is not necessarily a cause for concern, as (for Normal margins)
 a Kendall's $\tau$ of 0.75 corresponds to a $\phi$ of 0.924, which is very high.
@@
 of the p-values more so than negative serial dependences of the same strength.
-Results are very similar for normal and gamma margins.
+Results are very similar for Normal and Gamma margins.
 
@@
     $\in \{N(8,8), \Gamma(8,1)\}$. When the data was generated from $N(8,8)$,
-    we tested for the gamma family. When the data was generated from
-    $\Gamma(8,1)$, we tested for the normal family.
+    we tested for the Gamma family. When the data was generated from
+    $\Gamma(8,1)$, we tested for the Normal family.
   }
@@
 Results for $n \geq 400$
-do not appear to be to different when comparing gamma and normal
+do not appear to be to different when comparing Gamma and Normal
 margins, indicating that the method is robust to the marginal distribution.
@@
 which does not cover nonlinear dependence usually captured by autoregressive
-conditional heteroskedasticity \citep{engle1995arch}. The proposed method has
+conditional heteroskedasticity \citep{engle1995arch}. The NPBB method has
 no need to specify the serial dependence and, hence, produces results under

### 2025-10-20 manuscript/supplement.tex
smoothed supplement

--- 2025-10-04 manuscript/supplement.tex
@@
-%&latex
 \documentclass[12pt]{article}
@@
 \newcommand{\xz}[1]{\textcolor{cyan}{(XZ: #1)}}
+
+\renewcommand{\thefigure}{S-\arabic{figure}}
+\renewcommand{\thetable}{S-\arabic{table}}
+\renewcommand{\thesection}{S-\arabic{section}}
 
@@
 
-A heuristic justification for the $K_n(x)$ bias correction term was
-provided in the main manuscript. It may also help to demonstrate
-empirically that this the block bootstrap KS test with the $K_n$ bias
-correction holds its size at least as well as the block boostrap KS
-test with the \citet{babu2004goodness} bias correction and is at
-least as powerful. For this reason, we conducted a simulation study
-with parameter settings identical to the main study in the paper
-except for the choice of bias correction.
-
 \begin{figure}[tbp]
@@
   \caption{Q-Q plots of the p-values testing that a time series
-    have marginal normal distribution with true data generating distribution
-    being $N(8,8)$ when using \citet{babu2004goodness}'s bias correction term.}
+    has a marginal Normal distribution with true data generating distribution
+    being $N(8,8)$ when using  bias correction term $C_n$.}
   \label{fig:qq_n_C_n}
@@
   \caption{Q-Q plots of the p-values testing that a time series
-    have marginal gamma distribution with true data generating distribution
-    being $\Gamma(8,1)$ when using \citet{babu2004goodness}'s bias correction term.}
+    has a marginal Gamma distribution with true data generating distribution
+    being $\Gamma(8,1)$ when using  bias correction term $C_n$.}
   \label{fig:qq_g_C_n}
@@
     $n \in \{100, 200, 400, 800\}$ and true marginal distribution
-    $\in \{N(8,8), \Gamma(8,1)\}$, when using \citet{babu2004goodness}'s bias correction term. When the data was generated from $N(8,8)$,
-    we tested for the gamma family. When the data was generated from
-    $\Gamma(8,1)$, we tested for the normal family.
+    $\in \{N(8,8), \Gamma(8,1)\}$, when using bias correction term
+    $C_n$. When the data was generated from $N(8,8)$,
+    we tested for the Gamma family. When the data was generated from
+    $\Gamma(8,1)$, we tested for the Normal family.
   }
@@
 
-Based on Figures~\ref{fig:qq_n_C_n, fig:qq_g_C_n, fig:rr_C_n}, the empirical performance is very similar under either choice of bias correction term. For practical applications, we recommend.....
+To evaluate the practical difference between the two bias correction
+terms, this section presents a direct comparison between the
+nonparametric block bootstrap KS tests based on $K_n(x)$ and on
+$C_n(x)$. The $K_n(x)$ correction, which was heuristically justified in
+the main manuscript, is designed to center the empirical process in a
+manner consistent with the dependence structure of the series. In
+contrast, $C_n(x)$ is the bias correction proposed by
+\citet{babu2004goodness} for independent observations.
+
+A simulation study was conducted using the same settings as in the main
+paper, varying sample size, block length, and dependence strength, with
+the only difference being the choice of bias correction term.
+Figures~\ref{fig:qq_n_C_n}--\ref{fig:rr_C_n} present the results for
+$C_n(x)$, which are the counterparts of the figures in the main
+manuscript obtained
+using $K_n(x)$. Across the same parameter configurations, both versions
+of the test maintain comparable size and power, and their performance
+differences appear negligible for the cases examined.
+
+These findings suggest that, within the range of settings studied, the
+circular block bootstrap already removes most dependence-induced bias,
+so that the additional centering adjustment has limited practical
+impact. Although $C_n(x)$ requires slightly less computation, we
+continue to recommend $K_n(x)$ for its theoretical motivation, while
+recognizing that in the present experiments their empirical behavior is
+essentially indistinguishable.
 
 \section{Block Size Selection}
-
-The choice of block size is a key factor influencing the performance
-of block bootstrap methods, particularly in settings with serial
-dependence. While our main simulations used a fixed block size
-$l = \lceil n^{1/3} \rceil$, the optimal block size depends on the
-stength and structure of dependence \citep{hall1995blocking,
-  buhlmann1999block,  politis2004automatic}. Motivated by this, we
-further examined the use of an automatic block-length selection scheme
-as proposed by \citet{politis2004automatic}, which aims to adaptively
-choose the block size based on the data. The simulation settings
-remain the same as in the study reported earlier.
-
-% To address this, we considered  using the automatic block-length selection
-% scheme for circular block bootstrap as described in Section~3.3 of
-% \citet{politis2004automatic}. Unfortunately, using this setting results in
-% the selection of block
-% sizes that can be quite large (sometimes as large or larger than $n$), leading
-% to less variation between the bootstrapped
-% samples. Figures~\ref{fig:large_block}
-% demonstrate that for highly temporally
-% dependent samples (especially when the autocorrelation is negative),
-% the block size is frequently larger than $\sqrt{n}$. For more moderate 
-% positive temporal dependence, the block size may not be overly large
-% as frequently. Still, even for these moderately dependent samples, the 
-% block sizes are almost always larger than $l = \lceil n^{1/3} \rceil$, a setting
-% which was considered optimal by \citep{buhlmann1999block}. This
-% is demonstrated in Figure~\ref{fig:block_dist} with a histogram
-% of the selected block sizes for the 20000 samples with $n = 800$, $\tau = 0.5$, 
-% and $X_i \sim N(8, 8)$.
 
@@
   \caption{Distribution of the selected block sizes using
-  \citet{politis2004automatic}'s procedure applied to 20000 length-800 time 
-  series with
+    \citet{politis2004automatic}'s procedure applied to 20,000
+    time series of length-800 with
     Kendall's $\tau = 0.5$ data generating distribution $N(8,8)$. The vertical
-    dashed line is $l = \lceil n^{1/3} \rceil$ for $n = 800$, which is equivalent 
-    to 10.
+    dashed line marks $l = \lceil n^{1/3} \rceil \approx 10$.
   }
@@
 
-Automatic block size selection tends to yield larger block sizes than our
-fixed choice $l = \lceil n^{1/3} \rceil$, as expected, but under strong
-negative or very strong positive dependence it systematically produces
-block sizes that are excessively large, sometimes as large as or larger
-than $n$. Note that in our simulations, we set the final block size to 
-$\min \{n, \hat l\}$, where
-$\hat l$ is the block size selected by \citet{politis2004automatic}'s
-procedure. Figure~\ref{fig:block_dist} illustrates the typical behavior by
-showing the distribution of block sizes selected by \citet{politis2004automatic}
-for $n = 800$, $\tau = 0.5$, and $X_i \sim N(8,8)$. The majority of selected
-block sizes exceed $\lceil n^{1/3} \rceil$, and many approach or exceed
-$\sqrt{n}$. Figure~\ref{fig:large_block} presents the proportion of selected
-block sizes exceeding $\sqrt{n}$ across varying levels of dependence and sample 
-sizes.
-The selection of block sizes larger than $\sqrt{n}$ occurs systematically under 
-strong
-negative dependence, and is also frequent under very strong positive dependence.
+The choice of block size plays a central role in determining the
+finite-sample behavior of block bootstrap methods when serial
+dependence is present. Although our main simulations used the fixed rule
+$l = \lceil n^{1/3} \rceil$, the effective block size can vary with the
+strength and pattern of dependence
+\citep{hall1995blocking, buhlmann1999block, politis2004automatic}.
+To evaluate the impact of data-driven selection, we examined the
+automatic block-length procedure proposed by
+\citet{politis2004automatic}, which selects the block size adaptively
+from the observed series. All other simulation settings were kept
+identical to those in the main paper.
+
+The automatically selected block sizes were generally larger than the
+fixed choice $l = \lceil n^{1/3} \rceil$, as anticipated, but the
+procedure sometimes produced unrealistically large values under certain
+dependence structures. In particular, when the series exhibited strong
+negative or very strong positive dependence, the selected block sizes
+were often excessively large---occasionally comparable to or exceeding
+the sample size $n$. In our implementation, we set the final block
+length to $\min\{n, \hat{l}\}$, where $\hat{l}$ denotes the value
+returned by the automatic procedure. Figure~\ref{fig:block_dist}
+illustrates the typical distribution of selected block sizes for $n =
+800$, $\tau = 0.5$, and $X_i \sim N(8,8)$, showing that most values
+exceed $\lceil n^{1/3} \rceil$ and many approach or surpass
+$\sqrt{n}$. Figure~\ref{fig:large_block} further summarizes the
+proportion of selected block sizes greater than $\sqrt{n}$ across
+different dependence levels and sample sizes, indicating that such
+oversizing occurs systematically under strong negative and very strong
+positive dependence.
 
@@
   \caption{Q-Q plots of the p-values testing that a time series
-    have marginal normal distribution with true data generating distribution
+    has a marginal Normal distribution with true data generating distribution
     being $N(8,8)$, when using \citet{politis2004automatic}'s procedure
@@
   \caption{Q-Q plots of the p-values testing that a time series
-    have marginal gamma distribution with true data generating distribution
+    has a marginal Gamma distribution with true data generating distribution
     being $\Gamma(8,1)$, when using \citet{politis2004automatic}'s procedure
@@
     to select block sizes. When the data was generated from $N(8,8)$,
-    we tested for the gamma family. When the data was generated from
-    $\Gamma(8,1)$, we tested for the normal family.
+    we tested for the Gamma family. When the data was generated from
+    $\Gamma(8,1)$, we tested for the Normal family.
   }
@@
 
-We evaluated the size and power performance of the NPBB test under automatic
-block length selection. The size performance is shown
-in Figures~\ref{fig:alt_qq_n} and \ref{fig:alt_qq_g}, which display Q-Q plots
-of the $p$-values under the null for Normal and Gamma margins, respectively.
-Recall from Figures~\ref{fig:qq_n} and \ref{fig:qq_g} that the cubic root 
-setting holds its size quite well with small $n$ for $|\tau| \leq 0.25$,
-whereas achieving nominal size for $|\tau| \geq 0.5$ require
-$n > 200$, and for $|\tau| \geq 0.75$ require $n > 800$. The automatic
-selection shows similar limitations for $|\tau| > 0.5$, where it does
-not hold its size. Moreover, deviations from the diagonal line appear
-larger for negative $\tau$, likely due to the high proportion of
-occurrence of overly large block sizes. For example, while the cubic
-root setting held its size well at $\tau = -0.25$ with small~$n$, the
-automatic selection does not. At the same time, under $\tau = 0$ or
-$\tau = 0.25$, the method with block size selected by
-\citep{politis2004automatic} maintains reasonable size for moderately
-positively dependent series.
+We next evaluated the size and power performance of the NPBB test when
+the block length was chosen automatically.
+Figures~\ref{fig:alt_qq_n} and~\ref{fig:alt_qq_g} display the empirical
+size through Q--Q plots of the $p$-values under the null for Normal and
+Gamma margins, respectively. For reference, the main paper showed that
+the fixed cubic root rule $l = \lceil n^{1/3} \rceil$ maintained size
+reasonably well for small~$n$ when $|\tau| \le 0.25$, whereas achieving
+nominal size required $n > 200$ for $|\tau| \ge 0.5$ and $n > 800$ for
+$|\tau| \ge 0.75$. The automatic selection exhibits a similar pattern
+of limitations: for $|\tau| > 0.5$, the empirical size again departs
+from nominal levels. Deviations from the diagonal line are more
+pronounced for negative~$\tau$, consistent with the high frequency of
+excessively large block sizes in those cases. For instance, while the
+cubic root rule held size adequately at $\tau = -0.25$ with small~$n$,
+the automatic procedure no longer does. In contrast, for
+$\tau \in \{0, 0.25\}$, the automatically selected block sizes yield
+size control comparable to the fixed rule, indicating satisfactory
+performance for weak or moderate positive dependence.
 
-Figure~\ref{fig:alt_rr} shows the power results under automatic selection.
-When compared to Figure~\ref{fig:rr}, the two settings exhibit similar power
-for $|\tau| \leq 0.5$, with the automatic selection sometimes yielding higher
-rejection rates, particularly for smaller negatively dependent samples.
-Overall, while the automatic selection from \citep{politis2004automatic}
-performs reasonably well in certain settings, we recommend caution when using
-it under negative~$\tau$ and smaller sample sizes, where maintaining nominal
-size may be more difficult. In such cases, it may be sensible to apply a more
-restrictive rule when setting the final block size---for example, using
-$\min \{\sqrt{n}, \hat{l}\}$.
+Figure~\ref{fig:alt_rr} summarizes the power analysis under automatic
+selection. Relative to the main paper’s results based on the cubic root
+rule, the two approaches show broadly similar power for
+$|\tau| \le 0.5$, with the automatic method occasionally achieving
+slightly higher rejection rates for small samples with mild negative
+dependence. Overall, these findings indicate that the automatic
+procedure of \citet{politis2004automatic} performs reasonably well under
+most conditions studied but may yield unstable results when dependence
+is negative and sample sizes are small. In such cases, it is advisable
+to adopt a more restrictive cap on the final block size---for example,
+setting it to $\min\{\sqrt{n}, \hat{l}\}$---to avoid excessive block
+lengths that can distort the bootstrap resampling.
 
